### 2019-01-22 thesis_1/main.tex
initial commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Masters/Doctoral Thesis 
% LaTeX Template
% Version 2.5 (27/8/17)
%
% This template was downloaded from:
% http://www.LaTeXTemplates.com
%
% Version 2.x major modifications by:
% Vel (vel@latextemplates.com)
%
% This template is based on a template by:
% Steve Gunn (http://users.ecs.soton.ac.uk/srg/softwaretools/document/templates/)
% Sunil Patel (http://www.sunilpatel.co.uk/thesis-template/)
%
% Template license:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
%oneside,
% ngerman for German
english,
% Single line spacing, alternatives: onehalfspacing or doublespacing
singlespacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%nolistspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
%parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
%chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
%consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

% Required for inputting international characters
\usepackage[utf8]{inputenc}

% Output font encoding for international characters
\usepackage[T1]{fontenc}

% Use the Palatino font by default
\usepackage{mathpazo}

% Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex}

% The filename of the bibliography
\addbibresource{example.bib}

% Required to generate language-dependent quotes in the bibliography
\usepackage[autostyle=true]{csquotes}

%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

\geometry{
	paper=a4paper,      % Change to letterpaper for US letter
	inner=2.5cm,        % Inner margin
	outer=3.8cm,        % Outer margin
	bindingoffset=.5cm, % Binding offset
	top=1.5cm,          % Top margin
	bottom=1.5cm,       % Bottom margin
	%showframe,         % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------
%	THESIS INFORMATION
%----------------------------------------------------------------------------------------

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Thesis Title}

% Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\supervisor{Dra. Dora \textsc{Medina}}

% Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\examiner{}

% Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\degree{Master in Nanotechnology (MNT)}

% Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\author{Osamu \textsc{Katagiri}}

% Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname
\addresses{Campo Grande 1341, Residencial El Refugio, CP 76146, Santiago de Querétaro, Qro.}

% Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\subject{Nanotechnology}

% Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\keywords{tec, de, monterrey}

% Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\university{\href{https://tec.mx/}{Instituto Tecnonólogico y de Estudios Superiores de Monterrey}}

% Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\department{\href{https://tec.mx/}{School of Engineering and Sciences}}

% Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\group{\href{https://tec.mx/es/estado-de-mexico}{ITESM Campus Estado de México}}

% Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
\faculty{\href{https://samp.itesm.mx/Programas/VistaPrograma?clave=MNT16&modoVista=Default&idioma=ES&cols=0}{Faculty: Nanotechnology}}

\AtBeginDocument{
\hypersetup{pdftitle=\ttitle}          % Set the PDF's title to your title
\hypersetup{pdfauthor=\authorname}     % Set the PDF's author to your name
\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
}

\begin{document}

% Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages
\frontmatter

% Default to the plain heading style until the thesis style is called for the body content
\pagestyle{plain}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}
\begin{center}

\vspace*{.06\textheight}
{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
\textsc{\Large Masters Thesis}\\[0.5cm]      % Thesis type

\HRule \\[0.4cm]                            % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm]                            % Horizontal line

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\

% Author name - remove the \href bracket to remove the link
%\href{http://www.osamukatagiri.com}{\authorname}
\authorname
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\

% Supervisor name - remove the \href bracket to remove the link
%\href{http://www.doramedina.com}{\supname}
\supname
\end{flushright}
\end{minipage}\\[3cm]

\vfill

\large \textit{A thesis submitted in fulfillment of the requirements\\ for the degree of
% University requirement text
\degreename}\\[0.3cm]
\textit{in}\\[0.4cm]
% Research group name and department name
\groupname\\\deptname\\[2cm]

\vfill

% Date
{\large \today}\\[4cm]
% University/department logo - uncomment to place it
%\includegraphics{./Figures/uniLogo.png}

\vfill
\end{center}
\end{titlepage}

%----------------------------------------------------------------------------------------
%	DECLARATION PAGE
%----------------------------------------------------------------------------------------

\begin{declaration}
\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

\noindent Signed:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

\noindent Date:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

\cleardoublepage

%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{0.2\textheight}

\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak

\hfill Dave Barry

%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents

The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots \\

\noindent
\textbf{keywords:} \keywordnames
\end{abstract}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
There are a number of people without whom this thesis might not have been written,
and to whom I am greatly indebted.\\

To my mother, Helena, who continues to learn, grow and develop and who has been a
source of encouragement and inspiration to me throughout my life, a very special
thank you for providing a ‘writing space’ and for nurturing me through the months of
writing. And also for the myriad of ways in which, throughout my life, you have
actively supported me in my determination to find and realise my potential, and to
make this contribution to our world.\\

To my mother-in-law, Maryam, known only briefly but loved and missed, who
represented to me ‘living proof’ of Black women’s ability to redefine and recreate our
lives despite, and maybe even because of, the tremendously constraining, oppressive
and repressive situations in which we often exist.\\

To my dear husband, Bala who remains willing to engage with the struggle, and
ensuing discomfort, of having a partner who refuses to accept the given role of the
"Black woman" and is actively engaged in redefining and redesigning that role. A
very special thank you for your practical and emotional support as I added the roles of
wife and then mother, to the competing demands of business, work, study and
personal development.\\

Thanks to dear Kamal and Azaria, for being so supportive - even when being ‘without
Mum’ was hard, and for your help with the bibliography and diagrams. This work is
for, and because of you and all the generations to come. It is dedicated to all our
journeys in learning to thrive.\\

It is also dedicated to Josephine - friend, ‘sister’, colleague, ‘co- traveller’ and
researcher - who knowingly and unknowingly- led me to an understanding of some of
the more subtle challenges to our ability to thrive. If our attempts to claim our right to
speak our truth, and to unravel and follow the threads through which our oppression is
maintained, and are instrumental in helping one other Black woman from ‘going over
the edge’ - in which sight we continuously live our lives - perhaps, it might be seen
that your invaluable contribution to the attainment of many of the insights gained was
worth it. It is also written in honour of all our my grandmothers, and their mothers,
and grandmothers, and to all our and mothers and grandmothers, who though not
marked by history struggled so heroically to resist the definitions attributed to them
by the dominant system and communicate messages of hope and expectation.
I am also very grateful to Maya Angelou, for the inspiration she has been to methrough her writings, poetry readings and as a living representation of a woman
thriving. Thanks to Mary Washington, Alice Walker, Jackie Kay, Buchi Emecheta,
Toni Cade, Lauretta Ngobo, bell hooks, and other Black women writers of the 1980’s,
who in telling stories for and about us validated me and my experiences in ways I
cannot begin to explain here.\\

Loving thanks to my friends / learning partners, Agnes, Susan, Ulana and Namonya,
who played such important roles along the journey, as we mutually engaged in
making sense of the various challenges we faced and in providing encouragement to
each other at those times when it seemed impossible to continue. I offer my gratitude
and appreciation to my supervisors, Judi Marshall and Peter Reason, for the deft ways
in which you lovingly challenged and supported me through out the whole of this
work - knowing when to push and when to let up. I offer special thanks to those who
supported me in the mechanics of producing this thesis. Rosemary, for reading and rereading drafts; Rajwant for editing and proofing; Susan for help with typing and for
helping me get ‘unstuck’ with this thesis on many occasions; and Peter and Trevor for
‘rescuing’ me at those times when I was almost defeated by the technology. Most of
all thanks to God the Divine who continues to make the impossible possible.

\end{acknowledgements}

%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------

\tableofcontents % Prints the main table of contents

\listoffigures % Prints the list of figures

\listoftables % Prints the list of tables

%----------------------------------------------------------------------------------------
%	ABBREVIATIONS
%----------------------------------------------------------------------------------------

\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)

\textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\

\end{abbreviations}

%----------------------------------------------------------------------------------------
%	PHYSICAL CONSTANTS/OTHER DEFINITIONS
%----------------------------------------------------------------------------------------

\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table

% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it

Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
%Constant Name & $Symbol$ & $Constant Value$ with units\\

\end{constants}

%----------------------------------------------------------------------------------------
%	SYMBOLS
%----------------------------------------------------------------------------------------

\begin{symbols}{lll} % Include a list of Symbols (a three column table)

$a$ & distance & \si{\meter} \\
$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
%Symbol & Name & Unit \\

\addlinespace % Gap to separate the Roman symbols from the Greek

$\omega$ & angular frequency & \si{\radian} \\

\end{symbols}

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------

\dedicatory{Dedicated to}
This thesis work is dedicated to my parents, William and Karen Ryan, who have always loved me unconditionally and whose good examples have taught me to work hard for the things that I aspire to achieve. They have been a constant source of support and encouragement during the challenges of graduate school and life. I am truly thankful for having you in my life.

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - CHAPTERS
%----------------------------------------------------------------------------------------

\mainmatter % Begin numeric (1,2,3...) page numbering

\pagestyle{thesis} % Return the page headers back to the "thesis" style

% Include the chapters of the thesis as separate files from the Chapters folder
% Uncomment the lines as you write the chapters

\include{Chapters/Chapter1}
%\include{Chapters/Chapter2} 
%\include{Chapters/Chapter3}
%\include{Chapters/Chapter4} 
%\include{Chapters/Chapter5}

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%----------------------------------------------------------------------------------------

\appendix % Cue to tell LaTeX that the following "chapters" are Appendices

% Include the appendices of the thesis as separate files from the Appendices folder
% Uncomment the lines as you write the Appendices

\include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\printbibliography[heading=bibintoc]

%----------------------------------------------------------------------------------------

\end{document}

### 2019-03-16 thesis_proposal_1/main.tex
thesis proposal template

--- 2019-01-22 thesis_1/main.tex
@@
 
-% Your supervisor's name, this is used in the title page, print it elsewhere with \supname
-\supervisor{Dra. Dora \textsc{Medina}}
+% Your supervisor's name, this is used in the title page, print it elsewhere with \supname and \cosupname
+\supervisor{Dr. Héctor Alán \textsc{Aguirre} Soto}
+\cosupervisor{Dra. Dora Iliana \textsc{Medina} Medina}
 
@@
 % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
-\degree{Master in Nanotechnology (MNT)}
+\degree{Master of Science in Nanotechnology (MNT)}
 
 % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
-\author{Osamu \textsc{Katagiri}}
+\author{Antonio Osamu \textsc{Katagiri} Tanaka}
 
 % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname
-\addresses{Campo Grande 1341, Residencial El Refugio, CP 76146, Santiago de Querétaro, Qro.}
+\addresses{Estado de México, Atizapan de Zaragoza}
 
@@
 
+% Your university's campus name and URL, this is used in the title page and abstract, print it elsewhere with \campusname
+\campus{\href{https://tec.mx/}{Campus Estado de México}}
+
 % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
@@
 % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
-\group{\href{https://tec.mx/es/estado-de-mexico}{ITESM Campus Estado de México}}
+\group{\href{https://www.medinadora.com/people}{ITESM \campusname}}
 
@@
 %----------------------------------------------------------------------------------------
-%	TITLE PAGE
+%	TITLE/COVER PAGE
 %----------------------------------------------------------------------------------------
@@
 % Author name - remove the \href bracket to remove the link
-%\href{http://www.osamukatagiri.com}{\authorname}
-\authorname
+\href{https://linkedin.com/in/osamu-katagiri-84b2b940/}{\authorname}
+%\authorname
 \end{flushleft}
@@
 \begin{flushright} \large
-\emph{Supervisor:} \\
-
+\emph{Principal Advisor:} \\
 % Supervisor name - remove the \href bracket to remove the link
@@
 \supname
+
+\bigskip
+
+\emph{Co-advisor and\\Director of Program:} \\
+% Supervisor name - remove the \href bracket to remove the link
+\href{https://www.medinadora.com/}{\cosupname}
+%\cosupname
 \end{flushright}
@@
 
-% Date
-{\large \today}\\[4cm]
+% Address and Date
+{\addressname \text{, } \large \today}\\[4cm]
 % University/department logo - uncomment to place it
@@
 %----------------------------------------------------------------------------------------
-%	DECLARATION PAGE
+%	COMMITTEE'S PAGE
 %----------------------------------------------------------------------------------------
 
-\begin{declaration}
-\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
-\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
+\begin{committee}
+\addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
+The committee members, hereby, recommend that the proposal by \authorname to be accepted to develop the thesis project as a partial requirement for the degree of \degreename.
 
-\begin{itemize} 
-\item This work was done wholly or mainly while in candidature for a research degree at this University.
-\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
-\item Where I have consulted the published work of others, this is always clearly attributed.
-\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
-\item I have acknowledged all main sources of help.
-\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
-\end{itemize}
+\vfill
 
-\noindent Signed:\\
-\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
+\begin{flushright} \large
 
-\noindent Date:\\
-\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
-\end{declaration}
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+
+\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
+%\href{http://www.alanaguirre.com}{\supname}
+\supname\\
+Tecnológico de Monterrey\\
+\emph{Principal Advisor}
+
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+
+\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
+%\href{http://www.alanaguirre.com}{\supname}
+1st committee member name\\
+1st committee member institution\\
+\emph{Committee Member}
+
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+
+\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
+%\href{http://www.alanaguirre.com}{\supname}
+2nd committee member name\\
+2nd committee member institution\\
+\emph{Committee Member}
+
+\end{flushright}
+
+\vfill
+
+\begin{center}
+
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+
+\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
+\cosupname \\
+\emph{Director of Program in Nanotechnology}\\
+School of Engineering and Sciences\\
+%\href{http://www.doramedina.com}{\supname}
+
+\bigskip
+\bigskip
+{\addressname \text{, } \large \today}\\[4cm]
+
+\end{center}
+\end{committee}
 
@@
 %----------------------------------------------------------------------------------------
-%	QUOTATION PAGE
+%	LIST OF CONTENTS/FIGURES/TABLES PAGES
 %----------------------------------------------------------------------------------------
 
-\vspace*{0.2\textheight}
+\tableofcontents % Prints the main table of contents
 
-\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
+%\listoffigures % Prints the list of figures
 
-\hfill Dave Barry
+%\listoftables % Prints the list of tables
 
@@
 %----------------------------------------------------------------------------------------
-%	ACKNOWLEDGEMENTS
-%----------------------------------------------------------------------------------------
-
-\begin{acknowledgements}
-\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
-There are a number of people without whom this thesis might not have been written,
-and to whom I am greatly indebted.\\
-
-To my mother, Helena, who continues to learn, grow and develop and who has been a
-source of encouragement and inspiration to me throughout my life, a very special
-thank you for providing a ‘writing space’ and for nurturing me through the months of
-writing. And also for the myriad of ways in which, throughout my life, you have
-actively supported me in my determination to find and realise my potential, and to
-make this contribution to our world.\\
-
-To my mother-in-law, Maryam, known only briefly but loved and missed, who
-represented to me ‘living proof’ of Black women’s ability to redefine and recreate our
-lives despite, and maybe even because of, the tremendously constraining, oppressive
-and repressive situations in which we often exist.\\
-
-To my dear husband, Bala who remains willing to engage with the struggle, and
-ensuing discomfort, of having a partner who refuses to accept the given role of the
-"Black woman" and is actively engaged in redefining and redesigning that role. A
-very special thank you for your practical and emotional support as I added the roles of
-wife and then mother, to the competing demands of business, work, study and
-personal development.\\
-
-Thanks to dear Kamal and Azaria, for being so supportive - even when being ‘without
-Mum’ was hard, and for your help with the bibliography and diagrams. This work is
-for, and because of you and all the generations to come. It is dedicated to all our
-journeys in learning to thrive.\\
-
-It is also dedicated to Josephine - friend, ‘sister’, colleague, ‘co- traveller’ and
-researcher - who knowingly and unknowingly- led me to an understanding of some of
-the more subtle challenges to our ability to thrive. If our attempts to claim our right to
-speak our truth, and to unravel and follow the threads through which our oppression is
-maintained, and are instrumental in helping one other Black woman from ‘going over
-the edge’ - in which sight we continuously live our lives - perhaps, it might be seen
-that your invaluable contribution to the attainment of many of the insights gained was
-worth it. It is also written in honour of all our my grandmothers, and their mothers,
-and grandmothers, and to all our and mothers and grandmothers, who though not
-marked by history struggled so heroically to resist the definitions attributed to them
-by the dominant system and communicate messages of hope and expectation.
-I am also very grateful to Maya Angelou, for the inspiration she has been to methrough her writings, poetry readings and as a living representation of a woman
-thriving. Thanks to Mary Washington, Alice Walker, Jackie Kay, Buchi Emecheta,
-Toni Cade, Lauretta Ngobo, bell hooks, and other Black women writers of the 1980’s,
-who in telling stories for and about us validated me and my experiences in ways I
-cannot begin to explain here.\\
-
-Loving thanks to my friends / learning partners, Agnes, Susan, Ulana and Namonya,
-who played such important roles along the journey, as we mutually engaged in
-making sense of the various challenges we faced and in providing encouragement to
-each other at those times when it seemed impossible to continue. I offer my gratitude
-and appreciation to my supervisors, Judi Marshall and Peter Reason, for the deft ways
-in which you lovingly challenged and supported me through out the whole of this
-work - knowing when to push and when to let up. I offer special thanks to those who
-supported me in the mechanics of producing this thesis. Rosemary, for reading and rereading drafts; Rajwant for editing and proofing; Susan for help with typing and for
-helping me get ‘unstuck’ with this thesis on many occasions; and Peter and Trevor for
-‘rescuing’ me at those times when I was almost defeated by the technology. Most of
-all thanks to God the Divine who continues to make the impossible possible.
-
-\end{acknowledgements}
-
-%----------------------------------------------------------------------------------------
-%	LIST OF CONTENTS/FIGURES/TABLES PAGES
-%----------------------------------------------------------------------------------------
-
-\tableofcontents % Prints the main table of contents
-
-\listoffigures % Prints the list of figures
-
-\listoftables % Prints the list of tables
-
-%----------------------------------------------------------------------------------------
 %	ABBREVIATIONS
@@
 
-\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
+%\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
 
-\textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\
+%\textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\
 
-\end{abbreviations}
+%\end{abbreviations}
 
@@
 
-\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
+%\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
 
@@
 
-Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
+%Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
 %Constant Name & $Symbol$ & $Constant Value$ with units\\
 
-\end{constants}
+%\end{constants}
 
@@
 
-\begin{symbols}{lll} % Include a list of Symbols (a three column table)
+%\begin{symbols}{lll} % Include a list of Symbols (a three column table)
 
-$a$ & distance & \si{\meter} \\
-$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
+%$a$ & distance & \si{\meter} \\
+%$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
 %Symbol & Name & Unit \\
 
-\addlinespace % Gap to separate the Roman symbols from the Greek
+%\addlinespace % Gap to separate the Roman symbols from the Greek
 
-$\omega$ & angular frequency & \si{\radian} \\
+%$\omega$ & angular frequency & \si{\radian} \\
 
-\end{symbols}
-
-%----------------------------------------------------------------------------------------
-%	DEDICATION
-%----------------------------------------------------------------------------------------
-
-\dedicatory{Dedicated to}
-This thesis work is dedicated to my parents, William and Karen Ryan, who have always loved me unconditionally and whose good examples have taught me to work hard for the things that I aspire to achieve.
-They have been a constant source of support and encouragement during the challenges of graduate school and life.
-I am truly thankful for having you in my life.
+%\end{symbols}
 
@@
 
-\include{Chapters/Chapter1}
-%\include{Chapters/Chapter2} 
-%\include{Chapters/Chapter3}
-%\include{Chapters/Chapter4} 
-%\include{Chapters/Chapter5}
+\include{Chapters/1_Introduction}
+\include{Chapters/2_ProblmemDefinitionAndMotivation} 
+\include{Chapters/3_HypothesisAndResearchQuestions}
+\include{Chapters/4_Objectives} 
+\include{Chapters/5_TheoreticalFramework}
+
+\include{Chapters/__IntroToLaTeX}
 
@@
 
-\include{Appendices/AppendixA}
+%\include{Appendices/AppendixA}
 %\include{Appendices/AppendixB}
@@
 
-\printbibliography[heading=bibintoc]
+\printbibliography
 

### 2019-03-16 thesis_proposal_1/Chapters/1_Introduction.tex
min feature

% Chapter Template

\chapter{Introduction} % Main chapter title

\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Main Section 1}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam ultricies lacinia euismod. Nam tempus risus in dolor rhoncus in interdum enim tincidunt. Donec vel nunc neque. In condimentum ullamcorper quam non consequat. Fusce sagittis tempor feugiat. Fusce magna erat, molestie eu convallis ut, tempus sed arcu. Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus. Integer dapibus ligula ac risus convallis pellentesque.

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat. Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper. Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue. In hac habitasse platea dictumst.

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Subsection 2}
Morbi rutrum odio eget arcu adipiscing sodales. Aenean et purus a est pulvinar pellentesque. Cras in elit neque, quis varius elit. Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci. Sed nec nulla auctor odio aliquet consequat. Ut nec nulla in ante ullamcorper aliquam at sed dolor. Phasellus fermentum magna in augue gravida cursus. Cras sed pretium lorem. Pellentesque eget ornare odio. Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Main Section 2}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

### 2019-03-18 thesis_proposal_1/Chapters/1_Introduction.tex
abstract summary

@@
 
-\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+\label{Chapter:Introduction}
 
@@
 
-\section{Main Section 1}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam ultricies lacinia euismod.
-Nam tempus risus in dolor rhoncus in interdum enim tincidunt.
-Donec vel nunc neque.
-In condimentum ullamcorper quam non consequat.
-Fusce sagittis tempor feugiat.
-Fusce magna erat, molestie eu convallis ut, tempus sed arcu.
-Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus.
-Integer dapibus ligula ac risus convallis pellentesque.
-
 %-----------------------------------
@@
 %-----------------------------------
-\subsection{Subsection 1}
-
-Nunc posuere quam at lectus tristique eu ultrices augue venenatis.
-Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat.
-Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper.
-Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue.
-In hac habitasse platea dictumst.
-
-%-----------------------------------
-%	SUBSECTION 2
-%-----------------------------------
-
-\subsection{Subsection 2}
-Morbi rutrum odio eget arcu adipiscing sodales.
-Aenean et purus a est pulvinar pellentesque.
-Cras in elit neque, quis varius elit.
-Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci.
-Sed nec nulla auctor odio aliquet consequat.
-Ut nec nulla in ante ullamcorper aliquam at sed dolor.
-Phasellus fermentum magna in augue gravida cursus.
-Cras sed pretium lorem.
-Pellentesque eget ornare odio.
-Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.
-
-%----------------------------------------------------------------------------------------
-%	SECTION 2
-%----------------------------------------------------------------------------------------
-
-\section{Main Section 2}
-
-Sed ullamcorper quam eu nisl interdum at interdum enim egestas.
-Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor.
-Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula.
-Donec eget quam sapien, in viverra eros.
-Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum.
-Vestibulum in orci quis felis tempor lacinia.
-Vivamus ornare ultrices facilisis.
-Ut hendrerit volutpat vulputate.
-Morbi condimentum venenatis augue, id porta ipsum vulputate in.
-Curabitur luctus tempus justo.
-Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl.
-Aliquam dictum sagittis velit sed iaculis.
-Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis.
-Nam elit libero, tincidunt ut aliquam at, molestie in quam.
-Aenean rhoncus vehicula hendrerit.

### 2019-03-18 thesis_proposal_1/Chapters/2_ProblmemDefinitionAndMotivation.tex
min feature
abstract summary

--- 2019-03-16 thesis_proposal_1/Chapters/1_Introduction.tex
@@
 
-\chapter{Introduction} % Main chapter title
+\chapter{Problem Definition and Motivation} % Main chapter title
 
-\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+\label{Chapter:ProblemDefinitionandMotivation}
 

### 2019-03-18 thesis_proposal_1/Chapters/3_HypothesisAndResearchQuestions.tex
min feature
abstract summary

--- 2019-03-16 thesis_proposal_1/Chapters/1_Introduction.tex
@@
 
-\chapter{Introduction} % Main chapter title
+\chapter{Hypothesis and Research Questions} % Main chapter title
 
-\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+\label{Chapter:HypothesisandResearchQuestions}
 

### 2019-03-18 thesis_proposal_1/Chapters/4_Objectives.tex
min feature
abstract summary

--- 2019-03-16 thesis_proposal_1/Chapters/1_Introduction.tex
@@
 
-\chapter{Introduction} % Main chapter title
+\chapter{Objectives} % Main chapter title
 
-\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+\label{Chapter:Objectives}
 

### 2019-03-18 thesis_proposal_1/Chapters/5_TheoreticalFramework.tex
min feature
abstract summary

--- 2019-03-16 thesis_proposal_1/Chapters/1_Introduction.tex
@@
 
-\chapter{Introduction} % Main chapter title
+\chapter{Theoretical Framework} % Main chapter title
 
-\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+\label{Chapter:TheoreticalFramework}
 

### 2019-03-18 thesis_proposal_1/main.tex
min feature
abstract summary

@@
 % Uncomment to add space between paragraphs
-%parskip,
+parskip,
 % Uncomment to not load the hyperref package
@@
 % Use the bibtex backend with the authoryear citation style (which resembles APA)
-\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex}
+\usepackage[backend=biber,style=authoryear,natbib=true]{biblatex}
+% MLA, APA, or IEEE? - https://www.overleaf.com/learn/latex/Biblatex_citation_styles
+%\usepackage[style=apa, backend=biber]{biblatex}
 
@@
 % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\thesistitle{Thesis Title}
+\thesistitle{Design of Polymer Solutions for the Fabrication of Conducting Carbon Nano-wires}
 
@@
 {\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
-\textsc{\Large Masters Thesis}\\[0.5cm]      % Thesis type
+\textsc{\Large Masters Thesis Proposal}\\[0.5cm]      % Thesis type
 
@@
 
-The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots \\
+Carbon fibers are versatile materials composed of carbon chains with a wide range of applications.
+Carbon nanowires have been fabricated with a photoresist, but little is known about polymers that can produce more conductive carbon nanowires after pyrolysis.
+FFES or Far field electrospinning is a inexpensive process to produce polymer fibers, but with low accuracy due to electric instabilities.
+Near field electrospinning (NFES) is similar to FFES, but with a reduced distance between the fiber source and the collector and higher precision.
+Various polymer solutions have being tested and measured through NFSE and photopolymerization processes; it was found that it is not possible to predict the behaviour of the electrospinning process, so additional properties are to be considered to achieve a stable process.
+The properties of the polymer solution can be amended to obtain a electrospun-able, photopolymerizable and pyrolyzable/graphitizable fibers.
+Analyse the rheology of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nanowires with them.
+Design polymer solutions that can be electrospun by NFES, photopolymerized, and then pyrolyzed into conducting carbon nanowires.
+The use of the newly designed polymer solution within the NFES-Photopolymerization-Pyrolysis process can be amended to achieve mass scale manufacturing of carbon nanowires in a cheap, continuous, simple and reproducible manner.
+The new/tailored polymer solution can be used to synthesize carbon nanowires with high conductive properties and reduced thickness.
+\\
 
@@
 \include{Chapters/5_TheoreticalFramework}
+\include{Chapters/6_Methodology}
+\include{Chapters/7_WorkPlan}
 
-\include{Chapters/__IntroToLaTeX}
+%\include{Chapters/__IntroToLaTeX}
 
@@
 
-\printbibliography
+\printbibliography[title={References}]
 

### 2019-03-18 thesis_proposal_1/main.tex
another draft

@@
 
+Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to the  //
+
+Over the last couple of decades, Carbon Nanowires (CNWs) have found important applications in the field of rapid label-free biosensing platforms for their excellent electrical, thermal and chemical properties.
+Despite the growing interest in incorporating these materials into sensitive analytical devices, there has been limited research efforts that explore the realistic incorporation of these structures into broader microsystems.
+The present dissertation explores two Advanced Additive Manufacturing (AdAM) techniques for the fabrication of CNWs with promising characteristics for sensing applications.
+The first technique, Electro-Mechanical Spinning (EMS) is a relatively new method for the production of CNWs with highly-oriented patterning capabilities, and is assessed in terms of the minimum feature sizes that it can attain reproducibly.
+The second method, Multiple Photon Polymerization (MPP) is a mature laser manufacturing technique that offers high repeatability, yet it has remained largely unexplored in the field of carbon materials.
+This work presents a study of how MPP can be used to create CNWs in terms of micro-fabrication parameters like laser power and scanning velocity.
+A thorough review study of the surface properties required for carbon materials to become eligible candidates in biosensing is also included in this dissertation.
+Lastly, an application of CNWs is presented, in which a Joule Heating technique is used to induce controlled breaking of the wires to produce nano-scale separated carbon electrodes, which hold potential for micro/nano particle manipulation in microfluidics.
+//
+
 Carbon fibers are versatile materials composed of carbon chains with a wide range of applications.

### 2019-03-18 thesis_proposal_1/main.tex
abstract done

--- 2019-03-16 thesis_proposal_1/main.tex
@@
 % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
-\keywords{tec, de, monterrey}
+\keywords{nanotechnology, carbon, nano-wires, electrospinning, NFES}
 
@@
 \vspace*{.06\textheight}
-{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
-\textsc{\Large Masters Thesis}\\[0.5cm]      % Thesis type
+{\scshape\LARGE \univname\par} % University name
 
-\HRule \\[0.4cm]                            % Horizontal line
-{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
-\HRule \\[1.5cm]                            % Horizontal line
+\begin{center}
+\includegraphics[width=0.15\textwidth]{./Figures/uniLogo.png}
+\end{center}
+
+\vspace{0.5cm}
+\textsc{\Large Masters Thesis Proposal}\\[0.5cm]      % Thesis type
+
+\HRule \\[0.5cm]                            % Horizontal line
+{\huge \bfseries \ttitle\par}\vspace{0.25cm} % Thesis title
+\HRule \\[0.5cm]                            % Horizontal line
 
@@
 \end{flushright}
-\end{minipage}\\[3cm]
+\end{minipage}\\[2cm]
 
@@
 
-\large \textit{A thesis submitted in fulfillment of the requirements\\ for the degree of
+\large \textit{A thesis proposal submitted in fulfillment of the requirements\\ for the degree of
 % University requirement text
@@
 
-The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots \\
+Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to their matchless properties in electrical matters.
+Regardless of the high interest in the implementation of carbon nano-wires in several applications and devices, no feasible processes have been developed to synthesize carbon nano-wires.
+Carbon nano-wires have been fabricated with the use of a photoresist, but little is known about polymers that can produce more conductive carbon nano-wires after pyrolysis.
+Various polymer solutions have being tested and measured through near field electrospinning (NFES) and photopolymerization processes; it was found that it is not possible to predict the behaviour of the electrospinning process, so additional properties are to be considered to achieve a stable manufacturing process.
+The thesis proposal is to analyse the rheology of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nanowires with them.
+The research process will include the design of polymer solutions that can be electrospun, photopolymerized, and then pyrolyzed into conducting carbon nanowires.
+The research is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of carbon nano-wires in a cheap, continuous, simple and reproducible manner.
+\\
 

### 2019-03-18 thesis_proposal_1/Chapters/3_HypothesisAndResearchQuestions.tex
new examples

@@
 %-----------------------------------
+
+1.2 Research hypotheses
+
+The research hypotheses of the following dissertation are divided into two sections.
+The first section is related to additive manufacturing techniques used to produce the CNWs; the second one includes the proposed hypotheses with regards to functionalization those structures.
+
+1.2.1 Additive manufacturing
+
+Hypothesis 1 (H1): The geometry (diameter and length) of CNWs produced by ElectroMechanical Spinning (EMS) can be controlled by having consistent fabrication parameters (stage velocity, voltage, dispense rate, polymer formulation).
+A given set of parameters should, therefore, result in a repeatable nanowire structure with defined geometry.
+We expect this repeatability will be evident in the statistical deviation from a mean value of the measured diameter and length.
+
+Hypothesis 2 (H2): MPP lithography can be used to produce sub-micrometric CNWs by pyrolysis of a highly cross-linked photoresin, such as SU-8.
+The dimensions of the produced CNWs are expected to depend on the process variables.
+By controlling the energy dosage impinged on the photoresin, the localized polymerized volume will vary in size.
+Therefore, it is expected that dosage will be directly correlated to the diameter of the polymerized polymeric microstructure precursor (and consequently, the diameter of its carbonized version, the CNWs).
+
+1.2.2 Functionalization of carbon nanowires
+
+Hypothesis 3 (H3): Through a suitable surface chemistry modification, CNWs can provide a platform that can serve for biomolecule immobilization.
+
+Hypothesis 4 (H4): Localized surface modification of CNWs can be achieved by chemically protecting the rest of the device and addressing only the wire area.
+• Glassy carbon is chemically inert material. We expect this material will be inefficient for biomolecule immobilization.
+• By locally depositing a material with stronger affinity to biomolecules, we can study the performance of Suspended CNW as biosensors.
+In this study, the molecule 4- aminobenzoic acid (4-ABA) will be explored as the interfacing molecule between the surface wire area (composed of GC) and a protein probe.
+
+1.3 Research questions
+
+The following research questions were formulated as a function of hypotheses 1-4:
+
+1.
+H1: What are the parameters (stage velocity, voltage, dispense rate, polymer formulation) for EMS that allow the fabrication of CNWs?
+Why have those parameters failed to produce reproducible CNWs in the past?
+Are there research efforts that suggest the use of an automated deposition of polymeric nanofibers with EMS, which can be pyrolyzed into CNWs?
+
+2.
+H2: In the literature, is there any evidence of the process parameters that should be employed to fabricate SU-8 polymeric structures with MPP?
+How does the minimum characteristic features that can be obtained through MPP (i.e.
+voxels) scale with two and three photon absorption (TPA, 3PA) processes?
+What are the specific role played by variables such as the intensity of the laser, frequency of operation, writing speed (or stage velocity) in the efficiency of the 2PA/3PA process?
+
+3.
+H3: What are the most important surface characteristics that allow protein immobilization in an interface?
+Is there any evidence in the literature that GC can serve as a platform for biomolecule detection?
+What are the most common functionalization techniques that have been used in carbon nanostructures?
+What are the most recent techniques and, are they promising?
+
+4.
+H4: What methods can be employed to achieve local surface modification of CNWs?
+Are there any reported methods in the literature?
+Is there a manufacturing method that can allow the selective addressing of the CNW micro/nano-surface, while protecting the rest of the C-MEMS device?
+Are Electrochemical Modification (ECM) techniques suitable for local modification of GC materials?

### 2019-03-18 thesis_proposal_1/Chapters/4_Objectives.tex
new examples

@@
 %-----------------------------------
+
+In view of the manufacturing and surface chemistry challenges posed by CNW biosensor
+fabrication, the following dissertation is divided in two central objectives:
+
+1) To explore the feasibility of using advanced additive manufacturing techniques to improve the reproducibility of CNW production in the nanoscale range.20 In particular, EMS and Direct Femtosecond Laser Writing (DLW) techniques will be studied and tested in terms of their fabrication parameters.
+Furthermore, morphological and electrical characterization of the obtained samples will be key in the discussion and assessment of this objective.
+
+2) To study the surface chemistry of CNWs as a material for biomolecule immobilization.
+The goal will be to explore a functionalization technique that will allow the surface modification of GC to achieve the immobilization of a biomolecule.
+GC will be studied in particular since it is the predominant material obtained from advanced manufacturing techniques like EMS46 and TPP.50

### 2019-03-19 thesis_proposal_1/Chapters/1_Introduction.tex
new examples
thesis proposal progress

@@
 \label{Chapter:Introduction}
+
+Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
+Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
+\cite{Siddiqui2019} Due to some of matchless properties that allow carbon nano-materials to be utilized within multiple functionalities including high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties and high conductivity.
+\cite{Siddiqui2019}
+
+This document bestow a thesis proposal to perform a research to engineer and design a polymer solution to achieve mass scale manufacturing of carbon nano-wires in a cheap, continuous, simple and reproducible manner.
+The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization and carbonization, as they have shown to be promising methods for synthesis of carbon nano-materials.
+\cite{Cardenas2017} A number of processes have been developed for specific purposes of polymeric nano-fibers, some include surface deposition, composites, and chemical adjustments.
+Polymeric nano-fibers could be also pyrolyzed to generate carbon nano-wires with conductive capabilities \cite{Madou2011} for electrochemical sensing and energy storage purposes.
+
+Nanotechnology has explored different polymer patterning techniques to integrate carbon nano-wires structures.
+One technique is known as far-field electrospinning, a process in which electrified jets of polymer solution are jettisoned to synthesize nano-fibers which then are pyrolyzed at high temperatures.
+One sub-technique derived from electrospinning is near field electromechanical spinning or EMS.
+EMS has proved to deliver high control in patterning polymeric nano-fibers.
+\cite{Cardenas2017}
+
+The proposal is to continue the previous work done in regards of the synthesis of carbon nano-wires.
+Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist.
+\cite{Cardenas2017} This proposal research is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by nier field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires.
+The polymer solutions described in \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.
+
+Near-field electrospinning or NFES allows large scale manufacturability combined with controlled guidance.
+\cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation so that the resulting in limited control for nano-fiber patterning.
+\cite{Madou2011} the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.
 

### 2019-03-19 thesis_proposal_1/Chapters/3_HypothesisAndResearchQuestions.tex
thesis proposal progress

--- 2019-03-18 thesis_proposal_1/Chapters/3_HypothesisAndResearchQuestions.tex
@@
 \label{Chapter:HypothesisandResearchQuestions}
+
+\section{Research Hypothesis}
+
+The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers to synthesize carbon nano-wires with specified dimensions (diameter and length).
+
+\section{Research Questions}
+
+\begin{itemize}
+	\item{
+	Are there any evidence of carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
+	}
+	\item{
+	What are the process parameters to consider/control for the fabrication processes of carbon nano-wires? 
+	}
+	\item{
+	What rheological properties are to be controlled/tested to deliver a electrospun-able and pyrozable polymer solution?	
+	}
+	\item{
+	Are there any efforts employed to the design of polymer solutions that can be electrospun, photopolymerized, and pyrolyzed into conducting carbon nanowires?
+	}
+	\item{
+	Are the fabrication parameters defined in \cite{Cardenas2017} optimal for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
+	}
+\end{itemize}
 

### 2019-03-19 thesis_proposal_1/Chapters/4_Objectives.tex
thesis proposal progress

--- 2019-03-18 thesis_proposal_1/Chapters/4_Objectives.tex
@@
 \label{Chapter:Objectives}
+
+\section{General objective}
+Exercise the practice and feasibility of a new synthesis process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner.
+
+\section{Particular objective}
+Design polymer solutions that can be electrospun by NFES, photopolymerized, and then pyrolyzed; through rheological analyses to determine if they can be easily employed for conducting carbon nano-wire synthesis.
 

### 2019-03-19 thesis_proposal_1/Chapters/4_Objectives.tex
proposal in preogress

--- 2019-03-18 thesis_proposal_1/Chapters/4_Objectives.tex
@@
 \label{Chapter:Objectives}
+
+\section{General objective}
+Exercise the practice and feasibility of a new synthesis process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner.
+
+\section{Particular objective}
+
+\begin{itemize}
+	\item{
+Design polymer solutions that can be electrospun by NFES, photopolymerized, and then pyrolyzed.
+    }
+    \item{
+    Through rheological analyses, determine if polymer solutions can be easily employed for conducting carbon nano-wire synthesis.    
+    }
+\end{itemize}
 

### 2019-03-19 thesis_proposal_1/Chapters/5_TheoreticalFramework.tex
thesis proposal progress
proposal in preogress

@@
 \label{Chapter:TheoreticalFramework}
+
+% This involves a thorough state-ofthe-art bibliographic review, the building of a formal foundation, the study of related techniques, analysis and awareness of previous works and study of fundamental aspects that can help carry on your research.
+
+\section{Electro-Mechanical Spinning}
+Diverse polymer patterning techniques have been developed to integrate and synthesize carbon nano-wires.
+A typical technique is electrospinning.
+Electrospinning requires the application of an electrostatic force to a polymer solution to spin fibers.
+The applied electric field, the solution conductivity, jet length, solution viscosity surrounding gas, flow rate and the collector geometry are important parameters that influence the fiber formation during the spinning.
+\cite{Nataraj2012} Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
+The process in which the electrospun jet can be controlled near the
+tip is called NFES or near-field electrospinning.
+\cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning.
+\cite{Nataraj2012}
+
+\section{Carbon nano-fibers}
+Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand nm; composed mostly by carbon atoms aligned parallel to the long axis of the fiber.
+\cite{Nataraj2012} Carbon nano-wires are different from carbon tubes, as CMWs are not composed by graphene sheets in cylindrical form.
+\cite{Nataraj2012}
 

### 2019-03-19 thesis_proposal_1/Chapters/2_ProblmemDefinitionAndMotivation.tex
thesis proposal progress
proposal in preogress
new save

@@
 \label{Chapter:ProblemDefinitionandMotivation}
+
+% Describe the current situation of this problem.
+% identifying the obstacles and the possible applications of your research.
+% background of the problem (e.g. origins, previous attempts, etc.). 
+% State the problem in detail mentioning all relative aspects, variables, relationships,
+% stressing on the importance of finding a solution to the problem.
+
+Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques.
+However little is known about polymers that can produce conductive carbon nanowires after pyrolysis.
+In the past years photon polymerization processes have been apllied to the fabrication of nano-structures with the use of a photoresist.
+\cite{Boer2014} Photon polymerization techniques
+
+This method is a subset of SLA; however, the use of a multiphoton femtosecond laser produces results that are quite unique (Greiner et al., 2012; Ovsianikov et al., 2012).
+The resolutions are exceptional (Figure 10.15(a)–(c)), with nanoscale tolerances and the ability to produce very small pores and highly detailed structures (Hribar et al., 2014).
+Similar to that of SLA, a photocurable resin is required and currently only small objects can be produced and the resins are often toxic (Figure 10.15(d)–(f)).
+However, these limitations are well known and there are groups working intensively to overcome these challenges.
+Ovsianikov et al.
+(2012) demonstrated 3D photografting of a PEG-based matrix to produce functionalized regions within the hydrogel.
+Laza et al.
+(2012) also performed two-photon polymerization within lamellar fluid flow (Figure 10.15(g)–(i)).
+Without turbulence, the precise flow allows a small structure such as a spring to be produced in a continuous process.
+While not built as an entire scaffolding structure, fabricating elements that later can be combined into a scaffold is an exciting prospect.
 

### 2019-03-20 thesis_proposal_1/Chapters/1_Introduction.tex
proposal in preogress
proposal almost done

@@
 
+% Introduction to the Context where the proposal is going to be carried out.
 Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
-Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
+\cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
 \cite{Siddiqui2019} Due to some of matchless properties that allow carbon nano-materials to be utilized within multiple functionalities including high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties and high conductivity.
 \cite{Siddiqui2019}
+
+% Describe the Problematic Situation
+% Briefly describe the problem, the relevant aspects and factors that are part of it.
+% Justifify the relevance to provide a solution to the problem.
+% Explain what has been previoulsy done to find a solution to the problem.
+% Describe the proposed solution model
+% State the expected achievements by solving this problema.
+% Describe the organization of the document.
 

### 2019-03-20 thesis_proposal_1/Chapters/2_ProblmemDefinitionAndMotivation.tex
proposal almost done

--- 2019-03-18 thesis_proposal_1/Chapters/2_ProblmemDefinitionAndMotivation.tex
@@
 \label{Chapter:ProblemDefinitionandMotivation}
+
+% Describe the current situation of this problem.
+% identifying the obstacles and the possible applications of your research.
+% background of the problem (e.g. origins, previous attempts, etc.). 
+% State the problem in detail mentioning all relative aspects, variables, relationships,
+% stressing on the importance of finding a solution to the problem.
+
+Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques.
+However little is known about polymers that can produce conductive carbon nanowires after pyrolysis.
+In the past years photon polymerization processes have been apllied to the fabrication of nano-structures with the use of a photoresist.
+\cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures.
+\cite{Hribar2014} Normally Photon polymerization processes can only produce small objects and the resins are often toxic.
+\cite{Ovsianikov2012}
+
+On the other hand, electrospinning has been acknowledged for as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires.
+Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner.
+
+Since electrospinning is to be a better alternative for carbon nano-wire synthesis processes, for that purpose, it is required to develop polymer solutions that can be electrospun by near-field electrospinning (NFES) or electromechanic spinning, photopolymerized and pyrolyzed into conducting carbon nanowires.
+Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
+\cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
+\cite{Siddiqui2019} However most application are not currently feasible  due to the lack of a continuous, simple and reproducible fabrication method.
+With the newly required polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more application will become feasible.
 

### 2019-03-20 thesis_proposal_1/Chapters/2_ProblmemDefinitionAndMotivation.tex
landscape pages

@@
 
+\subsubsection*{\color{mygray}[Chapter ready for review]}
 % Describe the current situation of this problem.
@@
 Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques.
-However little is known about polymers that can produce conductive carbon nanowires after pyrolysis.
-In the past years photon polymerization processes have been apllied to the fabrication of nano-structures with the use of a photoresist.
-\cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures.
-\cite{Hribar2014} Normally Photon polymerization processes can only produce small objects and the resins are often toxic.
+However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis.
+In the past years photon polymerization processes have been applied to the fabrication of nano-structures with the use of a photoresist.
+\cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures, \cite{Hribar2014} However, it is typical of photon polymerization processes to yield small objects with waste resins that are often toxic.
 \cite{Ovsianikov2012}
@@
 Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner.
+\cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis.
+Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires.
+As stated in \cite{Cardenas2017}, mechano-electrispinning is an early technology invention, and brings new challenges, such as the reproducibility of carbon nano-wire production.
 
-Since electrospinning is to be a better alternative for carbon nano-wire synthesis processes, for that purpose, it is required to develop polymer solutions that can be electrospun by near-field electrospinning (NFES) or electromechanic spinning, photopolymerized and pyrolyzed into conducting carbon nanowires.
+Since electrospinning seems to be a better alternative for carbon nano-wire synthesis processes; and for that purpose of its implementation, it is required to develop polymer solutions that can be mechano-electrospun, photopolymerized and pyrolyzed into conducting carbon nano-wires.
 Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
@@
 \cite{Siddiqui2019} However most application are not currently feasible due to the lack of a continuous, simple and reproducible fabrication method.
-With the newly required polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more application will become feasible.
+With the newly designed polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more applications will become feasible.
 

### 2019-03-20 thesis_proposal_1/main.tex
thesis proposal progress
proposal in preogress
landscape pages

@@
 english,
-% Single line spacing, alternatives: onehalfspacing or doublespacing
-singlespacing,
+% Single line spacing, alternatives: singlespacing, onehalfspacing or doublespacing
+onehalfspacing,
 % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
 %draft,
-% If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
-%nolistspacing,
+% If the document is nolistspacing, onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
+onehalfspacing,
 % Uncomment to add the list of figures/tables/etc to the table of contents
@@
 % Uncomment to place the chapter title next to the number on one line
-%chapterinoneline,
+chapterinoneline,
 % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
@@
 
+% Use tu justify paragraphs
+\usepackage{ragged2e}
+
 % Use the bibtex backend with the authoryear citation style (which resembles APA)
-\usepackage[backend=biber,style=authoryear,natbib=true]{biblatex}
+\usepackage[backend=biber,natbib=true]{biblatex}
 % MLA, APA, or IEEE? - https://www.overleaf.com/learn/latex/Biblatex_citation_styles
@@
 % The filename of the bibliography
-\addbibresource{example.bib}
+\addbibresource{mainBiblio.bib}
 
@@
 \usepackage[autostyle=true]{csquotes}
+
+% to set default colours
+\usepackage{xcolor}
+\definecolor{mygray}{gray}{0.5}
+
+% for gantt charts
+\usepackage{tikz}
+\usepackage{gantt}
+
+\usepackage{lscape}
 
@@
 % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\thesistitle{Design of Polymer Solutions for the Fabrication of Conducting Carbon Nano-wires}
+\thesistitle{Graphitic carbon suspended nano-wires synthesis through mechanoelectrospinning of photocrosslinkable polymers}
 
@@
 
-\HRule \\[0.5cm]                            % Horizontal line
-{\huge \bfseries \ttitle\par}\vspace{0.25cm} % Thesis title
+\HRule \\%[0.5cm]                            % Horizontal line
+{\huge \bfseries \ttitle\par}\vspace{0.0cm} % Thesis title
 \HRule \\[0.5cm]                            % Horizontal line
@@
 \end{flushright}
-\end{minipage}\\[2cm]
+\end{minipage}\\[0.5cm]
 
@@
 % University requirement text
-\degreename}\\[0.3cm]
-\textit{in}\\[0.4cm]
+\degreename}\\[0.25cm]
+\textit{in}\\[0.25cm]
 % Research group name and department name
-\groupname\\\deptname\\[2cm]
+\groupname\\\deptname\\[1cm]
 
@@
 \bigskip
-\bigskip
 
@@
 %\href{http://www.alanaguirre.com}{\supname}
-1st committee member name\\
-1st committee member institution\\
+Marc \textsc{Madou}\\
+Tecnológico de Monterrey\\
 \emph{Committee Member}
 
-\bigskip
 \bigskip
@@
 %\href{http://www.alanaguirre.com}{\supname}
-2nd committee member name\\
-2nd committee member institution\\
+Sergio Omar \textsc{Martínez} Chapa\\
+Tecnológico de Monterrey\\
 \emph{Committee Member}
@@
 
-\bigskip
 \bigskip
@@
 
+\setlength{\parskip}{1.5em} % Paragraph spacing
+%\RaggedRight
+{\fontsize{12}{15} \selectfont
+
 \include{Chapters/1_Introduction}
@@
 \include{Chapters/7_WorkPlan}
+
+}
 

### 2019-03-26 thesis_proposal_1/main.tex
thesis proposal 1st draft done
Dora as co-advisor

@@
 % Two side (alternating margins) for binding by default, uncomment to switch to one side
-%oneside,
+oneside,
 % ngerman for German
@@
 % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\thesistitle{Graphitic carbon suspended nano-wires synthesis through mechanoelectrospinning of photocrosslinkable polymers}
+\thesistitle{Fabrication of graphitic-carbon suspended nanowires through mechanoelectrospinning of photocrosslinkable polymers}
 
@@
 \addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
-The committee members, hereby, recommend that the proposal by \authorname to be accepted to develop the thesis project as a partial requirement for the degree of \degreename.
-
-\vfill
+The committee members, hereby, recommend that the proposal by \authorname \text{ }to be accepted to develop the thesis project as a partial requirement for the degree of \degreename.
 
@@
 \bigskip
-\bigskip
-\bigskip
+\medskip
 
-\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
 %\href{http://www.alanaguirre.com}{\supname}
@@
 \bigskip
+\medskip
+
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
+%\href{http://www.alanaguirre.com}{\supname}
+\cosupname\\
+Tecnológico de Monterrey\\
+\emph{Co-Advisor}
+
 \bigskip
 \bigskip
+\medskip
 
-\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
 %\href{http://www.alanaguirre.com}{\supname}
@@
 \bigskip
-\bigskip
-\bigskip
+\medskip
 
-\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
 \cosupname \\
@@
 \bigskip
-\bigskip
-{\addressname \text{, } \large \today}\\[4cm]
+{\addressname \text{, } \large \today}\\[0cm]
 

### 2019-03-26 thesis_proposal_1/main.tex
abstract disposed

@@
 
-Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to their matchless properties in electrical matters.
-Regardless of the high interest in the implementation of carbon nano-wires in several applications and devices, no feasible processes have been developed to synthesize carbon nano-wires.
+Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to their unrivalled properties in electrical matters.
+Regardless of the high interest in the implementation of carbon nano-wires in several applications and devices, no feasible processes have been developed to fabricate carbon nano-wires.
 Carbon nano-wires have been fabricated with the use of a photoresist, but little is known about polymers that can produce more conductive carbon nano-wires after pyrolysis.
-Various polymer solutions have being tested and measured through near field electrospinning (NFES) and photopolymerization processes; it was found that it is not possible to predict the behaviour of the electrospinning process, so additional properties are to be considered to achieve a stable manufacturing process.
-The thesis proposal is to analyse the rheology of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nanowires with them.
+Various polymer solutions have been tested in near field electrospinning (NFES) and photopolymerization processes, however, few have been tested for nano-wire frabication purposes through pyrolysis.
+The intention behind the thesis proposal is to implement rheology analyses of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nanowires with them.
+This thesis work arises from the need to test a greater variety of polymers with the goal to design a polymer solution ti fabricate carbon nano-wires with better properties than the current SU-8 polymeric nano-fibers.
 The research process will include the design of polymer solutions that can be electrospun, photopolymerized, and then pyrolyzed into conducting carbon nanowires.
-The research is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of carbon nano-wires in a cheap, continuous, simple and reproducible manner.
+On the other hand, it is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of carbon nano-wires in a cheap, continuous, simple and reproducible manner.
 \\

### 2019-03-26 thesis_proposal_1/main.tex
min fix

@@
 Various polymer solutions have been tested in near field electrospinning (NFES) and photopolymerization processes, however, few have been tested for nano-wire frabication purposes through pyrolysis.
-The intention behind the thesis proposal is to implement rheology analyses of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nanowires with them.
-This thesis work arises from the need to test a greater variety of polymers with the goal to design a polymer solution ti fabricate carbon nano-wires with better properties than the current SU-8 polymeric nano-fibers.
+The intention behind the thesis proposal is to implement rheology analyses of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nano-wires with them.
+This thesis work arises from the need to test a greater variety of polymers with the goal to design a polymer solution to fabricate carbon nano-wires with better properties than the current SU-8 polymeric nano-fibers.
 The research process will include the design of polymer solutions that can be electrospun, photopolymerized, and then pyrolyzed into conducting carbon nanowires.
-On the other hand, it is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of carbon nano-wires in a cheap, continuous, simple and reproducible manner.
+On the other hand, it is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of carbon nano-wires in a inexpensive, continuous, simple and reproducible manner.
 \\

### 2019-03-28 thesis_proposal_1/Chapters/1_Introduction.tex
landscape pages
rheo measurements

@@
 
+\subsubsection*{\color{mygray}[Chapter ready for review]}
 % Introduction to the Context where the proposal is going to be carried out.
-Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
-\cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
-\cite{Siddiqui2019} Due to some of matchless properties that allow carbon nano-materials to be utilized within multiple functionalities including high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties and high conductivity.
-\cite{Siddiqui2019}
-
 % Describe the Problematic Situation
@@
 
-This document bestow a thesis proposal to perform a research to engineer and design a polymer solution to achieve mass scale manufacturing of carbon nano-wires in a cheap, continuous, simple and reproducible manner.
-The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization and carbonization, as they have shown to be promising methods for synthesis of carbon nano-materials.
-\cite{Cardenas2017} A number of processes have been developed for specific purposes of polymeric nano-fibers, some include surface deposition, composites, and chemical adjustments.
-Polymeric nano-fibers could be also pyrolyzed to generate carbon nano-wires with conductive capabilities \cite{Madou2011} for electrochemical sensing and energy storage purposes.
+Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
+\cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
+\cite{Siddiqui2019} Due to some of matchless properties that allow carbon nano-materials to be utilized within multiple functionalities including high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties and high conductivity.
+\cite{Siddiqui2019}
+
+This document bestow a thesis proposal to perform a research to engineer and design a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner.
+The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials.
+\cite{Cardenas2017} See Figure \ref{fig:fabricationFlowChart}.
+A number of processes have been developed for specific purposes of polymeric nano-fibers, some include surface deposition, composites, and chemical adjustments.
+Polymeric nano-fibers must be also pyrolyzed to generate carbon nano-wires with conductive capabilities \cite{Madou2011} for electrochemical sensing and energy storage purposes.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.95\textwidth]{./Figures/FabricationProcess.png}
+\decoRule
+\caption[Fabrication Process]{Fabrication process of carbon nano-wires to achieve through the proposed dissertation.}
+\label{fig:fabricationFlowChart}
+\end{figure}
 
 Nanotechnology has explored different polymer patterning techniques to integrate carbon nano-wires structures.
-One technique is known as far-field electrospinning, a process in which electrified jets of polymer solution are jettisoned to synthesize nano-fibers which then are pyrolyzed at high temperatures.
+One technique is known as far-field electrospinning, a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibers which then are pyrolyzed at high temperatures.
 One sub-technique derived from electrospinning is near field electromechanical spinning or EMS.
@@
 Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist.
-\cite{Cardenas2017} This proposal research is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by nier field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires.
+\cite{Cardenas2017} This research proposal is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by near field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires.
 The polymer solutions described in \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.

### 2019-03-28 thesis_proposal_1/main.tex
rheo measurements

@@
 
-%\listoffigures % Prints the list of figures
+\listoffigures % Prints the list of figures
 
 %\listoftables % Prints the list of tables
+
+%----------------------------------------------------------------------------------------
+%	ABBREVIATIONS
+%----------------------------------------------------------------------------------------
+
+\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
+
+\textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\
+
+\textbf{CEM} & \textbf{C}ampus \textbf{E}stado de \textbf{M}éxico\\
+
+\textbf{MNT} & \textbf{M}aestría en \textbf{N}ano\textbf{t}ecnología \emph{(Master of Science in Nanotechnology)}\\
+
+\textbf{CNWs} & \textbf{C}arbon \textbf{N}ano-\textbf{w}ire\textbf{s}\\
+
+\textbf{EMS} & \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\
+
+\textbf{FFES} & \textbf{F}ar \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
+
+\textbf{NFES} & \textbf{N}ear \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
+
+\textbf{SU-8} & a photoresist\\
+
+\end{abbreviations}
 
@@
 \end{abstract}
-
-%----------------------------------------------------------------------------------------
-%	ABBREVIATIONS
-%----------------------------------------------------------------------------------------
-
-%\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
-
-%\textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\
-
-%\end{abbreviations}
 

### 2019-03-29 thesis_proposal_LaTeX/Chapters/1_Introduction.tex
share to GoogleDrive

--- 2019-03-28 thesis_proposal_1/Chapters/1_Introduction.tex
@@
 Near-field electrospinning or NFES allows large scale manufacturability combined with controlled guidance.
-\cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation so that the resulting in limited control for nano-fiber patterning.
+\cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation, resulting in limited control for nano-fiber patterning in traditional NFES processes.
 \cite{Madou2011} the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.

### 2019-03-29 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
share to GoogleDrive

--- 2019-03-19 thesis_proposal_1/Chapters/3_HypothesisAndResearchQuestions.tex
@@
 
+\subsubsection*{\color{mygray}[Chapter ready for review]}
+% The system/technique/parameter X is better, for task Y, than each of its rivals Z, in dimension W.
+
 \section{Research Hypothesis}
 
-The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers to synthesize carbon nano-wires with specified dimensions (diameter and length).
+The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length).
 

### 2019-04-02 thesis_proposal_LaTeX/Chapters/1_Introduction.tex
proposal disposition

@@
 \cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
-\cite{Siddiqui2019} Due to some of matchless properties that allow carbon nano-materials to be utilized within multiple functionalities including high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties and high conductivity.
+\cite{Siddiqui2019} Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties and high conductivity.
 \cite{Siddiqui2019}
@@
 
-Near-field electrospinning or NFES allows large scale manufacturability combined with controlled guidance.
+Traditional near-field electrospinning or NFES allows large scale manufacturability combined with controlled guidance.
 \cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation, resulting in limited control for nano-fiber patterning in traditional NFES processes.

### 2019-04-02 thesis_proposal_LaTeX/Chapters/2_ProblmemDefinitionAndMotivation.tex
share to GoogleDrive
proposal disposition

--- 2019-03-20 thesis_proposal_1/Chapters/2_ProblmemDefinitionAndMotivation.tex
@@
 However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis.
-In the past years photon polymerization processes have been applied to the fabrication of nano-structures with the use of a photoresist.
-\cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures, \cite{Hribar2014} However, it is typical of photon polymerization processes to yield small objects with waste resins that are often toxic.
-\cite{Ovsianikov2012}
+The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}.
+In the past years photon polymerization processes have been applied to the fabrication of nano-structures with the use of a epoxy based photoresist.
+\cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures \cite{Hribar2014}.
 
-On the other hand, electrospinning has been acknowledged for as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires.
+On the other hand, electrospinning has been acknowledged as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires.
 Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner.
-\cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis.
+Cárdenas \cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis.
 Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires.
-As stated in \cite{Cardenas2017}, mechano-electrispinning is an early technology invention, and brings new challenges, such as the reproducibility of carbon nano-wire production.
+As stated in \cite{Cardenas2017}, mechano-electrospinning is an early technology invention, and brings new challenges, such as the reproducibility of carbon nano-wire production.
+Furthermore, the study of a new fabrication process to produce carbon nanowires that involves mechano-electrospinning will enable spatial control of the structures' patterning.
 
-Since electrospinning seems to be a better alternative for carbon nano-wire synthesis processes; and for that purpose of its implementation, it is required to develop polymer solutions that can be mechano-electrospun, photopolymerized and pyrolyzed into conducting carbon nano-wires.
+Since electrospinning seems to be a better alternative for carbon nano-wire fabrication processes; and for that purpose of its implementation, it is required to develop polymer solutions that can be mechano-electrospun, photopolymerized and pyrolyzed into conducting carbon nano-wires.
 Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
 \cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
-\cite{Siddiqui2019} However most application are not currently feasible due to the lack of a continuous, simple and reproducible fabrication method.
+\cite{Siddiqui2019} However most applications are not currently feasible due to the lack of a continuous, simple and reproducible fabrication method with inexpensive processes.
 With the newly designed polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more applications will become feasible.
+On the other hand, the new technique will overcome some limitations of other methods such as lithography currently has.
+For instance, patterns created by lithography processes cannot be originated, only replicated, all cinstituent points of the pattern can only be addressed at the same time, and the process requires the pattern to be encoded into a mask.
+\cite{Landis2011}
 

### 2019-04-02 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
proposal disposition

@@
 
-The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length).
+The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length).
 
@@
 	\item{
-	Are there any evidence of carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
+	Is there any evidence of carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
 	}
@@
 	\item{
-	Are the fabrication parameters defined in \cite{Cardenas2017} optimal for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
+	Are the optimal fabrication parameters defined \cite{Cardenas2017} for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
 	}

### 2019-04-02 thesis_proposal_LaTeX/Chapters/4_Objectives.tex
share to GoogleDrive
proposal disposition

--- 2019-03-19 thesis_proposal_1/Chapters/4_Objectives.tex
@@
 
+\subsubsection*{\color{mygray}[Chapter ready for review]}
+% Here you are meant to stipulate, in a broadly and specific way, what you want to achieve regarding the target problem.
+You may include the scope of your proposed research or any other element that you consider might set the boundaries of your work.
+% This section can also present the Solution Model which is the one you propose to solve the problem.
+Obviously, this model has to be consistent with the objectives that have already set up.
+This model is the one that guides the research work and that, eventually, leads to the PERSONAL CONTRIBUTION.
+
 \section{General objective}
-Exercise the practice and feasibility of a new synthesis process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner.
+Study the practice and feasibility of a new synthesis process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner; by the integration of mechano-electrospinning technique.
 
-\section{Particular objective}
+\section{Particular objectives}
 
@@
     Through rheological analyses, determine if polymer solutions can be easily employed for conducting carbon nano-wire synthesis.
+    }
+    \item{
+    Determine and control the polymer solution rheological properties along with the process parameters of carbon nano-wire synthesis.
     }

### 2019-04-02 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
share to GoogleDrive
proposal disposition

--- 2019-03-19 thesis_proposal_1/Chapters/5_TheoreticalFramework.tex
@@
 
+\subsubsection*{\color{mygray}[Chapter under work]}
+% Background and state-of-the-art
 % This involves a thorough state-ofthe-art bibliographic review, the building of a formal foundation, the study of related techniques, analysis and awareness of previous works and study of fundamental aspects that can help carry on your research.
 
+\section{Photoresists}
+The electronic industry requires sustainable raw material supply for its development \cite{Sutikno2016}.
+Photoresists are a type of raw material used in microelectronics, which is composed by four main elements: a polymer (resin), a photoactive compound, a solvent, and an additive \cite{Schuster2009}.
+The additive requires to be with a low molecular weight as it is intended to act as a photosensitive material.
+Photoresists are used within the manufacturing process of printed circuit boards \cite{Staab2011}.
+Photoresists are classified into two categories.
+The resist is defined as positive if the radiation exposed material is soluble in photoresist developer; otherwise, for negative photoresist the exposed material remains to stay in the photoresist surface as it crosslinks upon exposure \cite{Landis2011,Sharma2012}.
+In the manufacturing process of a semiconductor, the radiation sources which are often used in a lithography process are ultraviolet (UV) and X-ray \cite{Mekaru2015}.
+
+The polymeric material is available on the broad market either in liguid or solid state; \emph{MicroChem Corp.} (Westborough, MA, USA) is the principal provider of SU-8 photoresist.
+SU-8 and similar photoresists are inexpensive with good adhesion on the semiconductor surface and high sensitivity \cite{Staab2011}.
+Epoxy resins are copolymer-thermosetting plastics which are normally produced by a chemical reaction process that involves epichlorohydrin and bisphenol-A compound \cite{Singla2010}.
+A epoxy-based polymer is typically used to produce patterns by lithography with the application of UV radiation.
+Lithography is a technique to transfer patterns from a mask and then transferred onto the substrate \cite{Landis2011,Xu2014}.
+SU-8 is a epoxy-based negative photoresist with the advantages of being inexpensive with good mechanical properties, good chemical resistance, and good electrical isolation \cite{Xu2014}.
+SU-8 photoresists are used in the production processes of MEMS \cite{Zhang2001}.
+Photoresist-wise, the contrast and quality level of UV radiation lithography is affected by the wavelengths of radiation sources.
+The higher the sensitivity of the material, the better is the lithography process as it absorbs radiation energy with ease to perform photochemical reactions in forming patterns \cite{Zhang2001}.
+
+In summary, a photoresist is a "epoxy-based resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}
+
 \section{Electro-Mechanical Spinning}
+A number of techniques have being develop for the fabrication of nano-fibers, such as arc discharge [22], chemical vapor deposition, laser ablation [23], and vapor growth [21].
+Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required.
+The electrospinning method can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$
+
 Diverse polymer patterning techniques have been developed to integrate and synthesize carbon nano-wires.
@@
 Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand nm; composed mostly by carbon atoms aligned parallel to the long axis of the fiber.
-\cite{Nataraj2012} Carbon nano-wires are different from carbon tubes, as CMWs are not composed by graphene sheets in cylindrical form.
+\cite{Nataraj2012} Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form.
 \cite{Nataraj2012}

### 2019-04-02 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
new structure

@@
 \section{Electro-Mechanical Spinning}
-A number of techniques have being develop for the fabrication of nano-fibers, such as arc discharge [22], chemical vapor deposition, laser ablation [23], and vapor growth [21].
+Diverse polymer patterning techniques have being develop for the fabrication of nano-fibers, such as arc discharge [22], chemical vapor deposition, laser ablation [23], and vapor growth [21].
 Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required.
-The electrospinning method can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$
+The electrospinning method can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$ [24,25] from a polymer solution under the influence of an electrostatic force.
+The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry [26-30].
+[31-33]
 
-Diverse polymer patterning techniques have been developed to integrate and synthesize carbon nano-wires.
-A typical technique is electrospinning.
-Electrospinning requires the application of an electrostatic force to a polymer solution to spin fibers.
-The applied electric field, the solution conductivity, jet length, solution viscosity surrounding gas, flow rate and the collector geometry are important parameters that influence the fiber formation during the spinning.
-\cite{Nataraj2012} Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
-The process in which the electrospun jet can be controlled near the
-tip is called NFES or near-field electrospinning.
+\cite{Nataraj2012}
+
+Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
+The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning.
 \cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning.
@@
 
-\section{Carbon nano-fibers}
+\section{Carbon nano-wire}
 Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand nm; composed mostly by carbon atoms aligned parallel to the long axis of the fiber.

### 2019-04-03 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
2nd draft Done

@@
 
-\subsubsection*{\color{mygray}[Chapter under work]}
+%\subsubsection*{\color{mygray}[Chapter under work]}
 % Background and state-of-the-art
@@
 \section{Electro-Mechanical Spinning}
-Diverse polymer patterning techniques have being develop for the fabrication of nano-fibers, such as arc discharge [22], chemical vapor deposition, laser ablation [23], and vapor growth [21].
+Diverse polymer patterning techniques have being develop for the fabrication of nano-fibers, such as arc discharge \cite{Wang2007}, chemical vapor deposition, laser ablation \cite{Ren1998}, and vapor growth \cite{Nadarajah2008}.
 Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required.
-The electrospinning method can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$ [24,25] from a polymer solution under the influence of an electrostatic force.
-The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry [26-30].
-[31-33]
+The electrospinning method (invented by Formhals Anton in 1934) can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$ \cite{Jayaraman2003,Anton1930} from a polymer solution under the influence of an electrostatic force.
+The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry \cite{Anton1938,Larrondo1981,Baumgarten1971,Shin2001}.
 
-\cite{Nataraj2012}
+Even though electrospinning is an old invention \cite{Anton1930}, it is currently a trending topic among researchers \cite{Huang2003,Reneker2008,Schiffman2008}.
+Some of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers.
+The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $n m$ in some cases, which is something difficult to achieve by other techniques.
+Furthermore, the basic set-up can be modified with ease to fabricate different fibers with diversified functionalities with different materials.
+The produced fibers can be aligned or unaligned.
+Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques.
+On the other hand, the understanding of the electrospinning process has improved in the last years \cite{Li2012}.
+As Reneker and Yarin state: "Electrospinning has rapidly changed fiber making from a capital intensive, large scale process to a low cost, broadly applicable method that manufactures fibers on a laboratory bench, to serve diverse needs ranging from materials science and technology to life sciences and clinical medicine.`` \cite{Reneker2008}
+
+The main components of the electrospinning technique are the fluid control unit (e.g.
+syringe pump) and a DC power supply.
+The process also requires a target electrode or combination of electrodes on which the fibers can be collected.
+Figure \ref{fig:FFES} describes a typical electrospinning set-up.
+\cite{Li2012}
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/FFES.png}
+\decoRule
+\caption[Far Field Electrospinning set-up]{Typical far field electrospinning (FFES) set-up \cite{Li2012}.}
+\label{fig:FFES}
+\end{figure}
 
@@
 \cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning.
-\cite{Nataraj2012}
+\cite{Nataraj2012} The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher pressition when patterning.
+Figure \ref{fig:NFES} shows a typical near field mechano-electospinning apparatus.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/NFES.png}
+\decoRule
+\caption[Near Field Electrospinning set-up]{Typical near field electrospinning (NFES) set-up \cite{Zhu2016}.}
+\label{fig:NFES}
+\end{figure}
+
+%\section{Pyrolysis}
+%
 
 \section{Carbon nano-wire}
-Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand nm; composed mostly by carbon atoms aligned parallel to the long axis of the fiber.
+Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand $n m$; composed mostly by carbon atoms aligned parallel to the long axis of the fiber.
 \cite{Nataraj2012} Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form.
-\cite{Nataraj2012}
+\cite{Nataraj2012} Carbon nano-wires are typically fabricated by electrospinning and pyrolysis/carbonization as the main processes.
+During the fabrication process, the polymer molecules are to be crosslinked to prevent melting during the subsequent pyrolysis.
+The carbonization step removes non-carbonized components in form of condensable and incondensable gases \cite{Basu2018} to then yield carbon structures of about 50\% to 75\% of the mass of the original polymeric structure \cite{Nataraj2012}.
 

### 2019-04-03 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
pyro info

@@
 
-%\section{Pyrolysis}
-%
+\section{Pyrolysis}
+Pyrolysis is technique that involves heating of biomass in the absence of air or oxygen at a maximum pyrolysis temperature.
+A small amount of oxygen can burn the structures and make them unusable \cite{Pramanick2018}.
+Once the maximum pyrolysis temperature is reached, the temperature remains constant to produce solid char, liquids, and non-condensable products.
+In most cases the liquid product is the main interest of the pyrolysis process, and the properties of the pyrolysis products depend on the maximum pyrolysis temperature and the heating rate \cite{Pramanick2018,Basu2018}.
+
+The heating of large biomass molecules results in decomposition.
+The pyrolysis decomposition process comprises char, liquids (condensable gases) and non-condensable gases; where the consensable gases may suffer further decomposition into non-condensable gases such as $C O$, $C O_{2}$, $H_{2}$, and $C H_{4}$.
+Equation \ref{eq:genPyrolysis} is a general representation of the pyrolysis decomposition reaction \cite{Basu2018}.
+
+\begin{equation}
+C_{n} H_{m} O_{p} (biomass) \overset{heat}{\rightarrow} \underset{liquid}{\Sigma} C_{x} H_{y} O_{z} + \underset{gas}{\Sigma} C_{a} H_{b} O_{c} + H_{2} O + C (char)
+\label{eq:genPyrolysis}
+\end{equation}
+
+Pyrolysis yields solid products that are more energy dense than the initial biomass, however the gas and liquid products are less energy dense \cite{Basu2018}.
+The liquid product of pyrolysis is usually of colour black containing hydrocarbons with a large amount of oxygen and 20\% water.
+When the liguid product is of interest, a rapid "quenching`` (freeze) is required after pyrolysis to prevent further decomposition or reaction with other substances \cite{Basu2018}.
+The solid yields of pyrolysis is usually around 85\% carbon with some oxygen, hydrogen and other substances that are present within the initial biomass \cite{Basu2018}.
+The biomass decomposition by pyrolysis produces non-condensable and condensable gases.
+The vapors (condensable gases) add up to the liquid yield of pyrolysis which is generated upon cooling.
+The gases (non-condensable gases) are comprised by ethylene, ethane, methane, carbon monoxide and carbon dioxide \cite{Basu2018}.
 
 \section{Carbon nano-wire}
-Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand $n m$; composed mostly by carbon atoms aligned parallel to the long axis of the fiber.
-\cite{Nataraj2012} Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form.
-\cite{Nataraj2012} Carbon nano-wires are typically fabricated by electrospinning and pyrolysis/carbonization as the main processes.
+Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand $n m$; composed mostly by carbon atoms aligned parallel to the long axis of the fiber \cite{Nataraj2012}.
+Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form \cite{Nataraj2012}.
+Carbon nano-wires are typically fabricated by electrospinning and pyrolysis/carbonization as the main processes.
 During the fabrication process, the polymer molecules are to be crosslinked to prevent melting during the subsequent pyrolysis.

### 2019-04-05 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
related work chapter

--- 2019-04-02 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
@@
 
-\chapter{Theoretical Framework} % Main chapter title
+\chapter{Related Work} % Main chapter title
 
-\label{Chapter:TheoreticalFramework}
+\label{Chapter:RelatedWork}
 
-\subsubsection*{\color{mygray}[Chapter under work]}
-% Background and state-of-the-art
-% This involves a thorough state-ofthe-art bibliographic review, the building of a formal foundation, the study of related techniques, analysis and awareness of previous works and study of fundamental aspects that can help carry on your research.
-
-\section{Photoresists}
-The electronic industry requires sustainable raw material supply for its development \cite{Sutikno2016}.
-Photoresists are a type of raw material used in microelectronics, which is composed by four main elements: a polymer (resin), a photoactive compound, a solvent, and an additive \cite{Schuster2009}.
-The additive requires to be with a low molecular weight as it is intended to act as a photosensitive material.
-Photoresists are used within the manufacturing process of printed circuit boards \cite{Staab2011}.
-Photoresists are classified into two categories.
-The resist is defined as positive if the radiation exposed material is soluble in photoresist developer; otherwise, for negative photoresist the exposed material remains to stay in the photoresist surface as it crosslinks upon exposure \cite{Landis2011,Sharma2012}.
-In the manufacturing process of a semiconductor, the radiation sources which are often used in a lithography process are ultraviolet (UV) and X-ray \cite{Mekaru2015}.
-
-The polymeric material is available on the broad market either in liguid or solid state; \emph{MicroChem Corp.} (Westborough, MA, USA) is the principal provider of SU-8 photoresist.
-SU-8 and similar photoresists are inexpensive with good adhesion on the semiconductor surface and high sensitivity \cite{Staab2011}.
-Epoxy resins are copolymer-thermosetting plastics which are normally produced by a chemical reaction process that involves epichlorohydrin and bisphenol-A compound \cite{Singla2010}.
-A epoxy-based polymer is typically used to produce patterns by lithography with the application of UV radiation.
-Lithography is a technique to transfer patterns from a mask and then transferred onto the substrate \cite{Landis2011,Xu2014}.
-SU-8 is a epoxy-based negative photoresist with the advantages of being inexpensive with good mechanical properties, good chemical resistance, and good electrical isolation \cite{Xu2014}.
-SU-8 photoresists are used in the production processes of MEMS \cite{Zhang2001}.
-Photoresist-wise, the contrast and quality level of UV radiation lithography is affected by the wavelengths of radiation sources.
-The higher the sensitivity of the material, the better is the lithography process as it absorbs radiation energy with ease to perform photochemical reactions in forming patterns \cite{Zhang2001}.
-
-In summary, a photoresist is a "epoxy-based resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}
-
-\section{Electro-Mechanical Spinning}
-Diverse polymer patterning techniques have being develop for the fabrication of nano-fibers, such as arc discharge [22], chemical vapor deposition, laser ablation [23], and vapor growth [21].
-Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required.
-The electrospinning method can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$ [24,25] from a polymer solution under the influence of an electrostatic force.
-The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry [26-30].
-[31-33]
-
-\cite{Nataraj2012}
-
-Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
-The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning.
-\cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning.
-\cite{Nataraj2012}
-
-\section{Carbon nano-wire}
-Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand nm; composed mostly by carbon atoms aligned parallel to the long axis of the fiber.
-\cite{Nataraj2012} Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form.
-\cite{Nataraj2012}
+%\subsubsection*{\color{mygray}[Chapter under work]}
 
@@
 
+\section{Role of rheological properties in near field electrospun fibers morphology \cite{Flores2017}}
+
+\section{Advanced Manufacturing Techniques for the Fabrication and Surface Modification of Carbon Nanowires \cite{Cardenas2017}}
+
 %-----------------------------------

### 2019-04-05 thesis_proposal_LaTeX/Chapters/7_Methodology.tex
related work chapter

% Chapter Template

\chapter{Methodology} % Main chapter title

\label{Chapter:Methodology}

%\subsubsection*{\color{mygray}[Chapter under work]}
% process or set of steps that are to take place in order to fulfill the objectives. These steps must mention the experiments to conduct, how they are going to be carried out, the evaluation of the obtained results, the validation of the hypothesis, the answers to the research questions, and the last step must be the written report of the outcomes

The following describes the proposed work to be done to fulfill the objectives stated in this document. The tasks are grouped in several work packages as described bellow:

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Work package 1 : Preliminary Literature Review}
The first step to the thesis development is the study of preliminary literature and related work. The purpose of this work package is the familiarization of the existing techniques such as: far and near field electrospinning, lithography, pyrolysis, carbonization and photopolymerization. On the other hand, some research is to be done in order to recognize if there are any efforts in the design of electrospun-able, photopolymerizable and pyrolysable polymer solutions.

Furthermore, the motive of this work package is to find common parameters that could link the techniques mentioned above for the fabrication of carbon nano-wires from polymer solutions that can be electrospun by NFES, photopolymerized and then pyrolyzed. This work package is to be carried out through the entire thesis development process, as the state-of-the-art may change within that period of time.

\section{Work package 2 : Evaluation of Fabrication Parameters}
As the polymer solution is the principal input to the proposed technique (See Figure \ref{fig:fabricationFlowChart}), it is required to identify and understand the fabrication parameters that have an impact to the quality of the carbon nano-wires. For that reason two tasks are to be executed:

\begin{itemize}
	\item Study and identify the process parameters that influence the fabrication of carbon nano-wires
	\item Study and identify the rheological properties in polymer solutions that affect the electrospinning and pyrolysis techniques
\end{itemize}

\section{Work package 3 : Polymer Solution Design}
Once the process parameters and rheological properties that affect the fabrication of carbon nano-wires are identified, the design process shall take place. This work package is to study polymer solutions that can be electrospun by NFES, photopolymerized and pyrolyzed. The polymer solution design will comprise of two steps:

\begin{itemize}
	\item Prepare and test various polymer solutions with specific distinctions according to the identified solution properties and process parameters.
	\item Perform rheological analyses to determine if the prepared polymer solutions can be employed for the fabrication of carbon nano-wires.
\end{itemize}

\section{Work package 4 : Fabrication of Carbon Nano-wires}
From the rheological analyses, determine and control the polymer solution properties and fabricate carbon nano-wires.

This work package intends to involve several manufacturing processes (near field electrospinning, photopolymerization, pyrolization and carbonization) for the fabrication of carbon nano-wires. This task will require the integration of several techniques:

\begin{itemize}
	\item \emph{Electrospinning} - to convert the polymer solution into polymer nano-fibers
	\item \emph{Photopolymerization} - to change the chemical properties of the polymer solution and crosslink its molecules. This is to prevent the polymer to melt during pyrolysis \cite{Basu2018}.
	\item \emph{Pyrolysis} - to transform the polymer nano-fibers into conductive carbon nano-wires.
\end{itemize}

See Figure \ref{fig:fabricationFlowChart}.

\section{Work package 5 : Data Collection and Analysis of Results}
The data collection work package comprehends the study of the created carbon nano-wires using the newly design polymer solution. The purpose is characterize the carbon nano-wires and compare them to the carbon nano-structures produced by existing techniques.

\section{Work package 6 : Documentation}
Finally the documentation refers to the Thesis writing tasks. This task is intended to carried out through the entire thesis development process, as every work package above is to be referenced within the thesis document.

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------

### 2019-04-05 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
more related work

@@
 \cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning.
-\cite{Nataraj2012} The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher pressition when patterning.
+\cite{Nataraj2012} The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher precision when patterning.
 Figure \ref{fig:NFES} shows a typical near field mechano-electospinning apparatus.

### 2019-04-05 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
more related work

@@
 
+Flores studied SU-8 2002 polymer solutions in cyclopentanone with poly(ethylene) oxide (PEO) and tetrabutylammonium tetrafluoroborate (TBATFB).
+For that purpose, several samples were prepared with the adequate amounts of PEO and TBATFB with 5 $m l$ of SU-8 2002 and stirred at 160 $r p m$ for one hour at 75 $^\circ C$ in the absence of light.
+A 5 $m l$ syringe was used to extract the solution from the preparation vial.
+Finally the syringe was placed upside down for 24 hours to get rid of any bubbles within the solution.
+Table \ref{tbl:FloresSamples} lists the set of samples that were prepared as values in $w t \%$, dissolved in SU-8 2002.
+
+\begin{table}[th]
+\caption{Set of prepared samples}
+\begin{center}
+\begin{tabular}{ c c c c c c c } 
+\hline
+\text{} & \multicolumn{2}{c}{Serie A} & \multicolumn{2}{c}{Serie B} & \multicolumn{2}{c}{Serie C} \\
+\hline
+Sample & PEO & TBATFB & PEO & TBATFB & PEO & TBATFB \\
+\hline
+1 & 0.00 & 0.00 & 0.00 & 0.50 & 0.50 & 0.00 \\
+2 & 0.25 & 0.25 & 0.25 & 0.50 & 0.50 & 0.25 \\
+3 & 0.50 & 0.50 & 0.50 & 0.50 & 0.50 & 0.50 \\
+4 & 0.75 & 0.75 & 0.75 & 0.50 & 0.50 & 0.75 \\
+5 & 1.00 & 1.00 & 1.00 & 0.50 & 0.50 & 1.00 \\
+\hline
+\label{tbl:FloresSamples}
+\end{tabular}
+\end{center}
+\end{table}
+
+All the samples were executed in a rheometer (Physica MCR 301, Anton Paar) with a cone-and-plane geometry of diameter 24.979 $m m$, angle 4.014$^\circ$ and truncation of 249 $\mu m$.
+The measurements were performed at a temperature of 25 $\pm$ 0.1 $^\circ C$.
+For amplitude sweep measurements, the angular frequency was settled at 10 $s^{-1}$, and the percentage amplitude gamma $\% \gamma$, was varied from 0.1 to 1000\%.
+In flow curve tests, shear rate was applied from 0.1 to 100 $s^{-1}$.
+For frequency sweeps, the percentage of amplitude gamma, $\% \gamma$, was varied from 0.1 to 100 $s^{-1}$.
+During the measurements, the rheometer sample area was saturated with cyclopentanone to avoid solvent evaporation.
+
+\subsection{Rheological Characterization : \textbf{Amplitude Sweep}}
+The "Serie A`` result measurements indicate that the storage modulus $G'$ is smaller than the loss modulus $G''$.
+Both moduli have a parabolic behaviour.
+At low deformation the values of the moduli increase until they become stable at between 1 and 10 $\% \gamma$.
+After the stabilization, both modulus start to decrease.
+The increase of PEO and TBATFB concentration $G'$ and $G''$ also increase.
+Figure \ref{fig:SerieAampSweep} shows the amplitude sweep for the samples of "Serie A``.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/SerieAampSweep.png}
+\decoRule
+\caption[Serie A - Amplitude Sweep]{Serie A - Amplitude Sweep}
+\label{fig:SerieAampSweep}
+\end{figure}
+
+The results within Figure \ref{fig:SerieAampSweep} showed that no clear linear viscoelastic region is present.
+The material has influenced by small deformations, hence it is very sensible to external forces.
+No yield point was encountered as the moduli separate from each other with the increase of deformation.
+
+Figure \ref{fig:SerieBampSweep} illustrates the results obtained from the amplitude sweeps of Serie B samples.
+As shown in the figure, the concentration of 0 $w t \%$ shows a constant viscous modulus at 0.2 $Pa$.
+the 0.25 $w t \%$ concentration sample presented a similar behaviour to the 0 $w t \%$ sample but with a constant value of $G'$ at 2 $Pa$.
+The other concentrations show a similar parabolic behaviour as the ones in Serie A.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/SerieBampSweep.png}
+\decoRule
+\caption[Serie B - Amplitude Sweep]{Serie B - Amplitude Sweep}
+\label{fig:SerieBampSweep}
+\end{figure}
+
+\subsection{Rheological Characterization : \textbf{Flow Curve}}
+
+\subsection{Rheological Characterization : \textbf{Frequency Sweep}}
+
+\clearpage
+
 \section{Advanced Manufacturing Techniques for the Fabrication and Surface Modification of Carbon Nanowires \cite{Cardenas2017}}

### 2019-04-05 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
progress

@@
 
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/SerieCampSweep.png}
+\decoRule
+\caption[Serie C - Amplitude Sweep]{Serie C - Amplitude Sweep}
+\label{fig:SerieCampSweep}
+\end{figure}
+
+The amplitude sweep results of Serie C are depicted in Figure \ref{fig:SerieCampSweep}.
+Similar to series A and B, results show that the storage modulus $G'$ is smaller than the loss modulus $G''$ with a parabolic behaviour.
+Typically, the amplitude sweep is to determine the amplitude to be used in frequency sweeps.
+The amplitude determined by the amplitude sweeps shall keep the material structure undisturbed is known as the linear viscoelastic region (LVER).
+However, no LVER was found in the samples.
+For that reason, the percentage of amplitude gamma $\% \gamma$ was found by trial and error.
+Flores discovered that a $\% \gamma = 20$ has the best performance.
+
 \subsection{Rheological Characterization : \textbf{Flow Curve}}

### 2019-04-07 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
new state of the art

@@
 
+Figure \ref{fig:SerieAflowCurve} shows evidence that the equal increase of PEO and TBATFB concentrations result in an increase of shear viscosity rate $\gamma$.
+for concentrations from 1.00 to 0.25 $w t \%$, a slight increase of flow curve strain $\eta$ for low shear rates to 0.3 $s^{-1}$.
+For shear rates greater than 0.3 $s^{-1}$, the $\eta$ starts to decrease, as the polymer entanglements start to break apart, reducing friction between the polymer threads and therefore the viscosity also is reduced.
+The solution samples show a Newtonian-like behaviour and that may be caused by the use of the solvent cyclopentanone and by the small sized SU-8 2002 molecules.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/SerieAflowCurve.png}
+\decoRule
+\caption[Serie A - Flow curve]{Serie A - Flow curve}
+\label{fig:SerieAflowCurve}
+\end{figure}
+
+From the results in Figure \ref{fig:SerieAflowCurve}, it is noticeable that the addition of small amounts of PEO and TBATFB cause a change of one order of magnitude in shear viscosity in small concentration and a triple change in high concentrations.
+
+Series B flow curve results (Figure \ref{fig:SerieBflowCurve}) do not show a clear correlation between PEO concentrations and shear viscosity.
+For PEO of 1 $w t \%$, a slow increase in $\eta$ is present with the increase of shear rate, after $\gamma$ drops from 2 to 0.8 $Pa s$, a shear thinning behaviour is present.
+For 0.50 and 0.75 $w t \%$ concentrations, a shear thinning behaviour is present throughout the plot.
+For the 0.50 $w t \%$ sample, viscosity value varied between 0.2 and 0.4 $Pa s$; and between 0.5 and 2.0 $Pa s$ for the 0.75 $w t \%$ sample.
+Viscosity is stabilized at 0.1 $Pa s$ when the shear rate is between 1 and 20 \% for the sample of PEO $w t \%$.
+After stabilization, the viscosity decreases from 0.1 to 0.02 $Pa s$ for shear rates between 20 to 100 $s^{-1}$.
+For PEO 0.00 $w t \%$, a high variation is present in viscosity readings due to the presence of electrolytes cause amendments in the polymer chain within the solution.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/SerieBflowCurve.png}
+\decoRule
+\caption[Serie B - Flow curve]{Serie B - Flow curve}
+\label{fig:SerieBflowCurve}
+\end{figure}
+
 \subsection{Rheological Characterization : \textbf{Frequency Sweep}}

### 2019-04-11 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
min feature

@@
 
+The flow curve results of Serie C are presented in Figure \ref{fig:SerieCflowCurve}.
+The sample with 1 $w t \%$ TBATFB concentration shows a shear thinning behaviour for shear rates varying between 0.1 to 15 $s^{-1}$.
+The 1 $w t \%$ sample describes a drop in viscosity for shear rates between 15 to 20 $s^{-1}$ followed by a stable state.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/SerieCflowCurve.png}
+\decoRule
+\caption[Serie C - Flow curve]{Serie C - Flow curve}
+\label{fig:SerieCflowCurve}
+\end{figure}
+
 \subsection{Rheological Characterization : \textbf{Frequency Sweep}}

### 2019-04-29 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
2nd draft Done
proposal update

@@
 
-\subsubsection*{\color{mygray}[Chapter ready for review]}
+%\subsubsection*{\color{mygray}[Chapter ready for review]}
 % The system/technique/parameter X is better, for task Y, than each of its rivals Z, in dimension W.
@@
 The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length).
+The rheological properties of polymer solutions along with synthesis parameters are to be amended by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardemas \cite{Cardenas2017} work.
+PEO is to be replaced as its only purpose is to allow the electrospinning process to take place, but not benefit is obtained from it after pyrolysis.
 
@@
 	}
+	\item{
+	What PEO-similar materials can be used to allow the electrospinning technique and favor the carbon nano-wire properties after pyrolysis? 
+	}
 \end{itemize}

### 2019-04-29 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
proposal update

@@
 
+\section{Polymer Solutions}
+Polymer solutions display viscoelastic properties that provide unique properties due to their macromolecules.
+their chains are long and entangled.
+When a shear force is applied, the solution creates a large interaction between the molecules, hence the viscosity depends not only on temperature and shear, but also molecular weight distribution and concentration.
+The solvent also affects the viscosity \cite{Flores2017, Huang2003, Baumgarten1971}.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.50\textwidth]{./Figures/goodbadsolvent.png}
+\decoRule
+\caption[Effects in polymer chains dimensions due to solvent quality]{Effects in polymer chains dimensions due to solvent quality \cite{Flores2017}}
+\label{fig:goodbadsolvent}
+\end{figure}
+
+Figure \ref{fig:goodbadsolvent} shows how the quality of a solvent affects the polymer distribution within the solution.
+Moreover the prsence of electrolites also modify the structure of the polymer threads.
+In non-ionic solvents, the charges are distributed along the chains and their own repulsion stretches the polimer threads into a more aligned configuration when an electrolyte is added, as detailed in Figure \ref{fig:electrolyteConcentration}.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.50\textwidth]{./Figures/electrolyteConcentration.png}
+\decoRule
+\caption[Effects of electrolyte in polymer chain dimensions]{Effects of electrolyte in polymer chain dimensions \cite{Flores2017}}
+\label{fig:electrolyteConcentration}
+\end{figure}
+
+\section{Rheometry}
+Rheometry is the measuring technology used to determine rheological data.
+There are different measuring systems, instruments and analysis methods.
+Both, liquids and solid  can be investigated using rotational and oscillatory rheometers.
+Rotational tests are performed to characterize viscous behavior.
+In order to evaluate viscoelastic behavior, creep tests, relaxation tests and oscillatory tests are performed \cite{Flores2017}.
+
+\subsection{Amplitude Sweep}
+An amplitude sweep is a typical test used to characterize the behavior of a polymer
+solution or polymer melt.
+In this basic test a constant angular frequency is applied along with an increasing or decreasing deformation or strain, see Figure \ref{fig:ampSweep} a).
+The obtained results are the storage and loss moduli, $G'$ and $G''$ respectively, along the values of percentage of strain applied.
+The amplitude is the maximum of the oscillatory motion.
+Normally at low frequencies the viscoelastic material presents a linear behavior, this is when the viscoelastic properties are independent of the strain or stress imposed due to the structure of the material stays undisturbed.
+Nevertheless, as the amplitude is increased at some at some point this linear trend changes suddenly.
+Once this critical amplitude value is reached the material becomes more elastic or viscous depending on the solution initial state, see Figure \ref{fig:ampSweep} b) \cite{Flores2017}.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/ampSweep.png}
+\decoRule
+\caption[Amplitude Sweep]{a) Imposed amplitude along time with constant frequency. b) Results for an amplitude sweep \cite{Flores2017}}
+\label{fig:ampSweep}
+\end{figure}
+
+\subsection{Frequency Sweep}
+A frequency sweep, is a common oscillatory test useful to understand the rheological behavior of fluids as it measures the viscoelastic properties.
+This measurement is considered a viscoelastic spectrum, in general, the shorter the timescale the more elastic the material behaves.
+These results are related to the molecular structure of the sample.
+Figure \ref{fig:freqSweep} shows a typical data for a polymer melt where different regions are observed.
+Frequency sweep measurements also allow the estimation of the molecular weight distribution characteristics such as entanglement density and process-ability \cite{Flores2017}.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/freqSweep.png}
+\decoRule
+\caption[Frequency Sweep]{Typical results for a frequency sweep. \cite{Flores2017}}
+\label{fig:freqSweep}
+\end{figure}
+
+\subsection{Flow Curve}
+The viscosity is measured as a function of the shear rate in a rotational rheometer with different geometries according to the sample.
+Normally three types of behaviours can be characterized in flow curve measurements: a) ideal viscous, b) shear thinning and c) shear thickening.
+Figure \ref{fig:flowCurve} shows three different materials and their response to an imposed shear rate \cite{Flores2017}.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/flowCurve.png}
+\decoRule
+\caption[Flow Curves]{a) Flow curve stress vs stress.
+b) Flow curve strain vs shear viscosity.
+Both figures for i Newtonian fluid, ii Shear thinning fluid, iii Shear thickening fluid.
+\cite{Flores2017}}
+\label{fig:flowCurve}
+\end{figure}
+
 %----------------------------------------------------------------------------------------

### 2019-04-29 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
more state of the art
proposal update

@@
 \subsection{Rheological Characterization : \textbf{Flow Curve}}
-
 Figure \ref{fig:SerieAflowCurve} shows evidence that the equal increase of PEO and TBATFB concentrations result in an increase of shear viscosity rate $\gamma$.
@@
 The 1 $w t \%$ sample describes a drop in viscosity for shear rates between 15 to 20 $s^{-1}$ followed by a stable state.
+A similar behaviour is observed for concentration of 0.75 $w t \%$.
+and less evident for 0.0 $w t \%$.
+For concentrations of 0.5 $w t \%$ and 0.25 $w t \%$ the behaviour of the shear viscosity is similar.
 
@@
 \subsection{Rheological Characterization : \textbf{Frequency Sweep}}
+Figure \ref{fig:SerieAfreqSweep} shows that the solution with the lowest concentration of PEO and TBATFB has a decreasing behaviour of the viscosity, but for values greater to 3 $s^{-1}$ in frequency, the viscosity starts to increase.
+The solutions from 0.25 $w t \%$ to 1.00 $w t \%$ have the same shear-thinning behaviour.
+A direct relation between the concentrations and the viscosity values is discovered, where a small drop of viscosity is presented with the decrease of additive concentration.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/SerieAfreqSweep.png}
+\decoRule
+\caption[Serie A - Frequency Sweep]{Serie A - Frequency Sweep}
+\label{fig:SerieAfreqSweep}
+\end{figure}
+
+Figure \ref{fig:SerieBfreqSweep} shows the frequency sweep results from Serie B.
+The presented behaviour is similar to Serie A.
+for the lower concentrations of PEO, the equipment has not enough sensibility to make measurements of the storage modulus because this one is very low.
+At PEO 0.25 $w t \%$, the viscosity remains almost constant at 1 $Pa s$, but as in Serie A a little variation of viscosity is presented at the lowest values of angular frequency.
+On the other hand, for the 0.5, 0.75 and 1.00 $w t \%$ concentrations, the viscosity is similar.
+At 100 $s^{-1}$, the three high concentration samples converge to 2 $Pa s$.
+It is imperative to assume that 0.5 $w t \%$ is the critical concentration, under this concentration the systems presents different behaviours since the molecules have enough room to diffuse and break entanglements.
+When the critical entanglement concentration is exceeded, the polymer threads overlap and become tangled, therefore no more entanglements are no longer possible.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/SerieBfreqSweep.png}
+\decoRule
+\caption[Serie B - Frequency Sweep]{Serie B - Frequency Sweep}
+\label{fig:SerieBfreqSweep}
+\end{figure}
+
+The frequency sweep behaviours of Serie C are presented in Figure \ref{fig:SerieCfreqSweep}.
+The figure does not indicate a clear correlation between the viscosity and the addition of TBATFB.
+All samples have a similar behaviour and magnitude, except for the 0.75 $w t \%$ TBATFB concentration sample as it presents a non uniform behaviour.
+At low frequencies, the viscosity increases, then it remains constant at 20 $Pa s$ until a frequency value of 4 $s^{-1}$; the viscosity drastically decreases to 1 $Pa s$ and remains constant at that value.
+The 1.00 $w t \%$ sample has a decreasing viscosity behaviour at higher angular frequencies.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/SerieCfreqSweep.png}
+\decoRule
+\caption[Serie C - Frequency Sweep]{Serie C - Frequency Sweep}
+\label{fig:SerieCfreqSweep}
+\end{figure}
+
+Flores work \cite{Flores2017} carried out a series of experiments in order to correlate the rheological properties of polymer solutions used in electro-mechanical spinning processes for the fabrication of carbon micro structures.
+Shear flow and dynamic measurements tests such as flow curves, amplitude sweeps and frequency sweeps were carried in an oscillatory rheometer to study the rheological behaviour of polymeric solutions of SU-8 2002, an epoxy-based negative photoresist, Poly(ethylene) oxide (PEO), a flexible, non-ionic polymer, and TBATFB (Tetrabutylammonium tetrafluoroborate) that acts as an electrolyte.
+
+The concentrations of additives were varied from 0 $w t \%$ to 1.0 $w t \%$ with increments of 0.25.
+To observe the effects of each additive it was proposed a set of concentrations where both additives were equally varied (Serie A), TBATFB was constant the only PEO variations (Serie B), and PEO constant concentration with TBATFB variations (Serie C).
+It was found that the variation of the additives (PEO and TBATFB) affects the
+rheological behavior of the solution. Typically, the addition of PEO increase the
+elongational and shear viscosities while the addition of TBATFB modifies this property
+but in a non-predictable manner. The solutions do not present yield stress as can be
+seen in Amplitude Sweep and Frequency Sweep measurements.
 
@@
 
+As stated by Cardenas \cite{Cardenas2017}, the following parameters play an important role in the graphitic content on the fabrication of carbon nano-wires through electrospinning:
+
+\begin{enumerate}
+\item The thickness of the produced polymeric wires,
+\item the chemical composition and viscoelasticity of the polymeric solution,
+\item the molecular alignment of the polymer,
+\item the heat treatment temperature,
+\item the mechanical pulling on the polymer jet during electrospinning,
+\item the alifnment of polymer chains induced by the presence of an electric field, and
+\item the catalysts and solvents within the polymer solution.
+\end{enumerate}
+
+Cardenas reviewed different polymer fabrication techniques and materials to produce carbon nano-wires.
+Within Cardenas' work the following parameters were evaluated to study the desirable characteristics for building highly sensitive sensor devices: a) the chemical composition and viscoelasticity of the polymer solution, b) the thickness of the produced polymeric wires, c) the mechanical pulling on the polymeric jet during electrospinning, and d) the alignment of the polymer chains induced by the presence of an electric field.
+Cardenas' work states that various methods are implemented to produce nanofibers, such as laser ablation, chemical vapor deposition, discharge, and vapour growth.
+However, those techniques are abandoned due to their low yield output and expensive equipment.
+Whereas electrospinning (ES) of polymer solutions is a promising technique for simple and inexpensive fabrication of carbon nano-wires, which can be combined with a moving collector to yield even thinner fibers.
+
+The production of carbon sstructures involves to main procedures: a) polymer patterning such as photolithography, electrospinning, Computer Numerical Control (CNC), moulding, hot embossing, and recently, Multiple Photon Polymerization; and b) carbonization, which induces further thinning of the patterned polymer and its conversion into carbon.
+Cardenas conducted some experiments to characterize and analyse carbon nano-wires.
+Polymeric SU-8 nano fibers were produced by two different methods; for each method different polymer solutions were employed.
+
+\subsection{Method 1 : }
+
+\subsubsection{Polymer Solution}
+The polymeric solution was composed by 2 $ml$ of SU-8 2002 mixed with 0.5 $w t \%$ of PEO and 0.5 $w t \%$ of TBATFB to increase its conductivity and yield soother polymer jets during electrospinning.
+Magnetic stirring was performed for 1 $hr$ at 75 \textdegree{}$C$ with $rpm$ values between 100 and 150.
+
+\subsubsection{Deposition}
+A voltage around 100 $V$ was applied between a dispensing needle and the collector stage.
+The needle to collector distance was set to 100 $\mu m$.
+The collector was attached to a mechanically motorized stage, which allowed the SU-8 nanofibers patterning into the SU-8 microstructures.
+Three different stage velocities were tested (20,40 and 60 $mm/s$) to study the influence on the wire geometry.
+Acceleration of the stage was set to 500 $mm/s^{2}$.
+After deposition, samples were exposed to UV light for 45 $min$ to complete cross-linking.
+
+\subsection{Method 2 : }
+
+\subsubsection{Polymer Solution}
+The solution was composed of 4 $ml$ of SU-8 2025, 4 $mg$ of TBATFB and 80 $\mu L$ of SU-8 thinner. The solution was stirred for 1.5 $hrs$ at 100 $rpm$ at 75 \textdegree{}$C$.
+
+\subsubsection{Deposition}
+To pattern the fiber exactly on top of the SU-8 electrodes, a routine was set to move the needle relative to the collector.
+The polymer solution was dispensed at a rate of 8.847 $nL / min$ using a programmable syringe pump.
+A voltage of 200 $V$ was applied between the collector plate and the needle tip, and the polymer solution was allowed to flow for between 15 to 30 $min$ until it was stable.
+A higher voltage had to be applied compared to Method 1 due to the higher viscosity of the SU-8 2025 solution.
+Once a steady flow was achieved, the collector was moved relative to the needle tip using the motorized stage.
+The mechanical parameters used during were: a) velocity of 5000 $\mu m/s$, an acceleration of 2500 $\mu m/s^{2}$.
+The sample was exposed to UV light for 45 min to ensure complete cross-linking of the deposited SU-8 nanofiber.
+
+\subsection{Results and Discussion}
+To test the possibility of using SU-8 to fabricate carbon nano-wires, samples were pyrolyzed in an inert environment.
+Samples prepared by Method 1 failed the pyrolyzation as the deposited wires were mostly liquid before carbonization.
+The fibers produced by Method 2 had a yeild rate of 81 $\%$.
+The diameters after pyrolysis were analyzed and measured using SEM micrographs.
+
+Cardenas \cite{Cardenas2017} states that the geometry of the carbon nano-wires is also an important characteristic that affects the carbon structure conductivity, mechanical and thermal characteristics and crystallinity.
+The conducted experiments showed some techniques and materials that have been applied to fabricate carbon nano-wires, as well as the effects that fabrication parameters have on the final geometry of the carbon structures.
+The newly technique of electro-mechano-spinning (EMS) involved new polymer solutions along with a systematic deposition process.
+Cardenas found that the EMS proposed manufacturing technique yielded normally distributed diameters of 204 $nm$ with low variability, which is significantly reduced the uncertainty in the fabrication of carbon nano-wires.
+
 %-----------------------------------

### 2019-05-11 thesis_proposal_LaTeX/Chapters/1_Introduction.tex
2nd draft Done
Grammar corrections + new document structure

@@
 
-\subsubsection*{\color{mygray}[Chapter ready for review]}
+%\subsubsection*{\color{mygray}[Chapter ready for review]}
 % Introduction to the Context where the proposal is going to be carried out.
@@
 Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
-\cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
-\cite{Siddiqui2019} Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties and high conductivity.
+\cite{Siddiqui2019} Carbon nano-materials are suitable for catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing, and cancer detection.
+\cite{Siddiqui2019} Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity.
 \cite{Siddiqui2019}
 
-This document bestow a thesis proposal to perform a research to engineer and design a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner.
-The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials.
+This document bestows a thesis proposal to perform a research to engineer and design a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner.
+The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization, and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials.
 \cite{Cardenas2017} See Figure \ref{fig:fabricationFlowChart}.
@@
 
-The proposal is to continue the previous work done in regards of the synthesis of carbon nano-wires.
+The proposal is to continue the previous work done in regards to the synthesis of carbon nano-wires.
 Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist.

### 2019-05-11 thesis_proposal_LaTeX/Chapters/2_ProblmemDefinitionAndMotivation.tex
2nd draft Done
Grammar corrections + new document structure

@@
 
-\subsubsection*{\color{mygray}[Chapter ready for review]}
+%\subsubsection*{\color{mygray}[Chapter ready for review]}
 % Describe the current situation of this problem.
@@
 The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}.
-In the past years photon polymerization processes have been applied to the fabrication of nano-structures with the use of a epoxy based photoresist.
+In the past years, photon polymerization processes have been applied to the fabrication of nano-structures with the use of an epoxy based photoresist.
 \cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures \cite{Hribar2014}.
@@
 Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner.
-Cárdenas \cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis.
+Cardenas \cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis.
 Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires.
-As stated in \cite{Cardenas2017}, mechano-electrospinning is an early technology invention, and brings new challenges, such as the reproducibility of carbon nano-wire production.
+As stated in \cite{Cardenas2017}, mechano-electrospinning is an early technology invention and brings new challenges, such as the reproducibility of carbon nano-wire production.
 Furthermore, the study of a new fabrication process to produce carbon nanowires that involves mechano-electrospinning will enable spatial control of the structures' patterning.
@@
 On the other hand, the new technique will overcome some limitations of other methods such as lithography currently has.
-For instance, patterns created by lithography processes cannot be originated, only replicated, all cinstituent points of the pattern can only be addressed at the same time, and the process requires the pattern to be encoded into a mask.
+For instance, patterns created by lithography processes cannot be originated, only replicated, all constituent points of the pattern can only be addressed at the same time, and the process requires the pattern to be encoded into a mask.
 \cite{Landis2011}

### 2019-05-11 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
Grammar corrections + new document structure

--- 2019-04-02 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
@@
 The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length).
+The rheological properties of polymer solutions along with synthesis parameters are to be amended by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardenas \cite{Cardenas2017} work.
+PEO is to be replaced as its only purpose is to allow the electrospinning process to take place, but no benefit is obtained from it after pyrolysis.
 
@@
 	\item{
-	What rheological properties are to be controlled/tested to deliver a electrospun-able and pyrozable polymer solution?	
+	What rheological properties are to be controlled/tested to deliver an electrospun-able and pyrozable polymer solution?	
 	}
@@
 	Are the optimal fabrication parameters defined \cite{Cardenas2017} for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
+	}
+	\item{
+	What PEO-similar materials can be used to allow the electrospinning technique and favor the carbon nano-wire properties after pyrolysis? 
 	}

### 2019-05-11 thesis_proposal_LaTeX/Chapters/5_StateoftheArt.tex
proposal update
Grammar corrections + new document structure

--- 2019-04-29 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
@@
 The results within Figure \ref{fig:SerieAampSweep} showed that no clear linear viscoelastic region is present.
-The material has influenced by small deformations, hence it is very sensible to external forces.
+The material has influenced by small deformations, hence it is very sensitive to external forces.
 No yield point was encountered as the moduli separate from each other with the increase of deformation.
@@
 Figure \ref{fig:SerieAflowCurve} shows evidence that the equal increase of PEO and TBATFB concentrations result in an increase of shear viscosity rate $\gamma$.
-for concentrations from 1.00 to 0.25 $w t \%$, a slight increase of flow curve strain $\eta$ for low shear rates to 0.3 $s^{-1}$.
+For concentrations from 1.00 to 0.25 $w t \%$, a slight increase of flow curve strain $\eta$ for low shear rates to 0.3 $s^{-1}$.
 For shear rates greater than 0.3 $s^{-1}$, the $\eta$ starts to decrease, as the polymer entanglements start to break apart, reducing friction between the polymer threads and therefore the viscosity also is reduced.
@@
 
-From the results in Figure \ref{fig:SerieAflowCurve}, it is noticeable that the addition of small amounts of PEO and TBATFB cause a change of one order of magnitude in shear viscosity in small concentration and a triple change in high concentrations.
+From the results in Figure \ref{fig:SerieAflowCurve}, it is noticeable that the addition of small amounts of PEO and TBATFB cause a change of one order of magnitude in shear viscosity in small concentrations and a triple change in high concentrations.
 
@@
 The 1 $w t \%$ sample describes a drop in viscosity for shear rates between 15 to 20 $s^{-1}$ followed by a stable state.
-A similar behaviour is observed for concentration of 0.75 $w t \%$.
+A similar behaviour is observed for a concentration of 0.75 $w t \%$.
 and less evident for 0.0 $w t \%$.
@@
 At 100 $s^{-1}$, the three high concentration samples converge to 2 $Pa s$.
-It is imperative to assume that 0.5 $w t \%$ is the critical concentration, under this concentration the systems presents different behaviours since the molecules have enough room to diffuse and break entanglements.
+It is imperative to assume that 0.5 $w t \%$ is the critical concentration, under this concentration the systems present different behaviours since the molecules have enough room to diffuse and break entanglements.
 When the critical entanglement concentration is exceeded, the polymer threads overlap and become tangled, therefore no more entanglements are no longer possible.
@@
 \item the mechanical pulling on the polymer jet during electrospinning,
-\item the alifnment of polymer chains induced by the presence of an electric field, and
+\item the alignment of polymer chains induced by the presence of an electric field, and
 \item the catalysts and solvents within the polymer solution.
@@
 Within Cardenas' work the following parameters were evaluated to study the desirable characteristics for building highly sensitive sensor devices: a) the chemical composition and viscoelasticity of the polymer solution, b) the thickness of the produced polymeric wires, c) the mechanical pulling on the polymeric jet during electrospinning, and d) the alignment of the polymer chains induced by the presence of an electric field.
-Cardenas' work states that various methods are implemented to produce nanofibers, such as laser ablation, chemical vapor deposition, discharge, and vapour growth.
+Cardenas' work states that various methods are implemented to produce nanofibers, such as laser ablation, chemical vapor deposition, discharge, and vapor growth.
 However, those techniques are abandoned due to their low yield output and expensive equipment.
@@
 
-The production of carbon sstructures involves to main procedures: a) polymer patterning such as photolithography, electrospinning, Computer Numerical Control (CNC), moulding, hot embossing, and recently, Multiple Photon Polymerization; and b) carbonization, which induces further thinning of the patterned polymer and its conversion into carbon.
-Cardenas conducted some experiments to characterize and analyse carbon nano-wires.
+The production of carbon structures involves to main procedures: a) polymer patterning such as photolithography, electrospinning, Computer Numerical Control (CNC), molding, hot embossing, and recently, Multiple Photon Polymerization; and b) carbonization, which induces further thinning of the patterned polymer and its conversion into carbon.
+Cardenas conducted some experiments to characterize and analyze carbon nano-wires.
 Polymeric SU-8 nano fibers were produced by two different methods; for each method different polymer solutions were employed.
@@
 Samples prepared by Method 1 failed the pyrolyzation as the deposited wires were mostly liquid before carbonization.
-The fibers produced by Method 2 had a yeild rate of 81 $\%$.
+The fibers produced by Method 2 had a yield rate of 81 $\%$.
 The diameters after pyrolysis were analyzed and measured using SEM micrographs.
@@
 
+\clearpage
+
+\section{FIND PAPER THAT CONFIRMS THAT WITH THE INCREASE OF PEO CONCENTRATION, THE POROSITY DENSITY INCREASES IN CARBON STRUCTURES AFTER PYROLYSIS. \cite{newPAPER}}
+
+As explained in Section \ref{sec:pyrolysis}, the pyrolysis process is implemented to thermally decompose organic material into carbon. ...
+
 %-----------------------------------

### 2019-05-11 thesis_proposal_LaTeX/Chapters/6_TheoreticalFramework.tex
proposal update
Grammar corrections + new document structure

--- 2019-04-29 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
@@
 \section{Photoresists}
-The electronic industry requires sustainable raw material supply for its development \cite{Sutikno2016}.
+The electronic industry requires a sustainable raw material supply for its development \cite{Sutikno2016}.
 Photoresists are a type of raw material used in microelectronics, which is composed by four main elements: a polymer (resin), a photoactive compound, a solvent, and an additive \cite{Schuster2009}.
-The additive requires to be with a low molecular weight as it is intended to act as a photosensitive material.
+The additive requires to be with low molecular weight as it is intended to act as a photosensitive material.
 Photoresists are used within the manufacturing process of printed circuit boards \cite{Staab2011}.
@@
 
-The polymeric material is available on the broad market either in liguid or solid state; \emph{MicroChem Corp.} (Westborough, MA, USA) is the principal provider of SU-8 photoresist.
+The polymeric material is available on the broad market either in liquid or solid state; \emph{MicroChem Corp.} (Westborough, MA, USA) is the principal provider of SU-8 photoresist.
 SU-8 and similar photoresists are inexpensive with good adhesion on the semiconductor surface and high sensitivity \cite{Staab2011}.
 Epoxy resins are copolymer-thermosetting plastics which are normally produced by a chemical reaction process that involves epichlorohydrin and bisphenol-A compound \cite{Singla2010}.
-A epoxy-based polymer is typically used to produce patterns by lithography with the application of UV radiation.
+An epoxy-based polymer is typically used to produce patterns by lithography with the application of UV radiation.
 Lithography is a technique to transfer patterns from a mask and then transferred onto the substrate \cite{Landis2011,Xu2014}.
@@
 
-In summary, a photoresist is a "epoxy-based resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}
+In summary, a photoresist is an "epoxy-based resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}
 
 \section{Electro-Mechanical Spinning}
-Diverse polymer patterning techniques have being develop for the fabrication of nano-fibers, such as arc discharge \cite{Wang2007}, chemical vapor deposition, laser ablation \cite{Ren1998}, and vapor growth \cite{Nadarajah2008}.
+Diverse polymer patterning techniques have been developed for the fabrication of nano-fibers, such as arc discharge \cite{Wang2007}, chemical vapor deposition, laser ablation \cite{Ren1998}, and vapor growth \cite{Nadarajah2008}.
 Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required.
@@
 Even though electrospinning is an old invention \cite{Anton1930}, it is currently a trending topic among researchers \cite{Huang2003,Reneker2008,Schiffman2008}.
-Some of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers.
+One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers.
 The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $n m$ in some cases, which is something difficult to achieve by other techniques.
@@
 The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning.
-\cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning.
+\cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning.
 \cite{Nataraj2012} The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher precision when patterning.
-Figure \ref{fig:NFES} shows a typical near field mechano-electospinning apparatus.
+Figure \ref{fig:NFES} shows a typical near field mechano-electrospinning apparatus.
 
@@
 
-\section{Pyrolysis}
-Pyrolysis is technique that involves heating of biomass in the absence of air or oxygen at a maximum pyrolysis temperature.
+\section{Pyrolysis} \label{sec:pyrolysis}
+Pyrolysis is a technique that involves heating of biomass in the absence of air or oxygen at a maximum pyrolysis temperature.
 A small amount of oxygen can burn the structures and make them unusable \cite{Pramanick2018}.
@@
 The heating of large biomass molecules results in decomposition.
-The pyrolysis decomposition process comprises char, liquids (condensable gases) and non-condensable gases; where the consensable gases may suffer further decomposition into non-condensable gases such as $C O$, $C O_{2}$, $H_{2}$, and $C H_{4}$.
+The pyrolysis decomposition process comprises char, liquids (condensable gases) and non-condensable gases; where the condensable gases may suffer further decomposition into non-condensable gases such as $C O$, $C O_{2}$, $H_{2}$, and $C H_{4}$.
 Equation \ref{eq:genPyrolysis} is a general representation of the pyrolysis decomposition reaction \cite{Basu2018}.
@@
 
-Pyrolysis yields solid products that are more energy dense than the initial biomass, however the gas and liquid products are less energy dense \cite{Basu2018}.
+Pyrolysis yields solid products that are more energy dense than the initial biomass, however, the gas and liquid products are less energy dense \cite{Basu2018}.
 The liquid product of pyrolysis is usually of colour black containing hydrocarbons with a large amount of oxygen and 20\% water.
-When the liguid product is of interest, a rapid "quenching`` (freeze) is required after pyrolysis to prevent further decomposition or reaction with other substances \cite{Basu2018}.
-The solid yields of pyrolysis is usually around 85\% carbon with some oxygen, hydrogen and other substances that are present within the initial biomass \cite{Basu2018}.
+When the liquid product is of interest, a rapid "quenching`` (freeze) is required after pyrolysis to prevent further decomposition or reaction with other substances \cite{Basu2018}.
+The solid yields of pyrolysis are usually around 85\% carbon with some oxygen, hydrogen and other substances that are present within the initial biomass \cite{Basu2018}.
 The biomass decomposition by pyrolysis produces non-condensable and condensable gases.
 The vapors (condensable gases) add up to the liquid yield of pyrolysis which is generated upon cooling.
-The gases (non-condensable gases) are comprised by ethylene, ethane, methane, carbon monoxide and carbon dioxide \cite{Basu2018}.
+The gases (non-condensable gases) are comprised of ethylene, ethane, methane, carbon monoxide and carbon dioxide \cite{Basu2018}.
 
@@
 Figure \ref{fig:goodbadsolvent} shows how the quality of a solvent affects the polymer distribution within the solution.
-Moreover the prsence of electrolites also modify the structure of the polymer threads.
-In non-ionic solvents, the charges are distributed along the chains and their own repulsion stretches the polimer threads into a more aligned configuration when an electrolyte is added, as detailed in Figure \ref{fig:electrolyteConcentration}.
+Moreover the presence of electrolytes also modify the structure of the polymer threads.
+In non-ionic solvents, the charges are distributed along the chains and their own repulsion stretches the polymer threads into a more aligned configuration when an electrolyte is added, as detailed in Figure \ref{fig:electrolyteConcentration}.
 
@@
 
+\section{Preliminary Experiments}
+
+To verify Flores' work \cite{Flores2017}, a series of rheological measurements have been executed. Since one purpose of the proposed dissertation is to replace
+
 %----------------------------------------------------------------------------------------

### 2019-05-11 thesis_proposal_LaTeX/Chapters/7_Methodology.tex
Grammar corrections + new document structure

@@
 
-The following describes the proposed work to be done to fulfill the objectives stated in this document. The tasks are grouped in several work packages as described bellow:
+The following describes the proposed work to be done to fulfill the objectives stated in this document. The tasks are grouped in several work packages as described below:
 
@@
 \section{Work package 2 : Evaluation of Fabrication Parameters}
-As the polymer solution is the principal input to the proposed technique (See Figure \ref{fig:fabricationFlowChart}), it is required to identify and understand the fabrication parameters that have an impact to the quality of the carbon nano-wires.
+As the polymer solution is the principal input to the proposed technique (See Figure \ref{fig:fabricationFlowChart}), it is required to identify and understand the fabrication parameters that have an impact on the quality of the carbon nano-wires.
 For that reason two tasks are to be executed:
@@
 \section{Work package 5 : Data Collection and Analysis of Results}
-The data collection work package comprehends the study of the created carbon nano-wires using the newly design polymer solution.
+The data collection work package comprehends the study of the created carbon nano-wires using the new design polymer solution.
 The purpose is characterize the carbon nano-wires and compare them to the carbon nano-structures produced by existing techniques.
@@
 Finally the documentation refers to the Thesis writing tasks.
-This task is intended to carried out through the entire thesis development process, as every work package above is to be referenced within the thesis document.
+This task is intended to carry out through the entire thesis development process, as every work package above is to be referenced within the thesis document.
 

### 2019-05-28 thesis_proposal_LaTeX/Chapters/2_ProblmemDefinitionAndMotivation.tex
candidate polys

@@
 Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques.
-However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis.
-The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}.
-In the past years, photon polymerization processes have been applied to the fabrication of nano-structures with the use of an epoxy based photoresist.
-\cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures \cite{Hribar2014}.
+However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis, as it is generally believed that most polymers do not form significant amounts of graphitic carbon when carbonized.
+%The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}.
+In the past years, photopolymerization processes have been applied to the fabrication of nano-structures with the use of an epoxy based photoresist.
+\cite{Boer2014} Photopolymerization techniques deliver patterning resolutions with nano-scale tolerances through two-photon lithography for the production of highly detailed structures \cite{Hribar2014}.
 
@@
 Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner.
-Cardenas \cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis.
+Cardenas \cite{Cardenas2017} showed that electrospinning can be implemented with ease for carbon nano-wire synthesis.
 Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires.

### 2019-05-28 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
candidate polys

@@
 
-The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length).
+The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the fabrication conductive of carbon nano-wires with specified dimensions (diameter and length).
 The rheological properties of polymer solutions along with synthesis parameters are to be amended by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardenas \cite{Cardenas2017} work.
@@
 	\item{
-	Is there any evidence of carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
+	Is there any evidence of conductive carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
 	}
@@
 	\item{
-	Are the optimal fabrication parameters defined \cite{Cardenas2017} for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
+	What are the optimal fabrication parameters for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
 	}
 	\item{
-	What PEO-similar materials can be used to allow the electrospinning technique and favor the carbon nano-wire properties after pyrolysis? 
+	What materials can be used to ease the electrospinning process and favor the carbon nano-wire properties after pyrolysis? 
 	}

### 2019-05-28 thesis_proposal_LaTeX/Chapters/6_TheoreticalFramework.tex
min fix
candidate polys

@@
 Photoresists are classified into two categories.
-The resist is defined as positive if the radiation exposed material is soluble in photoresist developer; otherwise, for negative photoresist the exposed material remains to stay in the photoresist surface as it crosslinks upon exposure \cite{Landis2011,Sharma2012}.
+The resist is defined as positive if the radiation exposed material is soluble in photoresist developer; otherwise, for negative photoresist the exposed material remains to stay in the photoresist surface as it crosslinks upon exposure \cite{Landis2011,Sharma2012}, see Figure \ref{fig:PosNegResist}.
 In the manufacturing process of a semiconductor, the radiation sources which are often used in a lithography process are ultraviolet (UV) and X-ray \cite{Mekaru2015}.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.55\textwidth]{./Figures/PosNegResist.jpg}
+\decoRule
+\caption[Positive and negative resist exposure and development]{Positive and negative resist exposure and development \cite{Hoggan2002}}
+\label{fig:PosNegResist}
+\end{figure}
 
@@
 
-In summary, a photoresist is an "epoxy-based resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}
+In summary, a photoresist is a "resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}
 
@@
 
-\section{Rheometry}
-Rheometry is the measuring technology used to determine rheological data.
-There are different measuring systems, instruments and analysis methods.
-Both, liquids and solid  can be investigated using rotational and oscillatory rheometers.
-Rotational tests are performed to characterize viscous behavior.
-In order to evaluate viscoelastic behavior, creep tests, relaxation tests and oscillatory tests are performed \cite{Flores2017}.
+\section{Preliminary Experiments}
 
-\subsection{Amplitude Sweep}
-An amplitude sweep is a typical test used to characterize the behavior of a polymer
-solution or polymer melt.
-In this basic test a constant angular frequency is applied along with an increasing or decreasing deformation or strain, see Figure \ref{fig:ampSweep} a).
-The obtained results are the storage and loss moduli, $G'$ and $G''$ respectively, along the values of percentage of strain applied.
-The amplitude is the maximum of the oscillatory motion.
-Normally at low frequencies the viscoelastic material presents a linear behavior, this is when the viscoelastic properties are independent of the strain or stress imposed due to the structure of the material stays undisturbed.
-Nevertheless, as the amplitude is increased at some at some point this linear trend changes suddenly.
-Once this critical amplitude value is reached the material becomes more elastic or viscous depending on the solution initial state, see Figure \ref{fig:ampSweep} b) \cite{Flores2017}.
+\subsection{Materials and Sample Preparation}
+
+To verify Flores' work \cite{Flores2017}, a series of rheological measurements have been executed.
+For that purpose, the solutions in Flores work were recreated as follows: The polymer system in the study is SU-8 2002 (SU-8, an epoxy-based negative photoresist) dissolved in cyclopentanone with poly(ethylene oxide (PEO) to alter the viscoelastic properties of the polymer solution, and tetrabutylammonium tetrafluoroborate (TBATFB) to enhance the conductivity.
+Flores's results are listed in Section \ref{sec:FloresWrk}
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{./Figures/ampSweep.png}
+\includegraphics[width=0.75\textwidth]{./Figures/PEset1.png}
 \decoRule
-\caption[Amplitude Sweep]{a) Imposed amplitude along time with constant frequency. b) Results for an amplitude sweep \cite{Flores2017}}
-\label{fig:ampSweep}
+\caption[Set 1 of the Recreation of Flores' "Serie B`` Samples]{Set 1 of the Recreation of Flores' Serie B`` Samples}
+\label{fig:PEset1}
 \end{figure}
-
-\subsection{Frequency Sweep}
-A frequency sweep, is a common oscillatory test useful to understand the rheological behavior of fluids as it measures the viscoelastic properties.
-This measurement is considered a viscoelastic spectrum, in general, the shorter the timescale the more elastic the material behaves.
-These results are related to the molecular structure of the sample.
-Figure \ref{fig:freqSweep} shows a typical data for a polymer melt where different regions are observed.
-Frequency sweep measurements also allow the estimation of the molecular weight distribution characteristics such as entanglement density and process-ability \cite{Flores2017}.
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{./Figures/freqSweep.png}
+\includegraphics[width=0.75\textwidth]{./Figures/PEset2.png}
 \decoRule
-\caption[Frequency Sweep]{Typical results for a frequency sweep. \cite{Flores2017}}
-\label{fig:freqSweep}
+\caption[Set 2 of the Recreation of Flores' "Serie B`` Samples]{Set 2 of the Recreation of Flores' "Serie B`` Samples}
+\label{fig:PEset2}
 \end{figure}
 
-\subsection{Flow Curve}
-The viscosity is measured as a function of the shear rate in a rotational rheometer with different geometries according to the sample.
-Normally three types of behaviours can be characterized in flow curve measurements: a) ideal viscous, b) shear thinning and c) shear thickening.
-Figure \ref{fig:flowCurve} shows three different materials and their response to an imposed shear rate \cite{Flores2017}.
+The samples were prepared as follows, the suitable amounts of PEO and TBATFB were added to 5 $mL$ of SU-8 in a 20 $mL$ vial and stirred at 160 $r p m$ during 1 hour at 75 $^\circ C$.
+The proportions are represented in $w t \%$.
+The samples with higher PEO concentration required to be stirred for more time to get rid of all PEO bundles.
+In order to avert cross-linking of SU-8 threads, during the stirring, the samples were isolated from light.
+a 5 $mL$ syringe of was used to extract the solution from the vial.
+The recreated sample concentrations are depicted in Serie B within Table \ref{tbl:FloresSamples}.
+
+During the preliminary experiments, unlike to Flores' work, only the flow curve characterization was executed for two sample sets, as evidenced in Figures \ref{fig:PEset1} and \ref{fig:PEset2}.
+The two sets were characterized by the generation of flow curves with a "TA Instruments`` Discovery Hybrid Rheometer (DHR) at Tecnológico de Monterrey Campus Estado de México.
+The instrument's configuration was as follows:
+
+\begin{itemize}
+	\item Geometry: 60 $mm$, cone plate, peltier plate steel
+	\item Temperature: 20 $^\circ C$
+	\item Soak Time: 30.0 $s$
+	\item Shear rate: 0.004 to 0.03 $Hz$
+	\item Points per decade: 25
+\end{itemize}
+
+\subsection{Results}
+
+As stated by Flores \cite{Flores2017}, it is expected an increase in viscosity with the increase of PEO concentration.
+However, the rheological results of set 1 (Figure \ref{fig:PEset1results}) do not follow the expectations, as the 0.75 $w t \%$ PEO concentration is less viscous than the 0.50 concentration; and the 0.25 $w t \%$ PEO concentration is more viscous than the 0.75 concentration.
+On the other hand, results are not consistent with Flores' results as the viscosity values are as high as 200 $Pa.s$ as depicted in Figure \ref{fig:PEset1results}.
+The supposed values are to be around 0.0 and 10.0 $Pa.s$.
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{./Figures/flowCurve.png}
+\includegraphics[width=0.75\textwidth]{./Figures/PEset1results.png}
 \decoRule
-\caption[Flow Curves]{a) Flow curve stress vs stress.
-b) Flow curve strain vs shear viscosity.
-Both figures for i Newtonian fluid, ii Shear thinning fluid, iii Shear thickening fluid.
-\cite{Flores2017}}
-\label{fig:flowCurve}
+\caption[Set 1 Flow Curve Characterization of the Recreation of Flores' ``Serie B" Samples]{Set 1 Flow Curve Characterization of the Recreation of Flores' ``Serie B" Samples}
+\label{fig:PEset1results}
 \end{figure}
 
-\section{Preliminary Experiments}
+As shown in Figure \ref{fig:PEset1}, inconsistencies between Flores' work and the current flow curves have been for not stirring the samples until all the PEO lumps get completely dissolved in cyclopentanone.
+The lack of stirring, generated unknown PEO concentrations within each sample, hence the inconsistent results.
 
-To verify Flores' work \cite{Flores2017}, a series of rheological measurements have been executed. Since one purpose of the proposed dissertation is to replace
+For set 2, the rheological flow curve characterization was performed in the same way as in set 1, however, each sample was stirred for approximately 20 minutes before the characterization process.
+See Figure \ref{fig:PEset2}.
+Set 2 results, as depicted in Figure \ref{fig:PEset2results}, are consistent with the expectations.
+However, unlike Flores' results, the replicated flow curves have a less stable/constant value as they present a more pronounced shear thinning behaviour.
+The difference in the shear thinning behaviours shown in Figure \ref{fig:PEset2results} (preliminary experiment, set 2 results) and Figure \ref{fig:SerieBflowCurve} (Flores' results \cite{Flores2017}) may be caused by: 1) the use of different measurement instruments during the characterization process; and 2) the cyclopentanone solvent evaporation.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/PEset2results.png}
+\decoRule
+\caption[Set 2 Flow Curve Characterization of the Recreation of Flores' ``Serie B" Samples]{Set 2 Flow Curve Characterization of the Recreation of Flores' ``Serie B" Samples}
+\label{fig:PEset2results}
+\end{figure}
+
+%Does the viscosity of cyclopentanone coincide with the reported value in the literature? Can you make a table comparing your zero shear viscosity values against Flores'?
+
+\begin{table}[th]
+\caption{Method 1 and Method 2 conditions and parameters \cite{Cardenas2017}}
+\begin{center}
+\begin{tabular}{ >{\raggedright\arraybackslash}p{0.08\textwidth} >{\raggedright\arraybackslash}p{0.27\textwidth} >{\raggedright\arraybackslash}p{0.27\textwidth} >{\raggedright\arraybackslash}p{0.27\textwidth} }
+\hline
+Sample & PEO concentration [$w t \%$] & Preliminary zero shear viscosity measurements [$Pa.s$] & Flores' zero shear viscosity measurements [$Pa.s$] \\
+\hline
+1 & 0.00 & 0.31 & 0.03 \\
+2 & 0.25 & 0.88 & 0.3 \\
+3 & 0.50 & 1.42 & 0.4 \\
+4 & 0.75 & 7.28 & 2 \\
+5 & 1.00 & 9.25 & 3 \\
+\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+\end{center}
+\end{table}
+
+Table \ref{tbl:FloresCompare} compares the current zero shear viscosity measurements and Flores' measurements.
+The comparison shows that both measurements have the same behaviour with similar proportions, as the zero shear viscosity increases with the increase of PEO concentration.
+However, the results show that the current measured values are approximately three times larger that Flores' measurements.
 

### 2019-05-28 thesis_proposal_LaTeX/Chapters/7_Methodology.tex
candidate polys

@@
 
-\section{Work package 1 : Preliminary Literature Review}
+\section{Preliminary Literature Review}
 The first step to the thesis development is the study of preliminary literature and related work.
@@
 
-\section{Work package 2 : Evaluation of Fabrication Parameters}
+\section{Evaluation of Fabrication Parameters}
 As the polymer solution is the principal input to the proposed technique (See Figure \ref{fig:fabricationFlowChart}), it is required to identify and understand the fabrication parameters that have an impact on the quality of the carbon nano-wires.
@@
 
-\section{Work package 3 : Polymer Solution Design}
+\section{Polymer Solution Design}
 Once the process parameters and rheological properties that affect the fabrication of carbon nano-wires are identified, the design process shall take place.
@@
 
-\section{Work package 4 : Fabrication of Carbon Nano-wires}
+\section{Fabrication of Carbon Nano-wires}
 From the rheological analyses, determine and control the polymer solution properties and fabricate carbon nano-wires.
@@
 
-\section{Work package 5 : Data Collection and Analysis of Results}
+\section{Data Collection and Analysis of Results}
 The data collection work package comprehends the study of the created carbon nano-wires using the new design polymer solution.
@@
 
-\section{Work package 6 : Documentation}
+\section{Documentation}
 Finally the documentation refers to the Thesis writing tasks.

### 2019-06-10 NFES_Review/Chapters/_tbl_Collection.tex
NFES review article in progress

% Chapter Template
\begin{landscape}

\chapter{Summary} % Main chapter title

\label{Chapter:Summary}

%\subsubsection*{\color{mygray}[Chapter under work]}
%Once the Methodology has been established, it is important to set up the corresponding activities in an organized and timely manner. This is done using a Workplan Schedule. This provides us a clear idea of the amount of work needed expressed in periods of time.

% move margin to fit table
%\addtolength{\oddsidemargin}{-1.5in}
%\addtolength{\evensidemargin}{-.875in}
\addtolength{\topmargin}{0.5in}

\begin{table}[th]
\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
%\begin{center}
% total table width eq 0.91\textheight = 100%
\begin{tabular}{
>{\raggedright\arraybackslash}p{0.100\textheight}
>{\raggedright\arraybackslash}p{0.100\textheight}
>{\raggedright\arraybackslash}p{0.090\textheight}
>{\raggedright\arraybackslash}p{0.370\textheight}
>{\raggedright\arraybackslash}p{0.180\textheight}
>{\raggedright\arraybackslash}p{0.060\textheight} } 
\hline
Polymer & Solvent & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Reference \\
\hline
polyethylene oxide (PEO) (Dow Inc.: WSR- 301) &
Deionized water &
low-voltage and low-electrical field NFES &
\begin{itemize}[leftmargin=*]
\item Concentration: 1, 2, and 3 PEO wt \%
\item rise in solution conductivity with the increase in PEO concentration
\item Solution Stirring: 24 $h$ of free diffusion followed by 96 $h$ of stirring mixing at 30 $r p m$
\item 3 $m L$ syringe
\item 27 gauge type 304 stainless steel needle
\item solution deposition rate lower than 1 $\mu L / h$
\item needle-to-collector distance: 1 $m m$
\item The voltage turned when the polymer formed a full-sized droplet of 500 $\mu m$ diameter at the needle tip.
\end{itemize} &
\begin{itemize}[leftmargin=*]
\item 
\end{itemize} &
\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
\hline
\label{tbl:FloresCompare}
\end{tabular}
%\end{center}
\end{table}

\begin{table}[th]
\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
%\begin{center}
% total table width eq 0.91\textheight = 100%
\begin{tabular}{
>{\raggedright\arraybackslash}p{0.100\textheight}
>{\raggedright\arraybackslash}p{0.100\textheight}
>{\raggedright\arraybackslash}p{0.090\textheight}
>{\raggedright\arraybackslash}p{0.370\textheight}
>{\raggedright\arraybackslash}p{0.180\textheight}
>{\raggedright\arraybackslash}p{0.060\textheight} } 
\hline
Polymer & Solvent & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Reference \\
\hline
 &
 &
 &
\begin{itemize}[leftmargin=*]
\item NFES process initiated by an air interference with a glass microprobe tip (1 to 3 $\mu m$ tip diameter) to overcome the surface tension
\item Time to produce a stable continuous jet: 45 $min$
\end{itemize} &
 &
\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
\hline
\label{tbl:FloresCompare}
\end{tabular}
%\end{center}
\end{table}

\begin{table}[th]
\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
%\begin{center}
% total table width eq 0.91\textheight = 100%
\begin{tabular}{
>{\raggedright\arraybackslash}p{0.170\textheight}
>{\raggedright\arraybackslash}p{0.170\textheight}
>{\raggedright\arraybackslash}p{0.170\textheight}
>{\raggedright\arraybackslash}p{0.170\textheight}
>{\raggedright\arraybackslash}p{0.170\textheight}
>{\raggedright\arraybackslash}p{0.060\textheight} } 
\hline
Polymer & Solvent & NFES variant & Polymer Solution Properties & Process Properties & Reference \\
\hline
 &  &  &  &  & \cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
 &  &  &  &  & \cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
 &  &  &  &  & \cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
 &  &  &  &  & \cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
 &  &  &  &  & \cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
 &  &  &  &  & \cite{Gupta2007}   \\ %Novel Electrohydrodynamic Printing of Nanocomposite Biopolymer Scaffolds
 &  &  &  &  & \cite{Huang2015}   \\ %Versatile, kinetically controlled, high precision electrohydrodynamic writing of micro/nanofibers
 &  &  &  &  & \cite{Jiang2018}   \\ %Electrohydrodynamic Direct-Writing Micropatterns with Assisted Airflow
 &  &  &  &  & \cite{Kim2018}     \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
 &  &  &  &  & \cite{Lee2012}     \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning
 &  &  &  &  & \cite{Liu2014}     \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
 &  &  &  &  & \cite{Min2013}     \\ %Large-scale organic nanowire lithography and electronics
 &  &  &  &  & \cite{Pan2014}     \\ %Poly($\gamma$-benzyl $\alpha$, l-glutamate) in Cylindrical Near-Field Electrospinning Fabrication and Analysis of Piezoelectric Fibers
 &  &  &  &  & \cite{Pan2015}     \\ %Near-field electrospinning enhances the energy harvesting of hollow PVDF piezoelectric fibers
 &  &  &  &  & \cite{Song2015}    \\ %Patterned polydiacetylene-embedded polystyrene nanofibers based on electrohydrodynamic jet printing
 &  &  &  &  & \cite{Sun2006}     \\ %Near-Field Electrospinning
 &  &  &  &  & \cite{Wang2015}    \\ %Research on Multinozzle Near-Field Electrospinning Patterned Deposition
 &  &  &  &  & \cite{Wang2017}    \\ %Controllable deposition distance of aligned pattern via dual-nozzle near-field electrospinning
 &  &  &  &  & \cite{Wang2018}    \\ %Fabrication and evaluation of controllable deposition distance for aligned pattern by multi-nozzle near-field electrospinning
 &  &  &  &  & \cite{Xu2014}      \\ %Accuracy Improvement of Nano-fiber Deposition by Near-Field Electrospinning
 &  &  &  &  & \cite{Xue2014}     \\ %Rapid Patterning of 1-D Collagenous Topography as an ECM Protein Fibril Platform for Image Cytometry
 &  &  &  &  & \cite{Zheng2010}   \\ %Precision deposition of a nanofibre by near-field electrospinning
 &  &  &  &  & \cite{Zheng2014}   \\ %Electrohydrodynamic Direct-Write Orderly Micro/Nanofibrous Structure on Flexible Insulating Substrate
 &  &  &  &  & \cite{Zheng2012}   \\ %Polymer nanofibers prepared by low-voltage near-field electrospinning
\hline
\label{tbl:FloresCompare}
\end{tabular}
%\end{center}
\end{table}

\addtolength{\oddsidemargin}{0.0in}
\addtolength{\evensidemargin}{0.0in}
\addtolength{\topmargin}{0.0in}
\end{landscape}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------

### 2019-06-10 NFES_Review/Chapters/_tbl_Collection.tex
review progress

@@
 \begin{tabular}{
->{\raggedright\arraybackslash}p{0.100\textheight}
->{\raggedright\arraybackslash}p{0.100\textheight}
+>{\raggedright\arraybackslash}p{0.130\textheight}
+>{\raggedright\arraybackslash}p{0.130\textheight}
 >{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.370\textheight}
+>{\raggedright\arraybackslash}p{0.310\textheight}
 >{\raggedright\arraybackslash}p{0.180\textheight}
@@
 \hline
-polyethylene oxide (PEO) (Dow Inc.: WSR- 301) &
+Poly(ethylene oxide) (PEO) &
 Deionized water &
-low-voltage and low-electrical field NFES &
+Low-Voltage and Low-Electrical Field NFES &
 \begin{itemize}[leftmargin=*]
-\item Concentration: 1, 2, and 3 PEO wt \%
-\item rise in solution conductivity with the increase in PEO concentration
-\item Solution Stirring: 24 $h$ of free diffusion followed by 96 $h$ of stirring mixing at 30 $r p m$
+\item PEO Concentration: 1, 2, and 3 $w t \%$
+\item Rise in solution conductivity with the increase in PEO concentration
+\item Solution Stirring: 24 $h$ of free diffusion followed by 96 $h$ of stirring at 30 $r p m$
 \item 3 $m L$ syringe
 \item 27 gauge type 304 stainless steel needle
-\item solution deposition rate lower than 1 $\mu L / h$
+\item Solution deposition rate: lower than 1 $\mu L / h$
 \item needle-to-collector distance: 1 $m m$
-\item The voltage turned when the polymer formed a full-sized droplet of 500 $\mu m$ diameter at the needle tip.
 \end{itemize} &
 \begin{itemize}[leftmargin=*]
-\item 
+\item Diameter: 50-425 $n m$
 \end{itemize} &
@@
 \item Time to produce a stable continuous jet: 45 $min$
+\item Polymer jet initiated at 400-600 $V$ and dispensed at 200-400 $V$
+\item Collector linear speed: 10-40 $m m / s$
+\item The voltage turned on when the solution formed a full-sized droplet of 500 $\mu m$ diameter at the needle tip.
 \end{itemize} &
@@
 \cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
+\hline
+Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) &
+acetonitrile / toluene mixture (65 / 35) or acetic acid / toluene (17 / 83) or pure toluene &
+ &
+\begin{itemize}[leftmargin=*]
+\item Concentrations:
+    \begin{itemize}[leftmargin=*]
+    \item 250 $m g$ of PEO in 3.5 $m L$ of acetonitrile / toluene
+    \item 250 $m g$ of PEO in 3 $m L$ of acetic acid / toluene
+    \item 10 $m g$ of MEH-PPV in 2 $m L$ of toluene
+    \end{itemize}
+\end{itemize} &
+ &
+\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
 \hline
@@
 \begin{tabular}{
->{\raggedright\arraybackslash}p{0.170\textheight}
->{\raggedright\arraybackslash}p{0.170\textheight}
->{\raggedright\arraybackslash}p{0.170\textheight}
->{\raggedright\arraybackslash}p{0.170\textheight}
->{\raggedright\arraybackslash}p{0.170\textheight}
+>{\raggedright\arraybackslash}p{0.130\textheight}
+>{\raggedright\arraybackslash}p{0.130\textheight}
+>{\raggedright\arraybackslash}p{0.090\textheight}
+>{\raggedright\arraybackslash}p{0.310\textheight}
+>{\raggedright\arraybackslash}p{0.180\textheight}
 >{\raggedright\arraybackslash}p{0.060\textheight} }  
 \hline
-Polymer & Solvent & NFES variant & Polymer Solution Properties & Process Properties & Reference \\
+Polymer & Solvent & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Reference \\
 \hline
- &  &  &  &  & \cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
- &  &  &  &  & \cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
+% &  &  &  &  & \cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
+% &  &  &  &  & \cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
  &  &  &  &  & \cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns

### 2019-06-10 NFES_Review/Chapters/_tbl_Collection.tex
rotate table pages

@@
 % Chapter Template
+
 \begin{landscape}
+\pagebreak[4]\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 90}
 
@@
 Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) &
-acetonitrile / toluene mixture (65 / 35) or acetic acid / toluene (17 / 83) or pure toluene &
+acetonitrile / toluene mixture (65 / 35); acetic acid / toluene (17 / 83); pure toluene &
  &
@@
     \begin{itemize}[leftmargin=*]
-    \item 250 $m g$ of PEO in 3.5 $m L$ of acetonitrile / toluene
-    \item 250 $m g$ of PEO in 3 $m L$ of acetic acid / toluene
-    \item 10 $m g$ of MEH-PPV in 2 $m L$ of toluene
+    \item MEH-PPV solution: 10 $m g$ of MEH-PPV in 2 $m L$ of toluene
+    \item 500 $\mu L$ of MEH-PPV solution with 250 $m g$ of PEO in 3.5 $m L$ of acetonitrile / toluene (65 / 35)
+    \item 500 $\mu L$ of MEH-PPV solution with 250 $m g$ of PEO in 3 $m L$ of acetic acid / toluene (17 / 83)
     \end{itemize}
@@
 
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+%\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.130\textheight}
+>{\raggedright\arraybackslash}p{0.130\textheight}
+>{\raggedright\arraybackslash}p{0.090\textheight}
+>{\raggedright\arraybackslash}p{0.310\textheight}
+>{\raggedright\arraybackslash}p{0.180\textheight}
+>{\raggedright\arraybackslash}p{0.060\textheight} } 
+\hline
+ &
+ &
+ &
+\begin{itemize}[leftmargin=*]
+\item[]
+    \begin{itemize}[leftmargin=*]
+    \item The resulting MEH-PPV/PEO concentration is 1:100
+    \end{itemize}
+\item Solution Stirring:
+    \begin{itemize}[leftmargin=*]
+    \item MEH-PPV solution stirred for 4 $h$
+    \item PEO solution stirred for 8 $h$
+    \item MEH-PPV/PEO solution stirred and ultrasonically agitated
+    \end{itemize}
+\item Collector substrate: SiO2/Si (oxide thickness = 800 $n m$)
+\item needle-to-collector distance: 500 $\mu m$
+\item $\mu m$-diameter tip Tungsten spinneret in a 26 gauge needle
+\item Solution deposition rate: 50 $\mu L / h$
+\item Electrostatic voltage: around 1.3 $k V$
+\item x-y stage velocity: 50 $c m / s$
+\end{itemize} &
+\begin{itemize}
+\item distance between adjacent fibers: around 100 $\mu m$
+\item Fiber diameter: around 100 $n m$
+\end{itemize} &
+\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
+\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+%\end{center}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}[th]
@@
 \addtolength{\topmargin}{0.0in}
+
 \end{landscape}
+\pagebreak[4]\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 0}
 

### 2019-06-10 NFES_Review/Chapters/_tbl_Collection.tex
min feature

@@
 Deionized water &
-Low-Voltage and Low-Electrical Field NFES &
+Mechano electrospinning &
 \begin{itemize}[leftmargin=*]
@@
 \item needle-to-collector distance: 1 $m m$
+\item Collector substrate: Pyrolyzed SU-8 carbon and Si
 \end{itemize} &
@@
 acetonitrile / toluene mixture (65 / 35); acetic acid / toluene (17 / 83); pure toluene &
- &
+Mechano electrospinning &
 \begin{itemize}[leftmargin=*]
@@
 \end{itemize} &
- &
+\begin{itemize}
+\item Distance between adjacent fibers: around 100 $\mu m$
+\item Fiber diameter: around 100 $n m$
+\end{itemize} &
 \cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
@@
 \end{itemize} &
-\begin{itemize}
-\item distance between adjacent fibers: around 100 $\mu m$
-\item Fiber diameter: around 100 $n m$
-\end{itemize} &
+ &
 \cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
@@
 
-\addtolength{\oddsidemargin}{0.0in}
-\addtolength{\evensidemargin}{0.0in}
+%\addtolength{\oddsidemargin}{0.0in}
+%\addtolength{\evensidemargin}{0.0in}
 \addtolength{\topmargin}{0.0in}

### 2019-06-11 NFES_Review/Chapters/_tbl_Collection.tex
DLS Training files

@@
 >{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.310\textheight}
+>{\raggedright\arraybackslash}p{0.350\textheight}
 >{\raggedright\arraybackslash}p{0.180\textheight}
->{\raggedright\arraybackslash}p{0.060\textheight} }  
+>{\raggedright\arraybackslash}p{0.020\textheight} }  
 \hline
-Polymer & Solvent & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Reference \\
+Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
 \hline
@@
 \item Collector substrate: Pyrolyzed SU-8 carbon and Si
+\item NFES process initiated by an air interference with a glass microprobe tip (1 to 3 $\mu m$ tip diameter) to overcome the surface tension
+\item Time to produce a stable continuous jet: 45 $min$
+\item Polymer jet initiated at 400-600 $V$ and dispensed at 200-400 $V$
+\item Collector linear speed: 10-40 $m m / s$
+\item The voltage turned on when the solution formed a full-sized droplet of 500 $\mu m$ diameter at the needle tip.
 \end{itemize} &
@@
 >{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.310\textheight}
+>{\raggedright\arraybackslash}p{0.350\textheight}
 >{\raggedright\arraybackslash}p{0.180\textheight}
->{\raggedright\arraybackslash}p{0.060\textheight} } 
+>{\raggedright\arraybackslash}p{0.020\textheight} }  
 \hline
-Polymer & Solvent & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Reference \\
-\hline
- &
- &
- &
-\begin{itemize}[leftmargin=*]
-\item NFES process initiated by an air interference with a glass microprobe tip (1 to 3 $\mu m$ tip diameter) to overcome the surface tension
-\item Time to produce a stable continuous jet: 45 $min$
-\item Polymer jet initiated at 400-600 $V$ and dispensed at 200-400 $V$
-\item Collector linear speed: 10-40 $m m / s$
-\item The voltage turned on when the solution formed a full-sized droplet of 500 $\mu m$ diameter at the needle tip.
-\end{itemize} &
- &
-\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
+Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
 \hline
@@
     \item 500 $\mu L$ of MEH-PPV solution with 250 $m g$ of PEO in 3 $m L$ of acetic acid / toluene (17 / 83)
+    \item The resulting MEH-PPV/PEO concentration is 1:100
     \end{itemize}
+\item Solution Stirring: MEH-PPV solution stirred for 4 $h$; PEO solution stirred for 8 $h$; MEH-PPV/PEO solution stirred and ultrasonically agitated
+\item Collector substrate: SiO2/Si (oxide thickness = 800 $n m$)
+\item needle-to-collector distance: 500 $\mu m$
+\item $\mu m$-diameter tip Tungsten spinneret in a 26 gauge needle
+\item Solution deposition rate: 50 $\mu L / h$
+\item Electrostatic voltage: around 1.3 $k V$
+\item x-y stage velocity: 50 $c m / s$
 \end{itemize} &
-\begin{itemize}
+\begin{itemize}[leftmargin=*]
 \item Distance between adjacent fibers: around 100 $\mu m$
@@
 >{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.310\textheight}
+>{\raggedright\arraybackslash}p{0.350\textheight}
 >{\raggedright\arraybackslash}p{0.180\textheight}
->{\raggedright\arraybackslash}p{0.060\textheight} } 
+>{\raggedright\arraybackslash}p{0.020\textheight} }  
 \hline
- &
- &
+Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
+\hline
+Poly(ethylene oxide) (PEO) &
+Water &
  &
 \begin{itemize}[leftmargin=*]
-\item[]
-    \begin{itemize}[leftmargin=*]
-    \item The resulting MEH-PPV/PEO concentration is 1:100
-    \end{itemize}
-\item Solution Stirring:
-    \begin{itemize}[leftmargin=*]
-    \item MEH-PPV solution stirred for 4 $h$
-    \item PEO solution stirred for 8 $h$
-    \item MEH-PPV/PEO solution stirred and ultrasonically agitated
-    \end{itemize}
-\item Collector substrate: SiO2/Si (oxide thickness = 800 $n m$)
-\item needle-to-collector distance: 500 $\mu m$
-\item $\mu m$-diameter tip Tungsten spinneret in a 26 gauge needle
-\item Solution deposition rate: 50 $\mu L / h$
-\item Electrostatic voltage: around 1.3 $k V$
-\item x-y stage velocity: 50 $c m / s$
+\item 7 wt \% PEO aqueous solution
+\item Under room temperature and 1 $atm$
 \end{itemize} &
  &
-\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
+\cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
 \hline
@@
 % &  &  &  &  & \cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
- &  &  &  &  & \cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
+% &  &  &  &  & \cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
  &  &  &  &  & \cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering

### 2019-06-11 NFES_Review/Chapters/_tbl_Collection.tex
article progress

@@
 \item 7 wt \% PEO aqueous solution
-\item Under room temperature and 1 $atm$
+\item Under room temperature at 1 $atm$
+\item needle-to-collector distance: 500 $\mu m$
+\item needle diameter: outer: 200 $\mu m$; inner: 100 $\mu m$
+\item applied voltage for jet initiation: 1.5 $k V$
+\item applied voltage for fiber deposition: 600 $V$
+\item Mechanical drawing is applied by using a tungsten probe with 1 $\mu m$ tip diameter to poke inside the meniscus.
+\item The probe is then rapidly pulled away from the polymer droplet to activate the continuous electrospinning process
+\item polymer jet diameter: 3 $\mu m$
+\item polymer feed rate: 0.1 $\mu L / h$
+\item x-y stage velocity: 120 $m m / s$
 \end{itemize} &
- &
+\begin{itemize}[leftmargin=*]
+\item 108 $m$ yield in 15 $min$ with a fiber diameter of 709 $\pm$ 131 $n m$
+\item Fiber diameter: around 49-74 $n m$ when applied voltage is 800 $V$
+\end{itemize} &
 \cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns

### 2019-06-11 NFES_Review/Chapters/_tbl_Collection.tex
order with prices

@@
 Water &
- &
+Mechano electrospinning &
 \begin{itemize}[leftmargin=*]
@@
 
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+%\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.130\textheight}
+>{\raggedright\arraybackslash}p{0.130\textheight}
+>{\raggedright\arraybackslash}p{0.090\textheight}
+>{\raggedright\arraybackslash}p{0.350\textheight}
+>{\raggedright\arraybackslash}p{0.180\textheight}
+>{\raggedright\arraybackslash}p{0.020\textheight} }  
+\hline
+Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
+\hline
+Poly($\varepsilon$-Caprolactone) (PCL) &
+\emph{Not applicable.} &
+Melt Electrospinning Writing (MEW) &
+\begin{itemize}[leftmargin=*]
+\item Collector substrate: NCO-sP(EO-stat-PO)-coated glass slide surfaces
+\item fibre diameters are between 5 and 30 $\mu m$
+\end{itemize} &
+\begin{itemize}[leftmargin=*]
+\item 1
+\item 2
+\end{itemize} &
+\cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
+\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+%\end{center}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % &  &  &  &  & \cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
- &  &  &  &  & \cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
+% &  &  &  &  & \cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
  &  &  &  &  & \cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.

### 2019-06-12 NFES_Review/Chapters/_tbl_Collection.tex
flip table

@@
 
-\begin{landscape}
-\pagebreak[4]\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 90}
+%\begin{landscape}
+%\pagebreak[4]\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 90}
 
@@
 This provides us a clear idea of the amount of work needed expressed in periods of time.
+
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+%\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
+\hline
+Polymer(s): &
+Poly(ethylene oxide) (PEO) \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+Deionized water \\
+
+\hline
+NFES Variant: &
+Low-Voltage NFES \\
+
+\hline
+Polymer Solution and Process Properties: &
+\begin{itemize}[leftmargin=*]
+\item PEO Concentration: 1, 2, and 3 $w t \%$
+\item Rise in solution conductivity with the increase in PEO concentration
+\item Solution Stirring: 24 $h$ of free diffusion followed by 96 $h$ of stirring at 30 $r p m$
+\item 3 $m L$ syringe
+\item 27 gauge type 304 stainless steel needle
+\item Solution deposition rate: lower than 1 $\mu L / h$
+\item needle-to-collector distance: 1 $m m$
+\item Collector substrate: Pyrolyzed SU-8 carbon and Si
+\item NFES process initiated by an air interference with a glass microprobe tip (1 to 3 $\mu m$ tip diameter) to overcome the surface tension
+\item Time to produce a stable continuous jet: 45 $min$
+\item Polymer jet initiated at 400-600 $V$ and dispensed at 200-400 $V$
+\item Collector linear speed: 10-40 $m m / s$
+\item The voltage turned on when the solution formed a full-sized droplet of 500 $\mu m$ diameter at the needle tip.
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
+\begin{itemize}[leftmargin=*]
+\item Diameter: 50-425 $n m$
+\end{itemize} \\
+
+\hline
+Ref: & \cite{Bisht2011} \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
+\arrayrulecolor{black}\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+%\end{center}
+\end{table}
+
+\begin{landscape}
+\pagebreak[4]\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 90}
 
@@
 Deionized water &
-Mechano electrospinning &
+Low-Voltage NFES &
 \begin{itemize}[leftmargin=*]
@@
 acetonitrile / toluene mixture (65 / 35); acetic acid / toluene (17 / 83); pure toluene &
-Mechano electrospinning &
+\emph{Not determined.} &
 \begin{itemize}[leftmargin=*]
@@
 Water &
-Mechano electrospinning &
+Scanning Tip Electrospinning and NFES &
 \begin{itemize}[leftmargin=*]
@@
 \item Collector substrate: NCO-sP(EO-stat-PO)-coated glass slide surfaces
-\item fibre diameters are between 5 and 30 $\mu m$
+\item Accelerating voltage 2.0–10.0 $k V$
+\item Collector distance: 1–10 $m m$
+\item Heating temperature: 80–120 $^\circ C$
+\item Feeding air pressure 0.5–4.0 $bar$
+\item Spinneret diameters: 21, 23, 25, 27, 30, and 33 $G$
+\item Axis velocity: 1000–9000 $m m / min$
+\item Fibre spacing: 100 $\mu m$
 \end{itemize} &
 \begin{itemize}[leftmargin=*]
-\item 1
-\item 2
+\item Filament surface is smooth and homogeneous
+\item The crystalline regions formed perpendicular to the filament
+\item Fiber diameter: 817 $\pm$ 165 $n m$
 \end{itemize} &
 \cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
+\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+%\end{center}
+\end{table}
+
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+%\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.130\textheight}
+>{\raggedright\arraybackslash}p{0.130\textheight}
+>{\raggedright\arraybackslash}p{0.090\textheight}
+>{\raggedright\arraybackslash}p{0.350\textheight}
+>{\raggedright\arraybackslash}p{0.180\textheight}
+>{\raggedright\arraybackslash}p{0.020\textheight} }  
+\hline
+Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
+\hline
+Poly(vinylidine fluorid) (PVDF) &
+N,N-dimethylformamide (DMF) &
+Helix Electrohydrodynamic Printing (HE-printing) &
+\begin{itemize}[leftmargin=*]
+\item 1.8 $g$ PVDF in 4.1 $g$ of DMF and 4.1 $g$ of acetone to obtain a concentration of 18\%
+\item Solution kept at 35 $^\circ C$ for about 6 $h$ until the solution was homogeneous.
+\item Collector substrate: Poly(dimethylsiloxane) (PDMS) on Ecoflex
+\item Solution feed rate: 400 $n L / min$
+\item Needle diameter: inner 260 $\mu m$; external 510 $\mu m$
+\item Applied voltage: 1.5–3 $k V$
+\item Nozzle-to-collector distance: 10-50 $m m$
+\item x-y stage velocity: 0-400 $m m / min$
+\item At room temperature and 35–45\% humidity
+\end{itemize} &
+\begin{itemize}[leftmargin=*]
+\item Stretchable serpentine structures with specific wavelength and amplitude.
+\item Wavelength: about 100-2000 $\mu m$
+\item Fiber diameter: about 1.5-3 $\mu m$
+\end{itemize} &
+\cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
 \hline
@@
 % &  &  &  &  & \cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
- &  &  &  &  & \cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
+% &  &  &  &  & \cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
  &  &  &  &  & \cite{Gupta2007}   \\ %Novel Electrohydrodynamic Printing of Nanocomposite Biopolymer Scaffolds

### 2019-06-12 NFES_Review/Chapters/_tbl_Collection.tex
more flips

@@
 
+%----------------------------------------------------------------------%
 \begin{table}[th]
@@
 \end{table}
+%----------------------------------------------------------------------%
 
-\begin{landscape}
-\pagebreak[4]\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 90}
-
-% move margin to fit table
-%\addtolength{\oddsidemargin}{-1.5in}
-%\addtolength{\evensidemargin}{-.875in}
-\addtolength{\topmargin}{0.5in}
-
+%----------------------------------------------------------------------%
 \begin{table}[th]
@@
 \begin{tabular}{
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.350\textheight}
->{\raggedright\arraybackslash}p{0.180\textheight}
->{\raggedright\arraybackslash}p{0.020\textheight} }  
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
 \hline
-Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
+Polymer(s): &
+Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+acetonitrile / toluene mixture (65 / 35); acetic acid / toluene (17 / 83); pure toluene \\
+
 \hline
-Poly(ethylene oxide) (PEO) &
-Deionized water &
-Low-Voltage NFES &
-\begin{itemize}[leftmargin=*]
-\item PEO Concentration: 1, 2, and 3 $w t \%$
-\item Rise in solution conductivity with the increase in PEO concentration
-\item Solution Stirring: 24 $h$ of free diffusion followed by 96 $h$ of stirring at 30 $r p m$
-\item 3 $m L$ syringe
-\item 27 gauge type 304 stainless steel needle
-\item Solution deposition rate: lower than 1 $\mu L / h$
-\item needle-to-collector distance: 1 $m m$
-\item Collector substrate: Pyrolyzed SU-8 carbon and Si
-\item NFES process initiated by an air interference with a glass microprobe tip (1 to 3 $\mu m$ tip diameter) to overcome the surface tension
-\item Time to produce a stable continuous jet: 45 $min$
-\item Polymer jet initiated at 400-600 $V$ and dispensed at 200-400 $V$
-\item Collector linear speed: 10-40 $m m / s$
-\item The voltage turned on when the solution formed a full-sized droplet of 500 $\mu m$ diameter at the needle tip.
-\end{itemize} &
-\begin{itemize}[leftmargin=*]
-\item Diameter: 50-425 $n m$
-\end{itemize} &
-\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
+NFES Variant: &
+\emph{Not determined.} \\
+
 \hline
-\label{tbl:FloresCompare}
-\end{tabular}
-%\end{center}
-\end{table}
-
-\begin{table}[th]
-\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
-%\begin{center}
-% total table width eq 0.91\textheight = 100%
-\begin{tabular}{
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.350\textheight}
->{\raggedright\arraybackslash}p{0.180\textheight}
->{\raggedright\arraybackslash}p{0.020\textheight} }  
-\hline
-Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
-\hline
-Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) &
-acetonitrile / toluene mixture (65 / 35); acetic acid / toluene (17 / 83); pure toluene &
-\emph{Not determined.} &
+Polymer Solution and Process Properties: &
 \begin{itemize}[leftmargin=*]
@@
 \item x-y stage velocity: 50 $c m / s$
-\end{itemize} &
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
 \begin{itemize}[leftmargin=*]
@@
 \item Fiber diameter: around 100 $n m$
-\end{itemize} &
-\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
+\end{itemize} \\
+
 \hline
+Ref: & \cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
+\arrayrulecolor{black}\hline
 \label{tbl:FloresCompare}
@@
 \end{table}
+%----------------------------------------------------------------------%
+
+\begin{landscape}
+\pagebreak[4]\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 90}
+
+% move margin to fit table
+%\addtolength{\oddsidemargin}{-1.5in}
+%\addtolength{\evensidemargin}{-.875in}
+\addtolength{\topmargin}{0.5in}
 

### 2019-06-13 NFES_Review/Chapters/_tbl_Collection.tex
progress

@@
 \caption{Electrospun Polymer Solutions - Solution and Process Parameters}
-%\begin{center}
+\begin{center}
 % total table width eq 0.91\textheight = 100%
@@
 \end{tabular}
-%\end{center}
+\end{center}
 \end{table}
@@
 
-\begin{landscape}
-\pagebreak[4]\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 90}
-
-% move margin to fit table
-%\addtolength{\oddsidemargin}{-1.5in}
-%\addtolength{\evensidemargin}{-.875in}
-\addtolength{\topmargin}{0.5in}
-
+%----------------------------------------------------------------------%
 \begin{table}[th]
 \caption{Electrospun Polymer Solutions - Solution and Process Parameters}
-%\begin{center}
+\begin{center}
 % total table width eq 0.91\textheight = 100%
 \begin{tabular}{
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.350\textheight}
->{\raggedright\arraybackslash}p{0.180\textheight}
->{\raggedright\arraybackslash}p{0.020\textheight} }  
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
 \hline
-Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
+Polymer(s): &
+Poly(ethylene oxide) (PEO) \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+Water \\
+
 \hline
-Poly(ethylene oxide) (PEO) &
-Water &
-Scanning Tip Electrospinning and NFES &
+NFES Variant: &
+Scanning Tip Electrospinning and NFES \\
+
+\hline
+Polymer Solution and Process Properties: &
 \begin{itemize}[leftmargin=*]
@@
 \item x-y stage velocity: 120 $m m / s$
-\end{itemize} &
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
 \begin{itemize}[leftmargin=*]
@@
 \item Fiber diameter: around 49-74 $n m$ when applied voltage is 800 $V$
-\end{itemize} &
-\cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
+\end{itemize} \\
+
 \hline
+Ref: & \cite{Chang2008} \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
+\arrayrulecolor{black}\hline
 \label{tbl:FloresCompare}
 \end{tabular}
-%\end{center}
+\end{center}
 \end{table}
+%----------------------------------------------------------------------%
 
+%----------------------------------------------------------------------%
 \begin{table}[th]
 \caption{Electrospun Polymer Solutions - Solution and Process Parameters}
-%\begin{center}
+\begin{center}
 % total table width eq 0.91\textheight = 100%
 \begin{tabular}{
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.350\textheight}
->{\raggedright\arraybackslash}p{0.180\textheight}
->{\raggedright\arraybackslash}p{0.020\textheight} }  
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
 \hline
-Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
+Polymer(s): &
+Poly($\varepsilon$-Caprolactone) (PCL) \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+\emph{Not applicable.} \\
+
 \hline
-Poly($\varepsilon$-Caprolactone) (PCL) &
-\emph{Not applicable.} &
-Melt Electrospinning Writing (MEW) &
+NFES Variant: &
+Melt Electrospinning Writing (MEW) \\
+
+\hline
+Polymer Solution and Process Properties: &
 \begin{itemize}[leftmargin=*]
@@
 \item Fibre spacing: 100 $\mu m$
-\end{itemize} &
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
 \begin{itemize}[leftmargin=*]
@@
 \item Fiber diameter: 817 $\pm$ 165 $n m$
-\end{itemize} &
-\cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
+\end{itemize} \\
+
 \hline
+Ref: & \cite{Dalton2015} \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
+\arrayrulecolor{black}\hline
 \label{tbl:FloresCompare}
 \end{tabular}
-%\end{center}
+\end{center}
 \end{table}
+%----------------------------------------------------------------------%
 
+%----------------------------------------------------------------------%
 \begin{table}[th]
 \caption{Electrospun Polymer Solutions - Solution and Process Parameters}
-%\begin{center}
+\begin{center}
 % total table width eq 0.91\textheight = 100%
 \begin{tabular}{
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.350\textheight}
->{\raggedright\arraybackslash}p{0.180\textheight}
->{\raggedright\arraybackslash}p{0.020\textheight} }  
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
 \hline
-Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
+Polymer(s): &
+Poly(vinylidine fluorid) (PVDF) \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+N,N-dimethylformamide (DMF) \\
+
 \hline
-Poly(vinylidine fluorid) (PVDF) &
-N,N-dimethylformamide (DMF) &
-Helix Electrohydrodynamic Printing (HE-printing) &
+NFES Variant: &
+Helix Electrohydrodynamic Printing (HE-printing) \\
+
+\hline
+Polymer Solution and Process Properties: &
 \begin{itemize}[leftmargin=*]
@@
 \item At room temperature and 35–45\% humidity
-\end{itemize} &
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
 \begin{itemize}[leftmargin=*]
@@
 \item Fiber diameter: about 1.5-3 $\mu m$
-\end{itemize} &
-\cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
+\end{itemize} \\
+
 \hline
+Ref: & \cite{Duan2017} \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
+\arrayrulecolor{black}\hline
 \label{tbl:FloresCompare}
 \end{tabular}
-%\end{center}
+\end{center}
 \end{table}
+%----------------------------------------------------------------------%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%----------------------------------------------------------------------%
 \begin{table}[th]
 \caption{Electrospun Polymer Solutions - Solution and Process Parameters}
-%\begin{center}
+\begin{center}
 % total table width eq 0.91\textheight = 100%
 \begin{tabular}{
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.130\textheight}
->{\raggedright\arraybackslash}p{0.090\textheight}
->{\raggedright\arraybackslash}p{0.350\textheight}
->{\raggedright\arraybackslash}p{0.180\textheight}
->{\raggedright\arraybackslash}p{0.020\textheight} }  
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
 \hline
-Polymer(s) & Solvent(s) & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Ref. \\
+Polymer(s): &
+Polyhedral Oligomeric Silsesquioxane-Poly(Carbonate-Urea)Urethane (POSS-PCU) and Polyhedral Oligomeric Silsesquioxane-Poly(Caprolactone-Poly(Carbonate-Urea)Urethane) (POSS-PCL-PCU)\\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+Dimethylacetamide (DMAC) and 1-Butanol \\
+
 \hline
-% &  &  &  &  & \cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
-% &  &  &  &  & \cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
-% &  &  &  &  & \cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
-% &  &  &  &  & \cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
-% &  &  &  &  & \cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
- &  &  &  &  & \cite{Gupta2007}   \\ %Novel Electrohydrodynamic Printing of Nanocomposite Biopolymer Scaffolds
- &  &  &  &  & \cite{Huang2015}   \\ %Versatile, kinetically controlled, high precision electrohydrodynamic writing of micro/nanofibers
- &  &  &  &  & \cite{Jiang2018}   \\ %Electrohydrodynamic Direct-Writing Micropatterns with Assisted Airflow
- &  &  &  &  & \cite{Kim2018}     \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
- &  &  &  &  & \cite{Lee2012}     \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning
- &  &  &  &  & \cite{Liu2014}     \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
- &  &  &  &  & \cite{Min2013}     \\ %Large-scale organic nanowire lithography and electronics
- &  &  &  &  & \cite{Pan2014}     \\ %Poly($\gamma$-benzyl $\alpha$, l-glutamate) in Cylindrical Near-Field Electrospinning Fabrication and Analysis of Piezoelectric Fibers
- &  &  &  &  & \cite{Pan2015}     \\ %Near-field electrospinning enhances the energy harvesting of hollow PVDF piezoelectric fibers
- &  &  &  &  & \cite{Song2015}    \\ %Patterned polydiacetylene-embedded polystyrene nanofibers based on electrohydrodynamic jet printing
- &  &  &  &  & \cite{Sun2006}     \\ %Near-Field Electrospinning
- &  &  &  &  & \cite{Wang2015}    \\ %Research on Multinozzle Near-Field Electrospinning Patterned Deposition
- &  &  &  &  & \cite{Wang2017}    \\ %Controllable deposition distance of aligned pattern via dual-nozzle near-field electrospinning
- &  &  &  &  & \cite{Wang2018}    \\ %Fabrication and evaluation of controllable deposition distance for aligned pattern by multi-nozzle near-field electrospinning
- &  &  &  &  & \cite{Xu2014}      \\ %Accuracy Improvement of Nano-fiber Deposition by Near-Field Electrospinning
- &  &  &  &  & \cite{Xue2014}     \\ %Rapid Patterning of 1-D Collagenous Topography as an ECM Protein Fibril Platform for Image Cytometry
- &  &  &  &  & \cite{Zheng2010}   \\ %Precision deposition of a nanofibre by near-field electrospinning
- &  &  &  &  & \cite{Zheng2014}   \\ %Electrohydrodynamic Direct-Write Orderly Micro/Nanofibrous Structure on Flexible Insulating Substrate
- &  &  &  &  & \cite{Zheng2012}   \\ %Polymer nanofibers prepared by low-voltage near-field electrospinning
+NFES Variant: &
+Electrohydrodynamic 3D Print-patterning or Electrohydrodynamic Jetting \\
+
 \hline
+Polymer Solution and Process Properties: &
+\begin{itemize}[leftmargin=*]
+\item Solution concentration: POSS-PCU and POSS-PCL-PCU used in 20\% w/w concentration in DMAC
+\item Needle diameter: 750 $\mu m$
+\item Applied voltage: 8.0-10.0 $k V$
+\item Solution flow rate: less than 1 $\mu L / min$
+\item Needle-to-collector distance: about between 500 $\mu m$ to 2 $m m$
+\item x-y stage velocity: 10 $m m / s$
+\item Ethanol-coated substrate
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
+\begin{itemize}[leftmargin=*]
+\item Distance between adjacent fibers: 250 $\mu m$
+\item Fiber diameter: 5-50 $\mu m$
+\end{itemize} \\
+
+\hline
+Ref: & \cite{Gupta2007} \\ %Novel Electrohydrodynamic Printing of Nanocomposite Biopolymer Scaffolds
+\arrayrulecolor{black}\hline
 \label{tbl:FloresCompare}
 \end{tabular}
-%\end{center}
+\end{center}
 \end{table}
+%----------------------------------------------------------------------%
 
-%\addtolength{\oddsidemargin}{0.0in}
-%\addtolength{\evensidemargin}{0.0in}
-\addtolength{\topmargin}{0.0in}
+%----------------------------------------------------------------------%
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
 
-\end{landscape}
-\pagebreak[4]\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 0}
+\hline
+Polymer(s): &
+Poly(ethylene oxide) (PEO) \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+Distilled water \\
+
+\hline
+NFES Variant: &
+Electrohydrodynamic Writing or Mechanoelectrospinning (MES) \\
+
+\hline
+Polymer Solution and Process Properties: &
+\begin{itemize}[leftmargin=*]
+\item Polymer solution weight concentration: 6 $w t \%$ PEO
+\item Needle-to-collector distance: 7.5 $m m$
+\item Applied voltage to initiate the jet: 2 $k V$
+\item Applied voltage during deposition: 0.8-1 $k V$
+\item Under the room temperature and relative humidity of about 25\%.
+\item x-y stage velocity: around 400 $m m / s$
+\item Solution flow rate: 1200 $n L / min$
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
+\begin{itemize}[leftmargin=*]
+\item Distance between adjacent fibers: 5 $\mu m$
+\item Fiber diameter: 200-350 $n m$
+\end{itemize} \\
+
+\hline
+Ref: & \cite{Huang2015} \\ %Versatile, kinetically controlled, high precision electrohydrodynamic writing of micro/nanofibers
+\arrayrulecolor{black}\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+\end{center}
+\end{table}
+%----------------------------------------------------------------------%
+
+%----------------------------------------------------------------------%
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
+\hline
+Polymer(s): &
+Poly(ethylene oxide) (PEO) \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+Deionized water and the ethanol with a volume ratio of 3:1 \\
+
+\hline
+NFES Variant: &
+Airflow-assisted Electrohydrodynamic Direct-writing (EDW) \\
+
+\hline
+Polymer Solution and Process Properties: &
+\begin{itemize}[leftmargin=*]
+\item Concentration: 8 $w t \%$ PEO
+\item Outer airflow passage diameter: 1 $m m$
+\item Airflow gas pump pressure: 25 $k Pa$
+\item Inner liquid passage diameter: 0.21 $m m$
+\item Silicon substrate
+\item Needle-to-collector distance: 2 $m m$
+\item Solution flow rate: 30 $\mu L / h$
+\item Applied voltage: about 2 $k V$
+\item x-y stage velocity: between 1-20 $m m / s$
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
+\begin{itemize}[leftmargin=*]
+\item Fiber deposition position accuracy: 5.13 $\pm$ 6.67 $\mu m$
+\item Fiber diameter: 3.73 $\pm$ 1.37 $\mu m$
+\end{itemize} \\
+
+\hline
+Ref: & \cite{Jiang2018} \\ %Electrohydrodynamic Direct-Writing Micropatterns with Assisted Airflow
+\arrayrulecolor{black}\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+\end{center}
+\end{table}
+%----------------------------------------------------------------------%
+
+%\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
+%\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
+%\cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
+%\cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
+%\cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
+%\cite{Gupta2007}   \\ %Novel Electrohydrodynamic Printing of Nanocomposite Biopolymer Scaffolds
+%\cite{Huang2015}   \\ %Versatile, kinetically controlled, high precision electrohydrodynamic writing of micro/nanofibers
+%\cite{Jiang2018}   \\ %Electrohydrodynamic Direct-Writing Micropatterns with Assisted Airflow
+\cite{Kim2018}     \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
+\cite{Lee2012}     \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning
+\cite{Liu2014}     \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
+\cite{Min2013}     \\ %Large-scale organic nanowire lithography and electronics
+\cite{Pan2014}     \\ %Poly($\gamma$-benzyl $\alpha$, l-glutamate) in Cylindrical Near-Field Electrospinning Fabrication and Analysis of Piezoelectric Fibers
+\cite{Pan2015}     \\ %Near-field electrospinning enhances the energy harvesting of hollow PVDF piezoelectric fibers
+\cite{Song2015}    \\ %Patterned polydiacetylene-embedded polystyrene nanofibers based on electrohydrodynamic jet printing
+\cite{Sun2006}     \\ %Near-Field Electrospinning
+\cite{Wang2015}    \\ %Research on Multinozzle Near-Field Electrospinning Patterned Deposition
+\cite{Wang2017}    \\ %Controllable deposition distance of aligned pattern via dual-nozzle near-field electrospinning
+\cite{Wang2018}    \\ %Fabrication and evaluation of controllable deposition distance for aligned pattern by multi-nozzle near-field electrospinning
+\cite{Xu2014}      \\ %Accuracy Improvement of Nano-fiber Deposition by Near-Field Electrospinning
+\cite{Xue2014}     \\ %Rapid Patterning of 1-D Collagenous Topography as an ECM Protein Fibril Platform for Image Cytometry
+\cite{Zheng2010}   \\ %Precision deposition of a nanofibre by near-field electrospinning
+\cite{Zheng2014}   \\ %Electrohydrodynamic Direct-Write Orderly Micro/Nanofibrous Structure on Flexible Insulating Substrate
+\cite{Zheng2012}   \\ %Polymer nanofibers prepared by low-voltage
+
+%-%-%-%-%-%-%-%--------------------------------------------------------%
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
+\hline
+Polymer(s): &
+ \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+ \\
+
+\hline
+NFES Variant: &
+ \\
+
+\hline
+Polymer Solution and Process Properties: &
+\begin{itemize}[leftmargin=*]
+\item 1
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
+\begin{itemize}[leftmargin=*]
+\item a
+\end{itemize} \\
+
+\hline
+Ref: & \cite{Bisht2011} \\
+\arrayrulecolor{black}\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+\end{center}
+\end{table}
+%----------------------------------------------------------------------%
 

### 2019-06-13 NFES_Review/Chapters/_tbl_Collection.tex
min progress

@@
 
+%----------------------------------------------------------------------%
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
+\hline
+Polymer(s): &
+Poly(Vinylidene Fluoride) (PVDF) \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+Acetone and Dimethyl Sulfoxide (DMSO) \\
+
+\hline
+NFES Variant: &
+3D Electrospinning \\
+
+\hline
+Polymer Solution and Process Properties: &
+\begin{itemize}[leftmargin=*]
+\item Capstone FS-66 used as an anionic surfactant.
+\item Solution concentration: 17 $w t \%$ PVDF
+    \begin{itemize}[leftmargin=*]
+    \item 1.7 $g$ of PVDF added to 5 $g$ of acetone and dispersed for 30 $min$
+    \item 0.5 $g$ of Capstone FS-66 was added to 5 $g$ of DMSO and dispersed
+    \item then both solutions are mixed for more than 1 $h$
+    \end{itemize}
+\item Collector substrate: A4 size commercial printing paper (Double A)
+\item Needle inner diameter: 100 $\mu m$
+\item x-y stage velocity: 10 $m m / s$
+\item Solution flow rate: 14 $n L / min$
+\item Needle-to-collector distance: 750 $\mu m$
+\item Applied voltage: 1.9 $k V$
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
+\begin{itemize}[leftmargin=*]
+\item a
+\end{itemize} \\
+
+\hline
+Ref: & \cite{Kim2018} \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
+\arrayrulecolor{black}\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+\end{center}
+\end{table}
+%----------------------------------------------------------------------%
+
 %\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
@@
 %\cite{Jiang2018}   \\ %Electrohydrodynamic Direct-Writing Micropatterns with Assisted Airflow
-\cite{Kim2018}     \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
+%\cite{Kim2018}     \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
 \cite{Lee2012}     \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning

### 2019-06-13 NFES_Review/Chapters/_tbl_Collection.tex
NFES review progress

@@
 \begin{itemize}[leftmargin=*]
+\item A stack of fibers was produced, but fiber diameter is not reported.
+\end{itemize} \\
+
+\hline
+Ref: & \cite{Kim2018} \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
+\arrayrulecolor{black}\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+\end{center}
+\end{table}
+%----------------------------------------------------------------------%
+
+%----------------------------------------------------------------------%
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
+\hline
+Polymer(s): &
+Polycaprolactone \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+Chloroform \\
+
+\hline
+NFES Variant: &
+Direct-Write Electrospinning \\
+
+\hline
+Polymer Solution and Process Properties: &
+\begin{itemize}[leftmargin=*]
+\item Needle inner diameter: 200 $\mu m$
+\item Ground electrode to collector plate distance: 50 $\mu m$
+\item Solution concentration: 8.8 $w t \%$ Polycaprolactone
+\item Solution stirred for 120 $min$
+\item Applied voltage: 25 $k V$
+\item Needle-to-collector distance: 70 $m m$
+\item Solution flow rate: 0.1 $m L / h$
+\item Electrospun at 23 $^\circ C$ and relative humidity between 54 and 57 \%
+\item x-y stage velocity: 2-200 $m m / s$
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
+\begin{itemize}[leftmargin=*]
+\item Fiber diameter: 400 $n m$ to 950 $\mu m$
+\end{itemize} \\
+
+\hline
+Ref: & \cite{Lee2012} \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning
+\arrayrulecolor{black}\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+\end{center}
+\end{table}
+%----------------------------------------------------------------------%
+
+%----------------------------------------------------------------------%
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
+\hline
+Polymer(s): &
+Poly(Vinylidene Fluoride) (PVDF) \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+Dimethyl Sulfoxide (DMSO)
+    \begin{itemize}[leftmargin=*]
+    \item Acetone and surfactant (ZONYL UR) were applied to improve the evaporation rate and to reduce the surface tension.
+    \end{itemize} \\
+
+\hline
+NFES Variant: &
+Hollow Cylindrical Near-Field Electrospinning (HCNFES) \\
+
+\hline
+Polymer Solution and Process Properties: &
+\begin{itemize}[leftmargin=*]
+\item Solution concentration: 16, 18, and 20 $w t \%$ PVDF
+    \begin{itemize}[leftmargin=*]
+    \item DMSO:acetone concentration is 1:1
+    \item Surfactant amount: 0.2 $g$
+    \end{itemize}
+\item Solution preparation:
+    \begin{itemize}[leftmargin=*]
+    \item PVDF-acetone stirred for 30 $min$
+    \item sufractant-DMSO stirred for 30 $min$
+    \item Both solutions stirred for 60 $min$
+    \end{itemize}
+\item Needle-to-collector distance: 0.5 $m m$
+\item Applied voltage: 10-16 $k V$
+\item Tube collector rotational velocity: 900-1900 $rpm$
+    \begin{itemize}[leftmargin=*]
+    \item Tangential speed: 942.3-1989.3 $m m / s$
+    \end{itemize}
+\item Collector substrate: Poly(ethylene terephthalate) (PET)
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
+\begin{itemize}[leftmargin=*]
 \item a
@@
 \hline
-Ref: & \cite{Kim2018} \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
+Ref: & \cite{Liu2014} \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
 \arrayrulecolor{black}\hline
@@
 %\cite{Kim2018}     \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
-\cite{Lee2012}     \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning
-\cite{Liu2014}     \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
+%\cite{Lee2012}     \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning
+%\cite{Liu2014}     \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
 \cite{Min2013}     \\ %Large-scale organic nanowire lithography and electronics

### 2019-06-13 NFES_Review/Chapters/_tbl_Collection.tex
more NFES variants

@@
 \begin{itemize}[leftmargin=*]
-\item Solution concentration: 16, 18, and 20 $w t \%$ PVDF
+\item Solution concentration: 18 $w t \%$ PVDF
     \begin{itemize}[leftmargin=*]
@@
     \item Both solutions stirred for 60 $min$
+    \item Placed in a vacuum chamber for 15 $min$ to remove bubbles
     \end{itemize}
 \item Needle-to-collector distance: 0.5 $m m$
-\item Applied voltage: 10-16 $k V$
-\item Tube collector rotational velocity: 900-1900 $rpm$
+\item Applied voltage: 14 $k V$
+\item Tube collector rotational velocity: 1900 $rpm$
     \begin{itemize}[leftmargin=*]
-    \item Tangential speed: 942.3-1989.3 $m m / s$
+    \item Tangential speed: 1989.3 $m m / s$
     \end{itemize}
 \item Collector substrate: Poly(ethylene terephthalate) (PET)
+\end{itemize} \\
+
+\hline
+Fiber Characterization: &
+\begin{itemize}[leftmargin=*]
+\item Fiber diameter: around 1.2 $\mu m$ 
+\end{itemize} \\
+
+\hline
+Ref: & \cite{Liu2014} \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
+\arrayrulecolor{black}\hline
+\label{tbl:FloresCompare}
+\end{tabular}
+\end{center}
+\end{table}
+%----------------------------------------------------------------------%
+
+%----------------------------------------------------------------------%
+\begin{table}[th]
+\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
+\begin{center}
+% total table width eq 0.91\textheight = 100%
+\begin{tabular}{
+>{\raggedright\arraybackslash}p{0.28\textwidth}
+>{\raggedright\arraybackslash}p{0.72\textwidth} }
+
+\hline
+Polymer(s): &
+ \\
+
+\arrayrulecolor{lightgray}\hline
+Solvent(s): &
+Electrohydrodynamic Organic Nanowire printing (ONP) \\
+
+\hline
+NFES Variant: &
+ \\
+
+\hline
+Polymer Solution and Process Properties: &
+\begin{itemize}[leftmargin=*]
+\item 1
 \end{itemize} \\
@@
 \hline
-Ref: & \cite{Liu2014} \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
+Ref: & \cite{Min2013} \\ %Large-scale organic nanowire lithography and electronics
 \arrayrulecolor{black}\hline
@@
 %\cite{Liu2014}     \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
-\cite{Min2013}     \\ %Large-scale organic nanowire lithography and electronics
+%\cite{Min2013}     \\ %Large-scale organic nanowire lithography and electronics
 \cite{Pan2014}     \\ %Poly($\gamma$-benzyl $\alpha$, l-glutamate) in Cylindrical Near-Field Electrospinning Fabrication and Analysis of Piezoelectric Fibers

### 2019-06-17 NFES_Review/article.tex
new format

%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
\documentclass[3p,,preprint,12pt]{elsarticle}
\makeatletter\if@twocolumn\PassOptionsToPackage{switch}{lineno}\else\fi\makeatother

\usepackage{tabulary,xcolor}
\usepackage{amsfonts,amsmath,amssymb}
\usepackage[T1]{fontenc}
\makeatletter
\let\save@ps@pprintTitle\ps@pprintTitle
\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\itshape \null\hfill\today}}
\def\hlinewd#1{%
  \noalign{\ifnum0=`}\fi\hrule \@height #1%
  \futurelet\reserved@a\@xhline}
\def\tbltoprule{\hlinewd{.8pt}\\[-12pt]}
\def\tblbottomrule{\noalign{\vspace*{6pt}}\hline\noalign{\vspace*{2pt}}}
\def\tblmidrule{\noalign{\vspace*{6pt}}\hline\noalign{\vspace*{2pt}}}
\AtBeginDocument{\ifNAT@numbers \biboptions{sort&compress}\fi}
\makeatother

\usepackage{ifluatex}
\ifluatex
\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
\usepackage[]{unicode-math}
\unimathsetup{math-style=TeX}
\else 
\usepackage[utf8]{inputenc}
\fi 
\ifluatex\else\usepackage{stmaryrd}\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Following additional macros are required to function some 
% functions which are not available in the class used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{url,multirow,morefloats,floatflt,cancel,tfrupee}
\makeatletter

\AtBeginDocument{\@ifpackageloaded{textcomp}{}{\usepackage{textcomp}}}
\makeatother
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage[nointegrals]{wasysym}
\urlstyle{rm}
\makeatletter

%%%For Table column width calculation.
\def\mcWidth#1{\csname TY@F#1\endcsname+\tabcolsep}

%%Hacking center and right align for table
\def\cAlignHack{\rightskip\@flushglue\leftskip\@flushglue\parindent\z@\parfillskip\z@skip}
\def\rAlignHack{\rightskip\z@skip\leftskip\@flushglue \parindent\z@\parfillskip\z@skip}

%Etal definition in references
\@ifundefined{etal}{\def\etal{\textit{et~al}}}{}

%\if@twocolumn\usepackage{dblfloatfix}\fi
\usepackage{ifxetex}
\ifxetex\else\if@twocolumn\@ifpackageloaded{stfloats}{}{\usepackage{dblfloatfix}}\fi\fi

\AtBeginDocument{
\expandafter\ifx\csname eqalign\endcsname\relax
\def\eqalign#1{\null\vcenter{\def\\{\cr}\openup\jot\m@th
  \ialign{\strut$\displaystyle{##}$\hfil&$\displaystyle{{}##}$\hfil
      \crcr#1\crcr}}\,}
\fi
}

%For fixing hardfail when unicode letters appear inside table with endfloat
\AtBeginDocument{%
  \@ifpackageloaded{endfloat}%
   {\renewcommand\efloat@iwrite[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}}{\newif\ifefloat@tables}%
}%

\def\BreakURLText#1{\@tfor\brk@tempa:=#1\do{\brk@tempa\hskip0pt}}
\let\lt=<
\let\gt=>
\def\processVert{\ifmmode|\else\textbar\fi}
\let\processvert\processVert

\@ifundefined{subparagraph}{
\def\subparagraph{\@startsection{paragraph}{5}{2\parindent}{0ex plus 0.1ex minus 0.1ex}%
{0ex}{\normalfont\small\itshape}}%
}{}

% These are now gobbled, so won't appear in the PDF.
\newcommand\role[1]{\unskip}
\newcommand\aucollab[1]{\unskip}

\@ifundefined{tsGraphicsScaleX}{\gdef\tsGraphicsScaleX{1}}{}
\@ifundefined{tsGraphicsScaleY}{\gdef\tsGraphicsScaleY{.9}}{}
% To automatically resize figures to fit inside the text area
\def\checkGraphicsWidth{\ifdim\Gin@nat@width>\linewidth
	\tsGraphicsScaleX\linewidth\else\Gin@nat@width\fi}

\def\checkGraphicsHeight{\ifdim\Gin@nat@height>.9\textheight
	\tsGraphicsScaleY\textheight\else\Gin@nat@height\fi}

\def\fixFloatSize#1{}%\@ifundefined{processdelayedfloats}{\setbox0=\hbox{\includegraphics{#1}}\ifnum\wd0<\columnwidth\relax\renewenvironment{figure*}{\begin{figure}}{\end{figure}}\fi}{}}
\let\ts@includegraphics\includegraphics

\def\inlinegraphic[#1]#2{{\edef\@tempa{#1}\edef\baseline@shift{\ifx\@tempa\@empty0\else#1\fi}\edef\tempZ{\the\numexpr(\numexpr(\baseline@shift*\f@size/100))}\protect\raisebox{\tempZ pt}{\ts@includegraphics{#2}}}}

%\renewcommand{\includegraphics}[1]{\ts@includegraphics[width=\checkGraphicsWidth]{#1}}
\AtBeginDocument{\def\includegraphics{\@ifnextchar[{\ts@includegraphics}{\ts@includegraphics[width=\checkGraphicsWidth,height=\checkGraphicsHeight,keepaspectratio]}}}

\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\def\URL#1#2{\@ifundefined{href}{#2}{\href{#1}{#2}}}

%%For url break
\def\UrlOrds{\do\*\do\-\do\~\do\'\do\"\do\-}%
\g@addto@macro{\UrlBreaks}{\UrlOrds}

\edef\fntEncoding{\f@encoding}
\def\EUoneEnc{EU1}
\makeatother
\def\floatpagefraction{0.8} 
\def\dblfloatpagefraction{0.8}
\def\style#1#2{#2}
\def\xxxguillemotleft{\fontencoding{T1}\selectfont\guillemotleft}
\def\xxxguillemotright{\fontencoding{T1}\selectfont\guillemotright}

\newif\ifmultipleabstract\multipleabstractfalse%
\newenvironment{typesetAbstractGroup}{}{}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emergencystretch 20pt \tolerance = 1500 \def\floatpagefraction{0.8}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Feature enabled:
%toc: yes
%pagenum: yes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeatletter
\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
\makeatother
          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
\usepackage{etoolbox}

\usepackage{longtable}

\makeatletter
\AtBeginDocument{\@ifpackageloaded{rotating}{\PassOptionsToPackage{figuresright}{rotating}}{\usepackage[figuresright]{rotating}}\setlength{\rotFPtop}{0pt plus 1fil}\setlength{\rotFPbot}{0pt plus 1fil}}
\makeatother

\makeatletter
 \AtBeginDocument{%
  \@ifpackagewith{endfloat}{figuresonly}
  {\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}}%true
  {\@ifpackagewith{endfloat}{tablesonly}{\DeclareDelayedFloatFlavor{sidewaystable}{table}\DeclareDelayedFloatFlavor{longtable}{table}\DeclareDelayedFloatFlavor{landscape}{table}}%true
  {\@ifpackageloaded{endfloat}{\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}\DeclareDelayedFloatFlavor{sidewaystable}{table}\DeclareDelayedFloatFlavor{longtable}{table}\DeclareDelayedFloatFlavor{landscape}{table}}{}}%false
  }%false
  }
\makeatother

\usepackage{pdflscape}

\begin{document}

\begin{frontmatter}

\title{Review of Polymer Solutions for Near-Field Electrospinning with Spatial Control
}

\author[]{Antonio Osamu Katagiri Tanaka}
\ead{oskatagiri@gmail.com}
\author[]{H{\'e}ctor Al\'{a}n Aguirre Soto}
\ead{alan.aguirre@tec.mx}

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. 
\end{abstract}
\end{frontmatter}
\tableofcontents

\section{Introduction}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{NFES}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\begin{landscape}
\makeatletter\@twocolumnfalse\makeatother
\begingroup
\makeatletter\if@twocolumn\@ifundefined{theposttbl}{\gdef\TwoColDocument{true}\onecolumn\onecolumn}{}\fi\makeatother \setlength\LTcapwidth{\textheight}
\begin{longtable}{p{\dimexpr.1641\linewidth-2\tabcolsep}p{\dimexpr.13800000000000004\linewidth-2\tabcolsep}p{\dimexpr.1634\linewidth-2\tabcolsep}p{\dimexpr.46839999999999996\linewidth-2\tabcolsep}p{\dimexpr.0661\linewidth-2\tabcolsep}}
\caption{{Electrospun Polymer Solutions - Solution and Process Parameters} }
\label{tw-bab4042dace7}
\def\arraystretch{1}\\\endfirsthead \hline \noalign{\vskip3pt} \noalign{\textit{Table \thetable\ continued}} \noalign{\vskip3pt} \hline \endhead \hline \noalign{\vskip3pt} \noalign{\textit{\hfill Continued on next page}} \noalign{\vskip3pt} \endfoot \endlastfoot 
\tbltoprule Polymer(s) & Solvent(s) & NFES Variant & Process Parameters and Fiber Characterization & Ref.\\
\tblmidrule 
Poly(ethylene oxide) (PEO) &
  Deionized water &
  Low-Voltage NFES &
  \textbf{Solution Concentration:} 1, 2, and 3 $wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 27 gauge type 304; stainless steel needle \mbox{}\protect\newline \textbf{Solution deposition rate:} lower than 1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Pyrolyzed SU-8 carbon and Si \mbox{}\protect\newline \textbf{Applied voltage: }polymer jet initiated at 400-600 $V $ and dispensed at 200-400 $V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10-40$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 50-425$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
  \unskip~\cite{527120:11973130}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) &
  acetonitrile toluene mixture (65/35); acetic acid toluene (17/83); pure toluene &
  \textit{Not determined} &
  \textbf{Solution Concentration:} \mbox{}\protect\newline 10$mg $ of MEH-PPV in 2$mL $ of toluene; 500$mL $ of MEH-PPV solution with 250$mg $ of PEO in 3.5$mL $ of acetonitrile; 500$mL $ of MEH-PPV solution with 250$mg $ of PEO in 3$mL $ of acetic acid / toluene (17 / 83). The resulting MEH-PPV/PEO concentration is 1:100 \mbox{}\protect\newline \textbf{Nozzle:} mm-diameter tip Tungsten spinneret in a 26 gauge needle \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} SiO2/Si (oxide thickness = 800 nm) \mbox{}\protect\newline \textbf{Applied voltage:} around 1.3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 100$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} around 100$\mu m $ &
  \unskip~\cite{527120:11974305}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Poly(ethylene oxide) (PEO) &
  Water &
  Scanning Tip Electrospinning and NFES &
  \textbf{Solution Concentration:} 7$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 200$\mu m $ and inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:}\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 1.5 $kV $ and dispensed at 600$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 120$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 709$\pm $131$nm $; 49-74$nm $ when applied voltage is 800$V $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{ Not determined} \mbox{}\protect\newline \textbf{Notes:} 108$m $ yield in 15$min $ with a fiber diameter of 709$\pm $131$nm $ &
  \unskip~\cite{527120:11974306}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Poly(vinylidine fluorid) (PVDF) &
  N,N Dimethylformamide (DMF) &
  Helix Electrohydro-dynamic Printing (HE-printing) &
  \textbf{Solution Concentration:} 1.8$g $ PVDF in 4.1$g $ of DMF and 4.1$g $ of acetone. The resulting concentration is 18\% PVDF. \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 510$\mu m $ and inner diameter of 260$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 400$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 10-50$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Poly(dimethylsiloxane) (PDMS) on Ecoflex \mbox{}\protect\newline \textbf{Applied voltage:} 1.5{\textendash}3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0-400$mm/min $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 1.5-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
  \unskip~\cite{527120:11974308}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Polyhedral Oligomeric Silsesquioxane-Poly(Carbonate-Urea)Urethane (POSS-PCU) and Polyhedral Oligomeric Silsesquioxane Poly(Caprolactone-Poly(Carbonate-Urea)Urethane) (POSS-PCL-PCU) &
  Dimethyl acetamide (DMAC) and 1-Butanol &
  Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting &
  \textbf{Solution Concentration: }POSS-PCU and POSS-PCL-PCU used in 20\%$w/w $ concentration in DMAC \mbox{}\protect\newline \textbf{Nozzle:} needle of 750 $\mu m $ in diameter \mbox{}\protect\newline \textbf{Solution deposition rate:} less than 1$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: }about between 500$\mu m $ to 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 8.0-10.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5-50$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }250$\mu m $ &
  \unskip~\cite{527120:11974310}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Poly(ethylene oxide) (PEO) &
  Distilled water &
  Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) &
  \textbf{Solution Concentration:} 6$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:}\textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} 1200$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 7.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 2 $kV $ and dispensed at 0.8-1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} around 400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 200-350$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 5$\mu m $ &
  \unskip~\cite{527120:11974311}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Poly(ethylene oxide) (PEO) &
  Deionized water and the ethanol with a volume ratio of 3:1 &
  Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) &
  \textbf{Solution Concentration:} 8$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Outer airflow passage diameter: 1$mm $ Airflow gas pump pressure: 25$kPa $ Inner liquid passage diameter: 0.21$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 30$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Silicon \mbox{}\protect\newline \textbf{Applied voltage:} about 2$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 1-20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 3.73 $\pm $ 1.37$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }5.13 $\pm $ 6.67$\mu m $ &
  \unskip~\cite{527120:11974312}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Poly(Vinylidene Fluoride) (PVDF) &
  Acetone and Dimethyl Sulfoxide (DMSO) &
  3D Electrospinning &
  \textbf{Solution Concentration:} 17$wt\% $ PVDF; 1.7$g $ of PVDF, 5$g $ of acetone, 0.5$g $ of Capstone FS-66, 5$g $ of DMSO \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 14$\;nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 750$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} A4 size commercial printing paper (Double A) \mbox{}\protect\newline \textbf{Applied voltage:} 1.9$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:}\textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
  \unskip~\cite{527120:11974313}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
\tblbottomrule 
\end{longtable}
\endgroup
\makeatletter\@ifundefined{TwoColDocument}{}{\twocolumn}\makeatother 
\end{landscape}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{Polymer Solution and Process Parameters}

\section{Applications}

\section{Fiber Characterization}

\section{Conclusion}

\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}

\bibliographystyle{elsarticle-num}

\bibliography{\jobname}

\end{document}

### 2019-06-17 NFES_Review/article.tex
art progress (table complete?)

@@
   acetonitrile toluene mixture (65/35); acetic acid toluene (17/83); pure toluene &
-  \textit{Not determined} &
+  Typical NFES process &
   \textbf{Solution Concentration:} \mbox{}\protect\newline 10$mg $ of MEH-PPV in 2$mL $ of toluene; 500$mL $ of MEH-PPV solution with 250$mg $ of PEO in 3.5$mL $ of acetonitrile; 500$mL $ of MEH-PPV solution with 250$mg $ of PEO in 3$mL $ of acetic acid / toluene (17 / 83).
@@
   \unskip~\cite{527120:11974313}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
- &
-   &
-   &
-  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
-  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
- &
-   &
-   &
-  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
-  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
- &
-   &
-   &
-  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
-  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
- &
-   &
-   &
-  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
-  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
- &
-   &
-   &
-  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
-  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
- &
-   &
-   &
-  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
-  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(9-Vinyl Carbazole) (PVK) &
+  Styrene &
+  Typical NFES process &
+  \textbf{Solution Concentration:} 3.96$wt\% $ PVK in styrene \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 500$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} around 2.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Si/SiO2 \mbox{}\protect\newline \textbf{Applied voltage:} 3-4$kV $ \mbox{}\protect\newline x-y stage velocity: 13.3$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 289.26 $\pm $ 35.37$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }50$\mu m $ \mbox{}\protect\newline \textbf{Notes:} 15$m $ yield in 2$min $ &
+  \unskip~\cite{527120:11974316}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Polystyrene (PS) &
+  1,2,4-Trichloro benzene &
+  Electrohydro-dynamic (EHD) jet printing &
+  \textbf{Solution Concentration:} 1 to 5$wt\% $ PS \mbox{}\protect\newline \textbf{Nozzle:} Glass nozzle inner diameter of 2$\mu m $ and outer diameter of 2.66$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} Si \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: 20, 30, 40$\mu m $} \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} 500 to 400$V $ in 25$V $ increments \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.01-10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 60-170$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \unskip~\cite{527120:11974320}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(ethylene oxide) (PEO) &
+  \textit{Not determined} &
+  Typical NFES process &
+  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:}\textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} Si \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 25$\mu m $ &
+  \unskip~\cite{527120:11974321}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(ethylene oxide) (PEO) &
+  Distilled water &
+  Multinozzle NFES &
+  \textbf{Solution Concentration:} 5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} four-nozzle and six-nozzle array with needle spacing changes from 1.5$mm $ to 3.5$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 1-3$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:}\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 1.7-2.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.47$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 3-5 $mm $ &
+  \unskip~\cite{527120:11974322}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(ethylene oxide) (PEO) &
+  Distilled water &
+  Multinozzle NFES &
+  \textbf{Solution Concentration:}5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 0.18$mm $ and outer diameter of 0.36$mm $; with needle spacing changes from 2.0$mm $ to 3.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 3.0-4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 2.0-3.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 218-326$\mu m $ &
+  \unskip~\cite{527120:11974323}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(ethylene oxide) (PEO) &
+  Distilled water &
+  Multinozzle NFES &
+  \textbf{Solution Concentration:}5 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 180$\mu m $ and outer diameter of 360$\mu m $; with needle spacing changes of 2.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} chromium-plated glass \mbox{}\protect\newline \textbf{Applied voltage:} 2.5$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 2.3002-2.7224$mm $ &
+  \unskip~\cite{527120:11974324}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(ethylene oxide) (PEO) &
+  \textit{Not determined} &
+  Typical NFES process &
+  \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &
+  \unskip~\cite{527120:11974325}\\
+Gelatin \mbox{}\protect\newline (porcine skin) &
+  Acetic Acid and Ethyl Acetate &
+  Typical NFES process &
+  \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &
+  \unskip~\cite{527120:11974326}\\
+Poly(ethylene oxide) (PEO) &
+  Water/Ethanol (v/v = 60/40) &
+  Typical NFES process &
+  \textbf{Solution Concentration:} PEO concentrations of 16\% adn 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \unskip~\cite{527120:11974327}\\
+Poly(ethylene oxide) (PEO) &
+  Water/Ethanol (v/v = 3/1) &
+  Electrohydro-dynamic Direct-Write (EDW) &
+  \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless needle with inner diameter of 210$\mu m $ and outer diameter of 400$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L/h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(ethylene terephthalate) (PET) \mbox{}\protect\newline \textbf{Applied voltage:} 3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 700$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 15-35$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 70$\mu m $ &
+  \unskip~\cite{527120:11974328}\\
 \tblbottomrule 
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\textbf{Solution Concentration:}
+
+\textbf{Nozzle:}
+
+\textbf{Solution deposition rate:}
+
+\textbf{Nozzle-to-substrate distance:}
+
+\textbf{Substrate composition:}
+
+\textbf{Applied voltage:}
+
+\textbf{x-y stage velocity:}
+
+\textbf{Fiber Diameter:}
+
+\textbf{Distance between adjacent fibers:}
 

### 2019-06-18 NFES_Review/article.tex
table completed

@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Near-field electrospinning (NFES) have demonstrated to be one of the top techniques for the fabrication of nano and micro fibers with accurate spatial control.
+In the attempt to create  NFES has suffered a number of variations
+
+Lorem ipsum dolor sit amet
+
+One-dimensional (1-D) nanostructures have attracted enormous research interest due to their unique physicochemical properties and wide application potential.
+These 1-D nanofibers are being increasingly applied to biomedical fields owing to their high surface area-to-volume ratio, high porosity, and the ease of tuning their structures, functionalities, and properties.
+Many biomedical nanofiber reviews have focused on tissue engineering and drug delivery applications but have very rarely discussed their use as wound dressings.
+However, nanofibers have enormous potential as wound dressings and other clinical applications that could have wide impacts on the treatment of wounds.
+Herein, the authors review the main fabrication methods of nanofibers as well as requirements, strategies, and recent applications of nanofibers, and provide perspectives of the challenges and opportunities that face multifunctional nanofibers for active therapeutic applications.
+
+Near field electrospinning is one of the leading techniques in accurate placement of nanofibers.
+This technique has evolved from using AFM tips to supply a limited volume of solution for electrospinning to nozzle-based system where a continuous stream of solution can be extruded.
+
+The precision and accuracy of the fiber deposition has also vastly improved from simple formation of oriented fibers on a collector to precise deposition of the fiber at a specific point.
+Despite the progress, several intrinsic limitation or characteristic of near-field electrospinning still needs to be noted when employing this technique.
 \end{abstract}
+\begin{keyword} 
+      polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
+\end{keyword}
+
 \end{frontmatter}
@@
 \makeatletter\if@twocolumn\@ifundefined{theposttbl}{\gdef\TwoColDocument{true}\onecolumn\onecolumn}{}\fi\makeatother \setlength\LTcapwidth{\textheight}
-\begin{longtable}{p{\dimexpr.1641\linewidth-2\tabcolsep}p{\dimexpr.13800000000000004\linewidth-2\tabcolsep}p{\dimexpr.1634\linewidth-2\tabcolsep}p{\dimexpr.46839999999999996\linewidth-2\tabcolsep}p{\dimexpr.0661\linewidth-2\tabcolsep}}
+\begin{longtable}{p{\dimexpr.1641\linewidth-2\tabcolsep}p{\dimexpr.13520000000000005\linewidth-2\tabcolsep}p{\dimexpr.1662\linewidth-2\tabcolsep}p{\dimexpr.46839999999999996\linewidth-2\tabcolsep}p{\dimexpr.0661\linewidth-2\tabcolsep}}
 \caption{{Electrospun Polymer Solutions - Solution and Process Parameters} }
@@
   \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &
-  \unskip~\cite{527120:11974325}\\
+  \unskip~\cite{527120:11974325}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Gelatin \mbox{}\protect\newline (porcine skin) &
@@
   \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &
-  \unskip~\cite{527120:11974326}\\
+  \unskip~\cite{527120:11974326}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO) &
@@
   \textbf{Solution Concentration:} PEO concentrations of 16\% adn 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974327}\\
+  \unskip~\cite{527120:11974327}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO) &
@@
   \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless needle with inner diameter of 210$\mu m $ and outer diameter of 400$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L/h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(ethylene terephthalate) (PET) \mbox{}\protect\newline \textbf{Applied voltage:} 3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 700$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 15-35$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 70$\mu m $ &
-  \unskip~\cite{527120:11974328}\\
+  \unskip~\cite{527120:11974328}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(ethylene oxide) (PEO) &
+  Deionized water &
+  Mechano-Electrospinning &
+  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless steel nozzle with inner diameter of 160$\mu m $ and outer diameter of 310$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2-5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicone \mbox{}\protect\newline \textbf{Applied voltage:}polymer jet initiated at 2$kV $ and dispensed at 1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 200-400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} from 344$\pm $32 to 214$\pm $27$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \unskip~\cite{527120:11974304}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(co-Glycolic) acid (PLGA)  &
+  Dimethyl Carbonate (DMC) &
+  Tethered Pyro-Electrohydro-dynamic Spinning (TPES) &
+  \textbf{Solution Concentration:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle:} nozzle-free \mbox{}\protect\newline \textbf{Solution deposition rate:} The drop reservoir is placed directly on a flat substrate \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} Taylor's cone is focused and put in direct contact with the collector \mbox{}\protect\newline \textbf{Substrate composition:} Poly(tetrafluoroethylene) (PTFE) coated glass slide \mbox{}\protect\newline \textbf{Applied voltage:} pyro-electric field of between 2.7 $x10^{7}\;V/m $ and 5.5$x10^{7}\;V/m $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 304.7$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \unskip~\cite{527120:11974307}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(ethylene oxide) (PEO) with Tetrabutylammonium tetrafluoroborate (TBF) and SU-8 2002 &
+  N,N Dimethylformamide (DMF) &
+  Typical NFES process &
+  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline \textbf{Nozzle:} needle inner diameter of 533$\mu m $ and outer diameter of 710$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:}\textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:}\textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \unskip~\cite{527120:12033655}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(ethylene oxide) (PEO) &
+  Water:Ethanol (3:2) &
+  Suspension NFES &
+  \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} stainless steel needle (25 G) with inner diameter of 0.25$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 3$nL/s $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} between 0.5 and 10$mm $ with 0.5$mm $ increments \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon electrodes \mbox{}\protect\newline \textbf{Applied voltage:} 1.6$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50, 150, and 250$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 0.1 and 0.5$mm $ &
+  \unskip~\cite{527120:12033656}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+Poly(ethylene oxide) (PEO) &
+  Deionized water &
+   &
+  \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &
+  \unskip~\cite{527120:12033657}\\
 \tblbottomrule 
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\textbf{Solution Concentration:}
-
-\textbf{Nozzle:}
-
-\textbf{Solution deposition rate:}
-
-\textbf{Nozzle-to-substrate distance:}
-
-\textbf{Substrate composition:}
-
-\textbf{Applied voltage:}
-
-\textbf{x-y stage velocity:}
-
-\textbf{Fiber Diameter:}
-
-\textbf{Distance between adjacent fibers:}
 

### 2019-06-18 NFES_Review/article.tex
new intro

@@
 \begin{abstract}
-Near-field electrospinning (NFES) have demonstrated to be one of the top techniques for the fabrication of nano and micro fibers with accurate spatial control.
-In the attempt to create  NFES has suffered a number of variations
-
-Lorem ipsum dolor sit amet
-
-One-dimensional (1-D) nanostructures have attracted enormous research interest due to their unique physicochemical properties and wide application potential.
-These 1-D nanofibers are being increasingly applied to biomedical fields owing to their high surface area-to-volume ratio, high porosity, and the ease of tuning their structures, functionalities, and properties.
-Many biomedical nanofiber reviews have focused on tissue engineering and drug delivery applications but have very rarely discussed their use as wound dressings.
-However, nanofibers have enormous potential as wound dressings and other clinical applications that could have wide impacts on the treatment of wounds.
-Herein, the authors review the main fabrication methods of nanofibers as well as requirements, strategies, and recent applications of nanofibers, and provide perspectives of the challenges and opportunities that face multifunctional nanofibers for active therapeutic applications.
-
-Near field electrospinning is one of the leading techniques in accurate placement of nanofibers.
-This technique has evolved from using AFM tips to supply a limited volume of solution for electrospinning to nozzle-based system where a continuous stream of solution can be extruded.
-
-The precision and accuracy of the fiber deposition has also vastly improved from simple formation of oriented fibers on a collector to precise deposition of the fiber at a specific point.
-Despite the progress, several intrinsic limitation or characteristic of near-field electrospinning still needs to be noted when employing this technique.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 \end{abstract}
@@
 \section{Introduction}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Diverse polymer patterning techniques have been developed for the fabrication of nano-fibers, such as arc discharge [31], chemical vapor deposition, laser ablation [21], and vapor growth [18].
+Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required.
+The electrospinning method (invented by Formhals Anton in 1934)can produce fibers with a range of diameters between 10 nm and 10 mm [12,2] from a polymer solution under the influence of an electrostatic force.
+The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry [1, 14, 4, 26].
+
+Even though electrospinning is an old invention [2], it is currently a trending topic among researchers [11, 22, 23].
+One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers.
+The technique allows the production of thin continuous fibers with ease, with diameters down to 3 nm in some cases, which is something difficult to achieve by other techniques.
+Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials.
+The produced fibers can be aligned or unaligned.
+Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques.
+On the other hand, the understanding of the electrospinning process has improved in the last years [15].
+As Reneker and Yarin state: "Electrospinning has rapidly changed fiber making from a capital intensive, large scale process to a low cost, broadly applicable method that manufactures fibers on a laboratory bench, to serve diverse needs ranging from materials science and technology to life sciences and clinical medicine.`` [22]
+
+The main components of the electrospinning technique are the fluid control unit (e.g.
+syringe pump) and a DC power supply.
+The process also requires a target electrode or combination of electrodes on which the fibers can be collected.
+Figure 6.2 describes a typical electrospinning set-up.
+[15] Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
+The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning.
+[7] Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning.
+[19] The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher precision when patterning.
+Figure 6.3 shows a typical near field mechano-electrospinning apparatus.
 
@@
   Typical NFES process &
-  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline \textbf{Nozzle:} needle inner diameter of 533$\mu m $ and outer diameter of 710$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:}\textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:}\textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline $\mu m $$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:}\textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:}\textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
   \unskip~\cite{527120:12033655}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}

### 2019-06-20 NFES_Review/article.tex
update

@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement.
+In the past years (2006-2019), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process.
+Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties.
+This paper presents a review on the research and related development of electrospun fibers, emphasizing the used polymers, solvents, and fiber characteristics.
+Relevant summary of polymer solutions and near-field electrospinning processing conditions is provided in this paper.
 \end{abstract}
@@
 \section{Introduction}
-Diverse polymer patterning techniques have been developed for the fabrication of nano-fibers, such as arc discharge [31], chemical vapor deposition, laser ablation [21], and vapor growth [18].
-Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required.
-The electrospinning method (invented by Formhals Anton in 1934)can produce fibers with a range of diameters between 10 nm and 10 mm [12,2] from a polymer solution under the influence of an electrostatic force.
-The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry [1, 14, 4, 26].
-
-Even though electrospinning is an old invention [2], it is currently a trending topic among researchers [11, 22, 23].
+Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}.
 One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers.
@@
 Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques.
-On the other hand, the understanding of the electrospinning process has improved in the last years [15].
-As Reneker and Yarin state: "Electrospinning has rapidly changed fiber making from a capital intensive, large scale process to a low cost, broadly applicable method that manufactures fibers on a laboratory bench, to serve diverse needs ranging from materials science and technology to life sciences and clinical medicine.`` [22]
+On the other hand, the understanding of the electrospinning process has improved in the last years \unskip~\cite{527120:12073538}.
 
 The main components of the electrospinning technique are the fluid control unit (e.g.
-syringe pump) and a DC power supply.
+syringe pump) and a voltage power supply.
 The process also requires a target electrode or combination of electrodes on which the fibers can be collected.
-Figure 6.2 describes a typical electrospinning set-up.
-[15] Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
-The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning.
-[7] Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning.
-[19] The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher precision when patterning.
-Figure 6.3 shows a typical near field mechano-electrospinning apparatus.
+Figure 6.2 describes a typical electrospinning set-up \unskip~\cite{527120:12073538}.
+Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
+The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}.
+Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.
+Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control.
+NFES has suffered several modifications to improve the precision and accuracy of the fiber deposition.
 
 \section{NFES}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\unskip~\cite{527120:11973130}
+
+\unskip~\cite{527120:11974314}
+
+\unskip~\cite{527120:11974329}
+
+\unskip~\cite{527120:11974305}
+
+\unskip~\cite{527120:11974306}
+
+\unskip~\cite{527120:11974308}
+
+\unskip~\cite{527120:11974310}
+
+\unskip~\cite{527120:11974311}
+
+\unskip~\cite{527120:11974312}
+
+\unskip~\cite{527120:11974313}
+
+\unskip~\cite{527120:11974316}
+
+\unskip~\cite{527120:11974320}
+
+\unskip~\cite{527120:11974321}
+
+\unskip~\cite{527120:11974322}
+
+\unskip~\cite{527120:11974323}
+
+\unskip~\cite{527120:11974324}
+
+\unskip~\cite{527120:11974325}
+
+\unskip~\cite{527120:11974326}
+
+\unskip~\cite{527120:11974327}
+
+\unskip~\cite{527120:11974328}
+
+\unskip~\cite{527120:11974304}
+
+\unskip~\cite{527120:11974307}
+
+\unskip~\cite{527120:12033655}
+
+\unskip~\cite{527120:12033656}
+
+\unskip~\cite{527120:12033657}
+
+\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
 
@@
   Scanning Tip Electrospinning and NFES &
-  \textbf{Solution Concentration:} 7$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 200$\mu m $ and inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:}\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 1.5 $kV $ and dispensed at 600$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 120$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 709$\pm $131$nm $; 49-74$nm $ when applied voltage is 800$V $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{ Not determined} \mbox{}\protect\newline \textbf{Notes:} 108$m $ yield in 15$min $ with a fiber diameter of 709$\pm $131$nm $ &
+  \textbf{Solution Concentration:} 7$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 200$\mu m $ and inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 1.5 $kV $ and dispensed at 600$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 120$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 709$\pm $131$nm $; 49-74$nm $ when applied voltage is 800$V $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{ Not determined} \mbox{}\protect\newline \textbf{Notes:} 108$m $ yield in 15$min $ with a fiber diameter of 709$\pm $131$nm $ &
   \unskip~\cite{527120:11974306}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
@@
   Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) &
-  \textbf{Solution Concentration:} 6$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:}\textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} 1200$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 7.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 2 $kV $ and dispensed at 0.8-1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} around 400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 200-350$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 5$\mu m $ &
+  \textbf{Solution Concentration:} 6$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} 1200$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 7.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 2 $kV $ and dispensed at 0.8-1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} around 400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 200-350$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 5$\mu m $ &
   \unskip~\cite{527120:11974311}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
@@
   3D Electrospinning &
-  \textbf{Solution Concentration:} 17$wt\% $ PVDF; 1.7$g $ of PVDF, 5$g $ of acetone, 0.5$g $ of Capstone FS-66, 5$g $ of DMSO \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 14$\;nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 750$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} A4 size commercial printing paper (Double A) \mbox{}\protect\newline \textbf{Applied voltage:} 1.9$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:}\textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \textbf{Solution Concentration:} 17$wt\% $ PVDF; 1.7$g $ of PVDF, 5$g $ of acetone, 0.5$g $ of Capstone FS-66, 5$g $ of DMSO \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 14$\;nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 750$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} A4 size commercial printing paper (Double A) \mbox{}\protect\newline \textbf{Applied voltage:} 1.9$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
   \unskip~\cite{527120:11974313}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
@@
   Typical NFES process &
-  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:}\textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} Si \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 25$\mu m $ &
+  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} Si \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 25$\mu m $ &
   \unskip~\cite{527120:11974321}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
@@
   Multinozzle NFES &
-  \textbf{Solution Concentration:} 5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} four-nozzle and six-nozzle array with needle spacing changes from 1.5$mm $ to 3.5$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 1-3$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:}\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 1.7-2.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.47$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 3-5 $mm $ &
+  \textbf{Solution Concentration:} 5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} four-nozzle and six-nozzle array with needle spacing changes from 1.5$mm $ to 3.5$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 1-3$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 1.7-2.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.47$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 3-5 $mm $ &
   \unskip~\cite{527120:11974322}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
@@
   Multinozzle NFES &
-  \textbf{Solution Concentration:}5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 0.18$mm $ and outer diameter of 0.36$mm $; with needle spacing changes from 2.0$mm $ to 3.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 3.0-4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 2.0-3.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 218-326$\mu m $ &
+  \textbf{Solution Concentration:}5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 0.18$mm $ and outer diameter of 0.36$mm $; with needle spacing changes from 2.0$mm $ to 3.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 3.0-4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition: } \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 2.0-3.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 218-326$\mu m $ &
   \unskip~\cite{527120:11974323}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
@@
   Typical NFES process &
-  \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &
+  \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &
   \unskip~\cite{527120:11974325}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
@@
   Typical NFES process &
-  \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &
+  \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &
   \unskip~\cite{527120:11974326}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
@@
   Tethered Pyro-Electrohydro-dynamic Spinning (TPES) &
-  \textbf{Solution Concentration:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle:} nozzle-free \mbox{}\protect\newline \textbf{Solution deposition rate:} The drop reservoir is placed directly on a flat substrate \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} Taylor's cone is focused and put in direct contact with the collector \mbox{}\protect\newline \textbf{Substrate composition:} Poly(tetrafluoroethylene) (PTFE) coated glass slide \mbox{}\protect\newline \textbf{Applied voltage:} pyro-electric field of between 2.7 $x10^{7}\;V/m $ and 5.5$x10^{7}\;V/m $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 304.7$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \textbf{Solution Concentration:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle:} nozzle-free \mbox{}\protect\newline \textbf{Solution deposition rate:} The drop reservoir is placed directly on a flat substrate \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} Taylor's cone is focused and put in direct contact with the collector \mbox{}\protect\newline \textbf{Substrate composition:} Poly(tetrafluoroethylene) (PTFE) coated glass slide \mbox{}\protect\newline \textbf{Applied voltage:} pyro-electric field of between 2.7 $x10^{7}\;V/m $ and 5.5$x10^{7}\;V/m $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 304.7$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
   \unskip~\cite{527120:11974307}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
@@
   Typical NFES process &
-  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline $\mu m $$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:}\textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:}\textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline $\mu m $$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} \textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
   \unskip~\cite{527120:12033655}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}

### 2019-06-20 NFES_Review/article.tex
article in progress

@@
 
+\usepackage{float}
+
 \makeatletter
@@
 The process also requires a target electrode or combination of electrodes on which the fibers can be collected.
-Figure 6.2 describes a typical electrospinning set-up \unskip~\cite{527120:12073538}.
-Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
+Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
+Two sub-techniques can be derived from electrospinning depending on the distance between the dispensin g electrode and the collector.
 The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}.
 Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.
-Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control.
-NFES has suffered several modifications to improve the precision and accuracy of the fiber deposition.
+Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
+This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
 
-\section{NFES}
+\bgroup
+\fixFloatSize{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}{\includegraphics{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}}{}
+\makeatother 
+\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130} .}}
+\label{f-fe28447572e9}
+\end{figure*}
+\egroup
+
+\section{NFES articles' summary}
+The key advance that allows for lowering of the voltage and attendant increase in patterning control ofNFES is the use of a superelastic polymer ink.
+Solutions of such a polymer ink contain long entangled polymer chains that promote stretchability and are expected to augment continuity of the electrospun jets.
+This facilitates the continuous electrospinning of the polymer jet into nanofiber.
+
+The polymer jet does not self-initiate under the influence of the voltage because the electrostatic force cannot overcome the surface tension at the droplet - air interface.
+Therefore, the electrospinning process was initiated by introducing an artificial instability at the droplet - air interface with a glass microprobe tip (1 to 3 \ensuremath{\mu }m tip diameter) that resulted in a very high local electric field, sufficient to overcome the interfacial surface tension, giving rise to the formation of the Taylor cone and initiation of the polymer jet.
+
+Therefore, we believe that 2 wt \% PEO solution has the proper balance of viscosity, conductivity, and resistance to hardening that allows for low-voltage continuous electrospinning.
+
+At 300 Vand lower, the perturbation phenomenon was eliminated and straight deposition patterns were obtained (as seen in Figure 4c,d).
+This could be achieved with slow stage speeds (20-40 mm/s) clearly demonstrating that the low-voltage NFES technique substantially reduces bending instabilities
+
+Another advantage oflower voltage operation lies in reduction of the diameter of the jet, leading to thinner nanofibers.
+This is most likely due to the lower electrostatic forces at play that reduce the feed rate of the polymer, thus reducing jet thickness.
+Therefore, the voltage can be manipulated to directly control the thickness of the nanofibers
+
+Further investigation into the effect of voltage on the thickness \mbox{}\protect\newline of nanofibers reveals an increasing linear trend of average diameter versus voltage as shown in Figure 6.
+This trend is opposite to that observed in far-field electrospinning
+
+We further demonstrate the ability to integrate low-voltage \mbox{}\protect\newline NFES ``writing'' capability with 3D substrates by suspending nanofibers on carbon micropost arrays on a Si substrate.
+In a typical example, we use posts of a height of40 \ensuremath{\mu }m, a diameter of 30 \ensuremath{\mu }m, an interpostal distance of 100 \ensuremath{\mu }m.
 \unskip~\cite{527120:11973130}
@@
 \tblmidrule 
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO MW = 4 000 000) &
   Deionized water &
-  Low-Voltage NFES &
+  Low-Voltage NFES (LV NFES) &
   \textbf{Solution Concentration:} 1, 2, and 3 $wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 27 gauge type 304; stainless steel needle \mbox{}\protect\newline \textbf{Solution deposition rate:} lower than 1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Pyrolyzed SU-8 carbon and Si \mbox{}\protect\newline \textbf{Applied voltage: }polymer jet initiated at 400-600 $V $ and dispensed at 200-400 $V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10-40$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 50-425$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
@@
   Deionized water &
-   &
+  Typical NFES process &
   \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &

### 2019-06-24 NFES_Review/article.tex
article progress

--- 2019-06-20 NFES_Review/article.tex
@@
 % Feature enabled:
-%toc: yes
 %pagenum: yes
@@
 \makeatother
-          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
-\usepackage{etoolbox}
 
 \usepackage{longtable}
+
+\usepackage{float}
 
@@
 \end{frontmatter}
-\tableofcontents
 
@@
 The process also requires a target electrode or combination of electrodes on which the fibers can be collected.
-Figure 6.2 describes a typical electrospinning set-up \unskip~\cite{527120:12073538}.
+Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
 Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
@@
 Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.
-Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control.
-NFES has suffered several modifications to improve the precision and accuracy of the fiber deposition.
+Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
+This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
 
-\section{NFES}
-\unskip~\cite{527120:11973130}
+\bgroup
+\fixFloatSize{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}{\includegraphics{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}}{}
+\makeatother 
+\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130} .}}
+\label{f-fe28447572e9}
+\end{figure*}
+\egroup
 
-\unskip~\cite{527120:11974314}
+\section{Polymer Solution and NFES Parameters}
+To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
+Kameoka et al (2003) demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip.
+Near-field electrospinning, has exhibited to be capable fabricate nano fibers over and nano fiber patterns (Sun et al 2006).
+Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner.
+Using a spinneret with a reservoir (e.g.
+syringe) of solution generally produces fibers with diameter of a few micrometers [Gupta et al 2007; Xue et al 2014] since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through.
+Coppola et al (2014) have showned a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop,  averting the issue of nozzle clogging.
+The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al's (2014) work.
+The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al (2008) used a 100 \textmu m inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al (2013) used a \textmu m-diameter tip Tungsten spinneret in a 26 gauge needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
 
-\unskip~\cite{527120:11974329}
+\subsection{Applied Voltage}Further development in the near field electrospinning spinning process have attempted to improve fiber deposition precision and reducing fiber diameter.
+Camillo et al (2013) was able to fabricate 100 nm diameter fiber at an applied voltage of 1.5 kV and a tip to collector distance of 500 \textmu m using a modified fine tip spinneret.
+Separate reports by Chang et al (2008) and Bisht et al (2011) have shown that higher voltage leads to a significant increase in the fiber diameter (in the micrometer range) and loss of jet stability.
+The remedy is to significantly reduce the voltage used in the electrospinning process to about 200 to 600 V with tip to collector distance at about 0.5 to 1 mm.
+However, the charges on the solution drop at the tip of the needle were insufficient to break free from the surface tension to initiate electrospinning without assistance.
+Chang et al (2008) used a tungsten probe tip and Bisht et al (2011) used a glass microprobe tip (1 to 3 \textmu m tip diameter) to mechanically draw the solution at the tip of the needle to initiate electrospinning.
+In the study by Chang et al (2008), reduction of electrospinning voltage from 1.5 kV (at tip to collector distance of 500 \textmu m) to 600 V reduces the fiber diameter from 3 \textmu m to 50 nm.
+Using a lower voltage of 200 V with tip to collector distance of 1 mm, Bisht et al (2011) was able to pattern nanofibers (polyethylene oxide) with diameter below 20 nm.
+Similar to electrospinning with longer tip to collector distance, it is likely that there is an optimum voltage which the fiber diameter obtained will be at its finest.
+Voltage higher or lower than this value will see an increase in the fiber diameter.
+Song et al (2015) showed that when the voltage for electrospinning polystyrene was increased from 400 to 500V, at a tip to collector distance of 20 \textmu m, the fiber diameter reduced from close to 160 nm to about 60 nm.
+Such fiber diameter response to voltage is due to a balance of stretching of the jet and the speed at which it hit the collector.
+While increasing voltage causes greater stretching which reduces the fiber diameter, this also causes greater jet acceleration where the stretching terminates when the jet hit the collector.
 
-\unskip~\cite{527120:11974305}
+To use a low working voltage in near field electrospinning while eliminating the need to use a physical object to initiate electrospinning, an alternative is to use a higher voltage for initiation of electrospinning and switch to a lower voltage once the jet has erupted from the nozzle.
+Huang et al (2014) used this concept with a movable stage collector to produce ordered patterns with interfiber pitch of 50 \textmu m.
+By controlling the height between the nozzle tip and the collector stage and the speed of stage, fibers with different orientation and cross-sectional shape can be obtained.
+Generally, closer distance between nozzle tip and collector (ranging from 0.5 mm to 2 mm) results in flat fibers due to impaction of the electrospinning jet.
+A limitation of the setup is that the landing point at electrospinning jet initiation cannot be determined although subsequent adjustment can be made after the jet has landed or the structure can be built up based on the displacement relative to the landing point.
+To control the landing point of the electrospinning jet, a target point may be set.
 
-\unskip~\cite{527120:11974306}
+Low voltage, near field electrospinning has shown characteristics that differ from conventional near field electrospinning using higher voltage.
+Fiber diameter has already been shown to be smaller using this technique.
+With low voltage, near field electrospinning, the fiber diameter was found to be sensitive to the collector stage movement due to mechanical stretching; low velocity giving rise to larger fiber diameter and vice versa [Bisht et al 2011].
+Instead of very fine spinneret tip, Bisht et al (2011) showed that it is possible to spin fibers with diameter less than 100 nm using a 27 gauge needle (approx.
+200 \textmu m inner diameter).
 
-\unskip~\cite{527120:11974308}
+\subsubsection{Electric field}Electrospinning jet can be very sensitive to variation in electric field.
+Thus a target with electric field profile that attracts the jet may be used to guide the electrospinning jet towards the desired landing point.
+Bisht et al (2011) demonstrated the precision and accuracy of low voltage, near field electrospinning by suspending fiber across carbon post with diameter of 30 \textmu m and interpostal distance of 100 \textmu m.
+Min et al (2013) used near field electrospinning to deposit semiconducting poly(3-hexylthiophene) (P3HT):PEO-blend organic nanowire over multiple field-effect transistors on a flexible polyarylate substrate at a speed of 13.3 cm/s with regular spacing of 50 \textmu m and fiber diameter of 289 nm.
+They have also demonstrated the ability to spin highly aligned nanowires from other materials such as poly(9-vinyl carbazole) (PVK) and poly\{[N,N'-bis(2-octyldodecyl)-naphthalene-1,4,5,8-bis(dicarboximide)-2,6-diyl]-alt-5,5'-(2,2'-bithiophene)\}.
 
-\unskip~\cite{527120:11974310}
+The combination of near-field electrospinning and a guiding electrode has the potential to obtain precise and accurate fiber deposition.
+Xu et al (2014) used a guiding electrode behind the collector to create a direct line from the nozzle tip to it.
+This significantly dampens the deviation of the electrospinning jet from its original path as a result of electrostatic repulsion from the preceding deposited nano fiber.
+Without the guiding electrode, the near-field electrospun fibers have a spread of 74 \textmu m.
+With the guiding electrode, the spread was reduced to just 7 \textmu m.
+This raises the possibility of building up 3D structures using electrospinning.
+Kim et al (2018) used inkjet printing with conductive Ag nanoparticles loaded ink to form patterns on a paper as a target for near field electrospun fibers.
+The conductive printed pattern served as a guiding electrode for the electrospinning jet.
+Poly(vinylidene fluoride) (PVDF) solution was electrospun from a height of 750 \textmu m and a 150 \textmu m offset from the edge of the pattern.
+The sensitivity of the electrospinning jet towards the electric field can be seen as the fibers are stacked on the edge of the conductive pattern where the relative electric field was much higher at the edge than at its center.
+When the pattern lines formed acute angle, right-angle or obtuse angle, the accuracy of the deposited fibers are influenced by slight changes in the relative electric field.
+From acute angle to right-angle, the electric field singularity increases from the edge to the intersection between the lines.
+In this case, the fibers were stacked directly on the edge of the line and to the middle of the intersection.
+For lines forming obtuse angle, the deposited fibers followed the edge of the lines by veered off the line at the intersection.
 
-\unskip~\cite{527120:11974311}
+\subsection{Substrate}In near field electrospinning, one of the risks is electrical shorting due to the proximity of the charged needle tip to the grounded collector.
+Any electrical shorting will disrupt the electrospinning process and result in discontinuous fiber.
+While using a lower voltage may reduce this risk, an alternative is to use a less conductive collector.
+Liu et al (2014) used a rotating glass tube with a copper foil lining at the inner surface of the tube for the collection of electrospun oriented polyvinylidene fluoride (PVDF) fiber.
+While initial fiber alignment was excellent, the alignment starts to deteriorate after prolonged fiber deposition which can be attributed to the presence of residual charges.
 
-\unskip~\cite{527120:11974312}
+The influence of residual charges on the precision of fiber deposited is more pronounced when an insulating surface and a conductive surface were used as collectors.
+Choi et al (2017) used a hydrophobic and insulating acrylic substrate as collector.
+To increase conductivity of selected region of the collector, plasma treatment was carried out to render those region hydrophilic.
+The collector was placed in a high humidity environment such that the hydrophilic region will be slightly conductive due to the presence of water molecule attached to it.
+Near field electrospinning of polyurethane showed that on the insulating hydrophobic surface, the fibers were twisted and curved due to weak electric field profile between the emitter and the collector surface and the inability of charges to escape.
+In contrast, on the hydrophilic region, the fiber were placed in accordance to the movement of the emitter relative to the collector.
+This shows that electrical charges on the electrospinning jet needs to escape for precise deposition and even an insulating substrate with slight conductivity is crucial for ordered fiber arrangement.
 
-\unskip~\cite{527120:11974313}
+\subsection{Polymer Solution}In electrospinning, it is generally agreed that with higher concentration, the diameter of the fibers increased due to greater viscosity which resist stretching.
+In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased [Chang et al 2008; Zheng et al 2012].
+However, in separate studies by Pan et al (2014) using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and Pan et al (2015) using polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
+Pan et al (2015) attributed this to a higher charge accumulation in higher concentration PVDF solution.
+However, more studies need to be carried out to verify this.
 
-\unskip~\cite{527120:11974316}
+\section{NFES Variants}
+Low-Voltage NFES (LV NFES) \unskip~\cite{527120:11973130}
 
-\unskip~\cite{527120:11974320}
+Scanning Tip Electrospinning \unskip~\cite{527120:11974306}
 
-\unskip~\cite{527120:11974321}
+3D Electrospinning \unskip~\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\cite{527120:11974310}
 
-\unskip~\cite{527120:11974322}
+Multinozzle NFES \unskip~\cite{527120:11974322,527120:11974323,527120:11974324}
 
-\unskip~\cite{527120:11974323}
+Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\cite{527120:11974304}
 
-\unskip~\cite{527120:11974324}
+Suspension NFES \unskip~\cite{527120:12033656}
 
-\unskip~\cite{527120:11974325}
+Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\cite{527120:11974320}
 
-\unskip~\cite{527120:11974326}
+Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\cite{527120:11974312}
 
-\unskip~\cite{527120:11974327}
-
-\unskip~\cite{527120:11974328}
-
-\unskip~\cite{527120:11974304}
-
-\unskip~\cite{527120:11974307}
-
-\unskip~\cite{527120:12033655}
-
-\unskip~\cite{527120:12033656}
-
-\unskip~\cite{527120:12033657}
-
-\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
+Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\cite{527120:11974307}
 
@@
 \tblmidrule 
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 4,000,000) &
   Deionized water &
-  Low-Voltage NFES &
+  Low-Voltage NFES (LV NFES) &
   \textbf{Solution Concentration:} 1, 2, and 3 $wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 27 gauge type 304; stainless steel needle \mbox{}\protect\newline \textbf{Solution deposition rate:} lower than 1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Pyrolyzed SU-8 carbon and Si \mbox{}\protect\newline \textbf{Applied voltage: }polymer jet initiated at 400-600 $V $ and dispensed at 200-400 $V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10-40$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 50-425$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
   \unskip~\cite{527120:11973130}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) &
+Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000) with Poly(ethylene oxide) (PEO; MW = 300,000) &
   acetonitrile toluene mixture (65/35); acetic acid toluene (17/83); pure toluene &
@@
 \end{landscape}
+
+\section{Conclusion}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\section{Polymer Solution and Process Parameters}
-
-\section{Applications}
-
-\section{Fiber Characterization}
-
-\section{Conclusion}
-
-\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}
 

### 2019-06-24 NFES_Review/article.tex
article new structure

@@
 
-\section{Polymer Solution and NFES Parameters}
+\section{Polymer Solution}
+In electrospinning, it is generally agreed that with higher concentration, the diameter of the fibers increased due to greater viscosity which resist stretching.
+In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased [Chang et al 2008; Zheng et al 2012].
+However, in separate studies by Pan et al (2014) using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and Pan et al (2015) using polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
+Pan et al (2015) attributed this to a higher charge accumulation in higher concentration PVDF solution.
+However, more studies need to be carried out to verify this.
+
+\subsection{Polymers}
+
+\subsection{Solvents}
+
+\section{NFES Parameters}
 To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
@@
 This shows that electrical charges on the electrospinning jet needs to escape for precise deposition and even an insulating substrate with slight conductivity is crucial for ordered fiber arrangement.
-
-\subsection{Polymer Solution}In electrospinning, it is generally agreed that with higher concentration, the diameter of the fibers increased due to greater viscosity which resist stretching.
-In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased [Chang et al 2008; Zheng et al 2012].
-However, in separate studies by Pan et al (2014) using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and Pan et al (2015) using polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
-Pan et al (2015) attributed this to a higher charge accumulation in higher concentration PVDF solution.
-However, more studies need to be carried out to verify this.
-
-\section{NFES Variants}
-Low-Voltage NFES (LV NFES) \unskip~\cite{527120:11973130}
-
-Scanning Tip Electrospinning \unskip~\cite{527120:11974306}
-
-3D Electrospinning \unskip~\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\cite{527120:11974310}
-
-Multinozzle NFES \unskip~\cite{527120:11974322,527120:11974323,527120:11974324}
-
-Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\cite{527120:11974304}
-
-Suspension NFES \unskip~\cite{527120:12033656}
-
-Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\cite{527120:11974320}
-
-Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\cite{527120:11974312}
-
-Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\cite{527120:11974307}
-
 \begin{landscape}
@@
 
+\section{NFES Variants}
+Low-Voltage NFES (LV NFES) \unskip~\cite{527120:11973130}
+
+Scanning Tip Electrospinning \unskip~\cite{527120:11974306}
+
+3D Electrospinning \unskip~\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\cite{527120:11974310}
+
+Multinozzle NFES \unskip~\cite{527120:11974322,527120:11974323,527120:11974324}
+
+Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\cite{527120:11974304}
+
+Suspension NFES \unskip~\cite{527120:12033656}
+
+Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\cite{527120:11974320}
+
+Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\cite{527120:11974312}
+
+Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\cite{527120:11974307}
+
 \section{Conclusion}

### 2019-08-12 NFES_Review/article.tex
mol structures

--- 2019-06-20 NFES_Review/article.tex
@@
 %%
-\documentclass[3p,,preprint,12pt]{elsarticle}
+\documentclass[5p,,preprint,12pt,twocolumn]{elsarticle}
 \makeatletter\if@twocolumn\PassOptionsToPackage{switch}{lineno}\else\fi\makeatother
@@
 % Feature enabled:
-%toc: yes
 %pagenum: yes
+%text-layout: twocolumn
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \makeatother
-          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
-\usepackage{etoolbox}
 
@@
 One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers.
-The technique allows the production of thin continuous fibers with ease, with diameters down to 3 nm in some cases, which is something difficult to achieve by other techniques.
+The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $nm $ in some cases, which is something difficult to achieve by other techniques.
 Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials.
@@
 Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
-Two sub-techniques can be derived from electrospinning depending on the distance between the dispensin g electrode and the collector.
+Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
 The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}.
 Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.
-Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
-This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
 
@@
 \egroup
+Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
+This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
 
-\section{NFES articles' summary}
-The key advance that allows for lowering of the voltage and attendant increase in patterning control ofNFES is the use of a superelastic polymer ink.
-Solutions of such a polymer ink contain long entangled polymer chains that promote stretchability and are expected to augment continuity of the electrospun jets.
-This facilitates the continuous electrospinning of the polymer jet into nanofiber.
+\section{Polymer Solution}
+In electrospinning, it is generally agreed that with higher concentration, the diameter of the fibers increased due to greater viscosity which resist stretching.
+In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}.
+However, in separate studies by Pan et al.\unskip~\cite{527120:11974317,527120:12321129} using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
+Pan et al.\unskip~\cite{527120:12321129} attributed this to a higher charge accumulation in higher concentration PVDF solution.
+However, more studies need to be carried out to verify this.
 
-The polymer jet does not self-initiate under the influence of the voltage because the electrostatic force cannot overcome the surface tension at the droplet - air interface.
-Therefore, the electrospinning process was initiated by introducing an artificial instability at the droplet - air interface with a glass microprobe tip (1 to 3 \ensuremath{\mu }m tip diameter) that resulted in a very high local electric field, sufficient to overcome the interfacial surface tension, giving rise to the formation of the Taylor cone and initiation of the polymer jet.
+\subsection{Polymers}[SECTION UNDERWORK]
 
-Therefore, we believe that 2 wt \% PEO solution has the proper balance of viscosity, conductivity, and resistance to hardening that allows for low-voltage continuous electrospinning.
+\subsection{Solvents}[SECTION UNDERWORK]
 
-At 300 Vand lower, the perturbation phenomenon was eliminated and straight deposition patterns were obtained (as seen in Figure 4c,d).
-This could be achieved with slow stage speeds (20-40 mm/s) clearly demonstrating that the low-voltage NFES technique substantially reduces bending instabilities
+\section{NFES Parameters}
+To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
+Kameoka et al.\unskip~\cite{527120:12321556} demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip.
 
-Another advantage oflower voltage operation lies in reduction of the diameter of the jet, leading to thinner nanofibers.
-This is most likely due to the lower electrostatic forces at play that reduce the feed rate of the polymer, thus reducing jet thickness.
-Therefore, the voltage can be manipulated to directly control the thickness of the nanofibers
+Near-field electrospinning, has exhibited to be capable fabricate nano fibers over and nano fiber patterns \unskip~\cite{527120:11974321}.
+Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner.
+Using a spinneret with a reservoir (e.g.
+syringe) of solution generally produces fibers with diameter of a few micrometers \unskip~\cite{527120:11974310,527120:11974326}, since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through.
 
-Further investigation into the effect of voltage on the thickness \mbox{}\protect\newline of nanofibers reveals an increasing linear trend of average diameter versus voltage as shown in Figure 6.
-This trend is opposite to that observed in far-field electrospinning
+Coppola et al.\unskip~\cite{527120:11974307} have showed a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop, averting the issue of nozzle clogging.
+The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al.'s\unskip~\cite{527120:11974326} work.
 
-We further demonstrate the ability to integrate low-voltage \mbox{}\protect\newline NFES ``writing'' capability with 3D substrates by suspending nanofibers on carbon micropost arrays on a Si substrate.
-In a typical example, we use posts of a height of40 \ensuremath{\mu }m, a diameter of 30 \ensuremath{\mu }m, an interpostal distance of 100 \ensuremath{\mu }m.
-\unskip~\cite{527120:11973130}
+The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al.\unskip~\cite{527120:11974306} used a 100 $\mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
 
-\unskip~\cite{527120:11974314}
+\subsection{Applied Voltage}In recent literature, near field electrospinning has been studied to reduce the fiber diameter and to improve the fiber deposition accuracy.
+Camillo et al.\unskip~\cite{527120:12322072} demonstrated that the application of a modified fine tip nozzle enables the fabrication of 100 $nm $ diameter fiber at a nozzle-to-substrate distance of 500 $\mu m $ and an applied voltage of 1.5 $kV $ .
+On the other hand, Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} came to the conclusion higher voltages yield thicker micro-fibers with a loss in jet stability.
 
-\unskip~\cite{527120:11974329}
+This discrepancy in literature between the applied voltage and resulting fiber diameter is due to the relationship with other variables such as nozzle-to-substrate distance and solution deposition rate.
+For instance, if a high voltage is applied at a low deposition rate then electrospraying is achieved, meaning the formation of several non-continuous fibers.
+The applied voltage shall be sufficient to break the surface tension and initiate the jet, but low enough to avoid multiple jets at the nozzle tip.
 
-\unskip~\cite{527120:11974305}
+Bisht et al.\unskip~\cite{527120:11973130} achieved the fabrication of thinner fibers with spatial control by reducing the applied voltage to 200-600 $V $  at a nozzle-to-substrate distance of 0.5-1 $mm $.
+The low voltage setting does not create enough charge to break the polymer solution surface tension to initiate the electrospinning process.
 
-\unskip~\cite{527120:11974306}
+Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} initiated the electrospun fibers by mechanically pull the polymer solution at the nozzle tip using a micro-probe tip.
+Chang and coworkers reduced the applied voltage from 1.5 $kV $ to 600 $V $ with a nozzle-to-substrate distance of 500 $\mu m $ to yield a fiber diameter between 3 $\mu m $  and 50 $nm $ .
+With an applied voltage of 200 $V $ and a nozzle-to-substrate distance of 1 $mm $ , PEO nano fibers were deposited with a diameter about 20 $nm $.
 
-\unskip~\cite{527120:11974308}
+In near-field electrospinning, the applied voltage has an impact on the produced fiber morphology.
+For instance, a voltage higher or lower to the optimum voltage will translate into an increase in fiber diameter.
+Song et al.\unskip~\cite{527120:11974320} demonstrated that a decrease in voltage from 400 to 500 $V $ can reduce the fiber diameter from 160 to about 60 $nm $with a nozzle-to-substrate distance of 20 $\mu m $.
+The optimum voltage is achieved when a balance is attained between the stretching of the jet and the speed at which it hits the substrate.
+The increase of voltage yields thinner fibers as it causes greater stretching, and a greater jet acceleration.
 
-\unskip~\cite{527120:11974310}
+Another workaround to break the polymer solution surface tension is to initialize the NFES process with a higher voltage and then lower the voltage once the jet is created.
+Huang et al.\unskip~\cite{527120:11974311} implemented the previous and yield ordered fibers with a distance between adjacent fibers of 50 $\mu m $.
+In most cases, a positive voltage is applied to the spinneret.
 
-\unskip~\cite{527120:11974311}
+\subsubsection{Nozzle-to-substrate distance}In NFES, the fiber morphology can be altered by the control of the height between the nozzle and the substrate (collector).
+With the decrease of the nozzle-to-substrate distance, the electric field strength increases; however it can cause incomplete solvent volatilisation and possible short circuits between the collector and the nozzle tip.
 
-\unskip~\cite{527120:11974312}
+An optimal nozzle-to-substrate distance shall be defined to ensure the fabrication of dry continuous fibers.
+If the solvent is not well evaporated, the produced fibers are prone to defects; on the other hand if solidification happens too fast, the solids can block the spinneret which can prevent a continuous fiber yield.
+Furthermore, the polymer jet will discharge itself as soon as possible, therefore long distances can result in low yields.
 
-\unskip~\cite{527120:11974313}
+Typically, metal nozzle tips are used, with small inner diameters.
+From literature, needles with small diameters produce thinner fibers.
+A thin nozzle tip can help the reduction of the fiber diameter, but also it is more likely to become blocked.
 
-\unskip~\cite{527120:11974316}
+\subsubsection{Electric field}Recent literature suggests that the fiber morphology depends on the electric field profile created by the applied voltage during NFES.
+Since the electric field is an induced force that attracts the solution jet towards the desired location within the collector.
 
-\unskip~\cite{527120:11974320}
+Bisht et al.\unskip~\cite{527120:11973130} and Min et al.\unskip~\cite{527120:11974316} have reported the ability to electrospin nano fibers with high accuracy.
+Min et al.
+\unskip~\cite{527120:11974316} implemented a NFES setup with multiple "field-effect transistors" on a flexible polyacrylate collector with an x-y stage velocity of 13.3 $cm/s $ to fabricate fibers with a diameter about 289 $nm $ and a distance between adjacent fibers of 50 $\mu m $.
 
-\unskip~\cite{527120:11974321}
+On the other hand, Bisht et al.\unskip~\cite{527120:11973130} showed evidence of fabricated fibers with low-voltage NFES with high accuracy and precision.
+Bisht et al.'s suspended fibers were deposited over carbon posts with a distance between adjacent fibers of 100 $\mu m $ with diameter of 30 $\mu m $\unskip~\cite{527120:11973130}.
 
-\unskip~\cite{527120:11974322}
+The employment of guided electrodes in NFES, adapts the fabrication process to yield a more accurate fiber deposition.
+For instance, Kim et al.\unskip~\cite{527120:11974313} manufactured ink patterns on a paper with silver nano particles.
+The printed patterns aid the fibers to land on the desired location.
+Kim et al.\unskip~\cite{527120:11974313} electrospun the fibers with a distance between adjacent fibers of 150 $\mu m $.
 
-\unskip~\cite{527120:11974323}
+Xu et al.\unskip~\cite{527120:11974325} created a straight jet from the nozzle tip to the substrate using a guiding electrode underneath the collector.
+The purpose of the guiding electrode is to adjust the path of the NFES jet.
+With the guiding electrode implementation, the fiber's spread was reduced from 74 $\mu m $ to 7 $\mu m $.
 
-\unskip~\cite{527120:11974324}
+\subsection{Substrate}Due to the close distance between the grounded substrate and the charged spinneret in NFES, the set up is prone to electrical shorts.
+In NFES, when a short circuit takes place, the electrospinning process is interrupted resulting in the fabrication of discontinuous fibers.
+Two workarounds to avoid electrical shorts is to lower the applied voltage and to install less conductive substrates \unskip~\cite{527120:11974315,527120:12322289}.
 
-\unskip~\cite{527120:11974325}
+Liu et al.\unskip~\cite{527120:11974315} discovered that the fiber alignment is improved by using a glass-cooper foil substrate, however the well aligned fibers are spoiled after prolonged depositions due to residual charges.
+Additionally, the effect of residual charges is amplified with the used collector substrate contains a conductive layer and a non-conductive layer\unskip~\cite{527120:11974315}.
 
-\unskip~\cite{527120:11974326}
-
-\unskip~\cite{527120:11974327}
-
-\unskip~\cite{527120:11974328}
-
-\unskip~\cite{527120:11974304}
-
-\unskip~\cite{527120:11974307}
-
-\unskip~\cite{527120:12033655}
-
-\unskip~\cite{527120:12033656}
-
-\unskip~\cite{527120:12033657}
-
-\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
-
+On the other hand, Choi et al.\unskip~\cite{527120:12322289} implemented a hydrophobic substrate to deposit the fibers with plasma treatment to increase the conductivity of selected areas.
+NFES was carried put with precise deposition as the fibers were placed as per the desired design within the hydrophilic substrate.
 \begin{landscape}
@@
 \tblmidrule 
-Poly(ethylene oxide) (PEO MW = 4 000 000) &
+Poly(ethylene oxide) (PEO; MW = 4,000,000) &
   Deionized water &
@@
   \unskip~\cite{527120:11973130}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) &
+Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000) with Poly(ethylene oxide) (PEO; MW = 300,000) &
   acetonitrile toluene mixture (65/35); acetic acid toluene (17/83); pure toluene &
@@
 \end{landscape}
+
+\section{NFES Variants}
+[SECTION UNDERWORK]
+
+\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES.
+Low voltage near field electrospinning produces thinner fibers with lower voltages.
+Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching.
+Bisht et al.
+(2011) reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
+
+\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\protect\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\protect\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\protect\cite{527120:11974304}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Suspension NFES \unskip~\protect\cite{527120:12033656}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\protect\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\protect\cite{527120:11974320}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\protect\cite{527120:11974312}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\protect\cite{527120:11974307}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\section{Conclusion}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.

### 2019-08-15 NFES_Review/article.tex
new article updates

@@
 % Feature enabled:
+%toc: yes
 %pagenum: yes
@@
 \makeatother
+          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
+\usepackage{etoolbox}
 
@@
 \end{frontmatter}
+\tableofcontents
 
@@
 However, more studies need to be carried out to verify this.
+\begin{table*}[!htbp]
+\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
+\label{tw-8687dd17082c}
+\def\arraystretch{1}
+\ignorespaces 
+\centering 
+\begin{tabulary}{\linewidth}{LL}
+\tbltoprule Observation & Concentration Adjustement\\
+\tblmidrule 
+Dripping, no stream &
+  Increase\\
+Splitting small droplets &
+  Increase slightly\\
+Steady stream &
+  No concentration adjustment\\
+Splitting large globs &
+  Decrease slightly\\
+Nozzle clogging  &
+  Decrease\\
+\tblbottomrule 
+\end{tabulary}\par 
+\end{table*}
 
-\subsection{Polymers}[SECTION UNDERWORK]
+\subsection{Polymers}The polymer selection is in function on the intended application.
+For example, a fast dissolving hydrophilic polymer such as poly(ethylene oxide) (PEO) is used for fast drug delivery systems.
+Otherwise, slow dissolving polymers such as poly($\varepsilon $-caprolactone) (PCL) or poly(lactic-co-glycolic acid) (PLGA) are implemented.
+\unskip~\cite{527120:13082763}
 
-\subsection{Solvents}[SECTION UNDERWORK]
+The polymer molecular weight along with the polymer concentration and solvent selection have a direct effect on the solution viscosity, conductivity and surface tension, hence the solution behavior in the electrospinning process.
+The spunable viscosity range varies with the polymer and solvent.
+
+Solutions with low viscosity are prone to insufficient polymer chain entanglements to produce fibers.\unskip~\cite{527120:13082763} On the other hand, if the solution is too viscous, then the surface tension cannot easily be overcome by the electric field.
+In both cases, the result can be droplets or particles forming rather than fibers; see Table~\ref{tw-8687dd17082c}.
+
+\subsection{Solvents}The solvent used must be capable of dissolving the polymer of interest at an appropriate concentration to form fibers, and must posses a suitable volatility.
+A low-volatility solvent like water may fail to evaporate completely over the distance between the spinneret and the collector.
+When the fibers form, they will hence contain residual water owing to this incomplete evaporation.
+The residue solvent will subsequently evaporate from the fibers upon storage, resulting in ribbon-like (flattened) fibers, wrinkles on the fiber surface or fused fibers.
+On the other hand, a high-volatility solvent may evaporate very quickly, leading to larger fiber diameters (less time for elongation before solidification) and clogging of the spinneret (due to drying of the liquid at the spinneret before jetting, or drying of the Taylor cone during jetting).
+Solvents commonly used for electrospinning include ethanol, chloroform, dichloromethane and hexafluoroisopropanol.
+
+Mixtures of miscible solvents can be used to ensure that sufficient polymer can be dissolved to give a solution of appropriate viscosity and volatility with suitable dielectric constant range to allow fiber formation.
+However, care must be taken because using a mixture of solvents with very different volatilities can result in porous fiber structures, as reported by Katsogiannis et al.
+for organic solvent mixtures with dimethyl sulfoxide (DMSO).\unskip~\cite{527120:13082766} DMSO evaporates much more slowly than the organic solvents used, which results in its incorporation into the fibers.
+The DMSO will eventually evaporate, yielding porous fibers.
+
+It is also important to take into account the surface tension of the solution.
+Solvents with very high surface tensions (e.g.
+water) can result in instability arising during the spinning process, and a broad range of fiber diameters in the products.
+If necessary, a surfactant can be added to reduce the surface tension, but this will be incorporated into the fibers produced.
 
@@
 
-The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al.\unskip~\cite{527120:11974306} used a 100 $\mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
+\subsection{Nozzle spinneret}The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al.\unskip~\cite{527120:11974306} used a 100 $\mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
+The nozzle most commonly comprises a simple narrow-bore, blunt-end metal needle.
+The diameter of the needle can vary, but most commonly researches work with internal diameters below 1 $mm $ .
+This translates to needles of gauge 18{\textendash}22.
+In general, this simple spinneret design can be used to achieve successful spinning.
+A blunt-end rather than a tapered-end for the needle exit is important as the size distribution of the products increase with an increase in needle tip angle.
+However, it should be noted that there will be some interactions between the solvent and polymer molecules in the solution and the metal surface of the spinneret.
+There will exist some attractive forces between the polar groups in the polymer and the electropositive metal surface, which can act counter to the drawing force of the electric field and can pull the polymer solution back into the spinneret.
+It has been found that coating the spinneret exterior in a non-conductive and non-stick polymer such as Teflon can reduce these interactions.\unskip~\cite{527120:13082768} As a result, the electrical energy can be more efficiently used to elongate and narrow the polymer jet, and narrower fibers can be produced.
+In addition, strong attractive forces between the polymer jet and the metal spinneret can result in fibers becoming attracted to the needle, leading to lower yields and potentially to blocking of the exit orifice.
+This effect too can be ameliorated using an epoxy coating.\unskip~\cite{527120:13082811}
 
@@
 
-\subsubsection{Nozzle-to-substrate distance}In NFES, the fiber morphology can be altered by the control of the height between the nozzle and the substrate (collector).
+\subsection{Nozzle-to-substrate distance}In NFES, the fiber morphology can be altered by the control of the height between the nozzle and the substrate (collector).
 With the decrease of the nozzle-to-substrate distance, the electric field strength increases; however it can cause incomplete solvent volatilisation and possible short circuits between the collector and the nozzle tip.
@@
 
-\subsubsection{Electric field}Recent literature suggests that the fiber morphology depends on the electric field profile created by the applied voltage during NFES.
+\subsection{Electric field}Recent literature suggests that the fiber morphology depends on the electric field profile created by the applied voltage during NFES.
 Since the electric field is an induced force that attracts the solution jet towards the desired location within the collector.
@@
 Poly(ethylene oxide) (PEO) &
-  Deionized water and the ethanol with a volume ratio of 3:1 &
+  Deionized water and ethanol with a volume ratio of 3:1 &
   Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) &
@@
 
+\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}
+
 \bibliographystyle{elsarticle-num}

### 2019-08-22 NFES_Review/article.tex
article progress

@@
 
-\title{Review of Polymer Solutions for Near-Field Electrospinning with Spatial Control
+\title{Polymers for Near-field Electrospinning with Spatial Control
 }
@@
 
-The main components of the electrospinning technique are the fluid control unit (e.g.
+\subsection{Types of electrospinning }The main components of the electrospinning technique are the fluid control unit (e.g.
 syringe pump) and a voltage power supply.
@@
 Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.
+
+\subsubsection{High voltage power supply}Direct Current \mbox{}\protect\newline Alternating Current
+
+\subsubsection{Polymer reservoir}Polymer melt \mbox{}\protect\newline Polymer solution
+
+\subsubsection{Stretching forces}Centrifugal force \mbox{}\protect\newline Blowing forces \mbox{}\protect\newline Electric force \mbox{}\protect\newline Microfluidic forces \mbox{}\protect\newline Mechanical force
+
+\subsubsection{Polymer yielding}Atomization (particles) \mbox{}\protect\newline Spraying (droplets) \mbox{}\protect\newline Spinning (fibers)
+
+\subsubsection{Dispensing nozzle}Coaxial / Monoaxial \mbox{}\protect\newline Multinozzle
+
+\subsubsection{Nozzle-to-substrate distance}Far Field Spinning \mbox{}\protect\newline Near Field Spinning
+
+\section{"Electro - DC - monoaxial - solution - NF - spinning"}
 
@@
 \section{Polymer Solution}
-In electrospinning, it is generally agreed that with higher concentration, the diameter of the fibers increased due to greater viscosity which resist stretching.
+In electrospinning, it is typically agreed that the diameter of the fibers increased with higher concentration due to greater viscosity which withstands stretching.
 In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}.
 However, in separate studies by Pan et al.\unskip~\cite{527120:11974317,527120:12321129} using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
-Pan et al.\unskip~\cite{527120:12321129} attributed this to a higher charge accumulation in higher concentration PVDF solution.
-However, more studies need to be carried out to verify this.
 \begin{table*}[!htbp]
@@
 \tblmidrule 
-Poly(ethylene oxide) (PEO; MW = 4,000,000) &
+Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) &
   Deionized water &
@@
   \unskip~\cite{527120:11973130}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000) with Poly(ethylene oxide) (PEO; MW = 300,000) &
+Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000 $g/mol $) with Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
   acetonitrile toluene mixture (65/35); acetic acid toluene (17/83); pure toluene &
   Typical NFES process &
-  \textbf{Solution Concentration:} \mbox{}\protect\newline 10$mg $ of MEH-PPV in 2$mL $ of toluene; 500$mL $ of MEH-PPV solution with 250$mg $ of PEO in 3.5$mL $ of acetonitrile; 500$mL $ of MEH-PPV solution with 250$mg $ of PEO in 3$mL $ of acetic acid / toluene (17 / 83).
-The resulting MEH-PPV/PEO concentration is 1:100 \mbox{}\protect\newline \textbf{Nozzle:} mm-diameter tip Tungsten spinneret in a 26 gauge needle \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} SiO2/Si (oxide thickness = 800 nm) \mbox{}\protect\newline \textbf{Applied voltage:} around 1.3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 100$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} around 100$\mu m $ &
+  \textbf{Solution Concentration:} \mbox{}\protect\newline 10$mg $ of MEH-PPV in 2$mL $ of toluene; 500$\mu L $ of MEH-PPV solution with 250$mg $ of PEO in 3.5$mL $ of acetonitrile / toluene (65 / 35); 500$\mu L $ of MEH-PPV solution with 250$mg $ of PEO in 3$mL $ of acetic acid / toluene (17 / 83).
+The resulting MEH-PPV/PEO concentration is 0.08 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} mm-diameter tip Tungsten spinneret in a 26 gauge needle \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} SiO2/Si (oxide thickness = 800 nm) \mbox{}\protect\newline \textbf{Applied voltage:} around 1.3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 100$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} around 100$\mu m $ &
   \unskip~\cite{527120:11974305}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MV = 300,000 $g/mol $) &
   Water &
@@
   \unskip~\cite{527120:11974306}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(vinylidine fluorid) (PVDF) &
+Poly(vinylidine fluorid) (PVDF; MW = 440,000 $g/mol $) &
   N,N Dimethylformamide (DMF) &
@@
 The resulting concentration is 18\% PVDF.
-\mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 510$\mu m $ and inner diameter of 260$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 400$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 10-50$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Poly(dimethylsiloxane) (PDMS) on Ecoflex \mbox{}\protect\newline \textbf{Applied voltage:} 1.5{\textendash}3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0-400$mm/min $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 1.5-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+\mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 510$\mu m $ and inner diameter of 260$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 400$nL/min $ \mbox{}\protect\newline \textbf{Nozazle-to-substrate distance:} 10-50$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Poly(dimethylsiloxane) (PDMS) on Ecoflex \mbox{}\protect\newline \textbf{Applied voltage:} 1.5{\textendash}3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0-400$mm/min $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 1.5-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
   \unskip~\cite{527120:11974308}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Polyhedral Oligomeric Silsesquioxane-Poly(Carbonate-Urea)Urethane (POSS-PCU) and Polyhedral Oligomeric Silsesquioxane Poly(Caprolactone-Poly(Carbonate-Urea)Urethane) (POSS-PCL-PCU) &
+Polyhedral Oligomeric Silsesquioxane-Poly(Carbonate-Urea)Urethane (POSS-PCU) and Polyhedral Oligomeric Silsesquioxane Poly(Caprolactone-Poly(Carbonate-Urea)Urethane) (POSS-PCL-PCU) \mbox{}\protect\newline (Dry Polycarbonate MW = 2000 $g/mol $) &
   Dimethyl acetamide (DMAC) and 1-Butanol &
@@
   \unskip~\cite{527120:11974310}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
   Distilled water &
@@
   \unskip~\cite{527120:11974311}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
   Deionized water and ethanol with a volume ratio of 3:1 &
@@
   \unskip~\cite{527120:11974312}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(Vinylidene Fluoride) (PVDF) &
+Poly(Vinylidene Fluoride) (PVDF; MW = 534,000 $g/mol $) &
   Acetone and Dimethyl Sulfoxide (DMSO) &
@@
   \unskip~\cite{527120:11974313}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(9-Vinyl Carbazole) (PVK) &
+Poly(9-Vinyl Carbazole) (PVK; MW = 1,100,000 $g/mol $) &
   Styrene &
@@
   \unskip~\cite{527120:11974316}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Polystyrene (PS) &
+Polystyrene (PS; MW \textit{Not determined}) &
   1,2,4-Trichloro benzene &
   Electrohydro-dynamic (EHD) jet printing &
-  \textbf{Solution Concentration:} 1 to 5$wt\% $ PS \mbox{}\protect\newline \textbf{Nozzle:} Glass nozzle inner diameter of 2$\mu m $ and outer diameter of 2.66$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} Si \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: 20, 30, 40$\mu m $} \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} 500 to 400$V $ in 25$V $ increments \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.01-10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 60-170$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \textbf{Solution Concentration:} 1 to 5$wt\% $ PS \mbox{}\protect\newline \textbf{Nozzle:} Glass nozzle inner diameter of 2$\mu m $ and outer diameter of 2.66$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance}: 20, 30, 40$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition: }Si \mbox{}\protect\newline \textbf{Applied voltage:} 500 to 400$V $ in 25$V $ increments \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.01-10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 60-170$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
   \unskip~\cite{527120:11974320}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
   \textit{Not determined} &
@@
   \unskip~\cite{527120:11974321}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
   Distilled water &
@@
   \unskip~\cite{527120:11974322}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
   Distilled water &
@@
   \unskip~\cite{527120:11974323}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
   Distilled water &
@@
   \unskip~\cite{527120:11974324}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) &
   \textit{Not determined} &
@@
   \unskip~\cite{527120:11974325}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Gelatin \mbox{}\protect\newline (porcine skin) &
+Gelatin \mbox{}\protect\newline (porcine skin; MW \textit{Not determined}) &
   Acetic Acid and Ethyl Acetate &
@@
   \unskip~\cite{527120:11974326}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
   Water/Ethanol (v/v = 60/40) &
   Typical NFES process &
-  \textbf{Solution Concentration:} PEO concentrations of 16\% adn 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
+  \textbf{Solution Concentration:} PEO concentrations of 16\% and 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
   \unskip~\cite{527120:11974327}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
   Water/Ethanol (v/v = 3/1) &
@@
   \unskip~\cite{527120:11974328}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
   Deionized water &
@@
   \unskip~\cite{527120:11974304}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(co-Glycolic) acid (PLGA)  &
+Poly(co-Glycolic) acid (PLGA; MW \textit{Not determined})  &
   Dimethyl Carbonate (DMC) &
@@
   \unskip~\cite{527120:11974307}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) with Tetrabutylammonium tetrafluoroborate (TBF) and SU-8 2002 &
+Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) with Tetrabutylammonium tetrafluoroborate (TBF; MW \textit{Not determined}) and SU-8 2002 &
   N,N Dimethylformamide (DMF) &
@@
   \unskip~\cite{527120:12033655}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; 200,000 $g/mol $) &
   Water:Ethanol (3:2) &
@@
   \unskip~\cite{527120:12033656}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO) &
+Poly(ethylene oxide) (PEO; MW = 400,000 $g/mol $) &
   Deionized water &
   Typical NFES process &
-  \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &
+  \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &
   \unskip~\cite{527120:12033657}\\
@@
 
+Nanofibers are fibers with diameters in the nanometer range. The development of nanofibers has greatly enhanced the scope for meeting up the modern world challenges.
+
+Currently there are two types of electrospinning systems available for producing nanofiber: needle based electrospinning and needleless electrospinning.
+This paper summarizes the basic mechanism of various types of needle based and needleless spinning systems described in various literatures by many researchers.
+
+\bgroup
+\fixFloatSize{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}{\includegraphics{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}}{}
+\makeatother 
+\caption{{}}
+\label{f-f076e2b74317}
+\end{figure*}
+\egroup
+
 \subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES.
@@
 Bisht et al.
-(2011) reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
+\unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
 
@@
 \section{Conclusion}
+
+\bgroup
+\fixFloatSize{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}{\includegraphics{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}}{}
+\makeatother 
+\caption{{}}
+\label{f-ab38f7e015f7}
+\end{figure*}
+\egroup
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 
+\section{NFES Achievements \& Challenges}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 \apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}

### 2019-08-29 NFES_Review/article.tex
updates to article

@@
 The produced fibers can be aligned or unaligned.
-Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques.
-On the other hand, the understanding of the electrospinning process has improved in the last years \unskip~\cite{527120:12073538}.
+Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques\unskip~\cite{527120:12073538}.
+On the other hand, the understanding of the electrospinning process has improved in the last years.
 
-\subsection{Types of electrospinning }The main components of the electrospinning technique are the fluid control unit (e.g.
-syringe pump) and a voltage power supply.
-The process also requires a target electrode or combination of electrodes on which the fibers can be collected.
-Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
+\subsection{Types of electrospinning (Classified by process properties)}Current literature dictates the typical spinning setup is comprised by three main components: a syringe needle, a fiber collector, and some way to dispense the fibers from the needle to the collector.
+The spinning process is an electrohydro-dynamic (EHD) technique that yields continuous polymer fibers.
+Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively.
+
+\bgroup
+\fixFloatSize{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}{\includegraphics{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}}{}
+\makeatother 
+\caption{{Electrohydro-dynamic techniques}}
+\label{f-02e0e3cf88d6}
+\end{figure*}
+\egroup
+In electrospinning the fibers are deposited by an electrical potential difference between the syringe needle and the collector.
+The supplied polymer (typically a polymer solution) is administrated at a constant rate to create and maintain a polymer drop at the dispensing nozzle.
+A high voltage (usually DC) is applied between the polymer feed and the collector.
+As the electric field increases, the polymer drop (held by its surface tension) is then deformed at the tip of the syringe needle to form a conical shape known as Taylor cone.
+When the electric force overcomes the surface tension force a polymer jet is ejected from the tip of the Taylor cone.
+As the polymer jet leaves the nozzle, it accelerates and stretches while traveling to the fiber collector.
+The fiber finally develops with the complete solvent evaporation.
+
+\subsubsection{High voltage power supply: Direct Current \& Alternating Current}Electricity comprises a flow of electrons (negatively charged subatomic particles).
+In direct current (DC; used for the vast majority ofelectrospinning work) the electrons flow in one direction continually.
+Itis also possible to have alternating current (AC), which is used to powermost electrical devices in the home.
+AC involves a periodic change in thedirection of current flow: that is, the electrons first flow in one directionand then switch to flow in the reverse direction.
+The switch betweendirections is repeated many times per second and is known as the frequency of the AC.
+Using an AC power supply rather than the conventional DC supply was first shown to generate polymer-based nanofibresin 2004.
+[3]
+
+The experimental set-up for AC electrospinning is similar to thatfor the DC process, but it does not require a grounded collector.
+Because the current alternates, the fibres produced at one instant in time carry apositive charge, while those generated shortly thereafter have a negativecharge.
+The positive and negative fibres thus discharge on each other,which results in an aerogel plume of fibres.
+The frequency of the AC current determines whether charge carriersof one polarity have sufficient time to charge the solution and result inspinning.
+The optimal AC frequency is material-dependent and typicallyin the range of 50 Hz{\textendash}1 kHz.
+[4]
+
+The AC approach has been explored for the fabrication of drugloaded fibres in a few recent studies.
+In one, Balogh et al.
+undertook adirect comparison of fibres prepared by DC and AC spinning.5 They usedthe beta-blocker carvedilol as a model drug, and fibres were generatedusing three different polymers: Eudragit EPO, a cationic copolymer soluble below pH 5.0; Eudragit L100-55, an anionic polymer soluble abovepH 5.5; and the neutral polymer poly(vinyl pyrrolidone) (PVP).
+It wasfound that fibres could be generated with all three polymers from bothtypes of spinning, but that it was possible to use muchfaster flow rates in the AC process.
+With DC spinning, a maximum flow rate of 5 ml h{\textendash}1 could be achieved, whereas with AC this could beincreased to up to 40 ml h{\textendash}1.
+All fibres, from both processes and madefrom all polymers, existed as amorphous solid dispersions.
+The drugrelease profiles were studied, and the AC and DC fibres were found to beindistinguishable in their performance.
+[Adapted with permission from Balogh, A.; Cselko, R.; Demuth,B.; Verreck, G.; Mensch, J.; Marosi, G.; Nagy, Z.
+K.
+`Alternating currentelectrospinning for preparation of fibrous drug delivery systems.' Int.J.
+Pharm.
+495 (2015): 75{\textendash}80.
+Copyright Elsevier 2015.]
+
+The same team have also compared AC and DC electrospinningof blends of hydroxypropylmethylcellulose (HPMC) and poly(ethyleneoxide) (PEO) with the poorly water-soluble diuretic spironolactone.
+[6] Both HPMC and PEO alone could be processed by the DC approach.
+Incontrast, AC electrospinning of HPMC led to a mixture of droplets andfibres, and high-molecular-weight PEOs did not yield any solid productsat all in the AC method.
+Selecting appropriate blends of the two polymers,however, permitted high-quality fibres to be formed via AC spinning.
+
+AC processing of HPMC or PEO with spironolactone also proved tobe problematic, but again with the right mix of HPMC and PEO drugloaded fibres could be generated.
+These were able to accelerate thedissolution rate of the drug, even at loadings of up to 40\% w/w.
+The ACgenerated fibres were found to be several orders of magnitude thinnerthan the DC electrospun fibres despite the flow rate being three timesfaster in the AC process.
+
+Similar observations have been reported using HPMC acetate succinate (HPMCAS) and spironolactone.
+[7] HPMCAS could not be processedby either DC or AC electrospinning; the addition of PEO permitted fibresto be produced with the DC approach, but not using AC, and the additionof an ionic surfactant or salt was required to produce high-quality fibreswith AC spinning.
+As with HPMC, the HPMCAS fibres led to a significantenhancement in the dissolution rate
+
+It is thus clear that AC electrospinning is similarly effective to theDC approach in producing drug delivery systems.
+Although its use in thisregard is in its infancy, given the fact it allows higher throughput than theDC technique, it seems certain that this is an approach which is likely toreceive much more attention in the coming years.
+
+\subsubsection{Polymer reservoir: Polymer melt \& Polymer solution}Another variant of electrospinning which has attracted some attentionin the drug delivery sphere is the melt process.
+This is discussed indetail in a recent review.
+[8] In brief, the process is analogous to the solution electrospinning discussed in previous sections, but in place of a polymer solution a melt is used.
+This adds some complexity to the process, because the syringe and spinneret must be heated to maintain thepolymer in its liquid state.
+Further, the elevated temperature can potentially lead to drug degradation, since many drugs are thermally labile.The fibres produced in melt spinning are typically found to have largerdiameters than those from the solution route due to the significantlyhigher viscosity of a polymer melt than its solution form.
+The apparatusused is depicted in [TODO: draw an apparatus used for melt electrospinning].
+
+Despite these apparent disadvantages, there are a number ofattractive aspects of the melt spinning process, not least the fact that itobviates the need to handle large volumes of volatile solvents.
+This bothrenders the process safer, particularly if it is to be performed on the largerscale, and precludes any solvent contamination in the products.
+
+The first report of a melt electrospun drug delivery system camefrom Nagy and co-workers, who prepared melt-spun fibres of Eudragit EPO loaded with carvedilol.
+[9] The drug and polymer were melted andmixed to form a homogeneous solid mixture prior to spinning, and thenprocessed as in a solution experiment but with both the syringe and spinneret heated.
+The melt fibres were much wider than analogous systemsprocessed through solution spinning, with those from melt processinghaving diameters of 5{\textendash}30 \ensuremath{\mu}m, as compared to 300{\textendash}1000 nm for the solution-spun fibres.
+The drug was completely amorphouslydispersed in the fibers regardless of the processing route.
+This is asexpected for solution spinning, and in the melt case was thought tobe because the experiment was carried out above the melting point ofcarvedilol.
+The melt fibres freed their drug loading faster than the solution-spun analogues, despite the much larger surface area of the latter.The authors ascribed this to the fact that the melt fibres had a loose nonwoven structure, whereas those prepared by solution spinning weremore tightly packed.
+
+This work has been built on to blend plasticisers with the polymerEudragit E and carvedilol active ingredient.
+[10] The plasticisers triacetin,Tween 80 and polyethylene glycol were all investigated with the goal ofreducing the melting point of the polymer/drug blend and thereby permitting lower temperatures to be used for spinning.
+This should reducethe likelihood of any degradation occurring.
+High-performance liquidchromatography data obtained on dissolved fibres revealed that the addition of plasticisers clearly reduced the amounts of carvedilol degradation products present after melt spinning
+
+A direct comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibres generatedby the melt and solution-spinning approaches has been reported by Lianand Meng.
+[11] These authors prepared curcumin-loaded fibres of around4 \ensuremath{\mu}m in diameter using both techniques.
+They found that there was agreater tendency for the curcumin to crystallise using the solution route(a result of its low solubility in the solvent used for spinning).
+The meltfibres led to a reduced burst release and a slower release rate.
+Thesefindings were attributed to the solution-spun fibres having a porous structure, which permitted both water ingress and the incorporated curcuminto diffuse out of the polymer matrix
+
+Melt electrospinning typically generates micron-size fibres.
+In arecent effort, however, highly uniform and precise deposition of PCLnanofibres (817 \ensuremath{\pm} 165 nm) was achieved using a method known as meltelectrospinning writing.
+[12] This combines melt electrospinning with additive manufacturing (three-dimensional (3D) printing) technology, usinga computer-controlled extruder moving on a translational stage to build a3D structure layer by layer.
+The 3D fibrous architecture produced allowedefficient in vitro proliferation of primary human mesenchymal stromalcells.
+The melt electrospinning writing technology can produce regular3D morphologies in a highly controllable and reproducible fashion, andis currently being explored for a range of tissue-engineering applications.
+
+Although melt electrospinning has received much less researchinterest than the solution process, it appears to be equally as flexible interms of handling multiple fluids, and coaxial melt spinning has beenreported.
+[13] The initial melt spinning experiment is perhaps harder toestablish than the solution route, but it is clear that this approach has agreat deal of unexplored potential in the development of drug deliverysystems.
+
+\subsubsection{Stretching forces}
+
+\paragraph{Centrifugal force}Centrifugal spinning employs a rotating polymer source to generate fibres.Several centrifugal methods can generate nanofibres.
+These includeForcespinning, which employs rotary speed of above 2000 revolutionsper minute (rpm), [14] electrocentrifugal spinning, [15] which combines astrong electric potential (as in electrospinning) with centrifugal force,and pressurised gyration, which adds high pressure ({\textgreater} 10 kPa) to centrifugal spinning to enhance fibre formation (see section 6.8).
+[16]
+
+These approaches can be applied to polymer solutions andemulsions, and if the source can be heated also to a polymer melt [TODO: draw an apparatus used for centrifugalspinning].
+[17] This technique has received some attention in the contextof drug delivery.
+For instance, Zander prepared PCL fibres using both thesolution and melt variants of the centrifugal technique.
+[18] This authoremployed spinning speeds in the range of 3000{\textendash}18,000 rpm, yieldingfibres of 10 \ensuremath{\mu }m in diameter.
+PC12 neuron cells could be successfullygrown on the fibres, demonstrating that they have potential in nervetissue engineering.
+
+In other work, centrifugally spun PCL/PVP fibres containing theantibiotic tetracycline have been produced from a methanol/chloroformsolution at 2000 rpm.
+[19] These were sub-micron in their diameters, andhighly aligned.
+The rate of drug release could be tuned by varying thePCL/PVP ratio in the fibres, and the fibres were found to be effective ininhibiting bacterial growth.
+Core/shell fibres for the delivery of growthfactors have further been reported from centrifugal spinning of a waterin-oil emulsion, with PCL dissolved in the oil phase.
+[20]
+
+Fibres have also been made using a melt process with sucrose (asugar dimer) loaded with a range of poorly water-soluble drugs, includingolanzapine (an antipsychotic medicine) and piroxicam (a non-steroidalanti-inflammatory).
+[21] The fibres were 10{\textendash}15 \ensuremath{\mu }m in diameter, and the dissolution rate of the drugs enhanced after fibre formation.
+
+Since the centrifugal spinning approach is a simple one whichallows relatively large-scale production of fibres, [22] it appears to havemuch promise in the drug delivery field.
+It can also be coupled toelectrospinning, with both centrifugal and electrical forces applied simultaneously to drive solvent evaporation.
+[15] Such centrifugalelectrospinning uses the same equipment as the standard centrifugalprocess but additionally applies a high voltage between the rotatingspinneret and the collector.
+It has been reported to lead to significantlyhigher throughput than standard electrospinning, [23] and to producehighly aligned fibres.
+[23, 24] Centrifugal electrospinning has further beendemonstrated to have potential in the production of drug deliverysystems, with a recent report of PVP fibres loaded with the antibiotictetracycline hydrochloride.
+[25] Production rates of up to 120 g h{\textendash}1 couldbe realised.
+
+\paragraph{Blowing forces}A pressurised gas can be exploited to produce nanoscale fibres, startingeither with a polymer solution in a technique known as solution blowingor from a molten polymer source (melt blowing).
+The experimentalapparatus used is similar to electrospinning, in that a polymer solution(or melt) is expelled through a needle (spinneret) at a controlled rate.The spinneret is surrounded by an outer nozzle which applies pressuredgas to the fluid being expelled, as illustrated in [TODO: draw an apparatus used for solution blow spinning or melt blowing].
+[26]
+
+A few studies have explored solution blowing in drug delivery,with the first such work being from Oliveira et al.
+in 2013.
+[27] These authors prepared poly(lactic acid) (PLA) fibres loaded with the hormone progesterone, which can be used to regulate the reproductivecycle in livestock.
+Fibres were produced from solutions with 6\% w/vPLA and between 0 and 8\% w/v progesterone.
+The PLAis semi-crystalline both before and after processing, while the drug isamorphous post-spinning.
+The fibres behave very similarly in termsof their release behaviour, regardless of the amount of drug loaded.
+
+A study comparing electrospun and solution-blown fibres of poly(3-hydroxybutyrate-co-3-hydroxyvalerate) loaded with sodium diclofenachas also been reported.
+[26] The drug-loaded fibres were slightly larger indiameter when generated by electrospinning, and the size uniformitywas higher through solution blowing.
+In general there was a greateramount of burst release seen with the electrospun fibres, but otherwisethere were no clear trends in the drug release data.
+
+Solution-blown fibres have additionally been created loaded withoil extracted from the medicinal plant Copaifera sp., which is oftenexplored for antimicrobial purposes.
+[28] These materials were constructedfrom a blend of the polymers PLA and PVP, and were around 1 \ensuremath{\mu}m indiameter.
+An increased PVP content was found to result in increased antibacterial activity after 24 h.
+
+The melt blowing process has also received some attention in thepharmaceutical setting, and the fibres produced compared with thosefrom both solution and melt electrospinning.
+[29] Marosi's team generatedformulations from a vinylpyrrolidone{\textendash}vinyl acetate copolymer, employingpoly(ethylene glycol) (PEG) as a plasticiser and carvedilol as a modeldrug.
+All three methods led to fibres, with the solution electrospun fibresnarrowest (at 2 \ensuremath{\mu}m in diameter), followed by the melt-blown (10\ensuremath{\mu}m) and melt-spun (50 \ensuremath{\mu}m) products.
+Carvedilol was rendered into the amorphous physical form by all three processing techniques, and all theformulations were able to accelerate the drug dissolution process.
+Themelt-blown and melt electrospun systems led to the fastest release, withalmost identical release profiles, while the solution-electrospun fibresfreed their drug cargo somewhat more slowly.
+
+A variant of the solution-blowing technique has been applied tothe processing of living cells (in this setting it has been referred to asbiothreading).
+[30] Using a pressurised coaxial needle with the exteriorfluid comprising a viscous polydimethylsiloxane solution and an aqueouscell suspension in the core, cells can be processed into scaffolds with nonoticeable loss in viability.
+
+Electrospinning and melt/solution blowing can be combined in a processknown as electroblowing.
+This employs both electricity and a gas flow toaid fibre elongation and solidification.
+The experimental apparatus usesa similar spinneret to that in [Figure apparatus used for solution blow spinning or melt blowing], and in addition to the gas flowa potential difference is applied between the spinneret and the collector.This technique has been shown to have significant potential in medicalapplications: in 2014, Jiang et al.
+applied electroblowing in vitro and invivo to deliver a homogeneous and continuous layer of a medical glue tostop bleeding during liver resection.
+[31]
+
+More recently, Balogh et al.
+prepared fibres of 2-hydroxypropyl-\ensuremath{\beta }-cyclodextrin loaded with sodium diclofenac.
+[32] They found that whenelectrospinning this system, very frequent clogging of the spinneretoccurred.
+Electroblowing overcame this issue and additionally allowedfaster flow rates to be used, increasing the amount of material thatcould be produced.
+However, the uniformity of the fibre products wascompromised, with more `beads-on-string' type morphology seen withthe blown products.
+In both cases, the fibres comprised amorphous soliddispersions with no crystalline drug evident.
+The electroblown fibresdissolved a little more slowly than those from electrospinning, but stillmuch more rapidly than a physical mixture of drug and cyclodextrin.
+
+A subsequent study using Eudragit E and itraconazole (anantifungal active pharmaceutical ingredient) also found that a fasterflow rate could be used in blowing, but that the fibre products from thelatter had less regular morphologies.
+[33] Again, the drug was amorphouslydispersed in the fibres, and the dissolution profiles of the electrospun andelectroblown systems were very similar.
+
+\paragraph{Electric force}
+
+\paragraph{Microfluidic forces}Microfluidic spinning is based on the use of micro (sub-millimetre)channels.
+A large number of these are located in a single microfluidicchip, and the rate and time of liquid expulsion from each channel are precisely controlled by computer.
+Microfluidic spinning can be coupled withelectrospinning, as described in detail in a recent review by Cheng et al.
+[51]While the productivity of microfluidic methods is a major challenge inscale-up, the technique offers the ability to generate fibres with a highlevel of complexity not easily achievable by electrospinning.
+For example,using a digitally programmed microfluidic flow, Kang et al.
+created functional microfibres with continuous spatiotemporal coding along thelength of the fibre.
+[52] The fibres contained varied chemical compositionsand topography, and localised bioactive agents.
+
+Microfluidic spinning therefore has the potential to enable veryprecisely tuneable loading of different drugs into a single fibre, allowingfor programmable release in different parts of the body at differenttimes.
+The technique is beginning to be explored for drug deliveryapplications.
+However, the materials used in microfluidics are usuallyhydrogels (crosslinked polymer networks solvated with water).
+Theseoften have fast degradation rates and as a result can be unsuitable forthe extended release of drugs, particularly small molecules.
+To helpmitigate this problem, Chae et al.
+developed a microfluidic spinningmethod using an isopropyl alcohol sheath flow with an aqueousalginate core flow.
+[53] This innovation resulted in nanofibres made ofhighly ordered alginate molecules.
+Ahn et al.
+loaded ampicillin intoalginate fibres prepared in this manner, [54 and found that the orderedstructure delayed fibre degradation, allowing extended-release profileof ampicillin over 7 days.
+
+\paragraph{Mechanical force}
+
+\subsubsection{Dispensing nozzle: Coaxial / Monoaxial: Single nozzle / Multinozzle}
+
+\subsubsection{Nozzle-to-substrate distance}
+
+\paragraph{Near Field Spinning}Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
 Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
@@
 
-\subsubsection{High voltage power supply}Direct Current \mbox{}\protect\newline Alternating Current
-
-\subsubsection{Polymer reservoir}Polymer melt \mbox{}\protect\newline Polymer solution
-
-\subsubsection{Stretching forces}Centrifugal force \mbox{}\protect\newline Blowing forces \mbox{}\protect\newline Electric force \mbox{}\protect\newline Microfluidic forces \mbox{}\protect\newline Mechanical force
-
-\subsubsection{Polymer yielding}Atomization (particles) \mbox{}\protect\newline Spraying (droplets) \mbox{}\protect\newline Spinning (fibers)
-
-\subsubsection{Dispensing nozzle}Coaxial / Monoaxial \mbox{}\protect\newline Multinozzle
-
-\subsubsection{Nozzle-to-substrate distance}Far Field Spinning \mbox{}\protect\newline Near Field Spinning
+\paragraph{Far Field Spinning}In  a far field electrospinning the process continues ...
+Decreasing the jet diameter, the surface charge density increases and the resulting high repulsive forces split the jet into several smaller jets.
+The jet is seriously elongated by a bending and whipping processes caused by electrostatic repulsion initiated at small bends in the fiber, until it is finally deposited on the collector.
+Two types of collector may be used, either stationary or rotary collector.
 
@@
 \bgroup
-\fixFloatSize{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}
+\fixFloatSize{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}
 \begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}{\includegraphics{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}}{}
+\centering \makeatletter\IfFileExists{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}{\includegraphics{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}}{}
 \makeatother 
@@
 
-\section{NFES Parameters}
+\section{Effect of the NFES Parameters}
+
+\bgroup
+\fixFloatSize{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}{\includegraphics{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}}{}
+\makeatother 
+\caption{{Near-Field ES Process Parameters}}
+\label{f-3629d3a3f9cf}
+\end{figure*}
+\egroup
 To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
@@
 \section{NFES Variants}
-[SECTION UNDERWORK]
+[SECTION to be REMOVED]
 
@@
 This paper summarizes the basic mechanism of various types of needle based and needleless spinning systems described in various literatures by many researchers.
-
-\bgroup
-\fixFloatSize{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}{\includegraphics{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}}{}
-\makeatother 
-\caption{{}}
-\label{f-f076e2b74317}
-\end{figure*}
-\egroup
 
@@
 \bgroup
+\fixFloatSize{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}{\includegraphics{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}}{}
+\makeatother 
+\caption{{Applied volage vs. Fiber diameter}}
+\label{f-59ed68f95344}
+\end{figure*}
+\egroup
+
+\bgroup
+\fixFloatSize{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}{\includegraphics{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}}{}
+\makeatother 
+\caption{{Solution concentration vs. Fiber diameter}}
+\label{f-0ba4df766d66}
+\end{figure*}
+\egroup
+
+\bgroup
 \fixFloatSize{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}
@@
 \makeatother 
-\caption{{}}
+\caption{{Solution concentration vs. Molecular weight}}
 \label{f-ab38f7e015f7}

### 2019-09-11 NFES_Review/article.tex
article progress

--- 2019-08-22 NFES_Review/article.tex
@@
 %toc: yes
+%bookmark: yes
 %pagenum: yes
 %text-layout: twocolumn
+%endfloat: placeins
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\makeatletter
+\@ifpackageloaded{hyperref}{\def\alreadybookmark{}}{\usepackage[hidelinks]{hyperref}}
+\@ifpackageloaded{bookmark}{}{\usepackage{bookmark}}
+\makeatother
+\ifdefined\alreadybookmark\def\pdfbookmark[#1]#2#3{}\fi
 \makeatletter
@@
           \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
+\usepackage[section]{placeins}
+
 \usepackage{etoolbox}
@@
 \begin{document}
+\pdfbookmark[title]{Polymers for Near-field Electrospinning with Spatial Control}{title}
 
@@
 
-\section{Introduction}
-Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}.
-One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers.
+\section{Types of electrospinning (Classified by process properties)}
+~Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}.
+One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano fibers from a variety of polymers.
 The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $nm $ in some cases, which is something difficult to achieve by other techniques.
@@
 The produced fibers can be aligned or unaligned.
-Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques.
-On the other hand, the understanding of the electrospinning process has improved in the last years \unskip~\cite{527120:12073538}.
+Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques\unskip~\cite{527120:12073538}.
+On the other hand, the understanding of the electrospinning process has improved in the last years.
 
-\subsection{Types of electrospinning }The main components of the electrospinning technique are the fluid control unit (e.g.
-syringe pump) and a voltage power supply.
-The process also requires a target electrode or combination of electrodes on which the fibers can be collected.
-Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
+Current literature dictates the typical spinning setup is comprised by three main components: a syringe needle, a fiber collector, and some way to dispense the fibers from the needle to the collector.
+The spinning process is an electrohydro-dynamic (EHD) technique that yields continuous polymer fibers.
+Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively.
+
+\bgroup
+\fixFloatSize{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}{\includegraphics{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}}{}
+\makeatother 
+\caption{{Electrohydro-dynamic techniques}}
+\label{f-02e0e3cf88d6}
+\end{figure*}
+\egroup
+In electrospinning the fibers are deposited by an electrical potential difference between the syringe needle and the collector.
+The supplied polymer (typically a polymer solution) is administrated at a constant rate to create and maintain a polymer drop at the dispensing nozzle.
+A high voltage (usually DC) is applied between the polymer feed and the collector.
+As the electric field increases, the polymer drop (held by its surface tension) is then deformed at the tip of the syringe needle to form a conical shape known as Taylor cone.
+When the electric force overcomes the surface tension force a polymer jet is ejected from the tip of the Taylor cone.
+As the polymer jet leaves the nozzle, it accelerates and stretches while traveling to the fiber collector.
+The fiber finally develops with the complete solvent evaporation.
+
+\subsection{High voltage power supply: Direct Current \& Alternating Current}Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction.
+Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow.
+Kessick et al.\unskip~\cite{527120:13444381} demonstrated the implementation of AC power supplies in the production of polymer fibers.
+
+The AC electrospinning setup is similar to that for the DC variant.
+AC electrospinning apparatus do not require a grounded collector as the current alternates.
+In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge.
+The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers.
+The optimal AC frequency depends on the materials used and is typically within of 50 $Hz $ {\textendash} 1 $kHz $.
+\unskip~\cite{527120:13443405}
+
+The AC technique has been studied for drug loaded related applications.
+Balogh et al.
+\unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques.
+They produced fibers by using three polymers: Eudragit EPO (cationic copolymer), Eudragit L100-55 (anionic polymer) and poly(vinyl pyrrolidone) (PVP) (neutral polymer).
+Balogh et al.
+discovered AC and DC electrospinning can produce fibers with all three polymers.
+However, The AC process allowed the implementation of faster flow rates than in the DC setup.
+The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $.
+AC electrospinning approach is as effective as the DC technique in producing drug delivery systems.
+
+\subsection{Polymer reservoir: Polymer melt \& Polymer solution}Another electrospinning classification is the melt process.
+As Brown et al.
+\unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used).
+The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state.
+The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution.
+The apparatus used by Brown et al.
+\unskip~\cite{527120:13445499} is depicted in .
+
+[TODO: draw an apparatus used for melt electrospinning].
+
+Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.
+
+The first report of a melt electrospun drug delivery system came from Nagy et al.
+\unskip~\cite{527120:13445555}, who prepared fibers by melt electrospinning of Eudragit EPO with carvedilol.
+The drug and polymer were melted and mixed to form a homogeneous solid mixture prior to spinning.
+The melt-spun fibers reached diameters of 5{\textendash}30 $\mu m $, compared to 300{\textendash}1000 $nm $ diameters produced from solution-spun fibers.
+
+This work has been built on to blend plasticisers with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticisers Triacetin, Tween 80 and Polyethylene Glycol were investigated by Attila et al.
+in order to reduce the melting point of the polymer-drug mixture.
+The temperature drop is desirable to minimize the occurring drug degradation.
+
+Lian and Meng\unskip~\cite{527120:13445754} performed a comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibers fabricated by the melt and solution electrospinning techniques.
+Lian and Meng\unskip~\cite{527120:13445754} reported that melt spinning is preferable when the polymer presents a low solubility, on the other hand the melt fibers were produced in a slower release rate.
+Lian and Men findings feature the solution-spun fibers to have a porous structure.
+Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning.
+In their effort, they achieved a precise deposition of PCL fibers with diameters of $817 \pm 165 nm $.
+
+In literature, melt electrospinning has less evidence than the solution approach.
+However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}.
+Currently, the melt electrospinning setup is harder to establish but the lack of research on this technique explains its unexplored potential.
+
+\subsection{Stretching forces}
+
+\subsubsection{Electric Field}
+
+\subsubsection{Centrifugal force}The spinning processes require the implementation of a force to break the polymer source into a polymer jet.
+Centrifugal spinning intends to produce fibers by the use of a rotating polymer source.
+The centrifugal force generated from typical rotatory speeds above 2000 rpm, results in fiber formation.
+\unskip~\cite{527120:13535559,527120:13535561}.
+
+The centrifugal force technique is applied to polymer solutions and melts.
+This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.
+Efforts in centrifugal spinning are focused on drug delivery applications.
+Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach.
+Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.
+
+On the other hand, PCL and PVP fibers were generated by Amalorpava et al.
+\unskip~\cite{527120:13536089}.
+Amalorpava achieved sub micron/size fiber diameters for drug release purposes and bacteria growth inhibition properties.
+Literature\unskip~\cite{527120:13536446} has shown that centrifugal approach has a simple setup that promises a large scale fabrication of fibers.
+
+In some cases the centrifugal force implementations and pressurized gyration can be combined with an electric field.
+The implementation of two stretching forces (centrifugal and electrical forces), can help solvent evaporation\unskip~\cite{527120:13536560}.
+Centrifugal electrospinning implements the same setup as the standard centrifugal spinning with the addition of a high voltage power supply between the rotating dispensing nozzle and the collector.
+The combined method has evidence to yield parallel fibers\unskip~\cite{527120:13536841,527120:13536900,527120:13537392,527120:13537393} at a higher rate \unskip~\cite{527120:13536841,527120:13536900} than the standard electrospinning approach.
+
+\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution.
+The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate.
+Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}.
+
+[TODO: draw an apparatus used for solution blow spinning or melt blowing] \unskip~\cite{527120:13538056}.
+
+A few studies have explored solution blowing in drug delivery, with the first such work being from Oliveira et al.
+in 2013.
+[27] These authors prepared poly(lactic acid) (PLA) fibres loaded with the hormone progesterone, which can be used to regulate the reproductivecycle in livestock.
+Fibres were produced from solutions with 6\% w/vPLA and between 0 and 8\% w/v progesterone.
+The PLAis semi-crystalline both before and after processing, while the drug isamorphous post-spinning.
+The fibres behave very similarly in termsof their release behaviour, regardless of the amount of drug loaded.
+
+A study comparing electrospun and solution-blown fibres of poly(3-hydroxybutyrate-co-3-hydroxyvalerate) loaded with sodium diclofenachas also been reported.
+[26] The drug-loaded fibres were slightly larger in diameter when generated by electrospinning, and the size uniformity was higher through solution blowing.
+In general there was a greateramount of burst release seen with the electrospun fibres, but otherwisethere were no clear trends in the drug release data.
+
+Solution-blown fibres have additionally been created loaded with oil extracted from the medicinal plant Copaifera sp., which is often explored for antimicrobial purposes.
+[28] These materials were constructed from a blend of the polymers PLA and PVP, and were around 1 \ensuremath{\mu}m in diameter.
+An increased PVP content was found to result in increased antibacterial activity after 24 h.
+
+The melt blowing process has also received some attention in thepharmaceutical setting, and the fibres produced compared with thosefrom both solution and melt electrospinning.
+[29] Marosi's team generatedformulations from a vinylpyrrolidone{\textendash}vinyl acetate copolymer, employingpoly(ethylene glycol) (PEG) as a plasticiser and carvedilol as a modeldrug.
+All three methods led to fibres, with the solution electrospun fibres narrowest (at 2 \ensuremath{\mu}m in diameter), followed by the melt-blown (10\ensuremath{\mu}m) and melt-spun (50 \ensuremath{\mu}m) products.
+Carvedilol was rendered into the amorphous physical form by all three processing techniques, and all theformulations were able to accelerate the drug dissolution process.
+Themelt-blown and melt electrospun systems led to the fastest release, withalmost identical release profiles, while the solution-electrospun fibresfreed their drug cargo somewhat more slowly.
+
+A variant of the solution-blowing technique has been applied tothe processing of living cells (in this setting it has been referred to asbiothreading).
+[30] Using a pressurised coaxial needle with the exteriorfluid comprising a viscous polydimethylsiloxane solution and an aqueouscell suspension in the core, cells can be processed into scaffolds with nonoticeable loss in viability.
+
+Electrospinning and melt/solution blowing can be combined in a processknown as electroblowing.
+This employs both electricity and a gas flow toaid fibre elongation and solidification.
+The experimental apparatus usesa similar spinneret to that in [Figure apparatus used for solution blow spinning or melt blowing], and in addition to the gas flowa potential difference is applied between the spinneret and the collector.This technique has been shown to have significant potential in medicalapplications: in 2014, Jiang et al.
+applied electroblowing in vitro and invivo to deliver a homogeneous and continuous layer of a medical glue tostop bleeding during liver resection.
+[31]
+
+More recently, Balogh et al.
+prepared fibres of 2-hydroxypropyl-\ensuremath{\beta }-cyclodextrin loaded with sodium diclofenac.
+[32] They found that whenelectrospinning this system, very frequent clogging of the spinneretoccurred.
+Electroblowing overcame this issue and additionally allowedfaster flow rates to be used, increasing the amount of material thatcould be produced.
+However, the uniformity of the fibre products wascompromised, with more `beads-on-string' type morphology seen withthe blown products.
+In both cases, the fibres comprised amorphous soliddispersions with no crystalline drug evident.
+The electroblown fibresdissolved a little more slowly than those from electrospinning, but stillmuch more rapidly than a physical mixture of drug and cyclodextrin.
+
+A subsequent study using Eudragit E and itraconazole (anantifungal active pharmaceutical ingredient) also found that a fasterflow rate could be used in blowing, but that the fibre products from thelatter had less regular morphologies.
+[33] Again, the drug was amorphouslydispersed in the fibres, and the dissolution profiles of the electrospun andelectroblown systems were very similar.
+
+\subsubsection{Microfluidic forces}Microfluidic spinning is based on the use of micro (sub-millimetre)channels.
+A large number of these are located in a single microfluidicchip, and the rate and time of liquid expulsion from each channel are precisely controlled by computer.
+Microfluidic spinning can be coupled withelectrospinning, as described in detail in a recent review by Cheng et al.
+[51]While the productivity of microfluidic methods is a major challenge inscale-up, the technique offers the ability to generate fibres with a highlevel of complexity not easily achievable by electrospinning.
+For example,using a digitally programmed microfluidic flow, Kang et al.
+created functional microfibres with continuous spatiotemporal coding along thelength of the fibre.
+[52] The fibres contained varied chemical compositionsand topography, and localised bioactive agents.
+
+Microfluidic spinning therefore has the potential to enable veryprecisely tuneable loading of different drugs into a single fibre, allowingfor programmable release in different parts of the body at differenttimes.
+The technique is beginning to be explored for drug deliveryapplications.
+However, the materials used in microfluidics are usuallyhydrogels (crosslinked polymer networks solvated with water).
+Theseoften have fast degradation rates and as a result can be unsuitable forthe extended release of drugs, particularly small molecules.
+To helpmitigate this problem, Chae et al.
+developed a microfluidic spinningmethod using an isopropyl alcohol sheath flow with an aqueousalginate core flow.
+[53] This innovation resulted in nanofibres made ofhighly ordered alginate molecules.
+Ahn et al.
+loaded ampicillin intoalginate fibres prepared in this manner, [54 and found that the orderedstructure delayed fibre degradation, allowing extended-release profileof ampicillin over 7 days.
+
+\subsubsection{Mechanical force}
+
+\subsection{Dispensing nozzle: Coaxial / Monoaxial: Single nozzle / Multinozzle}
+
+\subsection{Nozzle-to-substrate distance}
+
+\subsubsection{Near Field Spinning}Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
 Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
@@
 
-\subsubsection{High voltage power supply}Direct Current \mbox{}\protect\newline Alternating Current
-
-\subsubsection{Polymer reservoir}Polymer melt \mbox{}\protect\newline Polymer solution
-
-\subsubsection{Stretching forces}Centrifugal force \mbox{}\protect\newline Blowing forces \mbox{}\protect\newline Electric force \mbox{}\protect\newline Microfluidic forces \mbox{}\protect\newline Mechanical force
-
-\subsubsection{Polymer yielding}Atomization (particles) \mbox{}\protect\newline Spraying (droplets) \mbox{}\protect\newline Spinning (fibers)
-
-\subsubsection{Dispensing nozzle}Coaxial / Monoaxial \mbox{}\protect\newline Multinozzle
-
-\subsubsection{Nozzle-to-substrate distance}Far Field Spinning \mbox{}\protect\newline Near Field Spinning
+\subsubsection{Far Field Spinning}In  a far field electrospinning the process continues ...
+Decreasing the jet diameter, the surface charge density increases and the resulting high repulsive forces split the jet into several smaller jets.
+The jet is seriously elongated by a bending and whipping processes caused by electrostatic repulsion initiated at small bends in the fiber, until it is finally deposited on the collector.
+Two types of collector may be used, either stationary or rotary collector.
 
@@
 This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
+
+Nanofibers are fibers with diameters in the nanometer range. The development of nanofibers has greatly enhanced the scope for meeting up the modern world challenges.
+
+Currently there are two types of electrospinning systems available for producing nanofiber: needle based electrospinning and needleless electrospinning.
+This paper summarizes the basic mechanism of various types of needle based and needleless spinning systems described in various literatures by many researchers.
+
+\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES.
+Low voltage near field electrospinning produces thinner fibers with lower voltages.
+Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching.
+Bisht et al.
+\unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
+
+\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\protect\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\protect\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\protect\cite{527120:11974304}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Suspension NFES \unskip~\protect\cite{527120:12033656}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\protect\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\protect\cite{527120:11974320}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\protect\cite{527120:11974312}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+
+\subsection{Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\protect\cite{527120:11974307}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
 
@@
 
-\section{NFES Variants}
-[SECTION UNDERWORK]
-
-Nanofibers are fibers with diameters in the nanometer range. The development of nanofibers has greatly enhanced the scope for meeting up the modern world challenges.
-
-Currently there are two types of electrospinning systems available for producing nanofiber: needle based electrospinning and needleless electrospinning.
-This paper summarizes the basic mechanism of various types of needle based and needleless spinning systems described in various literatures by many researchers.
+\section{Conclusion}
 
 \bgroup
-\fixFloatSize{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}
+\fixFloatSize{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}
 \begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}{\includegraphics{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}}{}
+\centering \makeatletter\IfFileExists{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}{\includegraphics{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}}{}
 \makeatother 
-\caption{{}}
-\label{f-f076e2b74317}
+\caption{{Applied volage vs. Fiber diameter}}
+\label{f-59ed68f95344}
 \end{figure*}
@@
 
-\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES.
-Low voltage near field electrospinning produces thinner fibers with lower voltages.
-Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching.
-Bisht et al.
-\unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
-
-\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\protect\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\protect\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\protect\cite{527120:11974304}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Suspension NFES \unskip~\protect\cite{527120:12033656}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\protect\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\protect\cite{527120:11974320}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\protect\cite{527120:11974312}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\protect\cite{527120:11974307}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\section{Conclusion}
+\bgroup
+\fixFloatSize{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}{\includegraphics{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}}{}
+\makeatother 
+\caption{{Solution concentration vs. Fiber diameter}}
+\label{f-0ba4df766d66}
+\end{figure*}
+\egroup
 

### 2019-10-17 NFES_Review/Polymers_for_Nearfield_Electrospinning_with_Spatial_Control-2019-10-17-15-16/article.tex
nano tec presentation plus review paper progress

--- 2019-09-11 NFES_Review/article.tex
@@
 
-\section{Types of electrospinning (Classified by process properties)}
+\section{Fabrication Processes of Polymer Fibers}
 ~Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}.
@@
 \fixFloatSize{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}
-\begin{figure*}[!htbp]
+\begin{figure}[!htbp]
 \centering \makeatletter\IfFileExists{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}{\includegraphics{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}}{}
@@
 \label{f-02e0e3cf88d6}
-\end{figure*}
+\end{figure}
 \egroup
-In electrospinning the fibers are deposited by an electrical potential difference between the syringe needle and the collector.
-The supplied polymer (typically a polymer solution) is administrated at a constant rate to create and maintain a polymer drop at the dispensing nozzle.
-A high voltage (usually DC) is applied between the polymer feed and the collector.
-As the electric field increases, the polymer drop (held by its surface tension) is then deformed at the tip of the syringe needle to form a conical shape known as Taylor cone.
-When the electric force overcomes the surface tension force a polymer jet is ejected from the tip of the Taylor cone.
-As the polymer jet leaves the nozzle, it accelerates and stretches while traveling to the fiber collector.
-The fiber finally develops with the complete solvent evaporation.
-
-\subsection{High voltage power supply: Direct Current \& Alternating Current}Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction.
-Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow.
-Kessick et al.\unskip~\cite{527120:13444381} demonstrated the implementation of AC power supplies in the production of polymer fibers.
-
-The AC electrospinning setup is similar to that for the DC variant.
-AC electrospinning apparatus do not require a grounded collector as the current alternates.
-In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge.
-The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers.
-The optimal AC frequency depends on the materials used and is typically within of 50 $Hz $ {\textendash} 1 $kHz $.
-\unskip~\cite{527120:13443405}
-
-The AC technique has been studied for drug loaded related applications.
-Balogh et al.
-\unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques.
-They produced fibers by using three polymers: Eudragit EPO (cationic copolymer), Eudragit L100-55 (anionic polymer) and poly(vinyl pyrrolidone) (PVP) (neutral polymer).
-Balogh et al.
-discovered AC and DC electrospinning can produce fibers with all three polymers.
-However, The AC process allowed the implementation of faster flow rates than in the DC setup.
-The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $.
-AC electrospinning approach is as effective as the DC technique in producing drug delivery systems.
 
@@
 
+\subsection{Dispensing nozzle}Coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle [TODO: draw nested needles].
+\unskip~\cite{527120:13914792,527120:13914793} The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers.
+Sun et al.
+\unskip~\cite{527120:13914312} addressed electrospinning setups, where both the core and shell are comprised by PEO (poly(ethylene oxide)) and for a PEO shell with a poly(dode-cylthiophene) core.
+Sun et al.
+state that co-electrospinning has the potential to extend the range of materials that can be used for electrospinning.
+The shell solution can be modified to make the core solution spunable.
+It was also discovered that non-spunable solutions can by implemented as shell solutions in conjunction with a spunable core solution.
+\unskip~\cite{527120:13914968}
+
+Some advantages that co-electrospinning setups can offer include the preempting the initial jet burst from the spinneret nozzle.
+On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles.
+\unskip~\cite{527120:13914748,527120:13914750}.
+As in conventional NFES, in co-electrospinning, the needle tip is connected to a high voltage power supply with a grounded collector.
+With the influence of high electric fields, the fibers are prone to brake into separate layers due to the whipping instabilities as the jet travels to the substrate.
+The instability can be mitigated by adding additional ring electrodes between the spinneret and the grounded collector.
+\unskip~\cite{527120:13915304}
+
 \subsection{Stretching forces}
 
-\subsubsection{Electric Field}
+\subsubsection{Electric Field}Electrospinning (electrostatic fiber spinning) is a fiber fabrication approach that implements an electric field produce fibers by an electrical potential difference between the syringe needle and the collector.
+The typical electrospinning setup applies an electrostatic charge to the polymer fluid at the tip of the needle nozzle, which results in the formation of the Taylor cone \unskip~\cite{527120:13659828}, from which a single polymer jet is ejected to the grounded collector.
+From the Taylor cone, the supplied polymer jet (typically a polymer solution) accelerates and reduces in diameter.
+The fiber finally develops with the complete solvent evaporation.
+Electrospun fibers are prone to splitting with the increase in acceleration, where multiple fibers are yield in a process known as electrospraying \unskip~\cite{527120:13659925}.
+
+The electrospinning process starts with charging a polymer solution droplet.
+When a polymer solution is administrated with a syringe pump, solution droplets will fall under the influence of gravity.
+The solution dripping stops when the electric field is strong enough to break the solution's surface tension, causing the droplet to change shape forming a polymer solution jet\unskip~\cite{527120:12033655}.
+
+Shin et al.
+\unskip~\cite{527120:13659926} reported that the growth of the whipping instability is one important element within the electrospinning technique.
+As detailed in Shin's work, weak electric fields produce a single uniformly thinning jet, and strong electric fields the jet becomes unstable after traveling a short distance.
+
+\paragraph{High voltage power supply: Direct Current \& Alternating Current}Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction.
+Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow.
+Kessick et al.\unskip~\cite{527120:13444381} demonstrated the implementation of AC power supplies in the production of polymer fibers.
+
+The AC electrospinning setup is similar to that for the DC variant.
+AC electrospinning apparatus do not require a grounded collector as the current alternates.
+In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge.
+The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers.
+The optimal AC frequency depends on the materials used and is typically within of 50 $Hz $ {\textendash} 1 $kHz $.
+\unskip~\cite{527120:13443405}
+
+The AC technique has been studied for drug loaded related applications.
+Balogh et al.
+\unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques.
+They produced fibers by using three polymers: Eudragit EPO (cationic copolymer), Eudragit L100-55 (anionic polymer) and poly(vinyl pyrrolidone) (PVP) (neutral polymer).
+Balogh et al.
+discovered AC and DC electrospinning can produce fibers with all three polymers.
+However, The AC process allowed the implementation of faster flow rates than in the DC setup.
+The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $.
+AC electrospinning approach is as effective as the DC technique in producing drug delivery systems.
 
@@
 
-A few studies have explored solution blowing in drug delivery, with the first such work being from Oliveira et al.
-in 2013.
-[27] These authors prepared poly(lactic acid) (PLA) fibres loaded with the hormone progesterone, which can be used to regulate the reproductivecycle in livestock.
-Fibres were produced from solutions with 6\% w/vPLA and between 0 and 8\% w/v progesterone.
-The PLAis semi-crystalline both before and after processing, while the drug isamorphous post-spinning.
-The fibres behave very similarly in termsof their release behaviour, regardless of the amount of drug loaded.
+Poly(lactic acid) (PLA) fibers have been produced by solution blow spinning.
+Oliveira et al.
+\unskip~\cite{527120:13539278} fabricated the fibers from $6 wt\% $ PLA solutions with progesterone for live stock reproductive cycle regulation applications.
+On the other hand, Souza et al.\unskip~\cite{527120:13538056} conducted a study to compare the standard electrospinning and the solution blow spinning techniques.
+Poly(3-hydroxybutyrate-co-3-hydroxyvalerate) were fabricated by both methods.
+The fibers produced by electrospinning had thicker diameters and their size uniformity was higher in the fibers produced by solution blow spinning.
 
-A study comparing electrospun and solution-blown fibres of poly(3-hydroxybutyrate-co-3-hydroxyvalerate) loaded with sodium diclofenachas also been reported.
-[26] The drug-loaded fibres were slightly larger in diameter when generated by electrospinning, and the size uniformity was higher through solution blowing.
-In general there was a greateramount of burst release seen with the electrospun fibres, but otherwisethere were no clear trends in the drug release data.
+Jiang et al.\unskip~\cite{527120:13554126} combined the blowing technique with the electrospinning approach.
+The blow electrospinning technique implements both electric and gas flow forces to stretch the fibers.
+Jiang used an apparatus similar to those used in traditional electrospinning.
+The experimental setup requires a coaxial needle nozzle with a pressurized gas flow along with a potential difference between the dispensing needle and the grounded collector.
 
-Solution-blown fibres have additionally been created loaded with oil extracted from the medicinal plant Copaifera sp., which is often explored for antimicrobial purposes.
-[28] These materials were constructed from a blend of the polymers PLA and PVP, and were around 1 \ensuremath{\mu}m in diameter.
-An increased PVP content was found to result in increased antibacterial activity after 24 h.
+[TODO: draw Figure apparatus used for solution blow spinning or melt blowing]
 
-The melt blowing process has also received some attention in thepharmaceutical setting, and the fibres produced compared with thosefrom both solution and melt electrospinning.
-[29] Marosi's team generatedformulations from a vinylpyrrolidone{\textendash}vinyl acetate copolymer, employingpoly(ethylene glycol) (PEG) as a plasticiser and carvedilol as a modeldrug.
-All three methods led to fibres, with the solution electrospun fibres narrowest (at 2 \ensuremath{\mu}m in diameter), followed by the melt-blown (10\ensuremath{\mu}m) and melt-spun (50 \ensuremath{\mu}m) products.
-Carvedilol was rendered into the amorphous physical form by all three processing techniques, and all theformulations were able to accelerate the drug dissolution process.
-Themelt-blown and melt electrospun systems led to the fastest release, withalmost identical release profiles, while the solution-electrospun fibresfreed their drug cargo somewhat more slowly.
+\subsubsection{Mechanical force}Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette.
+\unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical applications.
+\unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers.
+Touch-spinning comprises a rotating stage with an embedded glass rod.
+[TODO: draw touch spinning setup].
+Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers.
+The rotation stretches the fiber, causing the fiber to increase in length and decrease in diameter.
+The increase in length causes the fiber surface are to increase and therefore making the polymer solution solvent to volatilize, ending with a dry fiber within the collector.
 
-A variant of the solution-blowing technique has been applied tothe processing of living cells (in this setting it has been referred to asbiothreading).
-[30] Using a pressurised coaxial needle with the exteriorfluid comprising a viscous polydimethylsiloxane solution and an aqueouscell suspension in the core, cells can be processed into scaffolds with nonoticeable loss in viability.
+The touch spinning technique implies that the fiber diameter can be controlled by the rotation speed and the polymer solution concentration.
+The main difference relays on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}
 
-Electrospinning and melt/solution blowing can be combined in a processknown as electroblowing.
-This employs both electricity and a gas flow toaid fibre elongation and solidification.
-The experimental apparatus usesa similar spinneret to that in [Figure apparatus used for solution blow spinning or melt blowing], and in addition to the gas flowa potential difference is applied between the spinneret and the collector.This technique has been shown to have significant potential in medicalapplications: in 2014, Jiang et al.
-applied electroblowing in vitro and invivo to deliver a homogeneous and continuous layer of a medical glue tostop bleeding during liver resection.
-[31]
+\subsubsection{Microfluidic forces}The microfluidic spinning technique manipulates and controls the polymer solution in networks of micrometer channels.
+The channel network are typically embedded in a microfluidic chip, where the solution deposition rate is controlled by active components (pumps and valves) with a computer.
+Cheng et al.
+\unskip~\cite{527120:13656236} compared and combined the microfluidic spinning and electrospinning techniques.
 
-More recently, Balogh et al.
-prepared fibres of 2-hydroxypropyl-\ensuremath{\beta }-cyclodextrin loaded with sodium diclofenac.
-[32] They found that whenelectrospinning this system, very frequent clogging of the spinneretoccurred.
-Electroblowing overcame this issue and additionally allowedfaster flow rates to be used, increasing the amount of material thatcould be produced.
-However, the uniformity of the fibre products wascompromised, with more `beads-on-string' type morphology seen withthe blown products.
-In both cases, the fibres comprised amorphous soliddispersions with no crystalline drug evident.
-The electroblown fibresdissolved a little more slowly than those from electrospinning, but stillmuch more rapidly than a physical mixture of drug and cyclodextrin.
+On the other hand, Kang et al.
+\unskip~\cite{527120:13656548} managed to fabricate micro fibers by imitating the "silk spinning" process of spiders.
+Kang's micro fibers properties were modified using a microfluidic system with a programmable flow control.
+The current microfluidic spinning approach is not scalable to a large fiber production, however it enables the fabrication of high-complex fibers that are not easily achieved by other methods.
 
-A subsequent study using Eudragit E and itraconazole (anantifungal active pharmaceutical ingredient) also found that a fasterflow rate could be used in blowing, but that the fibre products from thelatter had less regular morphologies.
-[33] Again, the drug was amorphouslydispersed in the fibres, and the dissolution profiles of the electrospun andelectroblown systems were very similar.
+[TODO: draw Figure apparatus used for microfluidic spinning]
 
-\subsubsection{Microfluidic forces}Microfluidic spinning is based on the use of micro (sub-millimetre)channels.
-A large number of these are located in a single microfluidicchip, and the rate and time of liquid expulsion from each channel are precisely controlled by computer.
-Microfluidic spinning can be coupled withelectrospinning, as described in detail in a recent review by Cheng et al.
-[51]While the productivity of microfluidic methods is a major challenge inscale-up, the technique offers the ability to generate fibres with a highlevel of complexity not easily achievable by electrospinning.
-For example,using a digitally programmed microfluidic flow, Kang et al.
-created functional microfibres with continuous spatiotemporal coding along thelength of the fibre.
-[52] The fibres contained varied chemical compositionsand topography, and localised bioactive agents.
+Microfluidic techniques offer the possibility to embed several components into a single fiber, where each component can be released at different parts of the fiber.
 
-Microfluidic spinning therefore has the potential to enable veryprecisely tuneable loading of different drugs into a single fibre, allowingfor programmable release in different parts of the body at differenttimes.
-The technique is beginning to be explored for drug deliveryapplications.
-However, the materials used in microfluidics are usuallyhydrogels (crosslinked polymer networks solvated with water).
-Theseoften have fast degradation rates and as a result can be unsuitable forthe extended release of drugs, particularly small molecules.
-To helpmitigate this problem, Chae et al.
-developed a microfluidic spinningmethod using an isopropyl alcohol sheath flow with an aqueousalginate core flow.
-[53] This innovation resulted in nanofibres made ofhighly ordered alginate molecules.
-Ahn et al.
-loaded ampicillin intoalginate fibres prepared in this manner, [54 and found that the orderedstructure delayed fibre degradation, allowing extended-release profileof ampicillin over 7 days.
+\subsection{Nozzle-to-substrate distance}[TODO: draw FFES setup], depicts the typical setup for the conventional far-field electrospinning (FFES).
+As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}.
+When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process.
+The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}.
+The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.
 
-\subsubsection{Mechanical force}
+In the intent to achieve controlled fiber deposition, Sun et al.
+\unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES).
+[TODO: draw NFES setup], describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line.
+Moreover, some mechanical influence is required to deposit fibers precisely.
+The mechanical force is introduced by moving collector.
+If the polymer solution jet speed is faster than the speed of the moving collector, the written fiber will curl; on the other hand, if the collector moves faster than the polymer jet, the fiber will gradually diminish \unskip~\cite{527120:11974327,527120:11974326}.
+Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.
 
-\subsection{Dispensing nozzle: Coaxial / Monoaxial: Single nozzle / Multinozzle}
-
-\subsection{Nozzle-to-substrate distance}
-
-\subsubsection{Near Field Spinning}Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
-Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
-The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}.
-Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.
-
-\subsubsection{Far Field Spinning}In  a far field electrospinning the process continues ...
-Decreasing the jet diameter, the surface charge density increases and the resulting high repulsive forces split the jet into several smaller jets.
-The jet is seriously elongated by a bending and whipping processes caused by electrostatic repulsion initiated at small bends in the fiber, until it is finally deposited on the collector.
-Two types of collector may be used, either stationary or rotary collector.
-
-\section{"Electro - DC - monoaxial - solution - NF - spinning"}
+The main difference between NFES and FFES is the distance between the needle and the collector which is higher in FFES (about 10 cm) compared to NFES which ranges in the mm scale.
+The short distance allow the production of well aligned fibers within particular designs.
+[7]
 
 \bgroup
-\fixFloatSize{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}{\includegraphics{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}}{}
+\fixFloatSize{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}{\includegraphics{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}}{}
 \makeatother 
-\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130} .}}
-\label{f-fe28447572e9}
-\end{figure*}
+\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130}.}}
+\label{f-8e5a75d9ba17}
+\end{figure}
 \egroup
+
+\section{Properties that Improve Accuracy of Nano-Fiber Deposition}
 Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
 This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
-
-Nanofibers are fibers with diameters in the nanometer range. The development of nanofibers has greatly enhanced the scope for meeting up the modern world challenges.
-
-Currently there are two types of electrospinning systems available for producing nanofiber: needle based electrospinning and needleless electrospinning.
-This paper summarizes the basic mechanism of various types of needle based and needleless spinning systems described in various literatures by many researchers.
 
@@
 
-\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+-{\textgreater} A continuous method for controlled electrospinning of polymeric nano fibers on two-dimensional (2D) and three-dimensional (3D) substrates using low voltage near-field electrospinning (LV NFES).
+The method overcomes some of the drawbacks in more conventional near-field electrospinning by using a super elastic polymer ink formulation.
+The visco-elastic nature of our polymer ink enables continuous electrospinning at a very low voltage of 200 V, almost an order of magnitude lower than conventional NFES, thereby reducing bending instabilities and increasing control of the resulting polymer jet.
+In one application, polymeric nano fibers are freely suspended between micro structures of 3D carbon on Si substrates to illustrate wiring together 3D components in any desired pattern.{\textless}-
 
-\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}-{\textgreater} A continuous near-field electrospinning (NFES) process has been developed to deposit solid nano fibers with orderly patterns over large areas.
+Before the onset of electrospinning, a bias voltage is applied to a semi-spherical shaped polymer droplet outside of a syringe needle, and a probe tip mechanically draws a single fiber from the droplet to initiate continuous NFES.
+Contrary to the conventional electrospinning process, we show that decreasing electrical field in continuous NFES results in smaller line width deposition, and nano fibers can be assembled into controlled complex patterns such as circular shapes and grid arrays on large and flat areas.
+{\textless}-
 
-\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}-{\textgreater} Characterized the behavior of polymer jet from near-field electrospinning onto the ink-jet patterned paper with conductive Ag nano particles in order to form the controlled three-dimensional nano structures.
+Using ink-jet patterned paper with conductive ink as a collector, the polymer jet is induced to the pre patterned shape through the concentrated electric field caused by singularity between the spinneret and the printed patterns.
+Due to the electric field enhancement of the deposited electrospun fiber, an additionally spun fiber can be stacked on the deposited fibers directly.
+Therefore, the controlled three-dimensional nano/micro structures can be successfully realized by the proposed method.
+We characterized the deposition of the electrospun fiber according to the distance between the ink-jet printed pattern and the spinneret.
+In addition, the sharp edged three-dimensional micro-structures were fabricated by carrying out the electrospinning on the patterns with various angled edges.
+A CCD camera was used to observe the behavior of the polymer jet, and the SEM image was analyzed to confirm that the fibers are stacked as desired.
 
-\subsection{Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\protect\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\protect\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\protect\cite{527120:11974304}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Uncover a new method for the preparation of bio-polymer scaffolds and demonstrate its potential for the development of organs with the aid of tissue engineering.
+Two novel nano-composite polymers, a non-biodegradable polyhedral oligomeric silsesquioxane-poly (carbonate-urea)urethane and a biodegradable polyhedral oligomeric silsesquioxane-polycaprolactone-poly(carbonate-urea)urethane, have been subjected to flow in an electric field.
+Electrically forced micro-threading of the polymers occurs and a three-dimensional print-patterning device was used to deposit fine (⬍50 \ensuremath{\mu}m) threads of polymer according to a pre-designed architecture to prepare scaffolds.
+The technique can offer tremendous potential in the development of organs.
+{\textless}-
 
-\subsection{Suspension NFES \unskip~\protect\cite{527120:12033656}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}-{\textgreater} Multinozzle electrospinning systems are designed to increase productivity, while near-field electrospinning (NFES) systems are designed to deposit solid nano fibers in a direct, continuous, and controllable manner.
+In this paper, several multinozzle NFES setups are tested.
+The experiment reveals that the deposition distance becomes larger when working distance and needle spacing increase, and the influence of voltage is relatively weaker.
+The deposition of double nozzle NFES has been studied with Coulomb's law and theoretical derivation has been verified by the experimental conclusion.
+The experiment result and theoretical derivation are helpful to get different distance of direct-written fibers by adjusting working distance or needle spacing to change distance of fibers largely and adjusting voltage to change distance slowly.
+Through these efforts, it is convenient to adjust the distance of straight fibers in multinozzle system.
+[1]
 
-\subsection{Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\protect\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\protect\cite{527120:11974320}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+For large area micro/nano pattern printing, multi-nozzle electrohydrodynamic (EHD) printing setup is an efficient method to boost productivity in near-field electrospinning (NFES) process.
+And controlling EHD multi-jet accurate deposition under the interaction of nozzles and other parameters are crucial concerns during the process.
+The influence and sensitivity of various parameters such as the needle length, needle spacing, electrode-to-collector distance, voltage etc.
+on the direct-write patterning performance was investigated by orthogonal experiments with dual-nozzle NFES setup, and then the deposition distance estimated based on a novel model was com- pared with measurement results and proven.
+More controllable deposition distance and much denser of aligned nano fiber can be achieved by rotating the dual-nozzle setup.
+This study can be greatly contributed to estimate the deposition distance and helpful to guide the multi-nozzle NFES process to accurate direct-write pattern in manufacturing process in the future.
 
-\subsection{Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\protect\cite{527120:11974312}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+To mass-volume fabricate micro- and nano scales aligned pattern, multi-nozzle near- field electrospinning (NFES) direct-writing technology is well proposed as a high- efficiency method in electrohydrodynamic (EHD) printing process.
+However, the interference effect among adjacent nozzles and coupling effect of various parameters have restricted to investigate deposition characteristic of multi-nozzle NFES and control EHD multi-jet deposition accuracy.
+In order to improve the accuracy of EHD multi-jet deposition with high-efficiency printing process, the experimental result compared with theoretical method were discussed.
+In this work, the influence of multi-nozzle geometry distribution and electrospinning parameters on deposition characteristic was studied with multi-nozzle NFES setup, and nozzles were in linear array.
+The deposition distance and homogeneity of aligned nano fibers were measured and explained with coefficient of dispersion on electric field among nozzles by simulation.
+Moreover, deposition distance of multi-nozzle NFES process was evalu- ated by modified theoretical derivation based on our previous studies.
+The modified theoretical derivation showed a good agreement with experiment results, and indicated that multi-nozzle NFES could accurately and efficiently direct-write aligned array pattern in the future.
+{\textless}-
 
-\subsection{Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\protect\cite{527120:11974307}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+\subsection{Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\protect\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\protect\cite{527120:11974328}}-{\textgreater} Direct writing of hierarchical micro/nano fibers have recently gained popularity in flexible/stretchable electronics due to its low cost, simple process and high throughput.
+A kinetically controlled mechanoelectrospinning (MES) is developed to directly write diversified hierarchical micro/nano fibers in a continuous and programmable manner.
+Unlike conventional near-field electrospinning, our MES method introduces a mechanical drawing force, to simultaneously enhance the positioning accuracy and morphology controllability.
+The MES is predominantly controlled by the substrate speed, the nozzle-to-substrate distance, and the applied voltage.
+As a demonstration, smooth straight, serpentine, self-similar, and bead-on-string structures are direct-written on silicon/elastomer substrates with a resolution of 200 nm.
+It is believed that MES can promote the low-cost, high precision fabrication of flexible/stretchable electronics or enable the direct writing of the sacrificial structures for nano scale lithography.
+
+AC pulse-modulated electrohydrodynamic direct-writing (EDW) was utilized to direct-write orderly micro/nano fibrous structure on the flexible insulating polyethylene terephthalate (PET) substrate.
+During the EDW process, AC electrical field induced charges to reciprocate along the jet and decreased the charge repulsive force that applied on charged jet.
+Thanks to the smaller charge repulsive force, stable straight jet can be built up to direct-write orderly micro/nano fibrous structures on the insulating substrate.
+The minimum motion velocity required to direct-write straight line fibrous structure on insulating PET substrate was 700 mm/s.
+Moreover, the influences of AC voltage amplitude, frequency, and duty cycle ratio on the line width of fibrous structures were investigated.
+This work proposes a novel solution to overcome the inherent charge repulsion emerging on the insulating substrate, and promotes the application of EDW technology on the flexible electronics.
+[1].
+{\textless}-
+
+\subsection{Mechano-Electrospinning \unskip~\protect\cite{527120:11974304}}-{\textgreater} A mechano-electrospinning method is presented to direct-write oriented nano fiber with high deposition accuracy in continuously tunable manner.
+This method uses a large nozzle to deposit high-resolution fiber-arrays by near-field localization.
+Due to the existence of mechanical drawing force, a higher resolution pattern can be direct-written by a lower voltage, which just keeps the Taylor cone stable.
+Then the fiber is stretched through a moving substrate, by which the deposited fiber can be continuously tuned from 400nm to 200nm in a linear relation- ship.
+The effects of the speed on the diameter and morphology of fibers are studied, and the analysis of the mechanism of the fiber alignment is given.
+The positionability and controllability make mechano-electrospinning very different from the traditional electrospinning, which only collects the fibers in the form of nonwoven fabric.
+In addition, the fibers fabricated by this method can directly deposit over a large flat area in the form of arrays and complex patterns with high precision.
+{\textless}-
+
+\subsection{Suspension NFES \unskip~\protect\cite{527120:12033656}}-{\textgreater} Near-field electrospinning (NFES) is widely recognized as a versatile nano fabrication method, one suitable for applications in tissue engineering.
+Rapid developments in this field have given rise to layered nano fibrous scaffolds.
+However, this electrostatic fabrication process is limited by the electric field inhibitory effects of polymer deposition.
+This leads to a major challenge: how to surpass this limitation on planar/layered constructs.
+While the current focus in this area largely lies with the investigation of new materials, techniques and increasing precision of NFES systems and patterning, exploration of complex collector substrates is often restricted by (i) available technology and (ii) access to complex electrode manufacturing tools.
+To achieve nano fiber arrays suspended in free space, this paper documents both the development of an integrated NFES system and the potential of standing electrodes manufactured via selective laser melting.
+This system was first tested by 2D patterning on planar silicon, using polyethylene oxide polymer solution.
+To demonstrate suspension NFES, two patterns operating within and around the standing electrodes produced high volume suspended nano arrays.
+Image analysis of the arrays allowed for the assessment of fiber directionality and isotropy.
+By scanning electron microscopy, it was found that a mean fiber diameter of 310 nm of the arrays was achieved.
+Effectively maneuvering between the electrode pillars required a precision automated system (unavailable off-the-shelf), developed in-house.
+This technique can be applied to the fabrication of nano fiber structures of sufficient volume for tissue engineering.
+{\textless}-
+
+\subsection{Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\protect\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\protect\cite{527120:11974320}}-{\textgreater} Micro/nano serpentine structures have widespread applications in flexible/stretchable electronics; however, challenges still exist for low-cost, high-efficiency and controllable manufacturing.
+Helix electrohydrodynamic printing (HE-printing) has been proposed here to realize controllable direct-writing of large area, highly aligned serpentine micro/nano fibers by introducing the rope coiling effect into printing process.
+By manipulating the flying trajectory and solidification degree of the micro/nano jet, the solidified micro/nano fiber flying in a stabilized helical manner and versatile serpentine structures deposited on a moving collector have been achieved.
+Systematic experiments and theoretical analysis were conducted to study the transformation behavior and the size changing rules for various deposited micro structures, and highly aligned serpentine microfibers were directly written by controlling the applied voltage, nozzle-to-collector distance and collector velocity.
+Furthermore, a hyper-stretchable piezoelectric device that can detect stretching, bending and pressure has been successfully fabricated using the printed serpentine micro/nano fibers, demonstrating the potential of HE-printing in stretchable electronics manufacturing.
+
+Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine noz- zle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity.
+In this article, the EHD jet printing system is utilized to print patterns of polystyrene (PS) nano fibers.
+The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano fibers was investigated.
+The EHD jet printing technology is further utilized to print various patterns of polydiacetylene (PDA)-embedded PS nano fibers.
+The EHD jet printing based nano fiber printing is advantageous over conventional electrospining based approaches in terms of patterned PDA images.
+In addition, an advanced EHD jet printing system which is adopted for aligned nano fiber printing will expand the application of nano fibers from bio and chemical sensors to tissue engineering and electronics.
+{\textless}-
+
+\subsection{Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\protect\cite{527120:11974312}}-{\textgreater} Electrohydrodynamic direct-writing (EDW) is a developing technology for high-resolution printing.
+How to decrease the line width and improve the deposition accuracy of direct-written patterns has been the key to the promotion for the further application of EDW.
+In this paper, an airflow-assisted spinneret for electrohydrodynamic direct-writing was designed.
+An assisted laminar airflow was introduced to the EDW process, which provided an additional stretching and constraining force on the jet to reduce the surrounding interference and enhance jet stability.
+The flow field and the electric field around the spinneret were simulated to direct the structure design of the airflow-assisted spinneret.
+Then, a series of experiments were conducted, and the results verified the spinneret design and demonstrated a stable ejection of jet in the EDW process.
+With assisted airflow, the uniformity of printed patterns and the deposition position accuracy of a charged jet can be improved.
+Complex patterns with positioning errors of less than 5\% have been printed and characterized, which provide an effective way to promote the integration of micro/nano systems.
+{\textless}-
+
+\subsection{Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\protect\cite{527120:11974307}}-{\textgreater} Although electrospinning (ES) allows the production of unsurpassed nano scale polymer fibers, the major draw- \mbox{}\protect\newline backs are the nozzle-clogging and single-jet spinneret, respectively.
+This is a real limitation in terms of usable polymers and for patterning active organics.
+Nowadays the micro-engineering of smart materials could represent a new route for many fields of technology ranging from the production of electronic and photonic devices [1\ensuremath{-}3] to regenerative medicine and tissue engineering.
+[4\ensuremath{-}7] An enormous technological interest is related to the possibility of patterning fibers directly in well-ordered patterns avoiding the deposition of nonwoven sub micrometer mats often occurring in ES.
+[8,9] In the past decade several attempts have been made using field- induced [10\ensuremath{-}13] and near-field ES, [14,15] but only very recently, with the introduction of mechano ES, [16] has the production of well- ordered fiber patterns been achieved.
+Nevertheless, some drawbacks related to the complexity of the setup, the operating temperature, and the selection of usable materials for problems related to nozzle clogging still persist.
+Moreover, high temperature can cause deterioration of the optical and electronic properties of active organic materials eventually embedded in the functionalize [d fibers.
+On the other side, interfering effects due to closeness of multiple electrified nozzles ban working with multiple spinnerets.
+Here we introduce a revolutionary nozzle-free approach, the tethered pyro-electrodynamic spinning (TPES) operating in wireless modality, i.e., without electric circuit, electrodes, and voltage supply.
+This novel approach definitively simplifies the ES apparatus extending the nano fiber spinning also to active organic polymers preserving at the same time all the properties of conventional systems.
+Fiber drawing from the liquid polymer is driven through the pyroelectric charge generated into a ferro-electric crystal (i.e., LiNbO3) able to induce the electro- hydrodynamics (EHD) pressure required for polymer manipulation without wires.
+The approach is highly flexible, simple, compact, and cost-effective when compared with classical ES, and last but not least, it allows working safely, avoiding the use of high-voltage equipment at kV scale.
+For the first time, in site observation of fiber drawing is provided allowing real-time adjustments and full control of the process.
+Moreover, the TPES adds to the capabilities of conventional ES the chance of printing polymer fibers even in the case of multiple drops opening the way to the multi jetting spinneret modality for multiplexing and speeding up the fabrication process.
+Printing of micro- and nano fibers directly from a polymer drop with unprecedented order, direct writing of sharp/straight edges, and easy multi jets electrospinning are demonstrated and reported.
+Experimental fabrication of patterns embedded with active molecules ensures that functionalized patterns preserve their functionalities after the TPES process.
+Results regarding the use of smart patterns for keeping alive and viable cultured cells are discussed.
+This study opens the way to innovative optogenesys analysis, guiding light for generating or trans- porting optical/electronic signals from and to cells.
+[17\ensuremath{-}21] The setup proposed in this work, unlike the conventional ES, is electrode-free and nozzle-free {\textless}-
 
@@
 However, in separate studies by Pan et al.\unskip~\cite{527120:11974317,527120:12321129} using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
-\begin{table*}[!htbp]
+\begin{table}[!htbp]
 \caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
@@
 \end{tabulary}\par 
-\end{table*}
+\end{table}
 
@@
 However, it should be noted that there will be some interactions between the solvent and polymer molecules in the solution and the metal surface of the spinneret.
-There will exist some attractive forces between the polar groups in the polymer and the electropositive metal surface, which can act counter to the drawing force of the electric field and can pull the polymer solution back into the spinneret.
+There will exist some attractive forces between the polar groups in the polymer and the electro positive metal surface, which can act counter to the drawing force of the electric field and can pull the polymer solution back into the spinneret.
 It has been found that coating the spinneret exterior in a non-conductive and non-stick polymer such as Teflon can reduce these interactions.\unskip~\cite{527120:13082768} As a result, the electrical energy can be more efficiently used to elongate and narrow the polymer jet, and narrower fibers can be produced.
@@
 \egroup
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 

### 2020-03-14 myPapers/NFES_Review/Polymers_for_Nearfield_Electrospinning_with_Spatial_Control/article.tex
organising my directories ...

--- 2019-10-17 NFES_Review/Polymers_for_Nearfield_Electrospinning_with_Spatial_Control-2019-10-17-15-16/article.tex
@@
 %text-layout: twocolumn
-%endfloat: placeins
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
           \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
-\usepackage[section]{placeins}
-
 \usepackage{etoolbox}
 
-\usepackage{longtable}
-
 \usepackage{float}
-
-\makeatletter
-\AtBeginDocument{\@ifpackageloaded{rotating}{\PassOptionsToPackage{figuresright}{rotating}}{\usepackage[figuresright]{rotating}}\setlength{\rotFPtop}{0pt plus 1fil}\setlength{\rotFPbot}{0pt plus 1fil}}
-\makeatother
-
-\makeatletter
- \AtBeginDocument{%
-  \@ifpackagewith{endfloat}{figuresonly}
-  {\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}}%true
-  {\@ifpackagewith{endfloat}{tablesonly}{\DeclareDelayedFloatFlavor{sidewaystable}{table}\DeclareDelayedFloatFlavor{longtable}{table}\DeclareDelayedFloatFlavor{landscape}{table}}%true
-  {\@ifpackageloaded{endfloat}{\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}\DeclareDelayedFloatFlavor{sidewaystable}{table}\DeclareDelayedFloatFlavor{longtable}{table}\DeclareDelayedFloatFlavor{landscape}{table}}{}}%false
-  }%false
-  }
-\makeatother
-
-\usepackage{pdflscape}
 
@@
 \bgroup
-\fixFloatSize{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}
+\fixFloatSize{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}
 \begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}{\includegraphics{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}}{}
+\centering \makeatletter\IfFileExists{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}{\includegraphics{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}}{}
 \makeatother 
@@
 The apparatus used by Brown et al.
-\unskip~\cite{527120:13445499} is depicted in .
+\unskip~\cite{527120:13445499} is depicted in Figure~\ref{f-1e9a6ae11444}.
 
-[TODO: draw an apparatus used for melt electrospinning].
-
+\bgroup
+\fixFloatSize{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}{\includegraphics{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}}{}
+\makeatother 
+\caption{{Typical Melt Electrospinning Setup}}
+\label{f-1e9a6ae11444}
+\end{figure}
+\egroup
 Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.
@@
 
-\subsection{Dispensing nozzle}Coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle [TODO: draw nested needles].
+\subsection{Dispensing nozzle}Coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle, see Figure~\ref{f-e0d8f2eb18d4}.
 \unskip~\cite{527120:13914792,527120:13914793} The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers.
@@
 
+\bgroup
+\fixFloatSize{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}{\includegraphics{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}}{}
+\makeatother 
+\caption{{Needle configurations in coaxial electrospinning. (a) the outer needle encasing the inner; (b) the inner needle protruding from the outer; (c) both needles inline with each other;}}
+\label{f-e0d8f2eb18d4}
+\end{figure}
+\egroup
 Some advantages that co-electrospinning setups can offer include the preempting the initial jet burst from the spinneret nozzle.
@@
 
+\bgroup
+\fixFloatSize{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}{\includegraphics{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}}{}
+\makeatother 
+\caption{{Typical setup used in pressurized gyration Processes}}
+\label{f-7cf6ac702e28}
+\end{figure}
+\egroup
 The centrifugal force technique is applied to polymer solutions and melts.
@@
 The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate.
-Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}.
+Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}, see Figure~\ref{f-92361290d8c3} .
 
-[TODO: draw an apparatus used for solution blow spinning or melt blowing] \unskip~\cite{527120:13538056}.
-
+\bgroup
+\fixFloatSize{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}{\includegraphics{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}}{}
+\makeatother 
+\caption{{Dispensing nozzle used for solution blow spinning or melt blowing. \unskip~\protect\cite{527120:13538056}}}
+\label{f-92361290d8c3}
+\end{figure}
+\egroup
 Poly(lactic acid) (PLA) fibers have been produced by solution blow spinning.
@@
 
-[TODO: draw Figure apparatus used for solution blow spinning or melt blowing]
-
-\subsubsection{Mechanical force}Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette.
+\subsubsection{Mechanical force}
+\bgroup
+\fixFloatSize{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}{\includegraphics{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}}{}
+\makeatother 
+\caption{{Typical mechanical fiber drawing process}}
+\label{f-432d16f420fb}
+\end{figure*}
+\egroup
+Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette.
 \unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical applications.
-\unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers.
-Touch-spinning comprises a rotating stage with an embedded glass rod.
-[TODO: draw touch spinning setup].
+\unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers where the fiber is created by stretching the polymer precursor with a moving collector, as depicted in Figure~\ref{f-432d16f420fb}.
+Touch-spinning comprises a moving stage with an embedded glass rod (Figure~\ref{f-f17259e76303}).
 Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers.
@@
 
+\bgroup
+\fixFloatSize{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}{\includegraphics{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}}{}
+\makeatother 
+\caption{{Touch-spinning technique.
+First rod is attached to a rotating stage and a polymer solution droplet is administrated through a needle.
+Then the rotating rod 'touches' the polymer precursor.
+Finally, as the rod rotates, the polymer solution is stretched and creates a fiber between the rod and the needle.}}
+\label{f-f17259e76303}
+\end{figure*}
+\egroup
 The touch spinning technique implies that the fiber diameter can be controlled by the rotation speed and the polymer solution concentration.
@@
 
-[TODO: draw Figure apparatus used for microfluidic spinning]
-
+\bgroup
+\fixFloatSize{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}{\includegraphics{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}}{}
+\makeatother 
+\caption{{Microfluidic device used by Kang et al.\unskip~\protect\cite{527120:13656548}}}
+\label{f-c0beae2757bf}
+\end{figure}
+\egroup
 Microfluidic techniques offer the possibility to embed several components into a single fiber, where each component can be released at different parts of the fiber.
 
-\subsection{Nozzle-to-substrate distance}[TODO: draw FFES setup], depicts the typical setup for the conventional far-field electrospinning (FFES).
+\subsection{Nozzle-to-substrate distance}
+\bgroup
+\fixFloatSize{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}{\includegraphics{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}}{}
+\makeatother 
+\caption{{a) Typical Far-field Electrospinning (FFES) Setup. b) Typical Near-field Electrospinning (NFES) Setup.}}
+\label{f-fbe88d27b932}
+\end{figure*}
+\egroup
+Figure~\ref{f-fbe88d27b932}.a, depicts the typical setup for the conventional far-field electrospinning (FFES).
 As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}.
@@
 In the intent to achieve controlled fiber deposition, Sun et al.
-\unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES).
-[TODO: draw NFES setup], describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line.
+\unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES),Figure~\ref{f-fbe88d27b932}, describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line.
 Moreover, some mechanical influence is required to deposit fibers precisely.
@@
 
-\bgroup
-\fixFloatSize{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}{\includegraphics{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}}{}
-\makeatother 
-\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130}.}}
-\label{f-8e5a75d9ba17}
-\end{figure}
-\egroup
-
 \section{Properties that Improve Accuracy of Nano-Fiber Deposition}
@@
 This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
+Table S1 is a collection of the relevant NFES process parameters and achieved fiber morphology.
 
-\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES.
+Some differences have been discovered between LV-NFES and conventional NFES.
 Low voltage near field electrospinning produces thinner fibers with lower voltages.
@@
 
--{\textgreater} A continuous method for controlled electrospinning of polymeric nano fibers on two-dimensional (2D) and three-dimensional (3D) substrates using low voltage near-field electrospinning (LV NFES).
-The method overcomes some of the drawbacks in more conventional near-field electrospinning by using a super elastic polymer ink formulation.
-The visco-elastic nature of our polymer ink enables continuous electrospinning at a very low voltage of 200 V, almost an order of magnitude lower than conventional NFES, thereby reducing bending instabilities and increasing control of the resulting polymer jet.
-In one application, polymeric nano fibers are freely suspended between micro structures of 3D carbon on Si substrates to illustrate wiring together 3D components in any desired pattern.{\textless}-
+Bisht et al.
+\unskip~\cite{527120:11973130} reports a controlled technique to fabricate polymeric nano fibers in a continuous manner, using a low voltage setup.
+Their purpose is to find a workaround to the drawbacks of traditional NFES by using a superelastic polymer precursor, which allow continuous patterning without breaking.
+In low voltage near-field electrospinning (LV NFES), a visco-elastic polymer is used to allow continuous spinning at about 200$V $ .
+The decrease in voltage is prone to produce a controlled polymer jet by reducing the bending instabilities.
+The authors demonstrate the effectiveness of this technique with the fabrication of suspended fibers, see Figure~\ref{f-52c94fbe4526} .
 
-\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}-{\textgreater} A continuous near-field electrospinning (NFES) process has been developed to deposit solid nano fibers with orderly patterns over large areas.
-Before the onset of electrospinning, a bias voltage is applied to a semi-spherical shaped polymer droplet outside of a syringe needle, and a probe tip mechanically draws a single fiber from the droplet to initiate continuous NFES.
-Contrary to the conventional electrospinning process, we show that decreasing electrical field in continuous NFES results in smaller line width deposition, and nano fibers can be assembled into controlled complex patterns such as circular shapes and grid arrays on large and flat areas.
-{\textless}-
+\bgroup
+\fixFloatSize{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}{\includegraphics{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}}{}
+\makeatother 
+\caption{{Suspended nano fibers of 2 wt \% PEO at 300 V.
+(a) Six carbon posts connected by nano fibers.
+(b) Individual nano fiber suspended between the posts.
+(c) Close up of the suspended nano fiber.
+\unskip~\protect\cite{527120:11973130}}}
+\label{f-52c94fbe4526}
+\end{figure*}
+\egroup
+Chang et al.
+\unskip~\cite{527120:11974306} developed a scanning tip electrospinning (a continuous NFES) technique to write nano fibers with control patterning.
+Similar to Bisht et al.
+\unskip~\cite{527120:11973130}, they also demonstrate that the decrease in the applied electric field yields thinner fibers that can be controlled to develop circular shapes (Figure~\ref{f-9d0c3125e550}) and grids (Figure~\ref{f-32e7d8abb3aa}) on a flat surfaces.
 
-\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}-{\textgreater} Characterized the behavior of polymer jet from near-field electrospinning onto the ink-jet patterned paper with conductive Ag nano particles in order to form the controlled three-dimensional nano structures.
-Using ink-jet patterned paper with conductive ink as a collector, the polymer jet is induced to the pre patterned shape through the concentrated electric field caused by singularity between the spinneret and the printed patterns.
-Due to the electric field enhancement of the deposited electrospun fiber, an additionally spun fiber can be stacked on the deposited fibers directly.
-Therefore, the controlled three-dimensional nano/micro structures can be successfully realized by the proposed method.
-We characterized the deposition of the electrospun fiber according to the distance between the ink-jet printed pattern and the spinneret.
-In addition, the sharp edged three-dimensional micro-structures were fabricated by carrying out the electrospinning on the patterns with various angled edges.
-A CCD camera was used to observe the behavior of the polymer jet, and the SEM image was analyzed to confirm that the fibers are stacked as desired.
+\bgroup
+\fixFloatSize{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}{\includegraphics{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}}{}
+\makeatother 
+\caption{{The three-character Cal is drawn on a silicon chip by a programmable x-y stage. \unskip~\protect\cite{527120:11974306}}}
+\label{f-9d0c3125e550}
+\end{figure}
+\egroup
 
-Uncover a new method for the preparation of bio-polymer scaffolds and demonstrate its potential for the development of organs with the aid of tissue engineering.
-Two novel nano-composite polymers, a non-biodegradable polyhedral oligomeric silsesquioxane-poly (carbonate-urea)urethane and a biodegradable polyhedral oligomeric silsesquioxane-polycaprolactone-poly(carbonate-urea)urethane, have been subjected to flow in an electric field.
-Electrically forced micro-threading of the polymers occurs and a three-dimensional print-patterning device was used to deposit fine (⬍50 \ensuremath{\mu}m) threads of polymer according to a pre-designed architecture to prepare scaffolds.
-The technique can offer tremendous potential in the development of organs.
-{\textless}-
+\bgroup
+\fixFloatSize{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}{\includegraphics{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}}{}
+\makeatother 
+\caption{{A triangular grid pattern. \unskip~\protect\cite{527120:11974306}}}
+\label{f-32e7d8abb3aa}
+\end{figure}
+\egroup
+Kim et al.
+\unskip~\cite{527120:11974313} experimented with a NFES variation where the fiber deposition is guided by conductive rails, see Figure~\ref{f-927e96fb5537} .
+As stated by the authors, the induced electric field is enhanced by the conductive pattern, which allows the fibers to follow the desired deposition path.
+As the fibers are prone to follow the conductive pattern, additional fibers can be stacked on each other.
+The stacking process was successfully achieved in high electric field conditions at: 750$\mu m $ substrate to collector distance, and 600 $\mu m $ needle to rail (offset) distance, see  .
+(Applied voltage not explicitly specified for "straight line pattern" and stacking experiments, only stated the implementation of 1.9 $kV $ on "sharp-edged shapes pattern" experiments).
 
-\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}-{\textgreater} Multinozzle electrospinning systems are designed to increase productivity, while near-field electrospinning (NFES) systems are designed to deposit solid nano fibers in a direct, continuous, and controllable manner.
-In this paper, several multinozzle NFES setups are tested.
-The experiment reveals that the deposition distance becomes larger when working distance and needle spacing increase, and the influence of voltage is relatively weaker.
-The deposition of double nozzle NFES has been studied with Coulomb's law and theoretical derivation has been verified by the experimental conclusion.
-The experiment result and theoretical derivation are helpful to get different distance of direct-written fibers by adjusting working distance or needle spacing to change distance of fibers largely and adjusting voltage to change distance slowly.
-Through these efforts, it is convenient to adjust the distance of straight fibers in multinozzle system.
-[1]
+\bgroup
+\fixFloatSize{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}{\includegraphics{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}}{}
+\makeatother 
+\caption{{NFES setup for controlled fiber deposition on pre-patterned conductive electrodes. \unskip~\protect\cite{527120:11974313}}}
+\label{f-927e96fb5537}
+\end{figure*}
+\egroup
 
-For large area micro/nano pattern printing, multi-nozzle electrohydrodynamic (EHD) printing setup is an efficient method to boost productivity in near-field electrospinning (NFES) process.
-And controlling EHD multi-jet accurate deposition under the interaction of nozzles and other parameters are crucial concerns during the process.
-The influence and sensitivity of various parameters such as the needle length, needle spacing, electrode-to-collector distance, voltage etc.
-on the direct-write patterning performance was investigated by orthogonal experiments with dual-nozzle NFES setup, and then the deposition distance estimated based on a novel model was com- pared with measurement results and proven.
-More controllable deposition distance and much denser of aligned nano fiber can be achieved by rotating the dual-nozzle setup.
-This study can be greatly contributed to estimate the deposition distance and helpful to guide the multi-nozzle NFES process to accurate direct-write pattern in manufacturing process in the future.
+\bgroup
+\fixFloatSize{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}{\includegraphics{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}}{}
+\makeatother 
+\caption{{SEM and CCD camera images of stacked fibers on the conductive pattern when high electric field and low electric field were applied}}
+\label{f-24b5148e8358}
+\end{figure}
+\egroup
+Gupta et al.\unskip~\cite{527120:11974310} introduced a new technique to fabricate polymer scaffolds for tissue engineering applications and organ development.
+The authors implemented two polymer solutions, with POSS-PCU (polyhedral oligomeric silsesquioxane-poly(carbonate-urea)urethane, a non-biodegradable polymer precursor) and with POSS-PCL-PCU (poly- hedral oligomeric silsesquioxane-polycaprolactone-poly(carbonate- urea)urethane, a biodegradable polymer precursor).
 
-To mass-volume fabricate micro- and nano scales aligned pattern, multi-nozzle near- field electrospinning (NFES) direct-writing technology is well proposed as a high- efficiency method in electrohydrodynamic (EHD) printing process.
-However, the interference effect among adjacent nozzles and coupling effect of various parameters have restricted to investigate deposition characteristic of multi-nozzle NFES and control EHD multi-jet deposition accuracy.
-In order to improve the accuracy of EHD multi-jet deposition with high-efficiency printing process, the experimental result compared with theoretical method were discussed.
-In this work, the influence of multi-nozzle geometry distribution and electrospinning parameters on deposition characteristic was studied with multi-nozzle NFES setup, and nozzles were in linear array.
-The deposition distance and homogeneity of aligned nano fibers were measured and explained with coefficient of dispersion on electric field among nozzles by simulation.
-Moreover, deposition distance of multi-nozzle NFES process was evalu- ated by modified theoretical derivation based on our previous studies.
-The modified theoretical derivation showed a good agreement with experiment results, and indicated that multi-nozzle NFES could accurately and efficiently direct-write aligned array pattern in the future.
-{\textless}-
+As described by Gupta et al.\unskip~\cite{527120:11974310}, the fiber deposition equipment is comprised by a stainless steel needle with a internal diameter of 750 $\mu m $ , connected to a high voltage power supply of up to 30 $k V $ with a deposition rate of about $\geq 1 \mu L min^{-1} $.
+The setup was embedded to a motorized collector capable of controlled programmable motions, see Figure~\ref{f-74de1f00848b}.
+The proposed technique was able to produce fibers of $150 \mu m $ in diameter with pre-designed patterns.
 
-\subsection{Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\protect\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\protect\cite{527120:11974328}}-{\textgreater} Direct writing of hierarchical micro/nano fibers have recently gained popularity in flexible/stretchable electronics due to its low cost, simple process and high throughput.
-A kinetically controlled mechanoelectrospinning (MES) is developed to directly write diversified hierarchical micro/nano fibers in a continuous and programmable manner.
-Unlike conventional near-field electrospinning, our MES method introduces a mechanical drawing force, to simultaneously enhance the positioning accuracy and morphology controllability.
-The MES is predominantly controlled by the substrate speed, the nozzle-to-substrate distance, and the applied voltage.
-As a demonstration, smooth straight, serpentine, self-similar, and bead-on-string structures are direct-written on silicon/elastomer substrates with a resolution of 200 nm.
-It is believed that MES can promote the low-cost, high precision fabrication of flexible/stretchable electronics or enable the direct writing of the sacrificial structures for nano scale lithography.
+\bgroup
+\fixFloatSize{images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}{\includegraphics{images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}}{}
+\makeatother 
+\caption{{Schematic illustration of the electrohydrodynamic process. \unskip~\protect\cite{527120:11974310}}}
+\label{f-74de1f00848b}
+\end{figure}
+\egroup
+Wang, et al., Huang, et al., and Chen, et al.
+\unskip~\cite{527120:11974322,527120:11974323,527120:11974324} experimented with several multi-nozzle near-field electrospinning of aligned nano fibers.
+The multinozzle NFES apparatus is similar to the one used in conventional NFES with some modifications to the needle nozzle, see Figures~\ref{f-96ee25855dea} and~\ref{f-4a1a1f58a423}.
+The authors implemented similar NFES setups where the installed linear array of nozzles is supplied with a constant flow rate of solution.
 
-AC pulse-modulated electrohydrodynamic direct-writing (EDW) was utilized to direct-write orderly micro/nano fibrous structure on the flexible insulating polyethylene terephthalate (PET) substrate.
-During the EDW process, AC electrical field induced charges to reciprocate along the jet and decreased the charge repulsive force that applied on charged jet.
-Thanks to the smaller charge repulsive force, stable straight jet can be built up to direct-write orderly micro/nano fibrous structures on the insulating substrate.
-The minimum motion velocity required to direct-write straight line fibrous structure on insulating PET substrate was 700 mm/s.
-Moreover, the influences of AC voltage amplitude, frequency, and duty cycle ratio on the line width of fibrous structures were investigated.
-This work proposes a novel solution to overcome the inherent charge repulsion emerging on the insulating substrate, and promotes the application of EDW technology on the flexible electronics.
-[1].
-{\textless}-
+\bgroup
+\fixFloatSize{images/add2f32e-eac8-460d-a7ff-3d0a7b07c15f-uwang_00.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/add2f32e-eac8-460d-a7ff-3d0a7b07c15f-uwang_00.png}{\includegraphics{images/add2f32e-eac8-460d-a7ff-3d0a7b07c15f-uwang_00.png}}{}
+\makeatother 
+\caption{{Schematic of multi-nozzle near-field electrospinning system \unskip~\protect\cite{527120:11974323}}}
+\label{f-96ee25855dea}
+\end{figure}
+\egroup
 
-\subsection{Mechano-Electrospinning \unskip~\protect\cite{527120:11974304}}-{\textgreater} A mechano-electrospinning method is presented to direct-write oriented nano fiber with high deposition accuracy in continuously tunable manner.
-This method uses a large nozzle to deposit high-resolution fiber-arrays by near-field localization.
-Due to the existence of mechanical drawing force, a higher resolution pattern can be direct-written by a lower voltage, which just keeps the Taylor cone stable.
-Then the fiber is stretched through a moving substrate, by which the deposited fiber can be continuously tuned from 400nm to 200nm in a linear relation- ship.
-The effects of the speed on the diameter and morphology of fibers are studied, and the analysis of the mechanism of the fiber alignment is given.
-The positionability and controllability make mechano-electrospinning very different from the traditional electrospinning, which only collects the fibers in the form of nonwoven fabric.
-In addition, the fibers fabricated by this method can directly deposit over a large flat area in the form of arrays and complex patterns with high precision.
-{\textless}-
+\bgroup
+\fixFloatSize{images/cd8e0617-d4d9-479b-a99b-a466cd21483c-uwang_01.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/cd8e0617-d4d9-479b-a99b-a466cd21483c-uwang_01.png}{\includegraphics{images/cd8e0617-d4d9-479b-a99b-a466cd21483c-uwang_01.png}}{}
+\makeatother 
+\caption{{The geometry distribution of linear array multi-nozzle system \unskip~\protect\cite{527120:11974323}}}
+\label{f-4a1a1f58a423}
+\end{figure}
+\egroup
+The purpose of multinozzle setups is to increase productivity, and not necessarily to deposit fibers in a direct, continuous and controllable manner, since the setup itself limits the patterning design to parallel aligned fibers, as sown in Figure~\ref{f-4f1fb5cbfee6}.
+The introduction of more needle \_also\_ introduces more process parameters that have an influence in the produced fiber morphology.
+The added process parameters comprise the needle length, and needle spacing \unskip~\cite{527120:11974323}.
 
-\subsection{Suspension NFES \unskip~\protect\cite{527120:12033656}}-{\textgreater} Near-field electrospinning (NFES) is widely recognized as a versatile nano fabrication method, one suitable for applications in tissue engineering.
-Rapid developments in this field have given rise to layered nano fibrous scaffolds.
-However, this electrostatic fabrication process is limited by the electric field inhibitory effects of polymer deposition.
-This leads to a major challenge: how to surpass this limitation on planar/layered constructs.
-While the current focus in this area largely lies with the investigation of new materials, techniques and increasing precision of NFES systems and patterning, exploration of complex collector substrates is often restricted by (i) available technology and (ii) access to complex electrode manufacturing tools.
-To achieve nano fiber arrays suspended in free space, this paper documents both the development of an integrated NFES system and the potential of standing electrodes manufactured via selective laser melting.
-This system was first tested by 2D patterning on planar silicon, using polyethylene oxide polymer solution.
-To demonstrate suspension NFES, two patterns operating within and around the standing electrodes produced high volume suspended nano arrays.
-Image analysis of the arrays allowed for the assessment of fiber directionality and isotropy.
-By scanning electron microscopy, it was found that a mean fiber diameter of 310 nm of the arrays was achieved.
-Effectively maneuvering between the electrode pillars required a precision automated system (unavailable off-the-shelf), developed in-house.
-This technique can be applied to the fabrication of nano fiber structures of sufficient volume for tissue engineering.
-{\textless}-
+\bgroup
+\fixFloatSize{images/9569179c-0fea-4f46-bb0f-b3103fbd20aa-uwang_02.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/9569179c-0fea-4f46-bb0f-b3103fbd20aa-uwang_02.png}{\includegraphics{images/9569179c-0fea-4f46-bb0f-b3103fbd20aa-uwang_02.png}}{}
+\makeatother 
+\caption{{Morphology of aligned nano fibers pattern during three-nozzle NFES process.
+The experiment works in environment as electrode-to-collector distance 4.0 mm and applied voltage 2.5KV \unskip~\protect\cite{527120:11974323}}}
+\label{f-4f1fb5cbfee6}
+\end{figure}
+\egroup
+The authors came to the conclusion that the distance between the deposited fibers increase with the increase of the needle-to-collector distance, as the influence of the applied voltage dissipates.
 
-\subsection{Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\protect\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\protect\cite{527120:11974320}}-{\textgreater} Micro/nano serpentine structures have widespread applications in flexible/stretchable electronics; however, challenges still exist for low-cost, high-efficiency and controllable manufacturing.
-Helix electrohydrodynamic printing (HE-printing) has been proposed here to realize controllable direct-writing of large area, highly aligned serpentine micro/nano fibers by introducing the rope coiling effect into printing process.
-By manipulating the flying trajectory and solidification degree of the micro/nano jet, the solidified micro/nano fiber flying in a stabilized helical manner and versatile serpentine structures deposited on a moving collector have been achieved.
-Systematic experiments and theoretical analysis were conducted to study the transformation behavior and the size changing rules for various deposited micro structures, and highly aligned serpentine microfibers were directly written by controlling the applied voltage, nozzle-to-collector distance and collector velocity.
-Furthermore, a hyper-stretchable piezoelectric device that can detect stretching, bending and pressure has been successfully fabricated using the printed serpentine micro/nano fibers, demonstrating the potential of HE-printing in stretchable electronics manufacturing.
+Huang, et al.\unskip~\cite{527120:11974311} studied the mechanoelectrospinning (MES) technique for the fabrication of nano fibers.
+The MES technique tries to improve deposition accuracy by the introduction of a mechanical drawing force.
+The MES is predominantly controlled by the collector stage velocity, the nozzle-to-collector distance, and the applied voltage.
+The authors believe that MES can compete as a low-cost, high precision fabrication of electronics and enable the direct writing of structures for nano scale lithography.
+Figure~\ref{f-7587d8081ccc} shows the polymer jet behavior when a mechanical force is implemented within the NFES process.
 
-Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine noz- zle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity.
-In this article, the EHD jet printing system is utilized to print patterns of polystyrene (PS) nano fibers.
-The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano fibers was investigated.
-The EHD jet printing technology is further utilized to print various patterns of polydiacetylene (PDA)-embedded PS nano fibers.
-The EHD jet printing based nano fiber printing is advantageous over conventional electrospining based approaches in terms of patterned PDA images.
-In addition, an advanced EHD jet printing system which is adopted for aligned nano fiber printing will expand the application of nano fibers from bio and chemical sensors to tissue engineering and electronics.
-{\textless}-
+\bgroup
+\fixFloatSize{images/db7d3b35-fe08-422f-afe4-78e0133b489b-uhuang_00.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/db7d3b35-fe08-422f-afe4-78e0133b489b-uhuang_00.png}{\includegraphics{images/db7d3b35-fe08-422f-afe4-78e0133b489b-uhuang_00.png}}{}
+\makeatother 
+\caption{{schematic diagram of leap direct-writing: the ink first accumulates at contact point and then gets stretched by mechanical drawing force.
+At a critical distance, the ink leaps to the next contact point, and gets stretched again \unskip~\protect\cite{527120:11974311}}}
+\label{f-7587d8081ccc}
+\end{figure}
+\egroup
+Zheng, et al.\unskip~\cite{527120:11974328} worked the near field electrospinning process with an AC power supply, also known as AC EDW (AC Pulse-Modulated Electrodynamic Direct-Writing).
+The alternating current decreased the repulsive force applied along the jet, allowing a stable jet.
+The AC EDW was implemented to produce micro fibers on an insulated PET (Polyethylene Terephthalate) collector.
+AC EDW fibers were successfully fabricated between x-y collector velocities from 700 to 1500 $mm / s $, see Figure~\ref{f-b2c382d8b6ab}.
+Zheng's work \unskip~\cite{527120:11974328}, Studied the effects of the AC voltage amplitude, frequency and duty cycle on the obtained fiber diameters.
+Zheng, et al.\unskip~\cite{527120:11974328} arrived to three conclusions: a) The fiber diameter increases from $\sim 14 \mu m $ to $\sim 35 \mu m $ with an increase in voltage amplitude from $\sim0V $ to $\sim 3000 V $, and decreases from $\sim 35 \mu m $ to $\sim 21 \mu m $ with an increase in voltage amplitude from $\sim 3000 V $ to $\sim 4000 V $; b) The fiber diameter increases from $\sim 14 \mu m $ to $\sim 35 \mu m $ with an increase in voltage amplitude from $\sim0V $ to $\sim 3000 V $, and decreases from $\sim 35 \mu m $ to $\sim 21 \mu m $ with an increase in voltage amplitude from $\sim 3000 V $ to $\sim 4000 V $;; and c) The fiber diameter increases from $\sim 14 \mu m $ to $\sim 35 \mu m $ with an increase in voltage amplitude from $\sim0V $ to $\sim 3000 V $, and decreases from $\sim 35 \mu m $ to $\sim 21 \mu m $ with an increase in voltage amplitude from $\sim 3000 V $ to $\sim 4000 V $;.
 
-\subsection{Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\protect\cite{527120:11974312}}-{\textgreater} Electrohydrodynamic direct-writing (EDW) is a developing technology for high-resolution printing.
-How to decrease the line width and improve the deposition accuracy of direct-written patterns has been the key to the promotion for the further application of EDW.
-In this paper, an airflow-assisted spinneret for electrohydrodynamic direct-writing was designed.
-An assisted laminar airflow was introduced to the EDW process, which provided an additional stretching and constraining force on the jet to reduce the surrounding interference and enhance jet stability.
-The flow field and the electric field around the spinneret were simulated to direct the structure design of the airflow-assisted spinneret.
-Then, a series of experiments were conducted, and the results verified the spinneret design and demonstrated a stable ejection of jet in the EDW process.
-With assisted airflow, the uniformity of printed patterns and the deposition position accuracy of a charged jet can be improved.
-Complex patterns with positioning errors of less than 5\% have been printed and characterized, which provide an effective way to promote the integration of micro/nano systems.
-{\textless}-
+\bgroup
+\fixFloatSize{images/f684a658-c64f-4f11-ba18-7debcb5e9977-uzheng_00.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/f684a658-c64f-4f11-ba18-7debcb5e9977-uzheng_00.png}{\includegraphics{images/f684a658-c64f-4f11-ba18-7debcb5e9977-uzheng_00.png}}{}
+\makeatother 
+\caption{{Micro fibers on insulated PET collector under AC electrical field with varying stage velocities\unskip~\protect\cite{527120:11974304}.}}
+\label{f-b2c382d8b6ab}
+\end{figure*}
+\egroup
+Micro and nano fibers have been written using AC pulse-modulated electrospinning by Bu et al.
+with polyehtylene terephthalate (PET) as substrate\unskip~\cite{527120:11974304}.
+The AC electrical field influences the electrospinning jet.
+The alternate current tends to decrease the repulsive electrical force allowing a stable straight jet between the dispensing nozzle and the insulating PET substrate.
+As depicted inFigure~\ref{f-b2c382d8b6ab}, Bu et al.
+varied the stage velocity.
+Faster stage velocities enable the deposition of straighter fibers\unskip~\cite{527120:11974304}.
 
-\subsection{Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\protect\cite{527120:11974307}}-{\textgreater} Although electrospinning (ES) allows the production of unsurpassed nano scale polymer fibers, the major draw- \mbox{}\protect\newline backs are the nozzle-clogging and single-jet spinneret, respectively.
-This is a real limitation in terms of usable polymers and for patterning active organics.
-Nowadays the micro-engineering of smart materials could represent a new route for many fields of technology ranging from the production of electronic and photonic devices [1\ensuremath{-}3] to regenerative medicine and tissue engineering.
-[4\ensuremath{-}7] An enormous technological interest is related to the possibility of patterning fibers directly in well-ordered patterns avoiding the deposition of nonwoven sub micrometer mats often occurring in ES.
-[8,9] In the past decade several attempts have been made using field- induced [10\ensuremath{-}13] and near-field ES, [14,15] but only very recently, with the introduction of mechano ES, [16] has the production of well- ordered fiber patterns been achieved.
-Nevertheless, some drawbacks related to the complexity of the setup, the operating temperature, and the selection of usable materials for problems related to nozzle clogging still persist.
-Moreover, high temperature can cause deterioration of the optical and electronic properties of active organic materials eventually embedded in the functionalize [d fibers.
-On the other side, interfering effects due to closeness of multiple electrified nozzles ban working with multiple spinnerets.
-Here we introduce a revolutionary nozzle-free approach, the tethered pyro-electrodynamic spinning (TPES) operating in wireless modality, i.e., without electric circuit, electrodes, and voltage supply.
-This novel approach definitively simplifies the ES apparatus extending the nano fiber spinning also to active organic polymers preserving at the same time all the properties of conventional systems.
-Fiber drawing from the liquid polymer is driven through the pyroelectric charge generated into a ferro-electric crystal (i.e., LiNbO3) able to induce the electro- hydrodynamics (EHD) pressure required for polymer manipulation without wires.
-The approach is highly flexible, simple, compact, and cost-effective when compared with classical ES, and last but not least, it allows working safely, avoiding the use of high-voltage equipment at kV scale.
-For the first time, in site observation of fiber drawing is provided allowing real-time adjustments and full control of the process.
-Moreover, the TPES adds to the capabilities of conventional ES the chance of printing polymer fibers even in the case of multiple drops opening the way to the multi jetting spinneret modality for multiplexing and speeding up the fabrication process.
-Printing of micro- and nano fibers directly from a polymer drop with unprecedented order, direct writing of sharp/straight edges, and easy multi jets electrospinning are demonstrated and reported.
-Experimental fabrication of patterns embedded with active molecules ensures that functionalized patterns preserve their functionalities after the TPES process.
-Results regarding the use of smart patterns for keeping alive and viable cultured cells are discussed.
-This study opens the way to innovative optogenesys analysis, guiding light for generating or trans- porting optical/electronic signals from and to cells.
-[17\ensuremath{-}21] The setup proposed in this work, unlike the conventional ES, is electrode-free and nozzle-free {\textless}-
+\bgroup
+\fixFloatSize{images/1847814e-ac17-4b33-ba90-6fe8b7336699-unagle_00.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/1847814e-ac17-4b33-ba90-6fe8b7336699-unagle_00.png}{\includegraphics{images/1847814e-ac17-4b33-ba90-6fe8b7336699-unagle_00.png}}{}
+\makeatother 
+\caption{{Planar nano fiber patterning. Microscopy images of PEO fibers on silicon wafers at different working distances.}}
+\label{f-f259e0a97fc2}
+\end{figure}
+\egroup
+ A mechano-electrospinning technique was presented by Nagle et al.\unskip~\cite{527120:12033656} similar to the one presented in Figure~\ref{f-432d16f420fb}.
+With the implementation of a mechanical drawing force, a higher resolution nano fibrous pattern can be produced with lower voltages as the Taylor cone becomes more stable.
+Nagle et al.
+studied PEO fibers at different nozzle to collector distances.
+Evidence suggest that better patterning accuracy increases with increasing nozzle to collector distance as the solution is effectively dried\unskip~\cite{527120:12033656}.
+Near field mechano-electrospinning enables the collection of non woven fibers over large areas.
 
@@
 \bgroup
-\fixFloatSize{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}{\includegraphics{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}}{}
+\fixFloatSize{images/43f61edd-73cd-4222-830e-3333f92934e9-uimg_nfesvariants.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/43f61edd-73cd-4222-830e-3333f92934e9-uimg_nfesvariants.png}{\includegraphics{images/43f61edd-73cd-4222-830e-3333f92934e9-uimg_nfesvariants.png}}{}
 \makeatother 
@@
 \label{f-3629d3a3f9cf}
-\end{figure*}
+\end{figure}
 \egroup
@@
 NFES was carried put with precise deposition as the fibers were placed as per the desired design within the hydrophilic substrate.
-\begin{landscape}
-\makeatletter\@twocolumnfalse\makeatother
-\begingroup
-\makeatletter\if@twocolumn\@ifundefined{theposttbl}{\gdef\TwoColDocument{true}\onecolumn\onecolumn}{}\fi\makeatother \setlength\LTcapwidth{\textheight}
-\begin{longtable}{p{\dimexpr.1641\linewidth-2\tabcolsep}p{\dimexpr.13520000000000005\linewidth-2\tabcolsep}p{\dimexpr.1662\linewidth-2\tabcolsep}p{\dimexpr.46839999999999996\linewidth-2\tabcolsep}p{\dimexpr.0661\linewidth-2\tabcolsep}}
-\caption{{Electrospun Polymer Solutions - Solution and Process Parameters} }
-\label{tw-bab4042dace7}
-\def\arraystretch{1}\\\endfirsthead \hline \noalign{\vskip3pt} \noalign{\textit{Table \thetable\ continued}} \noalign{\vskip3pt} \hline \endhead \hline \noalign{\vskip3pt} \noalign{\textit{\hfill Continued on next page}} \noalign{\vskip3pt} \endfoot \endlastfoot
-\tbltoprule Polymer(s) & Solvent(s) & NFES Variant & Process Parameters and Fiber Characterization & Ref.\\
-\tblmidrule 
-Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) &
-  Deionized water &
-  Low-Voltage NFES (LV NFES) &
-  \textbf{Solution Concentration:} 1, 2, and 3 $wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 27 gauge type 304; stainless steel needle \mbox{}\protect\newline \textbf{Solution deposition rate:} lower than 1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Pyrolyzed SU-8 carbon and Si \mbox{}\protect\newline \textbf{Applied voltage: }polymer jet initiated at 400-600 $V $ and dispensed at 200-400 $V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10-40$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 50-425$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11973130}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000 $g/mol $) with Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  acetonitrile toluene mixture (65/35); acetic acid toluene (17/83); pure toluene &
-  Typical NFES process &
-  \textbf{Solution Concentration:} \mbox{}\protect\newline 10$mg $ of MEH-PPV in 2$mL $ of toluene; 500$\mu L $ of MEH-PPV solution with 250$mg $ of PEO in 3.5$mL $ of acetonitrile / toluene (65 / 35); 500$\mu L $ of MEH-PPV solution with 250$mg $ of PEO in 3$mL $ of acetic acid / toluene (17 / 83).
-The resulting MEH-PPV/PEO concentration is 0.08 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} mm-diameter tip Tungsten spinneret in a 26 gauge needle \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} SiO2/Si (oxide thickness = 800 nm) \mbox{}\protect\newline \textbf{Applied voltage:} around 1.3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 100$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} around 100$\mu m $ &
-  \unskip~\cite{527120:11974305}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MV = 300,000 $g/mol $) &
-  Water &
-  Scanning Tip Electrospinning and NFES &
-  \textbf{Solution Concentration:} 7$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 200$\mu m $ and inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 1.5 $kV $ and dispensed at 600$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 120$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 709$\pm $131$nm $; 49-74$nm $ when applied voltage is 800$V $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{ Not determined} \mbox{}\protect\newline \textbf{Notes:} 108$m $ yield in 15$min $ with a fiber diameter of 709$\pm $131$nm $ &
-  \unskip~\cite{527120:11974306}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(vinylidine fluorid) (PVDF; MW = 440,000 $g/mol $) &
-  N,N Dimethylformamide (DMF) &
-  Helix Electrohydro-dynamic Printing (HE-printing) &
-  \textbf{Solution Concentration:} 1.8$g $ PVDF in 4.1$g $ of DMF and 4.1$g $ of acetone.
-The resulting concentration is 18\% PVDF.
-\mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 510$\mu m $ and inner diameter of 260$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 400$nL/min $ \mbox{}\protect\newline \textbf{Nozazle-to-substrate distance:} 10-50$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Poly(dimethylsiloxane) (PDMS) on Ecoflex \mbox{}\protect\newline \textbf{Applied voltage:} 1.5{\textendash}3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0-400$mm/min $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 1.5-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974308}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Polyhedral Oligomeric Silsesquioxane-Poly(Carbonate-Urea)Urethane (POSS-PCU) and Polyhedral Oligomeric Silsesquioxane Poly(Caprolactone-Poly(Carbonate-Urea)Urethane) (POSS-PCL-PCU) \mbox{}\protect\newline (Dry Polycarbonate MW = 2000 $g/mol $) &
-  Dimethyl acetamide (DMAC) and 1-Butanol &
-  Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting &
-  \textbf{Solution Concentration: }POSS-PCU and POSS-PCL-PCU used in 20\%$w/w $ concentration in DMAC \mbox{}\protect\newline \textbf{Nozzle:} needle of 750 $\mu m $ in diameter \mbox{}\protect\newline \textbf{Solution deposition rate:} less than 1$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: }about between 500$\mu m $ to 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 8.0-10.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5-50$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }250$\mu m $ &
-  \unskip~\cite{527120:11974310}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Distilled water &
-  Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) &
-  \textbf{Solution Concentration:} 6$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} 1200$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 7.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 2 $kV $ and dispensed at 0.8-1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} around 400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 200-350$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 5$\mu m $ &
-  \unskip~\cite{527120:11974311}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Deionized water and ethanol with a volume ratio of 3:1 &
-  Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) &
-  \textbf{Solution Concentration:} 8$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Outer airflow passage diameter: 1$mm $ Airflow gas pump pressure: 25$kPa $ Inner liquid passage diameter: 0.21$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 30$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Silicon \mbox{}\protect\newline \textbf{Applied voltage:} about 2$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 1-20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 3.73 $\pm $ 1.37$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }5.13 $\pm $ 6.67$\mu m $ &
-  \unskip~\cite{527120:11974312}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(Vinylidene Fluoride) (PVDF; MW = 534,000 $g/mol $) &
-  Acetone and Dimethyl Sulfoxide (DMSO) &
-  3D Electrospinning &
-  \textbf{Solution Concentration:} 17$wt\% $ PVDF; 1.7$g $ of PVDF, 5$g $ of acetone, 0.5$g $ of Capstone FS-66, 5$g $ of DMSO \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 14$\;nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 750$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} A4 size commercial printing paper (Double A) \mbox{}\protect\newline \textbf{Applied voltage:} 1.9$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974313}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(9-Vinyl Carbazole) (PVK; MW = 1,100,000 $g/mol $) &
-  Styrene &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 3.96$wt\% $ PVK in styrene \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 500$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} around 2.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Si/SiO2 \mbox{}\protect\newline \textbf{Applied voltage:} 3-4$kV $ \mbox{}\protect\newline x-y stage velocity: 13.3$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 289.26 $\pm $ 35.37$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }50$\mu m $ \mbox{}\protect\newline \textbf{Notes:} 15$m $ yield in 2$min $ &
-  \unskip~\cite{527120:11974316}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Polystyrene (PS; MW \textit{Not determined}) &
-  1,2,4-Trichloro benzene &
-  Electrohydro-dynamic (EHD) jet printing &
-  \textbf{Solution Concentration:} 1 to 5$wt\% $ PS \mbox{}\protect\newline \textbf{Nozzle:} Glass nozzle inner diameter of 2$\mu m $ and outer diameter of 2.66$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance}: 20, 30, 40$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition: }Si \mbox{}\protect\newline \textbf{Applied voltage:} 500 to 400$V $ in 25$V $ increments \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.01-10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 60-170$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974320}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  \textit{Not determined} &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} Si \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 25$\mu m $ &
-  \unskip~\cite{527120:11974321}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
-  Distilled water &
-  Multinozzle NFES &
-  \textbf{Solution Concentration:} 5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} four-nozzle and six-nozzle array with needle spacing changes from 1.5$mm $ to 3.5$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 1-3$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 1.7-2.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.47$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 3-5 $mm $ &
-  \unskip~\cite{527120:11974322}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
-  Distilled water &
-  Multinozzle NFES &
-  \textbf{Solution Concentration:}5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 0.18$mm $ and outer diameter of 0.36$mm $; with needle spacing changes from 2.0$mm $ to 3.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 3.0-4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition: } \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 2.0-3.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 218-326$\mu m $ &
-  \unskip~\cite{527120:11974323}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
-  Distilled water &
-  Multinozzle NFES &
-  \textbf{Solution Concentration:}5 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 180$\mu m $ and outer diameter of 360$\mu m $; with needle spacing changes of 2.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} chromium-plated glass \mbox{}\protect\newline \textbf{Applied voltage:} 2.5$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 2.3002-2.7224$mm $ &
-  \unskip~\cite{527120:11974324}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) &
-  \textit{Not determined} &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &
-  \unskip~\cite{527120:11974325}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Gelatin \mbox{}\protect\newline (porcine skin; MW \textit{Not determined}) &
-  Acetic Acid and Ethyl Acetate &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &
-  \unskip~\cite{527120:11974326}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Water/Ethanol (v/v = 60/40) &
-  Typical NFES process &
-  \textbf{Solution Concentration:} PEO concentrations of 16\% and 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974327}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Water/Ethanol (v/v = 3/1) &
-  Electrohydro-dynamic Direct-Write (EDW) &
-  \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless needle with inner diameter of 210$\mu m $ and outer diameter of 400$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L/h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(ethylene terephthalate) (PET) \mbox{}\protect\newline \textbf{Applied voltage:} 3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 700$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 15-35$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 70$\mu m $ &
-  \unskip~\cite{527120:11974328}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Deionized water &
-  Mechano-Electrospinning &
-  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless steel nozzle with inner diameter of 160$\mu m $ and outer diameter of 310$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2-5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicone \mbox{}\protect\newline \textbf{Applied voltage:}polymer jet initiated at 2$kV $ and dispensed at 1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 200-400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} from 344$\pm $32 to 214$\pm $27$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974304}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(co-Glycolic) acid (PLGA; MW \textit{Not determined})  &
-  Dimethyl Carbonate (DMC) &
-  Tethered Pyro-Electrohydro-dynamic Spinning (TPES) &
-  \textbf{Solution Concentration:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle:} nozzle-free \mbox{}\protect\newline \textbf{Solution deposition rate:} The drop reservoir is placed directly on a flat substrate \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} Taylor's cone is focused and put in direct contact with the collector \mbox{}\protect\newline \textbf{Substrate composition:} Poly(tetrafluoroethylene) (PTFE) coated glass slide \mbox{}\protect\newline \textbf{Applied voltage:} pyro-electric field of between 2.7 $x10^{7}\;V/m $ and 5.5$x10^{7}\;V/m $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 304.7$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974307}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) with Tetrabutylammonium tetrafluoroborate (TBF; MW \textit{Not determined}) and SU-8 2002 &
-  N,N Dimethylformamide (DMF) &
-  Typical NFES process &
-  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline $\mu m $$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} \textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:12033655}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; 200,000 $g/mol $) &
-  Water:Ethanol (3:2) &
-  Suspension NFES &
-  \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} stainless steel needle (25 G) with inner diameter of 0.25$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 3$nL/s $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} between 0.5 and 10$mm $ with 0.5$mm $ increments \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon electrodes \mbox{}\protect\newline \textbf{Applied voltage:} 1.6$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50, 150, and 250$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 0.1 and 0.5$mm $ &
-  \unskip~\cite{527120:12033656}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 400,000 $g/mol $) &
-  Deionized water &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &
-  \unskip~\cite{527120:12033657}\\
-\tblbottomrule 
-\end{longtable}
-\endgroup
-\makeatletter\@ifundefined{TwoColDocument}{}{\twocolumn}\makeatother 
-\end{landscape}
 
 \section{Conclusion}
+Helix electrodynamic printing (HE-printing) was presented by Duan et al.
+\unskip~\cite{527120:11974308} with the intention of depositing aligned fibers.
+The authors fabricated a stretchable piezoelectric device using micro and nano fibers to demonstrate the possible applications of HE-printinh for electronics manufacturing.
+Duan et al.
+concluded that the fiber morphology is mainly driven by: the stage velocity, the applied voltage, and the nozzle-to-collector distance.
 
 \bgroup
-\fixFloatSize{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}
+\fixFloatSize{images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}
 \begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}{\includegraphics{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}}{}
+\centering \makeatletter\IfFileExists{images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}{\includegraphics{images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}}{}
 \makeatother 
-\caption{{Applied volage vs. Fiber diameter}}
+\caption{{}}
+\label{f-30543905e028}
+\end{figure*}
+\egroup
+
+\bgroup
+\fixFloatSize{images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}{\includegraphics{images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}}{}
+\makeatother 
+\caption{{}}
 \label{f-59ed68f95344}
@@
 \bgroup
-\fixFloatSize{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}
+\fixFloatSize{images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}
 \begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}{\includegraphics{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}}{}
+\centering \makeatletter\IfFileExists{images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}{\includegraphics{images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}}{}
 \makeatother 
-\caption{{Solution concentration vs. Fiber diameter}}
-\label{f-0ba4df766d66}
+\caption{{}}
+\label{f-51afaccaf109}
 \end{figure*}
@@
 \bgroup
-\fixFloatSize{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}
+\fixFloatSize{images/6bd5e441-92a9-4f82-856d-85b3a7ada5ff-uplt_nozzlediameter_vs_polymerconcentration.png}
 \begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}{\includegraphics{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}}{}
+\centering \makeatletter\IfFileExists{images/6bd5e441-92a9-4f82-856d-85b3a7ada5ff-uplt_nozzlediameter_vs_polymerconcentration.png}{\includegraphics{images/6bd5e441-92a9-4f82-856d-85b3a7ada5ff-uplt_nozzlediameter_vs_polymerconcentration.png}}{}
 \makeatother 
-\caption{{Solution concentration vs. Molecular weight}}
-\label{f-ab38f7e015f7}
+\caption{{}}
+\label{f-47bf72d21b5d}
 \end{figure*}
@@
 
+\bgroup
+\fixFloatSize{images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}{\includegraphics{images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}}{}
+\makeatother 
+\caption{{}}
+\label{f-5f453fad619f}
+\end{figure*}
+\egroup
+
+\bgroup
+\fixFloatSize{images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}{\includegraphics{images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}}{}
+\makeatother 
+\caption{{}}
+\label{f-d977f56a0782}
+\end{figure*}
+\egroup
+
+\bgroup
+\fixFloatSize{images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}{\includegraphics{images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}}{}
+\makeatother 
+\caption{{}}
+\label{f-08e527ddef81}
+\end{figure*}
+\egroup
+
+\bgroup
+\fixFloatSize{images/42209168-f90a-4aaa-a235-c9049fb5bb59-uplt_solutiondepositionrate_vs_polymerconcentration.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/42209168-f90a-4aaa-a235-c9049fb5bb59-uplt_solutiondepositionrate_vs_polymerconcentration.png}{\includegraphics{images/42209168-f90a-4aaa-a235-c9049fb5bb59-uplt_solutiondepositionrate_vs_polymerconcentration.png}}{}
+\makeatother 
+\caption{{}}
+\label{f-232ba077005e}
+\end{figure*}
+\egroup
+Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine nozzle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity.
+The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano fibers was investigated.
+
 \section{NFES Achievements \& Challenges}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Near-field electrospinning (NFES) is widely recognized as a versatile nano fabrication method, one suitable for applications in tissue engineering.
+Rapid developments in this field have given rise to layered nano fibrous scaffolds.
+However, this electrostatic fabrication process is limited by the electric field inhibitory effects of polymer deposition.
+This leads to a major challenge: how to surpass this limitation on planar/layered constructs.
+While the current focus in this area largely lies with the investigation of new materials, techniques and increasing precision of NFES systems and patterning, exploration of complex collector substrates is often restricted by (i) available technology and (ii) access to complex electrode manufacturing tools.
+
+Although electrospinning (ES) allows the production of unsurpassed nano scale polymer fibers, the major drawbacks are the nozzle-clogging and single-jet spinneret, respectively.
+This is a real limitation in terms of usable polymers and for patterning active organics.
+Nowadays the micro-engineering of smart materials could represent a new route for many fields of technology ranging from the production of electronic and photonic devices [1\ensuremath{-}3] to regenerative medicine and tissue engineering.
+[4\ensuremath{-}7] An enormous technological interest is related to the possibility of patterning fibers directly in well-ordered patterns avoiding the deposition of nonwoven sub micrometer mats often occurring in ES.
+[8,9] In the past decade several attempts have been made using field- induced [10\ensuremath{-}13] and near-field ES, [14,15] but only very recently, with the introduction of mechano ES, [16] has the production of well- ordered fiber patterns been achieved.
+Nevertheless, some drawbacks related to the complexity of the setup, the operating temperature, and the selection of usable materials for problems related to nozzle clogging still persist.
+Moreover, high temperature can cause deterioration of the optical and electronic properties of active organic materials eventually embedded in the functionalize [d fibers.
+On the other side, interfering effects due to closeness of multiple electrified nozzles ban working with multiple spinnerets.
 \apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}

### 2020-03-14 myPapers/NFES_Review/SUPPLEMENTARY_INFORMATION_Polymers_for_Nearfield_Electrospinning_with_Spatial_Control/article.tex
organising my directories ...

--- 2019-09-11 NFES_Review/article.tex
@@
 %%
-\documentclass[5p,,preprint,12pt,twocolumn]{elsarticle}
+\documentclass[3p,,preprint,12pt]{elsarticle}
 \makeatletter\if@twocolumn\PassOptionsToPackage{switch}{lineno}\else\fi\makeatother
@@
 \makeatother
+
+  \renewenvironment{abstract}{\global\setbox\absbox=\vbox\bgroup
+    \hsize=\textwidth\def\baselinestretch{1}%
+  \noindent\unskip\textbf{}
+   \par\medskip\noindent\unskip\ignorespaces}
+   {\egroup}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Feature enabled:
-%toc: yes
-%bookmark: yes
-%pagenum: yes
-%text-layout: twocolumn
-%endfloat: placeins
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\makeatletter
-\@ifpackageloaded{hyperref}{\def\alreadybookmark{}}{\usepackage[hidelinks]{hyperref}}
-\@ifpackageloaded{bookmark}{}{\usepackage{bookmark}}
-\makeatother
-\ifdefined\alreadybookmark\def\pdfbookmark[#1]#2#3{}\fi
-\makeatletter
-\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
-\makeatother
-          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
-\usepackage[section]{placeins}
-
-\usepackage{etoolbox}
-
 \usepackage{longtable}
-
-\usepackage{float}
 
@@
 \begin{document}
-\pdfbookmark[title]{Polymers for Near-field Electrospinning with Spatial Control}{title}
 
@@
 
-\title{Polymers for Near-field Electrospinning with Spatial Control
+\title{SUPPLEMENTARY INFORMATION: Polymers for Near-field Electrospinning with Spatial Control
 }
@@
 
-\begin{abstract}
-Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement.
-In the past years (2006-2019), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process.
-Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties.
-This paper presents a review on the research and related development of electrospun fibers, emphasizing the used polymers, solvents, and fiber characteristics.
-Relevant summary of polymer solutions and near-field electrospinning processing conditions is provided in this paper.
-\end{abstract}
-\begin{keyword} 
-polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
-\end{keyword}
-
 \end{frontmatter}
-\tableofcontents
-
-\section{Types of electrospinning (Classified by process properties)}
-~Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}.
-One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano fibers from a variety of polymers.
-The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $nm $ in some cases, which is something difficult to achieve by other techniques.
-Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials.
-The produced fibers can be aligned or unaligned.
-Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques\unskip~\cite{527120:12073538}.
-On the other hand, the understanding of the electrospinning process has improved in the last years.
-
-Current literature dictates the typical spinning setup is comprised by three main components: a syringe needle, a fiber collector, and some way to dispense the fibers from the needle to the collector.
-The spinning process is an electrohydro-dynamic (EHD) technique that yields continuous polymer fibers.
-Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively.
-
-\bgroup
-\fixFloatSize{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}{\includegraphics{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}}{}
-\makeatother 
-\caption{{Electrohydro-dynamic techniques}}
-\label{f-02e0e3cf88d6}
-\end{figure*}
-\egroup
-In electrospinning the fibers are deposited by an electrical potential difference between the syringe needle and the collector.
-The supplied polymer (typically a polymer solution) is administrated at a constant rate to create and maintain a polymer drop at the dispensing nozzle.
-A high voltage (usually DC) is applied between the polymer feed and the collector.
-As the electric field increases, the polymer drop (held by its surface tension) is then deformed at the tip of the syringe needle to form a conical shape known as Taylor cone.
-When the electric force overcomes the surface tension force a polymer jet is ejected from the tip of the Taylor cone.
-As the polymer jet leaves the nozzle, it accelerates and stretches while traveling to the fiber collector.
-The fiber finally develops with the complete solvent evaporation.
-
-\subsection{High voltage power supply: Direct Current \& Alternating Current}Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction.
-Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow.
-Kessick et al.\unskip~\cite{527120:13444381} demonstrated the implementation of AC power supplies in the production of polymer fibers.
-
-The AC electrospinning setup is similar to that for the DC variant.
-AC electrospinning apparatus do not require a grounded collector as the current alternates.
-In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge.
-The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers.
-The optimal AC frequency depends on the materials used and is typically within of 50 $Hz $ {\textendash} 1 $kHz $.
-\unskip~\cite{527120:13443405}
-
-The AC technique has been studied for drug loaded related applications.
-Balogh et al.
-\unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques.
-They produced fibers by using three polymers: Eudragit EPO (cationic copolymer), Eudragit L100-55 (anionic polymer) and poly(vinyl pyrrolidone) (PVP) (neutral polymer).
-Balogh et al.
-discovered AC and DC electrospinning can produce fibers with all three polymers.
-However, The AC process allowed the implementation of faster flow rates than in the DC setup.
-The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $.
-AC electrospinning approach is as effective as the DC technique in producing drug delivery systems.
-
-\subsection{Polymer reservoir: Polymer melt \& Polymer solution}Another electrospinning classification is the melt process.
-As Brown et al.
-\unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used).
-The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state.
-The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution.
-The apparatus used by Brown et al.
-\unskip~\cite{527120:13445499} is depicted in .
-
-[TODO: draw an apparatus used for melt electrospinning].
-
-Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.
-
-The first report of a melt electrospun drug delivery system came from Nagy et al.
-\unskip~\cite{527120:13445555}, who prepared fibers by melt electrospinning of Eudragit EPO with carvedilol.
-The drug and polymer were melted and mixed to form a homogeneous solid mixture prior to spinning.
-The melt-spun fibers reached diameters of 5{\textendash}30 $\mu m $, compared to 300{\textendash}1000 $nm $ diameters produced from solution-spun fibers.
-
-This work has been built on to blend plasticisers with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticisers Triacetin, Tween 80 and Polyethylene Glycol were investigated by Attila et al.
-in order to reduce the melting point of the polymer-drug mixture.
-The temperature drop is desirable to minimize the occurring drug degradation.
-
-Lian and Meng\unskip~\cite{527120:13445754} performed a comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibers fabricated by the melt and solution electrospinning techniques.
-Lian and Meng\unskip~\cite{527120:13445754} reported that melt spinning is preferable when the polymer presents a low solubility, on the other hand the melt fibers were produced in a slower release rate.
-Lian and Men findings feature the solution-spun fibers to have a porous structure.
-Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning.
-In their effort, they achieved a precise deposition of PCL fibers with diameters of $817 \pm 165 nm $.
-
-In literature, melt electrospinning has less evidence than the solution approach.
-However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}.
-Currently, the melt electrospinning setup is harder to establish but the lack of research on this technique explains its unexplored potential.
-
-\subsection{Stretching forces}
-
-\subsubsection{Electric Field}
-
-\subsubsection{Centrifugal force}The spinning processes require the implementation of a force to break the polymer source into a polymer jet.
-Centrifugal spinning intends to produce fibers by the use of a rotating polymer source.
-The centrifugal force generated from typical rotatory speeds above 2000 rpm, results in fiber formation.
-\unskip~\cite{527120:13535559,527120:13535561}.
-
-The centrifugal force technique is applied to polymer solutions and melts.
-This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.
-Efforts in centrifugal spinning are focused on drug delivery applications.
-Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach.
-Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.
-
-On the other hand, PCL and PVP fibers were generated by Amalorpava et al.
-\unskip~\cite{527120:13536089}.
-Amalorpava achieved sub micron/size fiber diameters for drug release purposes and bacteria growth inhibition properties.
-Literature\unskip~\cite{527120:13536446} has shown that centrifugal approach has a simple setup that promises a large scale fabrication of fibers.
-
-In some cases the centrifugal force implementations and pressurized gyration can be combined with an electric field.
-The implementation of two stretching forces (centrifugal and electrical forces), can help solvent evaporation\unskip~\cite{527120:13536560}.
-Centrifugal electrospinning implements the same setup as the standard centrifugal spinning with the addition of a high voltage power supply between the rotating dispensing nozzle and the collector.
-The combined method has evidence to yield parallel fibers\unskip~\cite{527120:13536841,527120:13536900,527120:13537392,527120:13537393} at a higher rate \unskip~\cite{527120:13536841,527120:13536900} than the standard electrospinning approach.
-
-\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution.
-The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate.
-Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}.
-
-[TODO: draw an apparatus used for solution blow spinning or melt blowing] \unskip~\cite{527120:13538056}.
-
-A few studies have explored solution blowing in drug delivery, with the first such work being from Oliveira et al.
-in 2013.
-[27] These authors prepared poly(lactic acid) (PLA) fibres loaded with the hormone progesterone, which can be used to regulate the reproductivecycle in livestock.
-Fibres were produced from solutions with 6\% w/vPLA and between 0 and 8\% w/v progesterone.
-The PLAis semi-crystalline both before and after processing, while the drug isamorphous post-spinning.
-The fibres behave very similarly in termsof their release behaviour, regardless of the amount of drug loaded.
-
-A study comparing electrospun and solution-blown fibres of poly(3-hydroxybutyrate-co-3-hydroxyvalerate) loaded with sodium diclofenachas also been reported.
-[26] The drug-loaded fibres were slightly larger in diameter when generated by electrospinning, and the size uniformity was higher through solution blowing.
-In general there was a greateramount of burst release seen with the electrospun fibres, but otherwisethere were no clear trends in the drug release data.
-
-Solution-blown fibres have additionally been created loaded with oil extracted from the medicinal plant Copaifera sp., which is often explored for antimicrobial purposes.
-[28] These materials were constructed from a blend of the polymers PLA and PVP, and were around 1 \ensuremath{\mu}m in diameter.
-An increased PVP content was found to result in increased antibacterial activity after 24 h.
-
-The melt blowing process has also received some attention in thepharmaceutical setting, and the fibres produced compared with thosefrom both solution and melt electrospinning.
-[29] Marosi's team generatedformulations from a vinylpyrrolidone{\textendash}vinyl acetate copolymer, employingpoly(ethylene glycol) (PEG) as a plasticiser and carvedilol as a modeldrug.
-All three methods led to fibres, with the solution electrospun fibres narrowest (at 2 \ensuremath{\mu}m in diameter), followed by the melt-blown (10\ensuremath{\mu}m) and melt-spun (50 \ensuremath{\mu}m) products.
-Carvedilol was rendered into the amorphous physical form by all three processing techniques, and all theformulations were able to accelerate the drug dissolution process.
-Themelt-blown and melt electrospun systems led to the fastest release, withalmost identical release profiles, while the solution-electrospun fibresfreed their drug cargo somewhat more slowly.
-
-A variant of the solution-blowing technique has been applied tothe processing of living cells (in this setting it has been referred to asbiothreading).
-[30] Using a pressurised coaxial needle with the exteriorfluid comprising a viscous polydimethylsiloxane solution and an aqueouscell suspension in the core, cells can be processed into scaffolds with nonoticeable loss in viability.
-
-Electrospinning and melt/solution blowing can be combined in a processknown as electroblowing.
-This employs both electricity and a gas flow toaid fibre elongation and solidification.
-The experimental apparatus usesa similar spinneret to that in [Figure apparatus used for solution blow spinning or melt blowing], and in addition to the gas flowa potential difference is applied between the spinneret and the collector.This technique has been shown to have significant potential in medicalapplications: in 2014, Jiang et al.
-applied electroblowing in vitro and invivo to deliver a homogeneous and continuous layer of a medical glue tostop bleeding during liver resection.
-[31]
-
-More recently, Balogh et al.
-prepared fibres of 2-hydroxypropyl-\ensuremath{\beta }-cyclodextrin loaded with sodium diclofenac.
-[32] They found that whenelectrospinning this system, very frequent clogging of the spinneretoccurred.
-Electroblowing overcame this issue and additionally allowedfaster flow rates to be used, increasing the amount of material thatcould be produced.
-However, the uniformity of the fibre products wascompromised, with more `beads-on-string' type morphology seen withthe blown products.
-In both cases, the fibres comprised amorphous soliddispersions with no crystalline drug evident.
-The electroblown fibresdissolved a little more slowly than those from electrospinning, but stillmuch more rapidly than a physical mixture of drug and cyclodextrin.
-
-A subsequent study using Eudragit E and itraconazole (anantifungal active pharmaceutical ingredient) also found that a fasterflow rate could be used in blowing, but that the fibre products from thelatter had less regular morphologies.
-[33] Again, the drug was amorphouslydispersed in the fibres, and the dissolution profiles of the electrospun andelectroblown systems were very similar.
-
-\subsubsection{Microfluidic forces}Microfluidic spinning is based on the use of micro (sub-millimetre)channels.
-A large number of these are located in a single microfluidicchip, and the rate and time of liquid expulsion from each channel are precisely controlled by computer.
-Microfluidic spinning can be coupled withelectrospinning, as described in detail in a recent review by Cheng et al.
-[51]While the productivity of microfluidic methods is a major challenge inscale-up, the technique offers the ability to generate fibres with a highlevel of complexity not easily achievable by electrospinning.
-For example,using a digitally programmed microfluidic flow, Kang et al.
-created functional microfibres with continuous spatiotemporal coding along thelength of the fibre.
-[52] The fibres contained varied chemical compositionsand topography, and localised bioactive agents.
-
-Microfluidic spinning therefore has the potential to enable veryprecisely tuneable loading of different drugs into a single fibre, allowingfor programmable release in different parts of the body at differenttimes.
-The technique is beginning to be explored for drug deliveryapplications.
-However, the materials used in microfluidics are usuallyhydrogels (crosslinked polymer networks solvated with water).
-Theseoften have fast degradation rates and as a result can be unsuitable forthe extended release of drugs, particularly small molecules.
-To helpmitigate this problem, Chae et al.
-developed a microfluidic spinningmethod using an isopropyl alcohol sheath flow with an aqueousalginate core flow.
-[53] This innovation resulted in nanofibres made ofhighly ordered alginate molecules.
-Ahn et al.
-loaded ampicillin intoalginate fibres prepared in this manner, [54 and found that the orderedstructure delayed fibre degradation, allowing extended-release profileof ampicillin over 7 days.
-
-\subsubsection{Mechanical force}
-
-\subsection{Dispensing nozzle: Coaxial / Monoaxial: Single nozzle / Multinozzle}
-
-\subsection{Nozzle-to-substrate distance}
-
-\subsubsection{Near Field Spinning}Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
-Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
-The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}.
-Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.
-
-\subsubsection{Far Field Spinning}In  a far field electrospinning the process continues ...
-Decreasing the jet diameter, the surface charge density increases and the resulting high repulsive forces split the jet into several smaller jets.
-The jet is seriously elongated by a bending and whipping processes caused by electrostatic repulsion initiated at small bends in the fiber, until it is finally deposited on the collector.
-Two types of collector may be used, either stationary or rotary collector.
-
-\section{"Electro - DC - monoaxial - solution - NF - spinning"}
-
-\bgroup
-\fixFloatSize{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}{\includegraphics{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}}{}
-\makeatother 
-\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130} .}}
-\label{f-fe28447572e9}
-\end{figure*}
-\egroup
-Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
-This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
-
-Nanofibers are fibers with diameters in the nanometer range. The development of nanofibers has greatly enhanced the scope for meeting up the modern world challenges.
-
-Currently there are two types of electrospinning systems available for producing nanofiber: needle based electrospinning and needleless electrospinning.
-This paper summarizes the basic mechanism of various types of needle based and needleless spinning systems described in various literatures by many researchers.
-
-\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES.
-Low voltage near field electrospinning produces thinner fibers with lower voltages.
-Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching.
-Bisht et al.
-\unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
-
-\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\protect\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\protect\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\protect\cite{527120:11974304}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Suspension NFES \unskip~\protect\cite{527120:12033656}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\protect\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\protect\cite{527120:11974320}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\protect\cite{527120:11974312}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\protect\cite{527120:11974307}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\section{Polymer Solution}
-In electrospinning, it is typically agreed that the diameter of the fibers increased with higher concentration due to greater viscosity which withstands stretching.
-In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}.
-However, in separate studies by Pan et al.\unskip~\cite{527120:11974317,527120:12321129} using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
-\begin{table*}[!htbp]
-\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
-\label{tw-8687dd17082c}
-\def\arraystretch{1}
-\ignorespaces 
-\centering 
-\begin{tabulary}{\linewidth}{LL}
-\tbltoprule Observation & Concentration Adjustement\\
-\tblmidrule 
-Dripping, no stream &
-  Increase\\
-Splitting small droplets &
-  Increase slightly\\
-Steady stream &
-  No concentration adjustment\\
-Splitting large globs &
-  Decrease slightly\\
-Nozzle clogging  &
-  Decrease\\
-\tblbottomrule 
-\end{tabulary}\par 
-\end{table*}
-
-\subsection{Polymers}The polymer selection is in function on the intended application.
-For example, a fast dissolving hydrophilic polymer such as poly(ethylene oxide) (PEO) is used for fast drug delivery systems.
-Otherwise, slow dissolving polymers such as poly($\varepsilon $-caprolactone) (PCL) or poly(lactic-co-glycolic acid) (PLGA) are implemented.
-\unskip~\cite{527120:13082763}
-
-The polymer molecular weight along with the polymer concentration and solvent selection have a direct effect on the solution viscosity, conductivity and surface tension, hence the solution behavior in the electrospinning process.
-The spunable viscosity range varies with the polymer and solvent.
-
-Solutions with low viscosity are prone to insufficient polymer chain entanglements to produce fibers.\unskip~\cite{527120:13082763} On the other hand, if the solution is too viscous, then the surface tension cannot easily be overcome by the electric field.
-In both cases, the result can be droplets or particles forming rather than fibers; see Table~\ref{tw-8687dd17082c}.
-
-\subsection{Solvents}The solvent used must be capable of dissolving the polymer of interest at an appropriate concentration to form fibers, and must posses a suitable volatility.
-A low-volatility solvent like water may fail to evaporate completely over the distance between the spinneret and the collector.
-When the fibers form, they will hence contain residual water owing to this incomplete evaporation.
-The residue solvent will subsequently evaporate from the fibers upon storage, resulting in ribbon-like (flattened) fibers, wrinkles on the fiber surface or fused fibers.
-On the other hand, a high-volatility solvent may evaporate very quickly, leading to larger fiber diameters (less time for elongation before solidification) and clogging of the spinneret (due to drying of the liquid at the spinneret before jetting, or drying of the Taylor cone during jetting).
-Solvents commonly used for electrospinning include ethanol, chloroform, dichloromethane and hexafluoroisopropanol.
-
-Mixtures of miscible solvents can be used to ensure that sufficient polymer can be dissolved to give a solution of appropriate viscosity and volatility with suitable dielectric constant range to allow fiber formation.
-However, care must be taken because using a mixture of solvents with very different volatilities can result in porous fiber structures, as reported by Katsogiannis et al.
-for organic solvent mixtures with dimethyl sulfoxide (DMSO).\unskip~\cite{527120:13082766} DMSO evaporates much more slowly than the organic solvents used, which results in its incorporation into the fibers.
-The DMSO will eventually evaporate, yielding porous fibers.
-
-It is also important to take into account the surface tension of the solution.
-Solvents with very high surface tensions (e.g.
-water) can result in instability arising during the spinning process, and a broad range of fiber diameters in the products.
-If necessary, a surfactant can be added to reduce the surface tension, but this will be incorporated into the fibers produced.
-
-\section{Effect of the NFES Parameters}
-
-\bgroup
-\fixFloatSize{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}{\includegraphics{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}}{}
-\makeatother 
-\caption{{Near-Field ES Process Parameters}}
-\label{f-3629d3a3f9cf}
-\end{figure*}
-\egroup
-To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
-Kameoka et al.\unskip~\cite{527120:12321556} demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip.
-
-Near-field electrospinning, has exhibited to be capable fabricate nano fibers over and nano fiber patterns \unskip~\cite{527120:11974321}.
-Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner.
-Using a spinneret with a reservoir (e.g.
-syringe) of solution generally produces fibers with diameter of a few micrometers \unskip~\cite{527120:11974310,527120:11974326}, since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through.
-
-Coppola et al.\unskip~\cite{527120:11974307} have showed a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop, averting the issue of nozzle clogging.
-The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al.'s\unskip~\cite{527120:11974326} work.
-
-\subsection{Nozzle spinneret}The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al.\unskip~\cite{527120:11974306} used a 100 $\mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
-The nozzle most commonly comprises a simple narrow-bore, blunt-end metal needle.
-The diameter of the needle can vary, but most commonly researches work with internal diameters below 1 $mm $ .
-This translates to needles of gauge 18{\textendash}22.
-In general, this simple spinneret design can be used to achieve successful spinning.
-A blunt-end rather than a tapered-end for the needle exit is important as the size distribution of the products increase with an increase in needle tip angle.
-However, it should be noted that there will be some interactions between the solvent and polymer molecules in the solution and the metal surface of the spinneret.
-There will exist some attractive forces between the polar groups in the polymer and the electropositive metal surface, which can act counter to the drawing force of the electric field and can pull the polymer solution back into the spinneret.
-It has been found that coating the spinneret exterior in a non-conductive and non-stick polymer such as Teflon can reduce these interactions.\unskip~\cite{527120:13082768} As a result, the electrical energy can be more efficiently used to elongate and narrow the polymer jet, and narrower fibers can be produced.
-In addition, strong attractive forces between the polymer jet and the metal spinneret can result in fibers becoming attracted to the needle, leading to lower yields and potentially to blocking of the exit orifice.
-This effect too can be ameliorated using an epoxy coating.\unskip~\cite{527120:13082811}
-
-\subsection{Applied Voltage}In recent literature, near field electrospinning has been studied to reduce the fiber diameter and to improve the fiber deposition accuracy.
-Camillo et al.\unskip~\cite{527120:12322072} demonstrated that the application of a modified fine tip nozzle enables the fabrication of 100 $nm $ diameter fiber at a nozzle-to-substrate distance of 500 $\mu m $ and an applied voltage of 1.5 $kV $ .
-On the other hand, Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} came to the conclusion higher voltages yield thicker micro-fibers with a loss in jet stability.
-
-This discrepancy in literature between the applied voltage and resulting fiber diameter is due to the relationship with other variables such as nozzle-to-substrate distance and solution deposition rate.
-For instance, if a high voltage is applied at a low deposition rate then electrospraying is achieved, meaning the formation of several non-continuous fibers.
-The applied voltage shall be sufficient to break the surface tension and initiate the jet, but low enough to avoid multiple jets at the nozzle tip.
-
-Bisht et al.\unskip~\cite{527120:11973130} achieved the fabrication of thinner fibers with spatial control by reducing the applied voltage to 200-600 $V $  at a nozzle-to-substrate distance of 0.5-1 $mm $.
-The low voltage setting does not create enough charge to break the polymer solution surface tension to initiate the electrospinning process.
-
-Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} initiated the electrospun fibers by mechanically pull the polymer solution at the nozzle tip using a micro-probe tip.
-Chang and coworkers reduced the applied voltage from 1.5 $kV $ to 600 $V $ with a nozzle-to-substrate distance of 500 $\mu m $ to yield a fiber diameter between 3 $\mu m $  and 50 $nm $ .
-With an applied voltage of 200 $V $ and a nozzle-to-substrate distance of 1 $mm $ , PEO nano fibers were deposited with a diameter about 20 $nm $.
-
-In near-field electrospinning, the applied voltage has an impact on the produced fiber morphology.
-For instance, a voltage higher or lower to the optimum voltage will translate into an increase in fiber diameter.
-Song et al.\unskip~\cite{527120:11974320} demonstrated that a decrease in voltage from 400 to 500 $V $ can reduce the fiber diameter from 160 to about 60 $nm $with a nozzle-to-substrate distance of 20 $\mu m $.
-The optimum voltage is achieved when a balance is attained between the stretching of the jet and the speed at which it hits the substrate.
-The increase of voltage yields thinner fibers as it causes greater stretching, and a greater jet acceleration.
-
-Another workaround to break the polymer solution surface tension is to initialize the NFES process with a higher voltage and then lower the voltage once the jet is created.
-Huang et al.\unskip~\cite{527120:11974311} implemented the previous and yield ordered fibers with a distance between adjacent fibers of 50 $\mu m $.
-In most cases, a positive voltage is applied to the spinneret.
-
-\subsection{Nozzle-to-substrate distance}In NFES, the fiber morphology can be altered by the control of the height between the nozzle and the substrate (collector).
-With the decrease of the nozzle-to-substrate distance, the electric field strength increases; however it can cause incomplete solvent volatilisation and possible short circuits between the collector and the nozzle tip.
-
-An optimal nozzle-to-substrate distance shall be defined to ensure the fabrication of dry continuous fibers.
-If the solvent is not well evaporated, the produced fibers are prone to defects; on the other hand if solidification happens too fast, the solids can block the spinneret which can prevent a continuous fiber yield.
-Furthermore, the polymer jet will discharge itself as soon as possible, therefore long distances can result in low yields.
-
-Typically, metal nozzle tips are used, with small inner diameters.
-From literature, needles with small diameters produce thinner fibers.
-A thin nozzle tip can help the reduction of the fiber diameter, but also it is more likely to become blocked.
-
-\subsection{Electric field}Recent literature suggests that the fiber morphology depends on the electric field profile created by the applied voltage during NFES.
-Since the electric field is an induced force that attracts the solution jet towards the desired location within the collector.
-
-Bisht et al.\unskip~\cite{527120:11973130} and Min et al.\unskip~\cite{527120:11974316} have reported the ability to electrospin nano fibers with high accuracy.
-Min et al.
-\unskip~\cite{527120:11974316} implemented a NFES setup with multiple "field-effect transistors" on a flexible polyacrylate collector with an x-y stage velocity of 13.3 $cm/s $ to fabricate fibers with a diameter about 289 $nm $ and a distance between adjacent fibers of 50 $\mu m $.
-
-On the other hand, Bisht et al.\unskip~\cite{527120:11973130} showed evidence of fabricated fibers with low-voltage NFES with high accuracy and precision.
-Bisht et al.'s suspended fibers were deposited over carbon posts with a distance between adjacent fibers of 100 $\mu m $ with diameter of 30 $\mu m $\unskip~\cite{527120:11973130}.
-
-The employment of guided electrodes in NFES, adapts the fabrication process to yield a more accurate fiber deposition.
-For instance, Kim et al.\unskip~\cite{527120:11974313} manufactured ink patterns on a paper with silver nano particles.
-The printed patterns aid the fibers to land on the desired location.
-Kim et al.\unskip~\cite{527120:11974313} electrospun the fibers with a distance between adjacent fibers of 150 $\mu m $.
-
-Xu et al.\unskip~\cite{527120:11974325} created a straight jet from the nozzle tip to the substrate using a guiding electrode underneath the collector.
-The purpose of the guiding electrode is to adjust the path of the NFES jet.
-With the guiding electrode implementation, the fiber's spread was reduced from 74 $\mu m $ to 7 $\mu m $.
-
-\subsection{Substrate}Due to the close distance between the grounded substrate and the charged spinneret in NFES, the set up is prone to electrical shorts.
-In NFES, when a short circuit takes place, the electrospinning process is interrupted resulting in the fabrication of discontinuous fibers.
-Two workarounds to avoid electrical shorts is to lower the applied voltage and to install less conductive substrates \unskip~\cite{527120:11974315,527120:12322289}.
-
-Liu et al.\unskip~\cite{527120:11974315} discovered that the fiber alignment is improved by using a glass-cooper foil substrate, however the well aligned fibers are spoiled after prolonged depositions due to residual charges.
-Additionally, the effect of residual charges is amplified with the used collector substrate contains a conductive layer and a non-conductive layer\unskip~\cite{527120:11974315}.
-
-On the other hand, Choi et al.\unskip~\cite{527120:12322289} implemented a hydrophobic substrate to deposit the fibers with plasma treatment to increase the conductivity of selected areas.
-NFES was carried put with precise deposition as the fibers were placed as per the desired design within the hydrophilic substrate.
 \begin{landscape}
@@
   \textbf{Solution Concentration:} 1, 2, and 3 $wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 27 gauge type 304; stainless steel needle \mbox{}\protect\newline \textbf{Solution deposition rate:} lower than 1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Pyrolyzed SU-8 carbon and Si \mbox{}\protect\newline \textbf{Applied voltage: }polymer jet initiated at 400-600 $V $ and dispensed at 200-400 $V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10-40$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 50-425$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11973130}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730868}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000 $g/mol $) with Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
@@
 The resulting MEH-PPV/PEO concentration is 0.08 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} mm-diameter tip Tungsten spinneret in a 26 gauge needle \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} SiO2/Si (oxide thickness = 800 nm) \mbox{}\protect\newline \textbf{Applied voltage:} around 1.3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 100$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} around 100$\mu m $ &
-  \unskip~\cite{527120:11974305}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730813}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MV = 300,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 7$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 200$\mu m $ and inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 1.5 $kV $ and dispensed at 600$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 120$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 709$\pm $131$nm $; 49-74$nm $ when applied voltage is 800$V $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{ Not determined} \mbox{}\protect\newline \textbf{Notes:} 108$m $ yield in 15$min $ with a fiber diameter of 709$\pm $131$nm $ &
-  \unskip~\cite{527120:11974306}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730812}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(vinylidine fluorid) (PVDF; MW = 440,000 $g/mol $) &
@@
 \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 510$\mu m $ and inner diameter of 260$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 400$nL/min $ \mbox{}\protect\newline \textbf{Nozazle-to-substrate distance:} 10-50$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Poly(dimethylsiloxane) (PDMS) on Ecoflex \mbox{}\protect\newline \textbf{Applied voltage:} 1.5{\textendash}3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0-400$mm/min $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 1.5-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974308}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730810}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Polyhedral Oligomeric Silsesquioxane-Poly(Carbonate-Urea)Urethane (POSS-PCU) and Polyhedral Oligomeric Silsesquioxane Poly(Caprolactone-Poly(Carbonate-Urea)Urethane) (POSS-PCL-PCU) \mbox{}\protect\newline (Dry Polycarbonate MW = 2000 $g/mol $) &
@@
   Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting &
-  \textbf{Solution Concentration: }POSS-PCU and POSS-PCL-PCU used in 20\%$w/w $ concentration in DMAC \mbox{}\protect\newline \textbf{Nozzle:} needle of 750 $\mu m $ in diameter \mbox{}\protect\newline \textbf{Solution deposition rate:} less than 1$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: }about between 500$\mu m $ to 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 8.0-10.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5-50$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }250$\mu m $ &
-  \unskip~\cite{527120:11974310}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \textbf{Solution Concentration: }POSS-PCU and POSS-PCL-PCU used in 20\%$w/w $ concentration in DMAC \mbox{}\protect\newline \textbf{Nozzle:} needle of 750 $\mu m $ in diameter \mbox{}\protect\newline \textbf{Solution deposition rate:} less than 1$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: }about between 500$\mu m $ to 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 8.0-10.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 15-50$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }250$\mu m $ &
+  \unskip~\cite{705707:16730808}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 6$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} 1200$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 7.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 2 $kV $ and dispensed at 0.8-1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} around 400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 200-350$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 5$\mu m $ &
-  \unskip~\cite{527120:11974311}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730807}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 8$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Outer airflow passage diameter: 1$mm $ Airflow gas pump pressure: 25$kPa $ Inner liquid passage diameter: 0.21$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 30$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Silicon \mbox{}\protect\newline \textbf{Applied voltage:} about 2$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 1-20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 3.73 $\pm $ 1.37$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }5.13 $\pm $ 6.67$\mu m $ &
-  \unskip~\cite{527120:11974312}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730806}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(Vinylidene Fluoride) (PVDF; MW = 534,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 17$wt\% $ PVDF; 1.7$g $ of PVDF, 5$g $ of acetone, 0.5$g $ of Capstone FS-66, 5$g $ of DMSO \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 14$\;nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 750$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} A4 size commercial printing paper (Double A) \mbox{}\protect\newline \textbf{Applied voltage:} 1.9$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974313}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730805}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(9-Vinyl Carbazole) (PVK; MW = 1,100,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 3.96$wt\% $ PVK in styrene \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 500$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} around 2.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Si/SiO2 \mbox{}\protect\newline \textbf{Applied voltage:} 3-4$kV $ \mbox{}\protect\newline x-y stage velocity: 13.3$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 289.26 $\pm $ 35.37$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }50$\mu m $ \mbox{}\protect\newline \textbf{Notes:} 15$m $ yield in 2$min $ &
-  \unskip~\cite{527120:11974316}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730802}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Polystyrene (PS; MW \textit{Not determined}) &
@@
   \textbf{Solution Concentration:} 1 to 5$wt\% $ PS \mbox{}\protect\newline \textbf{Nozzle:} Glass nozzle inner diameter of 2$\mu m $ and outer diameter of 2.66$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance}: 20, 30, 40$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition: }Si \mbox{}\protect\newline \textbf{Applied voltage:} 500 to 400$V $ in 25$V $ increments \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.01-10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 60-170$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974320}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730798}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} Si \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 25$\mu m $ &
-  \unskip~\cite{527120:11974321}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730797}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} four-nozzle and six-nozzle array with needle spacing changes from 1.5$mm $ to 3.5$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 1-3$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 1.7-2.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.47$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 3-5 $mm $ &
-  \unskip~\cite{527120:11974322}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730796}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
@@
   \textbf{Solution Concentration:}5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 0.18$mm $ and outer diameter of 0.36$mm $; with needle spacing changes from 2.0$mm $ to 3.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 3.0-4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition: } \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 2.0-3.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 218-326$\mu m $ &
-  \unskip~\cite{527120:11974323}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730795}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
@@
   \textbf{Solution Concentration:}5 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 180$\mu m $ and outer diameter of 360$\mu m $; with needle spacing changes of 2.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} chromium-plated glass \mbox{}\protect\newline \textbf{Applied voltage:} 2.5$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 2.3002-2.7224$mm $ &
-  \unskip~\cite{527120:11974324}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730794}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &
-  \unskip~\cite{527120:11974325}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730793}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Gelatin \mbox{}\protect\newline (porcine skin; MW \textit{Not determined}) &
@@
   \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &
-  \unskip~\cite{527120:11974326}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730792}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} PEO concentrations of 16\% and 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974327}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730791}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless needle with inner diameter of 210$\mu m $ and outer diameter of 400$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L/h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(ethylene terephthalate) (PET) \mbox{}\protect\newline \textbf{Applied voltage:} 3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 700$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 15-35$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 70$\mu m $ &
-  \unskip~\cite{527120:11974328}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730790}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless steel nozzle with inner diameter of 160$\mu m $ and outer diameter of 310$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2-5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicone \mbox{}\protect\newline \textbf{Applied voltage:}polymer jet initiated at 2$kV $ and dispensed at 1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 200-400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} from 344$\pm $32 to 214$\pm $27$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974304}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730814}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(co-Glycolic) acid (PLGA; MW \textit{Not determined})  &
@@
   \textbf{Solution Concentration:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle:} nozzle-free \mbox{}\protect\newline \textbf{Solution deposition rate:} The drop reservoir is placed directly on a flat substrate \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} Taylor's cone is focused and put in direct contact with the collector \mbox{}\protect\newline \textbf{Substrate composition:} Poly(tetrafluoroethylene) (PTFE) coated glass slide \mbox{}\protect\newline \textbf{Applied voltage:} pyro-electric field of between 2.7 $x10^{7}\;V/m $ and 5.5$x10^{7}\;V/m $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 304.7$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974307}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730811}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) with Tetrabutylammonium tetrafluoroborate (TBF; MW \textit{Not determined}) and SU-8 2002 &
@@
   \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline $\mu m $$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} \textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:12033655}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730788}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; 200,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} stainless steel needle (25 G) with inner diameter of 0.25$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 3$nL/s $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} between 0.5 and 10$mm $ with 0.5$mm $ increments \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon electrodes \mbox{}\protect\newline \textbf{Applied voltage:} 1.6$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50, 150, and 250$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 0.1 and 0.5$mm $ &
-  \unskip~\cite{527120:12033656}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
+  \unskip~\cite{705707:16730787}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 Poly(ethylene oxide) (PEO; MW = 400,000 $g/mol $) &
@@
   \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &
-  \unskip~\cite{527120:12033657}\\
+  \unskip~\cite{705707:16730786}\\
 \tblbottomrule 
@@
 \end{landscape}
-
-\section{Conclusion}
-
-\bgroup
-\fixFloatSize{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}{\includegraphics{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}}{}
-\makeatother 
-\caption{{Applied volage vs. Fiber diameter}}
-\label{f-59ed68f95344}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}{\includegraphics{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}}{}
-\makeatother 
-\caption{{Solution concentration vs. Fiber diameter}}
-\label{f-0ba4df766d66}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}{\includegraphics{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}}{}
-\makeatother 
-\caption{{Solution concentration vs. Molecular weight}}
-\label{f-ab38f7e015f7}
-\end{figure*}
-\egroup
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\section{NFES Achievements \& Challenges}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}
+~
 

### 2020-03-14 myThesis/thesis_proposal_LaTeX/Chapters/4_Objectives.tex
organising my directories ...

--- 2019-04-02 thesis_proposal_LaTeX/Chapters/4_Objectives.tex
@@
 
-\subsubsection*{\color{mygray}[Chapter ready for review]}
+%\subsubsection*{\color{mygray}[Chapter ready for review]}
 % Here you are meant to stipulate, in a broadly and specific way, what you want to achieve regarding the target problem.
@@
 \section{General objective}
-Study the practice and feasibility of a new synthesis process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner; by the integration of mechano-electrospinning technique.
+Study the practice and feasibility of a new fabrication process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner; by the integration of mechano-electrospinning technique.
 
-\section{Particular objectives}
+\section{Specific objectives}
 
@@
     }
+    \item{
+    Discover a PEO-similar material to allow the electrospinning process as well as input favourable properties to the carbon nano-wire yield.
+    }
 \end{itemize}

### 2020-03-14 myPapers/SU8_PhysicalTreatment/Effect_of_Physical_Treatment_in_Electrical_Conductivity_of_SU8based_Carbon_Structures/article.tex
su8 paper upload

--- 2020-03-14 myPapers/NFES_Review/Polymers_for_Nearfield_Electrospinning_with_Spatial_Control/article.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Feature enabled:
-%toc: yes
-%bookmark: yes
-%pagenum: yes
-%text-layout: twocolumn
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\makeatletter
-\@ifpackageloaded{hyperref}{\def\alreadybookmark{}}{\usepackage[hidelinks]{hyperref}}
-\@ifpackageloaded{bookmark}{}{\usepackage{bookmark}}
-\makeatother
-\ifdefined\alreadybookmark\def\pdfbookmark[#1]#2#3{}\fi
-\makeatletter
-\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
-\makeatother
-          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
-\usepackage{etoolbox}
-
 \usepackage{float}
@@
 
-\title{Polymers for Near-field Electrospinning with Spatial Control
+\title{Effect of Physical Treatment in Electrical Conductivity of SU-8-based Carbon Structures
 }
 
-\author[]{Antonio Osamu Katagiri Tanaka}
+\author[a4afda52a866c]{Saeed Beigiborouleni}
+\ead{saeed.beigi@tec.mx}
+\author[a4afda52a866c]{Antonio Osamu Katagiri Tanaka}
 \ead{oskatagiri@gmail.com}
-\author[]{H{\'e}ctor Al\'{a}n Aguirre Soto}
-\ead{alan.aguirre@tec.mx}
+
+\address[a4afda52a866c]{
+    ITESM MTY\unskip, Av. Eugenio Garza Sada Sur\unskip, Monterrey\unskip, 2501\unskip, N.L.\unskip, Mexico}
 
 \begin{abstract}
-Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement.
-In the past years (2006-2019), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process.
-Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties.
-This paper presents a review on the research and related development of electrospun fibers, emphasizing the used polymers, solvents, and fiber characteristics.
-Relevant summary of polymer solutions and near-field electrospinning processing conditions is provided in this paper.
+[TODO: Re-write when the other sections are completed ...]
+
+The effects of physical treatment in electrical conductivity of SU-8 films are investigated.
+SU-8 films were fabricated through mechanical treatment and stabilization followed by pyrolyzation and characterized by four-point-probe method.
+Based on previous evidence, it is expected that the induced stress to increase the electrical conductivity of the carbon films.
+However, the SU-8 carbon films amendment after pyrolysis is mainly due to degassing losses, rather than strain induced forces, hence the small to none differences between the stress-induced and control samples.
+[AGREE?]
 \end{abstract}
-\begin{keyword} 
-polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
-\end{keyword}
+\end{frontmatter}
 
-\end{frontmatter}
-\tableofcontents
-
-\section{Fabrication Processes of Polymer Fibers}
-~Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}.
-One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano fibers from a variety of polymers.
-The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $nm $ in some cases, which is something difficult to achieve by other techniques.
-Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials.
-The produced fibers can be aligned or unaligned.
-Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques\unskip~\cite{527120:12073538}.
-On the other hand, the understanding of the electrospinning process has improved in the last years.
-
-Current literature dictates the typical spinning setup is comprised by three main components: a syringe needle, a fiber collector, and some way to dispense the fibers from the needle to the collector.
-The spinning process is an electrohydro-dynamic (EHD) technique that yields continuous polymer fibers.
-Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively.
+\section{Introduction}
+Nanostructures and nanostructured materials such as nanotubes, thin films, suspended nanofibers, and nanofiber mats exhibit unique properties that make them suitable as circuitry elements, structural materials and analytical sensors within micro-mechanical systems.
+Carbon-based nanostructures have been of interest due to their low reactivity, good electrical and thermal properties with electrochemical stability\unskip~\cite{708527:16798890}.
+One technique to fabricate carbon structures is through heat treatment/carbonization of organic materials.
+Organic materials decompose into simpler compounds when exposed to high temperatures in an inert atmosphere or vaccum\unskip~\cite{708527:16798894}; this process is known as pyrolysis.
+SU-8 is a well-known negative high transparency UV photoresist (see Figure~\ref{f-d9067a619988}) used as a carbon precursor in recent works\unskip~\cite{708527:16798894,708527:16798991,708527:16798990}.
 
 \bgroup
-\fixFloatSize{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}
+\fixFloatSize{images/c87f718a-dcb5-4fbe-957b-20a0d5843959-usu8composition.png}
 \begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}{\includegraphics{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}}{}
+\centering \makeatletter\IfFileExists{images/c87f718a-dcb5-4fbe-957b-20a0d5843959-usu8composition.png}{\includegraphics{images/c87f718a-dcb5-4fbe-957b-20a0d5843959-usu8composition.png}}{}
 \makeatother 
-\caption{{Electrohydro-dynamic techniques}}
-\label{f-02e0e3cf88d6}
+\caption{{SU-8 2000 Series Resists Composition. a) photo initiator; b-c) epoxy groups of different SU-8 monomers; d) solvent}}
+\label{f-d9067a619988}
 \end{figure}
 \egroup
+Cardenas-Benitez et al.\unskip~\cite{708527:16798894} studied the pyrolysis-induced shrinkage of photocured SU-8 structures due to the volatilized material/degassing and surface area of the microstructures, where the structures shrank about$70\% $ of their original size.
+Canton et al.\unskip~\cite{708527:16798990} reported that the shrinkage and elongation of suspended SU-8 fibers during pyrolysis influences the resulting electrical properties.
+In Canton et al.
+deposited fibers in supporting walls, as the walls shrink during pyrolysis strain forces elongate the fibers.
+Evidence states that the electrical conductivity increases when fibers are elongated/stretched with a decrease of their diameter\unskip~\cite{708527:16798990}.
 
-\subsection{Polymer reservoir: Polymer melt \& Polymer solution}Another electrospinning classification is the melt process.
-As Brown et al.
-\unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used).
-The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state.
-The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution.
-The apparatus used by Brown et al.
-\unskip~\cite{527120:13445499} is depicted in Figure~\ref{f-1e9a6ae11444}.
+On the other hand, literature suggest that the electrical conductivity of carbon electrodes is enhanced with the execution of mechanical treatments, as the precursor polymer chains align within the fibers.
+Recent efforts \unskip~\cite{708527:16799034,708527:16799035} report carbon fibers with superior electrical conductivity, where the polymer chains are aligned with the aid of carbon nanotubes and hydro-electromechanical strain via electrospinning processes.
+
+In this paper, the effects of physical treatment in electrical conductivity of SU-8 films.
+SU-8 films were fabricated through mechanical treatment and stabilization followed by pyrolyzation and characterized by the four-point-probe method.
+Based on previous evidence, it is expected that the induced stress to increase the electrical conductivity of the carbon films.
+
+\section{Materials and Methods}
+[TODO: List used materials and their origin]
+
+[TODO: Detailed preparation of the photoresist films]
 
 \bgroup
-\fixFloatSize{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}{\includegraphics{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}}{}
+\fixFloatSize{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}{\includegraphics{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}}{}
 \makeatother 
-\caption{{Typical Melt Electrospinning Setup}}
-\label{f-1e9a6ae11444}
-\end{figure}
-\egroup
-Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.
-
-The first report of a melt electrospun drug delivery system came from Nagy et al.
-\unskip~\cite{527120:13445555}, who prepared fibers by melt electrospinning of Eudragit EPO with carvedilol.
-The drug and polymer were melted and mixed to form a homogeneous solid mixture prior to spinning.
-The melt-spun fibers reached diameters of 5{\textendash}30 $\mu m $, compared to 300{\textendash}1000 $nm $ diameters produced from solution-spun fibers.
-
-This work has been built on to blend plasticisers with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticisers Triacetin, Tween 80 and Polyethylene Glycol were investigated by Attila et al.
-in order to reduce the melting point of the polymer-drug mixture.
-The temperature drop is desirable to minimize the occurring drug degradation.
-
-Lian and Meng\unskip~\cite{527120:13445754} performed a comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibers fabricated by the melt and solution electrospinning techniques.
-Lian and Meng\unskip~\cite{527120:13445754} reported that melt spinning is preferable when the polymer presents a low solubility, on the other hand the melt fibers were produced in a slower release rate.
-Lian and Men findings feature the solution-spun fibers to have a porous structure.
-Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning.
-In their effort, they achieved a precise deposition of PCL fibers with diameters of $817 \pm 165 nm $.
-
-In literature, melt electrospinning has less evidence than the solution approach.
-However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}.
-Currently, the melt electrospinning setup is harder to establish but the lack of research on this technique explains its unexplored potential.
-
-\subsection{Dispensing nozzle}Coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle, see Figure~\ref{f-e0d8f2eb18d4}.
-\unskip~\cite{527120:13914792,527120:13914793} The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers.
-Sun et al.
-\unskip~\cite{527120:13914312} addressed electrospinning setups, where both the core and shell are comprised by PEO (poly(ethylene oxide)) and for a PEO shell with a poly(dode-cylthiophene) core.
-Sun et al.
-state that co-electrospinning has the potential to extend the range of materials that can be used for electrospinning.
-The shell solution can be modified to make the core solution spunable.
-It was also discovered that non-spunable solutions can by implemented as shell solutions in conjunction with a spunable core solution.
-\unskip~\cite{527120:13914968}
-
-\bgroup
-\fixFloatSize{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}{\includegraphics{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}}{}
-\makeatother 
-\caption{{Needle configurations in coaxial electrospinning. (a) the outer needle encasing the inner; (b) the inner needle protruding from the outer; (c) both needles inline with each other;}}
-\label{f-e0d8f2eb18d4}
-\end{figure}
-\egroup
-Some advantages that co-electrospinning setups can offer include the preempting the initial jet burst from the spinneret nozzle.
-On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles.
-\unskip~\cite{527120:13914748,527120:13914750}.
-As in conventional NFES, in co-electrospinning, the needle tip is connected to a high voltage power supply with a grounded collector.
-With the influence of high electric fields, the fibers are prone to brake into separate layers due to the whipping instabilities as the jet travels to the substrate.
-The instability can be mitigated by adding additional ring electrodes between the spinneret and the grounded collector.
-\unskip~\cite{527120:13915304}
-
-\subsection{Stretching forces}
-
-\subsubsection{Electric Field}Electrospinning (electrostatic fiber spinning) is a fiber fabrication approach that implements an electric field produce fibers by an electrical potential difference between the syringe needle and the collector.
-The typical electrospinning setup applies an electrostatic charge to the polymer fluid at the tip of the needle nozzle, which results in the formation of the Taylor cone \unskip~\cite{527120:13659828}, from which a single polymer jet is ejected to the grounded collector.
-From the Taylor cone, the supplied polymer jet (typically a polymer solution) accelerates and reduces in diameter.
-The fiber finally develops with the complete solvent evaporation.
-Electrospun fibers are prone to splitting with the increase in acceleration, where multiple fibers are yield in a process known as electrospraying \unskip~\cite{527120:13659925}.
-
-The electrospinning process starts with charging a polymer solution droplet.
-When a polymer solution is administrated with a syringe pump, solution droplets will fall under the influence of gravity.
-The solution dripping stops when the electric field is strong enough to break the solution's surface tension, causing the droplet to change shape forming a polymer solution jet\unskip~\cite{527120:12033655}.
-
-Shin et al.
-\unskip~\cite{527120:13659926} reported that the growth of the whipping instability is one important element within the electrospinning technique.
-As detailed in Shin's work, weak electric fields produce a single uniformly thinning jet, and strong electric fields the jet becomes unstable after traveling a short distance.
-
-\paragraph{High voltage power supply: Direct Current \& Alternating Current}Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction.
-Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow.
-Kessick et al.\unskip~\cite{527120:13444381} demonstrated the implementation of AC power supplies in the production of polymer fibers.
-
-The AC electrospinning setup is similar to that for the DC variant.
-AC electrospinning apparatus do not require a grounded collector as the current alternates.
-In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge.
-The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers.
-The optimal AC frequency depends on the materials used and is typically within of 50 $Hz $ {\textendash} 1 $kHz $.
-\unskip~\cite{527120:13443405}
-
-The AC technique has been studied for drug loaded related applications.
-Balogh et al.
-\unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques.
-They produced fibers by using three polymers: Eudragit EPO (cationic copolymer), Eudragit L100-55 (anionic polymer) and poly(vinyl pyrrolidone) (PVP) (neutral polymer).
-Balogh et al.
-discovered AC and DC electrospinning can produce fibers with all three polymers.
-However, The AC process allowed the implementation of faster flow rates than in the DC setup.
-The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $.
-AC electrospinning approach is as effective as the DC technique in producing drug delivery systems.
-
-\subsubsection{Centrifugal force}The spinning processes require the implementation of a force to break the polymer source into a polymer jet.
-Centrifugal spinning intends to produce fibers by the use of a rotating polymer source.
-The centrifugal force generated from typical rotatory speeds above 2000 rpm, results in fiber formation.
-\unskip~\cite{527120:13535559,527120:13535561}.
-
-\bgroup
-\fixFloatSize{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}{\includegraphics{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}}{}
-\makeatother 
-\caption{{Typical setup used in pressurized gyration Processes}}
-\label{f-7cf6ac702e28}
-\end{figure}
-\egroup
-The centrifugal force technique is applied to polymer solutions and melts.
-This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.
-Efforts in centrifugal spinning are focused on drug delivery applications.
-Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach.
-Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.
-
-On the other hand, PCL and PVP fibers were generated by Amalorpava et al.
-\unskip~\cite{527120:13536089}.
-Amalorpava achieved sub micron/size fiber diameters for drug release purposes and bacteria growth inhibition properties.
-Literature\unskip~\cite{527120:13536446} has shown that centrifugal approach has a simple setup that promises a large scale fabrication of fibers.
-
-In some cases the centrifugal force implementations and pressurized gyration can be combined with an electric field.
-The implementation of two stretching forces (centrifugal and electrical forces), can help solvent evaporation\unskip~\cite{527120:13536560}.
-Centrifugal electrospinning implements the same setup as the standard centrifugal spinning with the addition of a high voltage power supply between the rotating dispensing nozzle and the collector.
-The combined method has evidence to yield parallel fibers\unskip~\cite{527120:13536841,527120:13536900,527120:13537392,527120:13537393} at a higher rate \unskip~\cite{527120:13536841,527120:13536900} than the standard electrospinning approach.
-
-\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution.
-The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate.
-Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}, see Figure~\ref{f-92361290d8c3} .
-
-\bgroup
-\fixFloatSize{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}{\includegraphics{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}}{}
-\makeatother 
-\caption{{Dispensing nozzle used for solution blow spinning or melt blowing. \unskip~\protect\cite{527120:13538056}}}
-\label{f-92361290d8c3}
-\end{figure}
-\egroup
-Poly(lactic acid) (PLA) fibers have been produced by solution blow spinning.
-Oliveira et al.
-\unskip~\cite{527120:13539278} fabricated the fibers from $6 wt\% $ PLA solutions with progesterone for live stock reproductive cycle regulation applications.
-On the other hand, Souza et al.\unskip~\cite{527120:13538056} conducted a study to compare the standard electrospinning and the solution blow spinning techniques.
-Poly(3-hydroxybutyrate-co-3-hydroxyvalerate) were fabricated by both methods.
-The fibers produced by electrospinning had thicker diameters and their size uniformity was higher in the fibers produced by solution blow spinning.
-
-Jiang et al.\unskip~\cite{527120:13554126} combined the blowing technique with the electrospinning approach.
-The blow electrospinning technique implements both electric and gas flow forces to stretch the fibers.
-Jiang used an apparatus similar to those used in traditional electrospinning.
-The experimental setup requires a coaxial needle nozzle with a pressurized gas flow along with a potential difference between the dispensing needle and the grounded collector.
-
-\subsubsection{Mechanical force}
-\bgroup
-\fixFloatSize{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}{\includegraphics{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}}{}
-\makeatother 
-\caption{{Typical mechanical fiber drawing process}}
-\label{f-432d16f420fb}
-\end{figure*}
-\egroup
-Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette.
-\unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical applications.
-\unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers where the fiber is created by stretching the polymer precursor with a moving collector, as depicted in Figure~\ref{f-432d16f420fb}.
-Touch-spinning comprises a moving stage with an embedded glass rod (Figure~\ref{f-f17259e76303}).
-Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers.
-The rotation stretches the fiber, causing the fiber to increase in length and decrease in diameter.
-The increase in length causes the fiber surface are to increase and therefore making the polymer solution solvent to volatilize, ending with a dry fiber within the collector.
-
-\bgroup
-\fixFloatSize{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}{\includegraphics{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}}{}
-\makeatother 
-\caption{{Touch-spinning technique.
-First rod is attached to a rotating stage and a polymer solution droplet is administrated through a needle.
-Then the rotating rod 'touches' the polymer precursor.
-Finally, as the rod rotates, the polymer solution is stretched and creates a fiber between the rod and the needle.}}
-\label{f-f17259e76303}
-\end{figure*}
-\egroup
-The touch spinning technique implies that the fiber diameter can be controlled by the rotation speed and the polymer solution concentration.
-The main difference relays on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}
-
-\subsubsection{Microfluidic forces}The microfluidic spinning technique manipulates and controls the polymer solution in networks of micrometer channels.
-The channel network are typically embedded in a microfluidic chip, where the solution deposition rate is controlled by active components (pumps and valves) with a computer.
-Cheng et al.
-\unskip~\cite{527120:13656236} compared and combined the microfluidic spinning and electrospinning techniques.
-
-On the other hand, Kang et al.
-\unskip~\cite{527120:13656548} managed to fabricate micro fibers by imitating the "silk spinning" process of spiders.
-Kang's micro fibers properties were modified using a microfluidic system with a programmable flow control.
-The current microfluidic spinning approach is not scalable to a large fiber production, however it enables the fabrication of high-complex fibers that are not easily achieved by other methods.
-
-\bgroup
-\fixFloatSize{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}{\includegraphics{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}}{}
-\makeatother 
-\caption{{Microfluidic device used by Kang et al.\unskip~\protect\cite{527120:13656548}}}
-\label{f-c0beae2757bf}
-\end{figure}
-\egroup
-Microfluidic techniques offer the possibility to embed several components into a single fiber, where each component can be released at different parts of the fiber.
-
-\subsection{Nozzle-to-substrate distance}
-\bgroup
-\fixFloatSize{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}{\includegraphics{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}}{}
-\makeatother 
-\caption{{a) Typical Far-field Electrospinning (FFES) Setup. b) Typical Near-field Electrospinning (NFES) Setup.}}
-\label{f-fbe88d27b932}
-\end{figure*}
-\egroup
-Figure~\ref{f-fbe88d27b932}.a, depicts the typical setup for the conventional far-field electrospinning (FFES).
-As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}.
-When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process.
-The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}.
-The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.
-
-In the intent to achieve controlled fiber deposition, Sun et al.
-\unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES),Figure~\ref{f-fbe88d27b932}, describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line.
-Moreover, some mechanical influence is required to deposit fibers precisely.
-The mechanical force is introduced by moving collector.
-If the polymer solution jet speed is faster than the speed of the moving collector, the written fiber will curl; on the other hand, if the collector moves faster than the polymer jet, the fiber will gradually diminish \unskip~\cite{527120:11974327,527120:11974326}.
-Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.
-
-The main difference between NFES and FFES is the distance between the needle and the collector which is higher in FFES (about 10 cm) compared to NFES which ranges in the mm scale.
-The short distance allow the production of well aligned fibers within particular designs.
-[7]
-
-\section{Properties that Improve Accuracy of Nano-Fiber Deposition}
-Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
-This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
-Table S1 is a collection of the relevant NFES process parameters and achieved fiber morphology.
-
-Some differences have been discovered between LV-NFES and conventional NFES.
-Low voltage near field electrospinning produces thinner fibers with lower voltages.
-Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching.
-Bisht et al.
-\unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
-
-Bisht et al.
-\unskip~\cite{527120:11973130} reports a controlled technique to fabricate polymeric nano fibers in a continuous manner, using a low voltage setup.
-Their purpose is to find a workaround to the drawbacks of traditional NFES by using a superelastic polymer precursor, which allow continuous patterning without breaking.
-In low voltage near-field electrospinning (LV NFES), a visco-elastic polymer is used to allow continuous spinning at about 200$V $ .
-The decrease in voltage is prone to produce a controlled polymer jet by reducing the bending instabilities.
-The authors demonstrate the effectiveness of this technique with the fabrication of suspended fibers, see Figure~\ref{f-52c94fbe4526} .
-
-\bgroup
-\fixFloatSize{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}{\includegraphics{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}}{}
-\makeatother 
-\caption{{Suspended nano fibers of 2 wt \% PEO at 300 V.
-(a) Six carbon posts connected by nano fibers.
-(b) Individual nano fiber suspended between the posts.
-(c) Close up of the suspended nano fiber.
-\unskip~\protect\cite{527120:11973130}}}
-\label{f-52c94fbe4526}
-\end{figure*}
-\egroup
-Chang et al.
-\unskip~\cite{527120:11974306} developed a scanning tip electrospinning (a continuous NFES) technique to write nano fibers with control patterning.
-Similar to Bisht et al.
-\unskip~\cite{527120:11973130}, they also demonstrate that the decrease in the applied electric field yields thinner fibers that can be controlled to develop circular shapes (Figure~\ref{f-9d0c3125e550}) and grids (Figure~\ref{f-32e7d8abb3aa}) on a flat surfaces.
-
-\bgroup
-\fixFloatSize{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}{\includegraphics{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}}{}
-\makeatother 
-\caption{{The three-character Cal is drawn on a silicon chip by a programmable x-y stage. \unskip~\protect\cite{527120:11974306}}}
-\label{f-9d0c3125e550}
-\end{figure}
-\egroup
-
-\bgroup
-\fixFloatSize{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}{\includegraphics{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}}{}
-\makeatother 
-\caption{{A triangular grid pattern. \unskip~\protect\cite{527120:11974306}}}
-\label{f-32e7d8abb3aa}
-\end{figure}
-\egroup
-Kim et al.
-\unskip~\cite{527120:11974313} experimented with a NFES variation where the fiber deposition is guided by conductive rails, see Figure~\ref{f-927e96fb5537} .
-As stated by the authors, the induced electric field is enhanced by the conductive pattern, which allows the fibers to follow the desired deposition path.
-As the fibers are prone to follow the conductive pattern, additional fibers can be stacked on each other.
-The stacking process was successfully achieved in high electric field conditions at: 750$\mu m $ substrate to collector distance, and 600 $\mu m $ needle to rail (offset) distance, see  .
-(Applied voltage not explicitly specified for "straight line pattern" and stacking experiments, only stated the implementation of 1.9 $kV $ on "sharp-edged shapes pattern" experiments).
-
-\bgroup
-\fixFloatSize{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}{\includegraphics{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}}{}
-\makeatother 
-\caption{{NFES setup for controlled fiber deposition on pre-patterned conductive electrodes. \unskip~\protect\cite{527120:11974313}}}
-\label{f-927e96fb5537}
+\caption{{Schematic diagram of the SU-8 carbon film fabrication process. a) . b) . c) . d) . e) . f) . g) . h) . i) . j) . k) . l) . }}
+\label{f-471d296f0590}
 \end{figure*}
@@
 
-\bgroup
-\fixFloatSize{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}{\includegraphics{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}}{}
-\makeatother 
-\caption{{SEM and CCD camera images of stacked fibers on the conductive pattern when high electric field and low electric field were applied}}
-\label{f-24b5148e8358}
-\end{figure}
-\egroup
-Gupta et al.\unskip~\cite{527120:11974310} introduced a new technique to fabricate polymer scaffolds for tissue engineering applications and organ development.
-The authors implemented two polymer solutions, with POSS-PCU (polyhedral oligomeric silsesquioxane-poly(carbonate-urea)urethane, a non-biodegradable polymer precursor) and with POSS-PCL-PCU (poly- hedral oligomeric silsesquioxane-polycaprolactone-poly(carbonate- urea)urethane, a biodegradable polymer precursor).
+\section{Results and discussion}
+[TODO: Depict the characterization evidence]
 
-As described by Gupta et al.\unskip~\cite{527120:11974310}, the fiber deposition equipment is comprised by a stainless steel needle with a internal diameter of 750 $\mu m $ , connected to a high voltage power supply of up to 30 $k V $ with a deposition rate of about $\geq 1 \mu L min^{-1} $.
-The setup was embedded to a motorized collector capable of controlled programmable motions, see Figure~\ref{f-74de1f00848b}.
-The proposed technique was able to produce fibers of $150 \mu m $ in diameter with pre-designed patterns.
-
-\bgroup
-\fixFloatSize{images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}{\includegraphics{images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}}{}
-\makeatother 
-\caption{{Schematic illustration of the electrohydrodynamic process. \unskip~\protect\cite{527120:11974310}}}
-\label{f-74de1f00848b}
-\end{figure}
-\egroup
-Wang, et al., Huang, et al., and Chen, et al.
-\unskip~\cite{527120:11974322,527120:11974323,527120:11974324} experimented with several multi-nozzle near-field electrospinning of aligned nano fibers.
-The multinozzle NFES apparatus is similar to the one used in conventional NFES with some modifications to the needle nozzle, see Figures~\ref{f-96ee25855dea} and~\ref{f-4a1a1f58a423}.
-The authors implemented similar NFES setups where the installed linear array of nozzles is supplied with a constant flow rate of solution.
-
-\bgroup
-\fixFloatSize{images/add2f32e-eac8-460d-a7ff-3d0a7b07c15f-uwang_00.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/add2f32e-eac8-460d-a7ff-3d0a7b07c15f-uwang_00.png}{\includegraphics{images/add2f32e-eac8-460d-a7ff-3d0a7b07c15f-uwang_00.png}}{}
-\makeatother 
-\caption{{Schematic of multi-nozzle near-field electrospinning system \unskip~\protect\cite{527120:11974323}}}
-\label{f-96ee25855dea}
-\end{figure}
-\egroup
-
-\bgroup
-\fixFloatSize{images/cd8e0617-d4d9-479b-a99b-a466cd21483c-uwang_01.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/cd8e0617-d4d9-479b-a99b-a466cd21483c-uwang_01.png}{\includegraphics{images/cd8e0617-d4d9-479b-a99b-a466cd21483c-uwang_01.png}}{}
-\makeatother 
-\caption{{The geometry distribution of linear array multi-nozzle system \unskip~\protect\cite{527120:11974323}}}
-\label{f-4a1a1f58a423}
-\end{figure}
-\egroup
-The purpose of multinozzle setups is to increase productivity, and not necessarily to deposit fibers in a direct, continuous and controllable manner, since the setup itself limits the patterning design to parallel aligned fibers, as sown in Figure~\ref{f-4f1fb5cbfee6}.
-The introduction of more needle \_also\_ introduces more process parameters that have an influence in the produced fiber morphology.
-The added process parameters comprise the needle length, and needle spacing \unskip~\cite{527120:11974323}.
-
-\bgroup
-\fixFloatSize{images/9569179c-0fea-4f46-bb0f-b3103fbd20aa-uwang_02.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/9569179c-0fea-4f46-bb0f-b3103fbd20aa-uwang_02.png}{\includegraphics{images/9569179c-0fea-4f46-bb0f-b3103fbd20aa-uwang_02.png}}{}
-\makeatother 
-\caption{{Morphology of aligned nano fibers pattern during three-nozzle NFES process.
-The experiment works in environment as electrode-to-collector distance 4.0 mm and applied voltage 2.5KV \unskip~\protect\cite{527120:11974323}}}
-\label{f-4f1fb5cbfee6}
-\end{figure}
-\egroup
-The authors came to the conclusion that the distance between the deposited fibers increase with the increase of the needle-to-collector distance, as the influence of the applied voltage dissipates.
-
-Huang, et al.\unskip~\cite{527120:11974311} studied the mechanoelectrospinning (MES) technique for the fabrication of nano fibers.
-The MES technique tries to improve deposition accuracy by the introduction of a mechanical drawing force.
-The MES is predominantly controlled by the collector stage velocity, the nozzle-to-collector distance, and the applied voltage.
-The authors believe that MES can compete as a low-cost, high precision fabrication of electronics and enable the direct writing of structures for nano scale lithography.
-Figure~\ref{f-7587d8081ccc} shows the polymer jet behavior when a mechanical force is implemented within the NFES process.
-
-\bgroup
-\fixFloatSize{images/db7d3b35-fe08-422f-afe4-78e0133b489b-uhuang_00.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/db7d3b35-fe08-422f-afe4-78e0133b489b-uhuang_00.png}{\includegraphics{images/db7d3b35-fe08-422f-afe4-78e0133b489b-uhuang_00.png}}{}
-\makeatother 
-\caption{{schematic diagram of leap direct-writing: the ink first accumulates at contact point and then gets stretched by mechanical drawing force.
-At a critical distance, the ink leaps to the next contact point, and gets stretched again \unskip~\protect\cite{527120:11974311}}}
-\label{f-7587d8081ccc}
-\end{figure}
-\egroup
-Zheng, et al.\unskip~\cite{527120:11974328} worked the near field electrospinning process with an AC power supply, also known as AC EDW (AC Pulse-Modulated Electrodynamic Direct-Writing).
-The alternating current decreased the repulsive force applied along the jet, allowing a stable jet.
-The AC EDW was implemented to produce micro fibers on an insulated PET (Polyethylene Terephthalate) collector.
-AC EDW fibers were successfully fabricated between x-y collector velocities from 700 to 1500 $mm / s $, see Figure~\ref{f-b2c382d8b6ab}.
-Zheng's work \unskip~\cite{527120:11974328}, Studied the effects of the AC voltage amplitude, frequency and duty cycle on the obtained fiber diameters.
-Zheng, et al.\unskip~\cite{527120:11974328} arrived to three conclusions: a) The fiber diameter increases from $\sim 14 \mu m $ to $\sim 35 \mu m $ with an increase in voltage amplitude from $\sim0V $ to $\sim 3000 V $, and decreases from $\sim 35 \mu m $ to $\sim 21 \mu m $ with an increase in voltage amplitude from $\sim 3000 V $ to $\sim 4000 V $; b) The fiber diameter increases from $\sim 14 \mu m $ to $\sim 35 \mu m $ with an increase in voltage amplitude from $\sim0V $ to $\sim 3000 V $, and decreases from $\sim 35 \mu m $ to $\sim 21 \mu m $ with an increase in voltage amplitude from $\sim 3000 V $ to $\sim 4000 V $;; and c) The fiber diameter increases from $\sim 14 \mu m $ to $\sim 35 \mu m $ with an increase in voltage amplitude from $\sim0V $ to $\sim 3000 V $, and decreases from $\sim 35 \mu m $ to $\sim 21 \mu m $ with an increase in voltage amplitude from $\sim 3000 V $ to $\sim 4000 V $;.
-
-\bgroup
-\fixFloatSize{images/f684a658-c64f-4f11-ba18-7debcb5e9977-uzheng_00.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/f684a658-c64f-4f11-ba18-7debcb5e9977-uzheng_00.png}{\includegraphics{images/f684a658-c64f-4f11-ba18-7debcb5e9977-uzheng_00.png}}{}
-\makeatother 
-\caption{{Micro fibers on insulated PET collector under AC electrical field with varying stage velocities\unskip~\protect\cite{527120:11974304}.}}
-\label{f-b2c382d8b6ab}
-\end{figure*}
-\egroup
-Micro and nano fibers have been written using AC pulse-modulated electrospinning by Bu et al.
-with polyehtylene terephthalate (PET) as substrate\unskip~\cite{527120:11974304}.
-The AC electrical field influences the electrospinning jet.
-The alternate current tends to decrease the repulsive electrical force allowing a stable straight jet between the dispensing nozzle and the insulating PET substrate.
-As depicted inFigure~\ref{f-b2c382d8b6ab}, Bu et al.
-varied the stage velocity.
-Faster stage velocities enable the deposition of straighter fibers\unskip~\cite{527120:11974304}.
-
-\bgroup
-\fixFloatSize{images/1847814e-ac17-4b33-ba90-6fe8b7336699-unagle_00.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/1847814e-ac17-4b33-ba90-6fe8b7336699-unagle_00.png}{\includegraphics{images/1847814e-ac17-4b33-ba90-6fe8b7336699-unagle_00.png}}{}
-\makeatother 
-\caption{{Planar nano fiber patterning. Microscopy images of PEO fibers on silicon wafers at different working distances.}}
-\label{f-f259e0a97fc2}
-\end{figure}
-\egroup
- A mechano-electrospinning technique was presented by Nagle et al.\unskip~\cite{527120:12033656} similar to the one presented in Figure~\ref{f-432d16f420fb}.
-With the implementation of a mechanical drawing force, a higher resolution nano fibrous pattern can be produced with lower voltages as the Taylor cone becomes more stable.
-Nagle et al.
-studied PEO fibers at different nozzle to collector distances.
-Evidence suggest that better patterning accuracy increases with increasing nozzle to collector distance as the solution is effectively dried\unskip~\cite{527120:12033656}.
-Near field mechano-electrospinning enables the collection of non woven fibers over large areas.
-
-\section{Polymer Solution}
-In electrospinning, it is typically agreed that the diameter of the fibers increased with higher concentration due to greater viscosity which withstands stretching.
-In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}.
-However, in separate studies by Pan et al.\unskip~\cite{527120:11974317,527120:12321129} using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
+\section{Nomenclature}
+[TODO: Add used acronyms and their meaning]
 \begin{table}[!htbp]
-\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
-\label{tw-8687dd17082c}
 \def\arraystretch{1}
@@
 \begin{tabulary}{\linewidth}{LL}
-\tbltoprule Observation & Concentration Adjustement\\
-\tblmidrule 
-Dripping, no stream &
-  Increase\\
-Splitting small droplets &
-  Increase slightly\\
-Steady stream &
-  No concentration adjustment\\
-Splitting large globs &
-  Decrease slightly\\
-Nozzle clogging  &
-  Decrease\\
+\tbltoprule 
+ &
+  \\
 \tblbottomrule 
@@
 
-\subsection{Polymers}The polymer selection is in function on the intended application.
-For example, a fast dissolving hydrophilic polymer such as poly(ethylene oxide) (PEO) is used for fast drug delivery systems.
-Otherwise, slow dissolving polymers such as poly($\varepsilon $-caprolactone) (PCL) or poly(lactic-co-glycolic acid) (PLGA) are implemented.
-\unskip~\cite{527120:13082763}
-
-The polymer molecular weight along with the polymer concentration and solvent selection have a direct effect on the solution viscosity, conductivity and surface tension, hence the solution behavior in the electrospinning process.
-The spunable viscosity range varies with the polymer and solvent.
-
-Solutions with low viscosity are prone to insufficient polymer chain entanglements to produce fibers.\unskip~\cite{527120:13082763} On the other hand, if the solution is too viscous, then the surface tension cannot easily be overcome by the electric field.
-In both cases, the result can be droplets or particles forming rather than fibers; see Table~\ref{tw-8687dd17082c}.
-
-\subsection{Solvents}The solvent used must be capable of dissolving the polymer of interest at an appropriate concentration to form fibers, and must posses a suitable volatility.
-A low-volatility solvent like water may fail to evaporate completely over the distance between the spinneret and the collector.
-When the fibers form, they will hence contain residual water owing to this incomplete evaporation.
-The residue solvent will subsequently evaporate from the fibers upon storage, resulting in ribbon-like (flattened) fibers, wrinkles on the fiber surface or fused fibers.
-On the other hand, a high-volatility solvent may evaporate very quickly, leading to larger fiber diameters (less time for elongation before solidification) and clogging of the spinneret (due to drying of the liquid at the spinneret before jetting, or drying of the Taylor cone during jetting).
-Solvents commonly used for electrospinning include ethanol, chloroform, dichloromethane and hexafluoroisopropanol.
-
-Mixtures of miscible solvents can be used to ensure that sufficient polymer can be dissolved to give a solution of appropriate viscosity and volatility with suitable dielectric constant range to allow fiber formation.
-However, care must be taken because using a mixture of solvents with very different volatilities can result in porous fiber structures, as reported by Katsogiannis et al.
-for organic solvent mixtures with dimethyl sulfoxide (DMSO).\unskip~\cite{527120:13082766} DMSO evaporates much more slowly than the organic solvents used, which results in its incorporation into the fibers.
-The DMSO will eventually evaporate, yielding porous fibers.
-
-It is also important to take into account the surface tension of the solution.
-Solvents with very high surface tensions (e.g.
-water) can result in instability arising during the spinning process, and a broad range of fiber diameters in the products.
-If necessary, a surfactant can be added to reduce the surface tension, but this will be incorporated into the fibers produced.
-
-\section{Effect of the NFES Parameters}
-
-\bgroup
-\fixFloatSize{images/43f61edd-73cd-4222-830e-3333f92934e9-uimg_nfesvariants.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/43f61edd-73cd-4222-830e-3333f92934e9-uimg_nfesvariants.png}{\includegraphics{images/43f61edd-73cd-4222-830e-3333f92934e9-uimg_nfesvariants.png}}{}
-\makeatother 
-\caption{{Near-Field ES Process Parameters}}
-\label{f-3629d3a3f9cf}
-\end{figure}
-\egroup
-To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
-Kameoka et al.\unskip~\cite{527120:12321556} demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip.
-
-Near-field electrospinning, has exhibited to be capable fabricate nano fibers over and nano fiber patterns \unskip~\cite{527120:11974321}.
-Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner.
-Using a spinneret with a reservoir (e.g.
-syringe) of solution generally produces fibers with diameter of a few micrometers \unskip~\cite{527120:11974310,527120:11974326}, since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through.
-
-Coppola et al.\unskip~\cite{527120:11974307} have showed a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop, averting the issue of nozzle clogging.
-The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al.'s\unskip~\cite{527120:11974326} work.
-
-\subsection{Nozzle spinneret}The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al.\unskip~\cite{527120:11974306} used a 100 $\mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
-The nozzle most commonly comprises a simple narrow-bore, blunt-end metal needle.
-The diameter of the needle can vary, but most commonly researches work with internal diameters below 1 $mm $ .
-This translates to needles of gauge 18{\textendash}22.
-In general, this simple spinneret design can be used to achieve successful spinning.
-A blunt-end rather than a tapered-end for the needle exit is important as the size distribution of the products increase with an increase in needle tip angle.
-However, it should be noted that there will be some interactions between the solvent and polymer molecules in the solution and the metal surface of the spinneret.
-There will exist some attractive forces between the polar groups in the polymer and the electro positive metal surface, which can act counter to the drawing force of the electric field and can pull the polymer solution back into the spinneret.
-It has been found that coating the spinneret exterior in a non-conductive and non-stick polymer such as Teflon can reduce these interactions.\unskip~\cite{527120:13082768} As a result, the electrical energy can be more efficiently used to elongate and narrow the polymer jet, and narrower fibers can be produced.
-In addition, strong attractive forces between the polymer jet and the metal spinneret can result in fibers becoming attracted to the needle, leading to lower yields and potentially to blocking of the exit orifice.
-This effect too can be ameliorated using an epoxy coating.\unskip~\cite{527120:13082811}
-
-\subsection{Applied Voltage}In recent literature, near field electrospinning has been studied to reduce the fiber diameter and to improve the fiber deposition accuracy.
-Camillo et al.\unskip~\cite{527120:12322072} demonstrated that the application of a modified fine tip nozzle enables the fabrication of 100 $nm $ diameter fiber at a nozzle-to-substrate distance of 500 $\mu m $ and an applied voltage of 1.5 $kV $ .
-On the other hand, Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} came to the conclusion higher voltages yield thicker micro-fibers with a loss in jet stability.
-
-This discrepancy in literature between the applied voltage and resulting fiber diameter is due to the relationship with other variables such as nozzle-to-substrate distance and solution deposition rate.
-For instance, if a high voltage is applied at a low deposition rate then electrospraying is achieved, meaning the formation of several non-continuous fibers.
-The applied voltage shall be sufficient to break the surface tension and initiate the jet, but low enough to avoid multiple jets at the nozzle tip.
-
-Bisht et al.\unskip~\cite{527120:11973130} achieved the fabrication of thinner fibers with spatial control by reducing the applied voltage to 200-600 $V $  at a nozzle-to-substrate distance of 0.5-1 $mm $.
-The low voltage setting does not create enough charge to break the polymer solution surface tension to initiate the electrospinning process.
-
-Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} initiated the electrospun fibers by mechanically pull the polymer solution at the nozzle tip using a micro-probe tip.
-Chang and coworkers reduced the applied voltage from 1.5 $kV $ to 600 $V $ with a nozzle-to-substrate distance of 500 $\mu m $ to yield a fiber diameter between 3 $\mu m $  and 50 $nm $ .
-With an applied voltage of 200 $V $ and a nozzle-to-substrate distance of 1 $mm $ , PEO nano fibers were deposited with a diameter about 20 $nm $.
-
-In near-field electrospinning, the applied voltage has an impact on the produced fiber morphology.
-For instance, a voltage higher or lower to the optimum voltage will translate into an increase in fiber diameter.
-Song et al.\unskip~\cite{527120:11974320} demonstrated that a decrease in voltage from 400 to 500 $V $ can reduce the fiber diameter from 160 to about 60 $nm $with a nozzle-to-substrate distance of 20 $\mu m $.
-The optimum voltage is achieved when a balance is attained between the stretching of the jet and the speed at which it hits the substrate.
-The increase of voltage yields thinner fibers as it causes greater stretching, and a greater jet acceleration.
-
-Another workaround to break the polymer solution surface tension is to initialize the NFES process with a higher voltage and then lower the voltage once the jet is created.
-Huang et al.\unskip~\cite{527120:11974311} implemented the previous and yield ordered fibers with a distance between adjacent fibers of 50 $\mu m $.
-In most cases, a positive voltage is applied to the spinneret.
-
-\subsection{Nozzle-to-substrate distance}In NFES, the fiber morphology can be altered by the control of the height between the nozzle and the substrate (collector).
-With the decrease of the nozzle-to-substrate distance, the electric field strength increases; however it can cause incomplete solvent volatilisation and possible short circuits between the collector and the nozzle tip.
-
-An optimal nozzle-to-substrate distance shall be defined to ensure the fabrication of dry continuous fibers.
-If the solvent is not well evaporated, the produced fibers are prone to defects; on the other hand if solidification happens too fast, the solids can block the spinneret which can prevent a continuous fiber yield.
-Furthermore, the polymer jet will discharge itself as soon as possible, therefore long distances can result in low yields.
-
-Typically, metal nozzle tips are used, with small inner diameters.
-From literature, needles with small diameters produce thinner fibers.
-A thin nozzle tip can help the reduction of the fiber diameter, but also it is more likely to become blocked.
-
-\subsection{Electric field}Recent literature suggests that the fiber morphology depends on the electric field profile created by the applied voltage during NFES.
-Since the electric field is an induced force that attracts the solution jet towards the desired location within the collector.
-
-Bisht et al.\unskip~\cite{527120:11973130} and Min et al.\unskip~\cite{527120:11974316} have reported the ability to electrospin nano fibers with high accuracy.
-Min et al.
-\unskip~\cite{527120:11974316} implemented a NFES setup with multiple "field-effect transistors" on a flexible polyacrylate collector with an x-y stage velocity of 13.3 $cm/s $ to fabricate fibers with a diameter about 289 $nm $ and a distance between adjacent fibers of 50 $\mu m $.
-
-On the other hand, Bisht et al.\unskip~\cite{527120:11973130} showed evidence of fabricated fibers with low-voltage NFES with high accuracy and precision.
-Bisht et al.'s suspended fibers were deposited over carbon posts with a distance between adjacent fibers of 100 $\mu m $ with diameter of 30 $\mu m $\unskip~\cite{527120:11973130}.
-
-The employment of guided electrodes in NFES, adapts the fabrication process to yield a more accurate fiber deposition.
-For instance, Kim et al.\unskip~\cite{527120:11974313} manufactured ink patterns on a paper with silver nano particles.
-The printed patterns aid the fibers to land on the desired location.
-Kim et al.\unskip~\cite{527120:11974313} electrospun the fibers with a distance between adjacent fibers of 150 $\mu m $.
-
-Xu et al.\unskip~\cite{527120:11974325} created a straight jet from the nozzle tip to the substrate using a guiding electrode underneath the collector.
-The purpose of the guiding electrode is to adjust the path of the NFES jet.
-With the guiding electrode implementation, the fiber's spread was reduced from 74 $\mu m $ to 7 $\mu m $.
-
-\subsection{Substrate}Due to the close distance between the grounded substrate and the charged spinneret in NFES, the set up is prone to electrical shorts.
-In NFES, when a short circuit takes place, the electrospinning process is interrupted resulting in the fabrication of discontinuous fibers.
-Two workarounds to avoid electrical shorts is to lower the applied voltage and to install less conductive substrates \unskip~\cite{527120:11974315,527120:12322289}.
-
-Liu et al.\unskip~\cite{527120:11974315} discovered that the fiber alignment is improved by using a glass-cooper foil substrate, however the well aligned fibers are spoiled after prolonged depositions due to residual charges.
-Additionally, the effect of residual charges is amplified with the used collector substrate contains a conductive layer and a non-conductive layer\unskip~\cite{527120:11974315}.
-
-On the other hand, Choi et al.\unskip~\cite{527120:12322289} implemented a hydrophobic substrate to deposit the fibers with plasma treatment to increase the conductivity of selected areas.
-NFES was carried put with precise deposition as the fibers were placed as per the desired design within the hydrophilic substrate.
-
-\section{Conclusion}
-Helix electrodynamic printing (HE-printing) was presented by Duan et al.
-\unskip~\cite{527120:11974308} with the intention of depositing aligned fibers.
-The authors fabricated a stretchable piezoelectric device using micro and nano fibers to demonstrate the possible applications of HE-printinh for electronics manufacturing.
-Duan et al.
-concluded that the fiber morphology is mainly driven by: the stage velocity, the applied voltage, and the nozzle-to-collector distance.
-
-\bgroup
-\fixFloatSize{images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}{\includegraphics{images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-30543905e028}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}{\includegraphics{images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-59ed68f95344}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}{\includegraphics{images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-51afaccaf109}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/6bd5e441-92a9-4f82-856d-85b3a7ada5ff-uplt_nozzlediameter_vs_polymerconcentration.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/6bd5e441-92a9-4f82-856d-85b3a7ada5ff-uplt_nozzlediameter_vs_polymerconcentration.png}{\includegraphics{images/6bd5e441-92a9-4f82-856d-85b3a7ada5ff-uplt_nozzlediameter_vs_polymerconcentration.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-47bf72d21b5d}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}{\includegraphics{images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-5f453fad619f}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}{\includegraphics{images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-d977f56a0782}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}{\includegraphics{images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-08e527ddef81}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/42209168-f90a-4aaa-a235-c9049fb5bb59-uplt_solutiondepositionrate_vs_polymerconcentration.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/42209168-f90a-4aaa-a235-c9049fb5bb59-uplt_solutiondepositionrate_vs_polymerconcentration.png}{\includegraphics{images/42209168-f90a-4aaa-a235-c9049fb5bb59-uplt_solutiondepositionrate_vs_polymerconcentration.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-232ba077005e}
-\end{figure*}
-\egroup
-Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine nozzle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity.
-The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano fibers was investigated.
-
-\section{NFES Achievements \& Challenges}
-Near-field electrospinning (NFES) is widely recognized as a versatile nano fabrication method, one suitable for applications in tissue engineering.
-Rapid developments in this field have given rise to layered nano fibrous scaffolds.
-However, this electrostatic fabrication process is limited by the electric field inhibitory effects of polymer deposition.
-This leads to a major challenge: how to surpass this limitation on planar/layered constructs.
-While the current focus in this area largely lies with the investigation of new materials, techniques and increasing precision of NFES systems and patterning, exploration of complex collector substrates is often restricted by (i) available technology and (ii) access to complex electrode manufacturing tools.
-
-Although electrospinning (ES) allows the production of unsurpassed nano scale polymer fibers, the major drawbacks are the nozzle-clogging and single-jet spinneret, respectively.
-This is a real limitation in terms of usable polymers and for patterning active organics.
-Nowadays the micro-engineering of smart materials could represent a new route for many fields of technology ranging from the production of electronic and photonic devices [1\ensuremath{-}3] to regenerative medicine and tissue engineering.
-[4\ensuremath{-}7] An enormous technological interest is related to the possibility of patterning fibers directly in well-ordered patterns avoiding the deposition of nonwoven sub micrometer mats often occurring in ES.
-[8,9] In the past decade several attempts have been made using field- induced [10\ensuremath{-}13] and near-field ES, [14,15] but only very recently, with the introduction of mechano ES, [16] has the production of well- ordered fiber patterns been achieved.
-Nevertheless, some drawbacks related to the complexity of the setup, the operating temperature, and the selection of usable materials for problems related to nozzle clogging still persist.
-Moreover, high temperature can cause deterioration of the optical and electronic properties of active organic materials eventually embedded in the functionalize [d fibers.
-On the other side, interfering effects due to closeness of multiple electrified nozzles ban working with multiple spinnerets.
-\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}
+\section*{Acknowledgments} [TODO: Don't know if this is required ...]
 

### 2020-03-14 myPapers/SU8_PhysicalTreatment/Effect_of_Physical_Treatment_in_Electrical_Conductivity_of_SU8based_Carbon_Structures/article.tex
img update

@@
 \bgroup
-\fixFloatSize{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}
+\fixFloatSize{images/345cc1b7-01c7-4e66-8e93-81ad0f990362-umethod.png}
 \begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}{\includegraphics{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}}{}
+\centering \makeatletter\IfFileExists{images/345cc1b7-01c7-4e66-8e93-81ad0f990362-umethod.png}{\includegraphics{images/345cc1b7-01c7-4e66-8e93-81ad0f990362-umethod.png}}{}
 \makeatother 
-\caption{{Schematic diagram of the SU-8 carbon film fabrication process. a) . b) . c) . d) . e) . f) . g) . h) . i) . j) . k) . l) . }}
+\caption{{Schematic diagram of the SU-8 carbon film fabrication process. }}
 \label{f-471d296f0590}
@@
 \tbltoprule 
- &
-  \\
+\textbf{PDMS} \mbox{}\protect\newline \textbf{UV} &
+  Polydimethylsiloxane \mbox{}\protect\newline Ultraviolet\\
 \tblbottomrule 

### 2020-05-25 myThesis/thesis_LaTeX/Chapters/1.tex
thesis  structure

--- 2019-09-11 NFES_Review/article.tex
@@
-%%
-%% Copyright 2007, 2008, 2009 Elsevier Ltd
-%%
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%%
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-\documentclass[5p,,preprint,12pt,twocolumn]{elsarticle}
-\makeatletter\if@twocolumn\PassOptionsToPackage{switch}{lineno}\else\fi\makeatother
+% Chapter Template
 
-\usepackage{tabulary,xcolor}
-\usepackage{amsfonts,amsmath,amssymb}
-\usepackage[T1]{fontenc}
-\makeatletter
-\let\save@ps@pprintTitle\ps@pprintTitle
-\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\itshape \null\hfill\today}}
-\def\hlinewd#1{%
-  \noalign{\ifnum0=`}\fi\hrule \@height #1%
-  \futurelet\reserved@a\@xhline}
-\def\tbltoprule{\hlinewd{.8pt}\\[-12pt]}
-\def\tblbottomrule{\noalign{\vspace*{6pt}}\hline\noalign{\vspace*{2pt}}}
-\def\tblmidrule{\noalign{\vspace*{6pt}}\hline\noalign{\vspace*{2pt}}}
-\AtBeginDocument{\ifNAT@numbers \biboptions{sort&compress}\fi}
-\makeatother
+\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title
 
-\usepackage{ifluatex}
-\ifluatex
-\usepackage{fontspec}
-\defaultfontfeatures{Ligatures=TeX}
-\usepackage[]{unicode-math}
-\unimathsetup{math-style=TeX}
-\else 
-\usepackage[utf8]{inputenc}
-\fi 
-\ifluatex\else\usepackage{stmaryrd}\fi
+\label{Chapter:1}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Following additional macros are required to function some 
-% functions which are not available in the class used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{url,multirow,morefloats,floatflt,cancel,tfrupee}
-\makeatletter
+%----------------------------------------------------------------------------------------
+%	SECTION 1
+%----------------------------------------------------------------------------------------
+\section{}
 
-\AtBeginDocument{\@ifpackageloaded{textcomp}{}{\usepackage{textcomp}}}
-\makeatother
-\usepackage{colortbl}
-\usepackage{xcolor}
-\usepackage{pifont}
-\usepackage[nointegrals]{wasysym}
-\urlstyle{rm}
-\makeatletter
-
-%%%For Table column width calculation.
-\def\mcWidth#1{\csname TY@F#1\endcsname+\tabcolsep}
-
-%%Hacking center and right align for table
-\def\cAlignHack{\rightskip\@flushglue\leftskip\@flushglue\parindent\z@\parfillskip\z@skip}
-\def\rAlignHack{\rightskip\z@skip\leftskip\@flushglue \parindent\z@\parfillskip\z@skip}
-
-%Etal definition in references
-\@ifundefined{etal}{\def\etal{\textit{et~al}}}{}
-
-%\if@twocolumn\usepackage{dblfloatfix}\fi
-\usepackage{ifxetex}
-\ifxetex\else\if@twocolumn\@ifpackageloaded{stfloats}{}{\usepackage{dblfloatfix}}\fi\fi
-
-\AtBeginDocument{
-\expandafter\ifx\csname eqalign\endcsname\relax
-\def\eqalign#1{\null\vcenter{\def\\{\cr}\openup\jot\m@th
-  \ialign{\strut$\displaystyle{##}$\hfil&$\displaystyle{{}##}$\hfil
-      \crcr#1\crcr}}\,}
-\fi
-}
-
-%For fixing hardfail when unicode letters appear inside table with endfloat
-\AtBeginDocument{%
-  \@ifpackageloaded{endfloat}%
-   {\renewcommand\efloat@iwrite[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}}{\newif\ifefloat@tables}%
-}%
-
-\def\BreakURLText#1{\@tfor\brk@tempa:=#1\do{\brk@tempa\hskip0pt}}
-\let\lt=<
-\let\gt=>
-\def\processVert{\ifmmode|\else\textbar\fi}
-\let\processvert\processVert
-
-\@ifundefined{subparagraph}{
-\def\subparagraph{\@startsection{paragraph}{5}{2\parindent}{0ex plus 0.1ex minus 0.1ex}%
-{0ex}{\normalfont\small\itshape}}%
-}{}
-
-% These are now gobbled, so won't appear in the PDF.
-\newcommand\role[1]{\unskip}
-\newcommand\aucollab[1]{\unskip}
-
-\@ifundefined{tsGraphicsScaleX}{\gdef\tsGraphicsScaleX{1}}{}
-\@ifundefined{tsGraphicsScaleY}{\gdef\tsGraphicsScaleY{.9}}{}
-% To automatically resize figures to fit inside the text area
-\def\checkGraphicsWidth{\ifdim\Gin@nat@width>\linewidth
-	\tsGraphicsScaleX\linewidth\else\Gin@nat@width\fi}
-
-\def\checkGraphicsHeight{\ifdim\Gin@nat@height>.9\textheight
-	\tsGraphicsScaleY\textheight\else\Gin@nat@height\fi}
-
-\def\fixFloatSize#1{}%\@ifundefined{processdelayedfloats}{\setbox0=\hbox{\includegraphics{#1}}\ifnum\wd0<\columnwidth\relax\renewenvironment{figure*}{\begin{figure}}{\end{figure}}\fi}{}}
-\let\ts@includegraphics\includegraphics
-
-\def\inlinegraphic[#1]#2{{\edef\@tempa{#1}\edef\baseline@shift{\ifx\@tempa\@empty0\else#1\fi}\edef\tempZ{\the\numexpr(\numexpr(\baseline@shift*\f@size/100))}\protect\raisebox{\tempZ pt}{\ts@includegraphics{#2}}}}
-
-%\renewcommand{\includegraphics}[1]{\ts@includegraphics[width=\checkGraphicsWidth]{#1}}
-\AtBeginDocument{\def\includegraphics{\@ifnextchar[{\ts@includegraphics}{\ts@includegraphics[width=\checkGraphicsWidth,height=\checkGraphicsHeight,keepaspectratio]}}}
-
-\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
-
-\def\URL#1#2{\@ifundefined{href}{#2}{\href{#1}{#2}}}
-
-%%For url break
-\def\UrlOrds{\do\*\do\-\do\~\do\'\do\"\do\-}%
-\g@addto@macro{\UrlBreaks}{\UrlOrds}
-
-\edef\fntEncoding{\f@encoding}
-\def\EUoneEnc{EU1}
-\makeatother
-\def\floatpagefraction{0.8} 
-\def\dblfloatpagefraction{0.8}
-\def\style#1#2{#2}
-\def\xxxguillemotleft{\fontencoding{T1}\selectfont\guillemotleft}
-\def\xxxguillemotright{\fontencoding{T1}\selectfont\guillemotright}
-
-\newif\ifmultipleabstract\multipleabstractfalse%
-\newenvironment{typesetAbstractGroup}{}{}%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\emergencystretch 20pt \tolerance = 1500 \def\floatpagefraction{0.8}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Feature enabled:
-%toc: yes
-%bookmark: yes
-%pagenum: yes
-%text-layout: twocolumn
-%endfloat: placeins
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\makeatletter
-\@ifpackageloaded{hyperref}{\def\alreadybookmark{}}{\usepackage[hidelinks]{hyperref}}
-\@ifpackageloaded{bookmark}{}{\usepackage{bookmark}}
-\makeatother
-\ifdefined\alreadybookmark\def\pdfbookmark[#1]#2#3{}\fi
-\makeatletter
-\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
-\makeatother
-          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
-\usepackage[section]{placeins}
-
-\usepackage{etoolbox}
-
-\usepackage{longtable}
-
-\usepackage{float}
-
-\makeatletter
-\AtBeginDocument{\@ifpackageloaded{rotating}{\PassOptionsToPackage{figuresright}{rotating}}{\usepackage[figuresright]{rotating}}\setlength{\rotFPtop}{0pt plus 1fil}\setlength{\rotFPbot}{0pt plus 1fil}}
-\makeatother
-
-\makeatletter
- \AtBeginDocument{%
-  \@ifpackagewith{endfloat}{figuresonly}
-  {\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}}%true
-  {\@ifpackagewith{endfloat}{tablesonly}{\DeclareDelayedFloatFlavor{sidewaystable}{table}\DeclareDelayedFloatFlavor{longtable}{table}\DeclareDelayedFloatFlavor{landscape}{table}}%true
-  {\@ifpackageloaded{endfloat}{\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}\DeclareDelayedFloatFlavor{sidewaystable}{table}\DeclareDelayedFloatFlavor{longtable}{table}\DeclareDelayedFloatFlavor{landscape}{table}}{}}%false
-  }%false
-  }
-\makeatother
-
-\usepackage{pdflscape}
-
-\begin{document}
-\pdfbookmark[title]{Polymers for Near-field Electrospinning with Spatial Control}{title}
-
-\begin{frontmatter}
-
-\title{Polymers for Near-field Electrospinning with Spatial Control
-}
-
-\author[]{Antonio Osamu Katagiri Tanaka}
-\ead{oskatagiri@gmail.com}
-\author[]{H{\'e}ctor Al\'{a}n Aguirre Soto}
-\ead{alan.aguirre@tec.mx}
-
-\begin{abstract}
-Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement.
-In the past years (2006-2019), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process.
-Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties.
-This paper presents a review on the research and related development of electrospun fibers, emphasizing the used polymers, solvents, and fiber characteristics.
-Relevant summary of polymer solutions and near-field electrospinning processing conditions is provided in this paper.
-\end{abstract}
-\begin{keyword} 
-polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
-\end{keyword}
-
-\end{frontmatter}
-\tableofcontents
-
-\section{Types of electrospinning (Classified by process properties)}
-~Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}.
-One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano fibers from a variety of polymers.
-The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $nm $ in some cases, which is something difficult to achieve by other techniques.
-Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials.
-The produced fibers can be aligned or unaligned.
-Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques\unskip~\cite{527120:12073538}.
-On the other hand, the understanding of the electrospinning process has improved in the last years.
-
-Current literature dictates the typical spinning setup is comprised by three main components: a syringe needle, a fiber collector, and some way to dispense the fibers from the needle to the collector.
-The spinning process is an electrohydro-dynamic (EHD) technique that yields continuous polymer fibers.
-Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively.
-
-\bgroup
-\fixFloatSize{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}{\includegraphics{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}}{}
-\makeatother 
-\caption{{Electrohydro-dynamic techniques}}
-\label{f-02e0e3cf88d6}
-\end{figure*}
-\egroup
-In electrospinning the fibers are deposited by an electrical potential difference between the syringe needle and the collector.
-The supplied polymer (typically a polymer solution) is administrated at a constant rate to create and maintain a polymer drop at the dispensing nozzle.
-A high voltage (usually DC) is applied between the polymer feed and the collector.
-As the electric field increases, the polymer drop (held by its surface tension) is then deformed at the tip of the syringe needle to form a conical shape known as Taylor cone.
-When the electric force overcomes the surface tension force a polymer jet is ejected from the tip of the Taylor cone.
-As the polymer jet leaves the nozzle, it accelerates and stretches while traveling to the fiber collector.
-The fiber finally develops with the complete solvent evaporation.
-
-\subsection{High voltage power supply: Direct Current \& Alternating Current}Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction.
-Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow.
-Kessick et al.\unskip~\cite{527120:13444381} demonstrated the implementation of AC power supplies in the production of polymer fibers.
-
-The AC electrospinning setup is similar to that for the DC variant.
-AC electrospinning apparatus do not require a grounded collector as the current alternates.
-In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge.
-The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers.
-The optimal AC frequency depends on the materials used and is typically within of 50 $Hz $ {\textendash} 1 $kHz $.
-\unskip~\cite{527120:13443405}
-
-The AC technique has been studied for drug loaded related applications.
-Balogh et al.
-\unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques.
-They produced fibers by using three polymers: Eudragit EPO (cationic copolymer), Eudragit L100-55 (anionic polymer) and poly(vinyl pyrrolidone) (PVP) (neutral polymer).
-Balogh et al.
-discovered AC and DC electrospinning can produce fibers with all three polymers.
-However, The AC process allowed the implementation of faster flow rates than in the DC setup.
-The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $.
-AC electrospinning approach is as effective as the DC technique in producing drug delivery systems.
-
-\subsection{Polymer reservoir: Polymer melt \& Polymer solution}Another electrospinning classification is the melt process.
-As Brown et al.
-\unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used).
-The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state.
-The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution.
-The apparatus used by Brown et al.
-\unskip~\cite{527120:13445499} is depicted in .
-
-[TODO: draw an apparatus used for melt electrospinning].
-
-Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.
-
-The first report of a melt electrospun drug delivery system came from Nagy et al.
-\unskip~\cite{527120:13445555}, who prepared fibers by melt electrospinning of Eudragit EPO with carvedilol.
-The drug and polymer were melted and mixed to form a homogeneous solid mixture prior to spinning.
-The melt-spun fibers reached diameters of 5{\textendash}30 $\mu m $, compared to 300{\textendash}1000 $nm $ diameters produced from solution-spun fibers.
-
-This work has been built on to blend plasticisers with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticisers Triacetin, Tween 80 and Polyethylene Glycol were investigated by Attila et al.
-in order to reduce the melting point of the polymer-drug mixture.
-The temperature drop is desirable to minimize the occurring drug degradation.
-
-Lian and Meng\unskip~\cite{527120:13445754} performed a comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibers fabricated by the melt and solution electrospinning techniques.
-Lian and Meng\unskip~\cite{527120:13445754} reported that melt spinning is preferable when the polymer presents a low solubility, on the other hand the melt fibers were produced in a slower release rate.
-Lian and Men findings feature the solution-spun fibers to have a porous structure.
-Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning.
-In their effort, they achieved a precise deposition of PCL fibers with diameters of $817 \pm 165 nm $.
-
-In literature, melt electrospinning has less evidence than the solution approach.
-However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}.
-Currently, the melt electrospinning setup is harder to establish but the lack of research on this technique explains its unexplored potential.
-
-\subsection{Stretching forces}
-
-\subsubsection{Electric Field}
-
-\subsubsection{Centrifugal force}The spinning processes require the implementation of a force to break the polymer source into a polymer jet.
-Centrifugal spinning intends to produce fibers by the use of a rotating polymer source.
-The centrifugal force generated from typical rotatory speeds above 2000 rpm, results in fiber formation.
-\unskip~\cite{527120:13535559,527120:13535561}.
-
-The centrifugal force technique is applied to polymer solutions and melts.
-This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.
-Efforts in centrifugal spinning are focused on drug delivery applications.
-Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach.
-Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.
-
-On the other hand, PCL and PVP fibers were generated by Amalorpava et al.
-\unskip~\cite{527120:13536089}.
-Amalorpava achieved sub micron/size fiber diameters for drug release purposes and bacteria growth inhibition properties.
-Literature\unskip~\cite{527120:13536446} has shown that centrifugal approach has a simple setup that promises a large scale fabrication of fibers.
-
-In some cases the centrifugal force implementations and pressurized gyration can be combined with an electric field.
-The implementation of two stretching forces (centrifugal and electrical forces), can help solvent evaporation\unskip~\cite{527120:13536560}.
-Centrifugal electrospinning implements the same setup as the standard centrifugal spinning with the addition of a high voltage power supply between the rotating dispensing nozzle and the collector.
-The combined method has evidence to yield parallel fibers\unskip~\cite{527120:13536841,527120:13536900,527120:13537392,527120:13537393} at a higher rate \unskip~\cite{527120:13536841,527120:13536900} than the standard electrospinning approach.
-
-\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution.
-The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate.
-Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}.
-
-[TODO: draw an apparatus used for solution blow spinning or melt blowing] \unskip~\cite{527120:13538056}.
-
-A few studies have explored solution blowing in drug delivery, with the first such work being from Oliveira et al.
-in 2013.
-[27] These authors prepared poly(lactic acid) (PLA) fibres loaded with the hormone progesterone, which can be used to regulate the reproductivecycle in livestock.
-Fibres were produced from solutions with 6\% w/vPLA and between 0 and 8\% w/v progesterone.
-The PLAis semi-crystalline both before and after processing, while the drug isamorphous post-spinning.
-The fibres behave very similarly in termsof their release behaviour, regardless of the amount of drug loaded.
-
-A study comparing electrospun and solution-blown fibres of poly(3-hydroxybutyrate-co-3-hydroxyvalerate) loaded with sodium diclofenachas also been reported.
-[26] The drug-loaded fibres were slightly larger in diameter when generated by electrospinning, and the size uniformity was higher through solution blowing.
-In general there was a greateramount of burst release seen with the electrospun fibres, but otherwisethere were no clear trends in the drug release data.
-
-Solution-blown fibres have additionally been created loaded with oil extracted from the medicinal plant Copaifera sp., which is often explored for antimicrobial purposes.
-[28] These materials were constructed from a blend of the polymers PLA and PVP, and were around 1 \ensuremath{\mu}m in diameter.
-An increased PVP content was found to result in increased antibacterial activity after 24 h.
-
-The melt blowing process has also received some attention in thepharmaceutical setting, and the fibres produced compared with thosefrom both solution and melt electrospinning.
-[29] Marosi's team generatedformulations from a vinylpyrrolidone{\textendash}vinyl acetate copolymer, employingpoly(ethylene glycol) (PEG) as a plasticiser and carvedilol as a modeldrug.
-All three methods led to fibres, with the solution electrospun fibres narrowest (at 2 \ensuremath{\mu}m in diameter), followed by the melt-blown (10\ensuremath{\mu}m) and melt-spun (50 \ensuremath{\mu}m) products.
-Carvedilol was rendered into the amorphous physical form by all three processing techniques, and all theformulations were able to accelerate the drug dissolution process.
-Themelt-blown and melt electrospun systems led to the fastest release, withalmost identical release profiles, while the solution-electrospun fibresfreed their drug cargo somewhat more slowly.
-
-A variant of the solution-blowing technique has been applied tothe processing of living cells (in this setting it has been referred to asbiothreading).
-[30] Using a pressurised coaxial needle with the exteriorfluid comprising a viscous polydimethylsiloxane solution and an aqueouscell suspension in the core, cells can be processed into scaffolds with nonoticeable loss in viability.
-
-Electrospinning and melt/solution blowing can be combined in a processknown as electroblowing.
-This employs both electricity and a gas flow toaid fibre elongation and solidification.
-The experimental apparatus usesa similar spinneret to that in [Figure apparatus used for solution blow spinning or melt blowing], and in addition to the gas flowa potential difference is applied between the spinneret and the collector.This technique has been shown to have significant potential in medicalapplications: in 2014, Jiang et al.
-applied electroblowing in vitro and invivo to deliver a homogeneous and continuous layer of a medical glue tostop bleeding during liver resection.
-[31]
-
-More recently, Balogh et al.
-prepared fibres of 2-hydroxypropyl-\ensuremath{\beta }-cyclodextrin loaded with sodium diclofenac.
-[32] They found that whenelectrospinning this system, very frequent clogging of the spinneretoccurred.
-Electroblowing overcame this issue and additionally allowedfaster flow rates to be used, increasing the amount of material thatcould be produced.
-However, the uniformity of the fibre products wascompromised, with more `beads-on-string' type morphology seen withthe blown products.
-In both cases, the fibres comprised amorphous soliddispersions with no crystalline drug evident.
-The electroblown fibresdissolved a little more slowly than those from electrospinning, but stillmuch more rapidly than a physical mixture of drug and cyclodextrin.
-
-A subsequent study using Eudragit E and itraconazole (anantifungal active pharmaceutical ingredient) also found that a fasterflow rate could be used in blowing, but that the fibre products from thelatter had less regular morphologies.
-[33] Again, the drug was amorphouslydispersed in the fibres, and the dissolution profiles of the electrospun andelectroblown systems were very similar.
-
-\subsubsection{Microfluidic forces}Microfluidic spinning is based on the use of micro (sub-millimetre)channels.
-A large number of these are located in a single microfluidicchip, and the rate and time of liquid expulsion from each channel are precisely controlled by computer.
-Microfluidic spinning can be coupled withelectrospinning, as described in detail in a recent review by Cheng et al.
-[51]While the productivity of microfluidic methods is a major challenge inscale-up, the technique offers the ability to generate fibres with a highlevel of complexity not easily achievable by electrospinning.
-For example,using a digitally programmed microfluidic flow, Kang et al.
-created functional microfibres with continuous spatiotemporal coding along thelength of the fibre.
-[52] The fibres contained varied chemical compositionsand topography, and localised bioactive agents.
-
-Microfluidic spinning therefore has the potential to enable veryprecisely tuneable loading of different drugs into a single fibre, allowingfor programmable release in different parts of the body at differenttimes.
-The technique is beginning to be explored for drug deliveryapplications.
-However, the materials used in microfluidics are usuallyhydrogels (crosslinked polymer networks solvated with water).
-Theseoften have fast degradation rates and as a result can be unsuitable forthe extended release of drugs, particularly small molecules.
-To helpmitigate this problem, Chae et al.
-developed a microfluidic spinningmethod using an isopropyl alcohol sheath flow with an aqueousalginate core flow.
-[53] This innovation resulted in nanofibres made ofhighly ordered alginate molecules.
-Ahn et al.
-loaded ampicillin intoalginate fibres prepared in this manner, [54 and found that the orderedstructure delayed fibre degradation, allowing extended-release profileof ampicillin over 7 days.
-
-\subsubsection{Mechanical force}
-
-\subsection{Dispensing nozzle: Coaxial / Monoaxial: Single nozzle / Multinozzle}
-
-\subsection{Nozzle-to-substrate distance}
-
-\subsubsection{Near Field Spinning}Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}.
-Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector.
-The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}.
-Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.
-
-\subsubsection{Far Field Spinning}In  a far field electrospinning the process continues ...
-Decreasing the jet diameter, the surface charge density increases and the resulting high repulsive forces split the jet into several smaller jets.
-The jet is seriously elongated by a bending and whipping processes caused by electrostatic repulsion initiated at small bends in the fiber, until it is finally deposited on the collector.
-Two types of collector may be used, either stationary or rotary collector.
-
-\section{"Electro - DC - monoaxial - solution - NF - spinning"}
-
-\bgroup
-\fixFloatSize{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}{\includegraphics{images/397f8131-9380-45a0-8289-a666e0d4f8c6-udrf_nfes.jpg}}{}
-\makeatother 
-\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130} .}}
-\label{f-fe28447572e9}
-\end{figure*}
-\egroup
-Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
-This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
-
-Nanofibers are fibers with diameters in the nanometer range. The development of nanofibers has greatly enhanced the scope for meeting up the modern world challenges.
-
-Currently there are two types of electrospinning systems available for producing nanofiber: needle based electrospinning and needleless electrospinning.
-This paper summarizes the basic mechanism of various types of needle based and needleless spinning systems described in various literatures by many researchers.
-
-\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES.
-Low voltage near field electrospinning produces thinner fibers with lower voltages.
-Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching.
-Bisht et al.
-\unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
-
-\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\protect\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\protect\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\protect\cite{527120:11974304}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Suspension NFES \unskip~\protect\cite{527120:12033656}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\protect\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\protect\cite{527120:11974320}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\protect\cite{527120:11974312}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\subsection{Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\protect\cite{527120:11974307}}Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-
-\section{Polymer Solution}
-In electrospinning, it is typically agreed that the diameter of the fibers increased with higher concentration due to greater viscosity which withstands stretching.
-In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}.
-However, in separate studies by Pan et al.\unskip~\cite{527120:11974317,527120:12321129} using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
-\begin{table*}[!htbp]
-\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
-\label{tw-8687dd17082c}
-\def\arraystretch{1}
-\ignorespaces 
-\centering 
-\begin{tabulary}{\linewidth}{LL}
-\tbltoprule Observation & Concentration Adjustement\\
-\tblmidrule 
-Dripping, no stream &
-  Increase\\
-Splitting small droplets &
-  Increase slightly\\
-Steady stream &
-  No concentration adjustment\\
-Splitting large globs &
-  Decrease slightly\\
-Nozzle clogging  &
-  Decrease\\
-\tblbottomrule 
-\end{tabulary}\par 
-\end{table*}
-
-\subsection{Polymers}The polymer selection is in function on the intended application.
-For example, a fast dissolving hydrophilic polymer such as poly(ethylene oxide) (PEO) is used for fast drug delivery systems.
-Otherwise, slow dissolving polymers such as poly($\varepsilon $-caprolactone) (PCL) or poly(lactic-co-glycolic acid) (PLGA) are implemented.
-\unskip~\cite{527120:13082763}
-
-The polymer molecular weight along with the polymer concentration and solvent selection have a direct effect on the solution viscosity, conductivity and surface tension, hence the solution behavior in the electrospinning process.
-The spunable viscosity range varies with the polymer and solvent.
-
-Solutions with low viscosity are prone to insufficient polymer chain entanglements to produce fibers.\unskip~\cite{527120:13082763} On the other hand, if the solution is too viscous, then the surface tension cannot easily be overcome by the electric field.
-In both cases, the result can be droplets or particles forming rather than fibers; see Table~\ref{tw-8687dd17082c}.
-
-\subsection{Solvents}The solvent used must be capable of dissolving the polymer of interest at an appropriate concentration to form fibers, and must posses a suitable volatility.
-A low-volatility solvent like water may fail to evaporate completely over the distance between the spinneret and the collector.
-When the fibers form, they will hence contain residual water owing to this incomplete evaporation.
-The residue solvent will subsequently evaporate from the fibers upon storage, resulting in ribbon-like (flattened) fibers, wrinkles on the fiber surface or fused fibers.
-On the other hand, a high-volatility solvent may evaporate very quickly, leading to larger fiber diameters (less time for elongation before solidification) and clogging of the spinneret (due to drying of the liquid at the spinneret before jetting, or drying of the Taylor cone during jetting).
-Solvents commonly used for electrospinning include ethanol, chloroform, dichloromethane and hexafluoroisopropanol.
-
-Mixtures of miscible solvents can be used to ensure that sufficient polymer can be dissolved to give a solution of appropriate viscosity and volatility with suitable dielectric constant range to allow fiber formation.
-However, care must be taken because using a mixture of solvents with very different volatilities can result in porous fiber structures, as reported by Katsogiannis et al.
-for organic solvent mixtures with dimethyl sulfoxide (DMSO).\unskip~\cite{527120:13082766} DMSO evaporates much more slowly than the organic solvents used, which results in its incorporation into the fibers.
-The DMSO will eventually evaporate, yielding porous fibers.
-
-It is also important to take into account the surface tension of the solution.
-Solvents with very high surface tensions (e.g.
-water) can result in instability arising during the spinning process, and a broad range of fiber diameters in the products.
-If necessary, a surfactant can be added to reduce the surface tension, but this will be incorporated into the fibers produced.
-
-\section{Effect of the NFES Parameters}
-
-\bgroup
-\fixFloatSize{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}{\includegraphics{images/d29b646e-eca6-4b31-ab15-4cfc6fc94809-udrf_electrospinningvariants.jpg}}{}
-\makeatother 
-\caption{{Near-Field ES Process Parameters}}
-\label{f-3629d3a3f9cf}
-\end{figure*}
-\egroup
-To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
-Kameoka et al.\unskip~\cite{527120:12321556} demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip.
-
-Near-field electrospinning, has exhibited to be capable fabricate nano fibers over and nano fiber patterns \unskip~\cite{527120:11974321}.
-Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner.
-Using a spinneret with a reservoir (e.g.
-syringe) of solution generally produces fibers with diameter of a few micrometers \unskip~\cite{527120:11974310,527120:11974326}, since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through.
-
-Coppola et al.\unskip~\cite{527120:11974307} have showed a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop, averting the issue of nozzle clogging.
-The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al.'s\unskip~\cite{527120:11974326} work.
-
-\subsection{Nozzle spinneret}The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al.\unskip~\cite{527120:11974306} used a 100 $\mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
-The nozzle most commonly comprises a simple narrow-bore, blunt-end metal needle.
-The diameter of the needle can vary, but most commonly researches work with internal diameters below 1 $mm $ .
-This translates to needles of gauge 18{\textendash}22.
-In general, this simple spinneret design can be used to achieve successful spinning.
-A blunt-end rather than a tapered-end for the needle exit is important as the size distribution of the products increase with an increase in needle tip angle.
-However, it should be noted that there will be some interactions between the solvent and polymer molecules in the solution and the metal surface of the spinneret.
-There will exist some attractive forces between the polar groups in the polymer and the electropositive metal surface, which can act counter to the drawing force of the electric field and can pull the polymer solution back into the spinneret.
-It has been found that coating the spinneret exterior in a non-conductive and non-stick polymer such as Teflon can reduce these interactions.\unskip~\cite{527120:13082768} As a result, the electrical energy can be more efficiently used to elongate and narrow the polymer jet, and narrower fibers can be produced.
-In addition, strong attractive forces between the polymer jet and the metal spinneret can result in fibers becoming attracted to the needle, leading to lower yields and potentially to blocking of the exit orifice.
-This effect too can be ameliorated using an epoxy coating.\unskip~\cite{527120:13082811}
-
-\subsection{Applied Voltage}In recent literature, near field electrospinning has been studied to reduce the fiber diameter and to improve the fiber deposition accuracy.
-Camillo et al.\unskip~\cite{527120:12322072} demonstrated that the application of a modified fine tip nozzle enables the fabrication of 100 $nm $ diameter fiber at a nozzle-to-substrate distance of 500 $\mu m $ and an applied voltage of 1.5 $kV $ .
-On the other hand, Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} came to the conclusion higher voltages yield thicker micro-fibers with a loss in jet stability.
-
-This discrepancy in literature between the applied voltage and resulting fiber diameter is due to the relationship with other variables such as nozzle-to-substrate distance and solution deposition rate.
-For instance, if a high voltage is applied at a low deposition rate then electrospraying is achieved, meaning the formation of several non-continuous fibers.
-The applied voltage shall be sufficient to break the surface tension and initiate the jet, but low enough to avoid multiple jets at the nozzle tip.
-
-Bisht et al.\unskip~\cite{527120:11973130} achieved the fabrication of thinner fibers with spatial control by reducing the applied voltage to 200-600 $V $  at a nozzle-to-substrate distance of 0.5-1 $mm $.
-The low voltage setting does not create enough charge to break the polymer solution surface tension to initiate the electrospinning process.
-
-Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} initiated the electrospun fibers by mechanically pull the polymer solution at the nozzle tip using a micro-probe tip.
-Chang and coworkers reduced the applied voltage from 1.5 $kV $ to 600 $V $ with a nozzle-to-substrate distance of 500 $\mu m $ to yield a fiber diameter between 3 $\mu m $  and 50 $nm $ .
-With an applied voltage of 200 $V $ and a nozzle-to-substrate distance of 1 $mm $ , PEO nano fibers were deposited with a diameter about 20 $nm $.
-
-In near-field electrospinning, the applied voltage has an impact on the produced fiber morphology.
-For instance, a voltage higher or lower to the optimum voltage will translate into an increase in fiber diameter.
-Song et al.\unskip~\cite{527120:11974320} demonstrated that a decrease in voltage from 400 to 500 $V $ can reduce the fiber diameter from 160 to about 60 $nm $with a nozzle-to-substrate distance of 20 $\mu m $.
-The optimum voltage is achieved when a balance is attained between the stretching of the jet and the speed at which it hits the substrate.
-The increase of voltage yields thinner fibers as it causes greater stretching, and a greater jet acceleration.
-
-Another workaround to break the polymer solution surface tension is to initialize the NFES process with a higher voltage and then lower the voltage once the jet is created.
-Huang et al.\unskip~\cite{527120:11974311} implemented the previous and yield ordered fibers with a distance between adjacent fibers of 50 $\mu m $.
-In most cases, a positive voltage is applied to the spinneret.
-
-\subsection{Nozzle-to-substrate distance}In NFES, the fiber morphology can be altered by the control of the height between the nozzle and the substrate (collector).
-With the decrease of the nozzle-to-substrate distance, the electric field strength increases; however it can cause incomplete solvent volatilisation and possible short circuits between the collector and the nozzle tip.
-
-An optimal nozzle-to-substrate distance shall be defined to ensure the fabrication of dry continuous fibers.
-If the solvent is not well evaporated, the produced fibers are prone to defects; on the other hand if solidification happens too fast, the solids can block the spinneret which can prevent a continuous fiber yield.
-Furthermore, the polymer jet will discharge itself as soon as possible, therefore long distances can result in low yields.
-
-Typically, metal nozzle tips are used, with small inner diameters.
-From literature, needles with small diameters produce thinner fibers.
-A thin nozzle tip can help the reduction of the fiber diameter, but also it is more likely to become blocked.
-
-\subsection{Electric field}Recent literature suggests that the fiber morphology depends on the electric field profile created by the applied voltage during NFES.
-Since the electric field is an induced force that attracts the solution jet towards the desired location within the collector.
-
-Bisht et al.\unskip~\cite{527120:11973130} and Min et al.\unskip~\cite{527120:11974316} have reported the ability to electrospin nano fibers with high accuracy.
-Min et al.
-\unskip~\cite{527120:11974316} implemented a NFES setup with multiple "field-effect transistors" on a flexible polyacrylate collector with an x-y stage velocity of 13.3 $cm/s $ to fabricate fibers with a diameter about 289 $nm $ and a distance between adjacent fibers of 50 $\mu m $.
-
-On the other hand, Bisht et al.\unskip~\cite{527120:11973130} showed evidence of fabricated fibers with low-voltage NFES with high accuracy and precision.
-Bisht et al.'s suspended fibers were deposited over carbon posts with a distance between adjacent fibers of 100 $\mu m $ with diameter of 30 $\mu m $\unskip~\cite{527120:11973130}.
-
-The employment of guided electrodes in NFES, adapts the fabrication process to yield a more accurate fiber deposition.
-For instance, Kim et al.\unskip~\cite{527120:11974313} manufactured ink patterns on a paper with silver nano particles.
-The printed patterns aid the fibers to land on the desired location.
-Kim et al.\unskip~\cite{527120:11974313} electrospun the fibers with a distance between adjacent fibers of 150 $\mu m $.
-
-Xu et al.\unskip~\cite{527120:11974325} created a straight jet from the nozzle tip to the substrate using a guiding electrode underneath the collector.
-The purpose of the guiding electrode is to adjust the path of the NFES jet.
-With the guiding electrode implementation, the fiber's spread was reduced from 74 $\mu m $ to 7 $\mu m $.
-
-\subsection{Substrate}Due to the close distance between the grounded substrate and the charged spinneret in NFES, the set up is prone to electrical shorts.
-In NFES, when a short circuit takes place, the electrospinning process is interrupted resulting in the fabrication of discontinuous fibers.
-Two workarounds to avoid electrical shorts is to lower the applied voltage and to install less conductive substrates \unskip~\cite{527120:11974315,527120:12322289}.
-
-Liu et al.\unskip~\cite{527120:11974315} discovered that the fiber alignment is improved by using a glass-cooper foil substrate, however the well aligned fibers are spoiled after prolonged depositions due to residual charges.
-Additionally, the effect of residual charges is amplified with the used collector substrate contains a conductive layer and a non-conductive layer\unskip~\cite{527120:11974315}.
-
-On the other hand, Choi et al.\unskip~\cite{527120:12322289} implemented a hydrophobic substrate to deposit the fibers with plasma treatment to increase the conductivity of selected areas.
-NFES was carried put with precise deposition as the fibers were placed as per the desired design within the hydrophilic substrate.
-\begin{landscape}
-\makeatletter\@twocolumnfalse\makeatother
-\begingroup
-\makeatletter\if@twocolumn\@ifundefined{theposttbl}{\gdef\TwoColDocument{true}\onecolumn\onecolumn}{}\fi\makeatother \setlength\LTcapwidth{\textheight}
-\begin{longtable}{p{\dimexpr.1641\linewidth-2\tabcolsep}p{\dimexpr.13520000000000005\linewidth-2\tabcolsep}p{\dimexpr.1662\linewidth-2\tabcolsep}p{\dimexpr.46839999999999996\linewidth-2\tabcolsep}p{\dimexpr.0661\linewidth-2\tabcolsep}}
-\caption{{Electrospun Polymer Solutions - Solution and Process Parameters} }
-\label{tw-bab4042dace7}
-\def\arraystretch{1}\\\endfirsthead \hline \noalign{\vskip3pt} \noalign{\textit{Table \thetable\ continued}} \noalign{\vskip3pt} \hline \endhead \hline \noalign{\vskip3pt} \noalign{\textit{\hfill Continued on next page}} \noalign{\vskip3pt} \endfoot \endlastfoot
-\tbltoprule Polymer(s) & Solvent(s) & NFES Variant & Process Parameters and Fiber Characterization & Ref.\\
-\tblmidrule 
-Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) &
-  Deionized water &
-  Low-Voltage NFES (LV NFES) &
-  \textbf{Solution Concentration:} 1, 2, and 3 $wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 27 gauge type 304; stainless steel needle \mbox{}\protect\newline \textbf{Solution deposition rate:} lower than 1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Pyrolyzed SU-8 carbon and Si \mbox{}\protect\newline \textbf{Applied voltage: }polymer jet initiated at 400-600 $V $ and dispensed at 200-400 $V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10-40$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 50-425$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11973130}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000 $g/mol $) with Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  acetonitrile toluene mixture (65/35); acetic acid toluene (17/83); pure toluene &
-  Typical NFES process &
-  \textbf{Solution Concentration:} \mbox{}\protect\newline 10$mg $ of MEH-PPV in 2$mL $ of toluene; 500$\mu L $ of MEH-PPV solution with 250$mg $ of PEO in 3.5$mL $ of acetonitrile / toluene (65 / 35); 500$\mu L $ of MEH-PPV solution with 250$mg $ of PEO in 3$mL $ of acetic acid / toluene (17 / 83).
-The resulting MEH-PPV/PEO concentration is 0.08 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} mm-diameter tip Tungsten spinneret in a 26 gauge needle \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} SiO2/Si (oxide thickness = 800 nm) \mbox{}\protect\newline \textbf{Applied voltage:} around 1.3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 100$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} around 100$\mu m $ &
-  \unskip~\cite{527120:11974305}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MV = 300,000 $g/mol $) &
-  Water &
-  Scanning Tip Electrospinning and NFES &
-  \textbf{Solution Concentration:} 7$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 200$\mu m $ and inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 1.5 $kV $ and dispensed at 600$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 120$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 709$\pm $131$nm $; 49-74$nm $ when applied voltage is 800$V $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{ Not determined} \mbox{}\protect\newline \textbf{Notes:} 108$m $ yield in 15$min $ with a fiber diameter of 709$\pm $131$nm $ &
-  \unskip~\cite{527120:11974306}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(vinylidine fluorid) (PVDF; MW = 440,000 $g/mol $) &
-  N,N Dimethylformamide (DMF) &
-  Helix Electrohydro-dynamic Printing (HE-printing) &
-  \textbf{Solution Concentration:} 1.8$g $ PVDF in 4.1$g $ of DMF and 4.1$g $ of acetone.
-The resulting concentration is 18\% PVDF.
-\mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 510$\mu m $ and inner diameter of 260$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 400$nL/min $ \mbox{}\protect\newline \textbf{Nozazle-to-substrate distance:} 10-50$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Poly(dimethylsiloxane) (PDMS) on Ecoflex \mbox{}\protect\newline \textbf{Applied voltage:} 1.5{\textendash}3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0-400$mm/min $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 1.5-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974308}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Polyhedral Oligomeric Silsesquioxane-Poly(Carbonate-Urea)Urethane (POSS-PCU) and Polyhedral Oligomeric Silsesquioxane Poly(Caprolactone-Poly(Carbonate-Urea)Urethane) (POSS-PCL-PCU) \mbox{}\protect\newline (Dry Polycarbonate MW = 2000 $g/mol $) &
-  Dimethyl acetamide (DMAC) and 1-Butanol &
-  Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting &
-  \textbf{Solution Concentration: }POSS-PCU and POSS-PCL-PCU used in 20\%$w/w $ concentration in DMAC \mbox{}\protect\newline \textbf{Nozzle:} needle of 750 $\mu m $ in diameter \mbox{}\protect\newline \textbf{Solution deposition rate:} less than 1$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: }about between 500$\mu m $ to 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 8.0-10.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5-50$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }250$\mu m $ &
-  \unskip~\cite{527120:11974310}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Distilled water &
-  Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) &
-  \textbf{Solution Concentration:} 6$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} 1200$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 7.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 2 $kV $ and dispensed at 0.8-1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} around 400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 200-350$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 5$\mu m $ &
-  \unskip~\cite{527120:11974311}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Deionized water and ethanol with a volume ratio of 3:1 &
-  Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) &
-  \textbf{Solution Concentration:} 8$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Outer airflow passage diameter: 1$mm $ Airflow gas pump pressure: 25$kPa $ Inner liquid passage diameter: 0.21$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 30$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Silicon \mbox{}\protect\newline \textbf{Applied voltage:} about 2$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 1-20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 3.73 $\pm $ 1.37$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }5.13 $\pm $ 6.67$\mu m $ &
-  \unskip~\cite{527120:11974312}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(Vinylidene Fluoride) (PVDF; MW = 534,000 $g/mol $) &
-  Acetone and Dimethyl Sulfoxide (DMSO) &
-  3D Electrospinning &
-  \textbf{Solution Concentration:} 17$wt\% $ PVDF; 1.7$g $ of PVDF, 5$g $ of acetone, 0.5$g $ of Capstone FS-66, 5$g $ of DMSO \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 14$\;nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 750$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} A4 size commercial printing paper (Double A) \mbox{}\protect\newline \textbf{Applied voltage:} 1.9$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974313}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(9-Vinyl Carbazole) (PVK; MW = 1,100,000 $g/mol $) &
-  Styrene &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 3.96$wt\% $ PVK in styrene \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 500$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} around 2.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Si/SiO2 \mbox{}\protect\newline \textbf{Applied voltage:} 3-4$kV $ \mbox{}\protect\newline x-y stage velocity: 13.3$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 289.26 $\pm $ 35.37$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }50$\mu m $ \mbox{}\protect\newline \textbf{Notes:} 15$m $ yield in 2$min $ &
-  \unskip~\cite{527120:11974316}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Polystyrene (PS; MW \textit{Not determined}) &
-  1,2,4-Trichloro benzene &
-  Electrohydro-dynamic (EHD) jet printing &
-  \textbf{Solution Concentration:} 1 to 5$wt\% $ PS \mbox{}\protect\newline \textbf{Nozzle:} Glass nozzle inner diameter of 2$\mu m $ and outer diameter of 2.66$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance}: 20, 30, 40$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition: }Si \mbox{}\protect\newline \textbf{Applied voltage:} 500 to 400$V $ in 25$V $ increments \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.01-10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 60-170$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974320}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  \textit{Not determined} &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} Si \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 25$\mu m $ &
-  \unskip~\cite{527120:11974321}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
-  Distilled water &
-  Multinozzle NFES &
-  \textbf{Solution Concentration:} 5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} four-nozzle and six-nozzle array with needle spacing changes from 1.5$mm $ to 3.5$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 1-3$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 1.7-2.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.47$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 3-5 $mm $ &
-  \unskip~\cite{527120:11974322}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
-  Distilled water &
-  Multinozzle NFES &
-  \textbf{Solution Concentration:}5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 0.18$mm $ and outer diameter of 0.36$mm $; with needle spacing changes from 2.0$mm $ to 3.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 3.0-4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition: } \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 2.0-3.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 218-326$\mu m $ &
-  \unskip~\cite{527120:11974323}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &
-  Distilled water &
-  Multinozzle NFES &
-  \textbf{Solution Concentration:}5 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 180$\mu m $ and outer diameter of 360$\mu m $; with needle spacing changes of 2.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} chromium-plated glass \mbox{}\protect\newline \textbf{Applied voltage:} 2.5$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 2.3002-2.7224$mm $ &
-  \unskip~\cite{527120:11974324}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) &
-  \textit{Not determined} &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &
-  \unskip~\cite{527120:11974325}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Gelatin \mbox{}\protect\newline (porcine skin; MW \textit{Not determined}) &
-  Acetic Acid and Ethyl Acetate &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &
-  \unskip~\cite{527120:11974326}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Water/Ethanol (v/v = 60/40) &
-  Typical NFES process &
-  \textbf{Solution Concentration:} PEO concentrations of 16\% and 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974327}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Water/Ethanol (v/v = 3/1) &
-  Electrohydro-dynamic Direct-Write (EDW) &
-  \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless needle with inner diameter of 210$\mu m $ and outer diameter of 400$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L/h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(ethylene terephthalate) (PET) \mbox{}\protect\newline \textbf{Applied voltage:} 3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 700$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 15-35$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 70$\mu m $ &
-  \unskip~\cite{527120:11974328}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &
-  Deionized water &
-  Mechano-Electrospinning &
-  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless steel nozzle with inner diameter of 160$\mu m $ and outer diameter of 310$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2-5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicone \mbox{}\protect\newline \textbf{Applied voltage:}polymer jet initiated at 2$kV $ and dispensed at 1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 200-400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} from 344$\pm $32 to 214$\pm $27$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974304}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(co-Glycolic) acid (PLGA; MW \textit{Not determined})  &
-  Dimethyl Carbonate (DMC) &
-  Tethered Pyro-Electrohydro-dynamic Spinning (TPES) &
-  \textbf{Solution Concentration:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle:} nozzle-free \mbox{}\protect\newline \textbf{Solution deposition rate:} The drop reservoir is placed directly on a flat substrate \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} Taylor's cone is focused and put in direct contact with the collector \mbox{}\protect\newline \textbf{Substrate composition:} Poly(tetrafluoroethylene) (PTFE) coated glass slide \mbox{}\protect\newline \textbf{Applied voltage:} pyro-electric field of between 2.7 $x10^{7}\;V/m $ and 5.5$x10^{7}\;V/m $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 304.7$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:11974307}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) with Tetrabutylammonium tetrafluoroborate (TBF; MW \textit{Not determined}) and SU-8 2002 &
-  N,N Dimethylformamide (DMF) &
-  Typical NFES process &
-  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline $\mu m $$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} \textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
-  \unskip~\cite{527120:12033655}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; 200,000 $g/mol $) &
-  Water:Ethanol (3:2) &
-  Suspension NFES &
-  \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} stainless steel needle (25 G) with inner diameter of 0.25$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 3$nL/s $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} between 0.5 and 10$mm $ with 0.5$mm $ increments \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon electrodes \mbox{}\protect\newline \textbf{Applied voltage:} 1.6$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50, 150, and 250$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 0.1 and 0.5$mm $ &
-  \unskip~\cite{527120:12033656}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
-Poly(ethylene oxide) (PEO; MW = 400,000 $g/mol $) &
-  Deionized water &
-  Typical NFES process &
-  \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &
-  \unskip~\cite{527120:12033657}\\
-\tblbottomrule 
-\end{longtable}
-\endgroup
-\makeatletter\@ifundefined{TwoColDocument}{}{\twocolumn}\makeatother 
-\end{landscape}
-
-\section{Conclusion}
-
-\bgroup
-\fixFloatSize{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}{\includegraphics{images/e4441f91-c9b9-48f1-a3ed-5ec3e5033092-uplt_diametervolage.png}}{}
-\makeatother 
-\caption{{Applied volage vs. Fiber diameter}}
-\label{f-59ed68f95344}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}{\includegraphics{images/6198525c-7b44-494e-a092-206ecb3c8f9c-uweightdiameterplot.png}}{}
-\makeatother 
-\caption{{Solution concentration vs. Fiber diameter}}
-\label{f-0ba4df766d66}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}{\includegraphics{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}}{}
-\makeatother 
-\caption{{Solution concentration vs. Molecular weight}}
-\label{f-ab38f7e015f7}
-\end{figure*}
-\egroup
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\section{NFES Achievements \& Challenges}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}
-
-\bibliographystyle{elsarticle-num}
-
-\bibliography{\jobname}
-
-\end{document}

### 2020-05-25 myThesis/thesis_LaTeX/main.tex
NFES data collection
thesis  structure

--- 2019-01-22 thesis_1/main.tex
@@
 % Two side (alternating margins) for binding by default, uncomment to switch to one side
-%oneside,
+oneside,
 % ngerman for German
 english,
-% Single line spacing, alternatives: onehalfspacing or doublespacing
-singlespacing,
+% Single line spacing, alternatives: singlespacing, onehalfspacing or doublespacing
+onehalfspacing,
 % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
 %draft,
-% If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
-%nolistspacing,
+% If the document is nolistspacing, onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
+onehalfspacing,
 % Uncomment to add the list of figures/tables/etc to the table of contents
@@
 % Uncomment to place the chapter title next to the number on one line
-%chapterinoneline,
+chapterinoneline,
 % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
-%consistentlayout,
+consistentlayout,
 % The class file specifying the document structure
@@
 \usepackage[T1]{fontenc}
+\usepackage{textcomp} % support the degree symbol
 
@@
 
+% Use tu justify paragraphs
+\usepackage{ragged2e}
+
 % Use the bibtex backend with the authoryear citation style (which resembles APA)
-\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex}
+\usepackage[backend=biber,natbib=true]{biblatex}
+% MLA, APA, or IEEE? - https://www.overleaf.com/learn/latex/Biblatex_citation_styles
+%\usepackage[style=apa, backend=biber]{biblatex}
 
 % The filename of the bibliography
-\addbibresource{example.bib}
+\addbibresource{mainBiblio.bib}
 
@@
 \usepackage[autostyle=true]{csquotes}
+
+% to set default colours
+\usepackage{xcolor}
+\definecolor{mygray}{gray}{0.5}
+
+% for gantt charts
+\usepackage{tikz}
+\usepackage{gantt}
+
+% to rotate pages in landscape
+\usepackage{lscape}
+
+% equation arrows with text
+\usepackage{amsmath}
+
+% insert degree celsius symbol
+\usepackage{textcomp}
+
+% include other pdf pages
+\usepackage{pdfpages}
 
@@
 % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\thesistitle{Thesis Title}
+\thesistitle{Fabrication of graphitic-carbon suspended nanowires through mechanoelectrospinning of photocrosslinkable polymers}
 
-% Your supervisor's name, this is used in the title page, print it elsewhere with \supname
-\supervisor{Dra. Dora \textsc{Medina}}
+% Your supervisor's name, this is used in the title page, print it elsewhere with \supname and \cosupname
+\supervisor{Dr. Héctor Alán \textsc{Aguirre} Soto}
+\cosupervisor{Dra. Dora Iliana \textsc{Medina} Medina}
 
@@
 \university{\href{https://tec.mx/}{Instituto Tecnonólogico y de Estudios Superiores de Monterrey}}
+
+% Your university's campus name and URL, this is used in the title page and abstract, print it elsewhere with \campusname
+\campus{\href{https://tec.mx/}{Campus Estado de México}}
 
@@
 \vspace*{.06\textheight}
-{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
-\textsc{\Large Masters Thesis}\\[0.5cm]      % Thesis type
+{\scshape\LARGE \univname\par} % University name
 
-\HRule \\[0.4cm]                            % Horizontal line
-{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
-\HRule \\[1.5cm]                            % Horizontal line
+\begin{center}
+\includegraphics[width=0.15\textwidth]{./Figures/uniLogo.png}
+\end{center}
+
+\vspace{0.5cm}
+\textsc{\Large Masters Thesis Proposal}\\[0.5cm]      % Thesis type
+
+\HRule \\%[0.5cm]                           % Horizontal line
+{\huge \bfseries \ttitle\par}\vspace{0.0cm} % Thesis title
+\HRule \\[0.5cm]                            % Horizontal line
 
@@
 \supname
+
+\bigskip
+
+\emph{Co-advisor and\\Director of Program:} \\
+% Supervisor name - remove the \href bracket to remove the link
+\href{https://www.medinadora.com/}{\cosupname}
+%\cosupname
 \end{flushright}
-\end{minipage}\\[3cm]
+\end{minipage}\\[0.5cm]
 
@@
 
-\large \textit{A thesis submitted in fulfillment of the requirements\\ for the degree of
+\large \textit{A thesis proposal submitted in fulfillment of the requirements\\ for the degree of
 % University requirement text
-\degreename}\\[0.3cm]
-\textit{in}\\[0.4cm]
+\degreename}\\[0.25cm]
+\textit{in}\\[0.25cm]
 % Research group name and department name
-\groupname\\\deptname\\[2cm]
+\groupname\\\deptname\\[1cm]
 
@@
 \end{titlepage}
+
+%----------------------------------------------------------------------------------------
+%	COMMITTEE'S PAGE
+%----------------------------------------------------------------------------------------
+
+%\includepdf[page=-]{./pdf/AlanDoraSigns}
+
+\begin{committee}
+\addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
+The committee members, hereby, recommend that the proposal by \authorname \text{ }to be accepted to develop the thesis project as a partial requirement for the degree of \degreename.
+
+\begin{flushright} \large
+
+\bigskip
+\bigskip
+\medskip
+
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
+%\href{http://www.alanaguirre.com}{\supname}
+\supname\\
+Tecnológico de Monterrey\\
+\emph{Principal Advisor}
+
+\bigskip
+\bigskip
+\medskip
+
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
+%\href{http://www.alanaguirre.com}{\supname}
+\cosupname\\
+Tecnológico de Monterrey\\
+\emph{Co-Advisor}
+
+\bigskip
+\bigskip
+\medskip
+
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
+%\href{http://www.alanaguirre.com}{\supname}
+Dr. Marc \textsc{Madou}\\
+Tecnológico de Monterrey\\
+\emph{Committee Member}
+
+\bigskip
+\bigskip
+\medskip
+
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
+%\href{http://www.alanaguirre.com}{\supname}
+Dr. Sergio Omar \textsc{Martínez} Chapa\\
+Tecnológico de Monterrey\\
+\emph{Committee Member}
+
+\end{flushright}
+
+\vfill
+
+\begin{center}
+
+\bigskip
+\bigskip
+\medskip
+
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
+\cosupname \\
+\emph{Director of Program in Nanotechnology}\\
+School of Engineering and Sciences\\
+%\href{http://www.doramedina.com}{\supname}
+
+\bigskip
+{\addressname \text{, } \large \today}\\[0cm]
+
+\end{center}
+\end{committee}
+
+\cleardoublepage
 
@@
 %----------------------------------------------------------------------------------------
-%	QUOTATION PAGE
+%	LIST OF CONTENTS/FIGURES/TABLES PAGES
 %----------------------------------------------------------------------------------------
 
-\vspace*{0.2\textheight}
+\tableofcontents % Prints the main table of contents
 
-\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
+\listoffigures % Prints the list of figures
 
-\hfill Dave Barry
+\listoftables % Prints the list of tables
 
@@
 
-The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots \\
+Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to their high conductivity.
+Regardless of the high interest in the implementation of carbon nano-wires in several applications and devices, no feasible processes have been developed to fabricate carbon nano-wires with spatial control at a reasonable cost.
+Carbon nano-wires have been fabricated with the use of a photoresist, but little is known about polymers that can produce more conductive carbon nano-wires after pyrolysis.
+Various polymer solutions have been tested in near field electrospinning (NFES) and photopolymerization separately, however, few have been tested for nano-wire fabrication purposes through pyrolysis.
+The intention behind the thesis proposal is to implement rheology analyses of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nano-wires with them.
+This thesis work arises from the need to test a greater variety of polymers with the goal to design a polymer solution to fabricate carbon nano-wires with better conductivity than the current SU-8 polymeric nano-fibers.
+The research process will include the design of polymer solutions that can be electrospun, photopolymerized, and then pyrolyzed into conducting carbon nanowires.
+On the other hand, it is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of conductive carbon nano-wires in an inexpensive, continuous, simple and reproducible manner as central components for nano-sensors.
+\\
 
@@
 %----------------------------------------------------------------------------------------
-%	LIST OF CONTENTS/FIGURES/TABLES PAGES
-%----------------------------------------------------------------------------------------
-
-\tableofcontents % Prints the main table of contents
-
-\listoffigures % Prints the list of figures
-
-\listoftables % Prints the list of tables
-
-%----------------------------------------------------------------------------------------
 %	ABBREVIATIONS
@@
 
+\textbf{CEM} & \textbf{C}ampus \textbf{E}stado de \textbf{M}éxico\\
+
+\textbf{CNWs} & \textbf{C}arbon \textbf{N}ano-\textbf{w}ire\textbf{s}\\
+
+\textbf{DC} & \textbf{D}irect \textbf{C}urrent\\
+
+\textbf{EMS} & \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\
+
+\textbf{FFES} & \textbf{F}ar \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
+
 \textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\
 
+\textbf{MA} & \textbf{Ma}ssachusetts\\
+
+\textbf{MEMS} & \textbf{M}icro\textbf{e}lectro\textbf{m}echanical \textbf{S}ystems\\
+
+\textbf{MNT} & \textbf{M}aestría en \textbf{N}ano\textbf{t}ecnología \emph{(Master of Science in Nanotechnology)}\\
+
+\textbf{MTY} & \textbf{M}on\textbf{t}erre\textbf{y} \emph{or} Campus \textbf{M}on\textbf{t}erre\textbf{y}\\
+
+\textbf{NFES} & \textbf{N}ear \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
+
+\textbf{USA} & \textbf{U}nited \textbf{S}tates of \textbf{A}merica\\
+
+\textbf{UV} & \textbf{U}ltra\textbf{v}iolet\\
+
 \end{abbreviations}
-
-%----------------------------------------------------------------------------------------
-%	PHYSICAL CONSTANTS/OTHER DEFINITIONS
-%----------------------------------------------------------------------------------------
-
-\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
-
-% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it
-
-Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
-%Constant Name & $Symbol$ & $Constant Value$ with units\\
-
-\end{constants}
 
@@
 
-$a$ & distance & \si{\meter} \\
-$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
-%Symbol & Name & Unit \\
+%$a$ & distance & \si{\meter} \\
+%$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
+Symbol & Name & Unit \\
 
@@
 %----------------------------------------------------------------------------------------
-%	DEDICATION
+%	PHYSICAL CONSTANTS/OTHER DEFINITIONS
 %----------------------------------------------------------------------------------------
 
-\dedicatory{Dedicated to}
-This thesis work is dedicated to my parents, William and Karen Ryan, who have always loved me unconditionally and whose good examples have taught me to work hard for the things that I aspire to achieve.
-They have been a constant source of support and encouragement during the challenges of graduate school and life.
-I am truly thankful for having you in my life.
+%\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
+
+% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it
+
+%Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
+%Constant Name & $Symbol$ & $Constant Value$ with units\\
+
+%\end{constants}
 
@@
 
-\include{Chapters/Chapter1}
-%\include{Chapters/Chapter2} 
-%\include{Chapters/Chapter3}
-%\include{Chapters/Chapter4} 
-%\include{Chapters/Chapter5}
+\setlength{\parskip}{1.5em} % Paragraph spacing
+%\RaggedRight
+{\fontsize{12}{15} \selectfont
+
+\include{./Chapters/1}
+\include{./Chapters/2}
+\include{./Chapters/3}
+\include{./Chapters/4}
+\include{./Chapters/5}
+\include{./Chapters/6}
+\include{./Chapters/7}
+
+}
+
+%\include{Chapters/__IntroToLaTeX}
+
+%----------------------------------------------------------------------------------------
+%	BIBLIOGRAPHY
+%----------------------------------------------------------------------------------------
+
+\printbibliography[title={References}]
 
@@
 %----------------------------------------------------------------------------------------
-%	BIBLIOGRAPHY
-%----------------------------------------------------------------------------------------
-
-\printbibliography[heading=bibintoc]
-
-%----------------------------------------------------------------------------------------
 

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/1.tex
thesis re-organisation

@@
 
-\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title
+\chapter{Introduction} % Main chapter title
 
@@
 %----------------------------------------------------------------------------------------
-\section{}
+\section{Problem definition and motivation}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+%Qué metodos se han utilizado? (SU-8)
+%Porqué se quiere fabricar las fibras de carbono
+%Para qué aplicaciones se han usado
+%Porqué es importante la conductividad
+%Porqué es importante que sea puro carbono
+
+%----------------------------------------------------------------------------------------
+%	SECTION 2
+%----------------------------------------------------------------------------------------
+\section{Research Questions}
+
+%----------------------------------------------------------------------------------------
+%	SECTION 3
+%----------------------------------------------------------------------------------------
+\section{Hypothesis}
+
+%----------------------------------------------------------------------------------------
+%	SECTION 4
+%----------------------------------------------------------------------------------------
+\section{Objectives}
+
+%----------------------------------------------------------------------------------------
+%	SECTION 5
+%----------------------------------------------------------------------------------------
+\section{Dissertation Outline}

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/2.tex
thesis  structure
thesis re-organisation

--- 2020-05-25 myThesis/thesis_LaTeX/Chapters/1.tex
@@
 
-\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title
+\chapter{Carbon Nanowires Research Developments in Terms of Published Papers, Synthesis and Production} % Main chapter title
 
-\label{Chapter:1}
+\label{Chapter:2}
 
@@
 \section{}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/3.tex
thesis  structure
thesis re-organisation

--- 2020-05-25 myThesis/thesis_LaTeX/Chapters/1.tex
@@
 
-\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title
+\chapter{Near-Field Electrospinning as an Affordable Way to Gain Spatial Control} % Main chapter title
 
-\label{Chapter:1}
+\label{Chapter:3}
 
@@
 %----------------------------------------------------------------------------------------
-\section{}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\section{Review of Polymer Solutions for NFES with Spatial Control}

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/4.tex
thesis  structure
thesis re-organisation

--- 2020-05-25 myThesis/thesis_LaTeX/Chapters/1.tex
@@
 
-\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title
+\chapter{Compatible Polymer-Solvent Combinations for Near-Field Electrospinning and Pyrolysis} % Main chapter title
 
-\label{Chapter:1}
+\label{Chapter:4}
 
@@
 %----------------------------------------------------------------------------------------
-\section{}
+\section{Design and Selection of Candidate Spunable Polymer Solutions}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+%high molecular weight, polymer-solution interaction (straight chains)
+
+\subsection{Rheology of candidate polymer solutions}
+
+%----------------------------------------------------------------------------------------
+%	SECTION 1
+%----------------------------------------------------------------------------------------
+\section{Effect of aromatic groups in oxygen-free polymers in NFES and Pyrolysis}

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/5.tex
thesis  structure
thesis re-organisation

--- 2020-05-25 myThesis/thesis_LaTeX/Chapters/1.tex
@@
 
-\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title
+\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning and Photopolymerization} % Main chapter title
 
-\label{Chapter:1}
+\label{Chapter:5}
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+%Were the selected candidates electrospunable?
+%Fiber morphology

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/6.tex
thesis  structure
thesis re-organisation

--- 2020-05-25 myThesis/thesis_LaTeX/Chapters/1.tex
@@
 
-\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title
+\chapter{Fabrication of Conductive Carbon nanofibers by Pyrolysis of Polymeric Fibers} % Main chapter title
 
-\label{Chapter:1}
+\label{Chapter:6}
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+%Yield rate
+%Carbon content
+%Conductivity
+%Fiber morphology

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/7.tex
thesis  structure
thesis re-organisation

--- 2020-05-25 myThesis/thesis_LaTeX/Chapters/1.tex
@@
 
-\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title
+\chapter{Comparison of the Carbon Fibers Obtained Against SU8-based Carbon Fibers} % Main chapter title
 
-\label{Chapter:1}
+\label{Chapter:7}
 
@@
 %----------------------------------------------------------------------------------------
-\section{}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\section{Fabrication and Characterization of Legacy SU-8 carbon fibers}

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/1.tex
introduction in progress

@@
 \label{Chapter:1}
+
+Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
+\cite{Siddiqui2019} Carbon nano-materials are suitable for catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing, and cancer detection.
+\cite{Siddiqui2019} Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity.
+\cite{Siddiqui2019}
+
+This document bestows a thesis proposal to perform a research to engineer and design a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner.
+The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization, and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials.
+\cite{Cardenas2017} See Figure \ref{fig:fabricationFlowChart}.
+A number of processes have been developed for specific purposes of polymeric nano-fibers, some include surface deposition, composites, and chemical adjustments.
+Polymeric nano-fibers must be also pyrolyzed to generate carbon nano-wires with conductive capabilities \cite{Madou2011} for electrochemical sensing and energy storage purposes.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.95\textwidth]{./Figures/FabricationProcess.png}
+\decoRule
+\caption[Fabrication Process]{Fabrication process of conductive carbon nano-wires to achieve through the proposed dissertation.}
+\label{fig:fabricationFlowChart}
+\end{figure}
+
+Nanotechnology has led to the study of different polymer patterning techniques to integrate carbon nano-wires structures.
+One technique is known as far-field electrospinning, a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibers which are then pyrolyzed at high temperatures.
+One sub-technique derived from electrospinning is near field electromechanical spinning or EMS.
+EMS has proved to deliver high control in patterning polymeric nano-fibers.
+\cite{Cardenas2017}
+
+The proposal is to continue the previous work done in regards to the synthesis of carbon nano-wires.
+Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist.
+\cite{Cardenas2017} This research proposal is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by near field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires.
+The polymer solutions described by Cardenas \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.
+
+Traditional near-field electrospinning or NFES allows large scale manufacturability combined with spatial control of material deposition.
+\cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation, resulting in limited control for nano-fiber patterning in traditional NFES processes.
+Madou et al.
+\cite{Madou2011} conclude that the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.
 
@@
 
+Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques.
+However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis, as it is generally believed that most polymers do not form significant amounts of graphitic carbon when carbonized.
+%The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}.
+In the past years, photopolymerization processes have been applied to the fabrication of nano-structures with the use of an epoxy based photoresist.
+\cite{Boer2014} Photopolymerization techniques deliver patterning resolutions with nano-scale tolerances through two-photon lithography for the production of highly detailed structures \cite{Hribar2014}.
+
+On the other hand, electrospinning has been acknowledged as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires.
+Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner.
+Cardenas \cite{Cardenas2017} showed that electrospinning can be implemented with ease for carbon nano-wire synthesis.
+Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires.
+As stated in \cite{Cardenas2017}, mechano-electrospinning is an early technology invention and brings new challenges, such as the reproducibility of carbon nano-wire production.
+Furthermore, the study of a new fabrication process to produce carbon nanowires that involves mechano-electrospinning will enable spatial control of the structures' patterning.
+
+Since electrospinning seems to be a better alternative for carbon nano-wire fabrication processes; and for that purpose of its implementation, it is required to develop polymer solutions that can be mechano-electrospun, photopolymerized and pyrolyzed into conducting carbon nano-wires.
+Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
+\cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
+\cite{Siddiqui2019} However most applications are not currently feasible due to the lack of a continuous, simple and reproducible fabrication method with inexpensive processes.
+With the newly designed polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more applications will become feasible.
+On the other hand, the new technique will overcome some limitations of other methods such as lithography currently has.
+For instance, patterns created by lithography processes cannot be originated, only replicated, all constituent points of the pattern can only be addressed at the same time, and the process requires the pattern to be encoded into a mask.
+\cite{Landis2011}
+
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\section{Research Questions}
+\section{Hypothesis}
+
+The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the fabrication conductive of carbon nano-wires with specified dimensions (diameter and length).
+The rheological properties of polymer solutions along with synthesis parameters are to be amended by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardenas \cite{Cardenas2017} work.
+PEO is to be replaced as its only purpose is to allow the electrospinning process to take place, but no benefit is obtained from it after pyrolysis.
 
@@
 %----------------------------------------------------------------------------------------
-\section{Hypothesis}
+\section{Research Questions}
+
+\begin{itemize}
+	\item{
+	Is there any evidence of conductive carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
+	}
+	\item{
+	What are the process parameters to consider/control for the fabrication processes of carbon nano-wires? 
+	}
+	\item{
+	What rheological properties are to be controlled/tested to deliver an electrospun-able and pyrozable polymer solution?	
+	}
+	\item{
+	Are there any efforts employed to the design of polymer solutions that can be electrospun, photopolymerized, and pyrolyzed into conducting carbon nanowires?
+	}
+	\item{
+	What are the optimal fabrication parameters for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
+	}
+	\item{
+	What materials can be used to ease the electrospinning process and favor the carbon nano-wire properties after pyrolysis? 
+	}
+\end{itemize}
 
@@
 
+\subsection{General objective}
+Study the practice and feasibility of a new fabrication process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner; by the integration of mechano-electrospinning technique.
+
+\subsection{Specific objectives}
+
+\begin{itemize}
+	\item{
+	Design polymer solutions that can be electrospun by NFES, photopolymerized, and then pyrolyzed.
+    }
+    \item{
+    Through rheological analyses, determine if polymer solutions can be easily employed for conducting carbon nano-wire synthesis.
+    }
+    \item{
+    Determine and control the polymer solution rheological properties along with the process parameters of carbon nano-wire synthesis.
+    }
+    \item{
+    Discover a PEO-similar material to allow the electrospinning process as well as input favourable properties to the carbon nano-wire yield.
+    }
+\end{itemize}
+
 %----------------------------------------------------------------------------------------

### 2020-05-28 myThesis/thesis_LaTeX/main.tex
thesis re-organisation
biber now working
quote

@@
 % Uncomment to place the chapter title next to the number on one line
-chapterinoneline,
+%chapterinoneline,
 % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
-consistentlayout,
+%consistentlayout,
 % The class file specifying the document structure
@@
 \usepackage{pdfpages}
+
+% stop all hyphenation
+%\raggedright
+\sloppy
+\usepackage[none]{hyphenat}
 
@@
 %----------------------------------------------------------------------------------------
-%	LIST OF CONTENTS/FIGURES/TABLES PAGES
+%	QUOTATION PAGE
 %----------------------------------------------------------------------------------------
 
-\tableofcontents % Prints the main table of contents
+\vspace*{0.2\textheight}
 
-\listoffigures % Prints the list of figures
+\begin{center}
+\includegraphics[width=0.60\textwidth]{./Figures/quote.png}
 
-\listoftables % Prints the list of tables
+\noindent\enquote{\itshape No great discovery was ever made without a bold guess.}\bigbreak
+\end{center}
+
+\begin{flushright}
+\textbf{Newton, Sir Isaac} \linebreak
+In W.I.B. Beveridge \linebreak
+\emph{The Art of Scientific Investigation} \linebreak
+Scientist (p. 145)
+\end{flushright}
 
@@
 
-To my mother, Helena, who continues to learn, grow and develop and who has been a
-source of encouragement and inspiration to me throughout my life, a very special
-thank you for providing a ‘writing space’ and for nurturing me through the months of
-writing. And also for the myriad of ways in which, throughout my life, you have
-actively supported me in my determination to find and realise my potential, and to
-make this contribution to our world.\\
+% To my mother, Helena, who continues to learn, grow and develop and who has been a source of encouragement and inspiration to me throughout my life, a very special thank you for providing a ‘writing space’ and for nurturing me through the months of writing.
+And also for the myriad of ways in which, throughout my life, you have actively supported me in my determination to find and realise my potential, and to make this contribution to our world.\\
 
-To my mother-in-law, Maryam, known only briefly but loved and missed, who
-represented to me ‘living proof’ of Black women’s ability to redefine and recreate our
-lives despite, and maybe even because of, the tremendously constraining, oppressive
-and repressive situations in which we often exist.\\
+% To my mother-in-law, Maryam, known only briefly but loved and missed, who represented to me ‘living proof’ of Black women’s ability to redefine and recreate our lives despite, and maybe even because of, the tremendously constraining, oppressive and repressive situations in which we often exist.\\
 
-To my dear husband, Bala who remains willing to engage with the struggle, and
-ensuing discomfort, of having a partner who refuses to accept the given role of the
-"Black woman" and is actively engaged in redefining and redesigning that role. A
-very special thank you for your practical and emotional support as I added the roles of
-wife and then mother, to the competing demands of business, work, study and
-personal development.\\
+% To my dear husband, Bala who remains willing to engage with the struggle, and ensuing discomfort, of having a partner who refuses to accept the given role of the "Black woman" and is actively engaged in redefining and redesigning that role.
+A very special thank you for your practical and emotional support as I added the roles of wife and then mother, to the competing demands of business, work, study and personal development.\\
 
-Thanks to dear Kamal and Azaria, for being so supportive - even when being ‘without
-Mum’ was hard, and for your help with the bibliography and diagrams. This work is
-for, and because of you and all the generations to come. It is dedicated to all our
-journeys in learning to thrive.\\
+% Thanks to dear Kamal and Azaria, for being so supportive - even when being ‘without Mum’ was hard, and for your help with the bibliography and diagrams.
+This work is for, and because of you and all the generations to come.
+It is dedicated to all our journeys in learning to thrive.\\
 
-It is also dedicated to Josephine - friend, ‘sister’, colleague, ‘co- traveller’ and
-researcher - who knowingly and unknowingly- led me to an understanding of some of
-the more subtle challenges to our ability to thrive. If our attempts to claim our right to
-speak our truth, and to unravel and follow the threads through which our oppression is
-maintained, and are instrumental in helping one other Black woman from ‘going over
-the edge’ - in which sight we continuously live our lives - perhaps, it might be seen
-that your invaluable contribution to the attainment of many of the insights gained was
-worth it. It is also written in honour of all our my grandmothers, and their mothers,
-and grandmothers, and to all our and mothers and grandmothers, who though not
-marked by history struggled so heroically to resist the definitions attributed to them
-by the dominant system and communicate messages of hope and expectation.
-I am also very grateful to Maya Angelou, for the inspiration she has been to methrough her writings, poetry readings and as a living representation of a woman
-thriving. Thanks to Mary Washington, Alice Walker, Jackie Kay, Buchi Emecheta,
-Toni Cade, Lauretta Ngobo, bell hooks, and other Black women writers of the 1980’s,
-who in telling stories for and about us validated me and my experiences in ways I
-cannot begin to explain here.\\
+% It is also dedicated to Josephine - friend, ‘sister’, colleague, ‘co- traveller’ and researcher - who knowingly and unknowingly- led me to an understanding of some of the more subtle challenges to our ability to thrive.
+If our attempts to claim our right to speak our truth, and to unravel and follow the threads through which our oppression is maintained, and are instrumental in helping one other Black woman from ‘going over the edge’ - in which sight we continuously live our lives - perhaps, it might be seen that your invaluable contribution to the attainment of many of the insights gained was worth it.
+It is also written in honour of all our my grandmothers, and their mothers, and grandmothers, and to all our and mothers and grandmothers, who though not marked by history struggled so heroically to resist the definitions attributed to them by the dominant system and communicate messages of hope and expectation.
+I am also very grateful to Maya Angelou, for the inspiration she has been to methrough her writings, poetry readings and as a living representation of a woman thriving.
+Thanks to Mary Washington, Alice Walker, Jackie Kay, Buchi Emecheta, Toni Cade, Lauretta Ngobo, bell hooks, and other Black women writers of the 1980’s, who in telling stories for and about us validated me and my experiences in ways I cannot begin to explain here.\\
 
-Loving thanks to my friends / learning partners, Agnes, Susan, Ulana and Namonya,
-who played such important roles along the journey, as we mutually engaged in
-making sense of the various challenges we faced and in providing encouragement to
-each other at those times when it seemed impossible to continue. I offer my gratitude
-and appreciation to my supervisors, Judi Marshall and Peter Reason, for the deft ways
-in which you lovingly challenged and supported me through out the whole of this
-work - knowing when to push and when to let up. I offer special thanks to those who
-supported me in the mechanics of producing this thesis. Rosemary, for reading and rereading drafts; Rajwant for editing and proofing; Susan for help with typing and for
-helping me get ‘unstuck’ with this thesis on many occasions; and Peter and Trevor for
-‘rescuing’ me at those times when I was almost defeated by the technology. Most of
-all thanks to God the Divine who continues to make the impossible possible.
+% Loving thanks to my friends and learning partners, Agnes, Susan, Ulana and Namonya, who played such important roles along the journey, as we mutually engaged in making sense of the various challenges we faced and in providing encouragement to each other at those times when it seemed impossible to continue.
+
+I offer my gratitude and appreciation to my supervisors, \supname and \cosupname, for the deft ways in which you lovingly challenged and supported me through out the whole of this work - knowing when to push and when to let up.
+I offer special thanks to those who supported me in the mechanics of producing this thesis.
+\supname, for reading and rereading drafts, editing and proofing, typing and helping me get ‘unstuck’ with this thesis on many occasions.
+And Braulio and Arnoldo for ‘rescuing’ me at those times when I was almost defeated by the laboratory equipment.
 
 \end{acknowledgements}
+
+%----------------------------------------------------------------------------------------
+%	LIST OF CONTENTS/FIGURES/TABLES PAGES
+%----------------------------------------------------------------------------------------
+
+\tableofcontents % Prints the main table of contents
+
+\listoffigures % Prints the list of figures
+
+\listoftables % Prints the list of tables
 
@@
 
+%% https://www.overleaf.com/learn/latex/bibtex_bibliography_styles
+%% abbrv, acm, alpha, apalike, ieeetr, plain, siam, unsrt
+%\bibliographystyle{plain}
+%\renewcommand\bibname{References}
+%\bibliography{mainBiblio}
+
 %----------------------------------------------------------------------------------------

### 2020-05-31 myThesis/thesis_LaTeX/Chapters/2.tex
thesis restructure

@@
 
-\chapter{Carbon Nanowires Research Developments in Terms of Published Papers, Synthesis and Production} % Main chapter title
+\chapter{Carbon Nanowires Research Developments in Terms of Published Papers, Synthesis and Fabrication} % Main chapter title
 
 \label{Chapter:2}
+
+Nanotechnology ability to control or assemble materials at the nanoscale has fostered the development of diverse nanomaterials and nanostructures, including quantum dots [1], nanofibers, nanotubes [2] and nanowires [3,4].
+These nanomaterials are of particular interest for biomedical applications in neurology, where conductive materials may promote electrical and chemical communication within the nervous system at the micro- and nano- scale levels.
+Applications of nanostructures to neuroscience have rapidly expanded from molecular imaging [5], to neuro- regenerative scaffolds [6] and neural interfaces [7-9].
+
+In this framework, carbon-based nanomaterials (CBNs) and in particular nanotubes deserve particular attention, due to the exponential increase in neuroscience applications of materials composed mainly by carbon with different hybridization or struc- tures [10].
+
+In this chapter we focus on the applications of CBNs-based technology to provide a picture of past and ongoing research in this field, highlighting the goals that have been achieved and the insights reached in understanding CBNs.
 
@@
 %----------------------------------------------------------------------------------------
-\section{}
+\section{Carbon and carbon-based nanomaterials}
+
+Carbon is the most versatile element in the periodic table [11], owing to the large number of bonds of different type and strength that can form with it or with many other elements.
+Moreover, the ability of carbon orbitals to hybridize in sp, sp2 and sp3 configura- tions paves the way to the existence of a number of allotropes.
+To date, the three naturally occurring allotropes of carbon (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nanotubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig.
+1].
+
+The interest in CBNs has increased exponentially in the last
+decades, first with the discovery offullerenes (1985), then with that of carbon nanotubes (CNTs; 1991) and finally with the synthesis of graphene (GR) (2004).
+
+The properties of these CBNs make them widely used in many
+fields ranging from material science [13], energy production and storage [14], environmental sciences [15,16], biology [17-19] and medicine [20,21].
+Table 1 summarizes the main properties of the most common CBNs [22-25]:
+
+Among the many carbon nanomaterials, CNTs and GR are currently the most popular representatives and have been exten- sively studied for their excellent mechanical strength, electrical and thermal conductivity and optical properties.
+The Young's modulus and tensile strength of CNTs and GR can reach 1 TPa and 130 GPa respectively [20,21].
+Carrier mobility of graphene is around 860 $cm^{2} V^{-1} s^{-1}$ (hole mobility of 844 $cm^{2} V^{-1} s^{-1}$ and carrier mobility of 866 $cm^{2} V^{-1} s^{-1}$), and the current density of metallic CNTs is orders of magnitude higher than those of metals such as copper [26,27].
+Thermal conductivities of CNTs and GR are about 3000e3500W/mK and 5000 W/mK respectively [28].
+The light absorption ratio of single-layer graphene is limited to 2.5\% [29].
+A large amount of the research efforts were focused on exploiting these properties for various applications including electronics, biological engineering, filtration, lightweight/strong composite materials, photovoltaic and energy storage [30-32].
+CNTs and GR are naturally good electrical conductors and their biocompatibility can be modulated [33], making them good candidates for improving electrodes for neural interfaces.
+Electrical recording or stimulation of nerve cells is widely employed in neural prostheses (for hearing, vision, and limb-movement recovery), in clinical therapies (treating Parkinson's disease, dystonia, and chronic pain), as well as in basic neuroscience studies.
+In all these applications, electrodes of various shapes and dimensions stimulate and/or re- cord neuronal activity to directly modulate behavior or to interface machine.
+The performance of the electrodes can be significantly improved by implementing the device with nanomaterial-based coatings (such as CBNs), since their high surface area can drastically increase charge injection capacity and decrease the interfacial impedance with neurons [34].
+
+%%%
+It is well known that the morphology of the electroactive material play an important role in electrochemical systems, once the intimate contact at the electrode/electrolyte interface is crucial to guarantee the charge transfer process [11,12].
+In this sense, nanos- tructured electroactive materials such as nanorods [13], nanofiber [14], nanoflowers [15,16], nanowires [17,18], among others [19,20], are being widely used to obtain improved electrochemical properties such as higher charge/discharge rate and improved task to accommodate stress due to volume changes occasioned by intercalation process.
+
+%----------------------------------------------------------------------------------------
+%	SECTION 2
+%----------------------------------------------------------------------------------------
+\section{Carbon nanowires}
+
+Carbon nanofibers (CNFs) have been classified as linear, sp2-based discontinuous filaments, where the aspect ratio is greater than 100 [207].
+Depending on the angle of the graphene layers that compose the filament, CNFs have even been classified as stacked (graphene layers stacked perpendicularly to the fiber axis) or herringbone/cupstacked (graphene layers stacked at an angle be- tween parallel and perpendicular to the fiber axis) [208].
+
+%%%
+Nanowires are one-dimensional, anisotropic structures, small in diameter, and large in surface-to-volume ratio.
+These characteris- tics confer to the nanowires special physical properties than those of traditional scale and dimensionality materials, such as electrical, optical thermal and mechanical properties.
+However, this make this kind of materials to have properties deeply dependent on their surface condition and geometrical configuration [21].
+The trans- port properties in the 1D nanostructures like the nanowires are affected by wire diameter, surface conditions, crystal quality, crystallographic orientation and material composition, thus the synthesis conditions are a crucial factor to obtain reproducible and high-quality nanowires for different application [21].
+
+The typical lengths and diameters of carbon nanofibers are in the ranges of 5e100mm and 5e500 nm, respectively [209].
+CNTs and GR are the most studied carbon nanomaterials for neural in- terfaces, however CNFs are also attractive in bio-interfacing de- velopments due to their chemical and physical properties [1]: CNFs are chemically stable and inert in physiological environment [2], they are biocompatible for long-term implantation due to CNFs solid carbon skeleton [3], they are electrically robust and conduc- tive for signal detection [4], they can be manufactured into 3D structures allowing intra-tissue and intracellular penetration [210], CNFs possess high surface-to-volume ratio, which greatly reduces electrical impedance, and [5] ultra-micro scale sizes that provide high spatial resolution.
+CNFs have been applied as promising ma- terials in many fields, such as energy conversion and storage, reinforcement of composites and self-sensing devices.
+
+In addition, CNF based materials have been developed as electroconductive scaffolds for neural tissues to facilitate communication through neural interfaces.
+Electrical fields are able to enhance and direct nerve growth [211], therefore electroconductive scaf- folds have been applied to enhance the nerve regeneration process, not only providing physical support for cell growth but also delivering the functional stimulus.
+CNFs may represent novel, versatile neural interfaces, being capable of dual-mode operation by detecting electrophysiological and neurochemical signals, not only at the extracellular level with high spatial resolution, but also at the intracellular level by penetrating into single neurons [9].
+
+Despite the longstanding experience on these nanomaterials and the deep knowledge of the CNFs-neuron interface in vitro, in vivo experiments on their possible application for the treatment of brain and spinal cord injuries or diseases are still limited to few examples [53,212,213].
+In the first report CNFs impregnated with subventricular stem cells were employed to promote neuro- regeneration after experimental stroke [53].
+The animals receiving the CNF-based treatment show reduction of the infarcted volume as well as recovery ofmotor and somatosensory activity.
+These data indicate that CNFs are optimal support material for neuronal tissue regeneration [53].
+
+Recently, Guo and collaborators [104] developed a polymer-based neural probe with CNFs composites as recording electrodes via the thermal drawing process [213].
+They demonstrated that in situ CNFs alignment was achieved during the thermal drawing, which contributes to a drastic improvement of electrical conductivity by 2 orders of magnitude compared to a conventional polymer electrode.
+The resulting neural probe has a miniature footprint, with a recording site reduced in size to match single neuron, yet maintaining impedance value able to capture neural signals.
+In chronic settings, long-term reliable electrophysiological recordings with single-spike resolution and minimal tissue response over extended period of implantation in wild-type mice were shown [213].
+
+%%%
+Nanostructured materials are particularly good for supercapacitor applications, providing high surface area, which leads to a high specific capacitance [22].
+Compared to 3D and 2D materials, 1D nanostructures have smaller dimension and higher aspect ratio, improving the transport of electrical carriers in one controllable direction and also can be exploited as elements in different kinds of nanodevices [23].
+In this way, nanowires have been satisfacto- rily used in supercapacitor electrodes due to their reduced ion dif- fusion path in comparison with 2D and 3D nanostructures, leading in higher charge/discharge rates [22,24].
+
+%%%
+Amongst the innumerous materials used to obtain 1D nanostructures, such as, carbon, silicon, transition metal oxides, the 1D nanostructured conductive polymers are a important group to fabricate energy storage devices, due their attractive characteristic, such as, mechanical properties, electrical conductivity, low cost, easy processing, high surface area and unique electroactive behavior, including high voltage window and high-doping rate during charge-discharge process [25].
+During the charge/discharge process in the conducting polymer occur the insertion/desertion ions from the electrolyte in the polymer backbone that could result in swelling and shrinkage of the polymer chain, leading to mechanical degradation of the electrodes and fading the electrochemical performance [26].
+An alternative to diminishment this drawback of the conductive polymers is fabricate composites that could improve the stability and conductivity of the electrodes [27].
+
+%%%
+In this way, composites based on conducting polymers and carbon or metal oxides materials in a nanowire architecture are a good strategy to develop high-performance devices due to the combination of the electrochemical properties of the polymer and/or composites with the morphological advantages of the nano- wires.
+These combination results in large interface between electrode/electrolyte, effective electronic transport pathway, short ion diffusion distance and easy relaxation strain, which could improve both capacity/capacitance and rate performance of battery and supercapacitors devices, respectively [28].
+Furthermore, the mechanical properties of nanowires allow the development of flexible devices, that require materials with versatile functional- ities including high flexibility and foldability without losing its high power and energy density and long lifetime [29].
+
+%----------------------------------------------------------------------------------------
+%	SECTION 3
+%----------------------------------------------------------------------------------------
+\section{Nanowires synthesis}
+
+%%%
+Numerous methods to prepare nanowires, which include template-assisted synthesis [30], vapor–liquid-solid (VLS) [31], electrodeposition [32], electrospinning [33], hydrothermal [34], also hierarchical arrangement techniques [35–37] to organize the nanowires have been studies in the last ten years.
+Nanowires based on organic, inorganic or hybrid materials have been applied in order to get single or composites nanomaterials for innumerous purposes, such as chemical and biochemical sensing devices, ther- moelectric, optical, magnetic and electrical application.
+In this sec- tion, we are focusing on the synthesis of conducting polymer (Section 2.1) and composites (Section 2.2) to develop materials in nanowires architectures.
+
+\subsection{Synthesis of conducting polymer nanowires}
+
+\section{\emph{conclude that NFES is the way to go}}

### 2020-06-04 myThesis/thesis_LaTeX/Chapters/1.tex
thesis structure

@@
 
-This document bestows a thesis proposal to perform a research to engineer and design a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner.
+This document bestows a thesis project to perform research to engineer and design a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner.
 The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization, and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials.
@@
 %----------------------------------------------------------------------------------------
+\section{Carbon Nanowires Research Developments in Terms of Published Papers, Synthesis and Fabrication}
+
+Nanotechnology ability to control or assemble materials at the nanoscale has fostered the development of diverse nanomaterials and nanostructures, including quantum dots [1], nanofibers, nanotubes [2] and nanowires [3,4].
+These nanomaterials are of particular interest for biomedical applications in neurology, where conductive materials may promote electrical and chemical communication within the nervous system at the micro- and nano- scale levels.
+Applications of nanostructures to neuroscience have rapidly expanded from molecular imaging [5], to neuro-regenerative scaffolds [6] and neural interfaces [7-9].
+
+In this framework, carbon-based nanomaterials (CBNs) and in particular nanotubes deserve particular attention, due to the exponential increase in neuroscience applications of materials composed mainly by carbon with different hybridization or structures [10].
+
+In this chapter we focus on the applications of CBNs-based technology to provide a picture of past and ongoing research in this field, highlighting the goals that have been achieved and the insights reached in understanding CBNs.
+
+\subsection{Carbon and carbon-based nanomaterials}
+
+Carbon is the most versatile element in the periodic table [11], owing to the large number of bonds of different type and strength that can form with it or with many other elements.
+Moreover, the ability of carbon orbitals to hybridize in sp, sp2 and sp3 configurations paves the way to the existence of a number of allotropes.
+To date, the three naturally occurring allotropes of carbon (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nanotubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig.
+1].
+
+The interest in CBNs has increased exponentially in the last
+decades, first with the discovery offullerenes (1985), then with that of carbon nanotubes (CNTs; 1991) and finally with the synthesis of graphene (GR) (2004).
+
+The properties of these CBNs make them widely used in many
+fields ranging from material science [13], energy production and storage [14], environmental sciences [15,16], biology [17-19] and medicine [20,21].
+Table 1 summarizes the main properties of the most common CBNs [22-25]:
+
+Among the many carbon nanomaterials, CNTs and GR are currently the most popular representatives and have been extensively studied for their excellent mechanical strength, electrical and thermal conductivity and optical properties.
+The Young's modulus and tensile strength of CNTs and GR can reach 1 TPa and 130 GPa respectively [20,21].
+Carrier mobility of graphene is around 860 $cm^{2} V^{-1} s^{-1}$ (hole mobility of 844 $cm^{2} V^{-1} s^{-1}$ and carrier mobility of 866 $cm^{2} V^{-1} s^{-1}$), and the current density of metallic CNTs is orders of magnitude higher than those of metals such as copper [26,27].
+Thermal conductivities of CNTs and GR are about 3000e3500W/mK and 5000 W/mK respectively [28].
+The light absorption ratio of single-layer graphene is limited to 2.5\% [29].
+A large amount of the research efforts were focused on exploiting these properties for various applications including electronics, biological engineering, filtration, lightweight/strong composite materials, photovoltaic and energy storage [30-32].
+CNTs and GR are naturally good electrical conductors and their biocompatibility can be modulated [33], making them good candidates for improving electrodes for neural interfaces.
+Electrical recording or stimulation of nerve cells is widely employed in neural prostheses (for hearing, vision, and limb-movement recovery), in clinical therapies (treating Parkinson's disease, dystonia, and chronic pain), as well as in basic neuroscience studies.
+In all these applications, electrodes of various shapes and dimensions stimulate and/or record neuronal activity to directly modulate behavior or to interface machine.
+The performance of the electrodes can be significantly improved by implementing the device with nanomaterial-based coatings (such as CBNs), since their high surface area can drastically increase charge injection capacity and decrease the interfacial impedance with neurons [34].
+
+%%%
+It is well known that the morphology of the electroactive material play an important role in electrochemical systems, once the intimate contact at the electrode/electrolyte interface is crucial to guarantee the charge transfer process [11,12].
+In this sense, nanostructured electroactive materials such as nanorods [13], nanofiber [14], nanoflowers [15,16], nanowires [17,18], among others [19,20], are being widely used to obtain improved electrochemical properties such as higher charge/discharge rate and improved task to accommodate stress due to volume changes occasioned by intercalation process.
+
+\subsection{Carbon nanowires}
+
+Carbon nanofibers (CNFs) have been classified as linear, sp2-based discontinuous filaments, where the aspect ratio is greater than 100 [207].
+Depending on the angle of the graphene layers that compose the filament, CNFs have even been classified as stacked (graphene layers stacked perpendicularly to the fiber axis) or herringbone/cupstacked (graphene layers stacked at an angle between parallel and perpendicular to the fiber axis) [208].
+
+%%%
+Nanowires are one-dimensional, anisotropic structures, small in diameter, and large in surface-to-volume ratio.
+These characteristics confer to the nanowires special physical properties than those of traditional scale and dimensionality materials, such as electrical, optical thermal and mechanical properties.
+However, this make this kind of materials to have properties deeply dependent on their surface condition and geometrical configuration [21].
+The transport properties in the 1D nanostructures like the nanowires are affected by wire diameter, surface conditions, crystal quality, crystallographic orientation and material composition, thus the synthesis conditions are a crucial factor to obtain reproducible and high-quality nanowires for different application [21].
+
+The typical lengths and diameters of carbon nanofibers are in the ranges of 5e100mm and 5e500 nm, respectively [209].
+CNTs and GR are the most studied carbon nanomaterials for neural interfaces, however CNFs are also attractive in bio-interfacing developments due to their chemical and physical properties [1]: CNFs are chemically stable and inert in physiological environment [2], they are biocompatible for long-term implantation due to CNFs solid carbon skeleton [3], they are electrically robust and conductive for signal detection [4], they can be manufactured into 3D structures allowing intra-tissue and intracellular penetration [210], CNFs possess high surface-to-volume ratio, which greatly reduces electrical impedance, and [5] ultra-micro scale sizes that provide high spatial resolution.
+CNFs have been applied as promising materials in many fields, such as energy conversion and storage, reinforcement of composites and self-sensing devices.
+
+In addition, CNF based materials have been developed as electroconductive scaffolds for neural tissues to facilitate communication through neural interfaces.
+Electrical fields are able to enhance and direct nerve growth [211], therefore electroconductive scaffolds have been applied to enhance the nerve regeneration process, not only providing physical support for cell growth but also delivering the functional stimulus.
+CNFs may represent novel, versatile neural interfaces, being capable of dual-mode operation by detecting electrophysiological and neurochemical signals, not only at the extracellular level with high spatial resolution, but also at the intracellular level by penetrating into single neurons [9].
+
+Despite the longstanding experience on these nanomaterials and the deep knowledge of the CNFs-neuron interface in vitro, in vivo experiments on their possible application for the treatment of brain and spinal cord injuries or diseases are still limited to few examples [53,212,213].
+In the first report CNFs impregnated with subventricular stem cells were employed to promote neuroregeneration after experimental stroke [53].
+The animals receiving the CNF-based treatment show reduction of the infarcted volume as well as recovery ofmotor and somatosensory activity.
+These data indicate that CNFs are optimal support material for neuronal tissue regeneration [53].
+
+Recently, Guo and collaborators [104] developed a polymer-based neural probe with CNFs composites as recording electrodes via the thermal drawing process [213].
+They demonstrated that in situ CNFs alignment was achieved during the thermal drawing, which contributes to a drastic improvement of electrical conductivity by 2 orders of magnitude compared to a conventional polymer electrode.
+The resulting neural probe has a miniature footprint, with a recording site reduced in size to match single neuron, yet maintaining impedance value able to capture neural signals.
+In chronic settings, long-term reliable electrophysiological recordings with single-spike resolution and minimal tissue response over extended period of implantation in wild-type mice were shown [213].
+
+%%%
+Nanostructured materials are particularly good for supercapacitor applications, providing high surface area, which leads to a high specific capacitance [22].
+Compared to 3D and 2D materials, 1D nanostructures have smaller dimension and higher aspect ratio, improving the transport of electrical carriers in one controllable direction and also can be exploited as elements in different kinds of nanodevices [23].
+In this way, nanowires have been satisfactorily used in supercapacitor electrodes due to their reduced ion diffusion path in comparison with 2D and 3D nanostructures, leading in higher charge/discharge rates [22,24].
+
+%%%
+Amongst the innumerous materials used to obtain 1D nanostructures, such as, carbon, silicon, transition metal oxides, the 1D nanostructured conductive polymers are a important group to fabricate energy storage devices, due their attractive characteristic, such as, mechanical properties, electrical conductivity, low cost, easy processing, high surface area and unique electroactive behavior, including high voltage window and high-doping rate during charge-discharge process [25].
+During the charge/discharge process in the conducting polymer occur the insertion/desertion ions from the electrolyte in the polymer backbone that could result in swelling and shrinkage of the polymer chain, leading to mechanical degradation of the electrodes and fading the electrochemical performance [26].
+An alternative to diminishment this drawback of the conductive polymers is fabricate composites that could improve the stability and conductivity of the electrodes [27].
+
+%%%
+In this way, composites based on conducting polymers and carbon or metal oxides materials in a nanowire architecture are a good strategy to develop high-performance devices due to the combination of the electrochemical properties of the polymer and/or composites with the morphological advantages of the nanowires.
+These combination results in large interface between electrode/electrolyte, effective electronic transport pathway, short ion diffusion distance and easy relaxation strain, which could improve both capacity/capacitance and rate performance of battery and supercapacitors devices, respectively [28].
+Furthermore, the mechanical properties of nanowires allow the development of flexible devices, that require materials with versatile functionalities including high flexibility and foldability without losing its high power and energy density and long lifetime [29].
+
+\subsection{Nanowires synthesis}
+
+%%%
+Numerous methods to prepare nanowires, which include template-assisted synthesis [30], vapor–liquid-solid (VLS) [31], electrodeposition [32], electrospinning [33], hydrothermal [34], also hierarchical arrangement techniques [35–37] to organize the nanowires have been studies in the last ten years.
+Nanowires based on organic, inorganic or hybrid materials have been applied in order to get single or composites nanomaterials for innumerous purposes, such as chemical and biochemical sensing devices, thermoelectric, optical, magnetic and electrical application.
+In this section, we are focusing on the synthesis of conducting polymer and composites to develop materials in nanowires architectures.
+
+\subsubsection{Synthesis of conducting polymer nanowires}
+
+\subsection{\emph{conclude that NFES is the way to go}}
+
+%----------------------------------------------------------------------------------------
+%	SECTION 2
+%----------------------------------------------------------------------------------------
 \section{Problem definition and motivation}
@@
 %----------------------------------------------------------------------------------------
-%	SECTION 2
+%	SECTION 3
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-%	SECTION 3
+%	SECTION 4
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-%	SECTION 4
+%	SECTION 5
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-%	SECTION 5
+%	SECTION 6
 %----------------------------------------------------------------------------------------

### 2020-06-04 myThesis/thesis_LaTeX/Chapters/4.tex
thesis restructure
thesis structure

@@
 
-\chapter{Compatible Polymer-Solvent Combinations for Near-Field Electrospinning and Pyrolysis} % Main chapter title
+\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning, Photopolymerization and Pyrolysis of Polymeric Fibers} % Main chapter title
 
@@
 %----------------------------------------------------------------------------------------
-\section{Design and Selection of Candidate Spunable Polymer Solutions}
-
-%high molecular weight, polymer-solution interaction (straight chains)
-
-\subsection{Rheology of candidate polymer solutions}
+\section{}
 
 %----------------------------------------------------------------------------------------
-%	SECTION 1
+%	SECTION 2
 %----------------------------------------------------------------------------------------
-\section{Effect of aromatic groups in oxygen-free polymers in NFES and Pyrolysis}
+\section{}
+
+%----------------------------------------------------------------------------------------
+%	SECTION 3
+%----------------------------------------------------------------------------------------
+\section{Fabrication and Characterization of Legacy SU-8 carbon fibers}
+
+\section{\emph{conclude with fibre morphology before and after pyrolysis. determine best pyrolysis process}}
+%Were the selected candidates electrospunable?
+%Fiber morphology
+%Yield rate
+%Carbon content
+%Conductivity
+%Fiber morphology

### 2020-06-17 myThesis/thesis_LaTeX/main.tex
thesis structure
title typo
thesis characterization chapter added
thesis - alpha_rate_fitting - new articles

@@
 % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\thesistitle{Fabrication of graphitic-carbon suspended nanowires through mechanoelectrospinning of photocrosslinkable polymers}
+\thesistitle{Fabrication of Graphitic-Carbon Suspended Nanowires Through Mechano-Near-Field Electrospinning of Photocrosslinkable Polymers}
 
@@
 
-I offer my gratitude and appreciation to my supervisors, \supname and \cosupname, for the deft ways in which you lovingly challenged and supported me through out the whole of this work - knowing when to push and when to let up.
+I offer my gratitude and appreciation to my supervisors, \supname and \cosupname, for the deft ways in which you fondly challenged and supported me through out the whole of this work - knowing when to push and when to let up.
 I offer special thanks to those who supported me in the mechanics of producing this thesis.
@@
 \include{./Chapters/6}
-\include{./Chapters/7}
+%\include{./Chapters/7}
 

### 2020-08-20 5_Thesis/THESIS_LaTeX/Chapters/3.tex
file re organisation

% Chapter Template

\chapter{Selection of Compatible Polymer-Solvent Combinations for Near-Field Electrospinning and Pyrolysis} % Main chapter title

\label{Chapter:3}

% search : electrospunable capacity vs. thermo analysis of polymers in solutions (bad/good solvents)

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Selection of Candidate Spunable Polymer Solutions}

%high molecular weight, polymer-solution interaction (straight chains)

\subsection{Rheology of candidate polymer solutions}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Effect of aromatic groups in oxygen-free polymers in NFES and Pyrolysis}

\section{\emph{conclude with a collection of potential spunable polymer solutions}}

### 2020-08-20 5_Thesis/THESIS_LaTeX/Chapters/4.tex
file re organisation

--- 2020-06-04 myThesis/thesis_LaTeX/Chapters/4.tex
@@
 
-\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning, Photopolymerization and Pyrolysis of Polymeric Fibers} % Main chapter title
+\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning, and Forward-thinking on Photopolymerization and Pyrolysis} % Main chapter title
 

### 2020-08-20 5_Thesis/THESIS_LaTeX/main.tex
file re organisation

--- 2020-06-17 myThesis/thesis_LaTeX/main.tex
@@
 % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\thesistitle{Fabrication of Graphitic-Carbon Suspended Nanowires Through Mechano-Near-Field Electrospinning of Photocrosslinkable Polymers}
+\thesistitle{Fabrication of Suspended Nanowires Through Mechano-Near-Field Electrospinning of Polymers in Solution for the Production of Glass-like Carbon}
 
@@
 \textbf{CEM}   & \textbf{C}ampus \textbf{E}stado de \textbf{M}éxico\\
-
 \textbf{CNWs}  & \textbf{C}arbon \textbf{N}ano-\textbf{w}ire\textbf{s}\\
-
 \textbf{DC}    & \textbf{D}irect \textbf{C}urrent\\
-
 \textbf{EMS}   & \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\
-
 \textbf{FFES}  & \textbf{F}ar \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
-
 \textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\
-
 \textbf{MA}    & \textbf{Ma}ssachusetts\\
-
 \textbf{MEMS}  & \textbf{M}icro\textbf{e}lectro\textbf{m}echanical \textbf{S}ystems\\
-
 \textbf{MNT}   & \textbf{M}aestría en \textbf{N}ano\textbf{t}ecnología \emph{(Master of Science in Nanotechnology)}\\
-
 \textbf{MTY}   & \textbf{M}on\textbf{t}erre\textbf{y} \emph{or} Campus \textbf{M}on\textbf{t}erre\textbf{y}\\
-
 \textbf{NFES}  & \textbf{N}ear \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
-
 \textbf{USA}   & \textbf{U}nited \textbf{S}tates of \textbf{A}merica\\
-
 \textbf{UV}    & \textbf{U}ltra\textbf{v}iolet\\
@@
 Symbol   & Name              & Unit \\
-
 \addlinespace % Gap to separate the Roman symbols from the Greek
-
 $\omega$ & angular frequency & \si{\radian} \\

### 2020-08-20 5_Thesis/thesis_proposal_LaTeX/Chapters/5_StateoftheArt.tex
file re organisation

--- 2019-05-11 thesis_proposal_LaTeX/Chapters/5_StateoftheArt.tex
@@
 
+The following is a literature review to highlight the work done by others that is related to the proposed dissertation.
+This section presents the work that the proposal is based on to show others attempts to solve a problem related to Section \ref{Chapter:ProblemDefinitionandMotivation}.
+
 %----------------------------------------------------------------------------------------
@@
 
+\label{sec:FloresWrk}
+
+\subsection{Rheometry}
+Rheometry is the measuring technology used to determine rheological data.
+There are different measuring systems, instruments and analysis methods.
+Both, liquids and solid  can be investigated using rotational and oscillatory rheometers.
+Rotational tests are performed to characterize viscous behavior.
+In order to evaluate viscoelastic behavior, creep tests, relaxation tests and oscillatory tests are performed \cite{Flores2017}.
+
+\subsubsection{Amplitude Sweep}
+An amplitude sweep is a typical test used to characterize the behavior of a polymer
+solution or polymer melt.
+In this basic test a constant angular frequency is applied along with an increasing or decreasing deformation or strain, see Figure \ref{fig:ampSweep} a).
+The obtained results are the storage and loss moduli, $G'$ and $G''$ respectively, along the values of percentage of strain applied.
+The amplitude is the maximum of the oscillatory motion.
+Normally at low frequencies the viscoelastic material presents a linear behavior, this is when the viscoelastic properties are independent of the strain or stress imposed due to the structure of the material stays undisturbed.
+Nevertheless, as the amplitude is increased at some at some point this linear trend changes suddenly.
+Once this critical amplitude value is reached the material becomes more elastic or viscous depending on the solution initial state, see Figure \ref{fig:ampSweep} b) \cite{Flores2017}.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/ampSweep.png}
+\decoRule
+\caption[Amplitude Sweep]{a) Imposed amplitude along time with constant frequency. b) Results for an amplitude sweep \cite{Flores2017}}
+\label{fig:ampSweep}
+\end{figure}
+
+\subsubsection{Frequency Sweep}
+A frequency sweep, is a common oscillatory test useful to understand the rheological behavior of fluids as it measures the viscoelastic properties.
+This measurement is considered a viscoelastic spectrum, in general, the shorter the timescale the more elastic the material behaves.
+These results are related to the molecular structure of the sample.
+Figure \ref{fig:freqSweep} shows a typical data for a polymer melt where different regions are observed.
+Frequency sweep measurements also allow the estimation of the molecular weight distribution characteristics such as entanglement density and process-ability \cite{Flores2017}.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/freqSweep.png}
+\decoRule
+\caption[Frequency Sweep]{Typical results for a frequency sweep. \cite{Flores2017}}
+\label{fig:freqSweep}
+\end{figure}
+
+\subsubsection{Flow Curve}
+The viscosity is measured as a function of the shear rate in a rotational rheometer with different geometries according to the sample.
+Normally three types of behaviours can be characterized in flow curve measurements: a) ideal viscous, b) shear thinning and c) shear thickening.
+Figure \ref{fig:flowCurve} shows three different materials and their response to an imposed shear rate \cite{Flores2017}.
+
+\begin{figure}[th]
+\centering
+\includegraphics[width=0.75\textwidth]{./Figures/flowCurve.png}
+\decoRule
+\caption[Flow Curves]{a) Flow curve stress vs stress.
+b) Flow curve strain vs shear viscosity.
+Both figures for i Newtonian fluid, ii Shear thinning fluid, iii Shear thickening fluid.
+\cite{Flores2017}}
+\label{fig:flowCurve}
+\end{figure}
+
+\subsection{Sample Preparation}
 Flores studied SU-8 2002 polymer solutions in cyclopentanone with poly(ethylene) oxide (PEO) and tetrabutylammonium tetrafluoroborate (TBATFB).
@@
 \begin{table}[th]
-\caption{Set of prepared samples}
+\caption{Set of prepared samples \cite{Flores2017}}
 \begin{center}
@@
 \decoRule
-\caption[Serie A - Amplitude Sweep]{Serie A - Amplitude Sweep}
+\caption[Serie A - Amplitude Sweep]{Serie A - Amplitude Sweep \cite{Flores2017}}
 \label{fig:SerieAampSweep}
@@
 \decoRule
-\caption[Serie B - Amplitude Sweep]{Serie B - Amplitude Sweep}
+\caption[Serie B - Amplitude Sweep]{Serie B - Amplitude Sweep \cite{Flores2017}}
 \label{fig:SerieBampSweep}
@@
 \decoRule
-\caption[Serie C - Amplitude Sweep]{Serie C - Amplitude Sweep}
+\caption[Serie C - Amplitude Sweep]{Serie C - Amplitude Sweep \cite{Flores2017}}
 \label{fig:SerieCampSweep}
@@
 \decoRule
-\caption[Serie A - Flow curve]{Serie A - Flow curve}
+\caption[Serie A - Flow curve]{Serie A - Flow curve \cite{Flores2017}}
 \label{fig:SerieAflowCurve}
@@
 \decoRule
-\caption[Serie B - Flow curve]{Serie B - Flow curve}
+\caption[Serie B - Flow curve]{Serie B - Flow curve \cite{Flores2017}}
 \label{fig:SerieBflowCurve}
@@
 \decoRule
-\caption[Serie C - Flow curve]{Serie C - Flow curve}
+\caption[Serie C - Flow curve]{Serie C - Flow curve \cite{Flores2017}}
 \label{fig:SerieCflowCurve}
@@
 \decoRule
-\caption[Serie A - Frequency Sweep]{Serie A - Frequency Sweep}
+\caption[Serie A - Frequency Sweep]{Serie A - Frequency Sweep \cite{Flores2017}}
 \label{fig:SerieAfreqSweep}
@@
 \decoRule
-\caption[Serie B - Frequency Sweep]{Serie B - Frequency Sweep}
+\caption[Serie B - Frequency Sweep]{Serie B - Frequency Sweep \cite{Flores2017}}
 \label{fig:SerieBfreqSweep}
@@
 \decoRule
-\caption[Serie C - Frequency Sweep]{Serie C - Frequency Sweep}
+\caption[Serie C - Frequency Sweep]{Serie C - Frequency Sweep \cite{Flores2017}}
 \label{fig:SerieCfreqSweep}
@@
 Cardenas conducted some experiments to characterize and analyze carbon nano-wires.
-Polymeric SU-8 nano fibers were produced by two different methods; for each method different polymer solutions were employed.
+Polymeric SU-8 nano fibers were produced by two different methods; for each method different polymer solutions were employed, See Table \ref{tbl:CardenasSummary}.
+
+\begin{table}[th]
+\caption{Method 1 and Method 2 conditions and parameters \cite{Cardenas2017}}
+\begin{center}
+\begin{tabular}{ >{\raggedright\arraybackslash}p{0.30\textwidth} >{\raggedright\arraybackslash}p{0.30\textwidth} >{\raggedright\arraybackslash}p{0.30\textwidth} } 
+\hline
+Conditions and Parameters & Method 1 & Method 2 \\
+\hline
+Solution materials & SU-8 2002, PEO and TBATFB & SU-8 2025, TBATFB and SU-8 thinner \\
+Solution preparation & stirred for 1 $hr$ at 75$^\circ C$ at 100-150 $r p m$ & stirred for 1.5 $hrs$ at 75$^\circ C$ at 100 $r p m$ \\
+Deposition voltage & 100 $V$ & 200 $V$ (due to the higher viscosity) \\
+Results & failed the pyrolyzation process & 81\% yield rate after pyrolyzation \\
+Fiber diameter & NA & 204 $nm$ \\
+\hline
+\label{tbl:CardenasSummary}
+\end{tabular}
+\end{center}
+\end{table}
 
@@
 
-\subsubsection{Polymer Solution}
+\subsubsection{SU-8 2002 Polymer Solution}
 The polymeric solution was composed by 2 $ml$ of SU-8 2002 mixed with 0.5 $w t \%$ of PEO and 0.5 $w t \%$ of TBATFB to increase its conductivity and yield soother polymer jets during electrospinning.
@@
 
-\subsubsection{Deposition}
+\subsubsection{Deposition of Electrospun SU-8 2002 Solution}
 A voltage around 100 $V$ was applied between a dispensing needle and the collector stage.
@@
 
-\subsubsection{Polymer Solution}
+\subsubsection{SU-8 2025 Polymer Solution}
 The solution was composed of 4 $ml$ of SU-8 2025, 4 $mg$ of TBATFB and 80 $\mu L$ of SU-8 thinner. The solution was stirred for 1.5 $hrs$ at 100 $rpm$ at 75 \textdegree{}$C$.
 
-\subsubsection{Deposition}
+\subsubsection{Deposition of Electrospun SU-8 2025 Solution}
 To pattern the fiber exactly on top of the SU-8 electrodes, a routine was set to move the needle relative to the collector.
@@
 The conducted experiments showed some techniques and materials that have been applied to fabricate carbon nano-wires, as well as the effects that fabrication parameters have on the final geometry of the carbon structures.
-The newly technique of electro-mechano-spinning (EMS) involved new polymer solutions along with a systematic deposition process.
-Cardenas found that the EMS proposed manufacturing technique yielded normally distributed diameters of 204 $nm$ with low variability, which is significantly reduced the uncertainty in the fabrication of carbon nano-wires.
+The new technique of electro-mechano-spinning (EMS) involved new polymer solutions along with a systematic deposition process.
+Cardenas \cite{Cardenas2017} found that the EMS proposed manufacturing technique yielded normally distributed diameters of 204 $nm$ with low variability, which is significantly reduced the uncertainty in the fabrication of carbon nano-wires.
 
-\clearpage
-
-\section{FIND PAPER THAT CONFIRMS THAT WITH THE INCREASE OF PEO CONCENTRATION, THE POROSITY DENSITY INCREASES IN CARBON STRUCTURES AFTER PYROLYSIS. \cite{newPAPER}}
-
-As explained in Section \ref{sec:pyrolysis}, the pyrolysis process is implemented to thermally decompose organic material into carbon. ...
+%\clearpage
+%
+%\section{FIND PAPER THAT CONFIRMS THAT WITH THE INCREASE OF PEO CONCENTRATION, THE POROSITY DENSITY INCREASES IN CARBON STRUCTURES AFTER PYROLYSIS. \cite{newPAPER}}
+%
+%As explained in Section \ref{sec:pyrolysis}, the pyrolysis process is implemented to thermally decompose organic material into carbon. ...
 

### 2020-08-20 3_helpingOthers/Alan/alpha_rate_fitting/matlabFit.m

@@ -1,0 +1,6 @@
+x = [0.003652583, 0.001774215, 0.031965924, 0.075, 0.161258301, ...
+    0.526700194, 0.731638427, 0.8, 0.82, 0.83, 0.83];
+y = [0.019713504, 0.355176935, 0.79274908, 1.434469194, 2.875276684, ...
+    12.18139645, 6.831274434, 2.94538576, 1.092906364, 0.333333333, ...
+    0.333333333];
+cftool( x, y );

### 2020-08-20 9_characterizationRheology/GNFmodels.py

@@ -1,0 +1,298 @@
+from numpy                import array, sum, inf, square, mean, sqrt, var, logspace, log10
+from tkinter              import Tk
+from matplotlib.pyplot    import figure, tight_layout, legend, yscale, xscale, savefig, scatter, plot, title
+from matplotlib           import rcParams, rcParamsDefault
+from pandas               import read_csv
+from tkinter              import filedialog
+from tkinter.simpledialog import askinteger
+from warnings             import filterwarnings
+from sys                  import exit as sysexit
+from scipy                import optimize
+from scipy.optimize       import differential_evolution
+
+def endProgram():
+    sysexit()
+
+def setupTkinterWindow():
+    root = Tk()
+    root.withdraw()
+    return root
+    
+def quitTkinterWindow(root):
+    root.quit()
+    root.destroy()
+
+def askForCVSfile():
+    filename = filedialog.askopenfilename(filetypes=[("CSV files", ".csv")])
+    return filename
+
+def removeTableOverhead(df, r):
+    dfcopy = df.copy()
+    for i in range(r):
+        dfcopy = dfcopy.drop([i]);
+    return dfcopy
+
+def removeColnameAndUnitRowsFromDF(df, r):
+    dfcopy = df.copy()
+    dfcopy = dfcopy.drop([r]);   # Remove colnames row from dataframe
+    dfcopy = dfcopy.drop([r+1]); # Remove units row from dataframe
+    return dfcopy
+
+def Text2Table(df):
+    dfcopy = df.copy()
+    dfcopy = dfcopy[0].str.split(",", expand=True);
+    return dfcopy
+
+def updateColumnnames(df, variables, units):
+    # Show variable names and units as column names
+    dfcopy         = df.copy()
+    df_header      = [col + " " + uni for col, uni in zip(variables, units)]
+    dfcopy.columns = df_header;
+    return dfcopy
+
+def renameColumnNames(df, r):
+    dfcopy    = df.copy()
+    variables = dfcopy.iloc[0]; # get variable names
+    units     = dfcopy.iloc[1]; # get units
+    dfcopy    = removeColnameAndUnitRowsFromDF(dfcopy, r)
+    dfcopy    = updateColumnnames(dfcopy, variables, units)
+    return dfcopy
+
[…]

### 2020-08-20 myThesis/Viscosity/GNFmodels.py
file re organisation 2

@@ -1,298 +1,0 @@
-from numpy                import array, sum, inf, square, mean, sqrt, var, logspace, log10
-from tkinter              import Tk
-from matplotlib.pyplot    import figure, tight_layout, legend, yscale, xscale, savefig, scatter, plot, title
-from matplotlib           import rcParams, rcParamsDefault
-from pandas               import read_csv
-from tkinter              import filedialog
-from tkinter.simpledialog import askinteger
-from warnings             import filterwarnings
-from sys                  import exit as sysexit
-from scipy                import optimize
-from scipy.optimize       import differential_evolution
-
-def endProgram():
-    sysexit()
-
-def setupTkinterWindow():
-    root = Tk()
-    root.withdraw()
-    return root
-    
-def quitTkinterWindow(root):
-    root.quit()
-    root.destroy()
-
-def askForCVSfile():
-    filename = filedialog.askopenfilename(filetypes=[("CSV files", ".csv")])
-    return filename
-
-def removeTableOverhead(df, r):
-    dfcopy = df.copy()
-    for i in range(r):
-        dfcopy = dfcopy.drop([i]);
-    return dfcopy
-
-def removeColnameAndUnitRowsFromDF(df, r):
-    dfcopy = df.copy()
-    dfcopy = dfcopy.drop([r]);   # Remove colnames row from dataframe
-    dfcopy = dfcopy.drop([r+1]); # Remove units row from dataframe
-    return dfcopy
-
-def Text2Table(df):
-    dfcopy = df.copy()
-    dfcopy = dfcopy[0].str.split(",", expand=True);
-    return dfcopy
-
-def updateColumnnames(df, variables, units):
-    # Show variable names and units as column names
-    dfcopy         = df.copy()
-    df_header      = [col + " " + uni for col, uni in zip(variables, units)]
-    dfcopy.columns = df_header;
-    return dfcopy
-
-def renameColumnNames(df, r):
-    dfcopy    = df.copy()
-    variables = dfcopy.iloc[0]; # get variable names
-    units     = dfcopy.iloc[1]; # get units
-    dfcopy    = removeColnameAndUnitRowsFromDF(dfcopy, r)
-    dfcopy    = updateColumnnames(dfcopy, variables, units)
-    return dfcopy
-
[…]

### 2020-08-21 4_Papers/NFES_Review/ARTICLE/article.tex
folder rename

--- 2020-03-14 myPapers/NFES_Review/Polymers_for_Nearfield_Electrospinning_with_Spatial_Control/article.tex
@@
 Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement.
-In the past years (2006-2019), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process.
+In the past years (2006-2020), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process.
 Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties.
@@
 One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano fibers from a variety of polymers.
-The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $nm $ in some cases, which is something difficult to achieve by other techniques.
+The technique allows the production of thin continuous fibers with ease, with micro and sub-micrometer diameters, which is something difficult to achieve by other techniques.
 Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials.
@@
 
-Current literature dictates the typical spinning setup is comprised by three main components: a syringe needle, a fiber collector, and some way to dispense the fibers from the needle to the collector.
-The spinning process is an electrohydro-dynamic (EHD) technique that yields continuous polymer fibers.
-Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively.
+Current literature dictates the typical spinning setup is comprised by three main components: a polymer reservoir, a fiber collector, and some way to dispense the fibers onto the collector.
+The spinning process is an electro-hydrodynamic (EHD) technique that yields continuous polymer fibers.
+Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively, seeFigure~\ref{f-02e0e3cf88d6}.
 
@@
 
-\subsection{Polymer reservoir: Polymer melt \& Polymer solution}Another electrospinning classification is the melt process.
-As Brown et al.
-\unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used).
-The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state.
-The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution.
-The apparatus used by Brown et al.
-\unskip~\cite{527120:13445499} is depicted in Figure~\ref{f-1e9a6ae11444}.
+\subsection{Stretching forces}
 
-\bgroup
-\fixFloatSize{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}{\includegraphics{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}}{}
-\makeatother 
-\caption{{Typical Melt Electrospinning Setup}}
-\label{f-1e9a6ae11444}
-\end{figure}
-\egroup
-Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.
-
-The first report of a melt electrospun drug delivery system came from Nagy et al.
-\unskip~\cite{527120:13445555}, who prepared fibers by melt electrospinning of Eudragit EPO with carvedilol.
-The drug and polymer were melted and mixed to form a homogeneous solid mixture prior to spinning.
-The melt-spun fibers reached diameters of 5{\textendash}30 $\mu m $, compared to 300{\textendash}1000 $nm $ diameters produced from solution-spun fibers.
-
-This work has been built on to blend plasticisers with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticisers Triacetin, Tween 80 and Polyethylene Glycol were investigated by Attila et al.
-in order to reduce the melting point of the polymer-drug mixture.
-The temperature drop is desirable to minimize the occurring drug degradation.
-
-Lian and Meng\unskip~\cite{527120:13445754} performed a comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibers fabricated by the melt and solution electrospinning techniques.
-Lian and Meng\unskip~\cite{527120:13445754} reported that melt spinning is preferable when the polymer presents a low solubility, on the other hand the melt fibers were produced in a slower release rate.
-Lian and Men findings feature the solution-spun fibers to have a porous structure.
-Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning.
-In their effort, they achieved a precise deposition of PCL fibers with diameters of $817 \pm 165 nm $.
-
-In literature, melt electrospinning has less evidence than the solution approach.
-However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}.
-Currently, the melt electrospinning setup is harder to establish but the lack of research on this technique explains its unexplored potential.
-
-\subsection{Dispensing nozzle}Coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle, see Figure~\ref{f-e0d8f2eb18d4}.
-\unskip~\cite{527120:13914792,527120:13914793} The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers.
-Sun et al.
-\unskip~\cite{527120:13914312} addressed electrospinning setups, where both the core and shell are comprised by PEO (poly(ethylene oxide)) and for a PEO shell with a poly(dode-cylthiophene) core.
-Sun et al.
-state that co-electrospinning has the potential to extend the range of materials that can be used for electrospinning.
-The shell solution can be modified to make the core solution spunable.
-It was also discovered that non-spunable solutions can by implemented as shell solutions in conjunction with a spunable core solution.
-\unskip~\cite{527120:13914968}
-
-\bgroup
-\fixFloatSize{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}{\includegraphics{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}}{}
-\makeatother 
-\caption{{Needle configurations in coaxial electrospinning. (a) the outer needle encasing the inner; (b) the inner needle protruding from the outer; (c) both needles inline with each other;}}
-\label{f-e0d8f2eb18d4}
-\end{figure}
-\egroup
-Some advantages that co-electrospinning setups can offer include the preempting the initial jet burst from the spinneret nozzle.
-On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles.
-\unskip~\cite{527120:13914748,527120:13914750}.
-As in conventional NFES, in co-electrospinning, the needle tip is connected to a high voltage power supply with a grounded collector.
+\subsubsection{Electric Field}Electrospinning (electrostatic fiber spinning) is a fiber fabrication approach that implements an electric field produce fibers by an electrical potential difference between the syringe needle and the collector.
 With the influence of high electric fields, the fibers are prone to brake into separate layers due to the whipping instabilities as the jet travels to the substrate.
@@
 
-\subsection{Stretching forces}
-
-\subsubsection{Electric Field}Electrospinning (electrostatic fiber spinning) is a fiber fabrication approach that implements an electric field produce fibers by an electrical potential difference between the syringe needle and the collector.
 The typical electrospinning setup applies an electrostatic charge to the polymer fluid at the tip of the needle nozzle, which results in the formation of the Taylor cone \unskip~\cite{527120:13659828}, from which a single polymer jet is ejected to the grounded collector.
@@
 The fiber finally develops with the complete solvent evaporation.
-Electrospun fibers are prone to splitting with the increase in acceleration, where multiple fibers are yield in a process known as electrospraying \unskip~\cite{527120:13659925}.
+Electrospun fibers are prone to splitting with the increase in acceleration due to high applied voltages, where multiple fibers are yield in a process known as electrospraying \unskip~\cite{527120:13659925}.
 
@@
 
-\paragraph{High voltage power supply: Direct Current \& Alternating Current}Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction.
+\paragraph{High voltage power supply: DC \& AC - }Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction.
 Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow.
@@
 In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge.
-The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers.
-The optimal AC frequency depends on the materials used and is typically within of 50 $Hz $ {\textendash} 1 $kHz $.
-\unskip~\cite{527120:13443405}
+The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers\unskip~\cite{527120:16885570}.
+The optimal AC frequency depends on the materials used and is typically within  $50Hz $ and  $1kHz $\unskip~\cite{527120:13443405}.
 
@@
 \unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques.
-They produced fibers by using three polymers: Eudragit EPO (cationic copolymer), Eudragit L100-55 (anionic polymer) and poly(vinyl pyrrolidone) (PVP) (neutral polymer).
-Balogh et al.
-discovered AC and DC electrospinning can produce fibers with all three polymers.
-However, The AC process allowed the implementation of faster flow rates than in the DC setup.
+Their work reports that AC and DC electrospinning can produce fibers with all three polymers, where the AC process allowed the implementation of faster flow rates than in the DC setup.
 The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $.
-AC electrospinning approach is as effective as the DC technique in producing drug delivery systems.
 
@@
 Centrifugal spinning intends to produce fibers by the use of a rotating polymer source.
-The centrifugal force generated from typical rotatory speeds above 2000 rpm, results in fiber formation.
+The centrifugal force generated from typical rotatory speeds above $2000 rpm $, results in fiber formation.
 \unskip~\cite{527120:13535559,527120:13535561}.
@@
 \makeatother 
-\caption{{Typical setup used in pressurized gyration Processes}}
+\caption{{Typical setup used in pressurized gyration processes}}
 \label{f-7cf6ac702e28}
@@
 \egroup
-The centrifugal force technique is applied to polymer solutions and melts.
+The centrifugal force technique has been applied to polymer solutions and melts.
 This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.
@@
 \subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution.
-The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate.
-Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}, see Figure~\ref{f-92361290d8c3} .
+The setup used for blow spinning is similar to the one used in coaxial electrospinning, where the polymer precursor is dispensed at a controlled rate.
+Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}, see Figure~\ref{f-92361290d8c3}.
 
@@
 Poly(3-hydroxybutyrate-co-3-hydroxyvalerate) were fabricated by both methods.
-The fibers produced by electrospinning had thicker diameters and their size uniformity was higher in the fibers produced by solution blow spinning.
-
-Jiang et al.\unskip~\cite{527120:13554126} combined the blowing technique with the electrospinning approach.
-The blow electrospinning technique implements both electric and gas flow forces to stretch the fibers.
-Jiang used an apparatus similar to those used in traditional electrospinning.
+The fibers produced by traditional electrospinning had thicker diameters and the size uniformity was higher in the fibers produced by solution blow spinning.
 The experimental setup requires a coaxial needle nozzle with a pressurized gas flow along with a potential difference between the dispensing needle and the grounded collector.
@@
 \makeatother 
-\caption{{Typical mechanical fiber drawing process}}
+\caption{{Typical mechanical fiber drawing process.
+First the needle makes contact with the substrate to break the polymer drop.
+Then the needle leaves the substrate and the collector moves to create and deposit the fiber.
+Once the fiber is written the needle makes contact witht the collector to fix the fiber deposition.}}
 \label{f-432d16f420fb}
@@
 \unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers where the fiber is created by stretching the polymer precursor with a moving collector, as depicted in Figure~\ref{f-432d16f420fb}.
-Touch-spinning comprises a moving stage with an embedded glass rod (Figure~\ref{f-f17259e76303}).
+Touch-spinning is another mechanical technique that comprises a moving stage with an embedded glass rod (Figure~\ref{f-f17259e76303}).
 Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers.
@@
 \egroup
-The touch spinning technique implies that the fiber diameter can be controlled by the rotation speed and the polymer solution concentration.
+The touch spinning technique implies that the fiber diameter can be controlled by the moving collector's speed and the polymer solution concentration.
 The main difference relays on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}
@@
 \unskip~\cite{527120:13656236} compared and combined the microfluidic spinning and electrospinning techniques.
+Heterogeneous materials and cell patterning within a single microfiber can be designed by the integration microfluidic channels.
+Therefore, microfluidic spinning is more suitable for cell encapsulation and tissues generation\unskip~\cite{527120:13656236}.
 
@@
 \unskip~\cite{527120:13656548} managed to fabricate micro fibers by imitating the "silk spinning" process of spiders.
-Kang's micro fibers properties were modified using a microfluidic system with a programmable flow control.
+Kang's micro fibers properties were modified using a microfluidic system with a programmable flow control (See Figure~\ref{f-c0beae2757bf}).
 The current microfluidic spinning approach is not scalable to a large fiber production, however it enables the fabrication of high-complex fibers that are not easily achieved by other methods.
@@
 
-\subsection{Nozzle-to-substrate distance}
+\subsection{Dispensing nozzle}Unlike traditional electrospinning, coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle, see Figure~\ref{f-4a5ffd16c3ab}\unskip~\cite{527120:13914792,527120:13914793}.
+The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers.
+Sun et al.
+\unskip~\cite{527120:13914312}.
+Addressed electrospinning setups, where both the core and shell are comprised by PEO (poly(ethylene oxide)) and for a PEO shell with a poly(dode-cylthiophene) core.
+Sun et al.
+state that co-electrospinning has the potential to extend the range of materials that can be used for electrospinning.
+The shell solution can be modified to make the core solution spunable.
+It was also discovered that non-spunable solutions can by implemented as shell solutions in conjunction with a spunable core solution.
+\unskip~\cite{527120:13914968}
+
 \bgroup
-\fixFloatSize{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}{\includegraphics{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}}{}
+\fixFloatSize{images/afe7da25-1366-4b1e-bf1a-0594eb2eaa88-uimg_nozzle.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/afe7da25-1366-4b1e-bf1a-0594eb2eaa88-uimg_nozzle.png}{\includegraphics{images/afe7da25-1366-4b1e-bf1a-0594eb2eaa88-uimg_nozzle.png}}{}
 \makeatother 
-\caption{{a) Typical Far-field Electrospinning (FFES) Setup. b) Typical Near-field Electrospinning (NFES) Setup.}}
-\label{f-fbe88d27b932}
-\end{figure*}
+\caption{{Needle configurations in coaxial electrospinning. (a) the outer needle encasing the inner; (b) the inner needle protruding from the outer; (c) both needles inline with each other;}}
+\label{f-4a5ffd16c3ab}
+\end{figure}
 \egroup
-Figure~\ref{f-fbe88d27b932}.a, depicts the typical setup for the conventional far-field electrospinning (FFES).
-As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}.
-When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process.
-The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}.
-The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.
+Some advantages that co-electrospinning setups can break the polymer drop surface tension, initiating the jet burst from the spinneret nozzle.
+On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles.
+\unskip~\cite{527120:13914748,527120:13914750}.
+As in conventional NFES, in co-electrospinning, the needle tip is connected to a high voltage power supply with a grounded collector.
 
-In the intent to achieve controlled fiber deposition, Sun et al.
-\unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES),Figure~\ref{f-fbe88d27b932}, describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line.
-Moreover, some mechanical influence is required to deposit fibers precisely.
-The mechanical force is introduced by moving collector.
-If the polymer solution jet speed is faster than the speed of the moving collector, the written fiber will curl; on the other hand, if the collector moves faster than the polymer jet, the fiber will gradually diminish \unskip~\cite{527120:11974327,527120:11974326}.
-Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.
+\subsection{Polymer Reservoir (Polymer Melt \& Polymer Solution)}Electrospinning processes can be classified on the polymer reservoir type.
+As Brown et al.
+\unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used).
+The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state.
+The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution.
+The apparatus used by Brown et al.
+\unskip~\cite{527120:13445499} is depicted in Figure~\ref{f-bfd139aecf8f}.
 
-The main difference between NFES and FFES is the distance between the needle and the collector which is higher in FFES (about 10 cm) compared to NFES which ranges in the mm scale.
-The short distance allow the production of well aligned fibers within particular designs.
-[7]
+\bgroup
+\fixFloatSize{images/9d06b4aa-134c-4fd6-bbf3-1ced4ac95046-uimg_metl_setup.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{images/9d06b4aa-134c-4fd6-bbf3-1ced4ac95046-uimg_metl_setup.png}{\includegraphics{images/9d06b4aa-134c-4fd6-bbf3-1ced4ac95046-uimg_metl_setup.png}}{}
+\makeatother 
+\caption{{Typical Melt Electrospinning Setup}}
+\label{f-bfd139aecf8f}
+\end{figure}
+\egroup
+Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales.
+Furthermore, polymer melt reservoirs get rid of any solvent contamination.
+
+The first report of a melt electrospun drug delivery system came from Nagy et al.
+\unskip~\cite{527120:13445555}, who prepared fibers by melt electrospinning of Eudragit EPO with carvedilol.
+The drug and polymer were melted and mixed to form a homogeneous solid mixture prior to spinning.
+The melt-spun fibers reached diameters of 5{\textendash}30 $\mu m $, compared to 300{\textendash}1000 $nm $ diameters produced from solution-spun fibers\unskip~\cite{527120:13445555}.
+
+Balogh et al.'s work has been built on to blend plasticizes with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticizes Triacetin, Tween 80 and Polyethylene Glycol were investigated in order to reduce the melting point of the polymer-drug mixture.
+The temperature drop is desirable to minimize the occurring drug degradation.
+
+Lian and Meng\unskip~\cite{527120:13445754} performed a comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibers fabricated by the melt and solution electrospinning techniques.
+They arrived to the conclusion that melt spinning is preferable when the polymer presents a low solubility.
+On the other hand the melt fibers were produced in a slower release rate.
+Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning.
+In their effort, they achieved a precise deposition of PCL fibers with diameters of $817 \pm 165 nm $.
+
+In literature, melt electrospinning has less evidence than the solution approach.
+However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}.
+Currently, the melt electrospinning setup is harder to determine and the lack of research on this technique explains its unexplored potential.
+
+\subsection{Polymer Solution}In electrospinning, it is typically agreed that the diameter of the fibers increased with higher concentration due to greater viscosity which withstands stretching.
+In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}, seeFigure~\ref{f-d977f56a0782}.
+\begin{table}[!htbp]
+\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
+\label{tw-be3662f66502}
+\def\arraystretch{1}
+\ignorespaces 
+\centering 
+\begin{tabulary}{\linewidth}{LL}
+\tbltoprule Observation & Concentration Adjustment\\
+\tblmidrule 
+Dripping, no stream &
+  Increase\\
+Splitting small droplets &
+  Increase slightly\\
+Steady stream &
+  No concentration adjustment\\
+Splitting large globs &
+  Decrease slightly\\
+Nozzle clogging &
+  Decrease\\
+\tblbottomrule 
+\end{tabulary}\par 
+\end{table}
+
+\subsubsection{Polymers}The polymer selection is in function on the intended application.
+For example, a fast dissolving hydrophilic polymer such as poly(ethylene oxide) (PEO) is used for fast drug delivery systems.
+Otherwise, slow dissolving polymers such as poly($\varepsilon $-caprolactone) (PCL) or poly(lactic-co-glycolic acid) (PLGA) are implemented.
+\unskip~\cite{527120:13082763}
+
+The polymer molecular weight along with the polymer concentration and solvent selection have a direct effect on the solution viscosity, conductivity and surface tension, hence the solution behavior in the electrospinning process.
+The spunable viscosity range varies with the polymer and solvent.
+
+Solutions with low viscosity are prone to insufficient polymer chain entanglements to produce fibers.\unskip~\cite{527120:13082763} On the other hand, if the solution is too viscous, then the surface tension cannot easily be overcome by the electric field.
+In both cases, the result can be droplets or particles forming rather than fibers as described inTable~\ref{tw-be3662f66502}.
+
+\subsubsection{Solvents}The solvent used must be capable of dissolving the polymer of interest at an appropriate concentration to form fibers, and must posses a suitable volatility.
+A low-volatility solvent like water may fail to evaporate completely over the distance between the spinneret and the collector.
+When the fibers form, they will hence contain residual water owing to this incomplete evaporation.
+The residue solvent will subsequently evaporate from the fibers upon storage, resulting in ribbon-like (flattened) fibers, wrinkles on the fiber surface or fused fibers.
+On the other hand, a high-volatility solvent may evaporate very quickly, leading to larger fiber diameters (less time for elongation before solidification) and clogging of the spinneret (due to drying of the liquid at the spinneret before jetting, or drying of the Taylor cone during jetting).
+Solvents commonly used for electrospinning include ethanol, chloroform, trichloroethane and hexafluoroisopropanol\unskip~\cite{527120:12073495,527120:16887323,527120:16887324}.
+
+Mixtures of miscible solvents can be used to ensure that sufficient polymer can be dissolved to give a solution of appropriate viscosity and volatility with suitable dielectric constant range to allow fiber formation.
+However, care must be taken because using a mixture of solvents with very different volatilities can result in porous fiber structures.
+As reported by Katsogiannis et al.
+for organic solvent mixtures with dimethyl sulfoxide (DMSO).\unskip~\cite{527120:13082766} DMSO evaporates much more slowly than the organic solvents used, which results in its incorporation into the fibers.
+The DMSO will eventually evaporate, yielding porous fibers.
+
+It is also important to take into account the surface tension of the solution.
+Solvents with very high surface tensions (e.g.
+water) can result in instability arising during the spinning process, and a broad range of fiber diameters in the products.
+If necessary, a surfactant can be added to reduce the surface tension, but this will be incorporated into the fibers produced.
 
@@
 Some differences have been discovered between LV-NFES and conventional NFES.
-Low voltage near field electrospinning produces thinner fibers with lower voltages.
+Low voltage near field electrospinning produces thinner fibers with lower voltages; as shown inFigure~\ref{f-59ed68f95344}.
 Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching.
 Bisht et al.
-\unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
+and Chang et al.
+\unskip~\cite{527120:11973130,527120:11974313} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
 
-Bisht et al.
-\unskip~\cite{527120:11973130} reports a controlled technique to fabricate polymeric nano fibers in a continuous manner, using a low voltage setup.
+Bisht and Chang's work \unskip~\cite{527120:11973130,527120:11974313} reports a controlled technique to fabricate polymeric nano fibers in a continuous manner, using a low voltage setup.
 Their purpose is to find a workaround to the drawbacks of traditional NFES by using a superelastic polymer precursor, which allow continuous patterning without breaking.
-In low voltage near-field electrospinning (LV NFES), a visco-elastic polymer is used to allow continuous spinning at about 200$V $ .
-The decrease in voltage is prone to produce a controlled polymer jet by reducing the bending instabilities.
-The authors demonstrate the effectiveness of this technique with the fabrication of suspended fibers, see Figure~\ref{f-52c94fbe4526} .
+In low voltage near-field electrospinning (LV NFES), a visco-elastic polymer is used to allow continuous spinning at about 200$V $.
 
-\bgroup
-\fixFloatSize{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}{\includegraphics{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}}{}
-\makeatother 
-\caption{{Suspended nano fibers of 2 wt \% PEO at 300 V.
-(a) Six carbon posts connected by nano fibers.
-(b) Individual nano fiber suspended between the posts.
-(c) Close up of the suspended nano fiber.
-\unskip~\protect\cite{527120:11973130}}}
-\label{f-52c94fbe4526}
-\end{figure*}
-\egroup
-Chang et al.
-\unskip~\cite{527120:11974306} developed a scanning tip electrospinning (a continuous NFES) technique to write nano fibers with control patterning.
-Similar to Bisht et al.
-\unskip~\cite{527120:11973130}, they also demonstrate that the decrease in the applied electric field yields thinner fibers that can be controlled to develop circular shapes (Figure~\ref{f-9d0c3125e550}) and grids (Figure~\ref{f-32e7d8abb3aa}) on a flat surfaces.
-
-\bgroup
-\fixFloatSize{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}{\includegraphics{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}}{}
-\makeatother 
-\caption{{The three-character Cal is drawn on a silicon chip by a programmable x-y stage. \unskip~\protect\cite{527120:11974306}}}
-\label{f-9d0c3125e550}
-\end{figure}
-\egroup
-
-\bgroup
-\fixFloatSize{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}{\includegraphics{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}}{}
-\makeatother 
-\caption{{A triangular grid pattern. \unskip~\protect\cite{527120:11974306}}}
-\label{f-32e7d8abb3aa}
-\end{figure}
-\egroup
 Kim et al.
-\unskip~\cite{527120:11974313} experimented with a NFES variation where the fiber deposition is guided by conductive rails, see Figure~\ref{f-927e96fb5537} .
+\unskip~\cite{527120:11974313} experimented with a NFES variation where the fiber deposition is guided by conductive rails, see Figure~\ref{f-927e96fb5537}.
 As stated by the authors, the induced electric field is enhanced by the conductive pattern, which allows the fibers to follow the desired deposition path.
 As the fibers are prone to follow the conductive pattern, additional fibers can be stacked on each other.
-The stacking process was successfully achieved in high electric field conditions at: 750$\mu m $ substrate to collector distance, and 600 $\mu m $ needle to rail (offset) distance, see  .
-(Applied voltage not explicitly specified for "straight line pattern" and stacking experiments, only stated the implementation of 1.9 $kV $ on "sharp-edged shapes pattern" experiments).
+The stacking process was successfully achieved in high electric field conditions at: 750$\mu m $ substrate to collector distance, and a 600 $\mu m $ needle to rail (offset) distance, see Figure~\ref{f-927e96fb5537}.
 
@@
 \egroup
-
-\bgroup
-\fixFloatSize{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}{\includegraphics{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}}{}
-\makeatother 
-\caption{{SEM and CCD camera images of stacked fibers on the conductive pattern when high electric field and low electric field were applied}}
-\label{f-24b5148e8358}
-\end{figure}
-\egroup
 Gupta et al.\unskip~\cite{527120:11974310} introduced a new technique to fabricate polymer scaffolds for tissue engineering applications and organ development.
-The authors implemented two polymer solutions, with POSS-PCU (polyhedral oligomeric silsesquioxane-poly(carbonate-urea)urethane, a non-biodegradable polymer precursor) and with POSS-PCL-PCU (poly- hedral oligomeric silsesquioxane-polycaprolactone-poly(carbonate- urea)urethane, a biodegradable polymer precursor).
-
 As described by Gupta et al.\unskip~\cite{527120:11974310}, the fiber deposition equipment is comprised by a stainless steel needle with a internal diameter of 750 $\mu m $ , connected to a high voltage power supply of up to 30 $k V $ with a deposition rate of about $\geq 1 \mu L min^{-1} $.
@@
 \unskip~\cite{527120:11974322,527120:11974323,527120:11974324} experimented with several multi-nozzle near-field electrospinning of aligned nano fibers.
-The multinozzle NFES apparatus is similar to the one used in conventional NFES with some modifications to the needle nozzle, see Figures~\ref{f-96ee25855dea} and~\ref{f-4a1a1f58a423}.
+The multi nozzle NFES apparatus is similar to the one used in conventional NFES with some modifications to the needle nozzle, see Figures~\ref{f-96ee25855dea} and~\ref{f-4a1a1f58a423}.
 The authors implemented similar NFES setups where the installed linear array of nozzles is supplied with a constant flow rate of solution.
@@
 \egroup
-The purpose of multinozzle setups is to increase productivity, and not necessarily to deposit fibers in a direct, continuous and controllable manner, since the setup itself limits the patterning design to parallel aligned fibers, as sown in Figure~\ref{f-4f1fb5cbfee6}.
-The introduction of more needle \_also\_ introduces more process parameters that have an influence in the produced fiber morphology.
-The added process parameters comprise the needle length, and needle spacing \unskip~\cite{527120:11974323}.
-
-\bgroup
-\fixFloatSize{images/9569179c-0fea-4f46-bb0f-b3103fbd20aa-uwang_02.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/9569179c-0fea-4f46-bb0f-b3103fbd20aa-uwang_02.png}{\includegraphics{images/9569179c-0fea-4f46-bb0f-b3103fbd20aa-uwang_02.png}}{}
-\makeatother 
-\caption{{Morphology of aligned nano fibers pattern during three-nozzle NFES process.
-The experiment works in environment as electrode-to-collector distance 4.0 mm and applied voltage 2.5KV \unskip~\protect\cite{527120:11974323}}}
-\label{f-4f1fb5cbfee6}
-\end{figure}
-\egroup
 The authors came to the conclusion that the distance between the deposited fibers increase with the increase of the needle-to-collector distance, as the influence of the applied voltage dissipates.
@@
 \egroup
-Zheng, et al.\unskip~\cite{527120:11974328} worked the near field electrospinning process with an AC power supply, also known as AC EDW (AC Pulse-Modulated Electrodynamic Direct-Writing).
-The alternating current decreased the repulsive force applied along the jet, allowing a stable jet.
-The AC EDW was implemented to produce micro fibers on an insulated PET (Polyethylene Terephthalate) collector.
-AC EDW fibers were successfully fabricated between x-y collector velocities from 700 to 1500 $mm / s $, see Figure~\ref{f-b2c382d8b6ab}.
-Zheng's work \unskip~\cite{527120:11974328}, Studied the effects of the AC voltage amplitude, frequency and duty cycle on the obtained fiber diameters.
-Zheng, et al.\unskip~\cite{527120:11974328} arrived to three conclusions: a) The fiber diameter increases from $\sim 14 \mu m $ to $\sim 35 \mu m $ with an increase in voltage amplitude from $\sim0V $ to $\sim 3000 V $, and decreases from $\sim 35 \mu m $ to $\sim 21 \mu m $ with an increase in voltage amplitude from $\sim 3000 V $ to $\sim 4000 V $; b) The fiber diameter increases from $\sim 14 \mu m $ to $\sim 35 \mu m $ with an increase in voltage amplitude from $\sim0V $ to $\sim 3000 V $, and decreases from $\sim 35 \mu m $ to $\sim 21 \mu m $ with an increase in voltage amplitude from $\sim 3000 V $ to $\sim 4000 V $;; and c) The fiber diameter increases from $\sim 14 \mu m $ to $\sim 35 \mu m $ with an increase in voltage amplitude from $\sim0V $ to $\sim 3000 V $, and decreases from $\sim 35 \mu m $ to $\sim 21 \mu m $ with an increase in voltage amplitude from $\sim 3000 V $ to $\sim 4000 V $;.
-
-\bgroup
-\fixFloatSize{images/f684a658-c64f-4f11-ba18-7debcb5e9977-uzheng_00.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/f684a658-c64f-4f11-ba18-7debcb5e9977-uzheng_00.png}{\includegraphics{images/f684a658-c64f-4f11-ba18-7debcb5e9977-uzheng_00.png}}{}
-\makeatother 
-\caption{{Micro fibers on insulated PET collector under AC electrical field with varying stage velocities\unskip~\protect\cite{527120:11974304}.}}
-\label{f-b2c382d8b6ab}
-\end{figure*}
-\egroup
 Micro and nano fibers have been written using AC pulse-modulated electrospinning by Bu et al.
@@
 The alternate current tends to decrease the repulsive electrical force allowing a stable straight jet between the dispensing nozzle and the insulating PET substrate.
-As depicted inFigure~\ref{f-b2c382d8b6ab}, Bu et al.
-varied the stage velocity.
-Faster stage velocities enable the deposition of straighter fibers\unskip~\cite{527120:11974304}.
+Bu et al.
+varied the stage velocity; faster stage velocities enable the deposition of straighter fibers\unskip~\cite{527120:11974304}.
 
-\bgroup
-\fixFloatSize{images/1847814e-ac17-4b33-ba90-6fe8b7336699-unagle_00.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{images/1847814e-ac17-4b33-ba90-6fe8b7336699-unagle_00.png}{\includegraphics{images/1847814e-ac17-4b33-ba90-6fe8b7336699-unagle_00.png}}{}
-\makeatother 
-\caption{{Planar nano fiber patterning. Microscopy images of PEO fibers on silicon wafers at different working distances.}}
-\label{f-f259e0a97fc2}
-\end{figure}
-\egroup
- A mechano-electrospinning technique was presented by Nagle et al.\unskip~\cite{527120:12033656} similar to the one presented in Figure~\ref{f-432d16f420fb}.
+ A mechano-electrospinning technique was presented by Nagle et al.\unskip~\cite{527120:12033656}.
 With the implementation of a mechanical drawing force, a higher resolution nano fibrous pattern can be produced with lower voltages as the Taylor cone becomes more stable.
@@
 Near field mechano-electrospinning enables the collection of non woven fibers over large areas.
-
-\section{Polymer Solution}
-In electrospinning, it is typically agreed that the diameter of the fibers increased with higher concentration due to greater viscosity which withstands stretching.
-In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}.
-However, in separate studies by Pan et al.\unskip~\cite{527120:11974317,527120:12321129} using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
-\begin{table}[!htbp]
-\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
-\label{tw-8687dd17082c}
-\def\arraystretch{1}
-\ignorespaces 
-\centering 
-\begin{tabulary}{\linewidth}{LL}
-\tbltoprule Observation & Concentration Adjustement\\
-\tblmidrule 
-Dripping, no stream &
-  Increase\\
-Splitting small droplets &
-  Increase slightly\\
-Steady stream &
-  No concentration adjustment\\
-Splitting large globs &
-  Decrease slightly\\
-Nozzle clogging  &
-  Decrease\\
-\tblbottomrule 
-\end{tabulary}\par 
-\end{table}
-
-\subsection{Polymers}The polymer selection is in function on the intended application.
-For example, a fast dissolving hydrophilic polymer such as poly(ethylene oxide) (PEO) is used for fast drug delivery systems.
-Otherwise, slow dissolving polymers such as poly($\varepsilon $-caprolactone) (PCL) or poly(lactic-co-glycolic acid) (PLGA) are implemented.
-\unskip~\cite{527120:13082763}
-
-The polymer molecular weight along with the polymer concentration and solvent selection have a direct effect on the solution viscosity, conductivity and surface tension, hence the solution behavior in the electrospinning process.
-The spunable viscosity range varies with the polymer and solvent.
-
-Solutions with low viscosity are prone to insufficient polymer chain entanglements to produce fibers.\unskip~\cite{527120:13082763} On the other hand, if the solution is too viscous, then the surface tension cannot easily be overcome by the electric field.
-In both cases, the result can be droplets or particles forming rather than fibers; see Table~\ref{tw-8687dd17082c}.
-
-\subsection{Solvents}The solvent used must be capable of dissolving the polymer of interest at an appropriate concentration to form fibers, and must posses a suitable volatility.
-A low-volatility solvent like water may fail to evaporate completely over the distance between the spinneret and the collector.
-When the fibers form, they will hence contain residual water owing to this incomplete evaporation.
-The residue solvent will subsequently evaporate from the fibers upon storage, resulting in ribbon-like (flattened) fibers, wrinkles on the fiber surface or fused fibers.
-On the other hand, a high-volatility solvent may evaporate very quickly, leading to larger fiber diameters (less time for elongation before solidification) and clogging of the spinneret (due to drying of the liquid at the spinneret before jetting, or drying of the Taylor cone during jetting).
-Solvents commonly used for electrospinning include ethanol, chloroform, dichloromethane and hexafluoroisopropanol.
-
-Mixtures of miscible solvents can be used to ensure that sufficient polymer can be dissolved to give a solution of appropriate viscosity and volatility with suitable dielectric constant range to allow fiber formation.
-However, care must be taken because using a mixture of solvents with very different volatilities can result in porous fiber structures, as reported by Katsogiannis et al.
-for organic solvent mixtures with dimethyl sulfoxide (DMSO).\unskip~\cite{527120:13082766} DMSO evaporates much more slowly than the organic solvents used, which results in its incorporation into the fibers.
-The DMSO will eventually evaporate, yielding porous fibers.
-
-It is also important to take into account the surface tension of the solution.
-Solvents with very high surface tensions (e.g.
-water) can result in instability arising during the spinning process, and a broad range of fiber diameters in the products.
-If necessary, a surfactant can be added to reduce the surface tension, but this will be incorporated into the fibers produced.
-
-\section{Effect of the NFES Parameters}
 
@@
 
-Near-field electrospinning, has exhibited to be capable fabricate nano fibers over and nano fiber patterns \unskip~\cite{527120:11974321}.
+Near-field electrospinning, has exhibited to be capable fabricate nano fibers and nano fiber patterns \unskip~\cite{527120:11974321}.
 Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner.
@@
 syringe) of solution generally produces fibers with diameter of a few micrometers \unskip~\cite{527120:11974310,527120:11974326}, since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through.
+As shown inFigure~\ref{f-51afaccaf109}, the implementation of thicker needle nozzles translate into an increase of the resulted fiber diameter
 
@@
 
-\subsection{Nozzle spinneret}The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al.\unskip~\cite{527120:11974306} used a 100 $\mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
+\subsection{Nozzle spinneret}The thinnest nozzles in literature so far are about $50 nm $ in diameter, by Chang et al.\unskip~\cite{527120:11974306} who used a  $100 \mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO).
+Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
 The nozzle most commonly comprises a simple narrow-bore, blunt-end metal needle.
@@
 However, it should be noted that there will be some interactions between the solvent and polymer molecules in the solution and the metal surface of the spinneret.
-There will exist some attractive forces between the polar groups in the polymer and the electro positive metal surface, which can act counter to the drawing force of the electric field and can pull the polymer solution back into the spinneret.
-It has been found that coating the spinneret exterior in a non-conductive and non-stick polymer such as Teflon can reduce these interactions.\unskip~\cite{527120:13082768} As a result, the electrical energy can be more efficiently used to elongate and narrow the polymer jet, and narrower fibers can be produced.
+There will exist some attractive forces between the polar groups in the polymer and the electro-positive metal surface, which can act counter to the drawing force of the electric field and can pull the polymer solution back into the spinneret.
+It has been found that coating the spinneret exterior in a non-conductive and non-stick polymer such as Teflon or epoxy coating can reduce these interactions.\unskip~\cite{527120:13082768,527120:13082811} As a result, the electrical energy can be more efficiently used to elongate and narrow the polymer jet, and narrower fibers can be produced.
 In addition, strong attractive forces between the polymer jet and the metal spinneret can result in fibers becoming attracted to the needle, leading to lower yields and potentially to blocking of the exit orifice.
-This effect too can be ameliorated using an epoxy coating.\unskip~\cite{527120:13082811}
 
 \subsection{Applied Voltage}In recent literature, near field electrospinning has been studied to reduce the fiber diameter and to improve the fiber deposition accuracy.
-Camillo et al.\unskip~\cite{527120:12322072} demonstrated that the application of a modified fine tip nozzle enables the fabrication of 100 $nm $ diameter fiber at a nozzle-to-substrate distance of 500 $\mu m $ and an applied voltage of 1.5 $kV $ .
-On the other hand, Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} came to the conclusion higher voltages yield thicker micro-fibers with a loss in jet stability.
-
-This discrepancy in literature between the applied voltage and resulting fiber diameter is due to the relationship with other variables such as nozzle-to-substrate distance and solution deposition rate.
+Madou et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} came to the conclusion higher voltages yield thicker micro-fibers with a loss in jet stability.
+This relationship between the applied voltage and resulting fiber diameter is influenced by other variables such as nozzle-to-substrate distance and solution deposition rate.
 For instance, if a high voltage is applied at a low deposition rate then electrospraying is achieved, meaning the formation of several non-continuous fibers.
@@
 
-Bisht et al.\unskip~\cite{527120:11973130} achieved the fabrication of thinner fibers with spatial control by reducing the applied voltage to 200-600 $V $  at a nozzle-to-substrate distance of 0.5-1 $mm $.
+Madou et al.\unskip~\cite{527120:11973130} achieved the fabrication of thinner fibers with spatial control by reducing the applied voltage to 200-600 $V $  at a nozzle-to-substrate distance of 0.5-1 $mm $.
 The low voltage setting does not create enough charge to break the polymer solution surface tension to initiate the electrospinning process.
 
-Bisht et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} initiated the electrospun fibers by mechanically pull the polymer solution at the nozzle tip using a micro-probe tip.
+Madou et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} initiated the electrospun fibers by mechanically pull the polymer solution at the nozzle tip using a micro-probe tip.
 Chang and coworkers reduced the applied voltage from 1.5 $kV $ to 600 $V $ with a nozzle-to-substrate distance of 500 $\mu m $ to yield a fiber diameter between 3 $\mu m $  and 50 $nm $ .
-With an applied voltage of 200 $V $ and a nozzle-to-substrate distance of 1 $mm $ , PEO nano fibers were deposited with a diameter about 20 $nm $.
+With an applied voltage of 200 $V $ and a nozzle-to-substrate distance of 1 $mm $.
 
@@
 Song et al.\unskip~\cite{527120:11974320} demonstrated that a decrease in voltage from 400 to 500 $V $ can reduce the fiber diameter from 160 to about 60 $nm $with a nozzle-to-substrate distance of 20 $\mu m $.
-The optimum voltage is achieved when a balance is attained between the stretching of the jet and the speed at which it hits the substrate.
-The increase of voltage yields thinner fibers as it causes greater stretching, and a greater jet acceleration.
+A workaround to break the polymer solution surface tension is to initialize the NFES process with a higher voltage and then lower the voltage once the jet is created.
+Huang et al.\unskip~\cite{527120:11974311} implemented the previous and yield ordered fibers with a distance between adjacent fibers of 50 $\mu m $.
 
-Another workaround to break the polymer solution surface tension is to initialize the NFES process with a higher voltage and then lower the voltage once the jet is created.
-Huang et al.\unskip~\cite{527120:11974311} implemented the previous and yield ordered fibers with a distance between adjacent fibers of 50 $\mu m $.
-In most cases, a positive voltage is applied to the spinneret.
+\subsection{Nozzle-to-substrate distance}
+\bgroup
+\fixFloatSize{images/4cc65220-1457-4d0d-bb04-9b1c8138aa96-uffes_vs_nfes.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{images/4cc65220-1457-4d0d-bb04-9b1c8138aa96-uffes_vs_nfes.png}{\includegraphics{images/4cc65220-1457-4d0d-bb04-9b1c8138aa96-uffes_vs_nfes.png}}{}
+\makeatother 
+\caption{{a) Typical Far-field Electrospinning (FFES) Setup. b) Typical Near-field Electrospinning (NFES) Setup.}}
+\label{f-c34559531e3e}
+\end{figure*}
+\egroup
+Figure~\ref{f-c34559531e3e}.a, depicts the typical setup for the conventional far-field electrospinning (FFES).
+As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}.
+When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process.
+The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}.
+The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.
 
-\subsection{Nozzle-to-substrate distance}In NFES, the fiber morphology can be altered by the control of the height between the nozzle and the substrate (collector).
+In the intent to achieve controlled fiber deposition, Sun et al.
+\unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES),Figure~\ref{f-c34559531e3e}.b, describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line.
+Moreover, some mechanical influence is required to deposit fibers precisely.
+The mechanical force is introduced by moving collector.
+If the polymer solution jet speed is faster than the speed of the moving collector, the written fiber will curl; on the other hand, if the collector moves faster than the polymer jet, the fiber will gradually diminish \unskip~\cite{527120:11974327,527120:11974326}.
+Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.
+
+The main difference between NFES and FFES is the distance between the needle and the collector which is higher in FFES (about 10 cm) compared to NFES which ranges in the mm scale.
+The short distance allow the production of well aligned fibers within particular designs.
+In NFES, the fiber morphology can be altered by the control of the distance between the nozzle and the substrate (collector).
 With the decrease of the nozzle-to-substrate distance, the electric field strength increases; however it can cause incomplete solvent volatilisation and possible short circuits between the collector and the nozzle tip.
@@
 
-Typically, metal nozzle tips are used, with small inner diameters.
-From literature, needles with small diameters produce thinner fibers.
-A thin nozzle tip can help the reduction of the fiber diameter, but also it is more likely to become blocked.
-
-\subsection{Electric field}Recent literature suggests that the fiber morphology depends on the electric field profile created by the applied voltage during NFES.
-Since the electric field is an induced force that attracts the solution jet towards the desired location within the collector.
-
-Bisht et al.\unskip~\cite{527120:11973130} and Min et al.\unskip~\cite{527120:11974316} have reported the ability to electrospin nano fibers with high accuracy.
-Min et al.
-\unskip~\cite{527120:11974316} implemented a NFES setup with multiple "field-effect transistors" on a flexible polyacrylate collector with an x-y stage velocity of 13.3 $cm/s $ to fabricate fibers with a diameter about 289 $nm $ and a distance between adjacent fibers of 50 $\mu m $.
-
-On the other hand, Bisht et al.\unskip~\cite{527120:11973130} showed evidence of fabricated fibers with low-voltage NFES with high accuracy and precision.
-Bisht et al.'s suspended fibers were deposited over carbon posts with a distance between adjacent fibers of 100 $\mu m $ with diameter of 30 $\mu m $\unskip~\cite{527120:11973130}.
-
-The employment of guided electrodes in NFES, adapts the fabrication process to yield a more accurate fiber deposition.
-For instance, Kim et al.\unskip~\cite{527120:11974313} manufactured ink patterns on a paper with silver nano particles.
-The printed patterns aid the fibers to land on the desired location.
-Kim et al.\unskip~\cite{527120:11974313} electrospun the fibers with a distance between adjacent fibers of 150 $\mu m $.
-
-Xu et al.\unskip~\cite{527120:11974325} created a straight jet from the nozzle tip to the substrate using a guiding electrode underneath the collector.
-The purpose of the guiding electrode is to adjust the path of the NFES jet.
-With the guiding electrode implementation, the fiber's spread was reduced from 74 $\mu m $ to 7 $\mu m $.
-
 \subsection{Substrate}Due to the close distance between the grounded substrate and the charged spinneret in NFES, the set up is prone to electrical shorts.
 In NFES, when a short circuit takes place, the electrospinning process is interrupted resulting in the fabrication of discontinuous fibers.
-Two workarounds to avoid electrical shorts is to lower the applied voltage and to install less conductive substrates \unskip~\cite{527120:11974315,527120:12322289}.
+Two workarounds to avoid electrical shorts is to lower the applied voltage and to use less conductive substrates \unskip~\cite{527120:11974315,527120:12322289}.
 
@@
 
-On the other hand, Choi et al.\unskip~\cite{527120:12322289} implemented a hydrophobic substrate to deposit the fibers with plasma treatment to increase the conductivity of selected areas.
+On the other hand, Choi et al.\unskip~\cite{527120:12322289} implemented a hydrophilic substrate to deposit the fibers with plasma treatment to increase the conductivity of selected areas.
 NFES was carried put with precise deposition as the fibers were placed as per the desired design within the hydrophilic substrate.
 
-\section{Conclusion}
+\section{Discussion \& NFES Challenges}
 Helix electrodynamic printing (HE-printing) was presented by Duan et al.
@@
 \makeatother 
-\caption{{}}
+\caption{{NFES Applied Voltage vs. Fiber Diameter}}
 \label{f-59ed68f95344}
@@
 \makeatother 
-\caption{{}}
+\caption{{Nozzle Diameter vs. Fiber Diameter}}
 \label{f-51afaccaf109}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/6bd5e441-92a9-4f82-856d-85b3a7ada5ff-uplt_nozzlediameter_vs_polymerconcentration.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/6bd5e441-92a9-4f82-856d-85b3a7ada5ff-uplt_nozzlediameter_vs_polymerconcentration.png}{\includegraphics{images/6bd5e441-92a9-4f82-856d-85b3a7ada5ff-uplt_nozzlediameter_vs_polymerconcentration.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-47bf72d21b5d}
 \end{figure*}
@@
 \makeatother 
-\caption{{}}
+\caption{{Nozzle to Collector Distance vs. Fiber Diameter}}
 \label{f-5f453fad619f}
@@
 \makeatother 
-\caption{{}}
+\caption{{Polymer Concentration vs. Fiber Diameter}}
 \label{f-d977f56a0782}
@@
 \makeatother 
-\caption{{}}
+\caption{{Solution Deposition Rate vs. Fiber Diameter}}
 \label{f-08e527ddef81}
-\end{figure*}
-\egroup
-
-\bgroup
-\fixFloatSize{images/42209168-f90a-4aaa-a235-c9049fb5bb59-uplt_solutiondepositionrate_vs_polymerconcentration.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{images/42209168-f90a-4aaa-a235-c9049fb5bb59-uplt_solutiondepositionrate_vs_polymerconcentration.png}{\includegraphics{images/42209168-f90a-4aaa-a235-c9049fb5bb59-uplt_solutiondepositionrate_vs_polymerconcentration.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-232ba077005e}
 \end{figure*}
@@
 
-\section{NFES Achievements \& Challenges}
 Near-field electrospinning (NFES) is widely recognized as a versatile nano fabrication method, one suitable for applications in tissue engineering.

### 2020-09-17 5_Thesis/THESIS_LaTeX/Chapters/1.tex
find carbyne SEM figure

--- 2020-06-04 myThesis/thesis_LaTeX/Chapters/1.tex
@@
 Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
-\cite{Siddiqui2019} Carbon nano-materials are suitable for catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing, and cancer detection.
-\cite{Siddiqui2019} Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity.
-\cite{Siddiqui2019}
+Carbon nano-materials are suitable for catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing, and cancer detection.
+Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity.
+\cite{Siddiqui2019, McCreery2008, Geim2011, Zhu2010, Katsnelson2008, Li2008, Geim2007, Geim2009}
 
-This document bestows a thesis project to perform research to engineer and design a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner.
-The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization, and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials.
+This document bestows a thesis project to perform research to engineer a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner.
+The research intends to involve several manufacturing processes such as near field electrospinning, photo-polymerization, pyrolization, and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials.
 \cite{Cardenas2017} See Figure \ref{fig:fabricationFlowChart}.
-A number of processes have been developed for specific purposes of polymeric nano-fibers, some include surface deposition, composites, and chemical adjustments.
+A number of processes have been developed for specific purposes of polymeric nano-fibres, some include surface deposition, composites, and chemical adjustments.
 Polymeric nano-fibers must be also pyrolyzed to generate carbon nano-wires with conductive capabilities \cite{Madou2011} for electrochemical sensing and energy storage purposes.
@@
 \centering
-\includegraphics[width=0.95\textwidth]{./Figures/FabricationProcess.png}
+\includegraphics[width=1.0\textwidth]{./Figures/FabricationProcess2.png}
 \decoRule
-\caption[Fabrication Process]{Fabrication process of conductive carbon nano-wires to achieve through the proposed dissertation.}
+\caption[Fabrication Process]{Fabrication process and characterization techniques of conductive carbon nano-wires to achieve through the dissertation.}
 \label{fig:fabricationFlowChart}
@@
 Nanotechnology has led to the study of different polymer patterning techniques to integrate carbon nano-wires structures.
-One technique is known as far-field electrospinning, a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibers which are then pyrolyzed at high temperatures.
-One sub-technique derived from electrospinning is near field electromechanical spinning or EMS.
-EMS has proved to deliver high control in patterning polymeric nano-fibers.
+One technique is known as far-field electrospinning (FFES), a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibres which are then pyrolyzed at high temperatures.
+One sub-technique derived from electrospinning is near-field electromechanical spinning or NFEMS.
+Unlike FFES, NFEMS has proved to deliver high control in patterning polymeric nano-fibres.
 \cite{Cardenas2017}
@@
 Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist.
-\cite{Cardenas2017} This research proposal is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by near field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires.
-The polymer solutions described by Cardenas \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.
+\cite{Cardenas2017, Flores2017} This work is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by NFEMS, photo-polymerized and pyrolyzed into conducting carbon nano-wires.
+The polymer solutions described by Cárdenas and Flores \cite{Flores2017, Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.
 
@@
 
-Nanotechnology ability to control or assemble materials at the nanoscale has fostered the development of diverse nanomaterials and nanostructures, including quantum dots [1], nanofibers, nanotubes [2] and nanowires [3,4].
-These nanomaterials are of particular interest for biomedical applications in neurology, where conductive materials may promote electrical and chemical communication within the nervous system at the micro- and nano- scale levels.
-Applications of nanostructures to neuroscience have rapidly expanded from molecular imaging [5], to neuro-regenerative scaffolds [6] and neural interfaces [7-9].
+% \cite{Rauti2019}
 
-In this framework, carbon-based nanomaterials (CBNs) and in particular nanotubes deserve particular attention, due to the exponential increase in neuroscience applications of materials composed mainly by carbon with different hybridization or structures [10].
-
-In this chapter we focus on the applications of CBNs-based technology to provide a picture of past and ongoing research in this field, highlighting the goals that have been achieved and the insights reached in understanding CBNs.
+Nanotechnology ability to control and piece together materials at the nano-scale has enabled the development of various carbon nano-materials and carbon nano-structures, such as nano-dots, nano-fibres, nano-tubes and nano-wires.
+\cite{Posthuma-Trumpie2012, Zhang2009, DeVolder2011, Cao2011} This chapter bestows on the applications at the micro-scale and nano-scale levels, as well as the current research of carbon-based nano-materials (CBNs).
 
@@
 
-Carbon is the most versatile element in the periodic table [11], owing to the large number of bonds of different type and strength that can form with it or with many other elements.
-Moreover, the ability of carbon orbitals to hybridize in sp, sp2 and sp3 configurations paves the way to the existence of a number of allotropes.
+Carbon is a versatile element capable to form a number of bonds with other elements or with itself.
+Furthermore, carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, hence the existence of different types of allotropes, see Figure \ref{fig:carbonAllotropes}.
 To date, the three naturally occurring allotropes of carbon (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nanotubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig.

### 2020-09-21 5_Thesis/THESIS_LaTeX/Chapters/1.tex
min update

@@
 Furthermore, carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, hence the existence of different types of allotropes, see Figure \ref{fig:carbonAllotropes}.
-To date, the three naturally occurring allotropes of carbon (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nanotubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig.
+To date, the three naturally occurring allotropes of carbon (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nano-tubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig.
 1].

### 2020-09-24 5_Thesis/THESIS_LaTeX/Chapters/1.tex
thesis in progress
thesis update

--- 2020-09-17 5_Thesis/THESIS_LaTeX/Chapters/1.tex
@@
 \centering
-\includegraphics[width=1.0\textwidth]{./Figures/FabricationProcess2.png}
+\includegraphics[width=1.0\textwidth]{./Figures/FabricationProcess.png}
 \decoRule
@@
 Furthermore, carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, hence the existence of different types of allotropes, see Figure \ref{fig:carbonAllotropes}.
-To date, the three naturally occurring allotropes of carbon (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nanotubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig.
+Currently, the three carbon allotropes (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nano-tubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig.
 1].

### 2020-11-07 05_Thesis/THESIS_LaTeX/Chapters/1.tex
able to fit lin

--- 2020-09-24 5_Thesis/THESIS_LaTeX/Chapters/1.tex
@@
 Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity.
-\cite{Siddiqui2019, McCreery2008, Geim2011, Zhu2010, Katsnelson2008, Li2008, Geim2007, Geim2009}
+\cite{McCreery2008, Geim2011, Zhu2010, Katsnelson2008, Li2008, Geim2007, Geim2009, Siddiqui2019}
 
@@
 
+\begin{figure}[th]
+\centering
+\includegraphics[scale=0.40]{./Figures/CBNfingerprint.png}
+\decoRule
+\caption[CBN Fingerprint]{Molecular to mesoscale structural features of synthetic polymers influence the emergence of specific microstructural features in polymer-derived carbon materials after pyrolysis.}
+\label{fig:CBNfingerprint}
+\end{figure}
+
 Carbon is a versatile element capable to form a number of bonds with other elements or with itself.
-Furthermore, carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, hence the existence of different types of allotropes, see Figure \ref{fig:carbonAllotropes}.
-Currently, the three carbon allotropes (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nano-tubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig.
-1].
+Cabon-based nano-materials (CBNs) exist in diverse forms, depending on the precise values of each degree of freedom that specify the material proclivity at multiple scales.
+Hybridization, crystallization, percolation, anisotropy, porosity, impurities and imperfections are some of the relevant features that determine the CBN set of properties.
+The combination of these features at the micro- and meso-scale burst a variety of macro-scale properties that comprise the CBN fingerprint (\ref{fig:CBNfingerprint}).
+The interminable collection of possible CBN fingerprints range from soft, conductive lubricants to very hard, low conductivity solids; and from black colour, bulks to transparent, disordered thin films.
+\cite{McCreery2008} Figure \ref{fig:carbonAllotropes} shows the existence of different types of allotrope as carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, assembling different types of allotropes.
 
-The interest in CBNs has increased exponentially in the last
-decades, first with the discovery offullerenes (1985), then with that of carbon nanotubes (CNTs; 1991) and finally with the synthesis of graphene (GR) (2004).
+\begin{figure}[th]
+\centering
+\includegraphics[scale=0.40]{./Figures/carbonAllotropes.png}
+\decoRule
+\caption[Carbon Allotropes]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
+\label{fig:carbonAllotropes}
+\end{figure}
+
+Due to the versatility and variety of CBNs, CBNs have been fabricated and implemented for various purposes.
+\cite{Geim2011, Katsnelson2008, Li2008, Geim2007, Geim2009, Siddiqui2019}.
+For instance, field effect transistors (FET) have been studied by Novoselov \cite{Novoselov2004} and Heersche et.
+al.
+\cite{Heersche2007}.
+Carbon FET devices have reported field-effect mobility one order of magnitude higher than that of silicon FETs.
+Other literature suggests CBNs to be favourable to detect a variety of gases and biomolecules.
+\cite{} As molecules are absorbed by the CBN, the carrier density and electrical resistivity of the carbon material changes.
+
+%% Zhu2010
 
 The properties of these CBNs make them widely used in many
-fields ranging from material science [13], energy production and storage [14], environmental sciences [15,16], biology [17-19] and medicine [20,21].
+fields ranging from material science [13, McCreery2008], energy production and storage [14], environmental sciences [15,16], biology [17-19] and medicine [20,21].
 Table 1 summarizes the main properties of the most common CBNs [22-25]:

### 2020-11-07 05_Thesis/THESIS_LaTeX/Chapters/4.tex
able to fit lin

--- 2020-06-04 myThesis/thesis_LaTeX/Chapters/4.tex
@@
 
-\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning, Photopolymerization and Pyrolysis of Polymeric Fibers} % Main chapter title
+\chapter{Fabrication and Characterization of Polymeric Fibers through Near-Field Electrospinning, and Forward-thinking on Photopolymerization and Pyrolysis} % Main chapter title
 
@@
 
+%----------------------------------------------------------------------------------------
+%	SECTION 3
+%----------------------------------------------------------------------------------------
+\section{Comparison of the Obtained Polymer Fibres Against SU8-based Carbon Fibres and Potential Applications}
+% Were the selected candidates electrospunable?
+% Fiber morphology
+
 \section{\emph{conclude with fibre morphology before and after pyrolysis. determine best pyrolysis process}}

### 2020-11-07 05_Thesis/THESIS_LaTeX/main.tex
able to fit lin

--- 2020-08-20 5_Thesis/THESIS_LaTeX/main.tex
@@
 
-% Use the bibtex backend with the authoryear citation style (which resembles APA)
-\usepackage[backend=biber,natbib=true]{biblatex}
-% MLA, APA, or IEEE? - https://www.overleaf.com/learn/latex/Biblatex_citation_styles
-%\usepackage[style=apa, backend=biber]{biblatex}
+% Import references handler
+\usepackage[
+    style     = ieee,         % references format style
+    backend   = biber,        % choose the processing program
+    natbib    = true,         % enable additional reference formats
+    citestyle = numeric-comp, % enable multiple citations
+    sortcites = true,         % sort references in multiple citations
+    sorting   = none          % sort the reference table
+]{biblatex}
 
@@
 \include{./Chapters/5}
-\include{./Chapters/6}
-%\include{./Chapters/7}
 

### 2020-11-07 05_Thesis/thesis_proposal_LaTeX/Chapters/1_Introduction.tex
able to fit lin

--- 2019-05-11 thesis_proposal_LaTeX/Chapters/1_Introduction.tex
@@
 \decoRule
-\caption[Fabrication Process]{Fabrication process of carbon nano-wires to achieve through the proposed dissertation.}
+\caption[Fabrication Process]{Fabrication process of conductive carbon nano-wires to achieve through the proposed dissertation.}
 \label{fig:fabricationFlowChart}
@@
 
-Nanotechnology has explored different polymer patterning techniques to integrate carbon nano-wires structures.
-One technique is known as far-field electrospinning, a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibers which then are pyrolyzed at high temperatures.
+Nanotechnology has led to the study of different polymer patterning techniques to integrate carbon nano-wires structures.
+One technique is known as far-field electrospinning, a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibers which are then pyrolyzed at high temperatures.
 One sub-technique derived from electrospinning is near field electromechanical spinning or EMS.
@@
 \cite{Cardenas2017} This research proposal is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by near field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires.
-The polymer solutions described in \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.
+The polymer solutions described by Cardenas \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.
 
-Traditional near-field electrospinning or NFES allows large scale manufacturability combined with controlled guidance.
+Traditional near-field electrospinning or NFES allows large scale manufacturability combined with spatial control of material deposition.
 \cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation, resulting in limited control for nano-fiber patterning in traditional NFES processes.
-\cite{Madou2011} the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.
+Madou et al.
+\cite{Madou2011} conclude that the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.
 

### 2020-11-09 05_Thesis/THESIS_LaTeX/main.tex
thesis match the template

@@
 % Your supervisor's name, this is used in the title page, print it elsewhere with \supname and \cosupname
-\supervisor{Dr. Héctor Alán \textsc{Aguirre} Soto}
-\cosupervisor{Dra. Dora Iliana \textsc{Medina} Medina}
+\supervisor{Dr. Héctor Alán Aguirre Soto}
+\cosupervisor{Dra. Dora Iliana Medina Medina}
 
@@
 % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
-\author{Antonio Osamu \textsc{Katagiri} Tanaka}
+\author{Antonio Osamu Katagiri Tanaka}
 
@@
 % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
-\keywords{nanotechnology, carbon, nano-wires, electrospinning, NFES}
+\keywords{nanotechnology, carbon, nano-wires, Near-Field Electrospinning, NFES}
 
@@
 \group{\href{https://www.medinadora.com/people}{ITESM \campusname}}
+
+\examDateAndAddress{\addressname \text{, } \large December 02, 2020}
 
@@
 
+% Research group name and department name
+\campusname\\\deptname\\[1cm]
+
 \begin{center}
-\includegraphics[width=0.15\textwidth]{./Figures/uniLogo.png}
+\includegraphics[width=0.20\textwidth]{./Figures/uniLogo.png}
 \end{center}
@@
 \vspace{0.5cm}
-\textsc{\Large Masters Thesis Proposal}\\[0.5cm]      % Thesis type
 
@@
 
-\begin{minipage}[t]{0.4\textwidth}
-\begin{flushleft} \large
-\emph{Author:}\\
+\emph{A thesis presented by:}\\
 
@@
 %\authorname
-\end{flushleft}
-\end{minipage}
-\begin{minipage}[t]{0.4\textwidth}
-\begin{flushright} \large
-\emph{Principal Advisor:} \\
-% Supervisor name - remove the \href bracket to remove the link
-%\href{http://www.doramedina.com}{\supname}
-\supname
-
-\bigskip
-
-\emph{Co-advisor and\\Director of Program:} \\
-% Supervisor name - remove the \href bracket to remove the link
-\href{https://www.medinadora.com/}{\cosupname}
-%\cosupname
-\end{flushright}
-\end{minipage}\\[0.5cm]
+\\[0.5cm]
 
@@
 
-\large \textit{A thesis proposal submitted in fulfillment of the requirements\\ for the degree of
 % University requirement text
-\degreename}\\[0.25cm]
+\large \textit{Submitted to the\\
+\deptname\\
+in partial fulfillment of the requirements for the degree of}\\[0.25cm]
+\textit{Master of Science}\\[0.25cm]
 \textit{in}\\[0.25cm]
-% Research group name and department name
-\groupname\\\deptname\\[1cm]
+\textit{Nanotechnology}
 
@@
 % Address and Date
-{\addressname \text{, } \large \today}\\[4cm]
+\examDate\\[4cm]
 % University/department logo - uncomment to place it
@@
 \begin{committee}
-\addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
-The committee members, hereby, recommend that the proposal by \authorname \text{ }to be accepted to develop the thesis project as a partial requirement for the degree of \degreename.
+%\addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
+The committee members, hereby, certify that have read the dissertation presented by \authorname \text{ } and that it is fully adequate in scope and quality as a partial requirement for the degree of \degreename.
 
@@
 Tecnológico de Monterrey\\
+\deptname\\
 \emph{Principal Advisor}
@@
 %\href{http://www.alanaguirre.com}{\supname}
-Dr. Marc \textsc{Madou}\\
-Tecnológico de Monterrey\\
+Dr. Marc Madou\\
+University of California\\
 \emph{Committee Member}
@@
 %\href{http://www.alanaguirre.com}{\supname}
-Dr. Sergio Omar \textsc{Martínez} Chapa\\
+Dr. Sergio Omar Martínez Chapa\\
 Tecnológico de Monterrey\\
@@
 \noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
-\cosupname \\
-\emph{Director of Program in Nanotechnology}\\
-School of Engineering and Sciences\\
+Dr. Martín Rogelio Bustamante Bello \\
+\emph{Associate Dean of Graduate Students}\\
+\deptname\\
 %\href{http://www.doramedina.com}{\supname}
@@
 \bigskip
-{\addressname \text{, } \large \today}\\[0cm]
+\examDate\\[0cm]
 
@@
 \begin{declaration}
-\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
+%\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
 \noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
@@
 \item This work was done wholly or mainly while in candidature for a research degree at this University.
-\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
+\item	Where any part of this dissertation has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
 \item	Where I have consulted the published work of others, this is always clearly attributed.
-\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
+\item	Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this dissertation is entirely my own work.
 \item	I have acknowledged all main sources of help.
-\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
+\item	Where the dissertation is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.
+\\
 \end{itemize}
 
-\noindent Signed:\\
-\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
+\bigskip
 
-\noindent Date:\\
-\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
+\begin{flushright}
+\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
+\authorname\\
+\examDate
+\end{flushright}
+
+\vfill
+
+\begin{center}
+@2020 by \authorname\\
+All rights reserved
+\end{center}
+
 \end{declaration}
@@
 
+%%----------------------------------------------------------------------------------------
+%%	QUOTATION PAGE
+%%----------------------------------------------------------------------------------------
+%
+%\vspace*{0.2\textheight}
+%
+%\begin{center}
+%\includegraphics[width=0.60\textwidth]{./Figures/quote.png}
+%
+%\noindent\enquote{\itshape No great discovery was ever made without a bold guess.}\bigbreak
+%\end{center}
+%
+%\begin{flushright}
+%\textbf{Newton, Sir Isaac} \linebreak
+%In W.I.B. Beveridge \linebreak
+%\emph{The Art of Scientific Investigation} \linebreak
+%Scientist (p. 145)
+%\end{flushright}
+
 %----------------------------------------------------------------------------------------
-%	QUOTATION PAGE
+%	DEDICATION
 %----------------------------------------------------------------------------------------
 
-\vspace*{0.2\textheight}
+\begin{dedication}
+%\addchaptertocentry{\dedicationname} % Add the acknowledgements to the table of contents
+Thanks for all your unconditional confidence, support, patience, and encouragement. You were my main motivation for pushing through this work.
 
-\begin{center}
-\includegraphics[width=0.60\textwidth]{./Figures/quote.png}
+\end{dedication}
 
-\noindent\enquote{\itshape No great discovery was ever made without a bold guess.}\bigbreak
-\end{center}
+%----------------------------------------------------------------------------------------
+%	ACKNOWLEDGEMENTS
+%----------------------------------------------------------------------------------------
 
-\begin{flushright}
-\textbf{Newton, Sir Isaac} \linebreak
-In W.I.B. Beveridge \linebreak
-\emph{The Art of Scientific Investigation} \linebreak
-Scientist (p. 145)
-\end{flushright}
+\begin{acknowledgements}
+%\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
+There are a number of people without whom this thesis might not have been written,
+and to whom I am greatly indebted.\\
+
+% To my mother, Helena, who continues to learn, grow and develop and who has been a source of encouragement and inspiration to me throughout my life, a very special thank you for providing a ‘writing space’ and for nurturing me through the months of writing.
+And also for the myriad of ways in which, throughout my life, you have actively supported me in my determination to find and realise my potential, and to make this contribution to our world.\\
+
+% To my mother-in-law, Maryam, known only briefly but loved and missed, who represented to me ‘living proof’ of Black women’s ability to redefine and recreate our lives despite, and maybe even because of, the tremendously constraining, oppressive and repressive situations in which we often exist.\\
+
+% To my dear husband, Bala who remains willing to engage with the struggle, and ensuing discomfort, of having a partner who refuses to accept the given role of the "Black woman" and is actively engaged in redefining and redesigning that role.
+A very special thank you for your practical and emotional support as I added the roles of wife and then mother, to the competing demands of business, work, study and personal development.\\
+
+% Thanks to dear Kamal and Azaria, for being so supportive - even when being ‘without Mum’ was hard, and for your help with the bibliography and diagrams.
+This work is for, and because of you and all the generations to come.
+It is dedicated to all our journeys in learning to thrive.\\
+
+% It is also dedicated to Josephine - friend, ‘sister’, colleague, ‘co- traveller’ and researcher - who knowingly and unknowingly- led me to an understanding of some of the more subtle challenges to our ability to thrive.
+If our attempts to claim our right to speak our truth, and to unravel and follow the threads through which our oppression is maintained, and are instrumental in helping one other Black woman from ‘going over the edge’ - in which sight we continuously live our lives - perhaps, it might be seen that your invaluable contribution to the attainment of many of the insights gained was worth it.
+It is also written in honour of all our my grandmothers, and their mothers, and grandmothers, and to all our and mothers and grandmothers, who though not marked by history struggled so heroically to resist the definitions attributed to them by the dominant system and communicate messages of hope and expectation.
+I am also very grateful to Maya Angelou, for the inspiration she has been to methrough her writings, poetry readings and as a living representation of a woman thriving.
+Thanks to Mary Washington, Alice Walker, Jackie Kay, Buchi Emecheta, Toni Cade, Lauretta Ngobo, bell hooks, and other Black women writers of the 1980’s, who in telling stories for and about us validated me and my experiences in ways I cannot begin to explain here.\\
+
+% Loving thanks to my friends and learning partners, Agnes, Susan, Ulana and Namonya, who played such important roles along the journey, as we mutually engaged in making sense of the various challenges we faced and in providing encouragement to each other at those times when it seemed impossible to continue.
+
+I offer my gratitude and appreciation to my supervisors, \supname \textit{ } and \cosupname, for the deft ways in which you fondly challenged and supported me through out the whole of this work - knowing when to push and when to let up.
+I offer special thanks to those who supported me in the mechanics of producing this thesis.
+\supname, for reading and rereading drafts, editing and proofing, typing and helping me get ‘unstuck’ with this thesis on many occasions.
+And Braulio and Arnoldo for ‘rescuing’ me at those times when I was almost defeated by the laboratory equipment.
+
+\end{acknowledgements}
 
@@
 %----------------------------------------------------------------------------------------
-%	ACKNOWLEDGEMENTS
-%----------------------------------------------------------------------------------------
-
-\begin{acknowledgements}
-\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
-There are a number of people without whom this thesis might not have been written,
-and to whom I am greatly indebted.\\
-
-% To my mother, Helena, who continues to learn, grow and develop and who has been a source of encouragement and inspiration to me throughout my life, a very special thank you for providing a ‘writing space’ and for nurturing me through the months of writing.
-And also for the myriad of ways in which, throughout my life, you have actively supported me in my determination to find and realise my potential, and to make this contribution to our world.\\
-
-% To my mother-in-law, Maryam, known only briefly but loved and missed, who represented to me ‘living proof’ of Black women’s ability to redefine and recreate our lives despite, and maybe even because of, the tremendously constraining, oppressive and repressive situations in which we often exist.\\
-
-% To my dear husband, Bala who remains willing to engage with the struggle, and ensuing discomfort, of having a partner who refuses to accept the given role of the "Black woman" and is actively engaged in redefining and redesigning that role.
-A very special thank you for your practical and emotional support as I added the roles of wife and then mother, to the competing demands of business, work, study and personal development.\\
-
-% Thanks to dear Kamal and Azaria, for being so supportive - even when being ‘without Mum’ was hard, and for your help with the bibliography and diagrams.
-This work is for, and because of you and all the generations to come.
-It is dedicated to all our journeys in learning to thrive.\\
-
-% It is also dedicated to Josephine - friend, ‘sister’, colleague, ‘co- traveller’ and researcher - who knowingly and unknowingly- led me to an understanding of some of the more subtle challenges to our ability to thrive.
-If our attempts to claim our right to speak our truth, and to unravel and follow the threads through which our oppression is maintained, and are instrumental in helping one other Black woman from ‘going over the edge’ - in which sight we continuously live our lives - perhaps, it might be seen that your invaluable contribution to the attainment of many of the insights gained was worth it.
-It is also written in honour of all our my grandmothers, and their mothers, and grandmothers, and to all our and mothers and grandmothers, who though not marked by history struggled so heroically to resist the definitions attributed to them by the dominant system and communicate messages of hope and expectation.
-I am also very grateful to Maya Angelou, for the inspiration she has been to methrough her writings, poetry readings and as a living representation of a woman thriving.
-Thanks to Mary Washington, Alice Walker, Jackie Kay, Buchi Emecheta, Toni Cade, Lauretta Ngobo, bell hooks, and other Black women writers of the 1980’s, who in telling stories for and about us validated me and my experiences in ways I cannot begin to explain here.\\
-
-% Loving thanks to my friends and learning partners, Agnes, Susan, Ulana and Namonya, who played such important roles along the journey, as we mutually engaged in making sense of the various challenges we faced and in providing encouragement to each other at those times when it seemed impossible to continue.
-
-I offer my gratitude and appreciation to my supervisors, \supname and \cosupname, for the deft ways in which you fondly challenged and supported me through out the whole of this work - knowing when to push and when to let up.
-I offer special thanks to those who supported me in the mechanics of producing this thesis.
-\supname, for reading and rereading drafts, editing and proofing, typing and helping me get ‘unstuck’ with this thesis on many occasions.
-And Braulio and Arnoldo for ‘rescuing’ me at those times when I was almost defeated by the laboratory equipment.
-
-\end{acknowledgements}
-
-%----------------------------------------------------------------------------------------
 %	LIST OF CONTENTS/FIGURES/TABLES PAGES
@@
 
+\listoffigures % Prints the list of figures
+\addchaptertocentry{\listfigurename} % Add to the table of contents
+
+\listoftables % Prints the list of tables
+\addchaptertocentry{\listtablename} % Add to the table of contents
+
 \tableofcontents % Prints the main table of contents
 
-\listoffigures % Prints the list of figures
+%----------------------------------------------------------------------------------------
+%	THESIS CONTENT - CHAPTERS
+%----------------------------------------------------------------------------------------
 
-\listoftables % Prints the list of tables
+\mainmatter % Begin numeric (1,2,3...) page numbering
+
+\pagestyle{thesis} % Return the page headers back to the "thesis" style
+
+% Include the chapters of the thesis as separate files from the Chapters folder
+% Uncomment the lines as you write the chapters
+
+\setlength{\parskip}{1.5em} % Paragraph spacing
+%\RaggedRight
+{\fontsize{12}{15} \selectfont
+
+\include{./Chapters/1}
+\include{./Chapters/2}
+\include{./Chapters/3}
+\include{./Chapters/4}
+\include{./Chapters/5}
+
+}
+
+%\include{Chapters/__IntroToLaTeX}
+
+\appendix % Cue to tell LaTeX that the following "chapters" are Appendices
+
+% Include the appendices of the thesis as separate files from the Appendices folder
+% Uncomment the lines as you write the Appendices
 
@@
 %----------------------------------------------------------------------------------------
-%	THESIS CONTENT - CHAPTERS
+%	THESIS CONTENT - APPENDICES
 %----------------------------------------------------------------------------------------
 
-\mainmatter % Begin numeric (1,2,3...) page numbering
-
-\pagestyle{thesis} % Return the page headers back to the "thesis" style
-
-% Include the chapters of the thesis as separate files from the Chapters folder
-% Uncomment the lines as you write the chapters
-
-\setlength{\parskip}{1.5em} % Paragraph spacing
-%\RaggedRight
-{\fontsize{12}{15} \selectfont
-
-\include{./Chapters/1}
-\include{./Chapters/2}
-\include{./Chapters/3}
-\include{./Chapters/4}
-\include{./Chapters/5}
-
-}
-
-%\include{Chapters/__IntroToLaTeX}
+%\include{Appendices/AppendixA}
+%\include{Appendices/AppendixB}
+%\include{Appendices/AppendixC}
 
@@
 
-\printbibliography[title={References}]
+\addcontentsline{toc}{chapter}{Bibliography}
+\printbibliography[title={Bibliography}]
 
@@
 %----------------------------------------------------------------------------------------
-%	THESIS CONTENT - APPENDICES
+%	CURRICULUM VITAE
 %----------------------------------------------------------------------------------------
 
-\appendix % Cue to tell LaTeX that the following "chapters" are Appendices
-
-% Include the appendices of the thesis as separate files from the Appendices folder
-% Uncomment the lines as you write the Appendices
-
-%\include{Appendices/AppendixA}
-%\include{Appendices/AppendixB}
-%\include{Appendices/AppendixC}
+\newpage 
+\addcontentsline{toc}{chapter}{Curriculum Vitae}
+\includepdf[page=-,fitpaper=false,landscape=false]{./pdf/CV/CV}
 

### 2020-11-09 05_Thesis/THESIS_LaTeX/pdf/CV/CV.tex
thesis match the template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

\vfill

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Osamu}{Katagiri}{ \urlstyle{same}\href{https://www.katagiri-mx.com/}{katagiri-mx.com} | \href{https://www.linkedin.com/in/osamu-k-84b2b940}{linkedin}\\ \href{mailto:osamu.katagiri@exatec.tec.mx}{osamu.katagiri@exatec.tec.mx}
}

\vfill

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.34\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Tecnológico de Monterrey}
\descript{MSc in Nanotechnology}
\location{Jan 2019 - Dec 2020 | Estado de México, MX}
\sectionsep

\subsection{Tecnológico de Monterrey}
\descript{BS in Digital Systems and Robotics}
\location{Aug2012 - May 2016 | Querétaro, MX}
\location{Cum. GPA: 3.6 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/katagirimx}{\bf katagirimx} \\
LinkedIn:// \href{https://www.linkedin.com/in/osamu-k-84b2b940}{\bf Osamu Katagiri-Tanaka} \\
Personal Website:// \href{https://www.katagiri-mx.com/}{\bf katagiri-mx.com}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Thermodynamics of Materials \\
Nano-structured Materials \\
Plastics and Composites Engineering \\
{\footnotesize \textit{\textbf{Rheology \& Electrospinning}}} \\
\sectionsep

\subsection{Undergraduate}
Sensors \\
Control Engineering \\
Digital Systems \\
Computer Architecture \\
Embedded Systems \\
Web Application Design \\
Microcontrollers \\
Electric Circuits \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Python \textbullet{} Javascript \textbullet{} \LaTeX\ \\
\location{Over 2000 lines:}
C \textbullet{} C++ \textbullet{} ADA \textbullet{} Verilog \textbullet{} VHDL \\
\location{Over 1000 lines:}
Java \textbullet{} CSS \textbullet{} PHP \textbullet{} Assembly \\
\location{Familiar:}
Android \textbullet{} MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{GE Aviation}
\descript{| Embedded Software Eng. }
\location{Jun 2018 - Dec 2019 | Querétaro, MX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item At General Electric's Business \& General Aviation Power Software team, I develop and test critical software for Aviation Power products. I have high responsibility in the development and in the documentation of the features and interactions with other systems.
\end{tightemize}
\sectionsep

\runsubsection{GE Aviation}
\descript{| SW Edison Engineering Development Program }
\location{June 2016 – May 2018 | Querétaro, MX}
\begin{tightemize}
\item EEDP is an intensive program for people who have a passion for technology, a drive for technical excellence, and share in GE's core values. It is designed to accelerate participants' professional development through intense technical training.
\end{tightemize}
\sectionsep

\runsubsection{GE Power}
\descript{| Software EID Intern }
\location{May 2015 – May 2016 | Querétaro, MX}
\begin{tightemize}
\item Support and improve engineering projects and activities.
\item Worked on the analysis and optimization of +20 wind turbines for every GE wind farm worldwide.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Macrophotoscience Reseach Group}
\descript{| MSc Student}
\location{Jan 2019 – Dec 2020 | Nuevo León, MX}
Worked with \textbf{\href{https://orcid.org/0000-0003-0455-5401}{Phd. Alan Aguirre}} and \textbf{\href{https://orcid.org/0000-0001-5325-0079}{Phd. Dora Medina}} to determine the electro-spunability of various polymer solutions for the fabrication of carbon nano-wires.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
May 2018	& top 4\%                    & Software EEDP graduate at GE Aviation\\
Aug 2015	& 1\textsuperscript{st}/1000 & GE 9th Lean Challenge\\
Nov 2014	& 1\textsuperscript{st}/50   & GEIQ’s Robotics Project\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
%\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{minipage}

\vfill

\end{document}  \documentclass[]{article}

### 2020-11-10 05_Thesis/THESIS_LaTeX/Chapters/1.tex
thesis match the template
references fix
thesis intro in progress

@@
 \decoRule
-\caption[Fabrication Process]{Fabrication process and characterization techniques of conductive carbon nano-wires to achieve through the dissertation.}
+\caption[Fabrication Process of Carbon Nano-wires]{Fabrication process and characterization techniques of conductive carbon nano-wires to achieve through the dissertation.}
 \label{fig:fabricationFlowChart}
@@
 \decoRule
-\caption[CBN Fingerprint]{Molecular to mesoscale structural features of synthetic polymers influence the emergence of specific microstructural features in polymer-derived carbon materials after pyrolysis.}
+\caption[Fingerprint of Carbon-based Nano-materials]{Molecular to mesoscale structural features of synthetic polymers influence the emergence of specific microstructural features in polymer-derived carbon materials after pyrolysis.}
 \label{fig:CBNfingerprint}
@@
 The interminable collection of possible CBN fingerprints range from soft, conductive lubricants to very hard, low conductivity solids; and from black colour, bulks to transparent, disordered thin films.
-\cite{McCreery2008} Figure \ref{fig:carbonAllotropes} shows the existence of different types of allotrope as carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, assembling different types of allotropes.
+\cite{McCreery2008} Figures \ref{fig:carbonAllotropes} and \ref{fig:carbonAllotropesDiagram} shows the existence of different types of allotrope as carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, assembling different types of allotropes.
 
@@
 \decoRule
-\caption[Carbon Allotropes]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
+\caption[Carbon sp-hybrid Nano-materials]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
 \label{fig:carbonAllotropes}
 \end{figure}
+
+\begin{figure}[th]
+\centering
+\includegraphics[scale=0.80]{./Figures/carbonAllotropesHybridization.png}
+\decoRule
+\caption[Ternary Diagram of Carbon Allotropes based on sp Content]{Ternary phase diagram of amorphous carbon regions based on hybridization degree.
+Adapted from \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015}.}
+\label{fig:carbonAllotropesDiagram}
+\end{figure}
+
+In terms of porosity, CBNs exhibit different properties according to the degree of 'open' and 'closed' pores.
+A 'closed pore' is a void or empty space in solid materials where a discontinuity is present within the array of atoms and molecules.
+On the other hand, an 'open pore' refers to a void which is connected to the outer surface of the solid, in other words a 'open pore' is a 'closed pore' with an opening to the external surface.
+\cite{Marsh1989} Figure \ref{fig:carbonAllotropesPorosityNOrder} shows a classification of carbon allotropes according to their porous content.
+
+\begin{figure}[th]
+\centering
+\includegraphics[scale=0.80]{./Figures/carbonAllotropesPorosityNOrder.png}
+\decoRule
+\caption[Ternary Diagram of Carbon Allotropes based on Porosity and Structural Order]{Ternary phase diagram of amorphous carbon regions based on structure order and porosity.
+Regions are colored by the degree of crystalline order within the carbon structure.
+White represents highly ordered structures, whereas white represents disordered structures.
+\cite{Marsh1989, Hugh1994}}
+\label{fig:carbonAllotropesPorosityNOrder}
+\end{figure}
+
+Thermal conductivity and electrical conductivity decrease with increasing porosity due to the reduced amount of material to conduct electrons and energy.
+Furthermore, porosity negatively affects the mechanical properties like strength and elastic modulus as it reduces the volume in which stresses are distributed.
+Moreover, stresses are concentrated at the pores which makes the material prone to mechanical failure.
+\cite{Marsh1989, Hugh1994}
 
@@
 Carbon FET devices have reported field-effect mobility one order of magnitude higher than that of silicon FETs.
-Other literature suggests CBNs to be favourable to detect a variety of gases and biomolecules.
-\cite{} As molecules are absorbed by the CBN, the carrier density and electrical resistivity of the carbon material changes.
-
-%% Zhu2010
-
-The properties of these CBNs make them widely used in many
-fields ranging from material science [13, McCreery2008], energy production and storage [14], environmental sciences [15,16], biology [17-19] and medicine [20,21].
-Table 1 summarizes the main properties of the most common CBNs [22-25]:
-
-Among the many carbon nanomaterials, CNTs and GR are currently the most popular representatives and have been extensively studied for their excellent mechanical strength, electrical and thermal conductivity and optical properties.
-The Young's modulus and tensile strength of CNTs and GR can reach 1 TPa and 130 GPa respectively [20,21].
-Carrier mobility of graphene is around 860 $cm^{2} V^{-1} s^{-1}$ (hole mobility of 844 $cm^{2} V^{-1} s^{-1}$ and carrier mobility of 866 $cm^{2} V^{-1} s^{-1}$), and the current density of metallic CNTs is orders of magnitude higher than those of metals such as copper [26,27].
-Thermal conductivities of CNTs and GR are about 3000e3500W/mK and 5000 W/mK respectively [28].
-The light absorption ratio of single-layer graphene is limited to 2.5\% [29].
-A large amount of the research efforts were focused on exploiting these properties for various applications including electronics, biological engineering, filtration, lightweight/strong composite materials, photovoltaic and energy storage [30-32].
-CNTs and GR are naturally good electrical conductors and their biocompatibility can be modulated [33], making them good candidates for improving electrodes for neural interfaces.
-Electrical recording or stimulation of nerve cells is widely employed in neural prostheses (for hearing, vision, and limb-movement recovery), in clinical therapies (treating Parkinson's disease, dystonia, and chronic pain), as well as in basic neuroscience studies.
-In all these applications, electrodes of various shapes and dimensions stimulate and/or record neuronal activity to directly modulate behavior or to interface machine.
-The performance of the electrodes can be significantly improved by implementing the device with nanomaterial-based coatings (such as CBNs), since their high surface area can drastically increase charge injection capacity and decrease the interfacial impedance with neurons [34].
-
-%%%
-It is well known that the morphology of the electroactive material play an important role in electrochemical systems, once the intimate contact at the electrode/electrolyte interface is crucial to guarantee the charge transfer process [11,12].
-In this sense, nanostructured electroactive materials such as nanorods [13], nanofiber [14], nanoflowers [15,16], nanowires [17,18], among others [19,20], are being widely used to obtain improved electrochemical properties such as higher charge/discharge rate and improved task to accommodate stress due to volume changes occasioned by intercalation process.
+Other literature suggests CBNs to be favorable to detect a variety of gases and biomolecules.
+\cite{Schedin2007, Ohno2009} As molecules are absorbed by the CBN, the carrier density and electrical resistivity of the carbon material changes.
+Moreover, CBNs have showed good performace in applications in energy (prevent wastage of energy), water (purification) and diagnostics (lab-on-chip systems and nano-sensors).
+\cite{Cao2011, Khanna2016} As mentioned above, the morphology of CBNs has an impact on the electrochemical and mechanical properties.
+\cite{Marsh1989, Hugh1994, Guo2018} In this regard, carbon nano-structures, such as nano-wires \cite{Kundu2019, Bencheikh2019, Bencheikh2019}, have been fabricated to achieve improved electrochemical characteristics.
 

### 2020-11-10 05_Thesis/THESIS_LaTeX/main.tex
thesis intro in progress

@@
 
-%%----------------------------------------------------------------------------------------
-%%	QUOTATION PAGE
-%%----------------------------------------------------------------------------------------
-%
-%\vspace*{0.2\textheight}
-%
-%\begin{center}
+%----------------------------------------------------------------------------------------
+%	QUOTATION PAGE
+%----------------------------------------------------------------------------------------
+
+\vspace*{\fill}
+
+\begin{center}
 %\includegraphics[width=0.60\textwidth]{./Figures/quote.png}
-%
-%\noindent\enquote{\itshape No great discovery was ever made without a bold guess.}\bigbreak
-%\end{center}
-%
-%\begin{flushright}
-%\textbf{Newton, Sir Isaac} \linebreak
-%In W.I.B. Beveridge \linebreak
-%\emph{The Art of Scientific Investigation} \linebreak
-%Scientist (p. 145)
-%\end{flushright}
+
+\noindent\enquote{\itshape Carbon is a simple element but ............... \\
+\medskip 
+One branch of chemistry is devoted to its compounds! \\
+\medskip 
+One branch of science is devoted to the many forms of the element as a solid material. \\
+\medskip 
+The best of this is that although most carbon materials are grey or black to the naked eye and the uninitiated, a closer examination reveals the form, beauty and even color of carbon science.}\bigbreak
+\end{center}
+
+\begin{flushright}
+\textbf{Marsh, Harry} \linebreak
+\emph{Universitat d'Alacant, Alicante, Spain} \linebreak
+\href{https://www.scopus.com/authid/detail.uri?authorId=7201585695}{scopus.com}
+\end{flushright}
+
+\vspace*{\fill}
 

### 2020-11-10 05_Thesis/THESIS_LaTeX/Chapters/1.tex
min progress

@@
 \centering
-\includegraphics[scale=0.80]{./Figures/carbonAllotropesHybridization.png}
+\includegraphics[scale=0.70]{./Figures/carbonAllotropesHybridization.png}
 \decoRule
 \caption[Ternary Diagram of Carbon Allotropes based on sp Content]{Ternary phase diagram of amorphous carbon regions based on hybridization degree.
-Adapted from \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015}.}
+Adapted from \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015, Vajtai2013}.}
 \label{fig:carbonAllotropesDiagram}
@@
 \centering
-\includegraphics[scale=0.80]{./Figures/carbonAllotropesPorosityNOrder.png}
+\includegraphics[scale=0.70]{./Figures/carbonAllotropesPorosityNOrder.png}
 \decoRule
@@
 Carbon FET devices have reported field-effect mobility one order of magnitude higher than that of silicon FETs.
-Other literature suggests CBNs to be favorable to detect a variety of gases and biomolecules.
+Other literature suggests CBNs to be favorable to detect a variety of gases and bio-molecules.
 \cite{Schedin2007, Ohno2009} As molecules are absorbed by the CBN, the carrier density and electrical resistivity of the carbon material changes.
-Moreover, CBNs have showed good performace in applications in energy (prevent wastage of energy), water (purification) and diagnostics (lab-on-chip systems and nano-sensors).
+Moreover, CBNs have showed good performance in applications in energy (prevent wastage of energy), water (purification) and diagnostics (lab-on-chip systems and nano-sensors).
 \cite{Cao2011, Khanna2016} As mentioned above, the morphology of CBNs has an impact on the electrochemical and mechanical properties.
@@
 
-Carbon nanofibers (CNFs) have been classified as linear, sp2-based discontinuous filaments, where the aspect ratio is greater than 100 [207].
-Depending on the angle of the graphene layers that compose the filament, CNFs have even been classified as stacked (graphene layers stacked perpendicularly to the fiber axis) or herringbone/cupstacked (graphene layers stacked at an angle between parallel and perpendicular to the fiber axis) [208].
+As depicted in Figure \ref{fig:carbonAllotropesDiagram}, carbon nano-fibers (CNFs) have been classified as linear, sp2-based structures.
+\cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015, Vajtai2013} Nano-fibers own good electrical, optical and mechanical characteristics, however those properties are highly dependent on the morphology of the fibers.
+\cite{Dresselhaus2007}
 

### 2020-11-15 05_Thesis/THESIS_LaTeX/Chapters/1.tex
min progress

@@
 \centering
-\includegraphics[scale=0.40]{./Figures/carbonAllotropes.png}
+\includegraphics[scale=0.30]{./Figures/carbonAllotropes.png}
 \decoRule
@@
 \centering
-\includegraphics[scale=0.70]{./Figures/carbonAllotropesHybridization.png}
+\includegraphics[scale=0.65]{./Figures/carbonAllotropesHybridization.png}
 \decoRule
@@
 \centering
-\includegraphics[scale=0.70]{./Figures/carbonAllotropesPorosityNOrder.png}
+\includegraphics[scale=0.65]{./Figures/carbonAllotropesPorosityNOrder.png}
 \decoRule
@@
 \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015, Vajtai2013} Nano-fibers own good electrical, optical and mechanical characteristics, however those properties are highly dependent on the morphology of the fibers.
+\cite{Dresselhaus2007} The material properties of 1D nano-structures depend on fiber diameter, porosity, crystallization degree and crystallization orientation.
+Consequently, the fabrication parameters and environment conditions have an impact on the reproducibility of high quality fibers.
 \cite{Dresselhaus2007}
 
-%%%
-Nanowires are one-dimensional, anisotropic structures, small in diameter, and large in surface-to-volume ratio.
-These characteristics confer to the nanowires special physical properties than those of traditional scale and dimensionality materials, such as electrical, optical thermal and mechanical properties.
-However, this make this kind of materials to have properties deeply dependent on their surface condition and geometrical configuration [21].
-The transport properties in the 1D nanostructures like the nanowires are affected by wire diameter, surface conditions, crystal quality, crystallographic orientation and material composition, thus the synthesis conditions are a crucial factor to obtain reproducible and high-quality nanowires for different application [21].
-
-The typical lengths and diameters of carbon nanofibers are in the ranges of 5e100mm and 5e500 nm, respectively [209].
-CNTs and GR are the most studied carbon nanomaterials for neural interfaces, however CNFs are also attractive in bio-interfacing developments due to their chemical and physical properties [1]: CNFs are chemically stable and inert in physiological environment [2], they are biocompatible for long-term implantation due to CNFs solid carbon skeleton [3], they are electrically robust and conductive for signal detection [4], they can be manufactured into 3D structures allowing intra-tissue and intracellular penetration [210], CNFs possess high surface-to-volume ratio, which greatly reduces electrical impedance, and [5] ultra-micro scale sizes that provide high spatial resolution.
-CNFs have been applied as promising materials in many fields, such as energy conversion and storage, reinforcement of composites and self-sensing devices.
-
-In addition, CNF based materials have been developed as electroconductive scaffolds for neural tissues to facilitate communication through neural interfaces.
-Electrical fields are able to enhance and direct nerve growth [211], therefore electroconductive scaffolds have been applied to enhance the nerve regeneration process, not only providing physical support for cell growth but also delivering the functional stimulus.
-CNFs may represent novel, versatile neural interfaces, being capable of dual-mode operation by detecting electrophysiological and neurochemical signals, not only at the extracellular level with high spatial resolution, but also at the intracellular level by penetrating into single neurons [9].
-
-Despite the longstanding experience on these nanomaterials and the deep knowledge of the CNFs-neuron interface in vitro, in vivo experiments on their possible application for the treatment of brain and spinal cord injuries or diseases are still limited to few examples [53,212,213].
-In the first report CNFs impregnated with subventricular stem cells were employed to promote neuroregeneration after experimental stroke [53].
-The animals receiving the CNF-based treatment show reduction of the infarcted volume as well as recovery ofmotor and somatosensory activity.
-These data indicate that CNFs are optimal support material for neuronal tissue regeneration [53].
-
-Recently, Guo and collaborators [104] developed a polymer-based neural probe with CNFs composites as recording electrodes via the thermal drawing process [213].
-They demonstrated that in situ CNFs alignment was achieved during the thermal drawing, which contributes to a drastic improvement of electrical conductivity by 2 orders of magnitude compared to a conventional polymer electrode.
-The resulting neural probe has a miniature footprint, with a recording site reduced in size to match single neuron, yet maintaining impedance value able to capture neural signals.
-In chronic settings, long-term reliable electrophysiological recordings with single-spike resolution and minimal tissue response over extended period of implantation in wild-type mice were shown [213].
-
-%%%
-Nanostructured materials are particularly good for supercapacitor applications, providing high surface area, which leads to a high specific capacitance [22].
-Compared to 3D and 2D materials, 1D nanostructures have smaller dimension and higher aspect ratio, improving the transport of electrical carriers in one controllable direction and also can be exploited as elements in different kinds of nanodevices [23].
-In this way, nanowires have been satisfactorily used in supercapacitor electrodes due to their reduced ion diffusion path in comparison with 2D and 3D nanostructures, leading in higher charge/discharge rates [22,24].
-
-%%%
-Amongst the innumerous materials used to obtain 1D nanostructures, such as, carbon, silicon, transition metal oxides, the 1D nanostructured conductive polymers are a important group to fabricate energy storage devices, due their attractive characteristic, such as, mechanical properties, electrical conductivity, low cost, easy processing, high surface area and unique electroactive behavior, including high voltage window and high-doping rate during charge-discharge process [25].
-During the charge/discharge process in the conducting polymer occur the insertion/desertion ions from the electrolyte in the polymer backbone that could result in swelling and shrinkage of the polymer chain, leading to mechanical degradation of the electrodes and fading the electrochemical performance [26].
-An alternative to diminishment this drawback of the conductive polymers is fabricate composites that could improve the stability and conductivity of the electrodes [27].
-
-%%%
-In this way, composites based on conducting polymers and carbon or metal oxides materials in a nanowire architecture are a good strategy to develop high-performance devices due to the combination of the electrochemical properties of the polymer and/or composites with the morphological advantages of the nanowires.
-These combination results in large interface between electrode/electrolyte, effective electronic transport pathway, short ion diffusion distance and easy relaxation strain, which could improve both capacity/capacitance and rate performance of battery and supercapacitors devices, respectively [28].
-Furthermore, the mechanical properties of nanowires allow the development of flexible devices, that require materials with versatile functionalities including high flexibility and foldability without losing its high power and energy density and long lifetime [29].
+Carbon nano-fibers (CNF) have diameters of several micrometers and are different from carbon nano-tubes (CNT). \cite{Weil1992, Huang2009, chung2012carbon, Subramoney1997, Dresselhaus2000}
 

### 2020-11-16 05_Thesis/THESIS_LaTeX/Chapters/1.tex
chapter 1 done?

@@
 \centering
-\includegraphics[scale=0.40]{./Figures/CBNfingerprint.png}
+\includegraphics[scale=0.37]{./Figures/CBNfingerprint.png}
 \decoRule
-\caption[Fingerprint of Carbon-based Nano-materials]{Molecular to mesoscale structural features of synthetic polymers influence the emergence of specific microstructural features in polymer-derived carbon materials after pyrolysis.}
+\caption[Fingerprint of Carbon-based Nano-materials]{Molecular to meso-scale structural features of synthetic polymers influence the emergence of specific micro-structural features in polymer-derived carbon materials after pyrolysis.}
 \label{fig:CBNfingerprint}
@@
 
-\subsection{Carbon nanowires}
+\subsection{Carbon Nano-wires}
 
@@
 Consequently, the fabrication parameters and environment conditions have an impact on the reproducibility of high quality fibers.
-\cite{Dresselhaus2007}
+\cite{Dresselhaus2007} Carbon nano-fibers (CNFs) have diameters of several micrometers (Figure \ref{fig:diameterComparisonOfCarbonFibers}) and are different from carbon nano-tubes (CNT).
+\cite{Weil1992, Huang2009, chung2012carbon, Subramoney1997, Dresselhaus2000} Unlike carbon nano-tubes with hollow cores, carbon nano-fibers can be represented as stacked layers along the thread length.
+\cite{Dresselhaus2000, Rodriguez1993, Yoon2004} The stacked geometry of carbon nano-fibers results in unique electrical, chemical and mechanical properties.
+\cite{Liu2009, Endo2003, Yokozeki2009} Unlike CNFs, carbon nano-tubes inherent problems such as high cost and low effective surface area, which limit their practical use.
+\cite{Vajtai2013}
 
-Carbon nano-fibers (CNF) have diameters of several micrometers and are different from carbon nano-tubes (CNT). \cite{Weil1992, Huang2009, chung2012carbon, Subramoney1997, Dresselhaus2000}
+\begin{figure}[th]
+\centering
+\includegraphics[scale=0.65]{./Figures/carbonFiberDiameterComparison.png}
+\decoRule
+\caption[Diameter comparison of various types of fibrous carbon materials]{Various types of fibrous carbon materials bear different characteristics according to their molecular structure.
+Adapted from \cite{Vajtai2013}}
+\label{fig:diameterComparisonOfCarbonFibers}
+\end{figure}
 
-\subsection{Nanowires synthesis}
+sp2 carbon nano-wires have been used for the improvement of power density and specific energy in lithium-ion batteries.
+\cite{Frackowiak2002, Endo2000, Winter1998} Authors posit that the performance and capacity of Li-ion batteries depend on the CNF structure and texture.
+Through the right combination of electrospinning and carbonization parameters, electrically conductive, mechanically tough and with thin diameter fibers have been achieved by Yoon et al.
+\cite{Yoon2004}.
+Yoon reported 431 mili-ampere-hour per gram batteries with vitreous carbon nanofibers.
+Yoon states that the battery capacity highly depends on the pyrolysis process parameters as the morphology of the fiber develops pores and hence different surface properties.
+CNFs supercapacitors have been investigated as energy storage devices due to their high power bearability and long lifecycles.
+\cite{Endo2001, Frackowiak2001, Pandolfo2006, Conway1999} The studies' authors posit that carbon nano-fibers can be implemented as high-power supercapacitors due to their large surface area and high electrical conductivity.
 
-%%%
-Numerous methods to prepare nanowires, which include template-assisted synthesis [30], vapor–liquid-solid (VLS) [31], electrodeposition [32], electrospinning [33], hydrothermal [34], also hierarchical arrangement techniques [35–37] to organize the nanowires have been studies in the last ten years.
-Nanowires based on organic, inorganic or hybrid materials have been applied in order to get single or composites nanomaterials for innumerous purposes, such as chemical and biochemical sensing devices, thermoelectric, optical, magnetic and electrical application.
-In this section, we are focusing on the synthesis of conducting polymer and composites to develop materials in nanowires architectures.
+On the other hand, the low reactivity and unique morphology of CNFs make them promising catalyst supports for metal nano-particles.
+\cite{Choi2002, Li2002, Planeix1994} It is well known that the morphology and nano-structure of the supporting material are the main factors that prevent agglomerations of nano-particles.
+\cite{RomanMartinez1995, Serp2008} Moreover, in bone tissue scaffold applications, collagen is the most popular scaffold.
+However, collagen scaffolds bring xenogenicity issues which leads to disease transfer or immunogenic reactions, besides its inhability to preserve its shape once placed in the body.
+\cite{Bach1998, Butler1998, Delustro1990, Chachques2008, Atala2006, Glowacki2008, Valarmathi2008, Faraj2007} Currently, carbon fibers have been studied for bone tissue scaffold, however early attempts yield too thick fibers for cell cultivation and tissue regeneration.
+\cite{Visuri1991, Parsons1989} As depicted in previous research of CNFs for different applications, fiber morphology seems to have a significant impact on their performance.
 
-\subsubsection{Synthesis of conducting polymer nanowires}
-
-\subsection{\emph{conclude that NFES is the way to go}}
+Typically, carbon nano-fibers (CNFs) are synthesized by a combination of a patterning process and a pyrolysis process.
+CNFs fabricated by electrospinning of polymer solutions with electrostatic forces.
+Electrospun CNFs have characteristics such as high surface area, thin morphology with nano-scale diameters.
+The properties of electrospun fibers allow CNFs to be implemented in nano-sensing devices, energy storage applications, and tissue scafflods.
+\cite{Khanna2016, Ramakrishna2005, Reneker2000, Norris2000, Vozzi2002, Kim2003, Dersch2005} Several patterning techniques have been attempted to achieve the desired fiber morphology.
+In addition to electrospinning, CNFs have been also fabricated by two-photon polymerization (TPP) and photo-lithography techniques.
+\cite{CardenasBenitez2019} Cardenas et al.
+implemented TPP and conventional UV lithography to study the fabrication of CNFs within carbon micro-electromechanical systems.
 
@@
 %Porqué es importante que sea puro carbono
+
+The role of carbon nano-fibers in nano-sensor devices play an important role, as portable instruments require light-weight and small-sized components.
+\cite{Khanna2016} Table \ref{tab:advantagesOfNanosensors} lists some advantages of nano-sensors that can be accomplished by the fabrication of CNFs via near-field electrospinning and a thermal treatment in an inert environment.
+
+\begin{table}[ht]
+\centering
+\caption[Advantages of Nano-sensors]{Advantages of Nano-sensors. Adapted from \cite{Khanna2016}}
+\begin{tabularx}{\textwidth}{lX}
+\hline
+\textbf{Advantage} & \textbf{Description} \\
+\hline
+High sensitivity & More accuracy, single molecule detection \\
+Small size & Light-weight, portability, low-power consumption, small sample size, reduced sample preparation, and ease of use \\
+Low response time & High-frequency, real time analysis \\
+Low cost & Disposable devices \\
+\hline
+\end{tabularx}
+\label{tab:advantagesOfNanosensors}
+\end{table}
+
+Sensors of small size require less time to output a stable signal as signals require less time to travel shorter lengths, hence signal noise is also reduced.
+Nano-sized sensors allow data collection and measurements to be performed in real time at faster speeds.
+\cite{Khanna2016} The nano-scale also allows sensors to increase the active surface area, enabling the absorption and detection of analytes in low concentrations.
+\cite{Khanna2016} The integration of small-sized sensing devices lean to lower fabrication costs as large-scale production and reproducible fabrication can be achieved when producing nanosensors.
+\cite{Khanna2016} Moreover, conventional sensors are bulky and require higher amounts of power to operate.
+In gas sensing, neither a large sensing surface or a large sample is required to get a readable output signal from the sensor.
+Power consumption can be saved by reducing the thermal mass of the sensor.
+\cite{Khanna2016} Furthermore, if several gases are to be detected, an array of several gas sensors are to be assembled into an array.
+A multi-gas sensor array can increase the size and cost, whereas an array of gas nano-sensors (each functionalized to detect a specific analyte) can be implemented into a single device.
+\cite{Khanna2016} Nano-sensors can be classified by the kind of energy or physycal phenomena that is detected, as depicted in Table \ref{tab:classificationOfNanosensors} for instance: biological, mechanical, thermal, chemical, and optical sensors.
+\cite{Khanna2016, BaudritJ2017}
+
+\begin{figure}[th]
+\centering
+\includegraphics[scale=0.50]{./Figures/typesOfNanoSensors.png}
+\decoRule
+\caption[Types of Nano-sensors]{Diagram examples of carbon-based nano-sensors. Adapted from \cite{BaudritJ2017}}
+\label{fig:diameterComparisonOfCarbonFibers}
+\end{figure}
+
+\begin{table}[ht]
+\centering
+\caption[Classification of Nano-sensors]{Classification of Nano-sensors. Adapted from \cite{Khanna2016}}
+\begin{tabularx}{\textwidth}{lX}
+\hline
+\textbf{Classification} & \textbf{Phenomena / Energy} \\
+\hline
+Mechanical & Position, acceleration, stress, strain, force, pressure, mass, density, viscosity, moment, torque \\
+Acoustic & Wave amplitude, phase, polarization, velocity \\
+Optical & Absorbance, reflectance, fluorescence, luminescence, refractive index, light scattering \\
+Thermal & Temperature, flux, thermal conductivity, specific heat \\
+Electrical & Charge, current, potential, dielectric constant, conductivity \\
+Magnetic & Magnetic field, flux, permeability \\
+Chemical & Components (identities, concentrations, states) \\
+Biological & Biomass (identities, concentrations, states) \\
+\hline
+\end{tabularx}
+\label{tab:classificationOfNanosensors}
+\end{table}
 
@@
 \subsection{General objective}
-Study the practice and feasibility of a new fabrication process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner; by the integration of mechano-electrospinning technique.
+Study the practice and feasibility of a new fabrication process to achieve mass scale manufacturing of polymeric micro-wires in an inexpensive, continuous, simple and reproducible manner by the integration of near-field electromechanical spinning (NFEMS) and forward-thinking on pyrolysis processes to convert polymeric micro-wires into carbon nano-wires.
 

### 2020-11-16 05_Thesis/THESIS_LaTeX/Chapters/2.tex
able to fit lin
chapter 2 in progress

--- 2020-05-28 myThesis/thesis_LaTeX/Chapters/3.tex
@@
-% Chapter Template
-
 \chapter{Near-Field Electrospinning as an Affordable Way to Gain Spatial Control} % Main chapter title
 
-\label{Chapter:3}
+\label{Chapter:2}
 
@@
 \section{Review of Polymer Solutions for NFES with Spatial Control}
+
+Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement.
+In the past years (2006-2020), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process.
+Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties.
+
+Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}.
+One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano fibers from a variety of polymers.
+The technique allows the production of thin continuous fibers with ease, with micro and sub-micrometer diameters, which is something difficult to achieve by other techniques.
+Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials.
+The produced fibers can be aligned or unaligned.
+Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques\unskip~\cite{527120:12073538}.
+On the other hand, the understanding of the electrospinning process has improved in the last years.
+
+Current literature dictates the typical spinning setup is comprised by three main components: a polymer reservoir, a fiber collector, and some way to dispense the fibers onto the collector.
+The spinning process is an electro-hydrodynamic (EHD) technique that yields continuous polymer fibers.
+Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively, seeFigure~\ref{f-02e0e3cf88d6}.
+
+\bgroup
+%\fixFloatSize{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}{\includegraphics[scale=0.65]{./images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}}{}
+\makeatother 
+\caption{{Electrohydro-dynamic techniques}}
+\label{f-02e0e3cf88d6}
+\end{figure}
+\egroup
+
+\subsection{Stretching forces}
+
+\subsubsection{Electric Field}Electrospinning (electrostatic fiber spinning) is a fiber fabrication approach that implements an electric field produce fibers by an electrical potential difference between the syringe needle and the collector.
+With the influence of high electric fields, the fibers are prone to brake into separate layers due to the whipping instabilities as the jet travels to the substrate.
+The instability can be mitigated by adding additional ring electrodes between the spinneret and the grounded collector.
+\unskip~\cite{527120:13915304}
+
+The typical electrospinning setup applies an electrostatic charge to the polymer fluid at the tip of the needle nozzle, which results in the formation of the Taylor cone \unskip~\cite{527120:13659828}, from which a single polymer jet is ejected to the grounded collector.
+From the Taylor cone, the supplied polymer jet (typically a polymer solution) accelerates and reduces in diameter.
+The fiber finally develops with the complete solvent evaporation.
+Electrospun fibers are prone to splitting with the increase in acceleration due to high applied voltages, where multiple fibers are yield in a process known as electrospraying \unskip~\cite{527120:13659925}.
+
+The electrospinning process starts with charging a polymer solution droplet.
+When a polymer solution is administrated with a syringe pump, solution droplets will fall under the influence of gravity.
+The solution dripping stops when the electric field is strong enough to break the solution's surface tension, causing the droplet to change shape forming a polymer solution jet\unskip~\cite{527120:12033655}.
+
+Shin et al.
+\unskip~\cite{527120:13659926} reported that the growth of the whipping instability is one important element within the electrospinning technique.
+As detailed in Shin's work, weak electric fields produce a single uniformly thinning jet, and strong electric fields the jet becomes unstable after traveling a short distance.
+
+\paragraph{High voltage power supply: DC \& AC - }Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction.
+Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow.
+Kessick et al.\unskip~\cite{527120:13444381} demonstrated the implementation of AC power supplies in the production of polymer fibers.
+
+The AC electrospinning setup is similar to that for the DC variant.
+AC electrospinning apparatus do not require a grounded collector as the current alternates.
+In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge.
+The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers\unskip~\cite{527120:16885570}.
+The optimal AC frequency depends on the materials used and is typically within  $50Hz $ and  $1kHz $\unskip~\cite{527120:13443405}.
+
+The AC technique has been studied for drug loaded related applications.
+Balogh et al.
+\unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques.
+Their work reports that AC and DC electrospinning can produce fibers with all three polymers, where the AC process allowed the implementation of faster flow rates than in the DC setup.
+The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $.
+
+\subsubsection{Centrifugal force}The spinning processes require the implementation of a force to break the polymer source into a polymer jet.
+Centrifugal spinning intends to produce fibers by the use of a rotating polymer source.
+The centrifugal force generated from typical rotatory speeds above $2000 rpm $, results in fiber formation.
+\unskip~\cite{527120:13535559,527120:13535561}.
+
+\bgroup
+%\fixFloatSize{./images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}{\includegraphics[scale=0.65]{./images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}}{}
+\makeatother 
+\caption{{Typical setup used in pressurized gyration processes}}
+\label{f-7cf6ac702e28}
+\end{figure}
+\egroup
+The centrifugal force technique has been applied to polymer solutions and melts.
+This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.
+Efforts in centrifugal spinning are focused on drug delivery applications.
+Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach.
+Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.
+
+On the other hand, PCL and PVP fibers were generated by Amalorpava et al.
+\unskip~\cite{527120:13536089}.
+Amalorpava achieved sub micron/size fiber diameters for drug release purposes and bacteria growth inhibition properties.
+Literature\unskip~\cite{527120:13536446} has shown that centrifugal approach has a simple setup that promises a large scale fabrication of fibers.
+
+In some cases the centrifugal force implementations and pressurized gyration can be combined with an electric field.
+The implementation of two stretching forces (centrifugal and electrical forces), can help solvent evaporation\unskip~\cite{527120:13536560}.
+Centrifugal electrospinning implements the same setup as the standard centrifugal spinning with the addition of a high voltage power supply between the rotating dispensing nozzle and the collector.
+The combined method has evidence to yield parallel fibers\unskip~\cite{527120:13536841,527120:13536900,527120:13537392,527120:13537393} at a higher rate \unskip~\cite{527120:13536841,527120:13536900} than the standard electrospinning approach.
+
+\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution.
+The setup used for blow spinning is similar to the one used in coaxial electrospinning, where the polymer precursor is dispensed at a controlled rate.
+Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}, see Figure~\ref{f-92361290d8c3}.
+
+\bgroup
+%\fixFloatSize{./images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}{\includegraphics[scale=0.65]{./images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}}{}
+\makeatother 
+\caption{{Dispensing nozzle used for solution blow spinning or melt blowing. \unskip~\protect\cite{527120:13538056}}}
+\label{f-92361290d8c3}
+\end{figure}
+\egroup
+Poly(lactic acid) (PLA) fibers have been produced by solution blow spinning.
+Oliveira et al.
+\unskip~\cite{527120:13539278} fabricated the fibers from $6 wt\% $ PLA solutions with progesterone for live stock reproductive cycle regulation applications.
+On the other hand, Souza et al.\unskip~\cite{527120:13538056} conducted a study to compare the standard electrospinning and the solution blow spinning techniques.
+Poly(3-hydroxybutyrate-co-3-hydroxyvalerate) were fabricated by both methods.
+The fibers produced by traditional electrospinning had thicker diameters and the size uniformity was higher in the fibers produced by solution blow spinning.
+The experimental setup requires a coaxial needle nozzle with a pressurized gas flow along with a potential difference between the dispensing needle and the grounded collector.
+
+\subsubsection{Mechanical force}
+\bgroup
+%\fixFloatSize{./images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}{\includegraphics[scale=0.35]{./images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}}{}
+\makeatother 
+\caption{{Typical mechanical fiber drawing process.
+First the needle makes contact with the substrate to break the polymer drop.
+Then the needle leaves the substrate and the collector moves to create and deposit the fiber.
+Once the fiber is written the needle makes contact witht the collector to fix the fiber deposition.}}
+\label{f-432d16f420fb}
+\end{figure*}
+\egroup
+Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette.
+\unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical applications.
+\unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers where the fiber is created by stretching the polymer precursor with a moving collector, as depicted in Figure~\ref{f-432d16f420fb}.
+Touch-spinning is another mechanical technique that comprises a moving stage with an embedded glass rod (Figure~\ref{f-f17259e76303}).
+Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers.
+The rotation stretches the fiber, causing the fiber to increase in length and decrease in diameter.
+The increase in length causes the fiber surface are to increase and therefore making the polymer solution solvent to volatilize, ending with a dry fiber within the collector.
+
+\bgroup
+%\fixFloatSize{./images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}{\includegraphics[scale=0.45]{./images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}}{}
+\makeatother 
+\caption{{Touch-spinning technique.
+First rod is attached to a rotating stage and a polymer solution droplet is administrated through a needle.
+Then the rotating rod 'touches' the polymer precursor.
+Finally, as the rod rotates, the polymer solution is stretched and creates a fiber between the rod and the needle.}}
+\label{f-f17259e76303}
+\end{figure*}
+\egroup
+The touch spinning technique implies that the fiber diameter can be controlled by the moving collector's speed and the polymer solution concentration.
+The main difference relays on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}
+
+\subsubsection{Microfluidic forces}The microfluidic spinning technique manipulates and controls the polymer solution in networks of micrometer channels.
+The channel network are typically embedded in a microfluidic chip, where the solution deposition rate is controlled by active components (pumps and valves) with a computer.
+Cheng et al.
+\unskip~\cite{527120:13656236} compared and combined the microfluidic spinning and electrospinning techniques.
+Heterogeneous materials and cell patterning within a single microfiber can be designed by the integration microfluidic channels.
+Therefore, microfluidic spinning is more suitable for cell encapsulation and tissues generation\unskip~\cite{527120:13656236}.
+
+On the other hand, Kang et al.
+\unskip~\cite{527120:13656548} managed to fabricate micro fibers by imitating the "silk spinning" process of spiders.
+Kang's micro fibers properties were modified using a microfluidic system with a programmable flow control (See Figure~\ref{f-c0beae2757bf}).
+The current microfluidic spinning approach is not scalable to a large fiber production, however it enables the fabrication of high-complex fibers that are not easily achieved by other methods.
+
+\bgroup
+%\fixFloatSize{./images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}{\includegraphics[scale=0.99]{./images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}}{}
+\makeatother 
+\caption{{Microfluidic device used by Kang et al.\unskip~\protect\cite{527120:13656548}}}
+\label{f-c0beae2757bf}
+\end{figure}
+\egroup
+Microfluidic techniques offer the possibility to embed several components into a single fiber, where each component can be released at different parts of the fiber.
+
+\subsection{Dispensing nozzle}Unlike traditional electrospinning, coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle, see Figure~\ref{f-4a5ffd16c3ab}\unskip~\cite{527120:13914792,527120:13914793}.
+The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers.
+Sun et al.
+\unskip~\cite{527120:13914312}.
+Addressed electrospinning setups, where both the core and shell are comprised by PEO (poly(ethylene oxide)) and for a PEO shell with a poly(dode-cylthiophene) core.
+Sun et al.
+state that co-electrospinning has the potential to extend the range of materials that can be used for electrospinning.
+The shell solution can be modified to make the core solution spunable.
+It was also discovered that non-spunable solutions can by implemented as shell solutions in conjunction with a spunable core solution.
+\unskip~\cite{527120:13914968}
+
+\bgroup
+%\fixFloatSize{./images/afe7da25-1366-4b1e-bf1a-0594eb2eaa88-uimg_nozzle.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/afe7da25-1366-4b1e-bf1a-0594eb2eaa88-uimg_nozzle.png}{\includegraphics[scale=0.80]{./images/afe7da25-1366-4b1e-bf1a-0594eb2eaa88-uimg_nozzle.png}}{}
+\makeatother 
+\caption{{Needle configurations in coaxial electrospinning. (a) the outer needle encasing the inner; (b) the inner needle protruding from the outer; (c) both needles inline with each other;}}
+\label{f-4a5ffd16c3ab}
+\end{figure}
+\egroup
+Some advantages that co-electrospinning setups can break the polymer drop surface tension, initiating the jet burst from the spinneret nozzle.
+On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles.
+\unskip~\cite{527120:13914748,527120:13914750}.
+As in conventional NFES, in co-electrospinning, the needle tip is connected to a high voltage power supply with a grounded collector.
+
+\subsection{Polymer Reservoir (Polymer Melt \& Polymer Solution)}Electrospinning processes can be classified on the polymer reservoir type.
+As Brown et al.
+\unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used).
+The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state.
+The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution.
+The apparatus used by Brown et al.
+\unskip~\cite{527120:13445499} is depicted in Figure~\ref{f-bfd139aecf8f}.
+
+\bgroup
+%\fixFloatSize{./images/9d06b4aa-134c-4fd6-bbf3-1ced4ac95046-uimg_metl_setup.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/9d06b4aa-134c-4fd6-bbf3-1ced4ac95046-uimg_metl_setup.png}{\includegraphics[scale=0.70]{./images/9d06b4aa-134c-4fd6-bbf3-1ced4ac95046-uimg_metl_setup.png}}{}
+\makeatother 
+\caption{{Typical Melt Electrospinning Setup}}
+\label{f-bfd139aecf8f}
+\end{figure}
+\egroup
+Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales.
+Furthermore, polymer melt reservoirs get rid of any solvent contamination.
+
+The first report of a melt electrospun drug delivery system came from Nagy et al.
+\unskip~\cite{527120:13445555}, who prepared fibers by melt electrospinning of Eudragit EPO with carvedilol.
+The drug and polymer were melted and mixed to form a homogeneous solid mixture prior to spinning.
+The melt-spun fibers reached diameters of 5{\textendash}30 $\mu m $, compared to 300{\textendash}1000 $nm $ diameters produced from solution-spun fibers\unskip~\cite{527120:13445555}.
+
+Balogh et al.'s work has been built on to blend plasticizes with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticizes Triacetin, Tween 80 and Polyethylene Glycol were investigated in order to reduce the melting point of the polymer-drug mixture.
+The temperature drop is desirable to minimize the occurring drug degradation.
+
+Lian and Meng\unskip~\cite{527120:13445754} performed a comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibers fabricated by the melt and solution electrospinning techniques.
+They arrived to the conclusion that melt spinning is preferable when the polymer presents a low solubility.
+On the other hand the melt fibers were produced in a slower release rate.
+Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning.
+In their effort, they achieved a precise deposition of PCL fibers with diameters of $817 \pm 165 nm $.
+
+In literature, melt electrospinning has less evidence than the solution approach.
+However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}.
+Currently, the melt electrospinning setup is harder to determine and the lack of research on this technique explains its unexplored potential.
+
+\subsection{Polymer Solution}In electrospinning, it is typically agreed that the diameter of the fibers increased with higher concentration due to greater viscosity which withstands stretching.
+In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}, seeFigure~\ref{f-d977f56a0782}.
+\begin{table}[!htbp]
+\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
+\label{tw-be3662f66502}
+\def\arraystretch{1}
+\ignorespaces 
+\centering 
+\begin{tabularx}{\textwidth}{ll}
+\hline Observation & Concentration Adjustment\\
+\hline 
+Dripping, no stream &
+  Increase\\
+Splitting small droplets &
+  Increase slightly\\
+Steady stream &
+  No concentration adjustment\\
+Splitting large globs &
+  Decrease slightly\\
+Nozzle clogging &
+  Decrease\\
+\hline 
+\end{tabularx}\par 
+\end{table}
+
+\subsubsection{Polymers}The polymer selection is in function on the intended application.
+For example, a fast dissolving hydrophilic polymer such as poly(ethylene oxide) (PEO) is used for fast drug delivery systems.
+Otherwise, slow dissolving polymers such as poly($\varepsilon $-caprolactone) (PCL) or poly(lactic-co-glycolic acid) (PLGA) are implemented.
+\unskip~\cite{527120:13082763}
+
+The polymer molecular weight along with the polymer concentration and solvent selection have a direct effect on the solution viscosity, conductivity and surface tension, hence the solution behavior in the electrospinning process.
+The spunable viscosity range varies with the polymer and solvent.
+
+Solutions with low viscosity are prone to insufficient polymer chain entanglements to produce fibers.\unskip~\cite{527120:13082763} On the other hand, if the solution is too viscous, then the surface tension cannot easily be overcome by the electric field.
+In both cases, the result can be droplets or particles forming rather than fibers as described inTable~\ref{tw-be3662f66502}.
+
+\subsubsection{Solvents}The solvent used must be capable of dissolving the polymer of interest at an appropriate concentration to form fibers, and must posses a suitable volatility.
+A low-volatility solvent like water may fail to evaporate completely over the distance between the spinneret and the collector.
+When the fibers form, they will hence contain residual water owing to this incomplete evaporation.
+The residue solvent will subsequently evaporate from the fibers upon storage, resulting in ribbon-like (flattened) fibers, wrinkles on the fiber surface or fused fibers.
+On the other hand, a high-volatility solvent may evaporate very quickly, leading to larger fiber diameters (less time for elongation before solidification) and clogging of the spinneret (due to drying of the liquid at the spinneret before jetting, or drying of the Taylor cone during jetting).
+Solvents commonly used for electrospinning include ethanol, chloroform, trichloroethane and hexafluoroisopropanol\unskip~\cite{527120:12073495,527120:16887323,527120:16887324}.
+
+Mixtures of miscible solvents can be used to ensure that sufficient polymer can be dissolved to give a solution of appropriate viscosity and volatility with suitable dielectric constant range to allow fiber formation.
+However, care must be taken because using a mixture of solvents with very different volatilities can result in porous fiber structures.
+As reported by Katsogiannis et al.
+for organic solvent mixtures with dimethyl sulfoxide (DMSO).\unskip~\cite{527120:13082766} DMSO evaporates much more slowly than the organic solvents used, which results in its incorporation into the fibers.
+The DMSO will eventually evaporate, yielding porous fibers.
+
+It is also important to take into account the surface tension of the solution.
+Solvents with very high surface tensions (e.g.
+water) can result in instability arising during the spinning process, and a broad range of fiber diameters in the products.
+If necessary, a surfactant can be added to reduce the surface tension, but this will be incorporated into the fibers produced.
+
+\section{Properties that Improve Accuracy of Nano-Fiber Deposition}
+Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
+This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
+Table S1 is a collection of the relevant NFES process parameters and achieved fiber morphology.
+
+Some differences have been discovered between LV-NFES and conventional NFES.
+Low voltage near field electrospinning produces thinner fibers with lower voltages; as shown inFigure~\ref{f-59ed68f95344}.
+Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching.
+Bisht et al.
+and Chang et al.
+\unskip~\cite{527120:11973130,527120:11974313} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
+
+Bisht and Chang's work \unskip~\cite{527120:11973130,527120:11974313} reports a controlled technique to fabricate polymeric nano fibers in a continuous manner, using a low voltage setup.
+Their purpose is to find a workaround to the drawbacks of traditional NFES by using a superelastic polymer precursor, which allow continuous patterning without breaking.
+In low voltage near-field electrospinning (LV NFES), a visco-elastic polymer is used to allow continuous spinning at about 200$V $.
+
+Kim et al.
+\unskip~\cite{527120:11974313} experimented with a NFES variation where the fiber deposition is guided by conductive rails, see Figure~\ref{f-927e96fb5537}.
+As stated by the authors, the induced electric field is enhanced by the conductive pattern, which allows the fibers to follow the desired deposition path.
+As the fibers are prone to follow the conductive pattern, additional fibers can be stacked on each other.
+The stacking process was successfully achieved in high electric field conditions at: 750$\mu m $ substrate to collector distance, and a 600 $\mu m $ needle to rail (offset) distance, see Figure~\ref{f-927e96fb5537}.
+
+\bgroup
+%\fixFloatSize{./images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}{\includegraphics[scale=0.70]{./images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}}{}
+\makeatother 
+\caption{{NFES setup for controlled fiber deposition on pre-patterned conductive electrodes. \unskip~\protect\cite{527120:11974313}}}
+\label{f-927e96fb5537}
+\end{figure*}
+\egroup
+Gupta et al.\unskip~\cite{527120:11974310} introduced a new technique to fabricate polymer scaffolds for tissue engineering applications and organ development.
+As described by Gupta et al.\unskip~\cite{527120:11974310}, the fiber deposition equipment is comprised by a stainless steel needle with a internal diameter of 750 $\mu m $ , connected to a high voltage power supply of up to 30 $k V $ with a deposition rate of about $\geq 1 \mu L min^{-1} $.
+The setup was embedded to a motorized collector capable of controlled programmable motions, see Figure~\ref{f-74de1f00848b}.
+The proposed technique was able to produce fibers of $150 \mu m $ in diameter with pre-designed patterns.
+
+\bgroup
+%\fixFloatSize{./images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}{\includegraphics[scale=0.60]{./images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}}{}
+\makeatother 
+\caption{{Schematic illustration of the electrohydrodynamic process. \unskip~\protect\cite{527120:11974310}}}
+\label{f-74de1f00848b}
+\end{figure}
+\egroup
+Wang, et al., Huang, et al., and Chen, et al.
+\unskip~\cite{527120:11974322,527120:11974323,527120:11974324} experimented with several multi-nozzle near-field electrospinning of aligned nano fibers.
+The multi nozzle NFES apparatus is similar to the one used in conventional NFES with some modifications to the needle nozzle, see Figure \ref{f-4a1a1f58a423}.
+The authors implemented similar NFES setups where the installed linear array of nozzles is supplied with a constant flow rate of solution.
+
+\bgroup
+%\fixFloatSize{./images/cd8e0617-d4d9-479b-a99b-a466cd21483c-uwang_01.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/cd8e0617-d4d9-479b-a99b-a466cd21483c-uwang_01.png}{\includegraphics[scale=0.70]{./images/cd8e0617-d4d9-479b-a99b-a466cd21483c-uwang_01.png}}{}
+\makeatother 
+\caption{{The geometry distribution of linear array multi-nozzle system \unskip~\protect\cite{527120:11974323}}}
+\label{f-4a1a1f58a423}
+\end{figure}
+\egroup
+The authors came to the conclusion that the distance between the deposited fibers increase with the increase of the needle-to-collector distance, as the influence of the applied voltage dissipates.
+
+Huang, et al.\unskip~\cite{527120:11974311} studied the mechanoelectrospinning (MES) technique for the fabrication of nano fibers.
+The MES technique tries to improve deposition accuracy by the introduction of a mechanical drawing force.
+The MES is predominantly controlled by the collector stage velocity, the nozzle-to-collector distance, and the applied voltage.
+The authors believe that MES can compete as a low-cost, high precision fabrication of electronics and enable the direct writing of structures for nano scale lithography.
+Figure~\ref{f-7587d8081ccc} shows the polymer jet behavior when a mechanical force is implemented within the NFES process.
+
+\bgroup
+%\fixFloatSize{./images/db7d3b35-fe08-422f-afe4-78e0133b489b-uhuang_00.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/db7d3b35-fe08-422f-afe4-78e0133b489b-uhuang_00.png}{\includegraphics[scale=0.90]{./images/db7d3b35-fe08-422f-afe4-78e0133b489b-uhuang_00.png}}{}
+\makeatother 
+\caption{{schematic diagram of leap direct-writing: the ink first accumulates at contact point and then gets stretched by mechanical drawing force.
+At a critical distance, the ink leaps to the next contact point, and gets stretched again \unskip~\protect\cite{527120:11974311}}}
+\label{f-7587d8081ccc}
+\end{figure}
+\egroup
+Micro and nano fibers have been written using AC pulse-modulated electrospinning by Bu et al.
+with polyehtylene terephthalate (PET) as substrate\unskip~\cite{527120:11974304}.
+The AC electrical field influences the electrospinning jet.
+The alternate current tends to decrease the repulsive electrical force allowing a stable straight jet between the dispensing nozzle and the insulating PET substrate.
+Bu et al.
+varied the stage velocity; faster stage velocities enable the deposition of straighter fibers\unskip~\cite{527120:11974304}.
+
+ A mechano-electrospinning technique was presented by Nagle et al.\unskip~\cite{527120:12033656}.
+With the implementation of a mechanical drawing force, a higher resolution nano fibrous pattern can be produced with lower voltages as the Taylor cone becomes more stable.
+Nagle et al.
+studied PEO fibers at different nozzle to collector distances.
+Evidence suggest that better patterning accuracy increases with increasing nozzle to collector distance as the solution is effectively dried\unskip~\cite{527120:12033656}.
+Near field mechano-electrospinning enables the collection of non woven fibers over large areas.
+
+\bgroup
+%\fixFloatSize{./images/43f61edd-73cd-4222-830e-3333f92934e9-uimg_nfesvariants.png}
+\begin{figure}[!htbp]
+\centering \makeatletter\IfFileExists{./images/43f61edd-73cd-4222-830e-3333f92934e9-uimg_nfesvariants.png}{\includegraphics[scale=0.65]{./images/43f61edd-73cd-4222-830e-3333f92934e9-uimg_nfesvariants.png}}{}
+\makeatother 
+\caption{{Near-Field ES Process Parameters}}
+\label{f-3629d3a3f9cf}
+\end{figure}
+\egroup
+To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
+Kameoka et al.\unskip~\cite{527120:12321556} demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip.
+
+Near-field electrospinning, has exhibited to be capable fabricate nano fibers and nano fiber patterns \unskip~\cite{527120:11974321}.
+Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner.
+Using a spinneret with a reservoir (e.g.
+syringe) of solution generally produces fibers with diameter of a few micrometers \unskip~\cite{527120:11974310,527120:11974326}, since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through.
+As shown inFigure~\ref{f-51afaccaf109}, the implementation of thicker needle nozzles translate into an increase of the resulted fiber diameter
+
+Coppola et al.\unskip~\cite{527120:11974307} have showed a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop, averting the issue of nozzle clogging.
+The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al.'s\unskip~\cite{527120:11974326} work.
+
+\subsection{Nozzle spinneret}The thinnest nozzles in literature so far are about $50 nm $ in diameter, by Chang et al.\unskip~\cite{527120:11974306} who used a  $100 \mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO).
+Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
+The nozzle most commonly comprises a simple narrow-bore, blunt-end metal needle.
+The diameter of the needle can vary, but most commonly researches work with internal diameters below 1 $mm $ .
+This translates to needles of gauge 18{\textendash}22.
+In general, this simple spinneret design can be used to achieve successful spinning.
+A blunt-end rather than a tapered-end for the needle exit is important as the size distribution of the products increase with an increase in needle tip angle.
+However, it should be noted that there will be some interactions between the solvent and polymer molecules in the solution and the metal surface of the spinneret.
+There will exist some attractive forces between the polar groups in the polymer and the electro-positive metal surface, which can act counter to the drawing force of the electric field and can pull the polymer solution back into the spinneret.
+It has been found that coating the spinneret exterior in a non-conductive and non-stick polymer such as Teflon or epoxy coating can reduce these interactions.\unskip~\cite{527120:13082768,527120:13082811} As a result, the electrical energy can be more efficiently used to elongate and narrow the polymer jet, and narrower fibers can be produced.
+In addition, strong attractive forces between the polymer jet and the metal spinneret can result in fibers becoming attracted to the needle, leading to lower yields and potentially to blocking of the exit orifice.
+
+\subsection{Applied Voltage}In recent literature, near field electrospinning has been studied to reduce the fiber diameter and to improve the fiber deposition accuracy.
+Madou et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} came to the conclusion higher voltages yield thicker micro-fibers with a loss in jet stability.
+This relationship between the applied voltage and resulting fiber diameter is influenced by other variables such as nozzle-to-substrate distance and solution deposition rate.
+For instance, if a high voltage is applied at a low deposition rate then electrospraying is achieved, meaning the formation of several non-continuous fibers.
+The applied voltage shall be sufficient to break the surface tension and initiate the jet, but low enough to avoid multiple jets at the nozzle tip.
+
+Madou et al.\unskip~\cite{527120:11973130} achieved the fabrication of thinner fibers with spatial control by reducing the applied voltage to 200-600 $V $  at a nozzle-to-substrate distance of 0.5-1 $mm $.
+The low voltage setting does not create enough charge to break the polymer solution surface tension to initiate the electrospinning process.
+
+Madou et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} initiated the electrospun fibers by mechanically pull the polymer solution at the nozzle tip using a micro-probe tip.
+Chang and coworkers reduced the applied voltage from 1.5 $kV $ to 600 $V $ with a nozzle-to-substrate distance of 500 $\mu m $ to yield a fiber diameter between 3 $\mu m $  and 50 $nm $ .
+With an applied voltage of 200 $V $ and a nozzle-to-substrate distance of 1 $mm $.
+
+In near-field electrospinning, the applied voltage has an impact on the produced fiber morphology.
+For instance, a voltage higher or lower to the optimum voltage will translate into an increase in fiber diameter.
+Song et al.\unskip~\cite{527120:11974320} demonstrated that a decrease in voltage from 400 to 500 $V $ can reduce the fiber diameter from 160 to about 60 $nm $with a nozzle-to-substrate distance of 20 $\mu m $.
+A workaround to break the polymer solution surface tension is to initialize the NFES process with a higher voltage and then lower the voltage once the jet is created.
+Huang et al.\unskip~\cite{527120:11974311} implemented the previous and yield ordered fibers with a distance between adjacent fibers of 50 $\mu m $.
+
+\subsection{Nozzle-to-substrate distance}
+\bgroup
+%\fixFloatSize{./images/4cc65220-1457-4d0d-bb04-9b1c8138aa96-uffes_vs_nfes.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/4cc65220-1457-4d0d-bb04-9b1c8138aa96-uffes_vs_nfes.png}{\includegraphics[scale=0.65]{./images/4cc65220-1457-4d0d-bb04-9b1c8138aa96-uffes_vs_nfes.png}}{}
+\makeatother 
+\caption{{a) Typical Far-field Electrospinning (FFES) Setup. b) Typical Near-field Electrospinning (NFES) Setup.}}
+\label{f-c34559531e3e}
+\end{figure*}
+\egroup
+Figure~\ref{f-c34559531e3e}.a, depicts the typical setup for the conventional far-field electrospinning (FFES).
+As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}.
+When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process.
+The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}.
+The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.
+
+In the intent to achieve controlled fiber deposition, Sun et al.
+\unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES),Figure~\ref{f-c34559531e3e}.b, describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line.
+Moreover, some mechanical influence is required to deposit fibers precisely.
+The mechanical force is introduced by moving collector.
+If the polymer solution jet speed is faster than the speed of the moving collector, the written fiber will curl; on the other hand, if the collector moves faster than the polymer jet, the fiber will gradually diminish \unskip~\cite{527120:11974327,527120:11974326}.
+Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.
+
+The main difference between NFES and FFES is the distance between the needle and the collector which is higher in FFES (about 10 cm) compared to NFES which ranges in the mm scale.
+The short distance allow the production of well aligned fibers within particular designs.
+In NFES, the fiber morphology can be altered by the control of the distance between the nozzle and the substrate (collector).
+With the decrease of the nozzle-to-substrate distance, the electric field strength increases; however it can cause incomplete solvent volatilisation and possible short circuits between the collector and the nozzle tip.
+
+An optimal nozzle-to-substrate distance shall be defined to ensure the fabrication of dry continuous fibers.
+If the solvent is not well evaporated, the produced fibers are prone to defects; on the other hand if solidification happens too fast, the solids can block the spinneret which can prevent a continuous fiber yield.
+Furthermore, the polymer jet will discharge itself as soon as possible, therefore long distances can result in low yields.
+
+\subsection{Substrate}Due to the close distance between the grounded substrate and the charged spinneret in NFES, the set up is prone to electrical shorts.
+In NFES, when a short circuit takes place, the electrospinning process is interrupted resulting in the fabrication of discontinuous fibers.
+Two workarounds to avoid electrical shorts is to lower the applied voltage and to use less conductive substrates \unskip~\cite{527120:11974315,527120:12322289}.
+
+Liu et al.\unskip~\cite{527120:11974315} discovered that the fiber alignment is improved by using a glass-cooper foil substrate, however the well aligned fibers are spoiled after prolonged depositions due to residual charges.
+Additionally, the effect of residual charges is amplified with the used collector substrate contains a conductive layer and a non-conductive layer\unskip~\cite{527120:11974315}.
+
+On the other hand, Choi et al.\unskip~\cite{527120:12322289} implemented a hydrophilic substrate to deposit the fibers with plasma treatment to increase the conductivity of selected areas.
+NFES was carried put with precise deposition as the fibers were placed as per the desired design within the hydrophilic substrate.
+
+\section{Data collection of NFES fiber morphology and process parameters}
+
+\section{Discussion \& NFES Challenges}
+Helix electrodynamic printing (HE-printing) was presented by Duan et al.
+\unskip~\cite{527120:11974308} with the intention of depositing aligned fibers.
+The authors fabricated a stretchable piezoelectric device using micro and nano fibers to demonstrate the possible applications of HE-printinh for electronics manufacturing.
+Duan et al.
+concluded that the fiber morphology is mainly driven by: the stage velocity, the applied voltage, and the nozzle-to-collector distance.
+
+\bgroup
+%\fixFloatSize{./images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}{\includegraphics[scale=0.65]{./images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}}{}
+\makeatother 
+\caption{{}}
+\label{f-30543905e028}
+\end{figure*}
+\egroup
+
+\bgroup
+%\fixFloatSize{./images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}{\includegraphics{./images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}}{}
+\makeatother 
+\caption{{NFES Applied Voltage vs. Fiber Diameter}}
+\label{f-59ed68f95344}
+\end{figure*}
+\egroup
+
+\bgroup
+%\fixFloatSize{./images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}{\includegraphics{./images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}}{}
+\makeatother 
+\caption{{Nozzle Diameter vs. Fiber Diameter}}
+\label{f-51afaccaf109}
+\end{figure*}
+\egroup
+
+\bgroup
+%\fixFloatSize{./images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}{\includegraphics{./images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}}{}
+\makeatother 
+\caption{{Nozzle to Collector Distance vs. Fiber Diameter}}
+\label{f-5f453fad619f}
+\end{figure*}
+\egroup
+
+\bgroup
+%\fixFloatSize{./images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}{\includegraphics{./images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}}{}
+\makeatother 
+\caption{{Polymer Concentration vs. Fiber Diameter}}
+\label{f-d977f56a0782}
+\end{figure*}
+\egroup
+
+\bgroup
+%\fixFloatSize{./images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}
+\begin{figure*}[!htbp]
+\centering \makeatletter\IfFileExists{./images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}{\includegraphics{./images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}}{}
+\makeatother 
+\caption{{Solution Deposition Rate vs. Fiber Diameter}}
+\label{f-08e527ddef81}
+\end{figure*}
+\egroup
+Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine nozzle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity.
+The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano fibers was investigated.
+
+Near-field electrospinning (NFES) is widely recognized as a versatile nano fabrication method, one suitable for applications in tissue engineering.
+Rapid developments in this field have given rise to layered nano fibrous scaffolds.
+However, this electrostatic fabrication process is limited by the electric field inhibitory effects of polymer deposition.
+This leads to a major challenge: how to surpass this limitation on planar/layered constructs.
+While the current focus in this area largely lies with the investigation of new materials, techniques and increasing precision of NFES systems and patterning, exploration of complex collector substrates is often restricted by (i) available technology and (ii) access to complex electrode manufacturing tools.
+
+Although electrospinning (ES) allows the production of unsurpassed nano scale polymer fibers, the major drawbacks are the nozzle-clogging and single-jet spinneret, respectively.
+This is a real limitation in terms of usable polymers and for patterning active organics.
+Nowadays the micro-engineering of smart materials could represent a new route for many fields of technology ranging from the production of electronic and photonic devices [1\ensuremath{-}3] to regenerative medicine and tissue engineering.
+[4\ensuremath{-}7] An enormous technological interest is related to the possibility of patterning fibers directly in well-ordered patterns avoiding the deposition of nonwoven sub micrometer mats often occurring in ES.
+[8,9] In the past decade several attempts have been made using field- induced [10\ensuremath{-}13] and near-field ES, [14,15] but only very recently, with the introduction of mechano ES, [16] has the production of well- ordered fiber patterns been achieved.
+Nevertheless, some drawbacks related to the complexity of the setup, the operating temperature, and the selection of usable materials for problems related to nozzle clogging still persist.
+Moreover, high temperature can cause deterioration of the optical and electronic properties of active organic materials eventually embedded in the functionalize [d fibers.
+On the other side, interfering effects due to closeness of multiple electrified nozzles ban working with multiple spinnerets.

### 2020-11-16 05_Thesis/THESIS_LaTeX/Chapters/2.tex
in progress

@@
 
+Near-field electrospinning process parameters and achieved fiber morphology data was collected into a single database with the purpose to analyze the data and find correlations between the process parameters and the obtained fiber morphology after a NFES process.
+The alalysis comprises from the first reported NFES apparatus built in 2003 by J.
+Kameoka et al.
+\cite{Kameoka2003a} to recent studies conducted in 2020.
+The data collection process was divided in three procedures depending on the format of the available information, as follows:
+
+\begin{enumerate}
+\item Case 1 : data is collected as is from literature. This procedure was implemented when the data is listed within tables and/or as text format.
+\item Case 2 : data is only presented in a figure as plots.
+\item Case 3 : data is not available in text format or plots, however Scanning Electron Microscopy Images (SEM) images are reported from the obtained fibers.
+\end{enumerate}
+
+\subsection{Image Analysis - Data extraction from plots}
+
+Most numerical data of NFES process parameters and fiber diameters is available only in the form of plots.
+The reported figures provide a visual relationship between the variables of interest, however recovering the numerical values of the data is a tedious process prone to errors.
+To avoid mistakes and accelerate the collection data from plots, \href{https://github.com/ankitrohatgi/WebPlotDigitizer}{WebPlotDigitizer} was used.
+WebPlotDigitizer is a HTML5 tool that facilitates accurate data extraction with ease of use.
+Figure \ref{fig:} is a screenshot of the software in use.
+
+\begin{figure}[th]
+\centering
+\includegraphics[scale=0.45]{./Figures/screenshotWebPlotDigitizer.png}
+\decoRule
+\caption[WebPlotDigitizer home-screen]{Open session of WebPlotDigitizer \href{https://github.com/ankitrohatgi/WebPlotDigitizer}{github.com}}
+\label{fig:screenshotWebPlotDigitizer}
+\end{figure}
+
+\subsection{Image Analysis - Data extraction from Scanning Electron Microscopy Images}
+
+Scanning Electron Microscopy Images (SEM) images contain information in a two-dimensional grid that can be extracted using point and line counting techniques, however this can be a laborious process for a large number of images.
+To decrease the complex and lavorious aspect of the counting process, a \emph{Python} script was developed to measure fiber diameters from the available SEM images.
+As shown in Figure \ref{fig:}, the image analysis algorithm follows three main steps: pre-processing, segmentation, object detection, and data processing.
+
 \section{Discussion \& NFES Challenges}

### 2020-11-16 05_Thesis/THESIS_LaTeX/Chapters/2.tex
chap2 in progress

@@
 \cite{Kameoka2003a} to recent studies conducted in 2020.
-The data collection process was divided in three procedures depending on the format of the available information, as follows:
+\cite{
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014} The data collection process was divided in three procedures depending on the format of the available information, as follows:
 
@@
 To decrease the complex and lavorious aspect of the counting process, a \emph{Python} script was developed to measure fiber diameters from the available SEM images.
-As shown in Figure \ref{fig:}, the image analysis algorithm follows three main steps: pre-processing, segmentation, object detection, and data processing.
+As shown in Figure \ref{fig:imageAnalysisAlgorithm}, the image analysis algorithm follows three main steps: pre-processing, segmentation, object detection, and data processing.
+
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.50]{./Figures/imageAnalysisAlgorithm.png}
+\decoRule
+\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
+Ilustration uses Yousefi et al.'s work as an example.
+\cite{Yousefi2019}}
+\label{fig:imageAnalysisAlgorithm}
+\end{figure}
+
+The adopted image analysis was implemented with the \emph{Python} package \emph{OpenCV}.
+First a segmentation procedure is executed over an input image to delimit the objects to be measured (fiber sections and scale bar).
+The segmentation step is the only step needed to be done manually in a image processing software, in this case \emph{Inkscape} was used.
+Next, the segmented image is passed to the \emph{Pyhton} script, which will convert its input image into a binary image.
+A binary image is a black and white image (with no gray scale) that ease the detection of the object edges as the color intensity change between the objects and the background is well defined.
+Once the binary image is computed, the \emph{Canny} edge detection algorithm is executed.
+Once the edges are well defined, a the image is dilated to make the edges more visible.
+The final step before measurement, the \emph{OpenCV} \emph{findContours} function is called to store the objects in memory.
+The first object to be measured is the scale bar as this is needed as a reference to convert the pixel counts to a metric unit.
+Finally, the objects are located within the image with four edge points, and the reference object is used to compute the metric length as the ratio of counted pixels between two edge points and the scale bar dimension in meters.
 
 \section{Discussion \& NFES Challenges}
+
 Helix electrodynamic printing (HE-printing) was presented by Duan et al.
 \unskip~\cite{527120:11974308} with the intention of depositing aligned fibers.
-The authors fabricated a stretchable piezoelectric device using micro and nano fibers to demonstrate the possible applications of HE-printinh for electronics manufacturing.
+The authors fabricated a stretchable piezoelectric device using micro and nano fibers to demonstrate the possible applications of HE-printing for electronics manufacturing.
 Duan et al.
@@
 
-\bgroup
-%\fixFloatSize{./images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{./images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}{\includegraphics[scale=0.65]{./images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}}{}
-\makeatother 
-\caption{{}}
-\label{f-30543905e028}
-\end{figure*}
-\egroup
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/plt_corMat.png}
+\decoRule
+\caption[NFES correlation matrix of process parameters and fiber morphology]{{Correlation matrix comprised by the NFES data from recent literature. 
+\cite{
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014} Fiber diameter is highly correlated with polymer solution concentration and slightly correlated with solution flow rate, zero-shear viscosity and nozzle diameter.}}
+\label{fig:plt_corMat}
+\end{figure}
 
-\bgroup
-%\fixFloatSize{./images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{./images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}{\includegraphics{./images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{NFES Applied Voltage vs. Fiber Diameter}}
-\label{f-59ed68f95344}
-\end{figure*}
-\egroup
+Figures \ref{fig:plt_Cpolymerwt_vs_Dfiberm}, \ref{fig:plt_Dnozzlem_vs_Dfiberm}, \ref{fig:plt_Lm_vs_Dfiberm}, \ref{fig:plt_Phi0V_vs_Dfiberm}, \ref{fig:plt_Qm3s_vs_Dfiberm} and \ref{fig:plt_vstagems_vs_Dfiberm} are scatter plots that depict the relationship of various process parameters (polymer concentration $C_{polymer}$, nozzle inner diameter $D_{nozzle}$, NFES working distance $L$, NFES applied voltage $\Phi_0$, flow rate $Q$, and stage velocity $v_{stage}$) with the final fiber diameter $D_{fiber}$.
+In a generalized summary, these figures suggest that thin fibers are produced with the implementation of low polymer concentrations, small nozzle diameters, short working distances, low applied voltages, low flow rates, and high stage xy velocities.
+Moreover, based on the degree of dispersion of the data points, polymer concentration $C_{polymer}$ is the most reliable process parameter to describe and predict the behavior of the fiber diameter, as most of the data can be grouped in a single cluster.
+Unlike $C_{polymer}$ in Figure \ref{fig:plt_Cpolymerwt_vs_Dfiberm}, various data clusters can be identified within the other scatter plots.
+For instance, Song's results \cite{Song2015} deviate from the main cluster in Figures \ref{fig:plt_Dnozzlem_vs_Dfiberm}, \ref{fig:plt_Lm_vs_Dfiberm}, \ref{fig:plt_Phi0V_vs_Dfiberm}, and \ref{fig:plt_vstagems_vs_Dfiberm}, this may be because Song et al.
+used Au/Pd coated glass capillary nozzles instead of the traditional stainless steel precision tips.
+However in the $C_{polymer}$ vs.
+$D_{fiber}$ figure, Song's results fit within the main cluster.
 
-\bgroup
-%\fixFloatSize{./images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{./images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}{\includegraphics{./images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{Nozzle Diameter vs. Fiber Diameter}}
-\label{f-51afaccaf109}
-\end{figure*}
-\egroup
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/plt_Cpolymerwt_vs_Dfiberm.png}
+\decoRule
+\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
+Ilustration uses Yousefi et al.'s work as an example.
+\cite{
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
+\label{fig:plt_Cpolymerwt_vs_Dfiberm}
+\end{figure}
 
-\bgroup
-%\fixFloatSize{./images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{./images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}{\includegraphics{./images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{Nozzle to Collector Distance vs. Fiber Diameter}}
-\label{f-5f453fad619f}
-\end{figure*}
-\egroup
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/plt_Dnozzlem_vs_Dfiberm.png}
+\decoRule
+\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
+Ilustration uses Yousefi et al.'s work as an example.
+\cite{
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
+\label{fig:plt_Dnozzlem_vs_Dfiberm}
+\end{figure}
 
-\bgroup
-%\fixFloatSize{./images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{./images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}{\includegraphics{./images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{Polymer Concentration vs. Fiber Diameter}}
-\label{f-d977f56a0782}
-\end{figure*}
-\egroup
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/plt_Lm_vs_Dfiberm.png}
+\decoRule
+\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
+Ilustration uses Yousefi et al.'s work as an example.
+\cite{
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
+\label{fig:plt_Lm_vs_Dfiberm}
+\end{figure}
 
-\bgroup
-%\fixFloatSize{./images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}
-\begin{figure*}[!htbp]
-\centering \makeatletter\IfFileExists{./images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}{\includegraphics{./images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}}{}
-\makeatother 
-\caption{{Solution Deposition Rate vs. Fiber Diameter}}
-\label{f-08e527ddef81}
-\end{figure*}
-\egroup
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/plt_Phi0V_vs_Dfiberm.png}
+\decoRule
+\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
+Ilustration uses Yousefi et al.'s work as an example.
+\cite{
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
+\label{fig:plt_Phi0V_vs_Dfiberm}
+\end{figure}
+
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/plt_Qm3s_vs_Dfiberm.png}
+\decoRule
+\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
+Ilustration uses Yousefi et al.'s work as an example.
+\cite{
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
+\label{fig:plt_Qm3s_vs_Dfiberm}
+\end{figure}
+
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/plt_vstagems_vs_Dfiberm.png}
+\decoRule
+\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
+Ilustration uses Yousefi et al.'s work as an example.
+\cite{
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
+\label{fig:plt_vstagems_vs_Dfiberm}
+\end{figure}
+
 Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine nozzle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity.
@@
 On the other side, interfering effects due to closeness of multiple electrified nozzles ban working with multiple spinnerets.
+
+\section{Diameter Prediction of Electrospun Fibers} % adimensional analysis
+
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/plt_Pi1_vs_Oh.png}
+\decoRule
+\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
+Ilustration uses Yousefi et al.'s work as an example.
+\cite{Helgeson2007,
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
+\label{fig:plt_Pi1_vs_Oh}
+\end{figure}

### 2020-11-16 05_Thesis/THESIS_LaTeX/main.tex
chapter 1 done?
chapter 2 in progress
chap2 in progress

@@
 \usepackage[utf8]{inputenc}
+\DeclareUnicodeCharacter{0301}{} % TODO: remove unicode character in .bib
 
@@
 \usepackage[none]{hyphenat}
+
+% table out of margin: any suggestion?
+\usepackage{tabularx}
+\renewcommand\arraystretch{1.5} % Add extra space between table rows
 
@@
 \textbf{MTY}   & \textbf{M}on\textbf{t}erre\textbf{y} \emph{or} Campus \textbf{M}on\textbf{t}erre\textbf{y}\\
+\textbf{NFEMS} & \textbf{N}ear-\textbf{F}ield \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\
 \textbf{NFES}  & \textbf{N}ear \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
@@
 \addlinespace % Gap to separate the Roman symbols from the Greek
-$\omega$ & angular frequency & \si{\radian} \\
+$\textrm{Mw}$  & Molecular Weight             & $\textrm{g} / \textrm{mole}$ \\
+$\eta_0$       & Zero-shear Viscosity         & $\textrm{Pa} \cdot \textrm{s}$	\\
+$K$            & Electrical Conductivity      & $\textrm{S} / \textrm{m}$	\\
+$\gamma$       & Surface Tension              & $\textrm{N} / \textrm{m}$ \\
+$\dot{\gamma}$ & Shear Rate                   & $1 / \textrm{s}$ \\
+$\rho$         & Density                      & $\textrm{Kg} / \textrm{m}^3$ \\
+$C_{polymer}$  & Polymer concentration        & $\textrm{wt\%}$	\\
+$D_{nozzle}$   & Nozzle Inner Diameter        & $\textrm{m}$ \\
+$Q$            & Flow Rate                    & $\textrm{m}^3 / \textrm{s}$	\\
+$L$            & NFES Working Distance        & $\textrm{m}$	\\
+$\Phi_0$       & NFES Applied Voltage         & $\textrm{V}$	\\
+$v_{stage}$    & Collector/Stage velocity     & $\textrm{m} / \textrm{s}$ \\
+$D_{fiber}$    & Fiber Diameter               & $\textrm{m}$ \\
+$FiberGap$     & Distance between fibers      & $\textrm{m}$ \\
+$R_{jet}$      & NFES Jet Radius              & $\textrm{m}$ \\
+$Oh$           & Ohnesorge number             & NA. \\
+$Pe$           & Peclet number                & NA. \\
+$Re$           & Reynolds number              & NA. \\
+$We$           & Weber number                 & NA. \\
+$\Psi$         & Dimensionless Field Strength & NA. \\
 

### 2020-11-16 05_Thesis/THESIS_LaTeX/Chapters/2.tex
min progress

@@
 
+Measurements were validaded with Camillo's, Gupta's, Jiang's, Min's, Sun's, Wang's, and Xue's \cite{Camillo2013, Gupta2007, Jiang2018, Min2013, Sun2006a, Wang2015, Xue2014} results as those authors reported both, a SEM image and the measured fiber diameter.
+For instance, Figure \ref{fig:imageAnalysisToolValidation} shows in white the reported diameters by Min and in blue the diameters measured by the \emph{Python script}.
+The measurement error of the developed script is about $3.2\%$ in avg.
+It is considerable to mention that the reported measurement error is mainly contributed to the fact that most fibers are not of the same diameter along the fiber length.
+In most cases, measurements at the end of the fibers are thicker than the ones measured u¿in the center.
+
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.8]{./Figures/imageAnalysisToolValidation.png}
+\decoRule
+\caption[Validation of the developed image analysis meassurement tool]{{Validation of the developed image analysis meassurement tool. SEM images of Min's work are used as an example. \cite{Min2013}}}
+\label{fig:imageAnalysisToolValidation}
+\end{figure}
+
 \section{Discussion \& NFES Challenges}
@@
 \decoRule
-\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
-Ilustration uses Yousefi et al.'s work as an example.
-\cite{
+\caption[Scatter Plot of Polymer Concentrations and Fiber Diameters from Literature Results]{Scatter Plot of Polymer Concentrations and Fiber Diameters from Literature Results. \cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 
+The trend of Figure \ref{fig:plt_Dnozzlem_vs_Dfiberm} shows that thicker nozzle diameters yield thicker fibers.
+However, the final fiber diameter can be reduced without changing the nozzle diameter.
+For instance Chang et al.
+\cite{Chang2008} achieved the thinnest fibers of about $50 nm$ in diameter even though Chang implemented nozzle needles of similar diameter as Shin, Min and Xu.
+\cite{Shin2019, Min2013, Xu2014}
+
 \begin{figure}[!th]
@@
 \decoRule
-\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
-Ilustration uses Yousefi et al.'s work as an example.
-\cite{
+\caption[Scatter Plot of Nozzle Inner Diameters and Fiber Diameters from Literature Results]{Scatter Plot of Nozzle Inner Diameters and Fiber Diameters from Literature Results. \cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 \decoRule
-\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
-Ilustration uses Yousefi et al.'s work as an example.
-\cite{
+\caption[Scatter Plot of NFES Working Distances and Fiber Diameters from Literature Results]{Scatter Plot of NFES Working Distances and Fiber Diameters from Literature Results. \cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 \decoRule
-\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
-Ilustration uses Yousefi et al.'s work as an example.
-\cite{
+\caption[Scatter Plot of NFES Applied Voltages and Fiber Diameters from Literature Results]{Scatter Plot of NFES Applied Voltages and Fiber Diameters from Literature Results. \cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 \decoRule
-\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
-Ilustration uses Yousefi et al.'s work as an example.
-\cite{
+\caption[Scatter Plot of Polymer Solution Flow Rates and Fiber Diameters from Literature Results]{Scatter Plot of Polymer Solution Flow Rates and Fiber Diameters from Literature Results. \cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 \decoRule
-\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images.
-Ilustration uses Yousefi et al.'s work as an example.
-\cite{
+\caption[Scatter Plot of Collector xy Stage Velocities and Fiber Diameters from Literature Results]{Scatter Plot of Collector xy Stage Velocities and Fiber Diameters from Literature Results. \cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,

### 2020-11-17 05_Thesis/THESIS_LaTeX/Chapters/2.tex
progress

@@
 WebPlotDigitizer is a HTML5 tool that facilitates accurate data extraction with ease of use.
-Figure \ref{fig:} is a screenshot of the software in use.
+Figure \ref{fig:screenshotWebPlotDigitizer} is a screenshot of the software in use.
 
@@
 \decoRule
-\caption[Scatter Plot of Polymer Concentrations and Fiber Diameters from Literature Results]{Scatter Plot of Polymer Concentrations and Fiber Diameters from Literature Results. \cite{
+\caption[Scatter Plot of Polymer Concentrations and Fiber Diameters from Literature Experimental Results]{Scatter Plot of Polymer Concentrations and Fiber Diameters from Literature Experimental Results.
+\cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 For instance Chang et al.
-\cite{Chang2008} achieved the thinnest fibers of about $50 nm$ in diameter even though Chang implemented nozzle needles of similar diameter as Shin, Min and Xu.
-\cite{Shin2019, Min2013, Xu2014}
+\cite{Chang2008} achieved the thinnest fibers of about $50 nm$ in diameter even though Chang implemented nozzle needles of similar diameter as Shin, Min and Xu by the implementation different settings on the other process parameters.
+\cite{Shin2019, Min2013, Xu2014} It is reasonable to notice that Chang's record of achieving the thinnest fiber may be a one time-successful since, neither the yield rate nor the reproducibility of their technique was not reported.
 
@@
 \decoRule
-\caption[Scatter Plot of Nozzle Inner Diameters and Fiber Diameters from Literature Results]{Scatter Plot of Nozzle Inner Diameters and Fiber Diameters from Literature Results. \cite{
+\caption[Scatter Plot of Nozzle Inner Diameters and Fiber Diameters from Literature Experimental Results]{Scatter Plot of Nozzle Inner Diameters and Fiber Diameters from Literature Experimental Results.
+\cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 
+The relationship between the fiber diameter the working distance $L$ and applied voltage $\Phi_0$ can be depicted in Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}.
+The near-field electrospinning jet is ejected from the Taylor cone when the applied voltage generates an electric field strong enough to break the solution drop.
+Changing the applied voltage will amend initial drop and fiber morphology, thereby resulting in a change in the fibers' properties.
+However, the effect of the applied voltage on the fiber diameter is not well defined.
+On one hand, many researchers posit that high applied voltages lead to larger fiber diameters, whereas other researchers have reported reductions in fiber diameter with high applied voltages as the electric field force increases on the charged jet.
+\cite{Zhang2005} Furthermore, Reneker and Chun observed that applied voltage does not significantly affect the diameter of electrospun polyethylene oxide (PEO) fibers.
+\cite{Reneker1996} Applied voltage has an influence on the fiber diameter, but the degree and direction of influence varies with other process parameters such as polymeric solution concentration and on the working distance \cite{Yordem2008, Chang2016}.
+
+Looking at Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}, the data points from Husain, Lee and Sonntag \ref{Husain2016, Lee2012, Sonntag2020} experimental results are outside the principal cluster since they implemented working distances around $10^{-1} \textrm{m}$, which is concidered to be the threshold between NFES and far-field electrospinning (FFES).
+One can observe that: a) in NFES fiber diameter increase with increasing applied voltage; and b) in FFES fiber diameter decrease with increasing applied voltage.
+On the other hand, data related to Liu's and Beachey's work \ref{Liu2014, Beachey2011} do not fit the main trend as they perform the electrospinning process with a rotating drum as the collector, instead of the typical xy stage.
+
 \begin{figure}[!th]
@@
 \decoRule
-\caption[Scatter Plot of NFES Working Distances and Fiber Diameters from Literature Results]{Scatter Plot of NFES Working Distances and Fiber Diameters from Literature Results. \cite{
+\caption[Scatter Plot of NFES Working Distances and Fiber Diameters from Literature Experimental Results]{Scatter Plot of NFES Working Distances and Fiber Diameters from Literature Experimental Results.
+\cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 \decoRule
-\caption[Scatter Plot of NFES Applied Voltages and Fiber Diameters from Literature Results]{Scatter Plot of NFES Applied Voltages and Fiber Diameters from Literature Results. \cite{
+\caption[Scatter Plot of NFES Applied Voltages and Fiber Diameters from Literature Experimental Results]{Scatter Plot of NFES Applied Voltages and Fiber Diameters from Literature Experimental Results.
+\cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 \decoRule
-\caption[Scatter Plot of Polymer Solution Flow Rates and Fiber Diameters from Literature Results]{Scatter Plot of Polymer Solution Flow Rates and Fiber Diameters from Literature Results. \cite{
+\caption[Scatter Plot of Polymer Solution Flow Rates and Fiber Diameters from Literature Experimental Results]{Scatter Plot of Polymer Solution Flow Rates and Fiber Diameters from Literature Experimental Results.
+\cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
@@
 \decoRule
-\caption[Scatter Plot of Collector xy Stage Velocities and Fiber Diameters from Literature Results]{Scatter Plot of Collector xy Stage Velocities and Fiber Diameters from Literature Results. \cite{
+\caption[Scatter Plot of Collector xy Stage Velocities and Fiber Diameters from Literature Experimental Results]{Scatter Plot of Collector xy Stage Velocities and Fiber Diameters from Literature Experimental Results.
+\cite{
   Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,

### 2020-11-17 05_Thesis/THESIS_LaTeX/Chapters/2.tex
progress

@@
 
-Looking at Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}, the data points from Husain, Lee and Sonntag \ref{Husain2016, Lee2012, Sonntag2020} experimental results are outside the principal cluster since they implemented working distances around $10^{-1} \textrm{m}$, which is concidered to be the threshold between NFES and far-field electrospinning (FFES).
+Looking at Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}, the data points from Husain, Lee and Sonntag \cite{Husain2016, Lee2012, Sonntag2020} experimental results are outside the principal cluster since they implemented working distances around $10^{-1} \textrm{m}$, which is concidered to be the threshold between NFES and far-field electrospinning (FFES).
 One can observe that: a) in NFES fiber diameter increase with increasing applied voltage; and b) in FFES fiber diameter decrease with increasing applied voltage.
-On the other hand, data related to Liu's and Beachey's work \ref{Liu2014, Beachey2011} do not fit the main trend as they perform the electrospinning process with a rotating drum as the collector, instead of the typical xy stage.
+On the other hand, data related to Liu's and Beachey's work \cite{Liu2014, Beachey2011} do not fit the main trend as they perform the electrospinning process with a rotating drum as the collector, instead of the typical xy stage.
 
@@
 
-Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine nozzle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity.
-The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano fibers was investigated.
+The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano-fibers was investigated, a summary is presented in Table \ref{tab:nfesProcessParameters}.
 
-Near-field electrospinning (NFES) is widely recognized as a versatile nano fabrication method, one suitable for applications in tissue engineering.
-Rapid developments in this field have given rise to layered nano fibrous scaffolds.
-However, this electrostatic fabrication process is limited by the electric field inhibitory effects of polymer deposition.
-This leads to a major challenge: how to surpass this limitation on planar/layered constructs.
-While the current focus in this area largely lies with the investigation of new materials, techniques and increasing precision of NFES systems and patterning, exploration of complex collector substrates is often restricted by (i) available technology and (ii) access to complex electrode manufacturing tools.
+\begin{table}[ht]
+\centering
+\caption[Near-Field Electrospinning Process Parameters]{Summary of the main parameters that drive the electrospinning process, ordered by: polymer solution parameters, process parameters, and ambient parameters.
+Adapted from \cite{Bagbi2019, Unnithan2015}}
+\begin{tabularx}{\textwidth}{lX}
+\hline
+\textbf{NFES Process Parameters} & \textbf{Effect} \\
+\hline
+\textbf{Solution Parameters:} &  \\
+Concentration & Concentration shall be high enough to produce uniform nano-fibers, but low enough to give the correct viscosity \\
+Molecular weight & High molecular weight polymers yield smoother fibers \\
+Viscosity & Zero-shear viscosity shall be optimal to generate a constant jet from the needle \\
+Conductivity & Solution shall be conductive enough for the electrif field to have influence on the jet \\
+\textbf{Process Parameters:} &  \\
+Applied voltage & Higher voltages eject more material from the nozzle \\
+Flow rate & Slow flow rates yield thinner fibers, but it shall be fast enough to prevent clogging and keep the Tailor cone in a constant size and shape \\
+Working distance & Long distances result in thinner fibers, however the spatial control is harmed \\
+\textbf{Ambient Parameters:} &  \\
+Humidity & Increasing humidity produces thicker diameters \\
+Temperature & Increasing temperature yields thinner fibers, however high temperatures make the nozzle prone to clog as the solvent evaporates at a faster rate \\
+\hline
+\end{tabularx}
+\label{tab:nfesProcessParameters}
+\end{table}
 
-Although electrospinning (ES) allows the production of unsurpassed nano scale polymer fibers, the major drawbacks are the nozzle-clogging and single-jet spinneret, respectively.
-This is a real limitation in terms of usable polymers and for patterning active organics.
-Nowadays the micro-engineering of smart materials could represent a new route for many fields of technology ranging from the production of electronic and photonic devices [1\ensuremath{-}3] to regenerative medicine and tissue engineering.
-[4\ensuremath{-}7] An enormous technological interest is related to the possibility of patterning fibers directly in well-ordered patterns avoiding the deposition of nonwoven sub micrometer mats often occurring in ES.
-[8,9] In the past decade several attempts have been made using field- induced [10\ensuremath{-}13] and near-field ES, [14,15] but only very recently, with the introduction of mechano ES, [16] has the production of well- ordered fiber patterns been achieved.
-Nevertheless, some drawbacks related to the complexity of the setup, the operating temperature, and the selection of usable materials for problems related to nozzle clogging still persist.
-Moreover, high temperature can cause deterioration of the optical and electronic properties of active organic materials eventually embedded in the functionalize [d fibers.
-On the other side, interfering effects due to closeness of multiple electrified nozzles ban working with multiple spinnerets.
+Near-field electrospinning (NFES) is known as a versatile nano-fabrication technique, suitable for several applications such as tissue engineering, chemical sensing, filtration, energy storage, besides others (see Figure \ref{fig:synthesesAndApplicationsOfNanofibers}).
+Fast developments in electrospinning has been observed in recent years.
+However, this process is limited by the electric field wiping instability effects during polymer deposition.
+This leads to a major challenge: how to surpass this limitation of planar two-dimensional prints.
+The current trend in this area lies on the research of new materials, techniques to increase precision patterning in NFES systems.
+
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/synthesesAndApplicationsOfNanofibers.png}
+\decoRule
+\caption[Syntheses and Applications of Nanofibers]{Syntheses and Applications of Nanofibers. Adapted from \cite{Kenry2017}}
+\label{fig:synthesesAndApplicationsOfNanofibers}
+\end{figure}
 

### 2020-11-17 05_Thesis/THESIS_LaTeX/Chapters/1.tex
chap2 in progress
progress

@@
 
-\begin{figure}[th]
+\begin{figure}[!th]
 \centering
@@
 \cite{CardenasBenitez2019} Cardenas et al.
-implemented TPP and conventional UV lithography to study the fabrication of CNFs within carbon micro-electromechanical systems.
+implemented TPP and conventional UV lithography to study the fabrication of CNFs within carbon micro-electromechanical systems (C-MEMS).
+The fabrication of these kind of carbon devices has been previously reported for teachniques, such as electrospinning and photoresist patterning by photolithography using SU-8.
+The typical fabrication process of C-MEMS begins with a spin-coating of a photoresist unto a substrate (typically SU-8), followed by patterning techniques with UV-exposure by photolithography.
+Followed by the development of the desired features solvent.
+Finally, the device is carbonized in a pyrolysis furnace in an inert environment.
+\cite{Pramanick2018a}
+
+Near-field electrospinning can be regarded as complementary technique, by which polymeric nanofibers can be produced, since the structural geometries created photolithography are restricted by the diffraction limit.
+\cite{Pramanick2018a, Okazaki1991} SU-8 is designed to produce vitrous carbon structure via photolithography, it is not design for electrospinning procedures as it lacks the right viscosity and solution conductivity.
+Cardenas \cite{Cardenas2017} and Flores \cite{Flores2017} have adapted the SU-8 formulation by the addition of tetrabutylammonium tetrafluoroborate (TBF) and poly(ethylene oxide) (PEO).
+TBF was added to increase the solution conductivity and PEO provides the required viscosity.
+Both additions are required to yield smooth solution flow during electrospinning.
+
+\begin{table}[ht]
+\centering
+\caption[Prepared Polymer Solutions in Previous Work]{Prepared Polymer Solutions in Previous Work \cite{Cardenas2017, Flores2017}}
+\begin{tabular}{cccc}
+\hline
+\textbf{Sample} & \multicolumn{3}{c}{\textbf{Concentration} $wt\%$} \\
+\hline
+{} & \textbf{SU-8} & \textbf{PEO} & \textbf{TBF} \\
+1 & 99.50 & 0.25 & 0.25 \\
+2 & 99.00 & 0.50 & 0.50 \\
+3 & 98.50 & 0.75 & 0.75 \\
+4 & 98.00 & 1.00 & 1.00 \\
+\hline
+\end{tabular}
+\label{tab:previousPreparedPolymerSolutions}
+\end{table}
+
+The thinnest fibers achieved by Cardenas \cite{Cardenas2017} were achieved with sample 1 of Table \ref{tab:previousPreparedPolymerSolutions}, with the following characteristics: a) Fiber yield rate of $81\%$; b) Fiber diameter before pyrolysis of $4.966 \mu m$; c) Fiber diameter after pyrolysis of $204 nm$; d) Average fiber length of $60.5 ± 4.3 \mu m$; and e) Fiber electrical resistance from $407 K \Omega$ to $1.727 M \Omega$.
+Cardenas results have areas of opportunity regarding the fiber yield rate and the high variability on the fiber electrical resistance.
+These undesirable characteristics could be a consequence of the addition of PEO to the solution.
+Figure \ref{fig:su8Components} illustrates the ingredients that comprise the SU-8 formulation.
+SU-8 based vitreous carbon is obtained after a pyrolysis process in which the oxygen already present in the SU-8 formulation allow the formation of close pores during annealing.
+However, the further addition of oxygen content present in the PEO molecules may be the cause of the low yield rate and high variability in electric resistivity from sample to sample.
+
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.50]{./Figures/su8Components.png}
+\decoRule
+\caption[Components of SU-8 2000 Series Resists]{Components of SU-8 2000 Series Resists. Adapted from \cite{Microchem2012}}
+\label{fig:su8Components}
+\end{figure}
 

### 2020-11-17 05_Thesis/THESIS_LaTeX/Chapters/2.tex
progress

@@
 
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.45]{./Figures/DifferentElectrospinningMethods.png}
+\decoRule
+\caption[Different Electrospinning Methods in Terms of Spatial Control, Fiber Throughput and Resolution]{Different Electrospinning Methods in Terms of Spatial Control, Fiber Throughput and Resolution.
+Adapted from \cite{Tourlomousis2017}}
+\label{fig:DifferentElectrospinningMethods}
+\end{figure}
+
+As depicted in Figure \ref{fig:DifferentElectrospinningMethods}, solution electrospinning yields fiber with higher resolution than melt electrospinning techniques, and near-field electrospinning offers greater spacial control on the deposition of fibers than the far-field technique.
+Moreover, solution electrospinning often involves the use of toxic solvents, whereas melt electrospinning is a solvent free process but with extra complexity as a heater needs to be installed.
+\cite{Tourlomousis2017}
+
 \section{Data collection of NFES fiber morphology and process parameters}
@@
 \item Case 2 : data is only presented in a figure as plots.
-\item Case 3 : data is not available in text format or plots, however Scanning Electron Microscopy Images (SEM) images are reported from the obtained fibers.
+\item Case 3 : data is not available in text format or plots, however Scanning Electron Microscopy (SEM) images are reported from the obtained fibers.
 \end{enumerate}
@@
 For instance, Figure \ref{fig:imageAnalysisToolValidation} shows in white the reported diameters by Min and in blue the diameters measured by the \emph{Python script}.
-The measurement error of the developed script is about $3.2\%$ in avg.
+The measurement error of the developed script is about $3.2\%$ in average.
 It is considerable to mention that the reported measurement error is mainly contributed to the fact that most fibers are not of the same diameter along the fiber length.
@@
 One can observe that: a) in NFES fiber diameter increase with increasing applied voltage; and b) in FFES fiber diameter decrease with increasing applied voltage.
-On the other hand, data related to Liu's and Beachey's work \cite{Liu2014, Beachey2011} do not fit the main trend as they perform the electrospinning process with a rotating drum as the collector, instead of the typical xy stage.
+On the other hand, data related to Liu's and Beachey's work \cite{Liu2014, Beachley2011} do not fit the main trend as they perform the electrospinning process with a rotating drum as the collector, instead of the typical xy stage.
 
@@
 
+Electrospinning is a simple process to fabricate fibers of different morphology.
+However, the final morphology of a fiber depends on various solution, process, and ambient parameters (Table \ref{tab:nfesProcessParameters}) with interaction with rheology and fluid dynamics.
+Given the connection of various parameters, it is not trivial to derive a mathematical model to describe the complete electrospinning process.
+Current attempts involve limited models that can only describe the steady jet region for specific polymer solutions.
+\cite{Hohman2001a,Feng2002a,Reneker2000} From literature \cite{Greiner2008, Deitzel2001, Cui2007, Beachley2011} and as described in Figure \ref{fig:plt_corMat}, zero-shear viscosity, flow rate and applied voltage are the main drivers that determine the final fiber morphology and dimensions.
+Other parameters such as solution surface tension, conductivity and working distance have less impact on the electrospun fibers.
+\cite{Ramakrishna2005} As shown in Figures \ref{fig:plt_Qm3s_vs_Dfiberm} and \ref{fig:plt_Cpolymerwt_vs_Dfiberm}, literature states that flow rate $Q$ and solution concentration $C_{polymer}$ are directly proportional to the fiber diameter $D_{fiber}$.
+\cite{Wang2008, McKee2004, Gupta2005}
+
+As mentioned in the previous section, the correlation between the final fiber diameter $D_{fiber}$ and the applied voltage $\Phi_0$ is not well defined.
+Most authors posit that the fiber diameter decreases with increasing voltage.
+\cite{Yuan2004, Wang2009, Thompson2007, Sajeev2008, Mazoochi2011, MATARAM2011, Liu2007, Homayoni2009, Zhang2005} Nevertheless, other publications state the inverse correlation.
+\cite{Rojas2009, Jeun2007} This discrepancy between the final fiber diameter $D_{fiber}$ and the applied voltage $\Phi_0$ may be attributed to the fact that $\Phi_0$ is also related to the electric field $\Phi_0 / L$, which in turn is related to the working distance $L$.
+As the electric field $\Phi_0 / L$ increases, the electric field forces loose influence under the polymer jet as the increased force results into faster evaporation of the solvent promoting faster solidification.
+On the other hand, polymer concentration $C_{polymer}$, and conductivity $K$ also have an effect on the electric field.
+\cite{Thompson2007, Mohan2002}
+
+On the other hand, Zhang et al., Kim et al., and Mituppatham et al.
+studied the relationship between the solution surface tension $\gamma$ and its conductivity $K$.
+\cite{Zhang2005, Kim2005, Mituppatham2004} Kim's and Mituppatham's work report a increase in fiber diameter with increasing conductivity in the polymer solution, while Zhang's reports the inverse relationship.
+The existing interdependence between the process and solution parameters adds complexity and ambiguity to the effect of each parameter.
+The fiber morphology not only depends on the process parameters, but also on the type of electrospinning process and on polymer-solvent system.
+\cite{Gadkari2014}
+
+Helgeson and Wagner \cite{Helgeson2007} have presented an adimensional analysis to predict the fiber diameter with conservation equations of momentum, mass, electric charge and four dimensionless numbers: Peclet number $ \displaystyle Pe = \frac{2 \bar{\varepsilon} v_0}{K R_0} $, Reynold number $ \displaystyle Re = \frac{\rho v_0 R_0}{\eta_0} $, Weber number $ \displaystyle We = \frac{\rho {v_0}^2 R_0}{\gamma} $, and the dimensionless electric field strength $ \displaystyle \Psi = \frac{\bar{\varepsilon} {E_0}^2}{\rho {v_0}^2} $.
+Where $\bar{\varepsilon}$ is the dielectric permitivity of the atmosphere, $K$ the solution conductivity, $\rho$ the density, $\eta_0$ the zero-shear viscosity, $\gamma$ the surface tension, $E_0$ the applied electric field, $R_0$ the initial jet radius, and $v_0$ the initial jet velocity.
+Since $R_0$ and $v_0$ can neither be controlled nor measured, Helgeson arrived to a correlation between the electrostatic and viscous forces $\Pi_1$ describing the stress directing the polymer jet elongation from the source to the collector plate.
+\cite{Helgeson2007}
+
+\begin{equation}\label{eqn:electroViscousRatio}
+    \Pi_1 = Re Pe \Psi = \frac{2 {\bar{\varepsilon}}^2 {\Phi_0}^2}{K \eta_0 L^2}
+\end{equation}
+
+Ohnesorge number, resulting from the manipulation of the Reynolds number $Re$ and the Weber number $We$, is used to explain the behavior of the polymeric solution jet under small disturbances, due the voltage presence, leads to the capillary rupture of the fluid jet.
+\cite{Helgeson2007}
+
+\begin{equation}\label{eqn:ohnesorgeNumber}
+    Oh = \frac{{Re}^2}{We} = \frac{\eta_0}{\sqrt{\rho \gamma R_{jet}}}
+\end{equation}
+
+Where $ \displaystyle R_{jet} = R_f \sqrt{\frac{1}{w_s}} $ is the wet radius of the jet solution, which is calculated from the radius of the dry fiber $R_f$ and the mass fraction of the polymer in solution $w_s$.
+\cite{Helgeson2007}
+
 \begin{figure}[!th]
@@
 \end{figure}
+
+Figure \ref{fig:plt_Pi1_vs_Oh} plots the $\Pi_1$ and $Oh$ values reported by \cite{Helgeson2007} along with new data points from the previous data collection of NFES fiber diameters and process parameters.
+It is possible to observe the predominance of the viscous and the electrostatic forces within the solution by the magnitude $\Pi_1$ (Equation \ref{eqn:electroViscousRatio}), on the other hand $Oh$ (Equation \ref{eqn:ohnesorgeNumber}) reflects the capacity of the viscous forces over the polymeric jet, which allows stability in the electrospinning process.
+The data points gathered by Helgeson et al.
+are from far-field electrospinning studies, whereas the new data points belong to near-field electrospinning studies.
+
+The collected data suggest that both types of electrospinning behave in a similar manner, where the FFES data fits better a linear behavior of slope $-1$.
+As the working distance closes in NFES, the data points fit a shallower slope with higher $\Pi_1$ values and lower $Oh$ values.
+This suggests that in NFES less viscous solutions have been used, since in long working distances a higher viscosity is needed to keep the integrity of the fiber in the whole traveling distance until it reaches the collector.
+For high $Oh$ values and elevated viscosity, the entanglement of the polymeric chains is higher, resulting in the formation of individual fibers; also, the jet is prone to faster solidification, due to an early evaporation of solvent, due to the resistance to the change of momentum, caused by the high viscosity in the polymeric solution, hence the need of higher voltages in FFES.
+Helgeson et al.
+suggest that with the following relationship in Equation \ref{eqn:ohnesorgeNumberRelationship} can be used to predict the fiber diameter, as in the trend in Figure \ref{fig:plt_Pi1_vs_Oh} $Oh$ has an inverse linear relationship with $\Pi_1$.
+\cite{Helgeson2007}
+
+\begin{equation}\label{eqn:ohnesorgeNumberRelationship}
+    \Pi_1 Oh = \frac{2 {\bar{\varepsilon}}^2 {\Phi_0}^2}{K L^2 \sqrt{\rho \gamma R_{jet}}} = 2.5 \pm 0.2 \times 10^{-8}
+\end{equation}
+
+The absence of the solution zero-shear viscosity in Equation \ref{eqn:ohnesorgeNumberRelationship} suggests that $\eta_0$ by its own is insufficient to predict the fiber diameter.
+The solution conductivity, process parameters and surface tension are the main drivers to describe the diameter of electrospun fibers.
+\cite{Helgeson2007}

### 2020-11-17 05_Thesis/THESIS_LaTeX/Chapters/3.tex
progress

% Chapter Template

\chapter{Selection of Compatible Polymer-Solvent Combinations for Near-Field Electrospinning and Pyrolysis} % Main chapter title

\label{Chapter:3}

% search : electrospunable capacity vs. thermo analysis of polymers in solutions (bad/good solvents)

Zhenan Bao et al. \cite{Liu2015a} investigated the effect of the polymer chemical structure (the effect of benzene rings) on the morphology, dimensions, composition, graphitization degree, crystallinity, and electrical conductivity of graphene nano-ribbons derived from four different types of electrospun polymers. The authors studied four polymers polystyrene (PS), poly(vinyl alcohol) (PVA), polyvinylphenol (PVP), and a phenolic resin known as Novolac. See Figure \ref{fig:zhenanBaoPolymers}. The authors created  electrospun polymer fibers out of the four selected polymers. PVP, Novolac and PVA have hydroxyl groups that can be functionalized with metal cations, while PS does not have such binding capability. On the other hand, PVP and Novolac have one benzene ring in each repeating unit, wheras PVA is mainly made out of sp3 carbon.

\begin{figure}[!th]
\centering
\includegraphics[scale=0.35]{./Figures/zhenanBaoPolymers.png}
\decoRule
\caption[Studied Polymers by Zhenan Bao et al. \cite{Liu2015a}]{Studied Polymers by Zhenan Bao et al. \cite{Liu2015a}}
\label{fig:zhenanBaoPolymers}
\end{figure}

Zhenan Bao et al. \cite{Liu2015a} found that higher sp2 carbon content (or more benzene rings) in the polymer chemical structure translates into higher graphitization degree and higher electrical conductivity in the final carbon structures. This finding can be use as a guide when choosing polymer precursors for the fabrication of carbon structures. Furthermore, the authors posit that polymers with functional groups are required for the creation of smooth and continuous fibers throw electrospinning. \cite{Liu2015a}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Selection of Candidate Spunable Polymer Solutions}
%high molecular weight, polymer-solution interaction (straight chains)
Given the conclusions from Zhenan Bao et al. \cite{Liu2015a} along with the extensive literature review and data analysis of Chapter \ref{Chapter:2}, the following polymer solutions were selected to be studied in this work. Polymer selection was based on the their high carbon content and presence of benzene rings. The purpose of the polymer selection is to focus the efforts to maximize the likelihood of polymers to yield carbon structures with high electrical conductivity and high graphitization degree; as testing every possible polymer-solvent system is not a practical way to carry on this research. Figure \ref{fig:selectedpolymers} lists the polymers that are going to be investigated. The selected polymers have been electrospun via far-field electrospinning for the fabrication of fibrous mats \cite{Fong1999, Min2013, Yousefi2019}, but no records of being spunable by NFES.

% 0dot25PEOinSU8_00    % POLY(ETHYLENE OXIDE) in Cyclopentanone
% 21dot21PSinTHF_00    % POLYSTYRENE in TETRAHYDROFURAN
% 15dot0PSBinTHFDMF_00 % POLY(STYRENE-CO-BUTADIENE) in TETRAHYDROFURAN and N,N-DIMETHYLFORMAMIDE
% 15dot0PVKinCHL_00    % POLY(9-VINYLCARBAZOLE) in CHLOROFORM
% XdotXPSMSinDMF       % POLY(STYRENE-CO-ALPHA-METHYLSTYRENE) in N,N-DIMETHYLFORMAMIDE

% 0dot5PVKinSU8_00     % POLY(9-VINYLCARBAZOLE) in Cyclopentanone

% PSB 
% PS  192 000
% PSMS
% PVK 1 100 000
% PEO 4 000 000

\begin{figure}[!th]
\centering
\includegraphics[scale=0.55]{./Figures/selectedpolymers.png}
\decoRule
\caption[Selection of Polymer-Solvent Systems to Investigate in this Work]{Selection of Polymer-Solvent Systems to Investigate in this Work. \cite{Fong1999, Min2013, Yousefi2019}}
\label{fig:selectedpolymers}
\end{figure}

\subsection{Rheology of candidate polymer solutions}
As stated in previous sections, near-field electrospinning requires the control of several parameters to obtain fibers with the desired properties. One of the main parameters are related to the polymer precursor such as molecular weight and its concentration in solution. The evaluation of polymer chain entanglements is an effective way to address the spunability of a polymer-solvent system. [23] Polymer concentration and molecular weight are the main factors in determining the entanglement degree between polymer chains. Solutions at low concentrations do not allow polymer chains to entangle leading the viscoeslasticity od the solution dependent only on individual polymer chains. As the polymer concentration increases, the chains overlap and become entangled. The concentration at which the entanglement initially takes place is the critical concentration $c^*$. Concentrations above the critical concentration $c^*$ generate a fast increase in chain entanglement. This rapid change in chain entanglement is translated into a fast increase in the viscoelasticity of the solution. Figure \ref{fig:concentrationViscosityPlotExplained} illustrates the relationship between polymer concentration and viscoelasticity.
\cite{Han2019}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.45]{./Figures/concentrationViscosityPlotExplained.png}
\decoRule
\caption[Selection of Polymer-Solvent Systems to Investigate in this Work]{Selection of Polymer-Solvent Systems to Investigate in this Work. \cite{Burghelea2020, Gupta2005}}
\label{fig:concentrationViscosityPlotExplained}
\end{figure}

\subsubsection{Materials and Sample Preparation}
The polymer system studied is SU-8 2002 dissolved in cyclopentanone with poly(ethylene) oxide and tetrabutylammonium tetrafluoroborate as additives, from now on SU-8, PEO and TBATFB. For the experiments, all reactants were used as they arrived. SU-8 was obtained from MicroChem(USA) while PEO and TBATFB 99\% were obtained from Sigma Aldrich (USA). PEO has a viscosity average molecular weight, Mv~4,000,000 with less than 1000 ppm of BHT as inhibitor. For preparing the samples, the adequate amount PEO and TBATFB were added
to 5 mL of SU-8 in a 20mL vial and stirred at 160rpm during 1 hour at 75°C.

The proportions are represented as SU-8:PEO:TBATFB in wt\%. The samples with higher PEO concentration often needed more time of stirring to eliminate all the PEO lumps. In order to avoid any chance of cross-linking of SU-8, during the stirring step, all the samples were isolated from light. To extract the solution from the vial, a syringe of 5mL was used. To eliminate the bubbles from the solution, the syringe was placed upside down during 24 hours before the tests.

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Effect of aromatic groups in oxygen-free polymers in NFES and Pyrolysis}

\section{\emph{conclude with a collection of potential spunable polymer solutions}}

### 2020-11-17 05_Thesis/THESIS_LaTeX/main.tex
progress

@@
 \medskip 
-One branch of chemistry is devoted to its compounds! \\
+one branch of chemistry is devoted to its compounds! \\
 \medskip 
-One branch of science is devoted to the many forms of the element as a solid material. \\
+... one branch of science is devoted to the many forms of the element as a solid material. \\
 \medskip 
-The best of this is that although most carbon materials are grey or black to the naked eye and the uninitiated, a closer examination reveals the form, beauty and even color of carbon science.}\bigbreak
+The best of this is that although most carbon materials are grey or black to the naked eye and the uninitiated.
+A closer examination reveals the form, beauty and even color of carbon science.}\bigbreak
 \end{center}
@@
 \include{./Chapters/4}
-\include{./Chapters/5}
+%\include{./Chapters/5}
 

### 2020-11-17 05_Thesis/THESIS_LaTeX/Chapters/3.tex
min progress

@@
 The evaluation of polymer chain entanglements is an effective way to address the spunability of a polymer-solvent system.
-[23] Polymer concentration and molecular weight are the main factors in determining the entanglement degree between polymer chains.
+\cite{Shenoy2005} Polymer concentration and molecular weight are the main factors in determining the entanglement degree between polymer chains.
 Solutions at low concentrations do not allow polymer chains to entangle leading the viscoeslasticity od the solution dependent only on individual polymer chains.
@@
 Figure \ref{fig:concentrationViscosityPlotExplained} illustrates the relationship between polymer concentration and viscoelasticity.
-\cite{Han2019}
+\cite{Burghelea2020, Gupta2005}
 
@@
 \decoRule
-\caption[Selection of Polymer-Solvent Systems to Investigate in this Work]{Selection of Polymer-Solvent Systems to Investigate in this Work. \cite{Burghelea2020, Gupta2005}}
+\caption[Selection of Polymer-Solvent Systems to Investigate in this Work]{Selection of Polymer-Solvent Systems to Investigate in this Work. \cite{Burghelea2020, Gupta2005, Han2019}}
 \label{fig:concentrationViscosityPlotExplained}
 \end{figure}
+
+Electrospinning of smooth, continuous fibers require a polymer concentration higher than the critical concentration.
+As shown in Figure \ref{fig:concentrationViscosityPlotExplained}, the critical concentration can be estimated from the change in slope.
+\cite{Burghelea2020, Gupta2005, Han2019}
 

### 2020-11-19 05_Thesis/THESIS_LaTeX/Chapters/3.tex
visco plots in progress

@@
 
-% 0dot25PEOinSU8_00    % POLY(ETHYLENE OXIDE) in Cyclopentanone
-% 21dot21PSinTHF_00    % POLYSTYRENE in TETRAHYDROFURAN
-% 15dot0PSBinTHFDMF_00 % POLY(STYRENE-CO-BUTADIENE) in TETRAHYDROFURAN and N,N-DIMETHYLFORMAMIDE
-% 15dot0PVKinCHL_00    % POLY(9-VINYLCARBAZOLE) in CHLOROFORM
-% XdotXPSMSinDMF       % POLY(STYRENE-CO-ALPHA-METHYLSTYRENE) in N,N-DIMETHYLFORMAMIDE
-
-% 0dot5PVKinSU8_00     % POLY(9-VINYLCARBAZOLE) in Cyclopentanone
-
 % PSB 
@@
 
-\subsection{Rheology of candidate polymer solutions}
+\section{Rheology of candidate polymer solutions}
 As stated in previous sections, near-field electrospinning requires the control of several parameters to obtain fibers with the desired properties.
@@
 \cite{Shenoy2005} Polymer concentration and molecular weight are the main factors in determining the entanglement degree between polymer chains.
+
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.50]{./Figures/criticalConcentrationEntanglement.png}
+\decoRule
+\caption[Polymer Chain Entanglement in Function of Polymer Concentration]{Effect of the polymer concentration on the structure of polymer chains in solution. Adapted from \cite{Burghelea2020}}
+\label{fig:criticalConcentrationEntanglement}
+\end{figure}
+
 Solutions at low concentrations do not allow polymer chains to entangle leading the viscoeslasticity od the solution dependent only on individual polymer chains.
@@
 The concentration at which the entanglement initially takes place is the critical concentration $c^*$.
-Concentrations above the critical concentration $c^*$ generate a fast increase in chain entanglement.
+Concentrations above the critical concentration $c^*$ generate a fast increase in chain entanglement (Figure \ref{fig:criticalConcentrationEntanglement}).
 This rapid change in chain entanglement is translated into a fast increase in the viscoelasticity of the solution.
@@
 \decoRule
-\caption[Selection of Polymer-Solvent Systems to Investigate in this Work]{Selection of Polymer-Solvent Systems to Investigate in this Work. \cite{Burghelea2020, Gupta2005, Han2019}}
+\caption[Effect on Solution Viscosity and Related Electrospinning Capability]{Effect on solution viscosity, polymer concentration and spinnability.
+Adapted from \cite{Burghelea2020, Gupta2005, Han2019}}
 \label{fig:concentrationViscosityPlotExplained}
@@
 As shown in Figure \ref{fig:concentrationViscosityPlotExplained}, the critical concentration can be estimated from the change in slope.
-\cite{Burghelea2020, Gupta2005, Han2019}
+\cite{Burghelea2020, Gupta2005, Han2019} Therefore, in order to find the critical/spinnable concentrations of the candidate polymer-solvent solutions (poly(styrene-co-butadiene) in tetrahydrofuran, poly(9-vinyl carbazole) in chloroform, polyestyrene in tetrahydrofuran, and poly(styrene-co-a-methylstyrene) - See Figure \ref{fig:selectedpolymers}), it is necessary to build the appropriate viscosity vs.
+concentration plots as described in the following sections.
 
-\subsubsection{Materials and Sample Preparation}
-The polymer system studied is SU-8 2002 dissolved in cyclopentanone with poly(ethylene) oxide and tetrabutylammonium tetrafluoroborate as additives, from now on SU-8, PEO and TBATFB.
-For the experiments, all reactants were used as they arrived.
-SU-8 was obtained from MicroChem(USA) while PEO and TBATFB 99\% were obtained from Sigma Aldrich (USA).
-PEO has a viscosity average molecular weight, Mv~4,000,000 with less than 1000 ppm of BHT as inhibitor.
-For preparing the samples, the adequate amount PEO and TBATFB were added
-to 5 mL of SU-8 in a 20mL vial and stirred at 160rpm during 1 hour at 75°C.
+%\begin{table}[!th]
+%\centering
+%\caption[Set of Polymer-Solvent Systems to be Analyzed]{Set of Polymer-Solvent Systems to be Analyzed}
+%\begin{tabularx}{\textwidth}{ l >{\raggedright\arraybackslash}X }
+%\hline
+%\textbf{Polymer}                                & \textbf{Solvent}                                      \\
+%\hline
+%Poly(Ethylene Oxide) (PEO) + SU-8 2002 (SU-8)   & Cyclopentanone                                        \\
+%Polystyrene (PS)                                & Tetrahydrofuran (THF)                                 \\
+%Poly(Styrene-co-Butadiene) (PSB)                & 1-Methyl-2-Pyrrolidinone (NMP)                        \\
+%Poly(Styrene-co-Butadiene) (PSB)                & Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) \\
+%Poly(Styrene-co-alpha-Methylstyrene) (PSMS)     & N,N-Dimethylformamide (DMF)                           \\
+%Poly(9-Vinylcarbazole) (PVK)                    & Chloroform (CHL)                                      \\
+%Poly(9-Vinylcarbazole) (PVK) + SU-8 2002 (SU-8) & Cyclopentanone                                        \\
+%\hline
+%\end{tabularx}
+%\label{tab:candidatePolymerSolventSystems}
+%\end{table}
 
-The proportions are represented as SU-8:PEO:TBATFB in wt\%.
-The samples with higher PEO concentration often needed more time of stirring to eliminate all the PEO lumps.
-In order to avoid any chance of cross-linking of SU-8, during the stirring step, all the samples were isolated from light.
-To extract the solution from the vial, a syringe of 5mL was used.
-To eliminate the bubbles from the solution, the syringe was placed upside down during 24 hours before the tests.
+\subsection{Materials and Sample Preparation}
+
+Seven polymer-solvent combinations are to be tested.
+The Poly(Ethylene Oxide) and SU-8 2002 combination is what has been used in past work \cite{Cardenas2017, Flores2017}, and will be used as the control sample set.
+The selected polymer-solvent combinations are to investigate the ability of oxygenless polymers to be electrospun and then carbonized into vitreous carbon.
+Tables \ref{tab:PEOinSU8}, \ref{tab:PSBinNMP}, \ref{tab:PSBinTHFnDMF}, \ref{tab:PSMSinDMF}, \ref{tab:PSinTHF}, \ref{tab:PVKinCHL}, and \ref{tab:PVKinSU8} list the prepared polymer systems.
+Tetrabutylammonium tetrafluoroborate (TBF) was added to all solutions to increase the conductivity of the solution.
+SU-8 contains $71\%$ of cyclopentanone, which acts as the solvent (Figure \ref{fig:su8Components}) \cite{Microchem2012}.
+
+\begin{table}[!th]
+\centering
+\caption[Poly(Ethylene Oxide) and SU-8 2002 : Control Sample Preparation]{Poly(Ethylene Oxide) and SU-8 2002 : Sample Preparation}
+\begin{tabular}{cccc}
+\hline
+\textbf{Sample} & \multicolumn{3}{c}{\textbf{Weight Percent} $wt\%$} \\
+\hline
+{}          & \textbf{SU-8} & \textbf{PEO} & \textbf{TBF} \\
+\textbf{ 1} & 99.50         & 0.00         & 0.50         \\
+\textbf{ 2} & 99.25         & 0.25         & 0.50         \\
+\textbf{ 3} & 99.00         & 0.50         & 0.50         \\
+\textbf{ 4} & 98.75         & 0.75         & 0.50         \\
+\textbf{ 5} & 98.50         & 1.00         & 0.50         \\
+\hline
+density $[\textrm{g} / \textrm{ml}]$
+   & 1.123         & {}           & {}           \\
+\hline
+\end{tabular}
+\label{tab:PEOinSU8}
+\end{table}
+
+\begin{table}[!th]
+\centering
+\caption[Polystyrene in Tetrahydrofuran : Sample Preparation]{Polystyrene in Tetrahydrofuran : Sample Preparation}
+\begin{tabular}{cccc}
+\hline
+\textbf{Sample} & \multicolumn{3}{c}{\textbf{Weight Percent} $wt\%$} \\
+\hline
+{}          & \textbf{THF} & \textbf{PS} & \textbf{TBF} \\
+\textbf{ 6} & 99.25        &  0.25       & 0.50         \\
+\textbf{ 7} & 94.50        &  5.00       & 0.50         \\
+\textbf{ 8} & 89.50        & 10.00       & 0.50         \\
+\textbf{ 9} & 84.50        & 15.00       & 0.50         \\
+\textbf{10} & 79.50        & 20.00       & 0.50         \\
+\textbf{11} & 69.50        & 30.00       & 0.50         \\
+\textbf{12} & 64.50        & 35.00       & 0.50         \\
+\textbf{13} & 59.50        & 40.00       & 0.50         \\
+\hline
+density $[\textrm{g} / \textrm{ml}]$
+   & 0.888        & {}          & {}           \\
+\hline
+\end{tabular}
+\label{tab:PSinTHF}
+\end{table}
+
+\begin{table}[!th]
+\centering
+\caption[Poly(Styrene-co-Butadiene) in 1-Methyl-2-Pyrrolidinone : Sample Preparation]{Poly(Styrene-co-Butadiene) in 1-Methyl-2-Pyrrolidinone : Sample Preparation}
+\begin{tabular}{cccc}
+\hline
+\textbf{Sample} & \multicolumn{3}{c}{\textbf{Weight Percent} $wt\%$} \\
+\hline
+{}          & \textbf{NMP} & \textbf{PSB} & \textbf{TBF} \\
+\textbf{14} & 98.50        &  1.00        & 0.50         \\
+\textbf{15} & 95.50        &  4.00        & 0.50         \\
+\textbf{16} & 91.50        &  8.00        & 0.50         \\
+\textbf{17} & 87.50        & 12.00        & 0.50         \\
+\hline
+density $[\textrm{g} / \textrm{ml}]$
+   & 1.027        & {}           & {}           \\
+\hline
+\end{tabular}
+\label{tab:PSBinNMP}
+\end{table}
+
+\begin{table}[!th]
+\centering
+\caption[Poly(Styrene-co-Butadiene) in Tetrahydrofuran and N,N-Dimethylformamide : Sample Preparation]{Poly(Styrene-co-Butadiene) in Tetrahydrofuran and N,N-Dimethylformamide : Sample Preparation}
+\begin{tabular}{ccccc}
+\hline
+\textbf{Sample} & \multicolumn{4}{c}{\textbf{Weight Percent} $wt\%$} \\
+\hline
+{}          & \textbf{THF} & \textbf{DMF} & \textbf{PSB} & \textbf{TBF} \\
+\textbf{18} & 70.875       & 23.625       &  5.00        & 0.50         \\
+\textbf{19} & 69.000       & 23.000       &  7.50        & 0.50         \\
+\textbf{20} & 67.125       & 22.375       & 10.00        & 0.50         \\
+\textbf{21} & 65.250       & 21.750       & 12.50        & 0.50         \\
+\textbf{22} & 63.375       & 21.125       & 15.00        & 0.50         \\
+\textbf{23} & 59.625       & 19.875       & 20.00        & 0.50         \\
+\textbf{24} & 55.875       & 18.625       & 25.00        & 0.50         \\
+\hline
+density $[\textrm{g} / \textrm{ml}]$
+   & 0.888        & 0.950        & {}           & {}           \\
+\hline
+\end{tabular}
+\label{tab:PSBinTHFnDMF}
+\end{table}
+
+\begin{table}[!th]
+\centering
+\caption[Poly(Styrene-co-alpha-Methylstyrene) in N,N-Dimethylformamide : Sample Preparation]{Poly(Styrene-co-alpha-Methylstyrene) in N,N-Dimethylformamide : Sample Preparation}
+\begin{tabular}{cccc}
+\hline
+\textbf{Sample} & \multicolumn{3}{c}{\textbf{Weight Percent} $wt\%$} \\
+\hline
+{}          & \textbf{DMF} & \textbf{PSMS} & \textbf{TBF} \\
+\textbf{25} & 99.00        &  0.50         & 0.50         \\
+\textbf{26} & 94.50        &  5.00         & 0.50         \\
+\textbf{27} & 89.50        & 10.00         & 0.50         \\
+\textbf{28} & 84.50        & 15.00         & 0.50         \\
+\hline
+density $[\textrm{g} / \textrm{ml}]$
+   & 0.950        & {}           & {}           \\
+\hline
+\end{tabular}
+\label{tab:PSMSinDMF}
+\end{table}
+
+\begin{table}[!th]
+\centering
+\caption[Poly(9-Vinylcarbazole) in Chloroform : Sample Preparation]{Poly(9-Vinylcarbazole) in Chloroform : Sample Preparation}
+\begin{tabular}{cccc}
+\hline
+\textbf{Sample} & \multicolumn{3}{c}{\textbf{Weight Percent} $wt\%$} \\
+\hline
+{}          & \textbf{CHL} & \textbf{PVK} & \textbf{TBF} \\
+\textbf{29} & 99.50        &  0.00        & 0.50         \\
+\textbf{30} & 99.49        &  0.01        & 0.50         \\
+\textbf{31} & 84.50        & 15.00        & 0.50         \\
+\textbf{32} & 79.50        & 20.00        & 0.50         \\
+\textbf{33} & 69.50        & 30.00        & 0.50         \\
+\hline
+density $[\textrm{g} / \textrm{ml}]$
+            & 1.492        & {}           & {}           \\
+\hline
+\end{tabular}
+\label{tab:PVKinCHL}
+\end{table}
+
+\begin{table}[!th]
+\centering
+\caption[Poly(9-Vinylcarbazole) and SU-8 2002 : Sample Preparation]{Poly(9-Vinylcarbazole) and SU-8 2002 : Sample Preparation}
+\begin{tabular}{cccc}
+\hline
+\textbf{Sample} & \multicolumn{3}{c}{\textbf{Weight Percent} $wt\%$} \\
+\hline
+{}          & \textbf{SU-8} & \textbf{PVK} & \textbf{TBF} \\
+\textbf{34} & 99.50         &  0.00        & 0.50         \\
+\textbf{35} & 99.495        &  0.005       & 0.50         \\
+\textbf{36} & 98.75         &  0.75        & 0.50         \\
+\textbf{37} & 94.50         &  5.00        & 0.50         \\
+\textbf{38} & 79.50         & 20.00        & 0.50         \\
+\hline
+density $[\textrm{g} / \textrm{ml}]$
+   & 1.123         & {}           & {}           \\
+\hline
+\end{tabular}
+\label{tab:PVKinSU8}
+\end{table}
+
+\FloatBarrier % keep tables together
+
+SU-8 2002 was obtained from MicroChem (Newton, MA, USA), while Tetrabutylammonium Tetrafluoroborate (TBF) of $99\%$ purity were, Poly(Ethylene Oxide) (PEO), Polystyrene (PS), Poly(Styrene-co-Butadiene) (PSB), Poly(Styrene-co-alpha-Methylstyrene) (PSMS), Poly(9-Vinylcarbazole) (PVK), Tetrahydrofuran (THF), 1-Methyl-2-Pyrrolidinone (NMP), N,N-Dimethylformamide (DMF), and Chloroform (CHL) were obtained from Sigma-Aldrich (Saint Louis, MI, USA).
+PEO has a viscosity-average molecular weight Mv of ~4,000,000, with less than 1000 ppm of Butylated Hydroxytoluene (BHT) as an inhibitor.
+PS has an average molecular weight Mw of ~192,000.
+PSB has a melt index of $6 \textrm{g} / 10 \textrm{min} (200^{\circ}C / 5 \textrm{kg})$, where the butadiene comprises 4 $wt\%$ PSMS has a melt viscosity of $10 \textrm{Pa} \cdot \textrm{s}$ at $161^{\circ}C$.
+PVK has an average molecular weight Mw of ~1,100,000 in powder form.
+THF is anhydrous and contained no inhibitor with $99.9\%$ purity.
+NMP is anhydrous with $99.5\%$ purity.
+DMF is anhydrous with $99.8\%$ purity.
+CHL has $99.5\%$ purity, a melting point of $-63^{\circ}C$, boiling point of $60.5^{\circ}C$, and a density of $1.492 \textrm{g} / \textrm{ml}$ at $25^{\circ}C$.
+CHL contains between 100 to 200 ppm amylenes as stabilizer.
+SU-8 is a high contrast, epoxy-based negative photoresist.
+All of the reactants were used as received.
+
+Samples of 3 militers were prepared with the adecuate amounts of polymer, salt and solvent.
+Solutions were stired at $160 rpm$ for $2 hours$ at $60^{\circ}C$.
+Samples with higher polymer concentrations often required more stirring time to eliminate all polymer aggregates.
+All solutions were left undisturbed for $3 hours$ in 4 ml vials to eliminate bubbles from the solution.
+
+\subsection{Rheological Characterization of polymer Solutions}
+All of the rheological tests were performed in a rotational rheometer (Discovery Hybrid Rheometer DHR, TA Instruments) equipped with a cone-and-plate (CP) geometry (diameter of $60 mm$, angle of $0.9969^{\circ}$, and truncation of $23 \mu m$) in a steel Peltier plate (Figure \ref{fig:solventTrap}a).
+The experiments were conducted at $20^{\circ}C$ and $3 hours$ after polymer solution preparation.
+Flow curve (FC) tests were conducted to obtain viscosity curves in function of the shear rate.
+Analysis were performed at shear rate range from $10^{-3} \textrm{ 1} / \textrm{s}$ to $10^{4} \textrm{ 1} / \textrm{s}$.
+A solvent trap cover (Figure \ref{fig:solventTrap}f) and solvent trap geometry (Figure \ref{fig:solventTrap}a) were used to create a thermally stable vapor barrier, virtually eliminating any solvent loss during the rheological experiments and improving temperature uniformity.
+Distilled water was used to create a seal between the CP geometry and the solvent trap cover (Figure \ref{fig:solventTrap}e).
+
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.50]{./Figures/solventTrap.png}
+\decoRule
+\caption[Rheometer - Solvent Trap Setup]{Rheometer - Solvent Trap Setup}
+\label{fig:solventTrap}
+\end{figure}
+
+Flow curves determine the flow behaviour of a sample by measuring the viscosity as a function of shear rate.
+For shear rates under $~10^{-2.25} \textrm{ 1} / \textrm{s}$ the rheometer was unable to take viscosity measurements, on the other hand for shar rates over $~10^{-3.5} \textrm{ 1} / \textrm{s}$ the measurements are discarded.
+At high shear rates, several factors such as inertial effects, and viscous heating can alter the rheometric measurements \cite{RByron1987, Macosko1994}.
+As the shear rate increases, the centrifugal stresses become large enough to overcome the surface tension stresses that keep the sample within the gap between the geometry and the plate.
+High centrifugal stresses result in the sample being thrown out of the measuring area; a phenomenon known as 'radial migration effect' \cite{Connelly1985}.
+Once the 'radial migration effect' partially ejects the sample, the viscosity measurements are lower than expected due to a drop in torque.
+\cite{Pipe2008}
+
+As depicted in the rheological results in Figures \ref{}, the constant-viscosity (Newtonian-like) behavior before the shear thinning onset was captured.
+In all samples, a noticeable shear-thinning behavior is observed.
+The Carreau–Yasuda model \cite{RByron1987} was fitted to the cone-and-plate  measurements to compute the zero-shear viscosity of each sample.
+
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/plt_FlowCurves_PEOinSU8.png}
+\decoRule
+\caption[Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions}
+\label{fig:plt_FlowCurves_PEOinSU8}
+\end{figure}
 

### 2020-11-20 05_Thesis/THESIS_LaTeX/Appendices/Appendix_CriticalConcentrations.tex
diameter fetching

% Appendix Template

\chapter{Critical Concentrations} % Main appendix title

\label{Appendix_CriticalConcentrations} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PEOinSU8.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions}
\label{fig:c_vs_v_PEOinSU8}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSinTHF.png}
\decoRule
\caption[Viscosity as a function of shear rate for Polystyrene (PS) and Tetrahydrofuran (THF) solutions]{Viscosity as a function of shear rate for Polystyrene (PS) and Tetrahydrofuran (THF) solutions}
\label{fig:c_vs_v_PSinTHF}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSBinNMP.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB) and 1-Methyl-2-Pyrrolidinone (NMP) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB) and 1-Methyl-2-Pyrrolidinone (NMP)}
\label{fig:c_vs_v_PSBinNMP}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSBinTHF-DMF.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB), Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB), Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) solutions}
\label{fig:c_vs_v_PSBinTHF-DMF}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSMSinDMF.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(Styrene-co-alpha-Methylstyrene) (PSMS) and N,N-Dimethylformamide (DMF) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-alpha-Methylstyrene) (PSMS) and N,N-Dimethylformamide (DMF) solutions}
\label{fig:c_vs_v_PSMSinDMF}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PCKinCHL.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and Chloroform (CHL) solutions]{Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and Chloroform (CHL) solutions}
\label{fig:c_vs_v_PCKinCHL}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/c_vs_v_PCKinSU8.png}
\decoRule
\caption[Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 solutions}
\label{fig:c_vs_v_PCKinSU8}
\end{figure}

### 2020-11-20 05_Thesis/THESIS_LaTeX/Appendices/Appendix_ViscosityCurves.tex
diameter fetching

--- 2020-11-20 05_Thesis/THESIS_LaTeX/Appendices/Appendix_CriticalConcentrations.tex
@@
 
-\chapter{Critical Concentrations} % Main appendix title
+\chapter{Flow Curves} % Main appendix title
 
-\label{Appendix_CriticalConcentrations} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}
+\label{AppendixX} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}
 
@@
 \centering
-\includegraphics[width=\textwidth]{./Figures/c_vs_v_PEOinSU8.png}
+\includegraphics[width=\textwidth]{./Figures/plt_PEOwtinSU8.png}
 \decoRule
 \caption[Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions}
-\label{fig:c_vs_v_PEOinSU8}
+\label{fig:plt_PEOwtinSU8}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSinTHF.png}
+\includegraphics[width=\textwidth]{./Figures/plt_PSwtinTHF.png}
 \decoRule
 \caption[Viscosity as a function of shear rate for Polystyrene (PS) and Tetrahydrofuran (THF) solutions]{Viscosity as a function of shear rate for Polystyrene (PS) and Tetrahydrofuran (THF) solutions}
-\label{fig:c_vs_v_PSinTHF}
+\label{fig:plt_PSwtinTHF}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSBinNMP.png}
+\includegraphics[width=\textwidth]{./Figures/plt_PSBwtinNMP.png}
 \decoRule
 \caption[Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB) and 1-Methyl-2-Pyrrolidinone (NMP) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB) and 1-Methyl-2-Pyrrolidinone (NMP)}
-\label{fig:c_vs_v_PSBinNMP}
+\label{fig:plt_PSBwtinNMP}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSBinTHF-DMF.png}
+\includegraphics[width=\textwidth]{./Figures/plt_PSBwtinTHFandDMF.png}
 \decoRule
 \caption[Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB), Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-Butadiene) (PSB), Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) solutions}
-\label{fig:c_vs_v_PSBinTHF-DMF}
+\label{fig:plt_PSBwtinTHFandDMF}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{./Figures/c_vs_v_PSMSinDMF.png}
+\includegraphics[width=\textwidth]{./Figures/plt_PSMSwtinDMF.png}
 \decoRule
 \caption[Viscosity as a function of shear rate for Poly(Styrene-co-alpha-Methylstyrene) (PSMS) and N,N-Dimethylformamide (DMF) solutions]{Viscosity as a function of shear rate for Poly(Styrene-co-alpha-Methylstyrene) (PSMS) and N,N-Dimethylformamide (DMF) solutions}
-\label{fig:c_vs_v_PSMSinDMF}
+\label{fig:plt_PSMSwtinDMF}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{./Figures/c_vs_v_PCKinCHL.png}
+\includegraphics[width=\textwidth]{./Figures/plt_PVKwtinCHL.png}
 \decoRule
 \caption[Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and Chloroform (CHL) solutions]{Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and Chloroform (CHL) solutions}
-\label{fig:c_vs_v_PCKinCHL}
+\label{fig:plt_PVKwtinCHL}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{./Figures/c_vs_v_PCKinSU8.png}
+\includegraphics[width=\textwidth]{./Figures/plt_PVKwtinSU8.png}
 \decoRule
 \caption[Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 solutions}
-\label{fig:c_vs_v_PCKinSU8}
+\label{fig:plt_PVKwtinSU8}
 \end{figure}

### 2020-11-20 05_Thesis/THESIS_LaTeX/Chapters/3.tex
diameter fetching

@@
 %Poly(9-Vinylcarbazole) (PVK)                    & Chloroform (CHL)                                      \\
-%Poly(9-Vinylcarbazole) (PVK) + SU-8 2002 (SU-8) & Cyclopentanone                                        \\
+%Poly(9-Vinylcarbazole) (PVK) + SU-8 2002 (SU-8) & Cyclopentanone (CPO)                                  \\
 %\hline
@@
 Tetrabutylammonium tetrafluoroborate (TBF) was added to all solutions to increase the conductivity of the solution.
-SU-8 contains $71\%$ of cyclopentanone, which acts as the solvent (Figure \ref{fig:su8Components}) \cite{Microchem2012}.
+SU-8 contains $71\%$ of cyclopentanone (CPO), which acts as the solvent (Figure \ref{fig:su8Components}) \cite{Microchem2012}.
 
@@
 
-As depicted in the rheological results in Figures \ref{}, the constant-viscosity (Newtonian-like) behavior before the shear thinning onset was captured.
-In all samples, a noticeable shear-thinning behavior is observed.
-The Carreau–Yasuda model \cite{RByron1987} was fitted to the cone-and-plate  measurements to compute the zero-shear viscosity of each sample.
+As depicted in the rheological results in Figures \ref{fig:plt_PEOwtinSU8}, \ref{fig:plt_PSwtinTHF}, \ref{fig:plt_PSBwtinNMP}, \ref{fig:plt_PSBwtinTHFandDMF}, \ref{fig:plt_PSMSwtinDMF}, \ref{fig:plt_PVKwtinCHL} and \ref{fig:plt_PVKwtinSU8}, the constant-viscosity (Newtonian-like) behavior before the shear thinning onset was captured.
+In all samples, a noticeable shear-thinning behavior is observed with an increase in viscosity with concentration increments.
+The shear-thinning behavior can be interpreted as the alignment of polymer chains to the flow in the direction of the applied shear stress.
+\cite{Floreshernandez2020} The Carreau–Yasuda model (Equation \ref{eqn:carreauYasudaModel}) \cite{RByron1987} was fitted to the cone-and-plate  measurements to compute the zero-shear viscosity of each sample.
+
+\begin{equation}\label{eqn:carreauYasudaModel}
+    \eta = \frac{\eta_0 - \eta_{\infty}}{\left[1 + \left(\kappa \dot{\gamma}\right)^a\right]^{\frac{(1 - n)}{a}}} + \eta_{\infty}
+\end{equation}
+
+Where: $\eta$ is the viscosity, $\dot{\gamma}$ the shear rate, $\eta_{\infty}$ the  infinite shear rate viscosity, $\eta_0$ the zero shear rate viscosity, $\kappa$ is the time constant, $n$ the Power Law index, $a$ the width of the transition region between the zero shear viscosity and the Power Law region.
+The model was fitted to the rheologial data to estimate $\eta_0$.
+Then, $\eta_0$ values are used to create diagrams that describe the effect of polymer concentration on the solution viscosity, as described in Figure \ref{fig:concentrationViscosityPlotExplained}.
+The critical concentrations are calculated from the change in slope in the zero-shear viscosity to concentration relationship as depicted in Figure \ref{fig:criticalConcentrationCalculation} for the PEO in SU-8 solutions.
+Appendix \ref{Appendix_CriticalConcentrations} contains the diagrams of the other polymer-solvent systems.
 
@@
 \centering
-\includegraphics[width=\textwidth]{./Figures/plt_FlowCurves_PEOinSU8.png}
+\includegraphics[width=\textwidth]{./Figures/criticalConcentrationCalculation.png}
 \decoRule
-\caption[Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions]{Viscosity as a function of shear rate for Poly(Ethylene Oxide) (PEO) and SU-8 2002 solutions}
-\label{fig:plt_FlowCurves_PEOinSU8}
+\caption[Estimation of the Critical Concentration of the PEO in SU-8 solutions]{The change in slope is given at 25 $wt\%$ PEO, which suggests that at 25 $wt\%$ the polymer chains are entangled.}
+\label{fig:criticalConcentrationCalculation}
 \end{figure}
+
+\begin{table}[!th]
+\centering
+\caption[Calculated Critical/Spinnable Concentrations for each Polymer-Solvent System]{Calculated Critical/Spinnable Concentrations for each Polymer-Solvent System}
+\begin{tabular}{lllll}
+\hline
+\textbf{Polymer} & \textbf{Molecular Weight $[\textrm{g} \cdot \textrm{mol}]$} & \textbf{Solvent} & \textbf{$c^* [\textrm{wt}\%]$} & \textbf{$\eta_0 [\textrm{Pa} \cdot \textrm{s}]$} \\
+\hline
+PEO  & 4,000,000                  & CPO (SU-8)  & 0.25  & 60.022 \\
+PS   & 192,000                    & THF         & 20.00 & 0.166  \\
+PSB  & 490,000   \cite{Doan2013}  & NMP         & 8.00  & 0.028  \\
+PSB  & 490,000   \cite{Doan2013}  & THF and DMF & 15.00 & 0.092  \\
+PSMS & 2,658,076 \cite{Colby1987} & DMF         & 5.00  & 0.282  \\
+PVK  & 1,100,000                  & CHL         & 15.00 & 41.861 \\
+PVK  & 1,100,000                  & CPO (SU-8)  & 0.75  & 49.657 \\
+\hline
+\end{tabular}
+\label{tab:calculatedSpinnableConcentrations}
+\end{table}
+
+Table \ref{tab:calculatedSpinnableConcentrations} summarizes the calculated critical concentrations for each system.
+In general, the critical concentration $c^*$ has proportional relationship with the polymer molecular weight, as a polymer's molecular weight greatly influences the solution viscosity.
+First, the structure of the polymer chain has an effect on its solubility as the intermolecular interactions between long molecules are stronger and the solvent molecules take longer to diffuse within the polymer aggregates.
+\cite{Ramakrishna2005} Second, the viscosity of a polymer solution will be smaller when a polymer of low molecular weight is dissolved than a solution of the same polymer but of a higher molecular weight.
+\cite{Ramakrishna2005} The molecular weight of the polymer describes the length of the polymer chain, which has an effect on the viscosity of the solution.
+Since the polymer length defines the amount of entanglement of the polymer chains in the solvent, a lower molecular weight shall be compensated by higher concentrations to reach the desired viscosity.
 

### 2020-11-21 05_Thesis/THESIS_LaTeX/Appendices/Appendix_MicroscopyChar.tex
file updates

% Appendix Template

\chapter{Optical Microscopy Characterization of Electrospun Fibers} % Main appendix title

\label{Appendix_MicroscopyChar} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.55]{./Figures/microscopy_peo_su8.png}
\decoRule
\caption[Morphology and Characterization of Electrospun Fibers at Different Voltages : Poly(Ethylene Oxide) (PEO) and SU-8 2002 ]{Morphology and Characterization of Electrospun Fibers at Different Voltages : Poly(Ethylene Oxide) (PEO) and SU-8 2002 }
\label{fig:microscopy_peo_su8}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.55]{./Figures/microscopy_ps_thf.png}
\decoRule
\caption[Morphology and Characterization of Electrospun Fibers at Different Voltages : Polystyrene (PS) in Tetrahydrofuran (THF) ]{Morphology and Characterization of Electrospun Fibers at Different Voltages : Polystyrene (PS) in Tetrahydrofuran (THF) }
\label{fig:microscopy_ps_thf}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.55]{./Figures/microscopy_psb_thf_dmf.png}
\decoRule
\caption[Morphology and Characterization of Electrospun Fibers at Different Voltages : Poly(Styrene-co-Butadiene) (PSB) in Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) ]{Morphology and Characterization of Electrospun Fibers at Different Voltages : Poly(Styrene-co-Butadiene) (PSB) in Tetrahydrofuran (THF) and N,N-Dimethylformamide (DMF) }
\label{fig:microscopy_psb_thf_dmf}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.55]{./Figures/microscopy_pvk_chl.png}
\decoRule
\caption[Morphology and Characterization of Electrospun Fibers at Different Voltages : Poly(9-Vinylcarbazole) (PVK) in Chloroform (CHL) ]{Morphology and Characterization of Electrospun Fibers at Different Voltages : Poly(9-Vinylcarbazole) (PVK) in Chloroform (CHL) }
\label{fig:microscopy_pvk_chl}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.55]{./Figures/microscopy_pvk_su8.png}
\decoRule
\caption[Morphology and Characterization of Electrospun Fibers at Different Voltages : Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 ]{Morphology and Characterization of Electrospun Fibers at Different Voltages : Poly(9-Vinylcarbazole) (PVK) and SU-8 2002 }
\label{fig:microscopy_pvk_su8}
\end{figure}

### 2020-11-21 05_Thesis/THESIS_LaTeX/Chapters/3.tex
file updates

@@
 First, the structure of the polymer chain has an effect on its solubility as the intermolecular interactions between long molecules are stronger and the solvent molecules take longer to diffuse within the polymer aggregates.
-\cite{Ramakrishna2005} Second, the viscosity of a polymer solution will be smaller when a polymer of low molecular weight is dissolved than a solution of the same polymer but of a higher molecular weight.
+\cite{Ramakrishna2005, Floreshernandez2020} Second, the viscosity of a polymer solution will be smaller when a polymer of low molecular weight is dissolved than a solution of the same polymer but of a higher molecular weight.
 \cite{Ramakrishna2005} The molecular weight of the polymer describes the length of the polymer chain, which has an effect on the viscosity of the solution.
 Since the polymer length defines the amount of entanglement of the polymer chains in the solvent, a lower molecular weight shall be compensated by higher concentrations to reach the desired viscosity.
-
-%----------------------------------------------------------------------------------------
-%	SECTION 1
-%----------------------------------------------------------------------------------------
-\section{Effect of aromatic groups in oxygen-free polymers in NFES and Pyrolysis}
-
-\section{\emph{conclude with a collection of potential spunable polymer solutions}}

### 2020-11-21 05_Thesis/THESIS_LaTeX/Chapters/4.tex
file updates

--- 2020-06-04 myThesis/thesis_LaTeX/Chapters/4.tex
@@
 
-\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning, Photopolymerization and Pyrolysis of Polymeric Fibers} % Main chapter title
+\chapter{Fabrication and Characterization of Polymeric Fibers through Near-Field Electrospinning} % Main chapter title
 
@@
 
-%----------------------------------------------------------------------------------------
-%	SECTION 1
-%----------------------------------------------------------------------------------------
-\section{}
+\section{Materials and Methods}
 
-%----------------------------------------------------------------------------------------
-%	SECTION 2
-%----------------------------------------------------------------------------------------
-\section{}
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.50]{./Figures/NFESsetup.png}
+\decoRule
+\caption[NFES experimental setup]{NFES experimental setup. Adapted from \cite{Floreshernandez2020}}
+\label{fig:NFESsetup}
+\end{figure}
 
-%----------------------------------------------------------------------------------------
-%	SECTION 3
-%----------------------------------------------------------------------------------------
-\section{Fabrication and Characterization of Legacy SU-8 carbon fibers}
+The near-field apparatus (Figure \ref{fig:NFESsetup}) is comprised by a high voltage supply (HVS448 3000 V, LabSmith, Livermore, CA, USA), a three-axis stage, syringe pump (Pump 11 Elite, Harvard Apparatus, Cambridge, MA, USA).
+Samples were prepared as per the rheology measurements in Chapter \ref{Chapter:3}.
+Experiments were conducted with 1 milliliter slip-tip insulin syringes with 21 gauge precision tips (Nordson Engineered Fluid Dispensing, Westlake, OH, USA).
+The power supply and 3-axis stage are controlled through a desktop computer, while the syringe pump is controlled manually.
+Fiber depositions were placed on a $\textrm{Si}-\textrm{SiO}_2$ wafer.
+The voltage between the nozzle tip and the collector was varied between $200 [\textrm{V}]$ and $600 [\textrm{V}]$ in increments of $100 [\textrm{V}]$, keeping a constant current of $10 \mu A$.
+For applied voltages under $400 [\textrm{V}]$, the electric field was not strong enough to overcome the surface tension of the polymer solution and initiate the jet.
+To enable the fiber deposition at low voltages, the polymer jet was manually initialed by breaking the surface tension with a sharp glass tip.
+The working distance $L$ and stage velocity was set at a constant values for all the experiments at $0.5 mm$ and $10 mm/s$ respectively.
+The syringe pump was set at a steady flow rate of $0.04 \mu \textrm{L} / \textrm{min}$.
 
-\section{\emph{conclude with fibre morphology before and after pyrolysis. determine best pyrolysis process}}
-%Were the selected candidates electrospunable?
-%Fiber morphology
-%Yield rate
-%Carbon content
-%Conductivity
-%Fiber morphology
+The calculated critical concentrations in Chapter \ref{Chapter:3} (Table \ref{tab:calculatedSpinnableConcentrations}) are used for the fabrication of polymeric fibers.
+One set of experiments was conducted for each polymer-solvent system to study the effect of applied voltage on fiber diameter.
+The morphology of the fibers were characterized with an optical microscope (Correct, Seiwa Optical, Dallas, TX, USA).
+Each sample was measured at 30+ points within the microscope field of view (Appendix \ref{Appendix_MicroscopyChar}).
+
+\section{Results}
+
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/boxplotsFiberDiameter.png}
+\decoRule
+\caption[Diameter of fibres for all the experiments]{Diameter of fibres for all the experiments with varing applied voltage $\Phi_0$}
+\label{fig:boxplotsFiberDiameter}
+\end{figure}
+
+Figure \ref{fig:boxplotsFiberDiameter} shows a dependence of fiber diameter as a function of the applied voltage and confirms what was already noticed in the correlation matrix in Chapter \ref{Chapter:2}, as lower voltages yield fibers with thinner diameters.
+This results verify the electro-spinnability of oxygen-less polymers by NFES into fibers of $1 \mu m$ to $5 \mu m$ in diameter.
+PS presented complications during the NFES process as fibers of this polymer do not adhere onto the substrate making them prone to fracture or substrate abandonment, specially when printing fibers of thin diameters.
+To ease this complication the working distance $L$ can be reduced to let the fibers dry on the surface and prevent complete solidification while traveling the distance $L$.
+The increase in applied voltage can also help with this problem as more material is pulled out of the dispensing needle, however this two fixes will translate into thicker fibers.
+
+The PVK and CHL system was the one that behaved with more similarity as the control sample of SU-8 and PEO.
+Uniform, $700 nm$ diameter fibers were achieved with PVK and CHL at the lowest voltage setting ($200 V$).
+Given the similarities with the control sample, PVK was choosen to replace the PEO to increase the spinnability of SU8.
+Therefore, the PVK in SU-8 system was tested in the same conditions as the previous experiments.
+Both polymers (PEO and PVK) in SU-8 yield parallel results in fiber morphology and in electrospinning preformanc.
+However, at high voltages, the PVK solution produced thinner fibers than those produced by the PEO solution.
+Moreover, as PVK does not contain any additional oxygen content in its structure, adding PVK can be a better alternative to electrospun SU-8 based fibers intended for carbonization as thinner fibers will have better opportunities to survive the pyrolysis process without breaking.
+
+On the other hand, the polymer-solvent systems comprised by Poly(Styrene-co-Butadiene) (PSB) in 1-Methyl-2-Pyrrolidinone (NMP) and Poly(Styrene-co-alpha-Methylstyrene) (PSMS) in N,N-Dimethylformamide (DMF) were unable to yield fibers.
+In the case of the PSB/NMP solutions, a hard shell was formed around the polymer drop at the tip of the nozzle preventing the jet to initiate, which causes clogging.
+Seems that rapid volatilization of NMP is not the case as PSB was successfully electrospun with higher volatile solvents (THF and DMF).
+Notice that vapor pressure of NMP is around $39 \textrm{Pa}$ at $25^{\circ} C$, THF and DMF have vapor pressures of about $19.3 \textrm{kPa}$ at $20^{\circ} C$ and $0.49 \textrm{kPa}$ at $25^{\circ} C$ respectively.
+\cite{ICSCs} On the other hand, PSMS in DMF was not able to produce fibers as the jet was not initiated.
+After noticin that que calculated critical concentration $c^*$ is not spinnable the solutions of 10 and 15 $wt\%$ were also tested in the NFES apparatus with no success.
+The cause of the non-spinnable nature of PSMS can be laid on the fact that PSMS pellets were brittle and capable of making fine PSMS dust with ease, unlike PS and PSB pellets which have an elastic behavior.
+
+\section{Conclusions and Future Work}
+
+A series of experiments were carried out in order to find a correlation between the rheological properties of different polymer solutions in near-field electro-mechanical spinning for carbon structures.
+Flow curve measurement tests where carried out in an oscillatory rheometer to estimate the critical concentrations of various polymer-solvent systems at which they are spinnable by NFES.
+Since the formulation is 0.25 $wt\%$ PEO in SU-8 2002 has been studied in the past and is known to yield good polymer solutions but fails at the pyrolysis, this work intends to find spinnable and pyrolyzable systems as well as a method to discover new spinnable polymer solutions.
+
+From the flow curve measurements, the zero-shear viscosity was estimated using the Carreau-Yassuda model.
+For all solutions, a shear thinning behavious was noticed.
+It was found that the viscosity-concentration plot is a good method to find the critical concentration at which the solution is able to produce fibers through NFES.
+However the method failed at calculating the spinnable concentration of PSMS.
+An significant takeaway is that a polymer does not have elastic properties in the pellet form, it will probably not work as a NFES polymer precursor.
+
+Fibers were fabricated at different applied voltages for each set of solutions in order to very that in NFES fiber diameter increases with increasing applied voltage, whereas the inverse relationship is true for FFES.
+Other parameters such as working distance, stage velocity, nozzle diameter, flow rate were kept constant for all experiments; however, for low applied voltages the jet shall be initialed by manually breaking the polymer drop.
+the thickest average fiber diameter was achieved with the PS in THF system ($\Phi_0 = 600 V$, $D_{fiber} = 5.304 \mu m$) and the thinnest was $0.976 \mu m$ using the PVK in CHL system and an applied voltage of $200 V$.
+It was proved that attainable rehological information can be used to modify the NFES process parameters to yield the desired fiber morphology.
+
+Moreover a data analysis was done on the NFES publications of the last 13 years to identify relationships between fiber diameter and the process parameters.
+For instance, it was confirmed that thin fibers are achived with los polymer concentrations, small nozzle diameters, low applied voltage, slow flow rates and high stage velocities.
+Also, using the collected data and the input of Helgeson's work \cite{Helgeson2007}, an dimensionless analysis was done to predict fiber diameters with easy to get parameters.
+Apart from the work done, this dissertation opens pending research to enable NFES for the fabrication of carbon structures.
+The following lists future work that could be done as a continuation of this thesis.
+
+\begin{itemize}
+\item Helgeson's model \cite{Helgeson2007} was thought to work with far-field electrospinning, hence the deviation of the NFES data from the model trend.
+For an accurate NFES fiber diameter prediction, the mechanical stresses introduced by the moving stage shall be considered in the model (Equation \ref{eqn:ohnesorgeNumberRelationship}).
+\item This work verifies the electro-spinnability of four new formulations, however fibers were not carbonized into carbon structures.
+Further work shall study the pyrolysis process of the proposed fibers to get carbon structures with good electrical conductivity.
+A photo-polymerization process could be introduced before pyrolyzation to increase the order of the molecules and achieve carbon with higher conductivity.
+\item Near-field electrospinning solutions require specific viscosities to initialte a polymer jet.
+The viscosity-concentration plot is a helpful tool to estimate the critical spinnable concentration of a polymer-solvent system.
+However there is room for improvement as this method only considers reological data.
+Other methods could be adopted to better tune other process parameters such as stage velocity, and applied voltage.
+\end{itemize}

### 2020-11-21 05_Thesis/THESIS_LaTeX/main.tex
visco plots in progress
diameter fetching
file updates

@@
 \usepackage[
-    style     = ieee,         % references format style
+    style     = numeric,      % references format style i.e. ieee
     backend   = biber,        % choose the processing program
@@
 \renewcommand\arraystretch{1.5} % Add extra space between table rows
+
+% keeps floats ‘in their place’, preventing them from floating past a
+% \FloatBarrier command into another section
+\usepackage{placeins}
 
@@
 %\addchaptertocentry{\dedicationname} % Add the acknowledgements to the table of contents
+To my parents, who believed in me no matter the outcome. Mom, dad, this work is possible because of you, for always telling me to believe in my dreams.
+
 Thanks for all your unconditional confidence, support, patience, and encouragement. You were my main motivation for pushing through this work.
@@
 And Braulio and Arnoldo for ‘rescuing’ me at those times when I was almost defeated by the laboratory equipment.
+
+I would also like to acknowledge the support from Tecnológico de Monterrey and CONACyT (tuiton and living expenses).
+I also thank Regina Elizabeth Vargas from CIDyT, for the countless hours she helped me with sample characterization.
+
+Finally, I would like to thank my family, who always believed in me.
+I am grateful for their love, caring and patience even in the hardest and restless days.
+They always encourage me to following my dreams, and that feeling will always be dear to me.
 
@@
 
-%\include{Appendices/AppendixA}
-%\include{Appendices/AppendixB}
-%\include{Appendices/AppendixC}
+\include{Appendices/Appendix_ViscosityCurves}
+\include{Appendices/Appendix_CriticalConcentrations}
+\include{Appendices/Appendix_MicroscopyChar}
 

### 2020-12-02 05_Thesis/THESIS_LaTeX/Appendices/Appendix_ImageAnalysisCode.tex
final work done

% Appendix Template

\chapter{Image Analysis Python Source Code} % Main appendix title

\label{Appendix_ImageAnalysisCode} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\begin{lstlisting}[language=Python, caption=Image Analysis Source Code, label=lis:imageAnalysisSourceCode]
# import the necessary packages
import numpy as np
import argparse
import imutils
import cv2 # pip install opencv-python
import matplotlib.pyplot as plt
# import torch
# import torchvision.transforms as T

from IPython.display import display, Image
from easydict import EasyDict
from scipy.spatial import distance as dist
from imutils import perspective
from imutils import contours

def midpoint(ptA, ptB):
    return ((ptA[0] + ptB[0]) * 0.5, (ptA[1] + ptB[1]) * 0.5)

def order_points(pts):
    # sort the points based on their x-coordinates
    xSorted = pts[np.argsort(pts[:, 0]), :]

    # grab the left-most and right-most points from the sorted
    # x-roodinate points
    leftMost = xSorted[:2, :]
    rightMost = xSorted[2:, :]

    # now, sort the left-most coordinates according to their
    # y-coordinates so we can grab the top-left and bottom-left
    # points, respectively
    leftMost = leftMost[np.argsort(leftMost[:, 1]), :]
    (tl, bl) = leftMost

    # now that we have the top-left coordinate, use it as an
    # anchor to calculate the Euclidean distance between the
    # top-left and right-most points; by the Pythagorean
    # theorem, the point with the largest distance will be
    # our bottom-right point
    D = dist.cdist(tl[np.newaxis], rightMost, "euclidean")[0]
    (br, tr) = rightMost[np.argsort(D)[::-1], :]

    # return the coordinates in top-left, top-right,
    # bottom-right, and bottom-left order
    return np.array([tl, tr, br, bl], dtype="float32")

def measureImg(
    orimgname_, imgname_, refIsXval, refImg, refVal, edgeType, 
    minObjArea, invertPimg, Threshold=128, denoise=0):

    #TUNE fineTuning TO MATCH THE REFERENCE OBJECT

    ### IMAGE PRE-PROCESSING
    # load the image
    orimg = cv2.imread(orimgname_)
    img = cv2.imread(imgname_)

    # Image Denoising
    dst = cv2.fastNlMeansDenoisingColored(
        src=img,
        dst=None,
        h=denoise,
        hColor=denoise,
        templateWindowSize=7,
        searchWindowSize=21)

    # Convert to grayscale
    grey = cv2.cvtColor(dst, cv2.COLOR_BGR2GRAY)

    cv2.imwrite('./img_grey.png', grey)

    # define a threshold, 128 is the middle of black and white
    # in grey scale
    thresh = Threshold #256/2

    # assign blue channel to zeros
    binary = cv2.threshold(grey, thresh, 256, cv2.THRESH_BINARY)[1]

    cv2.imwrite('./img_binary.png', binary)

#     # Inverting the colors
#     invert = abs(255 - binary)

    ### IMAGE PROCESSING
    # perform edge detection, then perform a dilation + erosion
    # to close gaps in between object edges
    if invertPimg:
        edged = cv2.Canny(binary, Threshold, Threshold)
    else:
        edged = cv2.Canny(grey, Threshold, Threshold)

    cv2.imwrite('./img_edged.png', edged)

    dilated = cv2.dilate(edged, None, iterations=1)
    eroded = cv2.erode(dilated, None, iterations=1)

    cv2.imwrite('./img_dilated.png', dilated)
    cv2.imwrite('./img_eroded.png', eroded)

    if edgeType == "dilated":
        Pimg = dilated
    elif edgeType == "eroded":
        Pimg = eroded
    else:
        Pimg = edged

    # Show and save image
    print()
    print('Image to Process:')
    imgname='./img_out.png'
    cv2.imwrite(imgname,Pimg)
    display(Image(filename=imgname))

    ### GET IMAGE MEASUREMENTS
    # find contours in the edge map
    cnts = cv2.findContours(
        Pimg.copy(),
        cv2.RETR_EXTERNAL,
        cv2.CHAIN_APPROX_SIMPLE)
    cnts = imutils.grab_contours(cnts)

    # sort the contours from left-to-right and initialize the
    # 'pixels per metric' calibration variable
    (cnts, _) = contours.sort_contours(cnts)

    # if the pixels per metric has not been initialized, then
    # compute it as the ratio of pixels to supplied metric
    # (in this case, inches) to match the reference object
    pixelsPerMetric = None
    i = 0
    for c in reversed(cnts):
        if cv2.contourArea(c) < minObjArea:
            continue

        if i == refImg and pixelsPerMetric is None:
            box = cv2.minAreaRect(c)
            box = cv2.cv.BoxPoints(box)
                if imutils.is_cv2()
                else cv2.boxPoints(box)
            box = np.array(box, dtype="int")
            box = perspective.order_points(box)
            (tl, tr, br, bl) = box
            (tltrX, tltrY) = midpoint(tl, tr)
            (blbrX, blbrY) = midpoint(bl, br)
            (tlblX, tlblY) = midpoint(tl, bl)
            (trbrX, trbrY) = midpoint(tr, br)
            dA = dist.euclidean((tltrX, tltrY), (blbrX, blbrY))
            dB = dist.euclidean((tlblX, tlblY), (trbrX, trbrY))
            if refIsXval:
                pixelsPerMetric = dB*(25400000/refVal)
            else:
                pixelsPerMetric = dA*(25400000/refVal)
        i += 1
        #print(pixelsPerMetric)

    # loop over the contours individually
    i = 0
    for c in reversed(cnts):
        # if the contour is not sufficiently large, ignore it
        if cv2.contourArea(c) < minObjArea:
            continue

        # compute the rotated bounding box of the contour
        orig = orimg.copy()
        box = cv2.minAreaRect(c)        
        box = cv2.cv.BoxPoints(box)
            if imutils.is_cv2()
            else cv2.boxPoints(box)
        box = np.array(box, dtype="int")

        # order the points in the contour such that they appear
        # in top-left, top-right, bottom-right, and bottom-left
        # order, then draw the outline of the rotated bounding
        # box
        box = perspective.order_points(box)
        cv2.drawContours(
            orig,
            [box.astype("int")],
            -1,
            (0, 255, 0),
            1)

        # loop over the original points and draw them
        for (x, y) in box:
            cv2.circle(orig, (int(x), int(y)), 2, (0, 0, 255), -1)

        # unpack the ordered bounding box, then compute the
        # midpoint between the top-left and top-right 
        # coordinates, followed by the midpoint between
        # bottom-left and bottom-right coordinates
        (tl, tr, br, bl) = box
        (tltrX, tltrY) = midpoint(tl, tr)
        (blbrX, blbrY) = midpoint(bl, br)

        # compute the midpoint between the top-left and
        # top-right points, followed by the midpoint between the 
        # top-righ and bottom-right
        (tlblX, tlblY) = midpoint(tl, bl)
        (trbrX, trbrY) = midpoint(tr, br)

        # draw the midpoints on the image
        cv2.circle(orig, (int(tltrX), int(tltrY)),
            2, (255, 0, 0), -1)
        cv2.circle(orig, (int(blbrX), int(blbrY)),
            2, (255, 0, 0), -1)
        cv2.circle(orig, (int(tlblX), int(tlblY)),
            2, (255, 0, 0), -1)
        cv2.circle(orig, (int(trbrX), int(trbrY)),
            2, (255, 0, 0), -1)

        # draw lines between the midpoints
        cv2.line(
            orig,
            (int(tltrX), int(tltrY)),
            (int(blbrX), int(blbrY)),
            (255, 0, 255), 1)
        cv2.line(
            orig,
            (int(tlblX), int(tlblY)),
            (int(trbrX), int(trbrY)),
            (255, 0, 255), 1)

        # compute the Euclidean distance between the midpoints
        dA = dist.euclidean((tltrX, tltrY), (blbrX, blbrY))
        dB = dist.euclidean((tlblX, tlblY), (trbrX, trbrY))

        # compute the size of the object
        dimA = dA / pixelsPerMetric
        dimB = dB / pixelsPerMetric

        # convert inches to nm
        dimA = dimA*25400000
        dimB = dimB*25400000

        # draw the object sizes on the image
        txtcolor=(255, 171, 0)
        cv2.putText(orig, "{:.2f}nm".format(dimB),
                    (int(tltrX - 15), int(tltrY - 10)), 
                    cv2.FONT_HERSHEY_SIMPLEX,
                    0.6, txtcolor, 2, 5)
        cv2.putText(orig, "{:.2f}nm".format(dimA),
                    (int(trbrX + 10), int(trbrY)), 
                    cv2.FONT_HERSHEY_SIMPLEX,
                    0.6, txtcolor, 2)

        # Show and save output image
        print()
        print('Measurements in progress ... ' + str(i))
        print('dimX=' + str(round(dimB,2)) + 'nm;  dimY=' + 
            str(round(dimA,2)) + 'nm;')
        imgname='./img_out.png'
        cv2.imwrite(imgname,orig)
        display(Image(filename=imgname))
        i += 1

help(measureImg);
display(Image(filename='./img/UScoinRef.png'));
measureImg(
    './img/example_01.png',
    './img/example_01.png',
    True, 5, 24260000,
    'eroded',
    100,
    False,
    Threshold=150,
    denoise=15);
\end{lstlisting}

### 2020-12-02 05_Thesis/THESIS_LaTeX/Appendices/Appendix_ReviewTable.tex
final work done

% Appendix Template
\chapter{Appendix NFES Review Table} % Main appendix title

\label{Appendix_NFESreviewTable} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\begin{landscape}
\makeatletter\@twocolumnfalse\makeatother
\begingroup
\makeatletter\if@twocolumn\@ifundefined{theposttbl}{\gdef\TwoColDocument{true}\onecolumn\onecolumn}{}\fi\makeatother \setlength\LTcapwidth{\textheight}
{\tiny
\begin{longtable}{p{.075\textwidth} p{.025\textwidth} p{.080\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} p{.05\textwidth} }
\caption{{Electrospun Polymer Solutions - Solution and Process Parameters} }
\def\arraystretch{1}\\\endfirsthead \hline \noalign{\vskip3pt} \noalign{\textit{Table \thetable\ continued}} \noalign{\vskip3pt} \hline \endhead \hline \noalign{\vskip3pt} \noalign{\textit{\hfill Continued on next page}} \noalign{\vskip3pt} \endfoot \endlastfoot 
Polymer & $Mw$ & Solvent & $\eta_0$ [Pa s] & $K$ [S / m] & $\gamma$ [N / m] & $\rho$ [Kg / $m^3$] & NFES Type & $C_{polymer}$ [wt$\%$] & $D_{nozzle}$ [m] & $Q$ [$m^3$ / s] & Substrate & $L$ [m] & $\Phi_0$ [V] & $v_{stage}$ [m / s] & $D_{fiber}$ [m] & $FiberGap$ [m] & Fiber Morphology & Fiber Structure & Reference \\
\hline
PEO / SU8 & 4e6 & Cyclopentanote & 0.2 - 32e-3 & 8e-3 - 11e-3 & 25 & 1149 - 1318 & xy stage & 0.25 - 1 & 108e-6 &  & Si & 0.1e-3 & 200 &  & 1.2e-6 - 3.49e-6 &  & straight & single & \cite{Aguirre-soto2002} \\
PCL & 80e3 & DCM / Methanol & 7e-3 &  &  & 1218.538 & xy stage & 8  -  20 & 337e-6 & 2.83e-10 & Al &  & 10000 - 20000 &  & 374e-9 - 1.33e-6 &  & straight & cross aligned & \cite{Beachley2011} \\
PCL & 50e6 & CF / DMF & 0.747 &  &  & 1142.62 & melt &  & 514e-6 & 1.39e-11 &  & 0.03 & 12000 & 4.5e-3 - 0.1e-3 & 10.6e-6 - 46.5e-6 &  & coil and straight & single & \cite{Brown2011} \\
PCL & 80e3 & CF / DMF & 747e-3 &  &  & 1142.62 & melt &  & 743e-6 & 1.39e-12 - 5.56e-12 & Al & 0.02 - 0.04 & 6000 - 12000 &  & 4.76e-6 - 33e-6 &  & coil & randomly distributed & \cite{Brown2014} \\
PEO & 300e3 & Water & 0.95 & 400e-6 & 1825.5 & 1000.6 & xy stage & 3 & 0.16e-3 & 8.33e-13 & Si & 0.005 & 1000 & 0.05 - 0.5 & 214e-9 - 344e-9 & 4.21e-5 & meander and straight & single & \cite{Bu2012} \\
MEH - PPV / PEO & 380e3 & Toluene & 573e-6 & 956.e-3 & 17e-3 & 865 & xy stage & 0.08 & 0.26e-3 & 1.39e-11 & SiO2 / Si & 0.5e-3 & 1300 & 0.5 & 1.38e-7 & 8.84e-5 & straight & aligned & \cite{Camillo2013} \\
PEO / SU8 & 4e6 & Cyclopentanote & 0.056 & 9e-3 & 25 & 1215.5 & xy stage & 0.25 & 108e-6 &  & Si & 0.1e-3 & 200 & 0.06 & 4.08e-6 &  & straight & single & \cite{Cardenas2017} \\
PEO & 300e6 & Water & 0.95 & 5.7e-3 & 8886.7 & 1000.6 & xy stage & 3 - 9 & 0.0001 & 2.80E - 14 &  & 0.0005  -  0.001 & 500  -  1200 & 0.12 & 119e-9 - 2.31e-6 &  & straight & mesh & \cite{Chang2008} \\
PVDF & 534e6 & CF / DMF & 0.74 &  &  & 1142.62 & xy stage & 18 &  &  &  & 0.35e-3 &  &  & 1.07e-6 - 2.16e-6 &  & straight & single & \cite{Chang2010} \\
PVDF & 534e3 & CF / DMF & 0.74 &  &  & 1142.62 & xy stage & 18 &  &  &  & 0.35e-3 &  &  & 6.13e-6 - 9.19e-6 &  & straight & aligned & \cite{Chang2011} \\
PU &  & CF / DMF & 0.74 &  &  & 1142.62 & xy stage & 10 &  &  & acrylic &  & 2000 & 0.1 & 9.32E - 06 & 5.22e-5 & straight & aligned & \cite{Choi2017} \\
PLGA &  & CF / DMF & 0.74 &  &  & 1142.62 & PYES &  &  &  & PTFE &  &  &  & 3.5e-7 &  & straight & aligned & \cite{Coppola2014} \\
PLGA & 54e3 & CF / DMF & 0.74 &  &  & 1142.62 & PYES & 25 &  &  & Si & 0.001 &  &  & 0.01e-3 - 0.03e-3 &  & straight & aligned & \cite{Coppola2020} \\
PCL & 83e3 &  &  &  &  &  & melt &  & 0.18e-3 &  & Al & 1.5e-3 & 2900 & 91.67e-3 & 8.17e-7 & 100.6e-6 & straight & mesh & \cite{Dalton2015} \\
PAN &  & CF / DMF & 0.74 &  &  & 1142.62 & rotating drum & 9 &  &  & Si & 1.85e-3 & 35 - 500 &  & 0.13e-6  - 0.349e-6 &  & straight & aligned & \cite{Deng2020} \\
PDO &  & CF / DMF & 0.0162  -  0.74 &  &  & 1142.62 - 1484 & xy stage & 14  -  20 & 340e-6  - 840e-6 & 2.78e-12 - 25.4e-12 & Al & 1.8e-3 - 0.003 & 1200 - 1600 & 0.01 - 0.1 & 3.19e-6 - 25.2e-6 &  & straight & mesh & \cite{E.King2019} \\
PMMA &  & CF / DMF & 0.74 &  &  & 1142.62 & xy stage & 16  -  24 &  & 13.9e-12 - 41.7e-12 &  & 0.0016 - 2.4e-3 & 1200 - 2400 & 0.06 & 1.41e-6 - 5.64e-6 &  & straight & mesh & \cite{Fattahi2017} \\
PEO / SU8 & 4e-6 & CF / DMF & 0.74 &  &  & 1142.62 & xy stage & 0.5 &  &  &  &  &  & 0.02  -  0.06 & 5.98E - 06 &  & straight & aligned & \cite{Flores2017} \\
PEO & 300e3 & Water & 0.95 & 859e-6 & 79e3 & 1e3 & xy stage & 8 & 0.4e-3 &  & Si & 0.5e-3 & 1100 & 0.2 & 7.4e-7 & 2e-5 & straight & single & \cite{Fuh2011} \\
PEO / Chitosan & 900e3 & DMSO & 2.1e-3 & 62e-3 & 4.48 & 1095.6 & xy stage & 5 & 0.4e-3 & 2.8e-14 &  & 0.5e-3 - 1e-3 & 800 - 1200 &  & 282e-12 - 785e-12 & 0.1e-3 & curved & aligned & \cite{Fuh2012} \\
PEO / Chitosan & 900e3 & CF / DMF & 0.74 &  &  & 1142.62 & xy stage & 5 &  &  & PPy & 0.5e-3 & 800 & 0.2 & 7.3e-7 & 0.02e-3 - 0.1e-3 & straight & mesh, randomly distributed and aligned & \cite{Fuh2013} \\
PVDF & 534e-3 & CF / DMF & 0.74 &  &  & 1142.62 &  & 16 &  &  &  & 1.2e-3 & 1440 &  & 907e-9 - 2.91e-6 &  & straight & aligned & \cite{Fuh2015} \\
PEO & 300e-3 & Water / Ethanol & 1.048316 & 2.6e-3 - 7.8e-3 & 11886.69 & 894.31 & xy stage & 20 & 4e-5 &  & Si & 1e-3 & 1700 & 0.05 - 0.35 & 816e-9 - 2.82e-6 &  & meander, coil and straight & single & \cite{GaofengZheng2010} \\
PAN & 150e3 & DMF & 0.94 &  &  & 802 & rotating drum & 11 & 159e-6 &  & Si & 0.7e-3 - 0.01 & 400 - 900 &  & 2.53e-6 &  & straight & aligned & \cite{George2020} \\
POSS - PCL - PCU & 2000 & CF / DMF & 0.74 & 10.2e-3 & 32235.64 & 1142.62 & xy stage & 20 & 750e-6 & 1.67e-11 &  & 0.5e-3 & 9000 & 0.01 & 18.7e-6 - 690e-6 & 352e-6 - 0.48e-3 & meander & mesh & \cite{Gupta2007} \\
PCL & 80e3 & CF / DMF & 0.74 &  &  & 1142.62 & xy stage &  & 912e-6 &  &  & 0.005 & 3000 & 0.05 & 108.3e6 - 150.5e-6 & 0.001 & straight & mesh & \cite{He2018} \\
PEtOx & 50e3 &  &  &  &  &  & melt &  & 160e-6 - 337e-6 &  & Al & 0.003  -  0.007 & 3000  -  7000 & 3.33e-3 & 12.5e-6 - 59.1e-6 &  & straight & cross aligned & \cite{Hochleitner2014} \\
PLA / PEG & 72000 &  &  &  &  &  & melt &  & 337e-6 &  & Si & 3.5e-3 & 4000 & 83.3e-3 & 3.1e-5 &  & straight & mesh & \cite{Hochleitner2017} \\
PEO & 300e3 & CF / DMF & 0.744 & 6.12e-5 & 34838.96 & 1142.62 & xy stage & 6 &  & 2e-11 &  & 0.005 - 7.5e-3 & 900 & 0.05 - 0.4 & 212e-9 - 352e-9 & 5e-6 & straight, coil, and meander & single and aligned & \cite{Huang2015} \\
PEO & 30000 & Water / Ethanol & 1.04 & 524.3e-6 & 11906.09 & 894.31 & xy stage & 8 & 210e-6 & 8.33e-12 & Si & 2e-3 & 2000 & 0.001 - 0.02 & 3.27e-6 - 9.77e-6 &  & meander & aligned & \cite{Jiang2018} \\
PEO & 100e3 & CF / DMF & 0.74 & 736.4e-6 & 4729.5 & 1142.62 & rotating drum & 10 &  &  & Si & 7.56e-3 - 12.5e-3 & 2000 & 0.11 - 1.70 & 101e-9 - 201e-9 &  & straight & aligned & \cite{Kameoka2003} \\
PEO & 900e3 & CF / DMF & 0.77 &  &  & 1142.62 & xy stage & 5 - 30 &  &  &  &  & 4500 &  & 150e-9 &  & coil & randomly distributed & \cite{Kameoka2003a} \\
PVDF & 534e3 & Acetone / DMSO & 0.16 &  &  & 943.42 & auxiliary electrodes & 17 & 0.1e-3 & 3.89e-12 & Paper & 750e-6 & 1900 & 0.01 &  &  & meander & single & \cite{Kim2018} \\
PCL & 50e3 & CF & 0.55 &  &  & 1483.24 & xy stage & 18.3 & 250e-6 &  &  &  & 6000 - 12000 & 5e-3  -  7.5e-3 & 33.4e-6 - 103e-6 &  & coil & single & \cite{Kolan2018} \\
PCL & 80e3 & CF & 0.55 & 997e-6 & 1978.8 & 1483.24 & xy stage & 8.8 & 0.2e-3 & 2.78e-11 & Si & 0.07 & 25e3 & 2e-3 - 0.5 &  &  & coil and meander & single & \cite{Lee2012} \\
PVDF & 534e3 & CF / DMF & 0.74 & 1.47e-5 & 4733.12 & 1142.62 & xy stage & 12 &  & 2.22E - 11 & Si & 5e-3 & 1200 & 0.03 & 4.23e-5 & 263.1e-6 & curved & mesh & \cite{Lei2015} \\
PVP & 1300e3 & CF / DMF & 0.73 & 2.94e-5 & 4737.7 & 1142.62 & xy stage & 17.4 & 510e-6 & 8.33e-11 & Si / SiO2 & 1e-3 & 50 & 0.8 & 1.7e-7 &  & straight & mesh & \cite{Lim2019} \\
PVDF & 534e-3 & Acetone / DMSO & 0.162 &  &  & 943.42 & xy stage & 18 & 0.3e-3 &  &  &  & 900  -  1200 & 0.03  -  0.09 & 2.54e-6 - 89.6e-6  &  & straight & aligned & \cite{Liu2013} \\
PVDF & 534e-3 & Acetone / DMSO & 0.162 &  &  & 943.42 & rotating drum & 18 & 381e-6 &  & Si & 0.5e-3 & 10e3 - 16e3 &  & 205e-9 - 1.45e-6 &  & straight & cross aligned & \cite{Liu2014} \\
PVDF & 534e3 & Acetone / DMSO & 0.16 &  &  & 943.42 & xy stage & 16  -  20 & 260e-6 & 1.67e-11 & Si & 1e-3 &  & 0.07 & 0.5e-6 - 20e-6 &  & straight & cross aligned & \cite{Liu2015a} \\
PVDF / PVA / SWCNT & 534e3 & Acetone / DMSO & 0.1 & 0.003 & 270 & 94 & xy stage & 21 & 159e-6 &  & paper & 0.001 & 1000  -  1800 & 0.01  -  0.09 & 3.99e-6  -  11.5e-6 & 0.1e-3 & straight & aligned & \cite{Luo2016} \\
PEO & 4e6 & Water & 0.95 & 0.57e-3 & 8892.6 & 1000.62 & xy stage & 2 & 210e-6 & 2.78e-13 & C /Si & 0.001 & 200  -  400 & 0.02 - 0.08 & 50.7e-9 - 423e-9 &  & straight & aligned and single & \cite{Madou2011} \\
PVK & 1100e3 & Styrene & 696e-6 & 6.31 & 3.6e-3 & 1300 & xy stage & 3.96 & 0.1e-3 & 8.33e-12 & Si / SiO2 & 2.5e-3 & 3500 & 133e-3 - 0.15 & 65e-9 - 707e-9 & 5e-5 & straight & aligned & \cite{Min2013} \\
PEO & 200e3 & Water / Ethanol & 1.04 & 523e-6 & 11907.5 & 894.3 & xy stage & 14 & 250e-6 & 3e-12 & Si & 5.25e-3 & 1600 & 0.15 & 3e-7 & 0.3e-3 & meander & aligned & \cite{Nagle2019} \\
PVDF & 534e3 & CF / DMF & 747e-3 &  &  & 1142.62 & rotating drum & 10  -  18 &  &  & Cu &  & 2000  -  10000 & 523.6e-3  -  2.6 & 35.3e-6  -  51.9e-6 &  & straight & aligned & \cite{Pan2014} \\
PVDF & 534e3 & CF / DMF & 747e-3 &  &  & 1142.62 & coaxial & 15  -  19 & 630e-6 &  & Cu &  & 8000  -  16000 & 0.53 - 2.62 & 10.3e-6 - 45.9e-6 &  & straight & aligned & \cite{Pan2015} \\
PCL & 45028 & CF / DMF & 0.74 &  &  & 1142.62 & xy stage & 25  -  70 & 0.3e-3 - 0.6e-3 & 0  -  1.21e-9 &  & 5e-3  -  0.01 & 3500  -  3900 & 0.2 & 58.7e-6 - 190e-6 &  & straight & single & \cite{Parajuli2016} \\
PEO / NaCl &  & CF / DMF & 0.7474335 &  &  & 1142.62 & xy stage & 0.1  -  1 &  &  &  &  &  &  & 92e-9  -  239e-9 &  & straight & aligned & \cite{Park2020} \\
PEO & 1000e3 & Water / Ethanol & 1.04 & 339e-6 & 11923.7 & 894.1 & xy stage & 4 & 160e-6 & 83.3e-12 - 25e-9 &  & 0.003 & 1500 &  & 5.74e-6  -  14.7e-6 &  & straight & mesh & \cite{Ru2014} \\
PEO / TiO2 & 300e3 & CF / DMF & 747e-3 & 618e-6 & 363503.0357 & 1142.62 & xy stage & 5.44 &  & 5.56e-12 & Si3N4 & 0.5e-3 & 1100 &  & 5e-7 & 4e-5 & straight & aligned & \cite{Ruggieri2013} \\
PIB &  &  &  &  &  &  & rotating drum & 15 & 360e-6 & 2e-11 &  &  & 12000 &  & 4.2e-7 &  & straight & cross aligned & \cite{Sarkar2007} \\
PS &  &  &  &  &  &  & rotating drum & 20 & 0.36e-3 & 1e-11 &  &  & 11000 &  & 4.1-7 &  & straight & cross aligned & \cite{Sarkar2007} \\
PEO / FeAl NP &  &  &  &  &  &  & rotating drum & 6 & 0.36e-3 & 1.17e-11 &  &  & 9500 &  & 4e-7 &  & straight & cross aligned & \cite{Sarkar2007} \\
PEO / Au NP &  &  &  &  &  &  & rotating drum & 10 & 0.36e-3 & 1.67e-11 &  &  & 9300 &  & 3.9e-7 &  & straight & cross aligned & \cite{Sarkar2007} \\
PEO / SWCNT &  &  &  &  &  &  & rotating drum & 8 & 360e-6 & 1.33e-11 &  &  & 9300 &  & 3.8e-7 &  & straight & cross aligned & \cite{Sarkar2007} \\
PEO &  &  &  &  &  &  & rotating drum & 8 & 360e-6 & 1.33e-11 &  &  & 9500 &  & 3.7e-7 &  & straight & cross aligned & \cite{Sarkar2007} \\
PEO / PPy & 5e6 & DMF / Acetone & 633.4e-3 &  &  & 948.8 & xy stage & 8 & 2.5e-5 &  &  &  & 1000 &  & 0.4e-6  -  0.7e-6 & 265e-6 & straight & aligned & \cite{Shen2016} \\
PEO & 400e3 & Water & 958.2e-3 & 286e-6 - 11e-3 & 2225.7 - 35611.8588 & 1000.62 & xy stage & 10 & 108e-6 &  &  & 750e-6 & 500  -  700 & 15e-3 & 130e-9  -  220e-9 &  & straight, coil and meander & single & \cite{Shin2018} \\
PEO & 4000e3 & Water & 958e-3 &  &  & 1000.62 & xy stage & 1.5 & 108e-6 &  &  &  & 650 & 0.2e-3 - 0.8e-3 & 94e-9  -  933e-9 &  & meander, coil and meander & single & \cite{Shin2019} \\
PS &  & TCB & 2.05e-3 &  &  & 1449.6 & xy stage & 5 & 2e-6 &  & Si & 20e-6  -  40e-6 & 400  -  500 & 2e-3 & 57.3e-9  -  167e-9 &  & straight & single & \cite{Song2015} \\
PCL & 80e3 & CF / DMF & 0.73 & 735e-6 & 4729.9 & 1142.62 & aligned needles & 10 & 337e-6 & 1.39e-10 & Si & 0.06 & 15000 &  & 1.21e-7 &  & straight & randomly distributed & \cite{Sonntag2020} \\
PEU &  & CF / DMF & 747e-3 &  &  & 1142.62 & touch spinning & 5 &  & 8.33e-11 &  &  &  &  & 3.28e-7 &  & straight & cross aligned & \cite{Strauss2019} \\
PCL &  & CF / DMF & 747e-3 &  &  & 1142.62 & touch spinning & 8 &  & 8.33e-11 &  &  &  &  & 3.26e-7 &  & straight & cross aligned & \cite{Strauss2019} \\
PEO / NT &  & CF / DMF & 0.74 &  &  & 1142.62 & touch spinning & 0.5 &  & 8.33e-11 &  &  &  &  & 3.2e-7 &  & straight & cross aligned & \cite{Strauss2019} \\
PEO &  & CF / DMF & 0.7474335 &  &  & 1142.62 & touch spinning & 0.5 &  & 8.33e-11 &  &  &  &  & 2.98e-7 &  & straight & cross aligned & \cite{Strauss2019} \\
PEO & 300e3 & CF / DMF & 0.7 &  &  & 1142.2 & xy stage & 3 &  &  & Si and SiO2 & 0.5e-3  -  3e-3 & 598  -  1255 & 0.2 & 3e-7 & 2.5e-5 & meander & single & \cite{Sun2006a} \\
PEO & 2000e3 & CF / DMF & 0.72 &  &  & 1142.6 & multinozzle xy stage & 5 &  & 3.33-11 &  & 2e-3  -  6e-3 & 1700  -  2700 &  &  & 5.47e-3 & straight & aligned & \cite{Wang2015} \\
PEO & 2e6 & Water & 0.92 &  &  & 1000.62 & multinozzle xy stage & 5 & 180e-6 & 3.33e-12 &  & 3e-3  -  5e-3 & 2300  -  2800 & 0.02 &  & 3.03e-3 & straight & aligned & \cite{Wang2017} \\
PEO & 2e6 & Water & 0.95 & 574.931e-3 & 8906.09 & 1000.62 & multinozzle xy stage & 5 & 180e-6 &  & SST & 4e-3 & 2500 & 0.02 & 6.23e-6 & 0.025 & straight & aligned & \cite{Wang2018a} \\
PEO & 4e6 &  &  &  &  &  & xy stage & 2 & 150e-6 &  & Si & 2e-3 & 1250 &  &  & 7e-6  -  74e-6 & meander & aligned & \cite{Xu2014} \\
PEO & 2e-6 & CF / DMF & 0.74 &  &  & 1142.62 & xy stage & 5 &  & 3.33e-12 &  & 2.5e-3  -  4e-3 & 1900  -  2700 & 0.05  -  0.3 & 696e-9  -  5.08e-6 &  & meander & aligned & \cite{Xu2019} \\
Gelatin &  & CF / DMF & 0.74 &  &  & 1142.62 & xy stage & 11 &  &  & PDMS & 1.25e-3 & 1000 &  & 9.02e-7 & 4e-5 & straight & aligned & \cite{Xue2014} \\
PEO & 900e3 & Water & 0.98 & 572.82e-6 & 8923.275983 & 1000.62 & xy stage & 5 & 110e-6 & 833e-15  -  2.78e-12 & PS & 0.5e-3  -  1.5e-3 & 1000  -  1300 & 8.77e-3  -  0.166 & 671e-9  -  19.9e-6 &  & straight & aligned & \cite{Yang2019} \\
PCL & 80e3 &  &  &  &  &  & xy stage &  & 260e-6 & 833e-15  -  2.78e-12 & PE & 2e-3 & 3000 &  & 6.8e-6 &  & meander & aligned & \cite{You2017} \\
PS & 240e3 & CF / DMF & 0.74 & 3.08e-3 & 910845.5 & 1142.62 & xy stage & 30 & 455e-6 & 0 & Au & 0.2e-3 & 2400 & 15e-3 & 7.81e-6 &  & straight & mesh & \cite{Yousefi2019} \\
PEO & 2e6 & CF / DMF & 0.75 & 735e-6 & 4749.86 & 1142.62 & multinozzle xy stage & 8 &  &  &  & 3e-3 & 2500 & 80e-3 & 2.89e-6  -  10e-6 & 2.06e-3 & straight & aligned & \cite{Zhang2019} \\
PEO & 300e3 & Water / Ethanol & 1.04 & 10.48e-3 & 11917.213 & 894.313 & xy stage & 18 & 4e-5 &  & Si & 1e-3 & 1700 & 0.36 & 4.89e-7 &  & coil & single & \cite{Zheng2010} \\
PEO & 300e3 & Water / Ethanol & 1.04 & 524e-6 & 11910.45 & 894.3 & xy stage & 14 & 210e-6 & 1.39e-11 & PET & 2e-3 & 500  -  4000 & 0.02  -  1 & 17.4e-6  -  65.8e-6 & 0.3e-3 & meander & aligned & \cite{Zheng2014} \\
PCL & 90e3 & CF / DMF & 0.74 & 7.37e-5 & 4735.564517 & 1142.62 & xy stage & 10 & 410e-6 & 16.7e-12  -  83.3e-12 & Si / Al & 1e-3  -  3e-3 & 800  -  4000 & 0.03 & 7.99e-6  -  91.5e-6 &  & straight & single & \cite{Zhou2011} \\
PEO & 2e6 & Water & 0.958 & 572e-6 & 8896.48 & 1000.62 & auxiliary electrodes & 4 & 160e-6 &  & Si & 4e-3 & 0  -  5000 & 5e-3 & 7.06e-6  -  13.6e-6 &  & meander and straight & single & \cite{Zhu2016} \\
\end{longtable}
}
\endgroup
\makeatletter\@ifundefined{TwoColDocument}{}{\twocolumn}\makeatother 
\end{landscape}

### 2020-12-02 05_Thesis/THESIS_LaTeX/Chapters/1.tex
visco plots in progress
final work done

@@
 
-Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
+Carbon nano-materials are subjected of great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
 Carbon nano-materials are suitable for catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing, and cancer detection.
-Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity.
+\cite{Kenry2017, BaudritJ2017} Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity.
 \cite{McCreery2008, Geim2011, Zhu2010, Katsnelson2008, Li2008, Geim2007, Geim2009, Siddiqui2019}
 
-This document bestows a thesis project to perform research to engineer a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner.
-The research intends to involve several manufacturing processes such as near field electrospinning, photo-polymerization, pyrolization, and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials.
+This document bestows a thesis project to perform research to engineer a polymer solution to contribute towards the long-term goal of achieving mass scale manufacturing of high conductive glass-like carbon nano-wires with a control of the jet diameter in an inexpensive, continuous, simple and reproducible manner.
+This thesis discusses several manufacturing processes such as near field electrospinning, photo-polymerization, pyrolization, and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials.
 \cite{Cardenas2017} See Figure \ref{fig:fabricationFlowChart}.
@@
 Nanotechnology has led to the study of different polymer patterning techniques to integrate carbon nano-wires structures.
-One technique is known as far-field electrospinning (FFES), a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibres which are then pyrolyzed at high temperatures.
+One technique is known as far-field electrospinning (FFES), a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibres which can then be pyrolyzed.
 One sub-technique derived from electrospinning is near-field electromechanical spinning or NFEMS.
-Unlike FFES, NFEMS has proved to deliver high control in patterning polymeric nano-fibres.
+Unlike FFES, NFEMS has proved to deliver sufficient spatial control for patterning polymeric nano-fibres.
 \cite{Cardenas2017}
 
-The proposal is to continue the previous work done in regards to the synthesis of carbon nano-wires.
-Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist.
-\cite{Cardenas2017, Flores2017} This work is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by NFEMS, photo-polymerized and pyrolyzed into conducting carbon nano-wires.
-The polymer solutions described by Cárdenas and Flores \cite{Flores2017, Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.
+The present work was proposed to continue the work done by others \cite{Cardenas2017, Flores2017} in regards to the synthesis of carbon nano-wires.
+Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and two-photon polymerization with a photoresist.
+\cite{Cardenas2017, Flores2017} This work is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by NFEMS to yield polymer fibers than can hopefully be crosslinked by UV light and the pyrolyzed and pyrolyzed into conducting carbon nano-wires.
+The polymer solutions described by Cárdenas and Flores \cite{Flores2017, Cardenas2017} were used as benchmarks and starting points for the present studies.
 
-Traditional near-field electrospinning or NFES allows large scale manufacturability combined with spatial control of material deposition.
-\cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation, resulting in limited control for nano-fiber patterning in traditional NFES processes.
-Madou et al.
-\cite{Madou2011} conclude that the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.
+Traditional near-field electrospinning or NFES allows large-scale manufacturing combined with spatial control of material deposition.
+\cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation, this seems to contradict the previous sentence.
+\cite{Madou2011} concluded that the state-of-the-art fabrication processes for polymer nano-fibers are still lacking in terms of precision, cost, speed and throughput.
 
@@
 
-Nanotechnology ability to control and piece together materials at the nano-scale has enabled the development of various carbon nano-materials and carbon nano-structures, such as nano-dots, nano-fibres, nano-tubes and nano-wires.
-\cite{Posthuma-Trumpie2012, Zhang2009, DeVolder2011, Cao2011} This chapter bestows on the applications at the micro-scale and nano-scale levels, as well as the current research of carbon-based nano-materials (CBNs).
+Nanotechnology's ability to control and piece together materials at the nano-scale has enabled the development of various carbon nano-materials and carbon nano-structures, such as nano-dots, nano-fibres, nano-tubes and nano-wires.
+\cite{Posthuma-Trumpie2012, Zhang2009, DeVolder2011, Cao2011} This section focuses on the applications at the micro-scale and nano-scale levels, as well as the current research of carbon-based nano-materials (CBNs).
 
@@
 
-Carbon is a versatile element capable to form a number of bonds with other elements or with itself.
-Cabon-based nano-materials (CBNs) exist in diverse forms, depending on the precise values of each degree of freedom that specify the material proclivity at multiple scales.
+Carbon is a versatile element capable of forming a number of bonds with other elements or with itself.
+Cabon-based nano-materials (CBNs) exist in diverse forms, depending on the precise values of each degree of freedom that specify the material properties at multiple scales.
 Hybridization, crystallization, percolation, anisotropy, porosity, impurities and imperfections are some of the relevant features that determine the CBN set of properties.
 The combination of these features at the micro- and meso-scale burst a variety of macro-scale properties that comprise the CBN fingerprint (\ref{fig:CBNfingerprint}).
-The interminable collection of possible CBN fingerprints range from soft, conductive lubricants to very hard, low conductivity solids; and from black colour, bulks to transparent, disordered thin films.
-\cite{McCreery2008} Figures \ref{fig:carbonAllotropes} and \ref{fig:carbonAllotropesDiagram} shows the existence of different types of allotrope as carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, assembling different types of allotropes.
+The interminable collection of possible CBN fingerprints range from soft, conductive lubricants to very hard, low conductivity solids \cite{Hugh1994}; and from black colour, bulks to transparent, disordered thin films.
+\cite{McCreery2008} Figures \ref{fig:carbonAllotropes} and \ref{fig:carbonAllotropesDiagram} show the existence of different allotropes based on carbon orbitals which have the ability to hybridize in sp1, sp2 and sp3 configurations, assembling different carbon allotropes.
 
@@
 \decoRule
-\caption[Carbon sp-hybrid Nano-materials]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
+\caption[Carbon sp-hybrid Nano-materials]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon-based materials such as fullerenes, porous carbon and glass-like carbon.}
 \label{fig:carbonAllotropes}
@@
 On the other hand, an 'open pore' refers to a void which is connected to the outer surface of the solid, in other words a 'open pore' is a 'closed pore' with an opening to the external surface.
-\cite{Marsh1989} Figure \ref{fig:carbonAllotropesPorosityNOrder} shows a classification of carbon allotropes according to their porous content.
+\cite{Marsh1989} Figure \ref{fig:carbonAllotropesPorosityNOrder} shows a classification of carbon allotropes according to their porosity.
 
@@
 Furthermore, porosity negatively affects the mechanical properties like strength and elastic modulus as it reduces the volume in which stresses are distributed.
-Moreover, stresses are concentrated at the pores which makes the material prone to mechanical failure.
+\cite{Hugh1994} Moreover, stresses are concentrated at the pores which makes the material prone to mechanical failure.
 \cite{Marsh1989, Hugh1994}
@@
 
-As depicted in Figure \ref{fig:carbonAllotropesDiagram}, carbon nano-fibers (CNFs) have been classified as linear, sp2-based structures.
+As depicted in Figure \ref{fig:carbonAllotropesDiagram}, carbon nano-wires (CNFs) have been classified as linear, sp2-rich structures.
 \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015, Vajtai2013} Nano-fibers own good electrical, optical and mechanical characteristics, however those properties are highly dependent on the morphology of the fibers.
-\cite{Dresselhaus2007} The material properties of 1D nano-structures depend on fiber diameter, porosity, crystallization degree and crystallization orientation.
+\cite{Dresselhaus2007} The material properties of 1D nano-structures depend on fiber diameter, porosity, crystallinity degree and crystallite orientation.
 Consequently, the fabrication parameters and environment conditions have an impact on the reproducibility of high quality fibers.
@@
 
-sp2 carbon nano-wires have been used for the improvement of power density and specific energy in lithium-ion batteries.
+Carbon nano-wires have been used for the improvement of power density and specific energy in lithium-ion batteries.
 \cite{Frackowiak2002, Endo2000, Winter1998} Authors posit that the performance and capacity of Li-ion batteries depend on the CNF structure and texture.
-Through the right combination of electrospinning and carbonization parameters, electrically conductive, mechanically tough and with thin diameter fibers have been achieved by Yoon et al.
+Through the right combination of electrospinning and carbonization parameters, electrically conductive, mechanically tough and low diameter fibers have been achieved by Yoon et al.
 \cite{Yoon2004}.
@@
 On the other hand, the low reactivity and unique morphology of CNFs make them promising catalyst supports for metal nano-particles.
-\cite{Choi2002, Li2002, Planeix1994} It is well known that the morphology and nano-structure of the supporting material are the main factors that prevent agglomerations of nano-particles.
+\cite{Choi2002, Li2002, Planeix1994} It is well known that the morphology and nano-structure of the supporting material are the main factors that prevent agglomeration of nano-particles.
 \cite{RomanMartinez1995, Serp2008} Moreover, in bone tissue scaffold applications, collagen is the most popular scaffold.
@@
 Typically, carbon nano-fibers (CNFs) are synthesized by a combination of a patterning process and a pyrolysis process.
-CNFs fabricated by electrospinning of polymer solutions with electrostatic forces.
 Electrospun CNFs have characteristics such as high surface area, thin morphology with nano-scale diameters.
@@
 implemented TPP and conventional UV lithography to study the fabrication of CNFs within carbon micro-electromechanical systems (C-MEMS).
-The fabrication of these kind of carbon devices has been previously reported for teachniques, such as electrospinning and photoresist patterning by photolithography using SU-8.
+The fabrication of these kind of carbon devices has been previously reported for techniques, such as electrospinning and photoresist patterning by photolithography using SU-8.
 The typical fabrication process of C-MEMS begins with a spin-coating of a photoresist unto a substrate (typically SU-8), followed by patterning techniques with UV-exposure by photolithography.
-Followed by the development of the desired features solvent.
+Followed by the development of the desired features.
 Finally, the device is carbonized in a pyrolysis furnace in an inert environment.
@@
 
-Near-field electrospinning can be regarded as complementary technique, by which polymeric nanofibers can be produced, since the structural geometries created photolithography are restricted by the diffraction limit.
+Near-field electrospinning can be regarded as a complementary technique, by which polymeric nanofibers can be produced, since the structural geometries created by photolithography are restricted by the diffraction limit.
 \cite{Pramanick2018a, Okazaki1991} SU-8 is designed to produce vitrous carbon structure via photolithography, it is not design for electrospinning procedures as it lacks the right viscosity and solution conductivity.
@@
 TBF was added to increase the solution conductivity and PEO provides the required viscosity.
-Both additions are required to yield smooth solution flow during electrospinning.
+Both additives are required to yield smooth solution flow during electrospinning.
+Figure \ref{fig:su8Components} illustrates the ingredients that comprise the SU-8 formulation.
 
-\begin{table}[ht]
+\begin{table}[!th]
 \centering
-\caption[Prepared Polymer Solutions in Previous Work]{Prepared Polymer Solutions in Previous Work \cite{Cardenas2017, Flores2017}}
+\caption[Polymer Solutions from Previous Work]{Polymer Solutions from Previous Work \cite{Cardenas2017, Flores2017}}
 \begin{tabular}{cccc}
@@
 {} & \textbf{SU-8} & \textbf{PEO} & \textbf{TBF} \\
-1 & 99.50 & 0.25 & 0.25 \\
+1  & 99.25         & 0.25         & 0.50         \\
 2  & 99.00         & 0.50         & 0.50         \\
-3 & 98.50 & 0.75 & 0.75 \\
-4 & 98.00 & 1.00 & 1.00 \\
+3  & 98.75         & 0.75         & 0.50         \\
+4  & 98.50         & 1.00         & 0.50         \\
 \hline
@@
 
-The thinnest fibers achieved by Cardenas \cite{Cardenas2017} were achieved with sample 1 of Table \ref{tab:previousPreparedPolymerSolutions}, with the following characteristics: a) Fiber yield rate of $81\%$; b) Fiber diameter before pyrolysis of $4.966 \mu m$; c) Fiber diameter after pyrolysis of $204 nm$; d) Average fiber length of $60.5 ± 4.3 \mu m$; and e) Fiber electrical resistance from $407 K \Omega$ to $1.727 M \Omega$.
+The thinnest fibers fabricated by Cardenas \cite{Cardenas2017} were achieved with sample 1 of Table \ref{tab:previousPreparedPolymerSolutions}, with the following characteristics: a) Fiber yield rate of $81\%$; b) Fiber diameter before pyrolysis of $4.966 \mu m$; c) Fiber diameter after pyrolysis of $204 nm$; d) Average fiber length of $60.5 ± 4.3 \mu m$; and e) Fiber electrical resistance from $407 K \Omega$ to $1.727 M \Omega$.
 Cardenas results have areas of opportunity regarding the fiber yield rate and the high variability on the fiber electrical resistance.
 These undesirable characteristics could be a consequence of the addition of PEO to the solution.
-Figure \ref{fig:su8Components} illustrates the ingredients that comprise the SU-8 formulation.
-SU-8 based vitreous carbon is obtained after a pyrolysis process in which the oxygen already present in the SU-8 formulation allow the formation of close pores during annealing.
+SU-8 based vitreous carbon is obtained after a pyrolysis process in which the oxygen already present in the SU-8 formulation allows the formation of close pores during annealing.
 However, the further addition of oxygen content present in the PEO molecules may be the cause of the low yield rate and high variability in electric resistivity from sample to sample.
@@
 
-The role of carbon nano-fibers in nano-sensor devices play an important role, as portable instruments require light-weight and small-sized components.
+The role of carbon nano-wires in nano-sensor devices play an important role, as portable instruments require light-weight and small-sized components.
 \cite{Khanna2016} Table \ref{tab:advantagesOfNanosensors} lists some advantages of nano-sensors that can be accomplished by the fabrication of CNFs via near-field electrospinning and a thermal treatment in an inert environment.
 
-\begin{table}[ht]
+\begin{table}[!th]
 \centering
@@
 Nano-sized sensors allow data collection and measurements to be performed in real time at faster speeds.
-\cite{Khanna2016} The nano-scale also allows sensors to increase the active surface area, enabling the absorption and detection of analytes in low concentrations.
-\cite{Khanna2016} The integration of small-sized sensing devices lean to lower fabrication costs as large-scale production and reproducible fabrication can be achieved when producing nanosensors.
-\cite{Khanna2016} Moreover, conventional sensors are bulky and require higher amounts of power to operate.
+\cite{Khanna2016} The nano-scale also allows sensors to increase the active surface area, enabling the absorption and detection of analytes at low concentrations.
+\cite{Khanna2016} Conventional sensors are bulky and require higher amounts of power to operate.
 In gas sensing, neither a large sensing surface or a large sample is required to get a readable output signal from the sensor.
@@
 A multi-gas sensor array can increase the size and cost, whereas an array of gas nano-sensors (each functionalized to detect a specific analyte) can be implemented into a single device.
-\cite{Khanna2016} Nano-sensors can be classified by the kind of energy or physycal phenomena that is detected, as depicted in Table \ref{tab:classificationOfNanosensors} for instance: biological, mechanical, thermal, chemical, and optical sensors.
+\cite{Khanna2016} Nano-sensors can be classified by the kind of energy or physical phenomena that is detected, as depicted in Table \ref{tab:classificationOfNanosensors} for instance: biological, mechanical, thermal, chemical, and optical sensors.
 \cite{Khanna2016, BaudritJ2017}
@@
 
-\begin{table}[ht]
+\begin{table}[!th]
 \centering
@@
 
-Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques.
+Carbon nanowires have been fabricated with a photoresist by two-photon polymerization techniques.
 However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis, as it is generally believed that most polymers do not form significant amounts of graphitic carbon when carbonized.
 %The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}.
-In the past years, photopolymerization processes have been applied to the fabrication of nano-structures with the use of an epoxy based photoresist.
+In the past, photopolymerization processes have been applied to the fabrication of nano-structures with the use of an epoxy based photoresist.
 \cite{Boer2014} Photopolymerization techniques deliver patterning resolutions with nano-scale tolerances through two-photon lithography for the production of highly detailed structures \cite{Hribar2014}.
 
-On the other hand, electrospinning has been acknowledged as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires.
+On the other hand, electrospinning has been classified as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires.
 Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner.
-Cardenas \cite{Cardenas2017} showed that electrospinning can be implemented with ease for carbon nano-wire synthesis.
+Cardenas \cite{Cardenas2017} showed that electrospinning can be implemented with ease for carbon nano-wire fabrication.
 Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires.
-As stated in \cite{Cardenas2017}, mechano-electrospinning is an early technology invention and brings new challenges, such as the reproducibility of carbon nano-wire production.
-Furthermore, the study of a new fabrication process to produce carbon nanowires that involves mechano-electrospinning will enable spatial control of the structures' patterning.
+As stated in \cite{Cardenas2017}, mechano-electrospinning is a recent technology invention and brings new challenges, such as the reproducibility of carbon nano-wire production.
+Furthermore, the study of a new fabrication process to produce carbon nano-wires that involves mechano-electrospinning will enable spatial control of the fiber deposition.
 
 Since electrospinning seems to be a better alternative for carbon nano-wire fabrication processes; and for that purpose of its implementation, it is required to develop polymer solutions that can be mechano-electrospun, photopolymerized and pyrolyzed into conducting carbon nano-wires.
-Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties.
-\cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection.
-\cite{Siddiqui2019} However most applications are not currently feasible due to the lack of a continuous, simple and reproducible fabrication method with inexpensive processes.
+Most applications of carbon-based materials are not currently feasible due to the lack of a continuous, simple and reproducible fabrication method with inexpensive processes.
 With the newly designed polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more applications will become feasible.
-On the other hand, the new technique will overcome some limitations of other methods such as lithography currently has.
+On the other hand, the new technique will overcome some limitations of other methods such as lithography.
 For instance, patterns created by lithography processes cannot be originated, only replicated, all constituent points of the pattern can only be addressed at the same time, and the process requires the pattern to be encoded into a mask.
@@
 
-The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the fabrication conductive of carbon nano-wires with specified dimensions (diameter and length).
-The rheological properties of polymer solutions along with synthesis parameters are to be amended by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardenas \cite{Cardenas2017} work.
+The viscoelastic properties of polymer solutions along with synthesis parameters
+%(stage velocity, voltage, dispense rate)
+can be controlled through rheological analyses to obtain low voltage electrospun-able, photopolymerizable and graphitizable solutions for the fabrication conductive of carbon nano-wires.
+% with specified dimensions (diameter and length).
+The viscoelastic properties of polymer solutions along with synthesis parameters can be modified by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardenas \cite{Cardenas2017} work.
 PEO is to be replaced as its only purpose is to allow the electrospinning process to take place, but no benefit is obtained from it after pyrolysis.
+The hypothesis is that oxygen-less polymers will yield carbon nano-wires of better quality than those made from PEO blends, therefore the study is to verify the eletrospinnability of high carbon content oxygen-less polymers in solution.
 
@@
 	\item{
-	What rheological properties are to be controlled/tested to deliver an electrospun-able and pyrozable polymer solution?	
-	}
-	\item{
-	Are there any efforts employed to the design of polymer solutions that can be electrospun, photopolymerized, and pyrolyzed into conducting carbon nanowires?
+	What viscoelastic properties are to be controlled/tested to deliver an electrospun-able and pyrozable polymer solution?	
 	}
@@
 \subsection{General objective}
-Study the practice and feasibility of a new fabrication process to achieve mass scale manufacturing of polymeric micro-wires in an inexpensive, continuous, simple and reproducible manner by the integration of near-field electromechanical spinning (NFEMS) and forward-thinking on pyrolysis processes to convert polymeric micro-wires into carbon nano-wires.
+Formulate polymer solutions by selection of linear high-molecular weight polymers and solvents and then match their viscoelastic properties to those of the benchmark SU-8/PEO solution to select the polymer/solvent combinations that have the greatest protential to replace or modify the SU-8/PEO formulation for the fabrication of microscopic polymer fibers that may be converted to conductive suspended carbon nano-wires.
 
@@
 	\item{
-	Design polymer solutions that can be electrospun by NFES, photopolymerized, and then pyrolyzed.
+	Propose polymer solutions that can be electrospun by Near-Field Electrospinning.
     }
     \item{
-    Through rheological analyses, determine if polymer solutions can be easily employed for conducting carbon nano-wire synthesis.
+    Through rheological analyses, determine if polymer solutions can have comparative viscoelastic properties to those of the SU-8/PEO benchmark.
     }
     \item{
-    Determine and control the polymer solution rheological properties along with the process parameters of carbon nano-wire synthesis.
+    Learn how the diameter of the electrospun polymer fiber can be controlled by appropriate tuning of the NFES parameters and solution properties. 
     }
     \item{
-    Discover a PEO-similar material to allow the electrospinning process as well as input favourable properties to the carbon nano-wire yield.
+    Propose alternatives to the SU-8/PEO benchmark formulation for the production of microscopic polymer fibers with potential for the fabrication of carbon nano-wires. 
     }
@@
 \section{Dissertation Outline}
+The dissertation is organized as follows.
+Chapter 1, an introduction to carbon-based nanomaterials is presented.
+The applications and characteristics of carbon structures are listed with an emphasis on carbon nano-wires.
+Chapter 2 is comprised by a review of the electrospinning process.
+The process parameters such as process variables, ambient parameters and solution properties and their influence in fibers formation are studied.
+Data collection of near-field electrospinning publications was done to execute an adimensional analysis to describe and predict the fiber diameterfrom the process parameters.
+Chapter 3 focuses on the selection of candidate polymer-solvent combinations to replace the PEO-SU-8 formulation.
+Rheological tests (frequency sweeps) were done to study the visoelasticity of polymer solutions.
+Chapter 3 estimates the optimal polymer concentrations to fabricate continuous fibers through NFES.
+Chapter 4 presents the fabrication of polymeric fibers.
+The near-filed process parameters, materials and methods are discussed, where a replicate of experiments of PEO solutions from literature is used as an experimental control.
+The last chapter shows the results of the fiber characterization of different sets of polymer solutions, though an optical microscope.
+Finally, the conclusions of this work and the considerations to future works are presented.

### 2020-12-02 05_Thesis/THESIS_LaTeX/Chapters/2.tex
visco plots in progress
final work done

@@
 Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement.
-In the past years (2006-2020), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process.
-Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties.
+\cite{He2017} In the past years (2006-2020) \cite{Helgeson2007,
+  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
+  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
+  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
+  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
+  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
+  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
+  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
+  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
+  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}, several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process.
+Each NFES variant intended to tailor the process parameters in order to improve the fibers' properties.
+
+Near-field electrospinning (NFES) is known as a versatile nano-fabrication technique, suitable for several applications such as tissue engineering, chemical sensing, filtration, energy storage, besides others (see Figure \ref{fig:synthesesAndApplicationsOfNanofibers}).
+Fast developments in electrospinning has been observed in recent years.
+However, this process is limited by the electric field wiping instability effects during polymer deposition.
+This leads to a major challenge: how to surpass this limitation of planar two-dimensional prints.
+The current trend in this area lies on the research of new materials, techniques to increase precision patterning in NFES systems.
+
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/synthesesAndApplicationsOfNanofibers.png}
+\decoRule
+\caption[Syntheses and Applications of Nanofibers]{Syntheses and Applications of Nanofibers. Adapted from \cite{Kenry2017}}
+\label{fig:synthesesAndApplicationsOfNanofibers}
+\end{figure}
 
@@
 The technique allows the production of thin continuous fibers with ease, with micro and sub-micrometer diameters, which is something difficult to achieve by other techniques.
-Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials.
+Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities from different materials.
 The produced fibers can be aligned or unaligned.
@@
 
-\subsubsection{Electric Field}Electrospinning (electrostatic fiber spinning) is a fiber fabrication approach that implements an electric field produce fibers by an electrical potential difference between the syringe needle and the collector.
+\subsubsection{Electric Field}Electrospinning (electrostatic fiber spinning) is a fiber fabrication approach that implements an electric field to produce fibers by applying an electrical potential difference between the syringe needle and the collector.
 With the influence of high electric fields, the fibers are prone to brake into separate layers due to the whipping instabilities as the jet travels to the substrate.
@@
 From the Taylor cone, the supplied polymer jet (typically a polymer solution) accelerates and reduces in diameter.
-The fiber finally develops with the complete solvent evaporation.
-Electrospun fibers are prone to splitting with the increase in acceleration due to high applied voltages, where multiple fibers are yield in a process known as electrospraying \unskip~\cite{527120:13659925}.
+The fiber finally develops upon complete solvent evaporation.
+Electrospun fibers are prone to splitting with the increase in acceleration due to high applied voltages, where multiple fibers are produced in a process known as electrospraying \unskip~\cite{527120:13659925}.
 
@@
 When a polymer solution is administrated with a syringe pump, solution droplets will fall under the influence of gravity.
-The solution dripping stops when the electric field is strong enough to break the solution's surface tension, causing the droplet to change shape forming a polymer solution jet\unskip~\cite{527120:12033655}.
+The solution dripping stops when the electric field is strong enough to break the solution's surface tension, causing the droplet to change shape forming a jet\unskip~\cite{527120:12033655}.
 
@@
 \unskip~\cite{527120:13659926} reported that the growth of the whipping instability is one important element within the electrospinning technique.
-As detailed in Shin's work, weak electric fields produce a single uniformly thinning jet, and strong electric fields the jet becomes unstable after traveling a short distance.
+As detailed in Shin's work, weak electric fields produce a single uniformly thinning jet, and at strong electric fields the jet becomes unstable after traveling a short distance.
 
@@
 Centrifugal spinning intends to produce fibers by the use of a rotating polymer source.
-The centrifugal force generated from typical rotatory speeds above $2000 rpm $, results in fiber formation.
+The centrifugal force generated from typical rotatory speeds above $2000 \textrm{ rpm}$, results in fiber formation.
 \unskip~\cite{527120:13535559,527120:13535561}.
@@
 Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach.
-Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.
+Zander's fibers were produced with rotatory speed between $3000$ and $18000 \textrm{ rpm}$ obtaining $10 \mu m $ diameters.
 
@@
 Centrifugal electrospinning implements the same setup as the standard centrifugal spinning with the addition of a high voltage power supply between the rotating dispensing nozzle and the collector.
-The combined method has evidence to yield parallel fibers\unskip~\cite{527120:13536841,527120:13536900,527120:13537392,527120:13537393} at a higher rate \unskip~\cite{527120:13536841,527120:13536900} than the standard electrospinning approach.
+The combined method has been proven to yield parallel fibers\unskip~\cite{527120:13536841,527120:13536900,527120:13537392,527120:13537393} at a higher rate \unskip~\cite{527120:13536841,527120:13536900} than the standard electrospinning approach.
 
-\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution.
+\subsubsection{Blowing forces}Nano-fibers can be produced with the implementation of pressurized gas with a polymer solution.
 The setup used for blow spinning is similar to the one used in coaxial electrospinning, where the polymer precursor is dispensed at a controlled rate.
@@
 Oliveira et al.
-\unskip~\cite{527120:13539278} fabricated the fibers from $6 wt\% $ PLA solutions with progesterone for live stock reproductive cycle regulation applications.
+\unskip~\cite{527120:13539278} fabricated fibers from $6 wt\% $ PLA solutions with progesterone for live stock reproductive cycle regulation applications.
 On the other hand, Souza et al.\unskip~\cite{527120:13538056} conducted a study to compare the standard electrospinning and the solution blow spinning techniques.
@@
 \makeatother 
-\caption{{Typical mechanical fiber drawing process.
-First the needle makes contact with the substrate to break the polymer drop.
-Then the needle leaves the substrate and the collector moves to create and deposit the fiber.
-Once the fiber is written the needle makes contact witht the collector to fix the fiber deposition.}}
+\caption{{Typical mechanical fiber drawing process}}
 \label{f-432d16f420fb}
 \end{figure*}
+% First the needle makes contact with the substrate to break the polymer drop.
+Then the needle leaves the substrate and the collector moves to create and deposit the fiber.
+Once the fiber is written the needle makes contact witht the collector to fix the fiber deposition.
+
 \egroup
 Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette.
-\unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical applications.
+\unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical complications.
 \unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers where the fiber is created by stretching the polymer precursor with a moving collector, as depicted in Figure~\ref{f-432d16f420fb}.
-Touch-spinning is another mechanical technique that comprises a moving stage with an embedded glass rod (Figure~\ref{f-f17259e76303}).
-Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers.
+Touch-spinning is another mechanical technique that comprises a moving stage with an embedded glass rod (Figure~\ref{f-f17259e76303}), where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers.
 The rotation stretches the fiber, causing the fiber to increase in length and decrease in diameter.
@@
 \makeatother 
-\caption{{Touch-spinning technique.
-First rod is attached to a rotating stage and a polymer solution droplet is administrated through a needle.
-Then the rotating rod 'touches' the polymer precursor.
-Finally, as the rod rotates, the polymer solution is stretched and creates a fiber between the rod and the needle.}}
+\caption{{Touch-spinning technique.}}
 \label{f-f17259e76303}
 \end{figure*}
+% First rod is attached to a rotating stage and a polymer solution droplet is administrated through a needle.
+Then the rotating rod 'touches' the polymer precursor.
+Finally, as the rod rotates, the polymer solution is stretched and creates a fiber between the rod and the needle.
+
 \egroup
 The touch spinning technique implies that the fiber diameter can be controlled by the moving collector's speed and the polymer solution concentration.
-The main difference relays on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}
+The main difference lies on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}
 
@@
 \unskip~\cite{527120:13656236} compared and combined the microfluidic spinning and electrospinning techniques.
-Heterogeneous materials and cell patterning within a single microfiber can be designed by the integration microfluidic channels.
-Therefore, microfluidic spinning is more suitable for cell encapsulation and tissues generation\unskip~\cite{527120:13656236}.
+Heterogeneous materials and cell patterning within a single microfiber can be designed by the integration of microfluidic channels.
+Therefore, microfluidic spinning is more suitable for cell encapsulation and tissue regeneration and tissue engineering \unskip~\cite{527120:13656236}.
 
@@
 \egroup
-Some advantages that co-electrospinning setups can break the polymer drop surface tension, initiating the jet burst from the spinneret nozzle.
-On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles.
+Some advantages of co-electrospinning setups are the breaking of the polymer drop surface tension, initiating the jet burst from the spinneret nozzle.
+On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the modification of the material properties by producing bubbles, scaffolds and particles.
 \unskip~\cite{527120:13914748,527120:13914750}.
@@
 
-\subsection{Polymer Reservoir (Polymer Melt \& Polymer Solution)}Electrospinning processes can be classified on the polymer reservoir type.
+\subsection{Polymer Reservoir (Polymer Melt \& Polymer Solution)}Electrospinning processes can be classified based on the type of polymer reservoir.
 As Brown et al.
-\unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used).
+\unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning.
 The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state.
-The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution.
+The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt.
 The apparatus used by Brown et al.
@@
 \egroup
-Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales.
-Furthermore, polymer melt reservoirs get rid of any solvent contamination.
-
+Despite the added complexity and thicker diameters, the melt electrospinning technique is safer to be performed on larger scales as it does not have the need to handle volatile solvents.
+Therefore, polymer melt reservoirs get rid of any solvent contamination.
 The first report of a melt electrospun drug delivery system came from Nagy et al.
@@
 
-Balogh et al.'s work has been built on to blend plasticizes with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticizes Triacetin, Tween 80 and Polyethylene Glycol were investigated in order to reduce the melting point of the polymer-drug mixture.
-The temperature drop is desirable to minimize the occurring drug degradation.
+Balogh et al.'s work has built on this idea by blending plasticizes with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticizes Triacetin, Tween 80 and Polyethylene Glycol were investigated in order to reduce the melting point of the polymer-drug mixture.
+A lower temperature is desirable to minimize the degradation of the drug.
 
@@
 They arrived to the conclusion that melt spinning is preferable when the polymer presents a low solubility.
-On the other hand the melt fibers were produced in a slower release rate.
+On the other hand, the melt fibers were produced in a slower release rate.
 Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning.
@@
 In literature, melt electrospinning has less evidence than the solution approach.
-However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}.
-Currently, the melt electrospinning setup is harder to determine and the lack of research on this technique explains its unexplored potential.
+However, melt electrospinning promises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}.
+Currently, the melt electrospinning setup is harder to analyze or study and the lack of research on this technique explains its unexplored potential.
 
-\subsection{Polymer Solution}In electrospinning, it is typically agreed that the diameter of the fibers increased with higher concentration due to greater viscosity which withstands stretching.
-In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}, seeFigure~\ref{f-d977f56a0782}.
+\subsection{Polymer Solution}In electrospinning, it is typically agreed that the diameter of the fibers increases as the polymer concentration increases due to greater viscosity, which resists the forces pulling on the solution.
+In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter appears to increase proportionally \unskip~\cite{527120:11974306,527120:11974329}, seeFigure~\ref{fig:plt_Cpolymerwt_vs_Dfiberm}.
 \begin{table}[!htbp]
-\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
+\caption{Approximation process to estimate the critical polymer concentration.}
 \label{tw-be3662f66502}
@@
 \end{table}
+% Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.
 
-\subsubsection{Polymers}The polymer selection is in function on the intended application.
+\subsubsection{Polymers}The polymer selection is typically guided by the intended final application of the fibers produced therefrom.
 For example, a fast dissolving hydrophilic polymer such as poly(ethylene oxide) (PEO) is used for fast drug delivery systems.
@@
 The polymer molecular weight along with the polymer concentration and solvent selection have a direct effect on the solution viscosity, conductivity and surface tension, hence the solution behavior in the electrospinning process.
-The spunable viscosity range varies with the polymer and solvent.
+The spinnable viscosity range varies with the polymer and solvent.
 
-Solutions with low viscosity are prone to insufficient polymer chain entanglements to produce fibers.\unskip~\cite{527120:13082763} On the other hand, if the solution is too viscous, then the surface tension cannot easily be overcome by the electric field.
-In both cases, the result can be droplets or particles forming rather than fibers as described inTable~\ref{tw-be3662f66502}.
+Solutions with low viscosity result in insufficient polymer chain entanglements to produce fibers.\unskip~\cite{527120:13082763} If the solution is too viscous, then the surface tension cannot easily be overcome by the electric field.
+In both cases, the result can be droplets or particles forming rather than fibers as described in Table~\ref{tw-be3662f66502}.
 
@@
 A low-volatility solvent like water may fail to evaporate completely over the distance between the spinneret and the collector.
-When the fibers form, they will hence contain residual water owing to this incomplete evaporation.
-The residue solvent will subsequently evaporate from the fibers upon storage, resulting in ribbon-like (flattened) fibers, wrinkles on the fiber surface or fused fibers.
+Hence, when the fibers form, they will contain residual water owing to this incomplete evaporation.
+The solvent will subsequently evaporate from the fibers upon storage, resulting in ribbon-like (flattened) fibers, wrinkles on the fiber surface or fused fibers.
 On the other hand, a high-volatility solvent may evaporate very quickly, leading to larger fiber diameters (less time for elongation before solidification) and clogging of the spinneret (due to drying of the liquid at the spinneret before jetting, or drying of the Taylor cone during jetting).
@@
 Mixtures of miscible solvents can be used to ensure that sufficient polymer can be dissolved to give a solution of appropriate viscosity and volatility with suitable dielectric constant range to allow fiber formation.
-However, care must be taken because using a mixture of solvents with very different volatilities can result in porous fiber structures.
-As reported by Katsogiannis et al.
+However, care must be taken because using a mixture of solvents with very different volatilities can result in porous fiber structures, as reported by Katsogiannis et al.
 for organic solvent mixtures with dimethyl sulfoxide (DMSO).\unskip~\cite{527120:13082766} DMSO evaporates much more slowly than the organic solvents used, which results in its incorporation into the fibers.
@@
 
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.45]{./Figures/DifferentElectrospinningMethods.png}
+\decoRule
+\caption[Different Electrospinning Methods in Terms of Spatial Control, Fiber Throughput and Resolution]{Different Electrospinning Methods in Terms of Spatial Control, Fiber Throughput and Resolution.
+Adapted from \cite{Tourlomousis2017}}
+\label{fig:DifferentElectrospinningMethods}
+\end{figure}
+
+As depicted in Figure \ref{fig:DifferentElectrospinningMethods}, solution electrospinning yields fibers with higher resolution than melt electrospinning techniques, and near-field electrospinning offers greater spatial control of the deposition of fibers than the far-field technique.
+Moreover, solution electrospinning often involves the use of toxic solvents, whereas melt electrospinning is a solvent free process but with the additional complexity as a heater needs to be installed.
+\cite{Tourlomousis2017}
+
 \section{Properties that Improve Accuracy of Nano-Fiber Deposition}
-Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition.
-This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
-Table S1 is a collection of the relevant NFES process parameters and achieved fiber morphology.
+Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has evolved through several modifications to improve the precision and accuracy of the fiber deposition.
+This work is intended to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.
+Appendix \ref{Appendix_NFESreviewTable} is a collection of the relevant NFES process parameters and achieved fiber morphology.
 
-Some differences have been discovered between LV-NFES and conventional NFES.
-Low voltage near field electrospinning produces thinner fibers with lower voltages; as shown inFigure~\ref{f-59ed68f95344}.
+Some differences have been discovered between Low-Voltage Near-Field Electrospinning (LV-NFES) and conventional NFES.
+Low voltage near field electrospinning produces thinner fibers with lower voltages; as shown in Figure~\ref{fig:plt_Phi0V_vs_Dfiberm}.
 Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching.
@@
 and Chang et al.
-\unskip~\cite{527120:11973130,527120:11974313} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
+\unskip~\cite{527120:11973130,527120:11974313} reported that thinner diameters are obtained with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.
 
-Bisht and Chang's work \unskip~\cite{527120:11973130,527120:11974313} reports a controlled technique to fabricate polymeric nano fibers in a continuous manner, using a low voltage setup.
-Their purpose is to find a workaround to the drawbacks of traditional NFES by using a superelastic polymer precursor, which allow continuous patterning without breaking.
+Bisht and Chang's work \unskip~\cite{527120:11973130,527120:11974313} reports a controlled technique to fabricate polymeric nano fibers in a continuous manner, using a low-voltage setup.
+Their purpose is to find a workaround to the drawbacks of traditional NFES by using a superelastic polymer precursor, which allows continuous patterning without breaking.
 In low voltage near-field electrospinning (LV NFES), a visco-elastic polymer is used to allow continuous spinning at about 200$V $.
@@
 As stated by the authors, the induced electric field is enhanced by the conductive pattern, which allows the fibers to follow the desired deposition path.
-As the fibers are prone to follow the conductive pattern, additional fibers can be stacked on each other.
+As the fibers are prone to follow the conductive pattern, additional fibers can be stacked on top of the previously deposited fibers.
 The stacking process was successfully achieved in high electric field conditions at: 750$\mu m $ substrate to collector distance, and a 600 $\mu m $ needle to rail (offset) distance, see Figure~\ref{f-927e96fb5537}.
@@
 \makeatother 
-\caption{{NFES setup for controlled fiber deposition on pre-patterned conductive electrodes. \unskip~\protect\cite{527120:11974313}}}
+\caption{{NFES setup for controlled fiber deposition on pre-patterned conductive electrodes. Adapted from \unskip~\protect\cite{527120:11974313}}}
 \label{f-927e96fb5537}
@@
 As described by Gupta et al.\unskip~\cite{527120:11974310}, the fiber deposition equipment is comprised by a stainless steel needle with a internal diameter of 750 $\mu m $ , connected to a high voltage power supply of up to 30 $k V $ with a deposition rate of about $\geq 1 \mu L min^{-1} $.
-The setup was embedded to a motorized collector capable of controlled programmable motions, see Figure~\ref{f-74de1f00848b}.
+The setup was embedded to a motorized collector capable of controlled programmable motions
+%, see Figure~\ref{f-74de1f00848b}.
 The proposed technique was able to produce fibers of $150 \mu m $ in diameter with pre-designed patterns.
@@
 %\fixFloatSize{./images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}
-\begin{figure}[!htbp]
-\centering \makeatletter\IfFileExists{./images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}{\includegraphics[scale=0.60]{./images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}}{}
-\makeatother 
-\caption{{Schematic illustration of the electrohydrodynamic process. \unskip~\protect\cite{527120:11974310}}}
-\label{f-74de1f00848b}
-\end{figure}
+%\begin{figure}[!htbp]
+%\centering \makeatletter\IfFileExists{./images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}{\includegraphics[scale=0.60]{./images/fa274bb7-a79d-48ae-9349-953df62c0094-ugupta_00.png}}{}
+%\makeatother 
+%\caption{{Schematic illustration of the electrohydrodynamic process. \unskip~\protect\cite{527120:11974310}}}
+%\label{f-74de1f00848b}
+%\end{figure}
 \egroup
@@
 \unskip~\cite{527120:11974322,527120:11974323,527120:11974324} experimented with several multi-nozzle near-field electrospinning of aligned nano fibers.
-The multi nozzle NFES apparatus is similar to the one used in conventional NFES with some modifications to the needle nozzle, see Figure \ref{f-4a1a1f58a423}.
+The multi-nozzle NFES apparatus is similar to the one used in conventional NFES with some modifications to the needle, see Figure \ref{f-4a1a1f58a423}.
 The authors implemented similar NFES setups where the installed linear array of nozzles is supplied with a constant flow rate of solution.
@@
 \makeatother 
-\caption{{The geometry distribution of linear array multi-nozzle system \unskip~\protect\cite{527120:11974323}}}
+\caption[Geometry Distribution of Linear Array Multi-Nozzle System]{The geometry distribution of linear array multi-nozzle system. \unskip~\protect Adapted from \cite{527120:11974323}.}
 \label{f-4a1a1f58a423}
@@
 \egroup
-The authors came to the conclusion that the distance between the deposited fibers increase with the increase of the needle-to-collector distance, as the influence of the applied voltage dissipates.
+The authors came to the conclusion that the distance between the deposited fibers increased as the needle-to-collector distance increased, due to the influence of the applied voltage dissipates.
 
-Huang, et al.\unskip~\cite{527120:11974311} studied the mechanoelectrospinning (MES) technique for the fabrication of nano fibers.
+Huang, et al.\unskip~\cite{527120:11974311} studied the mechanoelectrospinning (MES) technique for the fabrication of nano-fibers.
 The MES technique tries to improve deposition accuracy by the introduction of a mechanical drawing force.
 The MES is predominantly controlled by the collector stage velocity, the nozzle-to-collector distance, and the applied voltage.
-The authors believe that MES can compete as a low-cost, high precision fabrication of electronics and enable the direct writing of structures for nano scale lithography.
+The authors believe that MES can compete as a low-cost, high precision fabrication of electronics and enable the direct writing of structures for nano-scale lithography.
 Figure~\ref{f-7587d8081ccc} shows the polymer jet behavior when a mechanical force is implemented within the NFES process.
@@
 \makeatother 
-\caption{{schematic diagram of leap direct-writing: the ink first accumulates at contact point and then gets stretched by mechanical drawing force.
-At a critical distance, the ink leaps to the next contact point, and gets stretched again \unskip~\protect\cite{527120:11974311}}}
+\caption[Schematic diagram of leap direct-writing]{Schematic diagram of leap direct-writing. Adapted from \cite{527120:11974311}}
 \label{f-7587d8081ccc}
 \end{figure}
+% At a critical distance, the ink leaps to the next contact point, and gets stretched again \unskip~\protect\cite{527120:11974311}
+
 \egroup
-Micro and nano fibers have been written using AC pulse-modulated electrospinning by Bu et al.
-with polyehtylene terephthalate (PET) as substrate\unskip~\cite{527120:11974304}.
+Micro and nano-fibers have been written using AC pulse-modulated electrospinning by Bu et al.
+with polyethylene terephthalate (PET) as substrate\unskip~\cite{527120:11974304}.
 The AC electrical field influences the electrospinning jet.
@@
 Nagle et al.
-studied PEO fibers at different nozzle to collector distances.
-Evidence suggest that better patterning accuracy increases with increasing nozzle to collector distance as the solution is effectively dried\unskip~\cite{527120:12033656}.
-Near field mechano-electrospinning enables the collection of non woven fibers over large areas.
+studied PEO fibers at different nozzle-to-collector distances.
+Evidence suggests that better patterning accuracy increases with increasing nozzle to collector distance as the solution is effectively dried\unskip~\cite{527120:12033656}.
+Near field mechano-electrospinning enables the collection of non-woven fibers over large areas.
 
@@
 \egroup
-To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
+To spin nano-fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited.
 Kameoka et al.\unskip~\cite{527120:12321556} demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip.
 
-Near-field electrospinning, has exhibited to be capable fabricate nano fibers and nano fiber patterns \unskip~\cite{527120:11974321}.
+Near-field electrospinning, has been shown to enable the fabrication of nano-fibers and nano-fibrous patterns \unskip~\cite{527120:11974321}.
 Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner.
@@
 syringe) of solution generally produces fibers with diameter of a few micrometers \unskip~\cite{527120:11974310,527120:11974326}, since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through.
-As shown inFigure~\ref{f-51afaccaf109}, the implementation of thicker needle nozzles translate into an increase of the resulted fiber diameter
+The implementation of thicker needle nozzles translates into an increase in diameter of the deposited polymer fibers.
 
-Coppola et al.\unskip~\cite{527120:11974307} have showed a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop, averting the issue of nozzle clogging.
-The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al.'s\unskip~\cite{527120:11974326} work.
+Coppola et al.\unskip~\cite{527120:11974307} have showed a NFES variant that allows polymer nano-fibers to be deposited directly from a polymer drop, averting the issue of nozzle clogging.
+The fibers are also prone to soaking after deposition thus giving the fibers a semi-circular cross-section as shown by Xue and coworkers \unskip~\cite{527120:11974326}.
 
-\subsection{Nozzle spinneret}The thinnest nozzles in literature so far are about $50 nm $ in diameter, by Chang et al.\unskip~\cite{527120:11974306} who used a  $100 \mu m $ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO).
-Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
+\subsection{Nozzle spinneret}The thinnest nozzles in literature so far are about $50 \textrm{ nm}$ in diameter, by Chang et al.\unskip~\cite{527120:11974306} who used a  $100 \textrm{ } \mu \textrm{m}$ inner diameter needle tip to electrospin poly(ethylene oxide) (PEO).
+Camillo et al.\unskip~\cite{527120:12322072} used a micro-diameter-tip Tungsten spinneret in a 26G needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).
 The nozzle most commonly comprises a simple narrow-bore, blunt-end metal needle.
@@
 
-\subsection{Applied Voltage}In recent literature, near field electrospinning has been studied to reduce the fiber diameter and to improve the fiber deposition accuracy.
-Madou et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} came to the conclusion higher voltages yield thicker micro-fibers with a loss in jet stability.
+\subsection{Applied Voltage}In recent literature, near field electrospinning has been studied to reduce the fiber diameter and to improve the control over fiber deposition.
+Madou et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} came to the conclusion that higher voltages yield thicker micro-fibers with a loss in jet stability.
 This relationship between the applied voltage and resulting fiber diameter is influenced by other variables such as nozzle-to-substrate distance and solution deposition rate.
@@
 Madou et al.\unskip~\cite{527120:11973130} achieved the fabrication of thinner fibers with spatial control by reducing the applied voltage to 200-600 $V $  at a nozzle-to-substrate distance of 0.5-1 $mm $.
-The low voltage setting does not create enough charge to break the polymer solution surface tension to initiate the electrospinning process.
-
-Madou et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} initiated the electrospun fibers by mechanically pull the polymer solution at the nozzle tip using a micro-probe tip.
+The low voltage setting alone does not create enough charge to break the polymer solution surface tension to initiate the electrospinning process.
+Madou et al.\unskip~\cite{527120:11973130} and Chang et al.\unskip~\cite{527120:11974306} initiated the electrospun fibers by mechanically pulling the polymer solution at the nozzle tip using a micro-probe tip.
 Chang and coworkers reduced the applied voltage from 1.5 $kV $ to 600 $V $ with a nozzle-to-substrate distance of 500 $\mu m $ to yield a fiber diameter between 3 $\mu m $  and 50 $nm $ .
@@
 
-In near-field electrospinning, the applied voltage has an impact on the produced fiber morphology.
+In near-field electrospinning, the applied voltage has an impact on the morphology of the fiber.
 For instance, a voltage higher or lower to the optimum voltage will translate into an increase in fiber diameter.
-Song et al.\unskip~\cite{527120:11974320} demonstrated that a decrease in voltage from 400 to 500 $V $ can reduce the fiber diameter from 160 to about 60 $nm $with a nozzle-to-substrate distance of 20 $\mu m $.
+Song et al.\unskip~\cite{527120:11974320} demonstrated that an increase in voltage from 400 to 500 $V $ can reduce the fiber diameter from 160 to about 60 $nm $with a nozzle-to-substrate distance of 20 $\mu m $.
 A workaround to break the polymer solution surface tension is to initialize the NFES process with a higher voltage and then lower the voltage once the jet is created.
-Huang et al.\unskip~\cite{527120:11974311} implemented the previous and yield ordered fibers with a distance between adjacent fibers of 50 $\mu m $.
+Huang et al.\unskip~\cite{527120:11974311} implemented the previous and obtained ordered fibers with a distance between adjacent fibers of 50 $\mu m $.
 
@@
 As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}.
-When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process.
-The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}.
+When the polymer solution surface tension is overcome by the electric field potential difference, a jet is formed, starting the electrospinning process.
+The electrospinning process can be broken down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}.
 The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.
 
-In the intent to achieve controlled fiber deposition, Sun et al.
+With the goal of achieving controlled fiber deposition, Sun et al.
 \unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES),Figure~\ref{f-c34559531e3e}.b, describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line.
-Moreover, some mechanical influence is required to deposit fibers precisely.
+Moreover, some mechanical influence is required to deposit fibers with higher precision.
 The mechanical force is introduced by moving collector.
@@
 Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.
+Adimensional analyses have been done \cite{Sarkar2009,Tourlomousis2017,Cai2013,Wang2008a,Widartiningsih2020,Chang2014,Brooks2015,Helgeson2008,Helgeson2007,Gadkari2014} and can be used as a guide to design and prepare electrospinning setups, however these analyses are recently developed and hence their little appearance in literature publications.
 
-The main difference between NFES and FFES is the distance between the needle and the collector which is higher in FFES (about 10 cm) compared to NFES which ranges in the mm scale.
-The short distance allow the production of well aligned fibers within particular designs.
+The main difference between NFES and FFES is the distance between the needle and the collector which is higher in FFES (about 10 cm) compared to NFES, which ranges in the mm scale.
+The short distance allows the production of well-aligned fibers within particular designs.
 In NFES, the fiber morphology can be altered by the control of the distance between the nozzle and the substrate (collector).
@@
 An optimal nozzle-to-substrate distance shall be defined to ensure the fabrication of dry continuous fibers.
-If the solvent is not well evaporated, the produced fibers are prone to defects; on the other hand if solidification happens too fast, the solids can block the spinneret which can prevent a continuous fiber yield.
+If the solvent is not well evaporated, the produced fibers are prone to defects; on the other hand, if solidification happens too fast, the solids can block the spinneret which can prevent a continuous fiber yield.
 Furthermore, the polymer jet will discharge itself as soon as possible, therefore long distances can result in low yields.
@@
 
-Liu et al.\unskip~\cite{527120:11974315} discovered that the fiber alignment is improved by using a glass-cooper foil substrate, however the well aligned fibers are spoiled after prolonged depositions due to residual charges.
-Additionally, the effect of residual charges is amplified with the used collector substrate contains a conductive layer and a non-conductive layer\unskip~\cite{527120:11974315}.
+Liu et al.\unskip~\cite{527120:11974315} discovered that the fiber alignment is improved by using a glass-cooper foil substrate, however the alignment of the fibers is spoiled after prolonged depositions due to residual charges.
+Additionally, the effect of residual charges is amplified when the used collector substrate contains a conductive layer and a non-conductive layer\unskip~\cite{527120:11974315}.
 
-On the other hand, Choi et al.\unskip~\cite{527120:12322289} implemented a hydrophilic substrate to deposit the fibers with plasma treatment to increase the conductivity of selected areas.
-NFES was carried put with precise deposition as the fibers were placed as per the desired design within the hydrophilic substrate.
-
-\begin{figure}[!th]
-\centering
-\includegraphics[scale=0.45]{./Figures/DifferentElectrospinningMethods.png}
-\decoRule
-\caption[Different Electrospinning Methods in Terms of Spatial Control, Fiber Throughput and Resolution]{Different Electrospinning Methods in Terms of Spatial Control, Fiber Throughput and Resolution.
-Adapted from \cite{Tourlomousis2017}}
-\label{fig:DifferentElectrospinningMethods}
-\end{figure}
-
-As depicted in Figure \ref{fig:DifferentElectrospinningMethods}, solution electrospinning yields fiber with higher resolution than melt electrospinning techniques, and near-field electrospinning offers greater spacial control on the deposition of fibers than the far-field technique.
-Moreover, solution electrospinning often involves the use of toxic solvents, whereas melt electrospinning is a solvent free process but with extra complexity as a heater needs to be installed.
-\cite{Tourlomousis2017}
+In contrast, Choi et al.\unskip~\cite{527120:12322289} implemented a hydrophilic substrate to deposit the fibers with plasma treatment to increase the conductivity of selected areas.
+NFES was carried out with precise deposition as the fibers were placed as per the desired design within the hydrophilic substrate.
 
@@
 
-Near-field electrospinning process parameters and achieved fiber morphology data was collected into a single database with the purpose to analyze the data and find correlations between the process parameters and the obtained fiber morphology after a NFES process.
-The alalysis comprises from the first reported NFES apparatus built in 2003 by J.
+The near-field electrospinning process parameters and the morphological data (diameters and images) reported in papers reviewed was collected and classified into a single database with the purpose of analyzing and finding correlations between the process parameters and the obtained fiber diameter after a NFES process.
+The analysis was based from data ranging from the first reported NFES apparatus built in 2003 by J.
 Kameoka et al.
@@
   Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
-  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014} The data collection process was divided in three procedures depending on the format of the available information, as follows:
+  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014} The data was divided in three groups depending on the format of the available information, as follows:
 
 \begin{enumerate}
-\item Case 1 : data is collected as is from literature. This procedure was implemented when the data is listed within tables and/or as text format.
+\item Case 1 : data is collected as-is from literature. This procedure was implemented when the data is listed within tables and/or as text format.
 \item Case 2 : data is only presented in a figure as plots.
@@
 The reported figures provide a visual relationship between the variables of interest, however recovering the numerical values of the data is a tedious process prone to errors.
-To avoid mistakes and accelerate the collection data from plots, \href{https://github.com/ankitrohatgi/WebPlotDigitizer}{WebPlotDigitizer} was used.
+To avoid mistakes and accelerate the acquicition of data from the plots, \href{https://github.com/ankitrohatgi/WebPlotDigitizer}{WebPlotDigitizer} was used.
 WebPlotDigitizer is a HTML5 tool that facilitates accurate data extraction with ease of use.
@@
 
-The adopted image analysis was implemented with the \emph{Python} package \emph{OpenCV}.
-First a segmentation procedure is executed over an input image to delimit the objects to be measured (fiber sections and scale bar).
+The adopted image analysis was implemented with the \emph{Python} package \emph{OpenCV} (Appendix \ref{Appendix_ImageAnalysisCode}).
+First a segmentation procedure is executed over an input image to delimit the objects to be measured (fiber sections and scale-bars).
 The segmentation step is the only step needed to be done manually in a image processing software, in this case \emph{Inkscape} was used.
-Next, the segmented image is passed to the \emph{Pyhton} script, which will convert its input image into a binary image.
-A binary image is a black and white image (with no gray scale) that ease the detection of the object edges as the color intensity change between the objects and the background is well defined.
+Next, the segmented image is passed into the \emph{Pyhton} script, which will convert its input image into a binary image.
+A binary image is a black and white image (with no gray scale) that facilitates the detection of the object edges as the color intensity change between the objects and the background is well-defined.
 Once the binary image is computed, the \emph{Canny} edge detection algorithm is executed.
-Once the edges are well defined, a the image is dilated to make the edges more visible.
+Once the edges are well-defined, the image is dilated to make the edges more visible.
 The final step before measurement, the \emph{OpenCV} \emph{findContours} function is called to store the objects in memory.
@@
 Measurements were validaded with Camillo's, Gupta's, Jiang's, Min's, Sun's, Wang's, and Xue's \cite{Camillo2013, Gupta2007, Jiang2018, Min2013, Sun2006a, Wang2015, Xue2014} results as those authors reported both, a SEM image and the measured fiber diameter.
-For instance, Figure \ref{fig:imageAnalysisToolValidation} shows in white the reported diameters by Min and in blue the diameters measured by the \emph{Python script}.
+For instance, Figure \ref{fig:imageAnalysisToolValidation} shows in black the reported diameters by Min and in white the diameters measured by the \emph{Python script} of two samples.
 The measurement error of the developed script is about $3.2\%$ in average.
 It is considerable to mention that the reported measurement error is mainly contributed to the fact that most fibers are not of the same diameter along the fiber length.
-In most cases, measurements at the end of the fibers are thicker than the ones measured u¿in the center.
+In most cases, measurements at the end of the fibers are thicker than the ones measured in the center.
 
@@
 \section{Discussion \& NFES Challenges}
+\label{sec:parametersThatAffectTheDiameter}
 
@@
 \unskip~\cite{527120:11974308} with the intention of depositing aligned fibers.
-The authors fabricated a stretchable piezoelectric device using micro and nano fibers to demonstrate the possible applications of HE-printing for electronics manufacturing.
+The authors fabricated a stretchable piezoelectric device using micro- and nano-fibers to demonstrate the possible applications of HE-printing for electronics manufacturing.
 Duan et al.
-concluded that the fiber morphology is mainly driven by: the stage velocity, the applied voltage, and the nozzle-to-collector distance.
+concluded that the fiber morphology is mainly affected by: the stage velocity, the applied voltage, and the nozzle-to-collector distance.
 
@@
 For instance Chang et al.
-\cite{Chang2008} achieved the thinnest fibers of about $50 nm$ in diameter even though Chang implemented nozzle needles of similar diameter as Shin, Min and Xu by the implementation different settings on the other process parameters.
-\cite{Shin2019, Min2013, Xu2014} It is reasonable to notice that Chang's record of achieving the thinnest fiber may be a one time-successful since, neither the yield rate nor the reproducibility of their technique was not reported.
+\cite{Chang2008} achieved the thinnest fibers of about $50 \textrm{ nm}$ in diameter even though Chang implemented nozzle needles of similar diameter as Shin, Min and Xu by the implementation of different settings on the other process parameters.
+For instance: the glass glass capillary nozzles by Song \cite{Song2015}, the melt-NFES setup by \cite{Brown2011, Brown2014}, the long working distances implemented by Husain \cite{Husain2016}, the low stage velocities by Shin \cite{Shin2019} to fabricate coiled fibers, and the high polymer concentrations by Parajuli \cite{Parajuli2016} are some differences from the traditional NFES setup that are represented as isolated clusters within Figures \ref{fig:plt_Cpolymerwt_vs_Dfiberm}, \ref{fig:plt_Dnozzlem_vs_Dfiberm}, \ref{fig:plt_Lm_vs_Dfiberm}, \ref{fig:plt_Phi0V_vs_Dfiberm}, \ref{fig:plt_Qm3s_vs_Dfiberm} and \ref{fig:plt_vstagems_vs_Dfiberm}.
+It is worth nothing that Chang's thinnest fiber may be a one-time result where, neither the yield rate nor the reproducibility of their technique was not reported.
 
@@
 
-The relationship between the fiber diameter the working distance $L$ and applied voltage $\Phi_0$ can be depicted in Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}.
+The relationship between the fiber diameter, the working distance $L$ and applied voltage $\Phi_0$ can be depicted in Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}.
 The near-field electrospinning jet is ejected from the Taylor cone when the applied voltage generates an electric field strong enough to break the solution drop.
-Changing the applied voltage will amend initial drop and fiber morphology, thereby resulting in a change in the fibers' properties.
-However, the effect of the applied voltage on the fiber diameter is not well defined.
+Changing the applied voltage will change initial drop shape, thereby resulting in a change in the fibers' diameters.
+However, the effect of the applied voltage on the fiber diameter is not well understood.
 On one hand, many researchers posit that high applied voltages lead to larger fiber diameters, whereas other researchers have reported reductions in fiber diameter with high applied voltages as the electric field force increases on the charged jet.
 \cite{Zhang2005} Furthermore, Reneker and Chun observed that applied voltage does not significantly affect the diameter of electrospun polyethylene oxide (PEO) fibers.
-\cite{Reneker1996} Applied voltage has an influence on the fiber diameter, but the degree and direction of influence varies with other process parameters such as polymeric solution concentration and on the working distance \cite{Yordem2008, Chang2016}.
+\cite{Reneker1996} Applied voltage has an influence on the fiber diameter, but the degree and direction of the effect on the diameter varies with other process parameters such as polymeric solution concentration and on the working distance \cite{Yordem2008, Chang2016}.
 
-Looking at Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}, the data points from Husain, Lee and Sonntag \cite{Husain2016, Lee2012, Sonntag2020} experimental results are outside the principal cluster since they implemented working distances around $10^{-1} \textrm{m}$, which is concidered to be the threshold between NFES and far-field electrospinning (FFES).
+Looking at Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}, the data points from Husain, Lee and Sonntag \cite{Husain2016, Lee2012, Sonntag2020} are outside the principal cluster since they implemented working distances around $10^{-1} \textrm{m}$, which is considered to be the threshold between NFES and far-field electrospinning (FFES).
 One can observe that: a) in NFES fiber diameter increase with increasing applied voltage; and b) in FFES fiber diameter decrease with increasing applied voltage.
-On the other hand, data related to Liu's and Beachey's work \cite{Liu2014, Beachley2011} do not fit the main trend as they perform the electrospinning process with a rotating drum as the collector, instead of the typical xy stage.
+On the other hand, data related to Liu's and Beachey's work \cite{Liu2014, Beachley2011} do not fit the main trend as they performed the electrospinning process with a rotating drum as the collector, instead of the typical xy stage.
 
@@
 \textbf{Solution Parameters:} &  \\
-Concentration & Concentration shall be high enough to produce uniform nano-fibers, but low enough to give the correct viscosity \\
-Molecular weight & High molecular weight polymers yield smoother fibers \\
+Concentration & Concentration shall be high enough to produce uniform nano-fibers, but low enough to prevent nozzle clogging \\
+Molecular weight & High-molecular-weight polymers yield smoother fibers \\
 Viscosity & Zero-shear viscosity shall be optimal to generate a constant jet from the needle \\
-Conductivity & Solution shall be conductive enough for the electrif field to have influence on the jet \\
+Conductivity & Solution shall be conductive enough for the electric field to have influence on the jet \\
 \textbf{Process Parameters:} &  \\
 Applied voltage & Higher voltages eject more material from the nozzle \\
-Flow rate & Slow flow rates yield thinner fibers, but it shall be fast enough to prevent clogging and keep the Tailor cone in a constant size and shape \\
-Working distance & Long distances result in thinner fibers, however the spatial control is harmed \\
+Flow rate & Slow flow rates yield thinner fibers, but it shall be fast enough to prevent clogging and keep the Taylor cone in a constant size and shape \\
+Working distance & Long distances result in thinner fibers, however the spatial control is hampered \\
 \textbf{Ambient Parameters:} &  \\
@@
 
-Near-field electrospinning (NFES) is known as a versatile nano-fabrication technique, suitable for several applications such as tissue engineering, chemical sensing, filtration, energy storage, besides others (see Figure \ref{fig:synthesesAndApplicationsOfNanofibers}).
-Fast developments in electrospinning has been observed in recent years.
-However, this process is limited by the electric field wiping instability effects during polymer deposition.
-This leads to a major challenge: how to surpass this limitation of planar two-dimensional prints.
-The current trend in this area lies on the research of new materials, techniques to increase precision patterning in NFES systems.
-
-\begin{figure}[!th]
-\centering
-\includegraphics[width=\textwidth]{./Figures/synthesesAndApplicationsOfNanofibers.png}
-\decoRule
-\caption[Syntheses and Applications of Nanofibers]{Syntheses and Applications of Nanofibers. Adapted from \cite{Kenry2017}}
-\label{fig:synthesesAndApplicationsOfNanofibers}
-\end{figure}
-
 \section{Diameter Prediction of Electrospun Fibers} % adimensional analysis
 
-Electrospinning is a simple process to fabricate fibers of different morphology.
-However, the final morphology of a fiber depends on various solution, process, and ambient parameters (Table \ref{tab:nfesProcessParameters}) with interaction with rheology and fluid dynamics.
+Electrospinning is a simple process to fabricate fibers of different diameters.
+However, the final diameter of a fiber depends on various solution, process, and ambient parameters (Table \ref{tab:nfesProcessParameters}) with interaction with rheology and fluid dynamics.
 Given the connection of various parameters, it is not trivial to derive a mathematical model to describe the complete electrospinning process.
@@
 
-As mentioned in the previous section, the correlation between the final fiber diameter $D_{fiber}$ and the applied voltage $\Phi_0$ is not well defined.
+As mentioned in the previous section, the correlation between the final fiber diameter $D_{fiber}$ and the applied voltage $\Phi_0$ is not well understood.
 Most authors posit that the fiber diameter decreases with increasing voltage.
@@
 studied the relationship between the solution surface tension $\gamma$ and its conductivity $K$.
-\cite{Zhang2005, Kim2005, Mituppatham2004} Kim's and Mituppatham's work report a increase in fiber diameter with increasing conductivity in the polymer solution, while Zhang's reports the inverse relationship.
+\cite{Zhang2005, Kim2005, Mituppatham2004} Kim's and Mituppatham report a increase in fiber diameter with increasing conductivity in the polymer solution, while Zhang reports the inverse relationship.
 The existing interdependence between the process and solution parameters adds complexity and ambiguity to the effect of each parameter.
@@
 
-Helgeson and Wagner \cite{Helgeson2007} have presented an adimensional analysis to predict the fiber diameter with conservation equations of momentum, mass, electric charge and four dimensionless numbers: Peclet number $ \displaystyle Pe = \frac{2 \bar{\varepsilon} v_0}{K R_0} $, Reynold number $ \displaystyle Re = \frac{\rho v_0 R_0}{\eta_0} $, Weber number $ \displaystyle We = \frac{\rho {v_0}^2 R_0}{\gamma} $, and the dimensionless electric field strength $ \displaystyle \Psi = \frac{\bar{\varepsilon} {E_0}^2}{\rho {v_0}^2} $.
+Helgeson and Wagner \cite{Helgeson2007} have presented a dimension-less analysis to predict the fiber diameter with conservation equations of momentum, mass, electric charge and four dimensionless numbers: Peclet number $ \displaystyle Pe = \frac{2 \bar{\varepsilon} v_0}{K R_0} $, Reynold number $ \displaystyle Re = \frac{\rho v_0 R_0}{\eta_0} $, Weber number $ \displaystyle We = \frac{\rho {v_0}^2 R_0}{\gamma} $, and the dimensionless electric field strength $ \displaystyle \Psi = \frac{\bar{\varepsilon} {E_0}^2}{\rho {v_0}^2} $.
 Where $\bar{\varepsilon}$ is the dielectric permitivity of the atmosphere, $K$ the solution conductivity, $\rho$ the density, $\eta_0$ the zero-shear viscosity, $\gamma$ the surface tension, $E_0$ the applied electric field, $R_0$ the initial jet radius, and $v_0$ the initial jet velocity.
@@
 
-Ohnesorge number, resulting from the manipulation of the Reynolds number $Re$ and the Weber number $We$, is used to explain the behavior of the polymeric solution jet under small disturbances, due the voltage presence, leads to the capillary rupture of the fluid jet.
+the Ohnesorge number, resulting from the manipulation of the Reynolds number $Re$ and the Weber number $We$, is used to explain the behavior of the polymeric solution jet under small disturbances, due the presence of a voltage, leading to the capillary rupture of the fluid jet.
 \cite{Helgeson2007}
@@
 
-Figure \ref{fig:plt_Pi1_vs_Oh} plots the $\Pi_1$ and $Oh$ values reported by \cite{Helgeson2007} along with new data points from the previous data collection of NFES fiber diameters and process parameters.
-It is possible to observe the predominance of the viscous and the electrostatic forces within the solution by the magnitude $\Pi_1$ (Equation \ref{eqn:electroViscousRatio}), on the other hand $Oh$ (Equation \ref{eqn:ohnesorgeNumber}) reflects the capacity of the viscous forces over the polymeric jet, which allows stability in the electrospinning process.
+Figure \ref{fig:plt_Pi1_vs_Oh} plots the $\Pi_1$ and $Oh$ values reported by \cite{Helgeson2007} along with new data points from the data collection of NFES fiber diameters and process parameters.
+It is possible to observe the predominance of the viscous and the electrostatic forces within the solution by the magnitude $\Pi_1$ (Equation \ref{eqn:electroViscousRatio}).
+On the other hand $Oh$ (Equation \ref{eqn:ohnesorgeNumber}) reflects the capacity of the viscous forces over the polymeric jet, which allows stability in the electrospinning process.
 The data points gathered by Helgeson et al.
@@
 
-The collected data suggest that both types of electrospinning behave in a similar manner, where the FFES data fits better a linear behavior of slope $-1$.
+The analysis suggests that both types of electrospinning behave in a similar manner, where the FFES data fits better a linear behavior of slope $-1$.
 As the working distance closes in NFES, the data points fit a shallower slope with higher $\Pi_1$ values and lower $Oh$ values.
@@
 Helgeson et al.
-suggest that with the following relationship in Equation \ref{eqn:ohnesorgeNumberRelationship} can be used to predict the fiber diameter, as in the trend in Figure \ref{fig:plt_Pi1_vs_Oh} $Oh$ has an inverse linear relationship with $\Pi_1$.
+suggest that the following relationship in Equation \ref{eqn:ohnesorgeNumberRelationship} can be used to predict the fiber diameter, as in the trend in Figure \ref{fig:plt_Pi1_vs_Oh} $Oh$ has an inverse linear relationship with $\Pi_1$.
 \cite{Helgeson2007}
@@
 The absence of the solution zero-shear viscosity in Equation \ref{eqn:ohnesorgeNumberRelationship} suggests that $\eta_0$ by its own is insufficient to predict the fiber diameter.
-The solution conductivity, process parameters and surface tension are the main drivers to describe the diameter of electrospun fibers.
-\cite{Helgeson2007}
+The solution conductivity, process parameters and surface tension are also needed to describe the diameter of electrospun fibers \cite{Helgeson2007}, as stated in section \ref{sec:parametersThatAffectTheDiameter}.
+Moreover, the viscosity term is embedded within the mass fraction of the polymer in solution $w_s$ in the $R_{jet}$ term.
+Finally, Equation \ref{eqn:ohnesorgeNumberRelationship} can be validated by the observations from the correlation matrix and scatter plots as the same parameters are present in both analyses with the same proportional relationship.

### 2020-12-02 05_Thesis/THESIS_LaTeX/Chapters/3.tex
final work done

@@
 Zhenan Bao et al.
-\cite{Liu2015a} investigated the effect of the polymer chemical structure (the effect of benzene rings) on the morphology, dimensions, composition, graphitization degree, crystallinity, and electrical conductivity of graphene nano-ribbons derived from four different types of electrospun polymers.
+\cite{Liu2015a} investigated the effect of the polymer chemical structure (the effect of benzene rings) on the morphology, dimensions, composition, graphitization degree, crystallinity, and electrical conductivity of graphene nano-ribbons derived from four different types of electrospun polymers as templating agents.
 The authors studied four polymers polystyrene (PS), poly(vinyl alcohol) (PVA), polyvinylphenol (PVP), and a phenolic resin known as Novolac.
@@
 PVP, Novolac and PVA have hydroxyl groups that can be functionalized with metal cations, while PS does not have such binding capability.
-On the other hand, PVP and Novolac have one benzene ring in each repeating unit, wheras PVA is mainly made out of sp3 carbon.
+On the other hand, PVP and Novolac have one benzene ring in each repeating unit, wheras PVA is mainly made out of sp3-hybridized carbon.
 
@@
 This finding can be use as a guide when choosing polymer precursors for the fabrication of carbon structures.
-Furthermore, the authors posit that polymers with functional groups are required for the creation of smooth and continuous fibers throw electrospinning.
+Furthermore, the authors posit that polymers with functional OH groups are required for the creation of smooth and continuous fibers throw electrospinning.
 \cite{Liu2015a}
@@
 Given the conclusions from Zhenan Bao et al.
-\cite{Liu2015a} along with the extensive literature review and data analysis of Chapter \ref{Chapter:2}, the following polymer solutions were selected to be studied in this work.
+\cite{Liu2015a} along with the extensive literature review and data analysis of Chapter \ref{Chapter:2}, the following polymer-solvent combinations were selected to be studied in this work.
 Polymer selection was based on the their high carbon content and presence of benzene rings.
-The purpose of the polymer selection is to focus the efforts to maximize the likelihood of polymers to yield carbon structures with high electrical conductivity and high graphitization degree; as testing every possible polymer-solvent system is not a practical way to carry on this research.
-Figure \ref{fig:selectedpolymers} lists the polymers that are going to be investigated.
+The purpose of the polymer selection is to focus the efforts to maximize the likelihood of polymers to yield carbon structures with high electrical conductivity and a higher degree of graphitization as compared to the previously used SU-8/PEO combination in cyclopentanone; as testing every possible polymer-solvent system is not a practical way to carry on this research.
+Figure \ref{fig:selectedpolymers} lists the polymers that are going to be investigated along with their proposed solvents.
 The selected polymers have been electrospun via far-field electrospinning for the fabrication of fibrous mats \cite{Fong1999, Min2013, Yousefi2019}, but no records of being spunable by NFES.
@@
 
-Solutions at low concentrations do not allow polymer chains to entangle leading the viscoeslasticity od the solution dependent only on individual polymer chains.
-As the polymer concentration increases, the chains overlap and become entangled.
+Solutions at low concentrations do not allow polymer chains to entangle, leading the viscoeslasticity of the solution dependent only on the interaction of individual polymer chains.
+As the polymer concentration increases, the chains overlap and becomes entangled.
 The concentration at which the entanglement initially takes place is the critical concentration $c^*$.
 Concentrations above the critical concentration $c^*$ generate a fast increase in chain entanglement (Figure \ref{fig:criticalConcentrationEntanglement}).
-This rapid change in chain entanglement is translated into a fast increase in the viscoelasticity of the solution.
+This rapid change in chain entanglement is translated into a fast increase in the viscosity of the solution.
 Figure \ref{fig:concentrationViscosityPlotExplained} illustrates the relationship between polymer concentration and viscoelasticity.
@@
 
-Electrospinning of smooth, continuous fibers require a polymer concentration higher than the critical concentration.
-As shown in Figure \ref{fig:concentrationViscosityPlotExplained}, the critical concentration can be estimated from the change in slope.
+Electrospinning of smooth, continuous fibers require a polymer concentration equal or higher than the critical concentration.
+As shown in Figure \ref{fig:concentrationViscosityPlotExplained}, the critical concentration can be estimated from the change in slope of the log-viscosity to log-concentration curve.
 \cite{Burghelea2020, Gupta2005, Han2019} Therefore, in order to find the critical/spinnable concentrations of the candidate polymer-solvent solutions (poly(styrene-co-butadiene) in tetrahydrofuran, poly(9-vinyl carbazole) in chloroform, polyestyrene in tetrahydrofuran, and poly(styrene-co-a-methylstyrene) - See Figure \ref{fig:selectedpolymers}), it is necessary to build the appropriate viscosity vs.
@@
 Seven polymer-solvent combinations are to be tested.
-The Poly(Ethylene Oxide) and SU-8 2002 combination is what has been used in past work \cite{Cardenas2017, Flores2017}, and will be used as the control sample set.
-The selected polymer-solvent combinations are to investigate the ability of oxygenless polymers to be electrospun and then carbonized into vitreous carbon.
+The Poly(Ethylene Oxide) and SU-8 2002 combination is what has been used in previous work \cite{Cardenas2017, Flores2017}, and will be used as the control sample set.
+The selected polymer-solvent combinations were selected to investigate the ability of oxygenless polymers to be electrospun and then carbonized into vitreous carbon.
 Tables \ref{tab:PEOinSU8}, \ref{tab:PSBinNMP}, \ref{tab:PSBinTHFnDMF}, \ref{tab:PSMSinDMF}, \ref{tab:PSinTHF}, \ref{tab:PVKinCHL}, and \ref{tab:PVKinSU8} list the prepared polymer systems.
@@
 {}          & \textbf{THF} & \textbf{DMF} & \textbf{PSB} & \textbf{TBF} \\
-\textbf{18} & 70.875       & 23.625       &  5.00        & 0.50         \\
-\textbf{19} & 69.000       & 23.000       &  7.50        & 0.50         \\
-\textbf{20} & 67.125       & 22.375       & 10.00        & 0.50         \\
-\textbf{21} & 65.250       & 21.750       & 12.50        & 0.50         \\
-\textbf{22} & 63.375       & 21.125       & 15.00        & 0.50         \\
-\textbf{23} & 59.625       & 19.875       & 20.00        & 0.50         \\
-\textbf{24} & 55.875       & 18.625       & 25.00        & 0.50         \\
+\textbf{18} & 70.87        & 23.63        &  5.00        & 0.50         \\
+\textbf{19} & 69.00        & 23.00        &  7.50        & 0.50         \\
+\textbf{20} & 67.12        & 22.38        & 10.00        & 0.50         \\
+\textbf{21} & 65.25        & 21.75        & 12.50        & 0.50         \\
+\textbf{22} & 63.37        & 21.13        & 15.00        & 0.50         \\
+\textbf{23} & 59.62        & 19.88        & 20.00        & 0.50         \\
+\textbf{24} & 55.87        & 18.63        & 25.00        & 0.50         \\
 \hline
@@
 SU-8 2002 was obtained from MicroChem (Newton, MA, USA), while Tetrabutylammonium Tetrafluoroborate (TBF) of $99\%$ purity were, Poly(Ethylene Oxide) (PEO), Polystyrene (PS), Poly(Styrene-co-Butadiene) (PSB), Poly(Styrene-co-alpha-Methylstyrene) (PSMS), Poly(9-Vinylcarbazole) (PVK), Tetrahydrofuran (THF), 1-Methyl-2-Pyrrolidinone (NMP), N,N-Dimethylformamide (DMF), and Chloroform (CHL) were obtained from Sigma-Aldrich (Saint Louis, MI, USA).
-PEO has a viscosity-average molecular weight Mv of ~4,000,000, with less than 1000 ppm of Butylated Hydroxytoluene (BHT) as an inhibitor.
+PEO has a viscosity-average molecular weight Mw of ~4,000,000, with less than 1000 ppm of Butylated Hydroxytoluene (BHT) as an inhibitor.
 PS has an average molecular weight Mw of ~192,000.
@@
 
-Samples of 3 militers were prepared with the adecuate amounts of polymer, salt and solvent.
-Solutions were stired at $160 rpm$ for $2 hours$ at $60^{\circ}C$.
+Samples of 3 milliliters were prepared with the adecuate amounts of polymer, salt and solvent.
+Solutions were stired at $160 \textrm{ rpm}$ for $2 \textrm{ hours}$ at $60^{\circ}C$.
 Samples with higher polymer concentrations often required more stirring time to eliminate all polymer aggregates.
-All solutions were left undisturbed for $3 hours$ in 4 ml vials to eliminate bubbles from the solution.
+All solutions were left undisturbed for $3 \textrm{ hours}$ in $4 \textrm{ ml}$ vials to eliminate bubbles from the solution.
 
 \subsection{Rheological Characterization of polymer Solutions}
-All of the rheological tests were performed in a rotational rheometer (Discovery Hybrid Rheometer DHR, TA Instruments) equipped with a cone-and-plate (CP) geometry (diameter of $60 mm$, angle of $0.9969^{\circ}$, and truncation of $23 \mu m$) in a steel Peltier plate (Figure \ref{fig:solventTrap}a).
-The experiments were conducted at $20^{\circ}C$ and $3 hours$ after polymer solution preparation.
-Flow curve (FC) tests were conducted to obtain viscosity curves in function of the shear rate.
+All of the rheological tests were performed in a rotational rheometer (Discovery Hybrid Rheometer DHR, TA Instruments) equipped with a cone-and-plate (CP) geometry (diameter of $60 \textrm{ mm}$, angle of $0.9969^{\circ}$, and truncation of $23 \textrm{ } \mu \textrm{m}$) in a steel Peltier plate (Figure \ref{fig:solventTrap}a).
+The experiments were conducted at $20^{\circ}C$ and $3 \textrm{ hours}$ after polymer solution preparation.
+Flow curve (FC) tests were conducted to obtain viscosity curves as a function of the shear rate.
 Analysis were performed at shear rate range from $10^{-3} \textrm{ 1} / \textrm{s}$ to $10^{4} \textrm{ 1} / \textrm{s}$.
@@
 Where: $\eta$ is the viscosity, $\dot{\gamma}$ the shear rate, $\eta_{\infty}$ the  infinite shear rate viscosity, $\eta_0$ the zero shear rate viscosity, $\kappa$ is the time constant, $n$ the Power Law index, $a$ the width of the transition region between the zero shear viscosity and the Power Law region.
-The model was fitted to the rheologial data to estimate $\eta_0$.
+The features of the flow curves shown in Appendix \ref{Appendix_flowCurves} can be modeled using the Carreau-Yasuda model, with the benefits that it is possible to describe the shape and curvature of a flow curve through six fitting parameters and to predict behavior at unmeasured shear rates.
+The Carreau-Yasuda model is most applicable model due to the range of the measured data.
+Unlike the Sisko and Williamson models, the Carreau-Yassuda model considers both the infinite- and zero-shear rate viscosities.
+
+The Carreau-Yasuda model was fitted to the rheologial data to estimate $\eta_0$.
 Then, $\eta_0$ values are used to create diagrams that describe the effect of polymer concentration on the solution viscosity, as described in Figure \ref{fig:concentrationViscosityPlotExplained}.
@@
 
-Table \ref{tab:calculatedSpinnableConcentrations} summarizes the calculated critical concentrations for each system.
-In general, the critical concentration $c^*$ has proportional relationship with the polymer molecular weight, as a polymer's molecular weight greatly influences the solution viscosity.
-First, the structure of the polymer chain has an effect on its solubility as the intermolecular interactions between long molecules are stronger and the solvent molecules take longer to diffuse within the polymer aggregates.
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/ALLcriticalConcentrationCalculation.png}
+\decoRule
+\caption[Estimation of the Critical Concentration of the Candidate Polymer-Solvent Combinations]{Estimation of the Critical Concentration of the Candidate Polymer-Solvent Combinations.
+Individual plots are available in Appendix \ref{Appendix_CriticalConcentrations}}
+\label{fig:ALLcriticalConcentrationCalculation}
+\end{figure}
+
+Table \ref{tab:calculatedSpinnableConcentrations} was built from Figure \ref{fig:ALLcriticalConcentrationCalculation}, and summarizes the calculated critical concentrations for each system.
+In general, the critical concentration $c^*$ has a directly proportional relationship with the polymer molecular weight, as a polymer's molecular weight greatly influences the solution viscosity.
+First, the structure of the polymer chain has an effect on its solubility as the inter-molecular interactions between long molecules are stronger and the solvent molecules take longer to diffuse within the polymer aggregates.
 \cite{Ramakrishna2005, Floreshernandez2020} Second, the viscosity of a polymer solution will be smaller when a polymer of low molecular weight is dissolved than a solution of the same polymer but of a higher molecular weight.
 \cite{Ramakrishna2005} The molecular weight of the polymer describes the length of the polymer chain, which has an effect on the viscosity of the solution.
-Since the polymer length defines the amount of entanglement of the polymer chains in the solvent, a lower molecular weight shall be compensated by higher concentrations to reach the desired viscosity.
+Since the polymer length defines the amount of entanglement of the polymer chains in the solvent, a lower molecular weight shall be compensated by higher concentrations to reach the desired viscosity, see Figure \ref{fig:criticalConcentrationViscoAndMolWeight}.
+
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/criticalConcentrationViscoAndMolWeight.png}
+\decoRule
+\caption{Relationship between the critical concentrations, molecular weights, and zero-shear viscosities of the selected polymer solutions.}
+\label{fig:criticalConcentrationViscoAndMolWeight}
+\end{figure}

### 2020-12-02 05_Thesis/THESIS_LaTeX/Chapters/4.tex
defense update
final work done

--- 2020-08-20 5_Thesis/THESIS_LaTeX/Chapters/4.tex
@@
 
-\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning, and Forward-thinking on Photopolymerization and Pyrolysis} % Main chapter title
+\chapter{Fabrication and Characterization of Polymeric Fibers through Near-Field Electrospinning} % Main chapter title
 
@@
 
-%----------------------------------------------------------------------------------------
-%	SECTION 1
-%----------------------------------------------------------------------------------------
-\section{}
+The fabrication and characterization of polymeric fibers is addressed in this chapter as the last screening procedure to select the PEO/SU-8 replacement.
+The PEO/SU-8 replacement is to produce microscopic polymer fibers with potential for the fabrication of carbon nano-wires.
+This chapter reports PEO, PS, PSB, and PVK micro-fibers fabricated by low-voltage near-field electrospinning.
+The fabrication process is carried on to study the influence of applied voltage on the fiber diameter.
+The materials and sample preparation for the LV-NFES process are the same as those used in the rheological analyses in Chapter \ref{Chapter:3}.
 
-%----------------------------------------------------------------------------------------
-%	SECTION 2
-%----------------------------------------------------------------------------------------
-\section{}
+\section{Near-Field Electrospinning Setup}
 
-%----------------------------------------------------------------------------------------
-%	SECTION 3
-%----------------------------------------------------------------------------------------
-\section{Fabrication and Characterization of Legacy SU-8 carbon fibers}
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.50]{./Figures/NFESsetup.png}
+\decoRule
+\caption[NFES experimental setup]{NFES experimental setup. Adapted from \cite{Floreshernandez2020}}
+\label{fig:NFESsetup}
+\end{figure}
 
-\section{\emph{conclude with fibre morphology before and after pyrolysis. determine best pyrolysis process}}
-%Were the selected candidates electrospunable?
-%Fiber morphology
-%Yield rate
-%Carbon content
-%Conductivity
-%Fiber morphology
+The near-field apparatus (Figure \ref{fig:NFESsetup}) is comprised by a high voltage supply (HVS448 3000 V, LabSmith, Livermore, CA, USA), a three-axis stage, syringe pump (Pump 11 Elite, Harvard Apparatus, Cambridge, MA, USA).
+Samples were prepared as per the rheology measurements in Chapter \ref{Chapter:3}.
+Experiments were conducted with 1 milliliter slip-tip insulin syringes with 21 gauge precision tips (Nordson Engineered Fluid Dispensing, Westlake, OH, USA).
+The power supply and 3-axis stage are controlled through a desktop computer, while the syringe pump is controlled manually.
+Fiber depositions were placed on a $\textrm{Si}-\textrm{SiO}_2$ wafer.
+The voltage between the nozzle tip and the collector was varied between $200 [\textrm{V}]$ and $600 [\textrm{V}]$ in increments of $100 [\textrm{V}]$, keeping a constant current of $10 \textrm{ } \mu \textrm{A}$.
+For applied voltages under $400 [\textrm{V}]$, the electric field was not strong enough to overcome the surface tension of the polymer solution and initiate the jet.
+To enable the fiber deposition at low voltages, the polymer jet was manually initialized by breaking the surface tension with a sharp glass tip.
+The working distance $L$ and stage velocity was set at a constant values for all the experiments at $0.5 mm$ and $10 mm/s$ respectively.
+The syringe pump was set at a steady flow rate of $0.04 \mu \textrm{L} / \textrm{min}$.
+
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.50]{./Figures/microscope.png}
+\decoRule
+\caption{Correct, Seiwa Optical - Optical Microscope}
+\label{fig:microscope}
+\end{figure}
+
+The applied voltage range was set in a range between $200 [\textrm{V}]$ and $600 [\textrm{V}]$, since within that range fibers were able to electrospun into continuous and straight fibers.
+As shown in Figure \ref{fig:lowVoltageHighVoltage}, PEO/SU-8 fibers are produced with a meander morphology when the applied voltage is around $900 [\textrm{V}]$.
+Under $600 [\textrm{V}]$, straight and aligned fibers were fabricated and characterized.
+
+The calculated critical concentrations in Chapter \ref{Chapter:3} (Table \ref{tab:calculatedSpinnableConcentrations}) are used for the fabrication of polymeric fibers.
+One set of experiments was conducted for each polymer-solvent system to study the effect of applied voltage on fiber diameter.
+The morphology of the fibers was characterized with an optical microscope (Correct, Seiwa Optical, Dallas, TX, USA, Figure \ref{fig:microscope}).
+Each sample was measured at 30+ points within the microscope field of view (Appendix \ref{Appendix_MicroscopyChar}).
+
+\begin{figure}[!th]
+\centering
+\includegraphics[scale=0.40]{./Figures/lowVoltageHighVoltage.png}
+\decoRule
+\caption{Effect of applied voltage in fiber morphology}
+\label{fig:lowVoltageHighVoltage}
+\end{figure}
+
+\section{Results}
+
+\begin{figure}[!th]
+\centering
+\includegraphics[width=\textwidth]{./Figures/boxplotsFiberDiameter.png}
+\decoRule
+\caption[Diameter of fibres for all the experiments]{Diameter of fibres for all the experiments with varing applied voltage $\Phi_0$. Appendix \ref{Appendix_FiberDiameters}}
+\label{fig:boxplotsFiberDiameter}
+\end{figure}
+
+Figure \ref{fig:boxplotsFiberDiameter} shows a dependence of fiber diameter as a function of the applied voltage and confirms what was already noticed in the correlation matrix and the adimensional analysis in Chapter \ref{Chapter:2}, as lower voltages yield fibers with thinner diameters.
+This results verify the electro-spinnability of oxygen-less polymers by NFES into fibers of $1 \mu m$ to $5 \mu m$ in diameter.
+PS presented complications during the NFES process as fibers of this polymer do not adhere onto the substrate making them prone to fracture or substrate abandonment, specially when printing fibers of thin diameters.
+To ease this complication the working distance $L$ can be reduced to let the fibers dry on the surface and prevent complete solidification while traveling the distance $L$.
+The increase in applied voltage can also help with this problem as more material is pulled out of the dispensing needle, however this two fixes will translate into thicker fibers.
+
+The effect of applied voltage on fiber diameter can be contributed to the effect of the electric field on the surface tension of the polymer solution drop.
+Bateni and coworkers \cite{Bateni2005} have shown that surface tension increases with increasing applied voltage.
+Bateni also states that the effect of an electric field is stronger on alcohols with higher molecular weights \cite{Bateni2005}.
+Bateni's findings agree with Zhenan Bao's statements regarding polymers with OH functional groups are more easily electrospun than those without functional groups \cite{Liu2015a, Bateni2005}.
+Since the tested polymers are of different molecular weights, the effect of applied voltage is more significant in the PEO/SU-8 formulation as PEO has the highest molecular weight.
+On the other hand, the PSB in THF and DMF solution was the least affected by changes in applied voltage as PSB has the smallest molecular weight.
+Disregarding the molecular weight, the PS formulation has higher variation in fiber diameter.
+This outcome can be explained by the poor adhesion of the fibers to the substrate, as explained above.
+The effect of the applied voltage between the two PVK samples present some differences.
+The PVK in CHL solution has a stronger reaction to the electric field than the PVK in SU-8 formulation.
+This difference can be attributed to the fact that SU-8 is comprised by a series of monomers of low molecular weight.
+
+The PVK and CHL system was the one that behaved with more similarity as the control sample of SU-8 and PEO.
+Uniform, $700 \textrm{ nm}$ diameter fibers were achieved with PVK and CHL at the lowest voltage setting ($200 \textrm{ V}$).
+Given the similarities with the control sample, PVK was choosen to replace the PEO to increase the spinnability of SU8.
+Therefore, the PVK in SU-8 system was tested in the same conditions as the previous experiments.
+Both polymers (PEO and PVK) in SU-8 yield parallel results in fiber morphology and in electrospinning preformanc.
+However, at high voltages, the PVK solution produced thinner fibers than those produced by the PEO solution.
+Moreover, as PVK does not contain any additional oxygen content in its structure, adding PVK can be a better alternative to electrospun SU-8 based fibers intended for carbonization as thinner fibers will have better opportunities to survive the pyrolysis process without breaking.
+
+On the other hand, the polymer-solvent systems comprised by Poly(Styrene-co-Butadiene) (PSB) in 1-Methyl-2-Pyrrolidinone (NMP) and Poly(Styrene-co-alpha-Methylstyrene) (PSMS) in N,N-Dimethylformamide (DMF) were unable to yield fibers.
+In the case of the PSB/NMP solutions, a hard shell was formed around the polymer drop at the tip of the nozzle preventing the jet to initiate, which causes clogging.
+Seems that rapid volatilization of NMP is not the case as PSB was successfully electrospun with more volatile solvents (THF and DMF).
+Notice that vapor pressure of NMP is around $39 \textrm{Pa}$ at $25^{\circ} C$, THF and DMF have vapor pressures of about $19.3 \textrm{kPa}$ at $20^{\circ} C$ and $0.49 \textrm{kPa}$ at $25^{\circ} C$ respectively.
+\cite{ICSCs} On the other hand, PSMS in DMF was not able to produce fibers as the jet was not initiated.
+After noticing that que calculated critical concentration $c^*$ is not spinnable the solutions of 10 and 15 $wt\%$ were also tested in the NFES apparatus with no success.
+The cause of the non-spinnable nature of PSMS can be laid on the fact that PSMS pellets were brittle and capable of making fine PSMS dust with ease, unlike PS and PSB pellets which have an elastic behavior.

### 2020-12-02 05_Thesis/THESIS_LaTeX/Chapters/5.tex
able to fit lin
final work done

--- 2020-05-28 myThesis/thesis_LaTeX/Chapters/5.tex
@@
 
-\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning and Photopolymerization} % Main chapter title
+\chapter{Concluding Remarks} % Main chapter title
 
@@
 %----------------------------------------------------------------------------------------
-\section{}
+\section{Conclusions}
 
-%Were the selected candidates electrospunable?
-%Fiber morphology
+As stated within the introductory chapter \ref{Chapter:1}, this thesis is to verify the near-field electrospinnability of high-carbon oxygen-less polymers in solution.
+The spinnability of the tested solutions is used as a screening to choose candidate formulations that can replace the PEO in SU-8 solution.
+A near-field electrospinning literature review was used to learn about the effect of the process parameters and solution properties in the control of the fiber diameter.
+The review analyses (data analysis, parameter correlation, and adimensional analysis) declare that the polymer concentration is the parameter with the biggest impact on the fiber diameter, followed by the applied voltage, the working distance, and the zero-shear viscosity.
+
+Rheological analyses were performed to determine the viscoelastic properties of the candidate polymer solutions.
+Zero-shear viscosities of the solutions in interest are measured  to find solutions with spunable polymer concentrations.
+As explained in the following, viscosity and polymer concentration have a significant impact on the spinnablity of polymer solutions, but they are not sufficient by themselves.
+As demonstrated by the experiments to fabricate fibers through NFES, PSMS in DMF and PSB in NMP formulations were not spinnable at their critical concentrations.
+
+A series of experiments were carried out in order to find a correlation between the rheological properties of different polymer solutions in near-field electro-mechanical spinning for carbon structures.
+Flow curve measurement tests where carried out in an oscillatory rheometer to estimate the critical concentrations of various polymer-solvent systems at which they are spinnable by NFES.
+Since the formulation is 0.25 $wt\%$ PEO in SU-8 2002 has been studied in the past and is known to yield good polymer solutions but fails at the pyrolysis, this work intends to find spinnable and pyrolyzable systems as well as a method to discover new spinnable polymer solutions.
+
+From the flow curve measurements, the zero-shear viscosity was estimated using the Carreau-Yassuda model.
+For all solutions, a shear thinning behavious was noticed.
+It was found that the viscosity-concentration plot is a good method to find the critical concentration at which the solution is able to produce fibers through NFES.
+However the method failed at calculating the spinnable concentration of PSMS.
+An significant takeaway is that a polymer does not have elastic properties in the pellet form, it will probably not work as a NFES polymer precursor.
+
+Fibers were fabricated at different applied voltages for each set of solutions in order to very that in NFES fiber diameter increases with increasing applied voltage, whereas the inverse relationship is true for FFES.
+Other parameters such as working distance, stage velocity, nozzle diameter, flow rate were kept constant for all experiments; however, for low applied voltages the jet shall be initialed by manually breaking the polymer drop.
+the thickest average fiber diameter was achieved with the PS in THF system ($\Phi_0 = 600 V$, $D_{fiber} = 5.304 \mu m$) and the thinnest was $0.976 \mu m$ using the PVK in CHL system and an applied voltage of $200 V$.
+It was proved that attainable rehological information can be used to modify the NFES process parameters to yield the desired fiber morphology.
+
+Moreover a data analysis was done on the NFES publications of the last 13 years to identify relationships between fiber diameter and the process parameters.
+For instance, it was confirmed that thin fibers are achived with los polymer concentrations, small nozzle diameters, low applied voltage, slow flow rates and high stage velocities.
+Also, using the collected data and the input of Helgeson's work \cite{Helgeson2007}, an dimensionless analysis was done to predict fiber diameters with easy to get parameters.
+
+Finally, the fabricated fibers can be classified into three groups: a) the control sample (PEO in SU-8); b) poor quality fibers (PS in THF, and PSB in THF and DMF); and c) good quality fibers (PVK in CHL and PVK in SU-8).
+PS and PSB fibers have rough textures and low adhesion to the collector substrate.
+The rough surface and low adhesion is due to the rapid solvent volatilization, which results in fibers to solidify before landing on the substrate.
+The fast solidification minimize the fiber adhesion to the collector, causing the fibers to slip, and therefore the mechanical drag force in the fibers is reduced.
+Due to the low influence of the mechanical force, fibers are not stretched by the moving stage, which may explain the rough surface.
+
+On the other hand, the formulation regarding PVK deposited smooth fibers with good adhesion to the substrate, similar to the PEO/SU-8 solution.
+The thinnest fibers ($700 \textrm{ nm}$ in diameter) were achieved PVK in CHL formulation.
+Moreover, the PVK in SU-8 solution seems to be the formulation to replace the PEO in SU-8 solution.
+Assuming that the additional oxygen content in PEO negatively affects the fiber yield rate and electrical resistivity variance due to degassing during pyrolysis, the PCK does not contain additional oxygen content and has sp2-hybridized carbon which can promote the formation of graphitic carbon during pyrolysis.
+The already oxygen in SU-8 is necesary to create closed pores during annealing, characteristic of glass-like carbon.
+
+\section{Future work}
+
+Apart from the work done, this dissertation opens pending research to enable NFES for the fabrication of carbon structures.
+The following lists future work that could be done as a continuation of this thesis.
+
+\begin{itemize}
+\item Helgeson's model \cite{Helgeson2007} was thought to work with far-field electrospinning, hence the deviation of the NFES data from the model trend.
+For an accurate NFES fiber diameter prediction, the mechanical stresses introduced by the moving stage shall be considered in the model (Equation \ref{eqn:ohnesorgeNumberRelationship}).
+\item This work verifies the electro-spinnability of four new formulations, however fibers were not carbonized into carbon structures.
+Further work shall study the pyrolysis process of the proposed fibers to get carbon structures with good electrical conductivity.
+A photo-polymerization process could be introduced before pyrolyzation to increase the order of the molecules and achieve carbon with higher conductivity.
+\item Near-field electrospinning solutions require specific viscosities to initialte a polymer jet.
+The viscosity-concentration plot is a helpful tool to estimate the critical spinnable concentration of a polymer-solvent system.
+However there is room for improvement as this method only considers reological data.
+Other methods could be adopted to better tune other process parameters such as stage velocity, and applied voltage.
+\end{itemize}
+
+% enhance conductivity with photopolymerization, CNT streching, ...

### 2020-12-02 05_Thesis/THESIS_LaTeX/main.tex
defense update
slides update
final work done

@@
 
+\usepackage{xltabular}
+\usepackage{longtable}
+
 % keeps floats ‘in their place’, preventing them from floating past a
@@
 \usepackage{placeins}
+
+% import code snippets
+\usepackage{listings}
+\usepackage{xcolor}
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.99,0.99,0.96}
+\lstdefinestyle{mystyle}{
+  backgroundcolor   = \color{backcolour},
+  commentstyle      = \color{codegreen},
+  keywordstyle      = \color{magenta},
+  numberstyle       = \tiny\color{codegray},
+  stringstyle       = \color{codepurple},
+  basicstyle        = \ttfamily\small,
+  breakatwhitespace = false,
+  breaklines        = true,
+  captionpos        = b,
+  keepspaces        = true,
+  numbers           = left,
+  numbersep         = 2pt,
+  showspaces        = false,
+  showstringspaces  = false,
+  showtabs          = false,
+  tabsize           = 2,
+  aboveskip         = 0.1em,
+  belowskip         = 0.1em
+}
+\lstset{style=mystyle}
 
@@
 % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\thesistitle{Fabrication of Suspended Nanowires Through Mechano-Near-Field Electrospinning of Polymers in Solution for the Production of Glass-like Carbon}
+\thesistitle{Search for high-molecular weight linear polymers for the formulation of novel solutions for the fabrication of micro fibers by electromechanical spinning}
+% Fabrication of Suspended Nanowires Through Mechano-Near-Field Electrospinning of Polymers in Solution for the Production of Glass-like Carbon
 
@@
 Tecnológico de Monterrey\\
-\emph{Co-Advisor}
+\emph{Co-Advisor and Director of Program}
 
@@
 Dr. Marc Madou\\
-University of California\\
+University of California, Irvine\\
 \emph{Committee Member}
@@
 %\href{http://www.alanaguirre.com}{\supname}
-Dr. Sergio Omar Martínez Chapa\\
+Dr. Jaime Bonilla Ríos\\
 Tecnológico de Monterrey\\
@@
 \noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
-Dr. Martín Rogelio Bustamante Bello \\
+Dr. Rubén Morales Menéndez \\
 \emph{Associate Dean of Graduate Students}\\
@@
 
-Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to their high conductivity.
-Regardless of the high interest in the implementation of carbon nano-wires in several applications and devices, no feasible processes have been developed to fabricate carbon nano-wires with spatial control at a reasonable cost.
-Carbon nano-wires have been fabricated with the use of a photoresist, but little is known about polymers that can produce more conductive carbon nano-wires after pyrolysis.
-Various polymer solutions have been tested in near field electrospinning (NFES) and photopolymerization separately, however, few have been tested for nano-wire fabrication purposes through pyrolysis.
-The intention behind the thesis proposal is to implement rheology analyses of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nano-wires with them.
-This thesis work arises from the need to test a greater variety of polymers with the goal to design a polymer solution to fabricate carbon nano-wires with better conductivity than the current SU-8 polymeric nano-fibers.
-The research process will include the design of polymer solutions that can be electrospun, photopolymerized, and then pyrolyzed into conducting carbon nanowires.
-On the other hand, it is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of conductive carbon nano-wires in an inexpensive, continuous, simple and reproducible manner as central components for nano-sensors.
+Carbon nano-wires are versatile structures composed of carbon chains with a wide range of applications due to their high chemical resistance and electric properties.
+Regardless of the high interest in the implementation of carbon nano-wires in energy, environmental and health-care applications, no feasible processes have been developed to fabricate carbon nano-wires with spatial control at a reasonable cost.
+Carbon nano-wires have been fabricated with the use of a photoresist, but little is known about polymers that can produce conductive carbon nano-wires after pyrolysis.
+Various polymer solutions have been tested in near field electrospinning (NFES) and photopolymerization separately, however, few have been tested for nano-wire fabrication purposes through the process of spatio-temporal deposition with NFES, photo-polymerization for cross-linking and pyrolysis.
+The intention behind the thesis proposal is to use rheological analyses of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nano-wires with them.
+This thesis work arises from the need to test a greater variety of polymer-solvent combinations with the goal of designing a polymer solution to fabricate carbon nano-wires with higher conductivity than the current SU-8 polymeric nano-fibers.
+The present work includes the design of polymer solutions that can be electrospun, with the hope that the selected high molecular weight polymers can be photo-polymerized, and then pyrolyzed into conducting carbon nanowires.
+The overarching goal is to contribute towards the development of novel designed polymer solutions to achieve mass scale manufacturing of conductive carbon nano-wires in an inexpensive, continuous, simple and reproducible manner as central components for nano-sensors.
 \\
@@
 \include{./Chapters/4}
-%\include{./Chapters/5}
+\include{./Chapters/5}
 
@@
 \include{Appendices/Appendix_MicroscopyChar}
+\include{Appendices/Appendix_FiberDiameters}
+\include{Appendices/Appendix_ReviewTable}
+\include{Appendices/Appendix_ImageAnalysisCode}
 
@@
 
-\addcontentsline{toc}{chapter}{Bibliography}
-\printbibliography[title={Bibliography}]
+\printbibliography[heading=bibintoc, title={Bibliography}]
+% \addcontentsline{toc}{chapter}{Bibliography}
 
@@
 
-\newpage 
-\addcontentsline{toc}{chapter}{Curriculum Vitae}
-\includepdf[page=-,fitpaper=false,landscape=false]{./pdf/CV/CV}
+% \includepdf[page=-,fitpaper=false,landscape=false]{./pdf/CV/CV}
 

### 2020-12-04 05_Thesis/THESIS_LaTeX/main.tex
paper work

@@
 % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\thesistitle{Search for high-molecular weight linear polymers for the formulation of novel solutions for the fabrication of micro fibers by electromechanical spinning}
+\thesistitle{Search for High-Molecular Weight Linear Polymers for the Formulation of Novel Solutions for the Fabrication of Micro-Fibers by Electromechanical Spinning}
 % Fabrication of Suspended Nanowires Through Mechano-Near-Field Electrospinning of Polymers in Solution for the Production of Glass-like Carbon

### 2020-12-09 05_Thesis/THESIS_LaTeX/pdf/CV/CV.tex
MNT checklist

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\namesection{Osamu}{Katagiri}{ \urlstyle{same}\href{https://www.katagiri-mx.com/}{katagiri-mx.com} | \href{https://www.linkedin.com/in/osamu-k-84b2b940}{linkedin}\\ \href{mailto:osamu.katagiri@exatec.tec.mx}{osamu.katagiri@exatec.tec.mx}
+\namesection{Osamu}{Katagiri}{ \urlstyle{same}\href{https://www.katagiri-mx.com/}{katagiri-mx.com} | \href{https://www.linkedin.com/in/osamu-k-84b2b940}{linkedin}\\ \href{mailto:osamu.katagiri@exatec.tec.mx}{osamu.katagiri@exatec.tec.mx}\\
++52 55 2300 9176
 }
@@
 \location{Jan 2019 - Dec 2020 | Estado de México, MX}
+\location{Cum. GPA: 3.8 / 4.0}
 \sectionsep
@@
 \descript{BS in Digital Systems and Robotics}
-\location{Aug2012 - May 2016 | Querétaro, MX}
-\location{Cum. GPA: 3.6 / 4.0}
+\location{Aug 2012 - May 2016 | Querétaro, MX}
+\location{Cum. GPA: 3.5 / 4.0}
 \sectionsep
@@
 \subsection{Graduate}
-Thermodynamics of Materials \\
 Nano-structured Materials \\
+Carbon Nano-materials \\
 Plastics and Composites Engineering \\
-{\footnotesize \textit{\textbf{Rheology \& Electrospinning}}} \\
+\textit{\textbf{Rheology \& Electrospinning}} \\
 \sectionsep
@@
 \descript{| Embedded Software Eng. }
-\location{Jun 2018 - Dec 2019 | Querétaro, MX}
+\location{Jun 2018 - Dec 2018 | Querétaro, MX}
 \vspace{\topsep} % Hacky fix for awkward extra vertical space
 \begin{tightemize}
-\item At General Electric's Business \& General Aviation Power Software team, I develop and test critical software for Aviation Power products.
+\item At General Electric's Business \& General Aviation (BGA) Power Software team, I develop and test critical software for Aviation Power products.
 I have high responsibility in the development and in the documentation of the features and interactions with other systems.
@@
 \descript{| SW Edison Engineering Development Program }
-\location{June 2016 – May 2018 | Querétaro, MX}
+\location{Jun 2016 – May 2018 | Querétaro, MX}
 \begin{tightemize}
@@
 It is designed to accelerate participants' professional development through intense technical training.
+\item 1st rotation at GEIQ-BGA software validation \& verification team
+\item 2nd rotation at GEIQ-N\&G tools team
+\item 3rd and 4th rotations at GEIQ-BGA software development team
 \end{tightemize}
@@
 Alan Aguirre}} and \textbf{\href{https://orcid.org/0000-0001-5325-0079}{Phd.
-Dora Medina}} to determine the electro-spunability of various polymer solutions for the fabrication of carbon nano-wires.
+Dora Medina}} to determine the electro-spinnability of various polymer solutions for the fabrication of carbon nano-wires.
 \sectionsep
@@
 May 2018	& top 4\%                   & Software EEDP graduate at GE Aviation\\
-Aug 2015	& 1\textsuperscript{st}/1000 & GE 9th Lean Challenge\\
+Aug 2015	& 1\textsuperscript{st}/100 & GE 9th Lean Challenge\\
 Nov 2014	& 1\textsuperscript{st}/50  & GEIQ’s Robotics Project\\
